### 2016-03-13 paper/paper.tex
Start writing

% vim: set spell spelllang=en tw=100 et sw=4 sts=4 :

\documentclass{llncs}

\usepackage{showframe}

\usepackage{microtype}
\usepackage{complexity}                % \P, \NP etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \operatorname
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
\usepackage{placeins}                  % \FloatBarrier
\usepackage{cite}

\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing, patterns}

% lncs style
\crefname{algocf}{Algorithm}{Algorithms}
\Crefname{algocf}{Algorithm}{Algorithms}
\crefname{figure}{Fig.}{Figs.}
\Crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}
\crefname{proposition}{Proposition}{Propositions}
\Crefname{proposition}{Proposition}{Propositions}

\newcommand{\lineref}[1]{line~\ref{#1}}

\title{Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems}

\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]}\inst{1} \and Samba Ndojh Ndiaye\inst{2} \and Patrick
Prosser\inst{1} \and Christine Solnon \inst{3}}
\institute{University of Glasgow, Glasgow, Scotland \and
Universit\'e Lyon 1, LIRIS, UMR5205, F-69621, France  \and INSA-Lyon, LIRIS, UMR5205, F-69621, France}

\begin{document}

\maketitle

\begin{abstract}
    The maximum common subgraph problem is to find the largest subgraph common to two given graphs.
    This problem can be solved either by constraint-based search, or by reduction to the maximum
    clique problem. We evaluate these two approaches using modern algorithms. We also propose a
    restricted branching technique for the connected version of the problem, and show how to
    implement this in constraint-based and clique-inspired algorithms.
\end{abstract}

\section{Introduction}

Max common subgraph ?? cite some history and why we care

Connected \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08}

CP models \cite{DBLP:conf/cp/NdiayeS11}

Clique models, discuss below.

\subsection{Definitions and Notation}

\subsection{Datasets}

\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}

\section{Re-Evaluating the Clique Model}

Previous experimental work has used a maximal clique enumeration algorithm, even for the
maximisation problem. ?? check this! I recall someone using a bad max clique algorithm too.
\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}

We instead use a maximum clique algorithm. There has been a lot of recent
research on this
\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15}.

Also sparse stuff, but association graphs aren't sparse enough.

Say which clique algorithm we're using.

\subsection{Reduction to Maximum Clique in an Association Graph}

Explain association graph. ?? cite history, connections to microstructure

Discuss how edge labels, vertex labels, directed edges, etc, are handled. Note that we can generally
only handle very local side constraints, or injectivity (which is decomposable).

\subsection{Experimental Evaluation}

\cref{figure:unconnected-33}

\cref{figure:unconnected-plain}

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-33}
    \caption{Clique versus CP, 33\% labelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, the best
    clique approach compared to the best CP approach: the colour at a point indicates the number of
    instances with these runtimes.} \label{figure:unconnected-33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-plain}
    \caption{Clique versus CP, undirected, unlabelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, the best
    clique approach compared to the best CP approach: the colour at a point indicates the number of
    instances with these runtimes.} \label{figure:unconnected-plain}
\end{figure}

\subsection{Parallel Search}

\cite{DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16}

?? Stuff on EHPs, how work stealing matters here too

\section{Maximum Common Connected Subgraph}

Connectedness is not hereditary, but can be built up one vertex at a time. Alternatively,
connectedness is a constraint.

\subsection{Connectedness via Restricted Branching}

The key idea is that whenever we branch (except for the first choice we make), we select only from
variables which correspond to vertices which are adjacent to at least one other variable which has
been instantiated to a non-null value. If no such variables remain, the subgraph we are building
cannot grow any further, and all remaining variables must be instantiated to null.

?? We only need to work off whichever input gives us the variables. But the CP approach seems to
look at both?

?? Patrick reckons this reminds him of Prim's algorithm for minimum spanning trees.

\subsection{Connectedness as a Constraint}

Connectedness \cite{Brown:2005}

Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}

\subsection{A Clique-Inspired Algorithm}

We can use the branching idea inside a ``maximum clique'' algorithm, by providing additional
information on the meaning behind vertices in the association graph as input. To fit in with the
bitset encoding, we preconstruct a bitset for each vertex $v$ in the association graph, saying which
association graph vertices correspond to vertices adjacent to $v$ in the left-hand graph.

?? This gets confusing. Maybe we can come up with some clever terminology: when I was talking about
search trees and clique algorithms, I used the term 'node' for something in a search tree, and
'vertex' for something in a graph. Maybe we can use different terms for things in the association
graph, versus things in the two input graphs? Should we call association graph vertices
'assignments' and edges 'compatibilities' instead?

We keep track of allowed branching vertices in a set we call $A$. We only branch on vertices which
are present in $P \cap A$.

?? We could make this faster, since it'll be the same for each vertex corresponding to the same
left-hand vertex.

We must also ensure that the bound remains valid. The branching and bounding are integrated, and it
is not possible to alter the branching rule without also changing the bound. Our observation is that
the bound rule works for any valid colouring, not just a greedy one, so long as we always iterate
from the last colour class downwards, without skipping any vertices. Thus we construct a two-pass
greedy colouring such that all the vertices in $P \setminus A$ are to the left, and the vertices in
$P \cap A$ are to the right.

\cite{DBLP:conf/cp/McCreeshP14}

\subsection{Experimental Evaluation}

\paragraph{Connected, Undirected, 33\% Labelled} \cref{figure:connected-undir33} Above two seconds,
    the clique approach dominates except for three instances, and there is only one instance which
    the CP model can solve but the clique model cannot (?? is this an EHP and does parallel get rid
    of it?). The clique model is unable to solve only ??  instances within one hour, ?? all of which
    have 90 or 100 vertices.  On the other hand, for trivial instances, the clique approach is often
    expensive due to the association graph construction.

\paragraph{Connected, Undirected, Unlabelled} \cref{figure:connected-plain}, looks like the clique
approach doesn't do so well\ldots

?? My gut feeling is that if we have edge labels, the clique model wins, and if we don't, it's
likely to lose. So maybe I should run some experiments with vertex labels but not edge labels to
test this.

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-undir33}
    \caption{Clique versus CP, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
        the cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the best clique approach compared to the best CP approach: the colour at a point
        indicates the number of instances with these runtimes.} \label{figure:connected-undir33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus CP, connected, undirected, unlabelled, up to 25 vertices (and some 30 and
        35, which are still running\ldots). On the top, the cumulative number of instances solved by
    each approach, in under a certain time. On the bottom, the best clique approach compared to the
best CP approach: the colour at a point indicates the number of instances with these runtimes.}
\label{figure:connected-plain}
\end{figure}

\subsection{Parallel Search}

\cite{DBLP:conf/ictai/MinotNS15}

\section{Conclusion}

Some immoral perspectives on closely coupling branching with a particular constraint. Whether this
is useful for other things, like ASP.

We haven't discussed partial subgraphs, or connected directed.

Possibly portfolios.

Better instances.

\FloatBarrier

\bibliographystyle{splncs}
\bibliography{paper}

\end{document}

### 2016-03-13 paper/heatmapify.rb

@@ -1,0 +1,24 @@
+#!/usr/bin/ruby
+# vim: set sw=4 sts=4 et tw=80 :
+
+buckets = Hash.new(0)
+
+IO.readlines(ARGV[0]).each do | line |
+    words = line.split(' ')
+
+    x = words[1].to_f * 1000
+    bx = if x < 1 then 0 else (100 * (Math.log(x + 0.1) / Math.log(3600000))).round end
+
+    y = words[2].to_f
+    by = if y < 1 then 0 else (100 * (Math.log(words[2].to_f + 0.1) / Math.log(3600000))).round end
+
+    abort "bx is " + bx.to_s + " by is " + by.to_s if bx < 0 || bx > 100 || by < 0 || by > 100
+    buckets[[bx, by]] += 1
+end
+
+0.upto 100 do | x |
+    0.upto 100 do | y |
+        print(buckets[[x, y]].to_s + " ")
+    end
+    puts
+end

### 2016-03-14 paper/paper.tex
Funders

@@
 
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
+
 \title{Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems}
@@
 \author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
-Research Council [grant number EP/K503058/1]}\inst{1} \and Samba Ndojh Ndiaye\inst{2} \and Patrick
-Prosser\inst{1} \and Christine Solnon \inst{3}}
+    Research Council [grant number EP/K503058/1]}\inst{1} \and Samba Ndojh Ndiaye\thanks{This work
+was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)}\inst{2} \and Patrick
+Prosser\inst{1} \and Christine Solnon\samethanks[2] \inst{3}}
 \institute{University of Glasgow, Glasgow, Scotland \and

### 2016-03-15 paper/paper.tex
An algorithm
More graphs and data

@@
 
+\begin{algorithm}[tb] \DontPrintSemicolon
+\nl $\FuncSty{cliquishMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
+\nl \Begin{
+    \nl $\KwSty{global} ~ C_{\mathit{max}} \gets \emptyset$ \;
+    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
+    \nl $\FuncSty{expand}(G, \operatorname{V}(G), \emptyset, \emptyset)$ \;
+    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
+}
+\vspace{1ex}
+\nl $\FuncSty{expand}$ :: (Graph $G$, Set $C$, Set $A$, Set $P$) \;
+\nl \Begin{
+    \nl $\mathit{colourClasses} \gets \FuncSty{colour}(G, A, P)$ \;
+    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
+        \nl \ForEach{$v \textnormal{~in~} \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
+            \nl \lIf{$|C| + \FuncSty{length}(\mathit{colourClasses}) \leq |C_{\mathit{max}}|$}{\KwSty{return}}
+            \nl \lIf{$v \notin A ~ \KwSty{and} ~ C \ne \emptyset$}{\KwSty{return}}
+            \nl $C' \gets C \cup \{ v \}$\;
+            \nl \lIf{$|C'| > |C_{\mathit{max}}|$}{$C_{\mathit{max}} \gets C'$}
+            \nl $A' \gets A \cup \FuncSty{connected}(v)$ \;
+            \nl $P' \gets P \cap \operatorname{N}(G, v)$ \;
+            \nl \lIf{$P' \neq \emptyset$}{$\FuncSty{expand}(G, C', A', P')$}
+         }
+         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
+     }
+}
+\vspace{1ex}
+\nl $\FuncSty{colour}$ :: (Graph $G$, Set $A$, Set $P$) $\rightarrow$ List of List of Vertex \;
+\nl \Begin{
+    \nl $\KwSty{return}$ a greedy colouring of $P \setminus A$, followed by a greedy colouring of $P
+    \cap A$, both using static degree order in $G$ \;
+}
+\caption{A clique-inspired algorithm for MCCIS.}
+\label{algorithm:mc}
+\end{algorithm}
+
 We can use the branching idea inside a ``maximum clique'' algorithm, by providing additional
@@
     \input{gen-graph-connected-plain}
-    \caption{Clique versus CP, connected, undirected, unlabelled, up to 25 vertices (and some 30 and
-        35, which are still running\ldots). On the top, the cumulative number of instances solved by
-    each approach, in under a certain time. On the bottom, the best clique approach compared to the
-best CP approach: the colour at a point indicates the number of instances with these runtimes.}
+    \caption{Clique versus CP, connected, undirected, unlabelled, up to 35 vertices. On the top, the
+    cumulative number of instances solved by each approach, in under a certain time. On the bottom,
+    the best clique approach compared to the best CP approach: the colour at a point indicates the
+    number of instances with these runtimes.}
 \label{figure:connected-plain}

### 2016-03-21 paper/paper.tex
Tweaks

@@
 
-\usepackage{showframe}
+% \usepackage{showframe}
 
@@
     clique problem. We evaluate these two approaches using modern algorithms. We also propose a
-    restricted branching technique for the connected version of the problem, and show how to
-    implement this in constraint-based and clique-inspired algorithms.
+    restricted branching approach for the connected version of the problem,
+    show how to implement this in constraint-based and clique-inspired
+    algorithms, and compare it to conventional propagation.
 \end{abstract}
@@
     \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
-    \nl $\FuncSty{expand}(G, \operatorname{V}(G), \emptyset, \emptyset)$ \;
+    \nl $\FuncSty{expand}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \;
     \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;

### 2016-03-22 paper/paper.tex
No short variable names
More stuffing

--- 2016-03-14 paper/paper.tex
@@
 
+\renewcommand{\topfraction}{0.9}
+\renewcommand{\bottomfraction}{0.8}
+\renewcommand{\textfraction}{0.05}
+\renewcommand{\floatpagefraction}{0.85}
+
 \title{Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems}
@@
 
-\subsection{A Clique-Inspired Algorithm}
+\subsection{Connectedness in an Association Graph Algorithm}
+
+\begin{algorithm}[tb] \DontPrintSemicolon
+\nl $\FuncSty{associationMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
+\nl \Begin{
+    \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \;
+    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
+    \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \;
+    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
+}
+\vspace{1ex}
+\nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
+\nl \Begin{
+    \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \;
+    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{branchable}),$ \;
+    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{branchable}))$ \;
+    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
+        \nl \ForEach{$v \in \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
+            \nl \lIf{$|\mathit{solution}| + \FuncSty{length}(\mathit{colourClasses}) \leq |\mathit{incumbent}|$}{\KwSty{return}}
+            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne \emptyset$}{\KwSty{return}}
+            \nl $\mathit{solution}' \gets \mathit{solution} \cup \{ v \}$\;
+            \nl \lIf{$|\mathit{solution}'| > |\mathit{incumbent}|$}{$\mathit{incumbent} \gets
+            \mathit{solution}'$}
+            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \FuncSty{connected}(v)$ \;
+            \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \;
+            \nl \lIf{$\mathit{remaining}' \neq \emptyset$}{$\FuncSty{search}(G, \mathit{solution}',
+            \mathit{branchable}', \mathit{remaining}')$}
+         }
+         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
+     }
+}
+\vspace{1ex}
+\nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;
+\nl \Begin{
+    \nl $\mathit{result} \gets []$ \;
+    \nl \While{$\mathit{uncoloured} \ne \emptyset$}{
+        \nl $\mathit{colourClass} \gets []$ \;
+        \nl $\mathit{colourable} \gets \mathit{uncoloured}$ \;
+        \nl \While{$\mathit{colourable} \ne \emptyset$}{
+            \nl $v \gets \textnormal{the first vertex from}~\mathit{uncoloured}~\textnormal{by
+            static degree order from}~G$ \;
+            \nl $\FuncSty{append}(\mathit{colourClass}, v)$ \;
+            \nl $uncoloured \gets uncoloured \setminus \{ v \}$ \;
+            \nl $\mathit{colourable} \gets \mathit{colourable} \setminus \operatorname{N}(G, v)$ \;
+        }
+        \nl $\FuncSty{append}(\mathit{result}, \mathit{colourClass})$ \;
+    }
+    \nl $\KwSty{return} ~ \mathit{result}$ \;
+}
+\caption{An algorithm for MCCIS via an association graph.}
+\label{algorithm:mc}
+\end{algorithm}
 

### 2016-03-22 paper/heatmapify.rb

@@ -2,22 +2,23 @@
 # vim: set sw=4 sts=4 et tw=80 :
 
 buckets = Hash.new(0)
+granularity = 100
 
 IO.readlines(ARGV[0]).each do | line |
     words = line.split(' ')
 
-    x = words[1].to_f * 1000
-    bx = if x < 1 then 0 else (100 * (Math.log(x + 0.1) / Math.log(3600000))).round end
+    x = words[1].sub('1e10', '3600').to_f * 1000
+    bx = if x < 1 then 0 else (granularity * (Math.log(x + 0.1) / Math.log(3600000))).round end
 
-    y = words[2].to_f
-    by = if y < 1 then 0 else (100 * (Math.log(words[2].to_f + 0.1) / Math.log(3600000))).round end
+    y = words[2].sub('1e10', '3600000').to_f
+    by = if y < 1 then 0 else (granularity * (Math.log(y + 0.1) / Math.log(3600000))).round end
 
-    abort "bx is " + bx.to_s + " by is " + by.to_s if bx < 0 || bx > 100 || by < 0 || by > 100
+    abort "bx is " + bx.to_s + " by is " + by.to_s if bx < 0 || bx > granularity || by < 0 || by > granularity
     buckets[[bx, by]] += 1
 end
 
-0.upto 100 do | x |
-    0.upto 100 do | y |
+0.upto granularity do | x |
+    0.upto granularity do | y |
         print(buckets[[x, y]].to_s + " ")
     end
     puts

### 2016-03-23 paper/paper.tex
Change words
More writing

@@
 \newcommand{\lineref}[1]{line~\ref{#1}}
+\newcommand{\twolinesref}[2]{lines~\ref{#1} and~\ref{#2}}
 
 \newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\renewcommand{\topfraction}{0.9}
-\renewcommand{\bottomfraction}{0.8}
-\renewcommand{\textfraction}{0.05}
-\renewcommand{\floatpagefraction}{0.85}
 
@@
 \subsection{Definitions and Notation}
+
+A \emph{graph} $G = (V, E)$ consists of a set of vertices $V$ and a set of edges $E \subseteq V
+\times V$. In this paper our graphs may be directed, may have loops, and there is a label associated
+with each vertex and with each edge. For convenience, we treat undirected graphs as being directed
+graphs with symmetric adjacencies, and for unlabelled graphs we treat each vertex as having the same
+label, and each edge as having the same label. We write $\operatorname{V}(G)$ for $V$, and
+$\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood} of a vertex $v$ (that is, the set
+of vertices $w$ such that either $(v, w)$ or $(w, v)$ is an edge).
+
+Given two graphs $G_1$ and $G_2$, we say two pairs of vertices $(v_1, w_1) \in \operatorname{V}(G_1)
+\times \operatorname{V}(G_1)$ and $(v_2, w_2) \in \operatorname{V}(G_2) \times
+\operatorname{V}(G_2)$ are \emph{compatible} if both $v_1$ and $w_1$ and $v_2$ and $w_2$ are either
+non-adjacent or adjacent with the same label, and if the same holds for $(w_1, v_1)$ and $(w_2,
+v_2)$.  We say two vertices $v \in \operatorname{V}(G_1)$ and $w \in \operatorname{V}(G_2)$ are
+\emph{compatible} if they share the same label, and $(v, v)$ is compatible with $(w, w)$.
 
@@
 
-?? Stuff on EHPs, how work stealing matters here too
+?? Stuff on EHPs, how work stealing matters here too \cite{DBLP:journals/jco/BatsynGMP14}
 
@@
 connectedness is a constraint.
+
+\subsection{Connectedness as a Constraint}
+
+Connectedness \cite{Brown:2005}
+
+Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}
 
@@
 
-\subsection{Connectedness as a Constraint}
-
-Connectedness \cite{Brown:2005}
-
-Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}
+?? We need a picture here.
 
@@
 
-\begin{algorithm}[tb] \DontPrintSemicolon
+\begin{algorithm}[p] \DontPrintSemicolon
 \nl $\FuncSty{associationMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
 \nl \Begin{
-    \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \;
-    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
-    \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \;
-    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
+    \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \label{incumbent} \;
+    \nl $G \gets \FuncSty{associationGraph}(G_1, G_2)$ \label{buildassoc} \;
+    \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \label{firstsearch} \;
+    \nl $\KwSty{return} ~ \mathit{incumbent}$ \;
 }
@@
 \nl \Begin{
-    \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \;
+    \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \label{makecolours} \;
     $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{branchable}),$ \;
     $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{branchable}))$ \;
-    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
-        \nl \ForEach{$v \in \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
-            \nl \lIf{$|\mathit{solution}| + \FuncSty{length}(\mathit{colourClasses}) \leq |\mathit{incumbent}|$}{\KwSty{return}}
-            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne \emptyset$}{\KwSty{return}}
-            \nl $\mathit{solution}' \gets \mathit{solution} \cup \{ v \}$\;
+    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$\label{outerloop}}{
+        \nl \ForEach{$v \in \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$\label{innerloop}}{
+            \nl \lIf{$|\mathit{solution}| + \FuncSty{length}(\mathit{colourClasses}) \leq
+            |\mathit{incumbent}|$}{\KwSty{return}\label{bound}}
+            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne
+            \emptyset$}{\KwSty{return} \label{acceptbranchable}}
+            \nl $\mathit{solution}' \gets \mathit{solution} \cup \{ v \} \label{addv} \label{addvtosolution} $\;
             \nl \lIf{$|\mathit{solution}'| > |\mathit{incumbent}|$}{$\mathit{incumbent} \gets
-            \mathit{solution}'$}
-            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \FuncSty{connected}(v)$ \;
-            \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \;
+            \mathit{solution}'$ \label{newincumbent}}
+            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \FuncSty{connected}(G, v)$ \label{addtobranchable} \;
+            \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \label{filterremaining} \;
             \nl \lIf{$\mathit{remaining}' \neq \emptyset$}{$\FuncSty{search}(G, \mathit{solution}',
-            \mathit{branchable}', \mathit{remaining}')$}
+            \mathit{branchable}', \mathit{remaining}')$\label{recursesearch}}
          }
@@
     \nl $\mathit{result} \gets []$ \;
-    \nl \While{$\mathit{uncoloured} \ne \emptyset$}{
-        \nl $\mathit{colourClass} \gets []$ \;
+    \nl \While{$\mathit{uncoloured} \ne \emptyset$\label{whileuncoloured}}{
+        \nl $\mathit{colourClass} \gets []$ \label{newcolourclass} \;
         \nl $\mathit{colourable} \gets \mathit{uncoloured}$ \;
@@
             \nl $v \gets \textnormal{the first vertex from}~\mathit{uncoloured}~\textnormal{by
-            static degree order from}~G$ \;
-            \nl $\FuncSty{append}(\mathit{colourClass}, v)$ \;
+            static degree order from}~G$ \label{selectvtocolour} \;
+            \nl $\FuncSty{append}(\mathit{colourClass}, v)$ \label{addtocolourclass} \;
             \nl $uncoloured \gets uncoloured \setminus \{ v \}$ \;
@@
 }
+\vspace{1ex}
+\nl $\FuncSty{connected}$ :: (Graph $G$, Vertex $v$) $\rightarrow$ Set \;
+\nl \Begin{
+    \nl $\KwSty{return} ~ \{ w \in G : \FuncSty{first}(w) \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \;
+}
+\vspace{1ex}
+\nl $\FuncSty{associationGraph}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Graph \;
+\nl \Begin{
+    \nl $V \gets \{ (v_1, v_2) \in G_1 \times G_2 : \FuncSty{compatible}(v_1, v_2) \}$ \;
+    \nl $E \gets \{ ((v_1, v_2), (w_1, w_2)) \in V \times V : \FuncSty{compatible}((v_1, w_1), (v_2,
+    w_2)) \}$ \;
+    \nl $\KwSty{return} ~ (V, E)$ \;
+}
 \caption{An algorithm for MCCIS via an association graph.}
-\label{algorithm:mc}
+\label{algorithm:mccis}
 \end{algorithm}
 
-We can use the branching idea inside a ``maximum clique'' algorithm, by providing additional
-information on the meaning behind vertices in the association graph as input. To fit in with the
-bitset encoding, we preconstruct a bitset for each vertex $v$ in the association graph, saying which
-association graph vertices correspond to vertices adjacent to $v$ in the left-hand graph.
+It is not possible to determine connectedness from a raw association graph. However, we can take a
+maximum clique algorithm and mimic the branching strategy if we have access to the underlying graphs
+and can determine the ``meaning'' of the association graph vertices.
 
-?? This gets confusing. Maybe we can come up with some clever terminology: when I was talking about
-search trees and clique algorithms, I used the term 'node' for something in a search tree, and
-'vertex' for something in a graph. Maybe we can use different terms for things in the association
-graph, versus things in the two input graphs? Should we call association graph vertices
-'assignments' and edges 'compatibilities' instead?
+Most modern maximum clique algorithms for dense graphs use some variation of greedy graph colouring
+as a bound---the underlying observation is that each vertex in a clique must be given a different
+colour in a colouring, so if we can colour a subset of vertices using $k$ colours then a maximum
+clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
+heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
+last colour class created. Because of this coupling of branching and the bound (which is important
+in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
+viewed as variables \cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for
+branching at each stage inside a clique algorithm, we would lose completeness. Thus we must adapt
+the bound to take into account restricted branching.
 
-We keep track of allowed branching vertices in a set we call $A$. We only branch on vertices which
-are present in $P \cap A$.
+In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds an MCCIS via an
+association graph. If the additional
+branching restrictions are removed, the core of the algorithm is what Prosser
+\cite{DBLP:journals/algorithms/Prosser12} calls the ``MCSa1'' variant of a series of algorithms due
+to Tomita \textit{et al.}\
+\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
+bitset encoding approach due to San Segundo \textit{et al.}\
+\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13} (and we refer the reader to these
+papers for implementation details on how to use bitsets and other data structures to implement the
+colouring stage with very low constant factors).
 
-?? We could make this faster, since it'll be the same for each vertex corresponding to the same
-left-hand vertex.
+We begin by building the association graph (\lineref{buildassoc}). The main part of the algorithm
+then works by building up candidate cliques in the $\mathit{solution}$ variable, by recursive calls
+to the $\mathit{search}$ procedure---starting from the empty set (\lineref{firstsearch}), each
+recursive subcall adds one vertex to $\mathit{solution}$ (\lineref{addv}) in such a way that
+$\mathit{solution}$ is always a clique which corresponds to a connected common subgraph. The
+$\mathit{remaining}$ set contains the set of vertices which are adjacent to every vertex in
+$\mathit{solution}$, and which have not yet been accepted or rejected (and so initially it contains
+every vertex). The main loops in the $\FuncSty{search}$ procedure
+(\twolinesref{outerloop}{innerloop}) have the effect of iterating over each vertex in this set in a
+particular order---each vertex $v$ is selected in turn, and then a recursive call is made to
+consider the effects of including $v$ in $\mathit{solution}$ (\lineref{recursesearch}), followed by
+the next iteration where $v$ is instead rejected. When $v$ is accepted, we add it to the new
+$\mathit{solution'}$ (\lineref{addvtosolution}), and create a new $\mathit{remaining'}$ containing
+only the vertices in $\mathit{remaining}$ which are adjacent to $v$ (\lineref{filterremaining}).
 
-We must also ensure that the bound remains valid. The branching and bounding are integrated, and it
-is not possible to alter the branching rule without also changing the bound. Our observation is that
-the bound rule works for any valid colouring, not just a greedy one, so long as we always iterate
-from the last colour class downwards, without skipping any vertices. Thus we construct a two-pass
-greedy colouring such that all the vertices in $P \setminus A$ are to the left, and the vertices in
-$P \cap A$ are to the right.
+The $\mathit{branchable}$ set contains the set of association graph vertices which correspond to
+vertices adjacent to an already-accepted vertex in the first input graph---in CP terms, it is the
+set of assignments which could be made next which preserve connectedness. (Using only one of the two
+input graphs is sufficient for correctness, and has the advantage that the $\FuncSty{connected}$
+function may be implemented as a simple lookup into a precomputed array which maps each vertex in
+the first input graph to a bitset.) At the top of search, this set is empty, and is not used (our
+first vertex selection is special, and does not care about connectedness). At subsequent depths, we
+may only accept vertices which are in this set, and if no such vertices remain then we return
+immediately (\lineref{acceptbranchable}). When recursing, we extend $\mathit{branchable}$ with the
+new vertices permitted by our acceptance of the branching $v$ (\lineref{addtobranchable}). Note that
+we are assuming that inside the main loops, we encounter every vertex in $\mathit{remaining} \cap
+\mathit{connected}$ before any vertex in $\mathit{remaining} \setminus \mathit{connected}$.
 
-\cite{DBLP:conf/cp/McCreeshP14}
+As we proceed, we keep track of the best solution we have found so far---this is stored in the
+$\mathit{incumbent}$ variable (\twolinesref{incumbent}{newincumbent}). We use the incumbent,
+together with a colour bound, to prune portions of the search space which cannot contain a better
+solution. The colour bound operates as follows: at each entry to the $\FuncSty{search}$ procedure,
+we produce a greedy colouring of the vertices in $\mathit{remaining}$ (\lineref{makecolours}). This
+greedy colouring gives us a list of colour classes, each of which is a list of pairwise non-adjacent
+vertices. The two loops (\twolinesref{outerloop}{innerloop}) then iterate over each colour class,
+from last to first, and then over each vertex in that colour class, again from last to first.
+(Rather than actually using a list of lists and removing items, this process should be implemented
+using a pair of immutable flat arrays. This technique is described elsewhere
+\cite{DBLP:conf/cp/McCreeshP14}, so we do not discuss it here.) Finally, if at any point the number
+of remaining colour classes plus the number of vertices currently present in $\mathit{solution}$ is
+not strictly greater than the size of the incumbent, then we may backtrack immediately
+(\lineref{bound}).
+
+Finally, we describe the colouring process. In conventional clique algorithms, a simple greedy
+sequential colouring is used (possibly with the help of previous colourings to reduce the
+computational cost \cite{DBLP:conf/lion/NikolaevBS15}, and possibly with shortcuts taken for certain
+vertices \cite{DBLP:journals/cor/SegundoT14}, and possibly followed by a repair step to
+improve the colouring \cite{DBLP:conf/walcom/TomitaSHTW10}, or stronger bounding rules based upon
+MaxSAT inference \cite{DBLP:conf/ictai/LiFX13,DBLP:conf/lion/LiJX15,DBLP:journals/cor/SegundoNB15}).
+Such colourings will not give us the required property that vertices in $\mathit{remaining} \cap
+\mathit{connected}$ come last (so they are selected first by the reverse branching order). Thus we
+produce two greedy sequential colourings, first considering the non-branching vertices in
+$\mathit{remaining} \setminus \mathit{connected}$, followed by the branching vertices, and
+concatenate them (\lineref{makecolours}). This produces a valid colouring, since we do not merge any
+colour classes between the two stages, although it may use more colours than a single colouring
+would.
+
+Our $\FuncSty{colour}$ procedure is the same as the bit-parallel algorithm introduced by San Segundo
+\textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}. While we have remaining vertices to colour
+(\lineref{whileuncoloured}), we start a new colour class (\lineref{newcolourclass}), and then
+repeatedly pick a legal vertex to add to that colour class (\lineref{addtocolourclass}).  The
+selection of the next vertex to colour (\lineref{selectvtocolour}) may be performed efficiently in
+hardware if the association graph is permuted to be in degree order at the top of search. (Other
+initial vertex orderings have been considered on general clique problems
+\cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}; it is possible that special
+properties of the association graph could be exploited in this step.)
 

### 2016-03-24 paper/paper.tex
Pictures and text

@@
 \usepackage{cite}
+\usepackage[bottom]{footmisc}
 
@@
     clique problem. We evaluate these two approaches using modern algorithms. We also propose a
-    restricted branching approach for the connected version of the problem,
-    show how to implement this in constraint-based and clique-inspired
-    algorithms, and compare it to conventional propagation.
+    restricted branching approach for the connected version of the problem, show how to implement
+    this in constraint-based and clique-inspired algorithms, and compare it to conventional
+    propagation.
 \end{abstract}
@@
 
-Max common subgraph ?? cite some history and why we care
+\begin{figure}[b] % first page if possible
+    \centering
+    \begin{tikzpicture}[scale=0.4]%{{{
+        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+        \begin{scope}
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
 
-Connected \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08}
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [color=uofgsandstone!40] (M4) -- (M6);
+            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [color=uofgsandstone!40] (M6) -- (M8);
+            \draw [color=uofgsandstone!40] (M6) -- (M9);
+            \draw [very thick] (M7) -- (M9);
+            \draw [very thick] (M8) -- (M9);
+        \end{scope}
 
-CP models \cite{DBLP:conf/cp/NdiayeS11}
+        \begin{scope}[xshift=5cm]
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=1pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
 
-Clique models, discuss below.
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [color=uofgsandstone!40] (M4) -- (M6);
+            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [very thick] (M7) -- (M8);
+            \draw [very thick] (M8) -- (M9);
+        \end{scope}
+
+        \begin{scope}[xshift=12cm]
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [very thick] (M4) -- (M6);
+            \draw [very thick] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [very thick] (M6) -- (M8);
+            \draw [color=uofgsandstone!40] (M6) -- (M9);
+            \draw [color=uofgsandstone!40] (M7) -- (M9);
+            \draw [color=uofgsandstone!40] (M8) -- (M9);
+        \end{scope}
+
+        \begin{scope}[xshift=17cm]
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=1pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=1pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [very thick] (M4) -- (M6);
+            \draw [very thick] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [very thick] (M6) -- (M7);
+            \draw [draw=uofgsandstone!40] (M7) -- (M8);
+            \draw [draw=uofgsandstone!40] (M8) -- (M9);
+        \end{scope}
+\end{tikzpicture}
+\caption{A maximum common induced subgraph of the first two graphs has eight vertices. There are
+four symmetric solutions, all involving the shaded vertices. However, if we require the common
+subgraph to be connected, only seven vertices may be selected---one way to do this is shown in the
+third and fourth graphs.}\label{figure:mcsexample}
+\end{figure}
+
+A common subgraph of two graphs is a graph which is subgraph-isomorphic to both graphs---we
+illustrate this concept in \cref{figure:mcsexample}, and define this formally below. Finding a
+maximum common subgraph gives a measure of the similarity between two graphs, and allows for the
+edit distance to be computed ?? cite. Maximum common subgraph problems have applications in
+chemistry, computer vision, ?? cite.
+
+One approach to this problem is via constraint programming (CP) models
+\cite{DBLP:conf/cp/NdiayeS11}. These models are based upon constructing an injective mapping from
+the vertices of one graph (typically the smaller) to the other, in a similar manner to subgraph
+isomorphism algorithms ?? cite. However, to allow for a partial mapping, a special null value is
+added to each domain (and the injectivity condition does not apply to null values). The problem then
+becomes an optimisation problem, where we seek to minimise the number of null values. ?? find a way
+to work weak all diff in here. Unfortunately, this null value invalidates many of the invariants
+used for subgraph isomorphism---we may no longer reason using the degree of vertices, or the
+distances between them, for example, and so the problem can be much more challenging in practice.
+
+Another popular approach is to reduce the problem to finding a maximum clique (or sometimes,
+equivalently, an independent set or a vertex cover) in an association graph (which we describe
+below). This seems to be less effective in practice, but previous experimental evaluations have used
+weak clique algorithms, or even clique enumeration algorithms. Maximum clique algorithms are an
+active research area
+\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16},
+and so the first half of this paper re-evaluates this approach using a modern algorithm.
+
+(Other approaches have been tried, including MIP ?? cite, SAT.)
+
+A particularly challenging variant of the maximum common subgraph problem requires the selected
+subgraph to be connected \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08}. The second half
+of the paper looks at this variant. In principle, for a CP approach, we may simply add a ``forms a
+connected graph'' global constraint to the model. However, we will show that better results may be
+obtained via a special branching rule. We then explain how to adapt this branching rule to run
+inside a clique-like algorithm, to solve the problem via an association graph.
 
@@
 research on this
-\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15}.
+.
 

### 2016-03-28 paper/paper.tex
More things

--- 2016-03-23 paper/paper.tex
@@
     This problem can be solved either by constraint-based search, or by reduction to the maximum
-    clique problem. We evaluate these two approaches using modern algorithms. We also propose a
-    restricted branching approach for the connected version of the problem,
-    show how to implement this in constraint-based and clique-inspired
-    algorithms, and compare it to conventional propagation.
+    clique problem. We evaluate these two approaches using modern algorithms. We also investigate a
+    restricted branching approach for the connected version of the problem, show how to implement
+    this in constraint-based and clique-inspired algorithms, and compare it to conventional
+    propagation.
 \end{abstract}
@@
 
-Max common subgraph ?? cite some history and why we care
+\begin{figure}[b] % first page if possible
+    \centering
+    \begin{tikzpicture}[scale=0.33]%{{{
+        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+        \begin{scope}[rotate=90]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
 
-Connected \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08}
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [color=uofgsandstone!40] (M4) -- (M6);
+            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [color=uofgsandstone!40] (M6) -- (M8);
+            \draw [color=uofgsandstone!40] (M6) -- (M9);
+            \draw [very thick] (M7) -- (M9);
+            \draw [very thick] (M8) -- (M9);
+        \end{scope}
 
-CP models \cite{DBLP:conf/cp/NdiayeS11}
+        \begin{scope}[xshift=7cm, rotate=90]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
 
-Clique models, discuss below.
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [color=uofgsandstone!40] (M4) -- (M6);
+            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [very thick] (M7) -- (M8);
+            \draw [very thick] (M8) -- (M9);
+        \end{scope}
+
+        \begin{scope}[xshift=18cm, rotate=90]
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [very thick] (M4) -- (M6);
+            \draw [very thick] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [very thick] (M6) -- (M8);
+            \draw [color=uofgsandstone!40] (M6) -- (M9);
+            \draw [color=uofgsandstone!40] (M7) -- (M9);
+            \draw [color=uofgsandstone!40] (M8) -- (M9);
+        \end{scope}
+
+        \begin{scope}[xshift=25cm, rotate=90]
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [very thick] (M3) -- (M5);
+            \draw [very thick] (M4) -- (M6);
+            \draw [very thick] (M5) -- (M6);
+            \draw [very thick] (M3) -- (M1);
+            \draw [very thick] (M6) -- (M7);
+            \draw [draw=uofgsandstone!40] (M7) -- (M8);
+            \draw [draw=uofgsandstone!40] (M8) -- (M9);
+        \end{scope}
+\end{tikzpicture}
+\caption{A maximum common induced subgraph of the first two graphs has eight vertices. There are
+four symmetric solutions, all involving the shaded vertices. However, if we require the common
+subgraph to be connected, only seven vertices may be selected---one way to do this is shown in the
+third and fourth graphs.}\label{figure:mcsexample}
+\end{figure}
+
+Maximum common subgraph problems arise in biology and chemistry
+\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, computer vision ?? what should we cite?, ??
+anything else?, both directly and as a way of measuring the similarity or difference between two
+graphs \cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate
+this in \cref{figure:mcsexample}, and define the problem formally below.
 
@@
 
+?? Get edge vs vertex in early.
+
+\subsection{Existing Approaches}
+
+One approach to maximum common subgraph problems is via constraint programming
+\cite{DBLP:conf/mco/VismaraV08,DBLP:conf/cp/NdiayeS11}. The models are based upon constructing an
+injective mapping from the vertices of one graph (typically the smaller) to the other, in a similar
+manner to subgraph isomorphism algorithms
+\cite{DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}. However, to
+allow for a partial mapping, a special $\bot$ value is added to each domain. The objective is then
+to minimise the number of variables given the $\bot$ value---for best results, a special propagator
+for the injectivity condition is used, which simultaneously enforces that all variables taking
+non-$\bot$ are different, and restricts the number of $\bot$ values which may be used based upon the
+objective \cite{DBLP:conf/cp/PetitRB01}.  Unfortunately, the addition of $\bot$ also invalidates
+many of the invariants used for subgraph isomorphism---we may no longer reason using the degree of
+vertices, or the distances between them, for example, and so maximum common subgraph problems can be
+much more challenging in practice.
+
+Another widely studied approach is to reduce the problem to finding a maximum clique (or sometimes,
+equivalently, an independent set or a vertex cover) in an association graph (which we describe
+below). Conventional wisdom is that this approach is less effective in practice, but previous
+experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
+algorithms. Maximum clique algorithms are an active research area
+\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16},
+and so the first half of this paper re-evaluates the association graph approach using a modern
+algorithm.
+
+(Other approaches have been tried, including mixed integer programming
+\cite{DBLP:journals/anor/PivaS12}; SAT encodings seem to struggle even for subgraph isomorphism??
+cite IJCAI if it's not rejected?.)
+
+An interesting variant of the maximum common subgraph problem requires the selected subgraph to be
+connected
+\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
+Adding the connectedness requirement makes certain special cases solvable in polynomial time,
+including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
+\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. The second half of
+this paper looks at this variant on arbitrary graphs. In principle, for a constraint programming
+approach, we may simply add a ``forms a connected graph'' global constraint to the model
+\cite{Brown:2005,DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}. Alternatively, we could use a
+special branching rule to maintain connectedness during search ?? cite. We see that using both
+approaches together gives best results ?? does it?.  We also explain how to adapt this branching
+rule to run inside a modern clique-like algorithm, to solve the problem via an association graph.
+
+?? Summary, association graph is better when edges have labels.
+
 \subsection{Datasets}
@@
     \input{gen-graph-unconnected-33}
-    \caption{Clique versus CP, 33\% labelled. On the top, the cumulative
+    \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
     number of instances solved by each approach, in under a certain time. On the bottom, the best
-    clique approach compared to the best CP approach: the colour at a point indicates the number of
+    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
     instances with these runtimes.} \label{figure:unconnected-33}
@@
     \input{gen-graph-unconnected-plain}
-    \caption{Clique versus CP, undirected, unlabelled. On the top, the cumulative
+    \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
     number of instances solved by each approach, in under a certain time. On the bottom, the best
-    clique approach compared to the best CP approach: the colour at a point indicates the number of
+    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
     instances with these runtimes.} \label{figure:unconnected-plain}
 \end{figure}
+
+\subsection{Edge Labels}
 
@@
 
-\section{Maximum Common Connected Subgraph}
+\section{Find Maximum Common Connected Subgraphs}
 
@@
 variables which correspond to vertices which are adjacent to at least one other variable which has
-been instantiated to a non-null value. If no such variables remain, the subgraph we are building
-cannot grow any further, and all remaining variables must be instantiated to null.
+been instantiated to a value other than $\bot$. If no such variables remain, the subgraph we are building
+cannot grow any further, and all remaining variables must be instantiated to $\bot$.
 
-?? We only need to work off whichever input gives us the variables. But the CP approach seems to
+?? We only need to work off whichever input gives us the variables. But the constraint programming approach seems to
 look at both?
@@
 The $\mathit{branchable}$ set contains the set of association graph vertices which correspond to
-vertices adjacent to an already-accepted vertex in the first input graph---in CP terms, it is the
+vertices adjacent to an already-accepted vertex in the first input graph---in constraint programming terms, it is the
 set of assignments which could be made next which preserve connectedness. (Using only one of the two
@@
     the clique approach dominates except for three instances, and there is only one instance which
-    the CP model can solve but the clique model cannot (?? is this an EHP and does parallel get rid
+    the constraint programming model can solve but the clique model cannot (?? is this an EHP and does parallel get rid
     of it?). The clique model is unable to solve only ??  instances within one hour, ?? all of which
@@
     \input{gen-graph-connected-undir33}
-    \caption{Clique versus CP, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
+    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
         the cumulative number of instances solved by each approach, in under a certain time. On the
-        bottom, the best clique approach compared to the best CP approach: the colour at a point
+        bottom, the best clique approach compared to the best constraint programming approach: the colour at a point
         indicates the number of instances with these runtimes.} \label{figure:connected-undir33}
@@
     \input{gen-graph-connected-plain}
-    \caption{Clique versus CP, connected, undirected, unlabelled, up to 35 vertices. On the top, the
+    \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
     cumulative number of instances solved by each approach, in under a certain time. On the bottom,
-    the best clique approach compared to the best CP approach: the colour at a point indicates the
+    the best clique approach compared to the best constraint programming approach: the colour at a point indicates the
     number of instances with these runtimes.}

### 2016-03-28 paper/heatmapify.rb

@@ -7,10 +7,10 @@ granularity = 100
 IO.readlines(ARGV[0]).each do | line |
     words = line.split(' ')
 
-    x = words[1].sub('1e10', '3600').to_f * 1000
+    x = words[ARGV[1].to_i].sub('1e10', '3600').to_f * 1000
     bx = if x < 1 then 0 else (granularity * (Math.log(x + 0.1) / Math.log(3600000))).round end
 
-    y = words[2].sub('1e10', '3600000').to_f
+    y = words[ARGV[2].to_i].sub('1e10', '3600000').to_f
     by = if y < 1 then 0 else (granularity * (Math.log(y + 0.1) / Math.log(3600000))).round end
 
     abort "bx is " + bx.to_s + " by is " + by.to_s if bx < 0 || bx > granularity || by < 0 || by > granularity

### 2016-03-29 paper/paper.tex
More data

@@
 
+?? More? Can we scale to some of the SIP graphs?
+
 \section{Re-Evaluating the Clique Model}
@@
 
-We instead use a maximum clique algorithm. There has been a lot of recent
-research on this
-.
+We instead use a maximum clique algorithm.
 
@@
     \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
-    number of instances solved by each approach, in under a certain time. On the bottom, the best
-    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
-    instances with these runtimes.} \label{figure:unconnected-33}
+    number of instances solved by each approach, in under a certain time. On the bottom, an
+    instance-by-instance comparison of the two approaches: the colour at a point indicates the
+    number of instances with these runtimes.} \label{figure:unconnected-33}
 \end{figure}
@@
     \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
-    number of instances solved by each approach, in under a certain time. On the bottom, the best
-    clique approach compared to the best constraint programming approach: the colour at a point indicates the number of
-    instances with these runtimes.} \label{figure:unconnected-plain}
+    number of instances solved by each approach, in under a certain time. On the bottom, an
+        instance-by-instance comparison of the two approaches: the colour at a point indicates the
+    number of instances with these runtimes.} \label{figure:unconnected-plain}
 \end{figure}
@@
 
+\paragraph{Does connected make instances easier or harder?} We could plot connected vs not connected
+difficulties, and result sizes?
+
 \begin{figure}[p]
@@
         the cumulative number of instances solved by each approach, in under a certain time. On the
-        bottom, the best clique approach compared to the best constraint programming approach: the colour at a point
-        indicates the number of instances with these runtimes.} \label{figure:connected-undir33}
+        bottom, the association graph approach compared to the constraint programming approach with
+        both branching and filtering.} \label{figure:connected-undir33}
 \end{figure}
@@
     \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
-    cumulative number of instances solved by each approach, in under a certain time. On the bottom,
-    the best clique approach compared to the best constraint programming approach: the colour at a point indicates the
-    number of instances with these runtimes.}
+        cumulative number of instances solved by each approach, in under a certain time. On the
+        bottom, the association graph approach compared to the constraint programming approach
+    with both branching and filtering.}
 \label{figure:connected-plain}

### 2016-03-30 paper/paper.tex
More progress

@@
 
-% \usepackage{showframe}
+\usepackage{showframe}
 
-\usepackage{microtype}
+\usepackage{microtype}                 % typographic perfection
 \usepackage{complexity}                % \P, \NP etc
@@
 \usepackage{amsmath}                   % \operatorname
+\usepackage{amsfonts}                  % \mathbb
 \usepackage{hyperref}                  % clicky links
@@
 \usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
-\usepackage{placeins}                  % \FloatBarrier
-\usepackage{cite}
-\usepackage[bottom]{footmisc}
+\usepackage{cite}                      % automatically sort mass cites
+\usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
 
@@
 \end{tikzpicture}
-\caption{A maximum common induced subgraph of the first two graphs has eight vertices. There are
-four symmetric solutions, all involving the shaded vertices. However, if we require the common
-subgraph to be connected, only seven vertices may be selected---one way to do this is shown in the
-third and fourth graphs.}\label{figure:mcsexample}
+\caption{A maximum common induced subgraph of the first two graphs has eight vertices, shaded.
+However, if we require the common subgraph to be connected, only seven vertices may be
+selected---one way to do this is shown in the third and fourth graphs.}\label{figure:mcsexample}
 \end{figure}
@@
 
-A \emph{graph} $G = (V, E)$ consists of a set of vertices $V$ and a set of edges $E \subseteq V
-\times V$. In this paper our graphs may be directed, may have loops, and there is a label associated
-with each vertex and with each edge. For convenience, we treat undirected graphs as being directed
-graphs with symmetric adjacencies, and for unlabelled graphs we treat each vertex as having the same
-label, and each edge as having the same label. We write $\operatorname{V}(G)$ for $V$, and
-$\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood} of a vertex $v$ (that is, the set
-of vertices $w$ such that either $(v, w)$ or $(w, v)$ is an edge).
+We will be working with graphs which may be directed, which may have labels associated with
+vertices, edges, or both, and which may contain loops. To simplify notation, we will work with a
+single definition throughout: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of vertices
+$V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling function
+$e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex (or
+edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also use a
+distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices.  We write
+$\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
+of a vertex $v$ (that is, the set of vertices $w$ such that either $e(v, w) \ne \bot$ or $e(w, v)
+\ne \bot$).  A \emph{path} between two vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1,
+v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.
+A graph is \emph{connected} if a path exists between each distinct pair of vertices.
 
-Given two graphs $G_1$ and $G_2$, we say two pairs of vertices $(v_1, w_1) \in \operatorname{V}(G_1)
-\times \operatorname{V}(G_1)$ and $(v_2, w_2) \in \operatorname{V}(G_2) \times
-\operatorname{V}(G_2)$ are \emph{compatible} if both $v_1$ and $w_1$ and $v_2$ and $w_2$ are either
-non-adjacent or adjacent with the same label, and if the same holds for $(w_1, v_1)$ and $(w_2,
-v_2)$.  We say two vertices $v \in \operatorname{V}(G_1)$ and $w \in \operatorname{V}(G_2)$ are
-\emph{compatible} if they share the same label, and $(v, v)$ is compatible with $(w, w)$.
+Given two graphs $G_1 = (V_1, \ell_1, e_1)$ and $G_2 = (V_2, \ell_2, e_2)$, we say two pairs of
+vertices $(v_1, w_1) \in \operatorname{V}(G_1) \times \operatorname{V}(G_1)$ and $(v_2, w_2) \in
+\operatorname{V}(G_2) \times \operatorname{V}(G_2)$ are \emph{compatible}, written $(v_1, w_1)
+\simeq (v_2, w_2)$, if both $e_1(v_1, w_1) = e_2(v_2, w_2)$ and $e_1(w_1, v_1) = e_2(w_2, v_2)$. We
+say two vertices $v \in \operatorname{V}(G_1)$ and $w \in \operatorname{V}(G_2)$ are
+\emph{compatible}, written $v \simeq w$, if $\ell_1(v) = \ell_2(w)$ and $(v, v) \simeq (w, w)$.
 
-?? Get edge vs vertex in early.
+An \emph{induced subgraph isomorphism} from a graph $G$ to a graph $H$ is an injective function $i :
+\operatorname{V}(G) \rightarrow \operatorname{V}(H)$ such that for every vertex $v \in
+\operatorname{V}(G)$, $v \simeq i(v)$, and for every pair of vertices $(v, w) \in
+\operatorname{V}(G) \times \operatorname{V}(G)$, $(v, w) \simeq (i(v), i(w))$. A \emph{common
+induced subgraph isomorphism} between two graphs $G_1$ and $G_2$ is a graph $G$, together with a
+pair of induced subgraph isomorphisms $i_1 : G \rightarrow G_1$ and $i_2 : G \rightarrow G_2$. A
+\emph{common induced subgraph} of $G_1$ and $G_2$ is a graph $G$ which has a common subgraph
+isomorphism to $G_1$ and $G_2$. A \emph{maximum common (connected) induced subgraph} is a common
+(connected) induced subgraph with the largest possible number of vertices.  (The distinction between
+a common subgraph and a common subgraph isomorphism is relevant when counting distinct solutions,
+which we do not consider in this paper; in \cref{figure:mcsexample} on the left, there is only one
+maximum common subgraph, but four different maximum common subgraph isomorphisms are possible.)
+
+There is also a non-induced version of these problems, which is commonly known as the \emph{maximum
+common partial subgraph} problem: here, if $e(v, w) = \bot$, then $e_1(i_1(v), i_1(w))$ and
+$e_2(i_2(v), i_2(w))$ may take any value, and we must maximise the number of non-$\bot$ vertex pairs
+(i.e.\ edges) in $G$ instead (it is not entirely clear what the objective should be in directed
+graphs, or when loops are present). We restrict ourselves to the induced version in this paper (??
+we could do a journal version, because the clique side is rather involved\ldots).
 
@@
 \cite{DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}. However, to
-allow for a partial mapping, a special $\bot$ value is added to each domain. The objective is then
-to minimise the number of variables given the $\bot$ value---for best results, a special propagator
-for the injectivity condition is used, which simultaneously enforces that all variables taking
-non-$\bot$ are different, and restricts the number of $\bot$ values which may be used based upon the
-objective \cite{DBLP:conf/cp/PetitRB01}.  Unfortunately, the addition of $\bot$ also invalidates
-many of the invariants used for subgraph isomorphism---we may no longer reason using the degree of
-vertices, or the distances between them, for example, and so maximum common subgraph problems can be
-much more challenging in practice.
+allow for a partial mapping, a special $\bot$ value is added to each domain (and so we are
+constructing a maximum common subgraph isomorphism, where the common subgraph is implicitly the
+subgraph of the first graph given by taking the vertices which are not assigned to $\bot$, and the
+first subgraph isomorphism is the inclusion map). The objective is then to minimise the number of
+variables given the $\bot$ value---for best results, a special propagator for the injectivity
+condition is used, which simultaneously enforces that all variables taking non-$\bot$ are different,
+and restricts the number of $\bot$ values which may be used based upon the objective
+\cite{DBLP:conf/cp/PetitRB01}.  Unfortunately, the addition of $\bot$ also invalidates many of the
+invariants used for subgraph isomorphism---we may no longer reason using the degree of vertices, for
+example, and so maximum common subgraph problems can be much more challenging in practice.
 
@@
 
+?? Discuss the partial version briefly, cite the reduction.
+
 \subsection{Experimental Evaluation}
@@
     \centering
-    \input{gen-graph-unconnected-33}
+    % \input{gen-graph-unconnected-33}
     \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
@@
     \centering
-    \input{gen-graph-unconnected-plain}
+    % \input{gen-graph-unconnected-plain}
     \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
@@
 
-The key idea is that whenever we branch (except for the first choice we make), we select only from
-variables which correspond to vertices which are adjacent to at least one other variable which has
-been instantiated to a value other than $\bot$. If no such variables remain, the subgraph we are building
-cannot grow any further, and all remaining variables must be instantiated to $\bot$.
+\begin{figure}[tb]
+    \newcounter{stepcounter}
+    \centering
+    \begin{tikzpicture}[scale=0.33]%{{{
+        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+        \definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
+        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+        \begin{scope}
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
 
-?? We only need to work off whichever input gives us the variables. But the constraint programming approach seems to
-look at both?
+            \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [left = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [right = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [left = 0 of Md, font=\small] { \vphantom{0}d };
+            \node [right = 0 of Me, font=\small] { \vphantom{0}e };
+
+            \draw (Ma) -- (Mb);
+            \draw (Ma) -- (Mc);
+            \draw (Mb) -- (Mc);
+            \draw (Mb) -- (Md);
+            \draw (Mc) -- (Me);
+
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+            \draw [color=uofgsandstone!40] (M1) -- (M2);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [color=uofgsandstone!40] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+
+            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
+                \stepcounter{stepcounter}\roman{stepcounter}) Initial problem };
+        \end{scope}
+
+        \begin{scope}[xshift=13cm]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
+
+            \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [left = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [right = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [left = 0 of Md, font=\small] { \vphantom{0}d };
+            \node [right = 0 of Me, font=\small] { \vphantom{0}e };
+
+            \draw (Ma) -- (Mb);
+            \draw (Ma) -- (Mc);
+            \draw (Mb) -- (Mc);
+            \draw [dotted] (Mb) -- (Md);
+            \draw [dotted] (Mc) -- (Me);
+
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+            \draw [color=uofgsandstone!40] (M1) -- (M2);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [color=uofgsandstone!40] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+
+            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
+                \stepcounter{stepcounter}\roman{stepcounter}) Try $a \mapsto 1$ };
+        \end{scope}
+
+        \begin{scope}[xshift=26cm]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
+
+            \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [left = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [right = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [left = 0 of Md, font=\small] { \vphantom{0}d };
+            \node [right = 0 of Me, font=\small] { \vphantom{0}e };
+
+            \draw [very thick] (Ma) -- (Mb);
+            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!40] (Mb) -- (Mc);
+            \draw (Mb) -- (Md);
+            \draw [color=uofgsandstone!40] (Mc) -- (Me);
+
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [color=uofgsandstone!40] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+
+            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
+                \stepcounter{stepcounter}\roman{stepcounter}) Try $b \mapsto 2$ };
+        \end{scope}
+
+        \begin{scope}[yshift=-9cm]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
+
+            \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [left = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [right = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [left = 0 of Md, font=\small] { \vphantom{0}d };
+            \node [right = 0 of Me, font=\small] { \vphantom{0}e };
+
+            \draw [very thick] (Ma) -- (Mb);
+            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!40] (Mb) -- (Mc);
+            \draw [very thick] (Mb) -- (Md);
+            \draw [color=uofgsandstone!40] (Mc) -- (Me);
+
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [very thick] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+
+            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
+                \stepcounter{stepcounter}\roman{stepcounter}) Try $d \mapsto 4$ };
+        \end{scope}
+
+        \begin{scope}[xshift=13cm, yshift=-9cm]
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
+
+            \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [left = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [right = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [left = 0 of Md, font=\small] { \vphantom{0}d };
+            \node [right = 0 of Me, font=\small] { \vphantom{0}e };
+
+            \draw [very thick] (Ma) -- (Mb);
+            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!40] (Mb) -- (Mc);
+            \draw [very thick] (Mb) -- (Md);
+            \draw [color=uofgsandstone!40] (Mc) -- (Me);
+
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [very thick] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+
+            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
+                \stepcounter{stepcounter}\roman{stepcounter}) Forced $e \mapsto \bot$ };
+        \end{scope}
+    \end{tikzpicture}
+
+    \caption{Suppose we are looking for a connected common subgraph, using the graph on the left
+        for variables and the graph on the right (which has an isolated vertex) for values. We
+        initially consider $a \mapsto 1$. Our restricted branching rule requires us to select either variable
+        $b$ or variable $c$ subsequently, not $d$ or $e$. We try $b \mapsto 2$, which adds $d$
+        to the branchable variables, and forces $c \mapsto \bot$. We may now only branch on $d$, and
+        we try $d \mapsto 4$. Now the only remaining variable is unbranchable, and so $e = \bot$ is forced, even
+        though $5$ remains in its domain.}\label{figure:restricted}
+\end{figure}
+
+\cref{figure:restricted} The key idea is that whenever we branch (except for the first choice we
+make), we select only from variables which correspond to vertices which are adjacent to at least one
+other variable which has been instantiated to a value other than $\bot$. If no such variables
+remain, the subgraph we are building cannot grow any further, and all remaining variables must be
+instantiated to $\bot$.
+
+?? We only need to work off whichever input gives us the variables. But the constraint programming
+approach seems to look at both?
 
@@
 }
-\vspace{1ex}
+\vspace{0.9ex}
 \nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
@@
 }
-\vspace{1ex}
+\vspace{0.9ex}
 \nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;
@@
 }
-\vspace{1ex}
+\vspace{0.9ex}
 \nl $\FuncSty{connected}$ :: (Graph $G$, Vertex $v$) $\rightarrow$ Set \;
@@
 }
-\vspace{1ex}
+\vspace{0.9ex}
 \nl $\FuncSty{associationGraph}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Graph \;
 \nl \Begin{
-    \nl $V \gets \{ (v_1, v_2) \in G_1 \times G_2 : \FuncSty{compatible}(v_1, v_2) \}$ \;
-    \nl $E \gets \{ ((v_1, v_2), (w_1, w_2)) \in V \times V : \FuncSty{compatible}((v_1, w_1), (v_2,
-    w_2)) \}$ \;
-    \nl $\KwSty{return} ~ (V, E)$ \;
+    \nl $V \gets \{ (v_1, v_2) \in G_1 \times G_2 : v_1 \simeq v_2 \}$ \;
+    \nl $E \gets \{ ((v_1, v_2), (w_1, w_2)) \in V \times V : (v_1, w_1) \simeq (v_2, w_2) \}$ \;
+    \nl $\KwSty{return} ~ (V, v \mapsto 1, (v, w) \mapsto 1~\KwSty{if}~(v, w) \in E~\KwSty{otherwise}~\bot )$ \;
 }
-\caption{An algorithm for MCCIS via an association graph.}
+\caption{An algorithm for a maximum common connected induced subgraph isomorphism via an association graph.}
 \label{algorithm:mccis}
@@
 
-In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds an MCCIS via an
+In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
+connected induced subgraph isomorphism via an
 association graph. If the additional
@@
     \centering
-    \input{gen-graph-connected-undir33}
+    % \input{gen-graph-connected-undir33}
     \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
@@
     \centering
-    \input{gen-graph-connected-plain}
+    % \input{gen-graph-connected-plain}
     \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
@@
 
-\FloatBarrier
-
 \bibliographystyle{splncs}

### 2016-03-30 paper/paper.tex
More

@@
 
+\begin{figure}[tb]
+    \centering
+    \begin{tikzpicture}[scale=0.33]%{{{
+        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+        \begin{scope}
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 10) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 8) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 8) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Md) at (4, 8) {\phantom{0}};
+
+            \node [right = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [below = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [below = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [below = 0 of Md, font=\small] { \vphantom{0}d };
+
+            \draw [very thick] (Mb) -- (Mc);
+            \draw [very thick] (Mc) -- (Md);
+            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!40] (Ma) to [out=150, in=80, looseness=8] (Ma);
+            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
+        \end{scope}
+
+        \begin{scope}
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
+            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+
+            \draw [color=uofgsandstone!40] (M3) to [out=280, in=210, looseness=8] (M3);
+            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
+        \end{scope}
+
+        \begin{scope}[xshift=15cm]
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2, 9.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4, 9.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (6, 9.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (8, 9.5) {\phantom{0}};
+            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
+            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
+            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
+            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Ma1.north west) -- (Ma4.north east)
+            node [midway, above=0.7cm] { $a \mapsto$ };
+
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (0.5, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (0.5, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (0.5, 6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (0.5, 8) {\phantom{0}};
+            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
+            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
+            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mb1.south west) -- (Mb4.north west)
+            node [midway, left=0.7cm] { $b \mapsto$ };
+
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2, 0.5) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4, 0.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (6, 0.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (8, 0.5) {\phantom{0}};
+            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
+            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
+            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
+            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mc4.south east) -- (Mc1.south west)
+            node [midway, below=0.7cm] { $c \mapsto$ };
+
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9.5, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9.5, 4) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9.5, 6) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9.5, 8) {\phantom{0}};
+            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
+            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
+            node [midway, right=0.7cm] { $d \mapsto$ };
+
+            \begin{scope}[on background layer]
+                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
+                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
+                \draw [draw=uofgsandstone!40] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
+                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
+                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
+                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
+        \end{scope}
+        \end{scope}
+
+    \end{tikzpicture}
+
+    \caption{A maximum common induced subgraph between the two graphs on the left has three
+        vertices---one solution is highlighted. On the right, the association graph encoding: the
+    highlighted clique of size three shows the same solution.}\label{figure:association}
+\end{figure}
+
 Explain association graph. ?? cite history, connections to microstructure
@@
     \centering
-    % \input{gen-graph-unconnected-33}
+    \input{gen-graph-unconnected-33}
     \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
@@
     \centering
-    % \input{gen-graph-unconnected-plain}
+    \input{gen-graph-unconnected-plain}
     \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
@@
             \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
-                \stepcounter{stepcounter}\roman{stepcounter}) Try $a \mapsto 1$ };
+                \stepcounter{stepcounter}\roman{stepcounter}) Trying $a \mapsto 1$ };
         \end{scope}
@@
             \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
-                \stepcounter{stepcounter}\roman{stepcounter}) Try $b \mapsto 2$ };
+                \stepcounter{stepcounter}\roman{stepcounter}) Trying $b \mapsto 2$ };
         \end{scope}
@@
             \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
-                \stepcounter{stepcounter}\roman{stepcounter}) Try $d \mapsto 4$ };
+                \stepcounter{stepcounter}\roman{stepcounter}) Trying $d \mapsto 4$ };
         \end{scope}
@@
         we try $d \mapsto 4$. Now the only remaining variable is unbranchable, and so $e = \bot$ is forced, even
-        though $5$ remains in its domain.}\label{figure:restricted}
+        though $5$ remains in its domain and does not violate any constraints.}\label{figure:restricted}
 \end{figure}
@@
     \centering
-    % \input{gen-graph-connected-undir33}
+    \input{gen-graph-connected-undir33}
     \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
@@
     \centering
-    % \input{gen-graph-connected-plain}
+    \input{gen-graph-connected-plain}
     \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the

### 2016-03-30 paper/paper.tex
More

@@
 of a vertex $v$ (that is, the set of vertices $w$ such that either $e(v, w) \ne \bot$ or $e(w, v)
-\ne \bot$).  A \emph{path} between two vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1,
-v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.
-A graph is \emph{connected} if a path exists between each distinct pair of vertices.
+\ne \bot$); a vertex is \emph{isolated} if its neighbourhood is empty. A \emph{path} between two
+vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1, v_2, \ldots, v_n = w$ such that for
+each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.  A graph is \emph{connected} if a
+path exists between each distinct pair of vertices.
 
@@
 
+Explain association graph \cref{figure:association}, cite history, connections to microstructure
+\cite{DBLP:conf/aaai/Jegou93a}.
+
+Discuss how edge labels, vertex labels, directed edges, etc, are handled. Note that we can generally
+only handle very local side constraints, or injectivity (which is decomposable).
+
 \begin{figure}[tb]
@@
         \begin{scope}[xshift=15cm]
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2, 9.5) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4, 9.5) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (6, 9.5) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (8, 9.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
             \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
@@
 
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (0.5, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (0.5, 4) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (0.5, 6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (0.5, 8) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
             \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2, 0.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4, 0.5) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (6, 0.5) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (8, 0.5) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
             \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9.5, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9.5, 4) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9.5, 6) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9.5, 8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
             \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
@@
         vertices---one solution is highlighted. On the right, the association graph encoding: the
-    highlighted clique of size three shows the same solution.}\label{figure:association}
+        highlighted clique of size three shows the same solution. In practice the isolated vertices
+        (corresponding to assignments between incompatible vertices, which are unary constraints) would be
+        omitted.}\label{figure:association}
 \end{figure}
-
-Explain association graph. ?? cite history, connections to microstructure
-
-Discuss how edge labels, vertex labels, directed edges, etc, are handled. Note that we can generally
-only handle very local side constraints, or injectivity (which is decomposable).
 
@@
 \cref{figure:unconnected-plain}
+
+?? Break this down more by family, size, etc.
 
@@
 
-\subsection{Edge Labels}
+\subsection{Filtering from Edge Labels}
 
@@
             \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
-                \stepcounter{stepcounter}\roman{stepcounter}) Forced $e \mapsto \bot$ };
+                \stepcounter{stepcounter}\roman{stepcounter}) $e \mapsto \bot$ is forced };
         \end{scope}
@@
 
-?? We only need to work off whichever input gives us the variables. But the constraint programming
-approach seems to look at both?
-
 ?? Patrick reckons this reminds him of Prim's algorithm for minimum spanning trees.
-
-?? We need a picture here.
 
@@
 
+\paragraph{By family} ?? Break this down more by family, size, etc.
+
 \paragraph{Does connected make instances easier or harder?} We could plot connected vs not connected

### 2016-03-31 code/clique.cc
Bring in the code

@@ -1,0 +1,362 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "clique.hh"
+#include "bit_graph.hh"
+#include "template_voodoo.hh"
+
+#include <algorithm>
+#include <limits>
+#include <iostream>
+#include <atomic>
+#include <mutex>
+
+namespace
+{
+    using Association = std::map<std::pair<unsigned, unsigned>, unsigned>;
+    using AssociatedEdges = std::vector<std::pair<unsigned, unsigned> >;
+
+    auto modular_product(const VFGraph & g1, const VFGraph & g2) -> std::pair<Association, AssociatedEdges>
+    {
+        unsigned next_vertex = 0;
+        Association association;
+        AssociatedEdges edges;
+
+        for (unsigned l = 0 ; l < std::min(g1.vertices_by_label.size(), g2.vertices_by_label.size()) ; ++l)
+            for (unsigned v1 : g1.vertices_by_label[l])
+                for (unsigned v2 : g2.vertices_by_label[l])
+                    for (unsigned m = 0 ; m < std::min(g1.vertices_by_label.size(), g2.vertices_by_label.size()) ; ++m)
+                        for (unsigned w1 : g1.vertices_by_label[m])
+                            for (unsigned w2 : g2.vertices_by_label[m])
+                                if (v1 != w1 && v2 != w2
+                                        && (g1.edges[v1][v1] == g2.edges[v2][v2])
+                                        && (g1.edges[w1][w1] == g2.edges[w2][w2])
+                                        && (g1.edges[v1][w1] == g2.edges[v2][w2])
+                                        && (g1.edges[w1][v1] == g2.edges[w2][v2])) {
+
+                                    if (! association.count({v1, v2}))
+                                        association.insert({{v1, v2}, next_vertex++});
+                                    if (! association.count({w1, w2}))
+                                        association.insert({{w1, w2}, next_vertex++});
+
+                                    edges.push_back({association.find({v1, v2})->second, association.find({w1, w2})->second});
+                                }
+
+        return { association, edges };
+    }
+
+    auto unproduct(const Association & association, unsigned v) -> std::pair<unsigned, unsigned>
+    {
+        for (auto & a : association)
+            if (a.second == v)
+                return a.first;
+
+        throw "oops";
+    }
+
+    struct Incumbent
+    {
+        std::atomic<unsigned> value{ 0 };
+
+        std::mutex mutex;
+        std::vector<unsigned> c;
[…]

### 2016-03-31 code/solve_max_common_subgraph.cc

@@ -1,0 +1,355 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "clique.hh"
+
+#include <boost/program_options.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <exception>
+#include <cstdlib>
+#include <chrono>
+#include <thread>
+#include <mutex>
+#include <condition_variable>
+#include <algorithm>
+
+namespace po = boost::program_options;
+
+using std::chrono::steady_clock;
+using std::chrono::duration_cast;
+using std::chrono::milliseconds;
+
+namespace
+{
+    class GraphFileError :
+        public std::exception
+    {
+        private:
+            std::string _what;
+
+        public:
+            GraphFileError(const std::string & filename, const std::string & message) throw ();
+
+            auto what() const throw () -> const char *;
+    };
+
+    GraphFileError::GraphFileError(const std::string & filename, const std::string & message) throw () :
+        _what("Error reading graph file '" + filename + "': " + message)
+    {
+    }
+
+    auto GraphFileError::what() const throw () -> const char *
+    {
+        return _what.c_str();
+    }
+
+    auto read_word(std::ifstream & infile) -> unsigned
+    {
+        unsigned char a, b;
+        a = static_cast<unsigned char>(infile.get());
+        b = static_cast<unsigned char>(infile.get());
+        return unsigned(a) | (unsigned(b) << 8);
+    }
+
+    auto read_vf(const std::string & filename, bool unlabelled, bool undirected) -> VFGraph
+    {
+        VFGraph result;
+
+        std::ifstream infile{ filename };
+        if (! infile)
+            throw GraphFileError{ filename, "unable to open file" };
+
+        result.size = read_word(infile);
+        if (! infile)
+            throw GraphFileError{ filename, "error reading size" };
+
+        // to be like the CP 2011 labelling scheme...
+        int m = result.size * 33 / 100;
+        int p = 1, k1 = 0, k2 = 0;
+        while (p < m && k1 < 16) {
+            p *= 2;
+            k1 = k2;
+            k2++;
+        }
+
+        if (unlabelled)
+            result.vertices_by_label.resize(1);
+        else
+            result.vertices_by_label.resize(0x10000 >> (16 - k1));
+
+        result.vertex_labels.resize(result.size);
+        result.edges.resize(result.size);
+        for (auto & e : result.edges)
+            e.resize(result.size);
+
[…]

### 2016-04-01 paper/paper.tex
More pictures

@@
 
-\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing, patterns}
+\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing,
+    patterns, matrix}
 
@@
 \Crefname{proposition}{Proposition}{Propositions}
+
+% pretty colours
+\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
+\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
 
@@
     \begin{tikzpicture}[scale=0.33]%{{{
-        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
-        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
         \begin{scope}[rotate=90]
@@
     \begin{tikzpicture}[scale=0.33]%{{{
-        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
-        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
         \begin{scope}
@@
     \begin{tikzpicture}[scale=0.33]%{{{
-        \definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-        \definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
-        \definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
-        \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
         \begin{scope}
@@
 
-            \draw (Ma) -- (Mb);
-            \draw (Ma) -- (Mc);
-            \draw (Mb) -- (Mc);
-            \draw (Mb) -- (Md);
-            \draw (Mc) -- (Me);
+            \draw [draw=uofgsandstone!40] (Ma) -- (Mb);
+            \draw [draw=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [draw=uofgsandstone!40] (Mb) -- (Mc);
+            \draw [draw=uofgsandstone!40] (Mb) -- (Md);
+            \draw [draw=uofgsandstone!40] (Mc) -- (Me);
 
@@
 
-            \draw (Ma) -- (Mb);
-            \draw (Ma) -- (Mc);
-            \draw (Mb) -- (Mc);
+            \draw [draw=uofgsandstone!40] (Ma) -- (Mb);
+            \draw [draw=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [draw=uofgsandstone!40] (Mb) -- (Mc);
             \draw [dotted] (Mb) -- (Md);
@@
             \draw [color=uofgsandstone!40] (Mb) -- (Mc);
-            \draw (Mb) -- (Md);
+            \draw [color=uofgsandstone!40] (Mb) -- (Md);
             \draw [color=uofgsandstone!40] (Mc) -- (Me);
@@
 
+\begin{figure}[p]
+    \newcounter{stepcounter2}
+    \centering
+    \begin{tikzpicture}[scale=0.33]%{{{
+        \matrix (m) [matrix of nodes, column sep=0.5cm] {
+            \begin{tikzpicture}[scale=0.33]
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (2, 4) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mc) at (0, 2) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (2, 2) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (0, 0) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mf) at (2, 0) {\phantom{0}};
+
+                    \node [left = 0 of Ma, font=\small] { \vphantom{0}a };
+                    \node [right = 0 of Mb, font=\small] { \vphantom{0}b };
+                    \node [left = 0 of Mc, font=\small] { \vphantom{0}c };
+                    \node [right = 0 of Md, font=\small] { \vphantom{0}d };
+                    \node [left = 0 of Me, font=\small] { \vphantom{0}e };
+                    \node [right = 0 of Mf, font=\small] { \vphantom{0}f };
+
+                    \draw (Ma) -- (Mb);
+                    \draw (Ma) -- (Mc);
+                    \draw (Ma) -- (Md);
+                    \draw (Mc) -- (Md);
+                    \draw (Mc) -- (Me);
+                    \draw (Md) -- (Mf);
+
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M1) at (6, 4) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (8, 4) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (6, 2) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (8, 2) {\phantom{0}};
+                    \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (6, 0) {\phantom{0}};
+
+                    \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+                    \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+                    \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+                    \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+                    \node [left = 0 of M5, font=\small] { \vphantom{0}5 };
+
+                    \draw [color=uofgsandstone!40] (M1) -- (M2);
+                    \draw [color=uofgsandstone!40] (M1) -- (M3);
+                    \draw [color=uofgsandstone!40] (M2) -- (M4);
+                    \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \end{tikzpicture}
+            &
+            \begin{tikzpicture}[scale=0.33]
+                    \node [anchor=west] (Ns) at (0, 3.5) { $\mathit{solution}$ };
+                    \node [anchor=west] (Nb) at (0, 2) { $\mathit{branchable}$ };
+                    \node [anchor=west] (Nr) at (0, 0.5) { $\mathit{remaining}$ };
+
+                    \node [anchor=west] (Vs) at (5.5, 3.5) { $\{ (a, 1) \}$ };
+                    \node [anchor=west] (Vb) at (5.5, 2) { $\{ b, c, d \} \times \{1 \ldots 5 \}$ };
+                    \node [anchor=west] (Vr) at (5.5, 0.5) { $(\{ b, c, d \} \times \{ 2, 3 \}) \cup (\{ e, f\} \times \{ 4, 5 \})$ };
+            \end{tikzpicture}
+            \\[0.1cm]
+            \stepcounter{stepcounter2}\roman{stepcounter2}) Initial problem &
+            \stepcounter{stepcounter2}\roman{stepcounter2}) Search variables after guessing $a \mapsto 1$
+            \\[0.4cm]
+            \begin{tikzpicture}[scale=0.33]
+                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
+                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (3, 0) {\phantom{0}};
+
+                    \node [above = 0 of Me4, font=\small] { \vphantom{0}(e, 4) };
+                    \node [above = 0 of Me5, font=\small] { \vphantom{0}(e, 5) };
+                    \node [below = 0 of Mf4, font=\small] { \vphantom{0}(f, 4) };
+                    \node [below = 0 of Mf5, font=\small] { \vphantom{0}(f, 5) };
+
+                    \draw (Me4) -- (Mf5);
+                    \draw (Me5) -- (Mf4);
+            \end{tikzpicture}
+            &
+            \begin{tikzpicture}[scale=0.33]
+                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
+                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (3, 0) {\phantom{0}};
+                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (6, 0) {\phantom{0}};
+                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 0) {\phantom{0}};
+
+                    \node [above = 0 of Mb2, font=\small] { \vphantom{0}(b, 2) };
+                    \node [above = 0 of Mb3, font=\small] { \vphantom{0}(b, 3) };
+                    \node [below = 0 of Mc2, font=\small] { \vphantom{0}(c, 2) };
+                    \node [below = 0 of Mc3, font=\small] { \vphantom{0}(c, 3) };
+                    \node [below = 0 of Md2, font=\small] { \vphantom{0}(d, 2) };
+                    \node [below = 0 of Md3, font=\small] { \vphantom{0}(d, 3) };
+
+                    \draw (Mb2) -- (Mc3);
+                    \draw (Mb2) -- (Md3);
+                    \draw (Mb3) -- (Mc2);
+                    \draw (Mb3) -- (Md2);
+            \end{tikzpicture}
+            \\[0.1cm]
+            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \setminus \mathit{branchable}$ &
+            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \cap \mathit{branchable}$
+            \\
+        };
+    \end{tikzpicture}\\[0.3cm]\begin{tikzpicture}[scale=0.33]
+        \matrix (m) [matrix of nodes] {
+            \begin{tikzpicture}[scale=0.33]
+                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (9, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (12, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (15, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (18, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (21, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (24, 0) {\phantom{0}};
+                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (27, 0) {\phantom{0}};
+
+                \node [above = 0 of Me4, font=\small, xshift=-0.5ex] { \vphantom{0}[[(e, 4), };
+                \node [above = 0 of Me5, font=\small] { \vphantom{0}(e, 5)], };
+                \node [above = 0 of Mf4, font=\small] { \vphantom{0}[(f, 4), };
+                \node [above = 0 of Mf5, font=\small] { \vphantom{0}(f, 5)], };
+                \node [above = 0 of Mb2, font=\small] { \vphantom{0}[(b, 2), };
+                \node [above = 0 of Mb3, font=\small] { \vphantom{0}(b, 3)], };
+                \node [above = 0 of Mc2, font=\small] { \vphantom{0}[(c, 2), };
+                \node [above = 0 of Mc3, font=\small] { \vphantom{0}(c, 3), };
+                \node [above = 0 of Md2, font=\small] { \vphantom{0}(d, 2), };
+                \node [above = 0 of Md3, font=\small] { \vphantom{0}(d, 3)]]};
+            \end{tikzpicture}
+            \\[0.1cm]
+            \stepcounter{stepcounter2}\roman{stepcounter2}) The resulting $\mathit{colourClasses}$ variable.
+            \\
+        };
+    \end{tikzpicture}
+
+    \caption{Solving a maximum common connected problem using an association graph. Suppose we
+        have already mapped vertex $a$ to vertex $1$, giving the assignments on the right. Now we
+        have two subgraphs to colour. We need two colours for $\mathit{remaining} \setminus
+        \mathit{branchable}$, and we place these two colour classes first in the $\mathit{colourClasses}$
+        variable. We can also colour $\mathit{remaining} \cap \mathit{branchable}$ using two
+        colours, since we cannot simultaneously map $c$ to $2$ and $d$ to $3$, or vice-versa. Thus
+        $\mathit{colourClasses}$ becomes a list of four colour classes, the first three containing
+        two vertices each, and the last containing four vertices. This tells us that if we hope to
+        extend the current common subgraph by another four vertices, we
+        must pick one assignment from each of the four colour classes (which is not actually possible, so we
+    see the bound here gives an overestimate). The algorithm thus guesses $d \mapsto 3$ as its next
+assignment, and if that fails, $d \mapsto 2$, and so on; once $b \mapsto 3$ is reached, the bound
+decreases by one, and if $f \mapsto 5$ were reached we would stop due to a lack of remaining
+branchable vertices. }\label{figure:assocrestricted}
+\end{figure}
+
 It is not possible to determine connectedness from a raw association graph. However, we can take a

### 2016-04-02 paper/paper.tex
Breakdown data

@@
     \centering
+    \input{gen-graph-unconnected-33-breakdown}
+    \caption{Clique versus constraint programming, 33\% labelled, broken down by family.}
+        \label{figure:unconnected-33-breakdown}
+\end{figure}
+
+\begin{figure}[p]
+    \centering
     \input{gen-graph-unconnected-plain}
@@
     number of instances with these runtimes.} \label{figure:unconnected-plain}
+\end{figure}
+
+\begin{figure}[p]
+    \centering
+    \input{gen-graph-unconnected-plain-breakdown}
+    \caption{Clique versus constraint programming, undirected, unlabelled, broken down by family.}
+        \label{figure:unconnected-plain-breakdown}
 \end{figure}
@@
     \centering
+    \input{gen-graph-connected-undir33-breakdown}
+    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, broken down by family.}
+        \label{figure:connected-undir33-breakdown}
+\end{figure}
+
+\begin{figure}[p]
+    \centering
     \input{gen-graph-connected-plain}
@@
 
+\begin{figure}[p]
+    \centering
+    \input{gen-graph-connected-plain-breakdown}
+    \caption{Clique versus constraint programming, connected, undirected, unlabelled, broken down by family.}
+        \label{figure:connected-plain-breakdown}
+\end{figure}
+
 \subsection{Parallel Search}

### 2016-04-05 paper/paper.tex
More data
More things

--- 2016-04-01 paper/paper.tex
@@
 \usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
+\usepackage{placeins}
 
@@
 
+\renewcommand{\floatpagefraction}{0.8}
+\renewcommand{\topfraction}{0.9}
+\renewcommand{\bottomfraction}{0.8}
+
 \title{Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems}
@@
     This problem can be solved either by constraint-based search, or by reduction to the maximum
-    clique problem. We evaluate these two approaches using modern algorithms. We also investigate a
+    clique problem. We evaluate these two approaches using modern algorithms, and see that the best
+    choice depends mainly upon whether the graphs have labelled edges. We also investigate a
     restricted branching approach for the connected version of the problem, show how to implement
@@
 edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also use a
-distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices.  We write
+distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices; vertices $v$ and
+$w$ are said to be \emph{adjacent} if $e(v, w) \ne \bot$ or $e(w, v) \ne \bot$. We write
 $\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
-of a vertex $v$ (that is, the set of vertices $w$ such that either $e(v, w) \ne \bot$ or $e(w, v)
-\ne \bot$); a vertex is \emph{isolated} if its neighbourhood is empty. A \emph{path} between two
-vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1, v_2, \ldots, v_n = w$ such that for
-each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.  A graph is \emph{connected} if a
-path exists between each distinct pair of vertices.
+of a vertex $v$ (that is, the set of vertices adjacent to $v$); a vertex is \emph{isolated} if its
+neighbourhood is empty. A \emph{path} between two vertices $v$ and $w$ is a sequence of $n$ vertices
+$v = v_1, v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $v_m$ is adjacent
+to $v_{m + 1}$. A graph is \emph{connected} if a path exists between each distinct pair of vertices.
 
@@
 Another widely studied approach is to reduce the problem to finding a maximum clique (or sometimes,
-equivalently, an independent set or a vertex cover) in an association graph (which we describe
+equivalently, an independent set or a vertex cover ?? cite) in an association graph (which we describe
 below). Conventional wisdom is that this approach is less effective in practice, but previous
@@
 
-(Other approaches have been tried, including mixed integer programming
-\cite{DBLP:journals/anor/PivaS12}; SAT encodings seem to struggle even for subgraph isomorphism??
-cite IJCAI if it's not rejected?.)
+(Other approaches have been tried, including dedicated algorithms ?? cite, mixed integer programming
+\cite{DBLP:journals/anor/PivaS12}, and heuristics ?? cite; SAT encodings seem to struggle even for
+subgraph isomorphism??  cite IJCAI.)
 
@@
 
+% \begin{figure}[p]
+%     \centering
+%     \input{gen-graph-unconnected-33-breakdown}
+%     \caption{Clique versus constraint programming, 33\% labelled, broken down by family.}
+%         \label{figure:unconnected-33-breakdown}
+% \end{figure}
+
 \begin{figure}[p]
@@
 \end{figure}
+
+% \begin{figure}[p]
+%     \centering
+%     \input{gen-graph-unconnected-plain-breakdown}
+%     \caption{Clique versus constraint programming, undirected, unlabelled, broken down by family.}
+%         \label{figure:unconnected-plain-breakdown}
+% \end{figure}
 
@@
 
-\begin{figure}[p]
+\begin{figure}[tb]
     \newcounter{stepcounter2}
@@
 colour classes between the two stages, although it may use more colours than a single colouring
-would.
+would\footnote{What if we did not guarantee that vertices in $\mathit{remaining} \cap
+    \mathit{connected}$ came last, and just used a conventional colouring with the branching rule?
+    Suppose we had four vertices in $\mathit{remaining}$, and produced a colouring $[[v_1, v_2],
+    [v_3], [v_4]]$, and suppose that extending $\mathit{solution}$ with $\{ v_1, v_3, v_4 \}$ gives
+an optimal solution. If $v_4$ was not $\mathit{connected}$ yet, we would not branch on that subtree,
+and the bound could eliminate branching on $v_3$ and $v_1$, so we would miss the solution. Thus we
+cannot simply add the branching rule without also adapting the combined bound / ordering heuristic.}.
 
@@
 selection of the next vertex to colour (\lineref{selectvtocolour}) may be performed efficiently in
-hardware if the association graph is permuted to be in degree order at the top of search. (Other
+hardware if the association graph is permuted to be in degree order at the top of search. Other
 initial vertex orderings have been considered on general clique problems
 \cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}; it is possible that special
-properties of the association graph could be exploited in this step.)
+properties of the association graph could be exploited in this step.
 
@@
         both branching and filtering.} \label{figure:connected-undir33}
+\end{figure}
+
+% \begin{figure}[p]
+%     \centering
+%     \input{gen-graph-connected-undir33-breakdown}
+%     \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, broken down by family.}
+%         \label{figure:connected-undir33-breakdown}
+% \end{figure}
+
+\begin{figure}[tb]
+    \centering
+    \input{gen-graph-connected-cp-undir33.tex}
+    \caption{A pairwise comparison of different CP techniques for the connected, undirected, 33\%
+        labelled variant with graphs of up to 80 vertices. The colour at a point indicates the
+        number of instances with these runtimes, with darker colours representing more instances.}
+        \label{figure:connected-cp-undir33}
 \end{figure}
@@
 
+% \begin{figure}[p]
+%     \centering
+%     \input{gen-graph-connected-plain-breakdown}
+%     \caption{Clique versus constraint programming, connected, undirected, unlabelled, broken down by family.}
+%         \label{figure:connected-plain-breakdown}
+% \end{figure}
+
+\begin{figure}[tb]
+    \centering
+    \input{gen-graph-connected-cp-plain.tex}
+    \caption{Different CP techniques, connected, undirected, unlabelled, up to 35 vertices.}
+        \label{figure:connected-cp-plain}
+\end{figure}
+
 \subsection{Parallel Search}
@@
 
+\FloatBarrier
 \bibliographystyle{splncs}

### 2016-04-05 paper/heatmapify.rb

@@ -4,13 +4,16 @@
 buckets = Hash.new(0)
 granularity = 100
 
+xmul = ARGV[3].to_i
+ymul = ARGV[4].to_i
+
 IO.readlines(ARGV[0]).each do | line |
     words = line.split(' ')
 
-    x = words[ARGV[1].to_i].sub('1e10', '3600').to_f * 1000
+    x = words[ARGV[1].to_i].sub('1e10', (3600 / xmul).to_s).to_f * xmul
     bx = if x < 1 then 0 else (granularity * (Math.log(x + 0.1) / Math.log(3600000))).round end
 
-    y = words[ARGV[2].to_i].sub('1e10', '3600000').to_f
+    y = words[ARGV[2].to_i].sub('1e10', (3600000 / ymul).to_s).to_f * ymul
     by = if y < 1 then 0 else (granularity * (Math.log(y + 0.1) / Math.log(3600000))).round end
 
     abort "bx is " + bx.to_s + " by is " + by.to_s if bx < 0 || bx > granularity || by < 0 || by > granularity

### 2016-04-06 paper/paper.tex
More text and cites

@@
 Maximum common subgraph problems arise in biology and chemistry
-\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, computer vision ?? what should we cite?, ??
-anything else?, both directly and as a way of measuring the similarity or difference between two
-graphs \cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate
-this in \cref{figure:mcsexample}, and define the problem formally below.
-
-\subsection{Definitions and Notation}
-
-We will be working with graphs which may be directed, which may have labels associated with
-vertices, edges, or both, and which may contain loops. To simplify notation, we will work with a
-single definition throughout: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of vertices
-$V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling function
-$e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex (or
-edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also use a
-distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices; vertices $v$ and
-$w$ are said to be \emph{adjacent} if $e(v, w) \ne \bot$ or $e(w, v) \ne \bot$. We write
+\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
+\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
+\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
+designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
+and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
+measuring the similarity or difference between two graphs
+\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
+variants of the problem in \cref{figure:mcsexample}.
+
+Throughout this paper we will be working with graphs which may be directed, which may have labels
+associated with vertices, edges, or both, and which may contain loops. To simplify notation, we will
+work with a very broad definition: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of
+vertices $V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling
+function $e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex
+(or edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also
+use a distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices; vertices
+$v$ and $w$ are said to be \emph{adjacent} if $e(v, w) \ne \bot$ or $e(w, v) \ne \bot$. We write
 $\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
 of a vertex $v$ (that is, the set of vertices adjacent to $v$); a vertex is \emph{isolated} if its
-neighbourhood is empty. A \emph{path} between two vertices $v$ and $w$ is a sequence of $n$ vertices
-$v = v_1, v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $v_m$ is adjacent
-to $v_{m + 1}$. A graph is \emph{connected} if a path exists between each distinct pair of vertices.
+neighbourhood is empty. A (weak) \emph{path} between two vertices $v$ and $w$ is a sequence of $n$
+vertices $v = v_1, v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $v_m$ is
+adjacent to $v_{m + 1}$. A graph is (weakly) \emph{connected} if a path exists between each distinct
+pair of vertices.
 
@@
 (i.e.\ edges) in $G$ instead (it is not entirely clear what the objective should be in directed
-graphs, or when loops are present). We restrict ourselves to the induced version in this paper (??
-we could do a journal version, because the clique side is rather involved\ldots).
+graphs, or when loops are present). We restrict ourselves to the induced version in this paper.
 
@@
 
-Another widely studied approach is to reduce the problem to finding a maximum clique (or sometimes,
-equivalently, an independent set or a vertex cover ?? cite) in an association graph (which we describe
-below). Conventional wisdom is that this approach is less effective in practice, but previous
+Another widely studied approach ?? cite is to reduce the problem to finding a maximum clique (or sometimes,
+equivalently, an independent set or a vertex cover ?? cite) in an association graph \cite{LeviG}; we describe
+this below. Conventional wisdom is that this approach is less effective in practice, but previous
 experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
@@
 (Other approaches have been tried, including dedicated algorithms ?? cite, mixed integer programming
-\cite{DBLP:journals/anor/PivaS12}, and heuristics ?? cite; SAT encodings seem to struggle even for
-subgraph isomorphism??  cite IJCAI.)
+\cite{DBLP:journals/anor/PivaS12}, and heuristics \cite{DBLP:journals/jcisd/EnglertK15}; SAT
+encodings seem to struggle even for subgraph isomorphism \cite{UpcomingIJCAIPaper}.)
 
@@
 this paper looks at this variant on arbitrary graphs. In principle, for a constraint programming
-approach, we may simply add a ``forms a connected graph'' global constraint to the model
-\cite{Brown:2005,DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}. Alternatively, we could use a
-special branching rule to maintain connectedness during search ?? cite. We see that using both
-approaches together gives best results ?? does it?.  We also explain how to adapt this branching
-rule to run inside a modern clique-like algorithm, to solve the problem via an association graph.
-
-?? Summary, association graph is better when edges have labels.
+approach, we may simply add a ``forms a connected graph'' global constraint
+\cite{Brown:2005,DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05} to the model. Alternatively, we
+could use a special branching rule to maintain connectedness during search ?? cite. Neither approach
+seems directly viable with an association graph encoding---however, we show that it is possible to
+adapt the combined branching and bounding rule used by modern clique algorithms to preserve
+connectedness during search.
+
+Our experiments suggest that each approach gives broadly similar performance, although the
+association graph works better when graphs have edge labels (and we can explain why), and the
+constraint programming approach is better when edges are unlabelled. For the constraint programming
+model, using both a global constraint \emph{and} the branching rule in conjunction seems to be the
+safest option---although it is not always fastest, it is very rarely substantially worse than just
+using one or the other, and is often substantially better.
 
@@
 
-Explain association graph \cref{figure:association}, cite history, connections to microstructure
-\cite{DBLP:conf/aaai/Jegou93a}.
+Explain association graph \cref{figure:association}, cite history \cite{LeviG}, connections to
+microstructure \cite{DBLP:conf/aaai/Jegou93a}.
 

### 2016-04-06 paper/paper.tex
Graphery

@@
 
-% \usepackage{showframe}
+\usepackage{showframe}
 
@@
 
-\cref{figure:unconnected-33}
-
-\cref{figure:unconnected-plain}
-
 ?? Break this down more by family, size, etc.
@@
     \centering
-    \input{gen-graph-unconnected-33}
-    \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
-    number of instances solved by each approach, in under a certain time. On the bottom, an
-    instance-by-instance comparison of the two approaches: the colour at a point indicates the
-    number of instances with these runtimes.} \label{figure:unconnected-33}
+    \input{gen-graph-unconnected-cumulative}
+    \vspace*{1em}
+
+    \centering
+    \input{gen-graph-unconnected-heatmap}
+    \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
+        labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
+        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the two
+        approaches, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
+        the right.} \label{figure:unconnected-cumulative}
 \end{figure}
-
-% \begin{figure}[p]
-%     \centering
-%     \input{gen-graph-unconnected-33-breakdown}
-%     \caption{Clique versus constraint programming, 33\% labelled, broken down by family.}
-%         \label{figure:unconnected-33-breakdown}
-% \end{figure}
-
-\begin{figure}[p]
-    \centering
-    \input{gen-graph-unconnected-plain}
-    \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
-    number of instances solved by each approach, in under a certain time. On the bottom, an
-        instance-by-instance comparison of the two approaches: the colour at a point indicates the
-    number of instances with these runtimes.} \label{figure:unconnected-plain}
-\end{figure}
-
-% \begin{figure}[p]
-%     \centering
-%     \input{gen-graph-unconnected-plain-breakdown}
-%     \caption{Clique versus constraint programming, undirected, unlabelled, broken down by family.}
-%         \label{figure:unconnected-plain-breakdown}
-% \end{figure}
 
@@
 
-\paragraph{Connected, Undirected, 33\% Labelled} \cref{figure:connected-undir33} Above two seconds,
-    the clique approach dominates except for three instances, and there is only one instance which
-    the constraint programming model can solve but the clique model cannot (?? is this an EHP and does parallel get rid
-    of it?). The clique model is unable to solve only ??  instances within one hour, ?? all of which
-    have 90 or 100 vertices.  On the other hand, for trivial instances, the clique approach is often
-    expensive due to the association graph construction.
-
-\paragraph{Connected, Undirected, Unlabelled} \cref{figure:connected-plain}, looks like the clique
-approach doesn't do so well\ldots
+\paragraph{Connected, Undirected, 33\% Labelled}
+
+\paragraph{Connected, Undirected, Unlabelled}
 
@@
     \centering
-    \input{gen-graph-connected-undir33}
-    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
-        the cumulative number of instances solved by each approach, in under a certain time. On the
-        bottom, the association graph approach compared to the constraint programming approach with
-        both branching and filtering.} \label{figure:connected-undir33}
+    \input{gen-graph-connected-cumulative}
+    \vspace*{1em}
+
+    \centering
+    \input{gen-graph-connected-heatmap}
+    \caption{The cumulative number of connected instances solved in under a certain time: on the
+        top, 33\% undirected labelled graphs with up to 100 vertices, and in the middle, unlabelled
+        and undirected graphs with up to 35 vertices. On the bottom row, an instance-by-instance
+        comparison of the association and MAC both approaches, with 33\% labelled graphs on the
+        left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
 \end{figure}
-
-% \begin{figure}[p]
-%     \centering
-%     \input{gen-graph-connected-undir33-breakdown}
-%     \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, broken down by family.}
-%         \label{figure:connected-undir33-breakdown}
-% \end{figure}
 
@@
     \centering
-    \input{gen-graph-connected-cp-undir33.tex}
-    \caption{A pairwise comparison of different CP techniques for the connected, undirected, 33\%
-        labelled variant with graphs of up to 80 vertices. The colour at a point indicates the
+    \input{gen-graph-connected-cp.tex}
+    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
     number of instances with these runtimes, with darker colours representing more instances.}
-        \label{figure:connected-cp-undir33}
-\end{figure}
-
-\begin{figure}[p]
-    \centering
-    \input{gen-graph-connected-plain}
-    \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
-        cumulative number of instances solved by each approach, in under a certain time. On the
-        bottom, the association graph approach compared to the constraint programming approach
-    with both branching and filtering.}
-\label{figure:connected-plain}
-\end{figure}
-
-% \begin{figure}[p]
-%     \centering
-%     \input{gen-graph-connected-plain-breakdown}
-%     \caption{Clique versus constraint programming, connected, undirected, unlabelled, broken down by family.}
-%         \label{figure:connected-plain-breakdown}
-% \end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \input{gen-graph-connected-cp-plain.tex}
-    \caption{Different CP techniques, connected, undirected, unlabelled, up to 35 vertices.}
-        \label{figure:connected-cp-plain}
+        \label{figure:connected-cp}
 \end{figure}

### 2016-04-07 paper/paper.tex
Terminology

@@
     This problem can be solved either by constraint-based search, or by reduction to the maximum
-    clique problem. We evaluate these two approaches using modern algorithms, and see that the best
+    clique problem. We evaluate these two models using modern algorithms, and see that the best
     choice depends mainly upon whether the graphs have labelled edges. We also investigate a
-    restricted branching approach for the connected version of the problem, show how to implement
+    restricted branching technique for the connected version of the problem, show how to implement
     this in constraint-based and clique-inspired algorithms, and compare it to conventional
@@
 equivalently, an independent set or a vertex cover ?? cite) in an association graph \cite{LeviG}; we describe
-this below. Conventional wisdom is that this approach is less effective in practice, but previous
+this below. Conventional wisdom is that this model is less effective in practice, but previous
 experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
@@
 \cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16},
-and so the first half of this paper re-evaluates the association graph approach using a modern
+and so the first half of this paper re-evaluates the association graph model using a modern
 algorithm.
@@
 \cite{Brown:2005,DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05} to the model. Alternatively, we
-could use a special branching rule to maintain connectedness during search ?? cite. Neither approach
-seems directly viable with an association graph encoding---however, we show that it is possible to
-adapt the combined branching and bounding rule used by modern clique algorithms to preserve
-connectedness during search.
-
-Our experiments suggest that each approach gives broadly similar performance, although the
-association graph works better when graphs have edge labels (and we can explain why), and the
-constraint programming approach is better when edges are unlabelled. For the constraint programming
-model, using both a global constraint \emph{and} the branching rule in conjunction seems to be the
-safest option---although it is not always fastest, it is very rarely substantially worse than just
-using one or the other, and is often substantially better.
+could use a special branching rule to maintain connectedness during search ?? cite. Neither
+technique seems directly viable with an association graph encoding---however, we show that it is
+possible to adapt the combined branching and bounding rule used by modern clique algorithms to
+preserve connectedness during search.
+
+Our experiments suggest that each model and technique gives broadly similar performance, although
+the association graph works better when graphs have edge labels (and we discuss why), and constraint
+programming models are better when edges are unlabelled. For the constraint programming model, using
+both a global constraint \emph{and} the branching rule in conjunction seems to be the safest
+option---although it is not always fastest, it is very rarely substantially worse than just using
+one or the other, and is often substantially better.
 
@@
         with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the two
-        approaches, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
+        models, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
         the right.} \label{figure:unconnected-cumulative}
@@
 \cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
-bitset encoding approach due to San Segundo \textit{et al.}\
+bitset encoding due to San Segundo \textit{et al.}\
 \cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13} (and we refer the reader to these
@@
     \caption{The cumulative number of connected instances solved in under a certain time: on the
-        top, 33\% undirected labelled graphs with up to 100 vertices, and in the middle, unlabelled
+        top, 33\% labelled undirected graphs with up to 100 vertices, and in the middle, unlabelled
         and undirected graphs with up to 35 vertices. On the bottom row, an instance-by-instance
-        comparison of the association and MAC both approaches, with 33\% labelled graphs on the
+        comparison of the association and ``MAC both'' approaches, with 33\% labelled graphs on the
         left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
@@
 
-\begin{figure}[tb]
+\begin{figure}[p]
     \centering
@@
     \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
-    number of instances with these runtimes, with darker colours representing more instances.}
+    number of instances with these runtimes, with darker colours representing more instances. The
+    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
+    rows are for unlabelled and undirected graphs with up to 35 vertices.}
         \label{figure:connected-cp}

### 2016-04-07 paper/gen-graph-connected-heatmap.tex
Include generated stuff for now, to make it easier to build

\begin{tikzpicture}[gnuplot]
%% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
%% Thu 07 Apr 2016 11:12:14 BST
\tikzset{every node/.append style={font={\scriptsize}}}
% \path (0.000,0.000) rectangle (10.922,7.366);
\gpcolor{color=gp lt color border}
\gpsetlinetype{gp lt border}
\gpsetdashtype{gp dt solid}
\gpsetlinewidth{1.00}
\draw[gp path] (1.320,5.785)--(1.320,2.197)--(4.908,2.197);
\node[gp node center,rotate=-270] at (0.246,3.991) {Association Runtime (ms)};
\node[gp node center] at (3.114,1.427) {MAC Both Runtime (ms)};
\begin{scope}
\clip (1.320,5.785) rectangle (4.908,2.197);
\def\gprawrgbimagedata{%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff846eff6f65ff846eff7e6cff6f65ff8c72ff7367ff7e6cff8c72ff7869ffffffffac88ff9576%
  ff9576ff7869ff8c72ffac88ff846eff9576ff9576ff9f7dff8c72ff9f7dff8c72ff9576ffac88ff9f7dff8c72ff8c72%
  ff8c72ff9576ff8c72ff9f7dff8c72ffffffff9f7dff9576ff9f7dff9576ff9576ff9576ff7e6cff9f7dff9f7dffffff%
  ff9f7dffac88ff9f7dffffffff7e6cffac88ffffffffffffffffffff9f7dff9f7dffffffffffffffac88ffac88ffac88%
  ff9576ffac88ffffffffac88ffffffffffffff9f7dffac88ff9f7dffffffff9f7dffac88ff9f7dff9576ff6f65ff7869%
  ff7e6cfc6260fc6260ff6b63ac0527ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffac88%
  ffffffffffffffac88ffac88ffffffffac88ff9f7dffffffff9f7dee4156ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffac88ffac88ffffffffac88ff9f7ded4155ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7d%
  ff8c72ff9f7dff9f7dec3f55ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9576ffffffff9f7dffffff%
  ffac88ffffffffac88ff9f7dff9f7dff9576ff9f7dffac88e93c53ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ffac88ffffffff9f7dff8c72ff9576ff9f7dff9f7dff9f7dffffffffffffec4055ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffff7e6cffac88ffac88ff7e6cff9f7d%
  ff9f7dff9576e33450ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffffffff9576%
  ffac88ff846effac88ffac88ffac88ffac88ff9576ec3f55ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffac88ffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffac88ffac88%
  ff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9576ffac88ffac88ffac88ee4156ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffff9576%
  ffac88ffffffff9f7dff9f7dffac88ffac88ff9f7dff9f7dff9576ffffffff9f7dff9576ffffffff9576ffffffff9f7d%
  ffac88e1314fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ff9f7dff9f7dffac88ff8c72ff7e6c%
  ff9576ffffffff9576ff9576ff846eff9576de2e4dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ffac88ffffffffffffffffffff9f7dffac88ff9f7dff9f7dffffffff9f7dff9f7dff8c72ffac88ffffffff9576ff9f7d%
  ff9f7dff8c72ffffffff9576ffffffff8c72ffac88ffffffffffffff8c72ff9576dd2d4dffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffff9f7dff9f7dffac88%
  ffffffffac88ff9576ffffffffac88ff9576ffac88ff9576ffac88ff9f7dff846effac88ff8c72ff846eff8c72ff8c72%
  d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffffffff%
  ffac88ffac88ffffffffac88ffffffffac88ff9576ff9f7dffac88ff9f7dffac88ffac88ff9f7dffac88ffac88ff9f7d%
  ff9f7dff9576ff9f7dff8c72ffac88da294bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ff9576ffac88ffac88%
  ffffffff9f7dff8c72ffac88ff9f7dffac88ff846effac88ff846efe6862da294bffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffac88ffac88ffac88ff9f7dffffffff8c72%
  ffac88ffffffffffffff9f7dffffffff9f7dff9f7dffac88ff8c72ff8c72ffffffff9576ff7869ff7367ff8c72d7264a%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffac88ffffff%
  ffffffffac88ffffffffac88ffffffff9f7dffac88ff9f7dff9f7dffac88ffffffff9f7dff9f7dff7e6cff9576ff9f7d%
  ff9576ff7869ff7869ff6f65d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffac88ffffffffffffffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dff9f7dff9f7dff9f7dff9f7dffffff%
  ff9f7dff9576ff8c72ff9576ff9576ff7869ff7e6cf6545cfc6260d52349ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffff9f7dffffffffffffff8c72ff9f7dffac88ff9576%
  ffac88ff9576ff8c72ff9f7dff9f7dff9f7dff8c72ff9576ff6f65ff846eff6f65ff6b63fd6561fd6561d21f47ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffff%
  ffffffffffffffffffffffffff9f7dff9f7dff8c72ff9f7dffffffffac88ff9576ff7e6cff846eff846efe6862ff6b63%
  fe6862f7565cfc6260d8264affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88ffffffffac88%
  ffffffffffffff9576ffffffffac88ffac88ff9f7dffffffffac88ff8c72ffffffff9576ffac88ffac88ffac88ff7367%
  ff6f65ff7e6cfe6862fe6862f7585dfb605ffe6862f95c5ed32148ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9576ffac88ff9f7dffffffff9f7d%
  ff9f7dff9f7dff9576ff7e6cff8c72ff9576ff6f65ff6b63ff6b63fb605ffd6561ff6b63f85a5dda294bffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ff9f7dff9f7dffac88ffac88%
  ffffffffffffff9f7dff9f7dff9f7dffac88ff9f7dff9576ff6f65ff8c72ff7e6cff6b63fe6862ff6f65f34d59fe6862%
  f85a5dff6f65d7254affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffff%
  ffac88ffac88ff9f7dffac88ffac88ff9576ff8c72ff9576ffac88ff9576ff846eff9576ff8c72ff846efa5e5ffb605f%
  fa5e5ff7585dfb605ff7565cf85a5dfe6862fc6260d8264affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffffff%
  ffffffff9576ffffffffac88ffffffffffffffac88ffac88ffac88ff8c72ff9f7dff8c72ffac88ff8c72ff846eff7869%
  ff7e6cfd6561fd6561fd6561fa5e5ffd6561fa5e5fff6b63f85a5dfd6561fb605fff7e6ce1314fffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffff9f7dffac88ff9576ffac88ffac88ffffffffac88ffffffff9f7dff7e6cff9576%
  ff7367ffac88ff7869ff7869fe6862ff6b63fc6260fd6561ff7367fe6862fc6260fe6862f85a5df7585dfe6862ff6f65%
  ff6b63e73952ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffac88ffffffffffffffffffffffffffac88ffffffff9f7dffac88ffac88ff9f7dff9576%
  ffffffff9576ffac88ff8c72ff846eff9576ff846eff6f65ff846eff846eff7367f85a5dfb605ffc6260f7585df7565c%
  fd6561ff7367ff6f65fe6862ff7e6cff846eef4356ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffac88ffffffffac88ffffff%
  ffac88ff9f7dff9576ffffffffffffff8c72ffac88ff9576ff9576ff9576ff9576ff9576ff9f7dff7e6cff846efe6862%
  ff7869ff8c72fe6862ff6b63ff7367ff7869ff8c72ff846eff846eff9576ff9f7de83b53ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88%
  ffffffffac88ffac88ffffffffffffffffffff9576ff9f7dff8c72ff9576ff9f7dff846effac88ff9576ff8c72ffac88%
  ff7e6cff7e6cff8c72ff8c72ff6b63ff846eff6f65ff7869ff7367ff9f7dff9576ff7e6cff846eff9f7dff8c72ff8c72%
  ed4155ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9f7dff9576ff846eff9f7dffac88ff8c72ffac88%
  ff9576ff9576ff9f7dff846eff8c72ff7e6cfe6862ff6f65fc6260ff9576ff8c72ff846eff7e6cff9576ff9f7dff9576%
  ffffffff8c72ffac88ffac88ffac88f24a59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffff8c72ffffffff9f7dff9576%
  ff8c72ff9f7dffac88ffac88ff9f7dff846eff7869ff9f7dff7e6cff7e6cff7367ff6f65fd6561ff7e6cfe6862fe6862%
  ff9576ff8c72ff9f7dff846effffffff9f7dff9f7dff9f7dffac88ffffffe93c53ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dff9f7d%
  ffffffff9f7dff9576ff9f7dffac88ffac88ff9576ff8c72ff9f7dff9f7dff846efe6862ff6b63fd6561ff7367f95c5e%
  fe6862ff6f65ff846eff7e6cff7869ff6b63ff846eff9f7dff9f7dff846eff8c72ff9f7dff8c72ffffffff9f7df34d59%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ff9f7dff7e6cff8c72ff9576ff8c72ff846eff8c72ff8c72%
  fd6561ff7e6cfc6260ff846eff7869fd6561f95c5ef95c5eff6f65ff7e6cff9f7dff846eff9576ff9f7dff9576ffac88%
  ffac88ff8c72ff9576ff9f7def4457ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9f7dff9576ff8c72ff9f7d%
  ff8c72ff7367ff8c72fe6862ff7367ff6b63fb605ffc6260fe6862f85a5dfd6561f7565cff6f65fe6862ff6f65ff7869%
  ff8c72ff9576ff8c72ff9576ffac88ffffffffac88ffac88ff9f7df14858ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffac88ffac88%
  ff8c72ff7869ff9f7dff9f7df95c5eff7869fe6862fd6561ff7367fa5e5ff95c5ef7565cf5515bf6545cf7585dfc6260%
  fb605fff6f65fc6260ff6f65ff6b63ff846eff8c72ff9f7dff9576ffac88ffac88ffac88ff9576ffac88ef4356ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
  ff9576ffac88ffac88ff7367ff846eff7367fe6862ff6f65fb605ffd6561f95c5eff6f65f7585dff6b63f95c5ef85a5d%
  f7565cf24a59f5535bf4505aff6b63f7585dfa5e5fff6f65ff6b63ff7e6cff8c72ff8c72ffac88ff9f7dff9f7dff8c72%
  ffffffff8c72ff846ef14958ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffff%
  ffac88ffffffffffffffffffffac88ffac88ffac88ff9576ff9576ff7e6cff8c72ff7367f95c5eff7869f85a5dfb605f%
  fb605ff85a5df85a5dfc6260f6545cfa5e5ff7585dfd6561fa5e5ffc6260ff6b63ff7869ff7e6cff8c72fd6561ff846e%
  ffac88ffac88ff9f7dffac88ff9576ff9f7dff9576ff846ef7585dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffffff846eff8c72ff7e6cff846eff7e6c%
  ff6f65fb605ffe6862ff6b63fc6260f95c5efb605ff85a5df7585dfa5e5ffd6561fe6862fb605ffd6561fe6862ff6b63%
  ff6f65ff846eff7e6cff9f7dff8c72ff9576ff9f7dffac88ff9576ff9576ffac88ff9f7dffac88f24b59ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dff846effffff%
  ff846eff9576ff8c72ff7869ff7e6cff7367ff7367fa5e5ffc6260f7585dfb605ffb605ff95c5efe6862fc6260fb605f%
  ff7869ff6b63fe6862ff7367ff7869ff8c72ff9576ff7e6cff9576ff9576ff9f7dff9f7dff9f7dff8c72ff8c72ff7869%
  ff846eff9576f04557ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ffac88ffffffffac88ff9f7dff8c72ff9576ff846eff7367ff6f65ff7e6cf95c5efc6260fe6862fd6561fc6260fb605f%
  f95c5ef95c5ef95c5eff6f65fd6561ff8c72fd6561ff7e6cff6f65ff846eff8c72ff7869ff8c72ff9576ff9f7dffffff%
  ff846eff8c72ff9f7dffac88ff9f7dff846eff9f7df5515bffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffac88ff9576ffac88ffac88ff9576ff846eff846eff7e6cff7367fb605ffe6862ff6b63%
  fc6260fd6561ff846efb605fff8c72ff7e6cfb605fff6f65ff7869ff8c72ff7869ff6f65ff846eff6f65ff7e6cff846e%
  ff9576ff9576ff9576ff9576ff9576ff846eff846eff9576ff846eff9576ff9576ff9f7df24a59ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffff9f7dff9576ffffffff9576ff9f7dff846efe6862%
  f7565cff6f65f7565cf95c5eff7367fc6260fa5e5fff7367fe6862ff7869ff7869ff7e6cff7e6cff846eff7367ff9576%
  ff7e6cff7e6cff8c72ff846eff846eff9576ff7869ff7869ff8c72ff8c72ff9f7dff846eff9576ff7869ffffffff9576%
  ff9576e93c53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dff9f7dffac88ffac88%
  ff9f7dff9576ff9f7dff8c72fe6862fd6561fd6561fc6260ff7367ff7367ff7869ff7869fd6561ff6b63ff6b63ff7367%
  ff7e6cff846eff7367ff7869ff846eff7869ff7869ff846eff9f7dff7367ff8c72ff8c72ff8c72ff9576ff9f7dff9576%
  ff9f7dff8c72ff9576ff9576ff9f7dff9f7df34d59ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffac88%
  ffac88ff9f7dffffffffac88ffac88ffac88ff9f7dff8c72ff846eff7e6cff9576f85a5dff6f65ff6b63ff6b63ff7869%
  fc6260fd6561fe6862ff6b63fd6561ff6b63ff846eff7e6cff9576ff9f7dff8c72ff9576ff8c72ff7869ff8c72ff7e6c%
  ff8c72ffac88ff9f7dffac88ffac88ff9576ff9576ff9576ff8c72ff9576ffac88f4505affffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffac88ffffffffffffffac88ff8c72ff9f7dff8c72ff7367ff846eff846eff7e6cff7869ff8c72%
  fc6260ff7e6cff7367fb605fff7869ff7e6cff7367ff7e6cff7367ff7869ff8c72ff7e6cff8c72ffac88ff8c72ff7869%
  ff9576ff7367ff846eff7367ff7367ff7e6cff8c72ffac88ffac88ff7869ff846effffffff9576ff9576ff9f7dff9576%
  f14958ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ff8c72ff846eff9576ff9576ff9576%
  ff7869ff6b63ff846eff7869ff7e6cff7e6cfb605fff7367ff7e6cff9576ff8c72ff9576ff8c72ff8c72ff9576ff7367%
  ff6f65ff6f65ff7367ff8c72ff9576ff9576ff9f7dff7e6cff846eff7e6cff7e6cff846effac88ff9576ff9576ff9f7d%
  ff8c72ff9f7dffffffffac88ff9576ef4457ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffff9f7dffffffff9f7dffffffffffffffffffffac88ffffffff9f7dffac88ff9f7d%
  ff9f7dff846eff846eff8c72ff7367ff6f65ffac88ff6b63ff7869ff7869ff8c72ff9f7dff9f7dff7e6cff7e6cff8c72%
  ff8c72ff9576fe6862ffac88ff7869ff8c72ffac88ff7e6cff9576ff846eff7e6cff8c72ff7e6cff8c72ff7367ffac88%
  ff8c72ff8c72ff7869ff8c72ff9f7dff9576ffac88ff9f7dffac88ff846ef24a59ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88%
  ffac88ff846eff9576ff8c72ff9576ff9f7dff9f7dff846eff7e6cff7367ff7e6cff7869ff7e6cffac88ff9576ff6f65%
  ff9576ff7e6cff846eff9576ff7e6cff7e6cff7e6cff846eff7e6cff8c72ff8c72ff7869ff9f7dffac88ff9f7dff9f7d%
  ff8c72ff9576ff846eff9576ff7869ff8c72ff6f65ff846eff9576ff846eff9576ffac88ff846eff9f7dffac88f14958%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88%
  ffffffffffffffffffff9f7dffac88ffac88ffffffffac88ff8c72ff846eff9f7dff8c72ff8c72ff7e6cff7869ff7869%
  ff8c72ff6f65ff846eff7e6cff6f65ff7e6cff8c72ff846efb605fff7e6cff6b63ffac88ff846eff9576ff846eff8c72%
  ff9576ff8c72ff7869ff9f7dff9f7dff846eff8c72ff9f7dff8c72ff8c72ff9576ff846eff846eff9576ff9576ff9f7d%
  ff9576ff9f7dff7e6cff9f7df24a59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ff9576ffffffff9f7dffac88ffffffffac88ff9f7dff8c72ff9576ffac88ff8c72%
  ff9576ff7367ff7367ff7869ff9576ff8c72ff9576ff8c72ff7e6cff846efe6862ff7869ff7367ffac88ff6f65ff7e6c%
  ff7e6cff7e6cff846eff7e6cff846eff8c72ff8c72ff7869ff9576ff846eff846eff8c72ff846eff7e6cff8c72ff9576%
  ff9576ff9576ff9576ffac88ff9576ff8c72ffac88ff846efffffff85a5dffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffff9576ff9576ffffffff846eff9f7dffac88%
  ff7869ff9576ff7e6cfe6862ff7869fe6862ff7367fd6561ff9576ff7367ff7367ff7367ff846eff9576fa5e5fff7e6c%
  fb605fff7367fe6862ff846eff6f65ff846eff8c72fd6561ff8c72ff7869ff846eff6f65ffffffff9f7dff8c72ff846e%
  ff7e6cff7869ff9576ff9576ff8c72ff9576ff8c72ff9f7dff7e6cff846eff9f7dff9f7dff8c72ffac88f85a5dffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffffffffac88%
  ff9576ffffffff9576ff8c72ffac88ff7367ff7869ff9576fc6260ff6b63fe6862ff846eff846eff846eff6f65ff7869%
  ff6f65ff8c72ff9f7dff7e6cff846efd6561ff6b63ff846eff7869ff7e6cff7e6cff9f7dff7869ff846eff7e6cff846e%
  ff8c72ff846eff9576ff9f7dff9576ff6f65ff9f7dff846eff9f7dff7e6cffac88ff9576ff9576ff8c72ff8c72ffffff%
  ffac88ffac88ff9f7df24b59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ff9576ff846effffffff9576ff9576ff9576ffac88ff846eff846eff7e6cff6b63ff7367fe6862ff7869ff6f65%
  ff7e6cff7869ff7e6cff7869ff846effac88ff846eff7367ff9576fd6561ff7869ff7367ff6f65ff7869ff7869ff846e%
  ff846effac88ff7367ff8c72ff846eff8c72ff7367ffac88ff846eff7e6cff846eff7869ff7869ff846eff846eff9576%
  ff9f7dff8c72ffac88ffffffffac88ff9576ff846eff9576f7565cffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffac88ffffffffffffffffffffac88ffac88ff9576ffffffff9576ff8c72ff9576ffac88fa5e5f%
  ff846eff7367ff7e6cff846eff9f7dff6f65ff7367ff9576ff9f7dff9576ff7869ff7869fd6561ff7367fb605fff846e%
  fe6862ff9576ffac88ff7367ff7e6cff7869ff7e6cff9576ff9576ff7869ff6f65ff846eff6f65ff9576ff7869ff7e6c%
  ff846eff846eff6b63ff7e6cff9576ff8c72ff9f7dffac88ff9576ff7869ff9f7dffac88ff9576f34e5affffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9f7dffac88ffac88ffffffff9f7dffffffff9f7dffffffff9f7dff9576ff846eff9576ff8c72%
  ff9576ff9f7dff846eff846eff7e6cff9f7dff8c72ffac88ff7869ff7e6cff9f7dff9f7dff9576ff846eff8c72ff6f65%
  ff7367ff6b63ff7367ff846eff6b63fe6862ff846eff8c72ff6b63ff9576ff9f7dff9576ff7869ff846eff9576ff846e%
  ff846eff7869ff8c72ff7869ff6f65ff7e6cff8c72ff9576ff9576ff8c72ff9576ffac88ff9576ff9f7dff8c72ff846e%
  ff9576ffac88f5535bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dff8c72ffffffffac88ffffffff9f7d%
  ffac88ff8c72ff9f7dff9576ff9576ff846eff846eff7e6cff7869ff8c72ff7869ff9f7dff846eff7e6cff9576ff9f7d%
  ff8c72ffac88ff9f7dff846eff7367ff6b63ff846eff7869ff6f65ff7367ff9576ff846eff7367ff846eff8c72ff7e6c%
  fe6862ff6b63ff9576ff7e6cff7e6cffac88ffffffff846eff7e6cff8c72fe6862ff6f65ff7e6cffffffff8c72ff846e%
  ff9576ff846eff9576ff8c72ff9576ffffffffac88f24b59ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88%
  ffffffff8c72ffac88ff9f7dffac88ff9f7dff9f7dff7e6cff9f7dff7869ff846eff7e6cff9f7dff7367ff9576ff7869%
  ff7e6cff8c72ff6b63ff846eff7869ff9f7dff7e6cff846eff8c72ff7367ff7e6cff9f7dff7367ffac88ff7869ff846e%
  ffffffff8c72ff8c72ff8c72ff846effffffff7869ff9576ff7367ff7367ff9576fd6561ff7e6cff846effac88ff9f7d%
  ff8c72ff9576ff9576ff9f7dff6f65ff9576ffac88ff7869ff846eff9f7dff9576ff9576f6545cffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffff7367ff7e6cff9576ffffffff8c72ff8c72ff7e6c%
  ff7e6cff7869ff7e6cff846eff6b63ff7367ff7869ff7869ff7869ff7367ff9576ff846eff846eff846eff8c72fe6862%
  ff6b63ff7869ff846eff8c72ff9576ff9576ff846eff9576ff7e6cff846eff846eff846eff7367ff9576ff7e6cff6b63%
  ff846eff8c72ff9f7dff8c72ff9576ff846eff9576ff9f7dff7e6cff846eff9f7dff9f7dff8c72ff7869ff9576ffac88%
  ffac88f04557ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ff9576ffffffffac88ff9576ff9f7dff9576ff9576%
  ff9f7dff9f7dff8c72ffac88ff9576ff7869ff7869ff7869fd6561ff7869ff6b63ff7869fb605fff846eff7869ff8c72%
  ff7e6cff8c72ff846eff7e6cff8c72ff6f65ff7e6cff9576ff9576ff9576ff9f7dff846eff7869ff846eff9576ff7869%
  f85a5dff846eff7869ff7869ff846eff846eff7869ff846eff6f65ff8c72ffac88ff846eff9f7dffac88ff8c72ff8c72%
  ff9f7dff9f7dff9576ff9f7dffac88fffffff95c5effffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffac88ffffff%
  ff9f7dff846eff8c72ff9f7dff6f65ff9576ff7367fe6862ff7e6cff846eff7869ff6b63ff7367fd6561f85a5df85a5d%
  ff6b63ff7367ff7367ff7e6cff7869ff8c72ff8c72ff846eff8c72ff8c72ff846eff846eff8c72ff846eff7e6cff6b63%
  ff6f65ff7367ff9576ff7869ff6f65ff9576ff9576ff7e6cff846eff7367ff8c72ff7e6cff8c72ff9f7dff8c72ff9576%
  ff9576ff9576ff846eff9f7dff9576ff8c72ffac88ff8c72ff8c72ff8c72ffac88ff6b63ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffac88ff8c72ffffffffac88ff9576fe6862ff9576ff6f65ff9576ff7367ff7e6cff6f65ff6f65%
  f7585df7585dfd6561fa5e5fff7367ff7869ff6f65ff6f65ff846efe6862ff846eff9576ff8c72fe6862ff7869ff7367%
  ff7e6cff9f7dff7e6cff9576ff8c72ff8c72ff8c72ff7869ff9f7dff846eff6b63ff6f65ff7367ff7869fb605fff846e%
  ff6b63ff8c72ff9f7dff9576ff7e6cff7e6cff846eff7367ff7e6cff7e6cff9576ff8c72ff8c72ff9f7dff846eff9f7d%
  fa5e5fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9576ff9576ff846eff8c72ff7869ff9576ff7367%
  ff846eff7e6cff6f65fb605ff5515bf4505af4505af5535bf95c5eff6f65ff7869fe6862ff7869ff6f65ff846eff7e6c%
  ff846eff6f65ff7e6cff846eff7367ff7e6cff9f7dffac88ff846eff9f7dff846eff7e6cff7e6cff846eff9576fd6561%
  fd6561ff9576ff7367ff7869ff7869ff8c72ff846eff846eff7e6cffac88ff7e6cff9f7dff9f7dff846eff8c72ff9f7d%
  ff7e6cff8c72ff9576ff9576fffffffe6862ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffffff9f7dff9576ffffffff9576%
  ff9576ff7367ff846eff7869fa5e5ffa5e5ffe6862fa5e5ff24b59f5535bf4505af34d59fc6260f7565cff7e6cfc6260%
  ff6f65fe6862ff7869ff8c72ff7367ff846eff9576ff8c72ff9576ff846eff846eff6b63ff7367ff9f7dff6f65ff8c72%
  ff6f65ff7869ff846eff846eff7367ff7e6cff7e6cff7869ff8c72ff846eff7869ff9f7dff9576ff846eff7869ff846e%
  ffac88ff9f7dffac88ff8c72ff8c72ff9576ff846eff9576ff8c72ff9576ff7367ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffff9f7dffac88%
  ffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffff9f7dffac88ffffffff9f7dff9f7dff9576ffac88%
  ffffffff9f7dff8c72ffffffff8c72ff7869ff8c72ff8c72fa5e5ff85a5dff6f65fa5e5ff85a5df24b59fa5e5ff5535b%
  f14958fb605ff85a5dfc6260ff7e6cff6b63ff6b63ff7869ff7e6cff7367ff9f7dff7367ff7e6cff846eff6f65ff7869%
  ff7869ff9576fe6862ff7869ff7869ff7e6cff7e6cff6f65ff7367ff7367ff8c72ff846eff6b63ffac88ffffffff846e%
  ff7869ff7e6cffac88ff9576ff9576ffffffffffffffac88ffac88ffac88ff9f7dff9576ffac88ffffffffac88ff7869%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
  ff7e6cff9576ff8c72fc6260ff7367ff9f7dff7367ff9576ff9f7dff9576ff7869ff8c72ff9f7dff8c72ffffffff8c72%
  ff7869ff8c72ff9f7dff9576ff9576ff9576ff8c72ff9576ff9576fd6561ff8c72ff9f7dff7869fb605ff85a5dfc6260%
  f5515bf4505aee4256f5535bf34d59f04757f34e5af6545cf85a5dfb605ffd6561fb605fff7e6cff7869ff7e6cfe6862%
  ff7869ff7e6cff7367ff7367fe6862fe6862ff9576ff6b63ff6f65fc6260ff7869ff6b63ff7367ff6f65ff7869ff7869%
  ff7869ff846eff7367ffac88fe6862ff7367ff8c72ff9f7dff846eff9576ffac88ff9f7dff9576ff9576ff9f7dffffff%
  ffffffff9576ff9576ffffffff6b63ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff7367fe6862ff7367f95c5efc6260f95c5ef95c5eff6b63fa5e5ffc6260fe6862f5515b%
  fc6260fa5e5ffd6561ff7367ff7367fe6862ff846eff9f7dff846eff7367ff7367ff846eff6b63fe6862fe6862fd6561%
  ff7367ff6b63fe6862f14958f4505aee4256f4505af04757f14958ef4356f04557f14958f4505afa5e5ff95c5ef95c5e%
  ff7367fe6862ff846efd6561fe6862ff7e6cfc6260ff846eff7e6cfd6561fd6561ff7869fe6862ff6f65f95c5eff6b63%
  ff7869ff8c72ff8c72ff7367ff7869ff9576ff8c72ff846eff846eff9576ff846eff9576ff846eff8c72ff9f7dff7e6c%
  ff9f7dffac88ff9576ff9f7dff9576ff9f7dffac88ffac88ffac88ff7869ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88fe6862f5535bf7585df7565cf34e5af14858f14858%
  f7565cf7565cf5515bf7565cfa5e5ff34d59f34d59f34e5afc6260f4505af5535bfd6561ff7367fe6862fc6260ff6f65%
  fc6260fa5e5ffc6260f7565cff6b63f4505af7565cf5535bf34d59f24a59ee4256f04557ef4356ed4155ef4457f04557%
  ea3d54f04757ee4156f5515bf5535bf6545cf7565cff846eff846eff6f65f95c5efc6260f85a5df6545cfd6561fc6260%
  fd6561fc6260fe6862fb605fff6b63ff7367ff846eff7367ff7869ff9576ff846eff9f7dff9f7dff846eff9576ff7869%
  ffac88ff7869ff9576ff9576ff8c72ff9576ff8c72ff9f7dffac88ff9576ff8c72ffac88ffffffff9f7df7585dffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff6b63fc6260f6545c%
  f5535bf14858f04557f7565cfa5e5ff5515bf6545cf95c5ef7565ced4155de2e4ed62449df2f4eef4457f14858f95c5e%
  f5515bf85a5dff7367f5535bfa5e5fff6b63f85a5df5535bf85a5dfb605ff5535bf14858ef4356e83a53eb3e54eb3e54%
  f14958e83b53e73952ee4156ec3f55ec3f55ee4156ed4155f85a5df04757f14858f14858f34d59f4505af5535bfe6862%
  f4505af5515bfa5e5ffd6561fc6260f6545cff6f65ff6b63fc6260fd6561ff6b63fc6260ff6f65ff7e6cff6b63ff9f7d%
  ff9f7dff7869ff7367ff9576ff7869ff7e6cff8c72ff846eff7869ff9f7dff9576ff846eff8c72ff9576ff9576ffac88%
  ffffffff9f7dffffffe63852ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffac88fa5e5ffc6260f95c5ef95c5eff6b63fe6862ff6f65fc6260ff7e6cfd6561ff7e6cfe6862f5515bd9284bbe1037%
  b80c32d21f47db2a4ce33550f24b59f6545cf7585df24a59f4505af6545cfe6862fa5e5ff6545cf6545cec4055ed4155%
  e83a53df304ee33450e73a52ef4356e83a53e63852e73952e73a52eb3e54f4505aed4155ef4457fb605ff4505aef4457%
  ee4256f5515bf7585df14958f4505afb605ff85a5dff6f65fe6862fe6862fa5e5ffe6862ff846eff7367ff7e6cfb605f%
  fe6862ff7e6cff6b63ff846eff7367ff7869ff9576ff8c72ff9f7dff8c72ff9576ff7e6cff9576ff8c72ff7e6cff8c72%
  ff9f7dffac88ff7e6cff9576ff9f7dffac88ff7e6cff9f7dec4055ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffff7e6cf04757f7585df5535bf34d59f34e5aff7367fb605ffd6561fd6561ff6f65%
  fd6561fd6561ff6b63e43651d7254ad7254ae83b53f34e5af24b59f5515bef4457f34e5aee4256f7565cf5515bf85a5d%
  f04757ef4356e73a52ea3d54e2324fd8264adb2b4ce23350e63852e43651ee4156e83a53e43651ea3d54e73a52e43651%
  f04757f04757ef4356f7565cf14858f14858f34d59f34e5af14858f34e5afa5e5ffa5e5ff5515bfa5e5ff6545cfa5e5f%
  ff7367ff7367ff6f65ff7e6cfe6862ff7e6cff846eff6b63ff7367ff7869ff8c72ff7869ff7367ff7e6cff7869ff8c72%
  ff6f65ff7869ff846eff9576ff846eff8c72ff846effffffff9576ffac88ff9f7dffac88ff9f7df24b59ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7869ee4156e93c53f04557f14958e73a52%
  ec4055ec3f55f24b59fb605ff5515bf5515bf34e5af34e5aec4055f24a59f7585df24b59fc6260f5515bf95c5ef6545c%
  f6545cf6545cf14958ed4155e93c53ed4155e43651e33450e2324fdb2a4cde2e4de63852e33550e73a52ee4156e53751%
  ea3d54ec3f55ed4155ec4055e93c53ed4155e93c53f04557ee4256f14858f34d59f5515bef4457f24a59ef4356f85a5d%
  fa5e5ff95c5efc6260f7585dfe6862fa5e5ff85a5df85a5dff6f65ff6b63fe6862ff7e6cff6b63ff6b63ff6b63ff7869%
  ff7e6cfd6561ff8c72ff7367ff7367ff7367ff7e6cff8c72ff8c72ff7e6cff9f7dff9f7dff8c72ff9576ffac88ff9f7d%
  ff9576ffffffee4156ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff6b63%
  ec4055e73a52ef4356e83a53f34e5af14858f24b59fb605ff6545cf7585dea3d54d21f47ca1941c7173ed62449e63852%
  f34d59f85a5def4457f7565cf5515bf14858f4505af24a59f14858eb3e54e33550e73a52e53651e0314fdf2f4ee53751%
  dc2c4de43551e63852e53751ea3d54f24a59e83a53ee4256f04757ea3d54e63852ef4457ec4055ef4356f14958f14858%
  eb3e54f7565cf24a59f04557f4505af24b59fa5e5ff6545cf85a5df6545cf5535bf95c5ef7565cf5535bfc6260f7585d%
  ff8c72ff7e6cff9576ff6f65ff7e6cff7869ff9576ff7e6cff7367ff9576ff7869ff8c72ff7869ff846eff8c72ff846e%
  ff846eff9576ff9f7dff9f7dff9576ff9576ff9f7de53651ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ee4156f85a5df4505afd6561ff7869fa5e5fff846efb605fff846eff7e6cff9576fb605fda2a4c%
  c7173ebe1037c2133bd42248e53751eb3e54f04757f85a5df34e5af34e5aef4356f04557ee4256eb3e54e1314fe23450%
  e63852ea3d54e63852e43651e63852e1324feb3e54e23350ee4156f24a59ef4356f04757f14958f14858ed4155ee4256%
  f4505af04557f04557ee4156f5535bf6545cf4505af34d59f6545cfb605ffe6862f6545cfc6260fc6260fb605ff7565c%
  ff6b63fa5e5fff6f65ff6b63ff6f65ff7e6cff6b63ff9f7dff6f65ff8c72ff9576ff9576ffffffffac88ffac88ff8c72%
  ff9576ff7e6cffac88ff9f7dff9f7dff9f7dff846eff8c72ffac88ff8c72ff9f7dff9576e0314fffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff846ed21f47d11e46e2324fe53651ec4055ee4156f34d59f5515bff7367%
  f95c5efe6862fb605ff4505ae93c53e63852d8264ac6163ecf1d45d42148d9284be33450ea3d54e73952e23450d9284b%
  df2f4ee63852df2f4edd2d4ddc2c4cdf2f4ee43651e33550ea3d54e63852ea3d54eb3e54e93c53f4505aef4356ef4356%
  ef4356f14858f04757f5515bf5535bf24b59f6545cf24a59fc6260f7585df5535bf5515bfa5e5ff7565cff6b63ff7869%
  ff7367ff7e6cff6b63ff8c72ff7869ff6f65ff7869ff7367ff9f7dffac88ffac88ff7e6cffac88ff9f7dff9576ff8c72%
  ffffffff9f7dffffffffffffffac88ffac88ff9576ff8c72ffac88ffac88ffac88ff9f7dffac88ff9576ffac88ff9f7d%
  ffac88f7585dffffffffffffffffffffffffffffffffffffffffffffffffff7367e33450bd1036d11e46d62449dd2d4d%
  e23350e93c53ef4356f14858f24a59f7585df7585ded4155e0314fe23450de2d4dca1940c01239c91840d42148d7254a%
  e53651db2a4ce73952e33450dc2b4cda294be33450e2324fe2324fe63852df304ee0304ee43551ee4156e23450ed4155%
  f04757ee4256ef4457f24b59ea3d54e1324fed4155ee4256ef4356f04557fa5e5ff5535bf5515bf6545cff7869fc6260%
  fe6862ff6f65ff7367ff7367ff7869ff8c72ff7e6cff9576ff9576ffac88ff7e6cff9576ff9576ff9f7dff9576ff9f7d%
  ffac88ffac88ffac88ff8c72ffac88ffffffff8c72ffffffff9576ffffffffffffffac88ffac88ffffffffffffffac88%
  ffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffd52248%
  d42248df2f4ee83a53ee4256f5515bf14858fe6862fc6260f5535bee4256dd2d4de23350d52248ca1941c8183fd52349%
  da294bdb2b4ce0304ee33550e43551e73952e83b53e53751e83a53e43551e43551de2e4de23450e53651e53751ec4055%
  e93c53ea3d54ef4356ed4155f14958f14858f5535bef4356ef4356ee4256f85a5df85a5df7565cfa5e5ff7565cfd6561%
  ff6b63ff7367ff7869ff7869ff8c72ff9576ffac88ff9576ffffffff8c72ff9576ff9f7dffffffff9f7dff9f7dff9f7d%
  ff9f7dff8c72ffac88ff9f7dff8c72ffac88ffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9f7dffac88ff9f7d%
  ffffffffffffffac88ffac88ffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffff7e6cc4153cce1c44d9274bdc2b4cea3d54f24b59f24b59f7565ce23450d8264ad42248d52349%
  d7264ad42148c7173ecb1a42d32048da294bea3d54de2e4de2324fdf304ee1324fe1324fdb2a4cdc2b4cdb2a4ce1314f%
  dd2d4de43551e73a52e93c53e33450f14958ef4457f24a59f34d59f4505af4505af7565cf5535bf6545cf85a5df85a5d%
  fe6862fd6561f85a5dff9576f7585dfd6561ff6f65ff6b63ff9576ff7367ff846eff8c72ff9576ff9f7dffac88ffac88%
  ffac88ffac88ffffffffffffff9f7dffffffffac88ffffffffac88ff9f7dffffffffac88ff9f7dffac88ffac88ffac88%
  ff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffffb605fe23450e53651f04557f04557f6545cfa5e5ffa5e5f%
  fd6561d32148c5163dd7254aee4156f04757ee4256e93c53e73952ec3f55e1324fe2324fe73a52e43551dc2c4de23450%
  d9274bdb2a4ce0304edd2d4ddc2c4cdf2f4eeb3e54f4505af34e5af04757f24b59f34d59fb605ffd6561ff6f65fa5e5f%
  ff6b63f95c5ef7565cfc6260f95c5eff6f65fd6561ff9576ff7367ff7367ff6f65ff7e6cff9576ff9f7dff9f7dff9f7d%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffec4055d42148e33450%
  ed4155f34d59f7585df95c5ef7585df4505ae63852ee4156f24b59f24a59f14858ec3f55ef4356ec4055ee4156e63852%
  e83a53ec4055df2f4ee73952e43651e53651e73a52e83b53e33450ef4457f5535bf5515bf7565cf6545cfa5e5ff95c5e%
  ff6f65fa5e5ff5535bf4505afb605ff7565cfc6260fe6862ff7367fd6561fc6260ff6f65ff7e6cff7367ff8c72ff7e6c%
  ffac88ff8c72ff9f7dffac88ff9f7dff9f7dffac88ff8c72ffac88ffffffffffffffffffff9f7dffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ff846eff7367e93c53e73a52ef4457fd6561f95c5efd6561fb605fff7869e93c53da294be33550ef4457e1314fde2e4d%
  e63852f04757f04757f24a59ef4457e43551ea3d54e63852ec3f55e63852ee4156ea3d54eb3e54f04557ef4356f34e5a%
  f24b59ec3f55f5535bf14958f5535bf7565cf7585df85a5df7565cf7565cf85a5dff6f65f85a5dff6b63ff6b63ff6b63%
  ff846eff6b63fb605fff7869ff9f7dff9576ff846effac88ff8c72ffac88ff9f7dffac88ff9576ffac88ffac88ffac88%
  ffac88ff9f7dffffffffac88ffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffff7585df04557fd6561fd6561ff846eff8c72ff846eff7e6cff9576fa5e5fd11f46%
  d11e46e2324fe83b53dd2d4dd62449e93c53f5535bf7585dec3f55f24a59e83b53e73a52ef4356ee4156e73a52f14958%
  f04757f95c5ef14958f5535bf85a5dfd6561fb605ffe6862fb605ffb605fff7e6cfc6260ff7e6cff7869ff9576ff9576%
  ff9f7dff8c72ffac88ffac88ff8c72ff9f7dffac88ffac88ffac88ffffffffffffffac88ff9f7dffac88ffac88ff9f7d%
  ffffffffac88ffffffffac88ffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffff7e6ce0314fe33450ec3f55ff6b63ff7e6cff846e%
  ff7869fb605fff7367ef4457d9274be73a52ed4155e0314fdf2f4ee63852f04757f24b59f4505af14858ef4356ea3d54%
  ea3d54f14858f34d59ec4055f14858f6545cf7585df95c5ef85a5dfd6561ff9576ff8c72ff846effac88ff846eff9f7d%
  ffac88ffffffffffffff9f7dffffffffffffffac88ffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffdb2a4cc01239%
  cb1a42d9274be73952f14958f14958ec4055e0304ee1324fdc2c4dd52248d8264ad32148cd1b43d01d45d42148d52349%
  dc2c4ddd2d4dd62449d52349d42248dc2c4cdb2b4cdd2d4ddd2d4dea3d54e83a53f6545cf6545cfc6260ff7367ff8c72%
  ff9f7dff7e6cffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffff9f7ded4155d7254ae23350e83b53ee4156f04757f6545cd52248c3143bd11e46d52248d7254aca1941%
  d11e46d01e45d62449da294bda294bdc2c4dda294bdd2d4de2324fe63852e83b53eb3e54f04557f34e5af7585dfb605f%
  ff7367fe6862ff7367ff846eff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffff846ef95c5ef7565cf7585dff7367ff7e6cff7367f5535bdb2a4c%
  e1324fec4055ef4457e83b53e93c53ea3d54ed4155ef4356f24b59f24b59f04757f14858e53751f7565cf7585dfa5e5f%
  ff6f65fa5e5fff7869ff9576ff9576ff7367ffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7565cda2a4cd21f47de2e4de23450%
  e93c53e53751e33550d72549ce1c44d01e46d9274bdf2f4ed42248da294bde2d4dd9284be53751e43551df304edf2f4e%
  db2a4cea3d54f7565cfb605ff85a5dff6f65ff9576ff8c72ffffffffffffffac88ff9576ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576%
  e83b53d42148da294bdc2c4ce23450df2f4ede2e4dd42248d42248cd1b43d52349d62449d7254ad72549dc2c4ce73a52%
  e83a53e23450ec3f55e93c53ec3f55f5535bf5535bfd6561fc6260ff7e6cff846eff8c72ff8c72ff9f7dffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffa5e5fd52349d32047d9284bdc2b4cd8274ad7264ace1c44c6163dc5153dc9183fc8183f%
  ce1c44d11f46d21f47d42148da294bdc2c4dde2e4de2324fe53651f24a59f24a59fc6260fd6561ff6f65ff7367ff846e%
  ffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88e43651c3143bd32047de2d4dd9284bd52248c6163d%
  c01239bf1138c01138be1037c2133bc5163dc91840cc1b42cb1a42d32048cf1d45d62449e23450eb3e54f34e5af95c5e%
  fd6561ff7869ff7e6cffffffff9576ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffd6561c91840bb0e35%
  d21f47d21f47d62449c91840c9183fc91840c6163dc3143bc3143bc7173ec7173ec91840c91840cc1a42cf1d45d22047%
  de2e4de53751ee4256f5515bf95c5eff9f7dffac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffde2e4dbb0e35b2072dc8183fd01d45d52248cd1b43c4143cc3143b%
  bc0f36b90d33bf1138c4143cc3143bce1c44d32047d62449df2f4ee43651ec3f55f6545cff7e6cff7367ff9576ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffad0528c01239c01238c5163dc11239b80c33b3082eb40930b3082fb4092fba0d34bc0f36c1133acb1a41d72549%
  e33450ec4055f24a59f95c5eff6b63ff6b63ff7e6cffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8e0104a4041d9b0313990211980210%
  96020d97020ea1041ba90524b2082ebd1037c6163dd42248e53651f7565cff7e6cff9f7dffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffdc2b4c%
  f04757ea3d54e0314fe0304ee73952dc2c4ce43551e23350ea3d54ef4457fb605fff6b63ff9f7dff9576ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff8b0000f85a5dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff}%
\gprawimage{rgb}{1.302}{2.179}{101}{101}{3.624}{3.624}{\gprawrgbimagedata}{}
\end{scope}
\gpcolor{rgb color={0.000,0.000,0.000}}
\draw[gp path] (1.320,2.197)--(1.356,2.233)--(1.392,2.269)--(1.429,2.306)--(1.465,2.342)%
  --(1.501,2.378)--(1.537,2.414)--(1.574,2.451)--(1.610,2.487)--(1.646,2.523)--(1.682,2.559)%
  --(1.719,2.596)--(1.755,2.632)--(1.791,2.668)--(1.827,2.704)--(1.864,2.741)--(1.900,2.777)%
  --(1.936,2.813)--(1.972,2.849)--(2.009,2.886)--(2.045,2.922)--(2.081,2.958)--(2.117,2.994)%
  --(2.154,3.031)--(2.190,3.067)--(2.226,3.103)--(2.262,3.139)--(2.299,3.176)--(2.335,3.212)%
  --(2.371,3.248)--(2.407,3.284)--(2.444,3.321)--(2.480,3.357)--(2.516,3.393)--(2.552,3.429)%
  --(2.588,3.465)--(2.625,3.502)--(2.661,3.538)--(2.697,3.574)--(2.733,3.610)--(2.770,3.647)%
  --(2.806,3.683)--(2.842,3.719)--(2.878,3.755)--(2.915,3.792)--(2.951,3.828)--(2.987,3.864)%
  --(3.023,3.900)--(3.060,3.937)--(3.096,3.973)--(3.132,4.009)--(3.168,4.045)--(3.205,4.082)%
  --(3.241,4.118)--(3.277,4.154)--(3.313,4.190)--(3.350,4.227)--(3.386,4.263)--(3.422,4.299)%
  --(3.458,4.335)--(3.495,4.372)--(3.531,4.408)--(3.567,4.444)--(3.603,4.480)--(3.640,4.517)%
  --(3.676,4.553)--(3.712,4.589)--(3.748,4.625)--(3.784,4.661)--(3.821,4.698)--(3.857,4.734)%
  --(3.893,4.770)--(3.929,4.806)--(3.966,4.843)--(4.002,4.879)--(4.038,4.915)--(4.074,4.951)%
  --(4.111,4.988)--(4.147,5.024)--(4.183,5.060)--(4.219,5.096)--(4.256,5.133)--(4.292,5.169)%
  --(4.328,5.205)--(4.364,5.241)--(4.401,5.278)--(4.437,5.314)--(4.473,5.350)--(4.509,5.386)%
  --(4.546,5.423)--(4.582,5.459)--(4.618,5.495)--(4.654,5.531)--(4.691,5.568)--(4.727,5.604)%
  --(4.763,5.640)--(4.799,5.676)--(4.836,5.713)--(4.872,5.749)--(4.908,5.785);
\gpcolor{color=gp lt color border}
\draw[gp path] (1.320,2.197)--(1.500,2.197);
\node[gp node right] at (1.136,2.197) {1};
\draw[gp path] (1.320,2.744)--(1.500,2.744);
\node[gp node right] at (1.136,2.744) {10};
\draw[gp path] (1.320,5.481)--(1.500,5.481);
\draw[gp path] (1.320,5.785)--(1.500,5.785);
\node[gp node right] at (1.136,5.785) {1h};
\draw[gp path] (1.320,2.197)--(1.500,2.197);
\draw[gp path] (1.320,2.362)--(1.410,2.362);
\draw[gp path] (1.320,2.580)--(1.410,2.580);
\draw[gp path] (1.320,2.691)--(1.410,2.691);
\draw[gp path] (1.320,2.744)--(1.500,2.744);
\draw[gp path] (1.320,2.909)--(1.410,2.909);
\draw[gp path] (1.320,3.127)--(1.410,3.127);
\draw[gp path] (1.320,3.238)--(1.410,3.238);
\draw[gp path] (1.320,3.292)--(1.500,3.292);
\node[gp node right] at (1.136,3.292) {$10^{2}$};
\draw[gp path] (1.320,3.456)--(1.410,3.456);
\draw[gp path] (1.320,3.674)--(1.410,3.674);
\draw[gp path] (1.320,3.786)--(1.410,3.786);
\draw[gp path] (1.320,3.839)--(1.500,3.839);
\node[gp node right] at (1.136,3.839) {$10^{3}$};
\draw[gp path] (1.320,4.004)--(1.410,4.004);
\draw[gp path] (1.320,4.221)--(1.410,4.221);
\draw[gp path] (1.320,4.333)--(1.410,4.333);
\draw[gp path] (1.320,4.386)--(1.500,4.386);
\node[gp node right] at (1.136,4.386) {$10^{4}$};
\draw[gp path] (1.320,4.551)--(1.410,4.551);
\draw[gp path] (1.320,4.769)--(1.410,4.769);
\draw[gp path] (1.320,4.880)--(1.410,4.880);
\draw[gp path] (1.320,4.933)--(1.500,4.933);
\node[gp node right] at (1.136,4.933) {$10^{5}$};
\draw[gp path] (1.320,5.098)--(1.410,5.098);
\draw[gp path] (1.320,5.316)--(1.410,5.316);
\draw[gp path] (1.320,5.428)--(1.410,5.428);
\draw[gp path] (1.320,5.481)--(1.500,5.481);
\draw[gp path] (1.320,5.645)--(1.410,5.645);
\draw[gp path] (1.320,2.197)--(1.320,2.377);
\node[gp node center] at (1.320,1.889) {1};
\draw[gp path] (1.867,2.197)--(1.867,2.377);
\node[gp node center] at (1.867,1.889) {10};
\draw[gp path] (4.604,2.197)--(4.604,2.377);
\draw[gp path] (4.908,2.197)--(4.908,2.377);
\node[gp node center] at (4.908,1.889) {1h};
\draw[gp path] (1.320,2.197)--(1.320,2.377);
\draw[gp path] (1.485,2.197)--(1.485,2.287);
\draw[gp path] (1.703,2.197)--(1.703,2.287);
\draw[gp path] (1.814,2.197)--(1.814,2.287);
\draw[gp path] (1.867,2.197)--(1.867,2.377);
\draw[gp path] (2.032,2.197)--(2.032,2.287);
\draw[gp path] (2.250,2.197)--(2.250,2.287);
\draw[gp path] (2.361,2.197)--(2.361,2.287);
\draw[gp path] (2.415,2.197)--(2.415,2.377);
\node[gp node center] at (2.415,1.889) {$10^{2}$};
\draw[gp path] (2.579,2.197)--(2.579,2.287);
\draw[gp path] (2.797,2.197)--(2.797,2.287);
\draw[gp path] (2.909,2.197)--(2.909,2.287);
\draw[gp path] (2.962,2.197)--(2.962,2.377);
\node[gp node center] at (2.962,1.889) {$10^{3}$};
\draw[gp path] (3.127,2.197)--(3.127,2.287);
\draw[gp path] (3.344,2.197)--(3.344,2.287);
\draw[gp path] (3.456,2.197)--(3.456,2.287);
\draw[gp path] (3.509,2.197)--(3.509,2.377);
\node[gp node center] at (3.509,1.889) {$10^{4}$};
\draw[gp path] (3.674,2.197)--(3.674,2.287);
\draw[gp path] (3.892,2.197)--(3.892,2.287);
\draw[gp path] (4.003,2.197)--(4.003,2.287);
\draw[gp path] (4.056,2.197)--(4.056,2.377);
\node[gp node center] at (4.056,1.889) {$10^{5}$};
\draw[gp path] (4.221,2.197)--(4.221,2.287);
\draw[gp path] (4.439,2.197)--(4.439,2.287);
\draw[gp path] (4.551,2.197)--(4.551,2.287);
\draw[gp path] (4.604,2.197)--(4.604,2.377);
\draw[gp path] (4.768,2.197)--(4.768,2.287);
\draw[gp path] (1.320,5.785)--(1.320,2.197)--(4.908,2.197);
\node[gp node center] at (3.114,5.426) {33\% Labelled};
%% coordinates of the plot area
\gpdefrectangularnode{gp plot 1}{\pgfpoint{1.320cm}{2.197cm}}{\pgfpoint{4.908cm}{5.785cm}}
\draw[gp path] (6.780,5.785)--(6.780,2.197)--(10.368,2.197);
\node[gp node center,rotate=-270] at (5.706,3.991) {Association Runtime (ms)};
\node[gp node center] at (8.574,1.427) {MAC Both Runtime (ms)};
\begin{scope}
\clip (6.780,5.785) rectangle (10.368,2.197);
\def\gprawrgbimagedata{%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576ff9f7dff9f7dffffffffac88ff9f7d%
  ffffffff9f7dffac88ffffffff8c72ff8c72ffac88ffac88ffac88ff9f7dff846eff846efd6561fa5e5ffe6862ff7e6c%
  fe6862f85a5df7585df4505aef4457f04557e73952df2f4ee2324fd9284bd62449d42148d21f47d21f47cf1d44cd1b43%
  cc1b43d11e46d21f47cc1b43c7173ed01e46ca1940cd1c43cf1d45ce1c44d52349d42248dc2c4cda2a4cde2d4dd22047%
  d42248d8264ad7254ad7264aa00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffac88ff9f7dffffffff9f7dffffffffac88ff9f7dff9f7dffac88ffac88ffac88ff8c72ff6f65ff9f7dffac88ffac88%
  ff9f7dff8c72ff9f7dff7e6cff9576ff9576ffffffff9f7dff9f7dffffffffac88ffac88ffac88ffffffff9f7dff9f7d%
  ff9f7dffac88ffac88ff9f7dffac88ffffffffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
  ffffffffffffff9576ffffffff9576ffffffffac88ffffffffffffff9576ffac88ffac88ff9576ff846eff9576ff9f7d%
  ffac88ff8c72ffffffffac88ff9576ff9576ff846eff846eff846eff7869ff7e6cff7869ff7e6cff846eff9576ff9f7d%
  ffac88ff846effffffff9f7dff9576ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
  ffffffffffffffffffffffffffffffffffffffac88ff8c72ffffffff9f7dff9f7dffffffff9f7dffac88ffffffff9576%
  ff9576ffffffffac88ffffffff9f7dffac88ff9576ff7869ff9576ff9576ff846eff8c72ff6f65ff7367fd6561ff7e6c%
  fd6561ff8c72ff846eff7869ff9f7dff846eff9f7dff9576ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%
  ffffffffffffffffffe83b53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffac88ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88%
  ffac88ffffffffac88ffffffff846eff9f7dffffffffac88ff9576ffac88ff9f7dff8c72ff9576ff7e6cff7367f95c5e%
  fb605ffa5e5ffb605fff7367ff7367fc6260ff7869ff7367ff7869ff7e6cff7367ff9576ff9f7dff9f7dffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffe73952ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff846eff9f7dff7e6cffffffff9f7dffffffffffffffac88ffffffffac88%
  ff9576ffffffffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff9f7dffac88ff8c72ff7869ff8c72ff7e6c%
  ff7869fd6561f95c5ef95c5ef7565cf7585df5515bf14958fa5e5ff85a5dfb605fff6f65ff7367ff6b63f95c5efb605f%
  ff8c72ff8c72ffac88ffffffffac88ffffffff9f7dffffffffffffffffffffffffffac88fffffff04557ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9576ffac88ffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffff9576ff9f7dff7e6cff8c72%
  ffac88ff7e6cff6f65ff6f65ff7869ff7367f6545cfa5e5ff7585df5535bf24b59f85a5df5535bfc6260ff7e6cfc6260%
  f85a5df95c5ef6545cff6f65ff6f65ff9f7dff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffb605fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7d%
  ff9f7dff9576ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ff9576ffac88ffffffff9576ffffffff8c72%
  ff9f7dff9576ff846effac88ff8c72ff846eff7367f7585dff6b63f7585df85a5df24a59fb605fff6b63f6545cf24b59%
  f5535bf85a5df85a5df5535bf7585dff6b63f7565cff7367ff7e6cff9f7dff9576ffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffff8c72ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ff8c72ff9576ff9f7dffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88%
  ff9f7dffac88ffac88ffffffff9576ff8c72ff8c72ff9f7dff7e6cff7e6cf95c5eff7869ff6b63f7565cf5515bfe6862%
  fc6260f5515bf7585df95c5ef7565cfa5e5ff85a5dfd6561f5515bf7585df7565cfd6561ff7e6cff8c72ff9f7dffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffff8c72ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff8c72ff9f7dff9576ff9f7dffac88ffac88ffffff%
  ff9f7dffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dff9f7dffac88ff9f7dff9f7dff7367ff7367fd6561f7565c%
  fe6862f85a5df5515bf7565cf85a5df14958f5535bf85a5dfa5e5fff846eff6b63ff7e6cf24b59fa5e5ff85a5dfd6561%
  ff9576ff9576ff8c72ff9576ff9f7dffac88ffffffff9f7dffac88ffac88ffffffffffffffac88ffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff9576%
  ffac88ff9576ffac88ffffffffffffff9576ff9f7dffac88ff9f7dff9f7dff8c72ff8c72ff8c72ff9576ff8c72ff7869%
  fe6862ff6f65fc6260fa5e5ff7565cf6545cfb605ff5535bf14958ff7e6cfc6260fd6561ff6f65fc6260fe6862ff7869%
  fe6862f7585dfc6260ff6b63ff846eff9576ff9f7dffac88ffac88ffffffffac88ff9f7dffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88%
  ffac88ff8c72ffac88ffac88ffffffffffffffac88ffffffff9f7dffac88ff9576ffffffff9f7dff9f7dff9f7dffffff%
  ffffffff8c72ff7367ff7367ff8c72ff6f65f34e5af4505af34e5af85a5df6545cfb605ffa5e5ffc6260fb605fff846e%
  ff6f65ff7e6cff8c72ff7e6cff7367fb605ffc6260ff6f65ff6b63ff9576ff9576ffac88ffffffffac88ffac88ffffff%
  ffac88ffac88ffac88ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffac88ffac88ff9f7dffffffffffffff9f7dffffffffac88ffffffffffffff8c72ff9f7d%
  ff9f7dff9576ff9576ff9f7dffac88ff846eff7e6cff8c72ff6f65fc6260f7585df7565cf85a5df4505af7565cf6545c%
  f95c5eff7869ff7869fe6862ff846eff7367ff7869ff7367ff7367ff7869ff7e6cff6f65ff7869ff9f7dff8c72ffffff%
  ffac88ffffffff9f7dffffffffffffffffffffffffffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ff9f7dffac88ffac88ff9f7dff9576ffac88ff9f7dff9576ff9f7dff9576ff9f7dff7367ff9576ff6f65f7565cf7585d%
  f85a5df6545cf7585df85a5dff7367fc6260fb605ffe6862ff6f65ff9576ff8c72fc6260ff7367ff7e6cff846eff846e%
  ff7e6cff9576ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ff8c72ffffffffac88ffffffffac88ffac88ffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffff%
  ffffffff9f7dffac88ffac88ff9576ffac88ffffffffffffff9576ff9576ff9f7dffac88ff846eff846eff9576ff9576%
  ff7e6cff6b63fd6561f7585df85a5dfb605ff04757f4505afd6561fc6260ff6f65ff7869ff8c72ff7869ff8c72ff6f65%
  ff8c72fe6862ff9f7dff9576ff9576ffffffff9f7dffffffff9576ffac88ff8c72ff9576ffac88ffac88ffac88ff846e%
  ff9f7dff9576ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffff9f7dff9576ffffffffac88ff9f7dffac88ffac88ffffffff9f7dffac88ff9576ffac88ff9f7dff9576%
  ffac88ffffffff9f7dff7869ff9576ff7e6cff6f65f85a5dfc6260f34e5af95c5efe6862fc6260ff6f65ff7869ff846e%
  ff6f65ff6f65ff7e6cff7e6cff7869ff6b63ff7869ff7367ff9576ff8c72ffac88ffac88ffffffff846eff7e6cff7869%
  ff846effac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffac88ff9576ffac88ffac88ffffffff9f7dffac88ff9f7dffffffffac88ffac88ffac88%
  ffffffff846effac88ffac88ff9f7dff9576ff8c72ff8c72ff7367fd6561ff846eff6f65fa5e5ffe6862fb605ff7565c%
  fb605fff6f65ff846eff8c72ff6b63f95c5efc6260ff7e6cff7367ff7e6cff7e6cff846eff9576ffac88ff9576ff9f7d%
  ff9f7dff9f7dff9f7dff7367ff6f65ff846eff9576ff9576ffffffff9576ffffffffffffffffffffac88ffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576%
  ff9f7dffac88ffac88ff9576ff9f7dffac88ffac88ff8c72ff9576ff9576ffac88ff846eff9f7dff846eff7e6cff7869%
  ff6b63fc6260f85a5dfb605ffd6561ff7e6cff7e6cff7869ff9f7dff6b63ff7869ff7e6cff9576ff8c72ff7367ff7367%
  ff9576ffac88ffffffff9f7dffac88ffac88ff846eff7e6cff7869ff7869ff9f7dff9576ff9f7dffac88ff9576ffac88%
  ff9f7dffac88ff846effffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
  ffffffffffffffac88ffffffffffffff9576ffac88ff9576ffac88ff8c72ff9576ff9576ff7e6cff7e6cff846eff7e6c%
  ff9f7dff9576ff6f65fd6561ff7869ff846ef95c5eff8c72ff7869ff9576ff7e6cff6f65ff7869ff9576ff7367ff9f7d%
  ff846eff9f7dff7e6cff8c72ff9576ff9576ffffffff9f7dff9576ffffffffac88ff9576ff7869ff846eff7869ffffff%
  ff7e6cffffffff9f7dff9576ff9f7dff7e6cf85a5df85a5dff9f7dffffffffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ff9f7dffac88ff9576ffac88ffffffffffffffac88ffffffffac88ffac88ffac88ffac88ff7e6cff846eff9576ffffff%
  ffac88ff9f7dff8c72ff9f7dff846eff7869ff8c72ff7367fd6561ff9576ff7e6cff6b63ff7367ff6b63ff8c72ff7869%
  ff7e6cff8c72ff9576ff846eff7869ff7869ff9576ff9576ff9576ff9576ffac88ffac88ffffffff9f7dffffffff9f7d%
  ff9f7dff6f65ff7e6cff9f7dffffffffffffffac88ff9f7dff7e6cff9576fd6561f6545cff6b63ffac88ffac88ffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ff9f7dffffffffffffffffffffac88ffffffff9f7dff9f7dffffffffffffffac88ffffffffffffff9576%
  ffac88ff9f7dff7e6cff9f7dff9f7dff9576ff7e6cff9f7dffac88ff8c72ff8c72ff9f7dff7367ff7e6cff6b63ff846e%
  ff7367fd6561ff6f65ff6f65ff7e6cff9576ff8c72ff8c72ff846eff9576ff9f7dffac88ff9f7dffac88ffffffffffff%
  ff9576ff846eff7e6cff9576ffac88ff8c72ffffffffac88ff9f7dffac88ffac88ff7e6cfc6260fd6561ff7367f95c5e%
  f6545cff9576ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ffac88ff9576ffffff%
  ff8c72ff9f7dffac88ffffffff9f7dff9576ff9576ffac88ff846eff7367ff846eff7869ff7e6cff9576ff9576ff7e6c%
  ff8c72ff6b63ff7e6cff6f65ff7869ff7e6cff7367ff7367ff8c72ff8c72ff9576ff8c72ff9f7dffac88ff8c72ffffff%
  ffffffff9f7dff9f7dff9f7dff9f7dffffffff8c72ff8c72ff846eff9f7dff9f7dffac88ffac88ff8c72ffffffff9576%
  ff6f65fc6260fd6561ff6f65fd6561ff8c72ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88%
  ffffffffffffff9f7dffffffffac88ffffffff9f7dff9576ff8c72ff9f7dff7e6cff9576ff846eff9f7dff7869ff8c72%
  ff9576ff846effac88ff9f7dff9f7dff9f7dff846eff846eff9576ff846eff9576ff9576ff9576ff7e6cff9f7dff9f7d%
  ff8c72ff8c72ffac88ffac88ff9f7dffffffffac88ff9576ffffffff9576ff9f7dff7e6cff846eff846effac88ff9f7d%
  ffffffffac88ffffffffac88ff9576ff6f65fd6561ff6b63ff7869ff7e6cffffffffffffffffffffffffffffffffac88%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ff9576ffffffff9f7dff9576ff9f7dffffffffffffff9576ffac88ffac88ffac88ff9f7d%
  ff9576ff846eff846eff6f65ff7e6cff6b63ffac88ff7e6cff8c72ff846effffffff7869ff8c72ff9f7dff8c72ff9f7d%
  ffac88ff7367ffac88ff9576ff846effac88ff9576ffac88ffac88ff9f7dffffffffffffffffffffac88ffffffffac88%
  ff846eff9f7dffffffff9f7dff9f7dffac88ffac88ffffffffac88ff8c72ff9576ff846eff7e6cffac88ffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dff9f7dff8c72ffffffff9576ff9576%
  ffac88ff9576ffffffffac88ff9576ff9f7dff9f7dff6b63ff8c72ff7869ff9576ff846eff7869ff9f7dff9f7dff846e%
  ff9576ff846eff8c72ff846eff9576ff9576ffac88ff8c72ffac88ff9576ff9f7dffac88ffac88ffffffffac88ffac88%
  ffffffffffffffac88ffac88ff9f7dffac88ff7e6cff9576ffac88ffac88ffac88ff9f7dffffffffffffffffffff9f7d%
  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88%
  ffac88ff9f7dff9f7dff9576ff9576ff9576ff9f7dffffffff9f7dff8c72ff8c72ff9f7dff9576ff8c72ff7367ffac88%
  ff9576ff9f7dff9f7dffffffff8c72ff7e6cff8c72ff9576ff8c72ff9576ff9576ff9576ffac88ffac88ffffffffffff%
  ff8c72ff9f7dff9576ffffffffffffff9f7dffffffff7e6cff9f7dff7e6cff9f7dffffffffac88ffffffff9f7dff9576%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffac88ffffffffffffff9f7dffffffff9f7dffffffffffffffac88ffffffff9576ffac88ffac88ff9f7d%
  ff9576ff9576ff9f7dff9f7dffac88ffac88ff9f7dffffffff8c72ffac88ff9f7dff7367ff9576ff8c72ff9576ff846e%
  ff7e6cff7e6cff9576ff9576ff9576ff8c72ffac88ffffffffffffffac88ff8c72ff9f7dffac88ff9576ff9576ffac88%
  ff9f7dffac88ffffffff9f7dffffffffffffffac88ff9576ffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffff9576ff8c72ff9576ffac88ff9f7dff8c72%
  ff9576ff8c72ff8c72ff9576ff9f7dffac88ffac88ff9576ff7e6cffffffff8c72ff9576ff9f7dffac88ff846eff9576%
  ff7e6cff9576ffac88ff7869ff8c72ff7367ff7e6cff7869ff6f65ff9576ff8c72ffffffffffffffac88ff9576ffac88%
  ffac88ffac88ff9576ffac88ffffffff9f7dff9576ffffffffac88ffffffffac88ffffffffac88ffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ff9f7d%
  ff8c72ff7e6cff9576ffac88ff9f7dff9576ff9576ff9576ff9f7dff9f7dff9576ffffffffac88ff9f7dffac88ff9f7d%
  ffac88ff8c72ff9f7dffffffff9f7dff8c72ff7e6cff6b63ff846efc6260fc6260fb605ff95c5efd6561ff8c72ff9f7d%
  ff9f7dff8c72ff9f7dffffffffffffff9576ff9f7dffffffff9f7dffac88ffac88ff9576ff8c72ffffffff9f7dff9f7d%
  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffff9576ff9576ff8c72ff7e6cffac88ff8c72ff9576ff846eff7e6cff9576ff846eff9f7dff9f7d%
  ffffffff9f7dffffffff9f7dff8c72ff9f7dff9576ff8c72ff8c72ff846efb605ff95c5ef7585df85a5df5515bf85a5d%
  fb605ff6545cfe6862ff846eff9f7dffac88ff9f7dffffffff9f7dff9576ff9f7dff9f7dff8c72ffffffffac88ffac88%
  ff9f7dff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffac88ffffffffac88ff9f7dff7367ff7367ff8c72ff846effffffffac88ff9576%
  ff7e6cff9576ff9f7dffffffffffffff7869ffac88ff9f7dff9f7dff846eff7367ff846eff7e6cfd6561f7585df95c5e%
  fa5e5ff5535bf04557f34d59f14958f24b59f5515bff6b63ff7e6cff9f7dffffffffffffff9f7dffffffff9576ff8c72%
  ffac88ff846eff9f7dffffffffac88ff9576ffac88ffffffffffffffac88ffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ff9f7dff7869%
  ff9f7dffac88ffac88ff846eff9576ff9f7dffac88ff8c72ff9576ffac88ff8c72ff7e6cff846eff7367ff7e6cff7367%
  ff7367ff6b63fa5e5ff7565cf95c5efa5e5ff34e5af4505af95c5ef24a59f5515bf4505afc6260ff8c72ffac88ff9576%
  ff9576ffac88ffffffffac88ff9f7dff846eff9576ff9576ffffffffac88ff9f7dffac88ffffffffffffffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffac88ff9576ffac88ffac88ffffffffac88ff9f7dff8c72ff9576ff9f7dff9f7dff9576ff8c72ff7e6c%
  ff846eff6f65ff6b63ff7367ff6b63fe6862fc6260f85a5df85a5df6545cf4505af4505af7585df5535bf4505af4505a%
  fc6260ff7e6cffac88ff9576ff9f7dffffffffffffff9f7dffac88ff8c72ff8c72ff9f7dff9f7dff9f7dff9f7dff9f7d%
  ff9f7dffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffff9f7dffffffffac88ffac88ffffffffffffff9f7dffffffffffffffffffff9f7dff9576ff8c72%
  ff9f7dff9f7dff9576ff846eff8c72ff6b63f85a5df95c5ef7585dff6b63fa5e5ffd6561fb605ff6545cf6545cf34e5a%
  f7565cf4505af5515bfb605ff4505afb605fff7869ff8c72ff9f7dffac88ffffffffac88ffac88ffac88ff9f7dff9f7d%
  ff9f7dffffffff9f7dffffffffffffff9576ffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffffffffac88ffffff%
  ff9f7dffac88ffac88ffac88ff9f7dff9576ff846eff6f65fe6862ff7367fb605ff7585df95c5efc6260f6545cfe6862%
  f6545cf95c5efc6260f95c5efb605ff5515bf7585dff6f65ff7367ff8c72ff7e6cff9f7dff9576ff9f7dff9f7dff8c72%
  ff9f7dff9f7dffffffff9f7dffffffffac88ff9f7dffac88ffffffff9f7dffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7d%
  ffffffffac88ff9f7dff9f7dffffffffac88ffffffffac88ff846eff9f7dff8c72ff7e6cfe6862f95c5ef7565cf14958%
  f4505afd6561fa5e5ff7585dfe6862ff7367ff6f65f7585dfb605fff6b63f7565cff6b63fa5e5ffa5e5ffc6260ff846e%
  ffac88ffffffffffffff8c72ff9576ffac88ffffffffac88ffffffffffffff9576ffffffffffffffffffff9f7dff9f7d%
  ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ff9f7dff9576ff846eff9576ff846e%
  f85a5dff6b63f7565cf95c5ef4505af6545cf5535bff6b63fe6862ff6b63ff7e6cfe6862ff6b63ff6b63fe6862fb605f%
  f95c5eff6b63fe6862ff7e6cff846effffffffffffff9f7dffffffff7e6cffffffffffffff9576ff846effac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7dffac88ffffffffac88ff8c72ff9f7d%
  ff9f7dff9f7dff9f7dff7e6cfe6862fd6561f7565cf85a5df34d59f14958f95c5efa5e5ffe6862fd6561ff7367ff7e6c%
  ff7e6cff7e6cfb605ffd6561f6545cf85a5dff6f65ff6f65ff7e6cff9f7dff9576ffac88ff9f7dffac88ff8c72ffac88%
  ff7e6cff6b63ff6f65ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffffffff9f7dff9f7d%
  ffac88ffffffff9576ff9576ff9576ff9f7dff7869ff7e6cff7e6cfb605ff85a5dfa5e5ff7565cf5515bf95c5efc6260%
  ff6b63fe6862ff7e6cff7e6cff846eff9576fd6561ff6b63f95c5eff6b63ff6f65ffac88ff846eff8c72ff846eff7869%
  ff9576ff9576ff8c72ff9f7dff7367f7585ded4155f95c5eff9576ff9f7dff9f7dffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
  ffffffffffffffac88ffac88ffac88ffffffff9576ffac88ff9576ffac88ff8c72ffac88ff846eff6f65ff7e6cfe6862%
  fe6862fe6862ff7367fb605fff7869ff846eff9576ff846eff9576ff846eff7869ff6b63ff7869ff7367ff8c72ff9576%
  ff8c72ff6f65ff7869ff7e6cfd6561ff7e6cff846eff846eff8c72fa5e5fed4155eb3e54ff7367ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffffffff9576ffac88ff9f7dffac88ffac88ff9f7dff9f7dffac88ff9f7dff9f7dff7869%
  ff7e6cff7e6cff7367ff7869fc6260fb605fff7367ff9576ff7869ffac88ff9576ff8c72ff8c72ff8c72ff846eff8c72%
  ff6f65ff7869ff9576ff846effac88ff9576ff846eff6b63fa5e5fff7869ff8c72ff9f7dff7e6cff7e6cf7585df7585d%
  ff7869ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9576ffac88ffffffffac88%
  ff9f7dffac88ff9576ff6f65ff7367ff7367fe6862ff846eff8c72ff7869ff6f65ff7869ff9f7dff8c72ff846effac88%
  ff8c72ff8c72ffac88ffffffff8c72ff9f7dff9576ff9f7dff7e6cff9576ff9f7dff7e6cfe6862fd6561ff7869ff6b63%
  ff9576ff9576ff846eff8c72ff7e6cff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffffffffffac88ff9576%
  ffffffff9576ffffffffffffff8c72ffffffff9576ff9576ff7e6cff6f65ff6b63ff6f65ff9576ff7e6cff7e6cff9576%
  ff846eff7e6cff7869ff6f65ff846eff7e6cff8c72ff9f7dffac88ff9f7dff846eff7869ff9576ff8c72ff846eff9f7d%
  ff7367ff6f65ff8c72ff846effac88ff9576ff9f7dff9576ff9f7dffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ff9f7dffffffffffffffac88ffffffffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9576ff9576ff7869ff7367%
  ff9576ff7367ff9576ff9f7dff846eff8c72ff9f7dff6f65ff6b63ff7367ff8c72ff9f7dff846eff9576ffac88ffac88%
  ff9576ffffffff9f7dff8c72ff9f7dff9f7dff7e6cff9f7dff846eff9576ff9f7dffac88ff9f7dffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffff9f7dff846effac88ffac88ffffffff9f7dff9f7dffac88ff9f7dffffff%
  ffffffffac88ff7869ffac88ff8c72ff8c72ff7869ffac88ff8c72ff9f7dff846eff7367ff9f7dff846eff8c72ffac88%
  ff9576ff9576ff846eff9f7dffac88ff9576ff9576ff9576ff7869ff7869ffac88ffac88ff9576ffac88ff9f7dff9576%
  ff9f7dff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ff9576ff6b63%
  ffac88ff7e6cffffffff9f7dff7869ffac88ff9f7dff9576ff9576ff9576ffac88ff8c72ff7e6cff9f7dff8c72ff846e%
  ff9576ff9576ff9576ffac88ffffffff9f7dff9f7dff9f7dffffffff9f7dff9576ff7e6cff846eff846eff7e6cffffff%
  ff9576ffac88ff9f7dff9576ff9f7dffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffff9f7d%
  ffffffff9f7dff8c72ff7e6cff9576fe6862ff9576ffffffff9f7dff9576ff9f7dff9576ffac88ffac88ff846effac88%
  ff9576ffac88ffac88ffac88ff8c72ff8c72ff9f7dff9576ff9f7dffffffff9f7dff9576ffffffff8c72ff9576ffac88%
  ff9f7dff7869ff7367ff9576ff7e6cff9f7dff9576ff9f7dffac88ffac88ffffffffffffffac88ffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ff9f7dffffffffac88ff9576ff9576ff8c72fc6260ff7367ff6b63ffac88ffac88ffac88ffac88ff9f7d%
  ff9f7dffac88ffffffff846effffffff9f7dff7e6cff9576ff9576ffac88ff9f7dffffffffac88ff9f7dffffffff9f7d%
  ffffffff9f7dffffffff846eff9f7dff8c72ff7869ffac88ff7367ff9576ff9576ff9576ff9576ffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffff9f7dffffffff9f7dffffffff9576ffac88ff9f7dffac88ff846eff7e6cff7869%
  ffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dffac88ffac88ffac88ff846effac88ffffffff9f7dffac88ffffff%
  ffffffffac88ff9f7dffac88ffac88ff9f7dffac88ff8c72ffffffffffffff846eff9f7dff7367ffffffff846effffff%
  ffac88ff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff8c72ff9f7dffac88ff846effac88%
  ff9576ff9576ff846eff6f65ff9f7dff8c72ffac88ff9576ff9f7dffffffffffffff9f7dffac88ffffffffffffff9576%
  ff846eff9f7dffac88ffac88ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ffac88ff9576ffac88ff9576ff9f7d%
  ff846effffffff9f7dff9576ff9576ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
  ff9f7dffac88ffffffff9576ff9576ff9f7dff9576ff9f7dff846eff9f7dffffffff9f7dffac88ffffffff9576ffffff%
  ffac88ff9f7dff9f7dff9576ffac88ffffffffffffff9576ffffffffac88ff9576ffffffff8c72ffac88ffffffffffff%
  ffffffff9576ff9576ffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffff9f7dffffffffffffffffffffffffff8c72ff846effac88ff8c72ff9f7dff9f7dff9576ffffff%
  ffac88ffac88ffac88ff9576ff9f7dff9576ffac88ff9f7dffac88ff9f7dff9f7dff8c72ffac88ff9576ffac88ff9576%
  ff8c72ff846eff9f7dff7367ff9f7dffffffff9f7dff7e6cffac88ffffffffac88ff9f7dffffffff9f7dffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dff9576%
  ffac88ff9576ff9f7dffac88ff9f7dffffffff9f7dffac88ffac88ff8c72ffac88ff9576ff9f7dff9576ff7869ff8c72%
  ff9f7dff846eff9576ff9576ff846eff8c72ff8c72ff8c72ff9f7dff846eff8c72ff9576ffffffff846effffffffffff%
  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffffac88%
  ffac88ff9f7dff9f7dffac88ffac88ffac88ffffffffac88ff9576ff9576ff9f7dff9f7dff9f7dff9576ff9576ff846e%
  ff7e6cff7e6cff7e6cff7e6cff7e6cff7367ff7367ff9576ff9576ffac88ff846eff7869ff7869ff6f65ff9576ff7e6c%
  ff9576ff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9576ffffffffac88ffffffffac88ffffffff8c72ffac88ff8c72ff9576ff9576ff9f7dff8c72%
  ff846eff7e6cff7e6cff6f65fd6561ff6b63fb605ffd6561fa5e5fff7367fd6561fc6260ff8c72ff6b63ffac88ff846e%
  ff7869ff7869ff7367ff9576ff9576ff9f7dffffffff9576ffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffff9f7d%
  ff8c72ff8c72ff9576ff9f7dff846eff7367ff7869ff7e6cfb605ff7585df24b59f24a59f34d59f34e5afb605ffc6260%
  fd6561ff8c72ff7e6cff7e6cffac88ffac88ff7e6cff7367ffac88ff9f7dffac88ffac88ffac88ffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ff9576ffac88ff9576ff9576ff9576ff6f65ff846efc6260fc6260fa5e5ffc6260f85a5df5535bef4356%
  f4505af34e5aef4457f85a5df4505aff6b63ff846eff7e6cff7e6cff9f7dff8c72ff9f7dffffffff9576ff9f7dffffff%
  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff6b63ff7869ff8c72ff7367fd6561f95c5ef34d59%
  f5515bf14958f04757f04557f6545cf04757f34e5af5515bff6b63fc6260fb605fff8c72ff7367ff9576ff9f7dffac88%
  ffac88ff9f7dff7869ff846eff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff9576ffffffff9576ff9f7dff8c72ff8c72ff8c72%
  ff7869f85a5df5515bf24b59f6545cf24b59f5515bee4256f14958f85a5df5535bf95c5eff7367fb605fff7869ff6f65%
  ff7367ff9576ff8c72ff8c72ff9576ff9f7dff7e6cff9f7dff846effac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
  ff8c72ff9f7dff7869ff7e6cfb605ff7585df7585df4505af5515bfa5e5ff24b59f95c5ef34e5af85a5df85a5dff6f65%
  fc6260ff7869ff7367ff8c72ff846eff6b63ff7e6cff6f65ff6f65ff7e6cff6f65ff6f65ff846eff9f7dffac88ffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffff9f7dff9576ff8c72ff846eff8c72ff6f65fc6260fc6260f4505af34e5aec3f55f14958f95c5ef7565cf85a5d%
  fc6260fa5e5ffe6862fd6561fe6862ff8c72ff6f65ff7e6cff6f65fb605fff7367fe6862fa5e5ff5535bf85a5dff7367%
  ff8c72ff7869ff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
  ffffffffac88ffffffffac88ffffffff8c72ff9576ff9576ff9f7dff7367ff7869fd6561fc6260f24b59f34e5af14958%
  f24a59f85a5dfa5e5ffc6260ff6b63ff6f65ff6f65ff7869ff8c72ff7869ff846eff7e6cff846eff7e6cff7e6cfc6260%
  f85a5dfa5e5ffd6561fb605fff7e6cff8c72ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffff9f7dffac88ffffffff9f7dff9f7dff8c72ff846eff6f65ff6b63fa5e5ffe6862%
  f5515bf34d59f5535bf85a5df7585df7585dfc6260f7585dfc6260fe6862ff7869ff8c72ff8c72ff7e6cff6f65fc6260%
  fc6260ff9576fe6862ff7367ff6b63ff6f65f85a5dfd6561fd6561ff7367ffac88ffac88ffac88ffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffff846effac88ff7869%
  ff7e6cfe6862ff9576f95c5efc6260f24b59f34d59f7565cf34e5afa5e5ffa5e5fff7869ff7869ff7e6cffac88ff846e%
  ff7367ffac88ff7367ff846eff9576ff7367ff6b63ff7e6cff9f7dff7869ff6f65ff7367ffac88ff8c72ff9f7dffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffac88%
  ff9576ffac88ff8c72ff8c72fd6561ff7869ff6b63ff6b63ff7869fa5e5ffb605ffc6260f85a5dfc6260ff6b63ff7367%
  ff7869ff7869ff6b63ff9576ff7367ff6b63f95c5eff6f65ff7869f95c5eff6f65ff846eff7869fd6561ff9576ff7869%
  ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffff9f7dff8c72ff9f7dff9576ff9576ff8c72ff846efe6862ff7e6cff7367fa5e5ffa5e5ffd6561fa5e5f%
  ff7367f85a5dff7367ff6b63fc6260ff7869ff7e6cff7367ff846eff6f65ff7869ff7e6cf95c5eff7e6cff7367ff846e%
  ff8c72ff7869ff8c72ff8c72ff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffffffff9f7dff9576ffac88ff846eff7e6cff846eff7e6cff9f7dff8c72ff846e%
  fe6862ff7e6cfd6561ff7e6cfc6260fa5e5fff7869ff7869ff7367ff7e6cff8c72ff7367fe6862ff7367fe6862ff8c72%
  f95c5efb605fff6b63ff7869ff7869ff7869ff846eff9576ffac88ffffffff8c72ffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff846effac88ff8c72ff846eff846eff8c72%
  ff846eff8c72fd6561ff8c72ff846eff7367ff8c72ff6b63ff6f65ff7e6cff7e6cff8c72ff6b63ff9576ff8c72ff846e%
  ff6f65ff7367ff846eff7367ff7367f85a5dff6f65fd6561ff7367ff6f65ff9f7dff9576ffac88ffac88ffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9f7d%
  ff846eff9f7dff8c72ff9576ff7869fd6561ff7367ff8c72ff8c72ff8c72ff9576ff846eff7e6cff7367ffac88ffac88%
  ff9576ff7367ff8c72ff846efd6561ff6b63ff6f65ff7367ff7e6cff8c72ff9576ff7869ff9576ff8c72ffac88ff9f7d%
  ffac88ff8c72ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ff9f7dff9f7dffac88ff9576ff8c72ff8c72ff846eff6b63ff846eff9576ff846eff8c72%
  ff9f7dff8c72ff846eff9576ff7e6cff6f65ff9576ff7e6cff6f65fc6260f85a5dfe6862ff7869ff7869ff9576ff846e%
  ff7e6cff846eff9f7dff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9576ff9f7dff7e6cff846eff7869ff7869ff7367%
  fb605fff6f65ff7367ff846eff9576ff8c72ffac88ffffffff8c72ff9576ff846eff8c72fc6260ff846eff6f65fe6862%
  ff7367ff9576ff7869ff9f7dff9f7dffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffac88ffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ff9576ffac88ff9f7dff9f7dfe6862f7585df6545cff7e6cff8c72ff9f7dff9576ffffffff9576ff9576ffffffff9f7d%
  ff7e6cff9576ff7869ff846eff9576ff9f7dff7869ff9f7dffffffffac88ff9f7dffffffffac88ffac88ffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ff9f7dffac88ffffffffac88ffffffff8c72ff8c72ff8c72ff8c72ff9576ff846eff7869ff7e6cffffffffffffff9576%
  ffac88ffac88ffffffff8c72ff8c72ffac88ff9f7dffffffff8c72ff9576ffac88ff9f7dff9576ff9f7dffac88ffac88%
  ffac88ffac88ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff8c72ff9f7dff9f7dff7367ff8c72ff846eff9576%
  ff9576ff9f7dff9f7dff9f7dff9f7dffffffffffffffffffff9576ffffffffac88ff9f7dff9f7dff7e6cffffffff9576%
  ff9576ffac88ffac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ff9576ff8c72ff7869ff7367ff8c72f7585dff7367ff9576ff8c72ff9576ffac88ffac88ffffffffac88ffffffffac88%
  ffac88ffac88ff9576ffffffff9576ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffac88ff9f7dff846eff7367f85a5df6545cfe6862ff8c72ffac88ffac88ffffff%
  ffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffac88ff9f7dff8c72ff9f7dff9576%
  ff7e6cff7869ff846eff8c72ff9f7dffac88ff9576ffac88ffac88ffac88ffac88ffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9576%
  ff7367ff7e6cfe6862fc6260ff6f65ff6f65ff7869fd6561ff6b63ff7869ff846eff7e6cff9576ff8c72ffac88ffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffff9576ffffffffac88ff846eff7e6cff6b63fd6561f7565cf34e5af85a5df5535bf4505af5515bfb605ffe6862%
  ff6f65ff7869ff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffac88ff9576ff9576ff846efc6260f6545cf5535bf14958e53651e53751e93c53%
  ec3f55e63852f14858f24b59f34d59f24a59f85a5dfe6862ff846eff9576ff9f7dff9576ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffac88ff846eff7367fd6561f6545cf14858%
  eb3e54e93c53ea3d54e73a52e53751f04557ea3d54ea3d54f04557ea3d54f14858f34d59ff7367ff8c72ff8c72ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576ff8c72ff9576ff9f7dff846e%
  ff7e6cfe6862f95c5ef7585df5535bf34e5aed4155ef4356eb3e54f24b59f34e5aef4457f24b59f14858ef4356ef4356%
  f7565cff7e6cffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ff9576ff9576ff7869fd6561fb605ff5535bf04557f5515bef4457e93c53ea3d54e63852ea3d54ed4155f04557ee4256%
  f04757ea3d54e23450e73a52ee4156f7565cff7367ff7e6cffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffff9f7dff9f7dff9576ffffffff7e6cff6b63fe6862f7565cfe6862f34e5afb605ff7585df7585df7565c%
  f7585de83b53f5535bfa5e5ff6545cf85a5df34e5afb605ff7585dff6f65ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7dff9576ff9576ff846efc6260%
  fa5e5ffc6260ff6f65ff6f65fa5e5ffa5e5ff7585df7585df7585df85a5df95c5eff7869ff8c72ffffffffac88ffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ff8c72fc6260ff6f65f5515bf04557f6545cf5515bff6f65ff6b63f95c5ef95c5efa5e5ffd6561f7585dff7e6cff6b63%
  ff9f7dffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffac88ff8c72ff9f7dff9576ffac88ffffffffac88ffffffffffffffac88ffffffff9576%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffb3082eda294bd11f46d42248dc2b4c%
  df304eea3d54f6545cff6b63ff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff900106%
  bb0e35b3082ebb0e35c3143bc8183fd52349e0314ffb605fffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff}%
\gprawimage{rgb}{6.762}{2.179}{101}{101}{3.624}{3.624}{\gprawrgbimagedata}{}
\end{scope}
\gpcolor{rgb color={0.000,0.000,0.000}}
\draw[gp path] (6.780,2.197)--(6.816,2.233)--(6.852,2.269)--(6.889,2.306)--(6.925,2.342)%
  --(6.961,2.378)--(6.997,2.414)--(7.034,2.451)--(7.070,2.487)--(7.106,2.523)--(7.142,2.559)%
  --(7.179,2.596)--(7.215,2.632)--(7.251,2.668)--(7.287,2.704)--(7.324,2.741)--(7.360,2.777)%
  --(7.396,2.813)--(7.432,2.849)--(7.469,2.886)--(7.505,2.922)--(7.541,2.958)--(7.577,2.994)%
  --(7.614,3.031)--(7.650,3.067)--(7.686,3.103)--(7.722,3.139)--(7.759,3.176)--(7.795,3.212)%
  --(7.831,3.248)--(7.867,3.284)--(7.904,3.321)--(7.940,3.357)--(7.976,3.393)--(8.012,3.429)%
  --(8.048,3.465)--(8.085,3.502)--(8.121,3.538)--(8.157,3.574)--(8.193,3.610)--(8.230,3.647)%
  --(8.266,3.683)--(8.302,3.719)--(8.338,3.755)--(8.375,3.792)--(8.411,3.828)--(8.447,3.864)%
  --(8.483,3.900)--(8.520,3.937)--(8.556,3.973)--(8.592,4.009)--(8.628,4.045)--(8.665,4.082)%
  --(8.701,4.118)--(8.737,4.154)--(8.773,4.190)--(8.810,4.227)--(8.846,4.263)--(8.882,4.299)%
  --(8.918,4.335)--(8.955,4.372)--(8.991,4.408)--(9.027,4.444)--(9.063,4.480)--(9.100,4.517)%
  --(9.136,4.553)--(9.172,4.589)--(9.208,4.625)--(9.244,4.661)--(9.281,4.698)--(9.317,4.734)%
  --(9.353,4.770)--(9.389,4.806)--(9.426,4.843)--(9.462,4.879)--(9.498,4.915)--(9.534,4.951)%
  --(9.571,4.988)--(9.607,5.024)--(9.643,5.060)--(9.679,5.096)--(9.716,5.133)--(9.752,5.169)%
  --(9.788,5.205)--(9.824,5.241)--(9.861,5.278)--(9.897,5.314)--(9.933,5.350)--(9.969,5.386)%
  --(10.006,5.423)--(10.042,5.459)--(10.078,5.495)--(10.114,5.531)--(10.151,5.568)--(10.187,5.604)%
  --(10.223,5.640)--(10.259,5.676)--(10.296,5.713)--(10.332,5.749)--(10.368,5.785);
\gpcolor{color=gp lt color border}
\draw[gp path] (6.780,2.197)--(6.960,2.197);
\node[gp node right] at (6.596,2.197) {1};
\draw[gp path] (6.780,2.744)--(6.960,2.744);
\node[gp node right] at (6.596,2.744) {10};
\draw[gp path] (6.780,5.481)--(6.960,5.481);
\draw[gp path] (6.780,5.785)--(6.960,5.785);
\node[gp node right] at (6.596,5.785) {1h};
\draw[gp path] (6.780,2.197)--(6.960,2.197);
\draw[gp path] (6.780,2.362)--(6.870,2.362);
\draw[gp path] (6.780,2.580)--(6.870,2.580);
\draw[gp path] (6.780,2.691)--(6.870,2.691);
\draw[gp path] (6.780,2.744)--(6.960,2.744);
\draw[gp path] (6.780,2.909)--(6.870,2.909);
\draw[gp path] (6.780,3.127)--(6.870,3.127);
\draw[gp path] (6.780,3.238)--(6.870,3.238);
\draw[gp path] (6.780,3.292)--(6.960,3.292);
\node[gp node right] at (6.596,3.292) {$10^{2}$};
\draw[gp path] (6.780,3.456)--(6.870,3.456);
\draw[gp path] (6.780,3.674)--(6.870,3.674);
\draw[gp path] (6.780,3.786)--(6.870,3.786);
\draw[gp path] (6.780,3.839)--(6.960,3.839);
\node[gp node right] at (6.596,3.839) {$10^{3}$};
\draw[gp path] (6.780,4.004)--(6.870,4.004);
\draw[gp path] (6.780,4.221)--(6.870,4.221);
\draw[gp path] (6.780,4.333)--(6.870,4.333);
\draw[gp path] (6.780,4.386)--(6.960,4.386);
\node[gp node right] at (6.596,4.386) {$10^{4}$};
\draw[gp path] (6.780,4.551)--(6.870,4.551);
\draw[gp path] (6.780,4.769)--(6.870,4.769);
\draw[gp path] (6.780,4.880)--(6.870,4.880);
\draw[gp path] (6.780,4.933)--(6.960,4.933);
\node[gp node right] at (6.596,4.933) {$10^{5}$};
\draw[gp path] (6.780,5.098)--(6.870,5.098);
\draw[gp path] (6.780,5.316)--(6.870,5.316);
\draw[gp path] (6.780,5.428)--(6.870,5.428);
\draw[gp path] (6.780,5.481)--(6.960,5.481);
\draw[gp path] (6.780,5.645)--(6.870,5.645);
\draw[gp path] (6.780,2.197)--(6.780,2.377);
\node[gp node center] at (6.780,1.889) {1};
\draw[gp path] (7.327,2.197)--(7.327,2.377);
\node[gp node center] at (7.327,1.889) {10};
\draw[gp path] (10.064,2.197)--(10.064,2.377);
\draw[gp path] (10.368,2.197)--(10.368,2.377);
\node[gp node center] at (10.368,1.889) {1h};
\draw[gp path] (6.780,2.197)--(6.780,2.377);
\draw[gp path] (6.945,2.197)--(6.945,2.287);
\draw[gp path] (7.163,2.197)--(7.163,2.287);
\draw[gp path] (7.274,2.197)--(7.274,2.287);
\draw[gp path] (7.327,2.197)--(7.327,2.377);
\draw[gp path] (7.492,2.197)--(7.492,2.287);
\draw[gp path] (7.710,2.197)--(7.710,2.287);
\draw[gp path] (7.821,2.197)--(7.821,2.287);
\draw[gp path] (7.875,2.197)--(7.875,2.377);
\node[gp node center] at (7.875,1.889) {$10^{2}$};
\draw[gp path] (8.039,2.197)--(8.039,2.287);
\draw[gp path] (8.257,2.197)--(8.257,2.287);
\draw[gp path] (8.369,2.197)--(8.369,2.287);
\draw[gp path] (8.422,2.197)--(8.422,2.377);
\node[gp node center] at (8.422,1.889) {$10^{3}$};
\draw[gp path] (8.587,2.197)--(8.587,2.287);
\draw[gp path] (8.804,2.197)--(8.804,2.287);
\draw[gp path] (8.916,2.197)--(8.916,2.287);
\draw[gp path] (8.969,2.197)--(8.969,2.377);
\node[gp node center] at (8.969,1.889) {$10^{4}$};
\draw[gp path] (9.134,2.197)--(9.134,2.287);
\draw[gp path] (9.352,2.197)--(9.352,2.287);
\draw[gp path] (9.463,2.197)--(9.463,2.287);
\draw[gp path] (9.516,2.197)--(9.516,2.377);
\node[gp node center] at (9.516,1.889) {$10^{5}$};
\draw[gp path] (9.681,2.197)--(9.681,2.287);
\draw[gp path] (9.899,2.197)--(9.899,2.287);
\draw[gp path] (10.011,2.197)--(10.011,2.287);
\draw[gp path] (10.064,2.197)--(10.064,2.377);
\draw[gp path] (10.228,2.197)--(10.228,2.287);
\draw[gp path] (6.780,5.785)--(6.780,2.197)--(10.368,2.197);
\gpfill{rgb color={1.000,0.998,0.996}} (10.920,2.197)--(11.138,2.197)--(11.138,2.226)--(10.920,2.226)--cycle;
\gpfill{rgb color={1.000,0.934,0.895}} (10.920,2.225)--(11.138,2.225)--(11.138,2.254)--(10.920,2.254)--cycle;
\gpfill{rgb color={1.000,0.871,0.793}} (10.920,2.253)--(11.138,2.253)--(11.138,2.282)--(10.920,2.282)--cycle;
\gpfill{rgb color={1.000,0.807,0.692}} (10.920,2.281)--(11.138,2.281)--(11.138,2.310)--(10.920,2.310)--cycle;
\gpfill{rgb color={1.000,0.743,0.590}} (10.920,2.309)--(11.138,2.309)--(11.138,2.313)--(10.920,2.313)--cycle;
\gpfill{rgb color={1.000,0.737,0.580}} (10.920,2.312)--(11.138,2.312)--(11.138,2.338)--(10.920,2.338)--cycle;
\gpfill{rgb color={1.000,0.731,0.575}} (10.920,2.337)--(11.138,2.337)--(11.138,2.366)--(10.920,2.366)--cycle;
\gpfill{rgb color={1.000,0.724,0.570}} (10.920,2.365)--(11.138,2.365)--(11.138,2.394)--(10.920,2.394)--cycle;
\gpfill{rgb color={1.000,0.717,0.564}} (10.920,2.393)--(11.138,2.393)--(11.138,2.422)--(10.920,2.422)--cycle;
\gpfill{rgb color={1.000,0.710,0.559}} (10.920,2.421)--(11.138,2.421)--(11.138,2.450)--(10.920,2.450)--cycle;
\gpfill{rgb color={1.000,0.703,0.553}} (10.920,2.449)--(11.138,2.449)--(11.138,2.478)--(10.920,2.478)--cycle;
\gpfill{rgb color={1.000,0.696,0.548}} (10.920,2.477)--(11.138,2.477)--(11.138,2.506)--(10.920,2.506)--cycle;
\gpfill{rgb color={1.000,0.689,0.542}} (10.920,2.505)--(11.138,2.505)--(11.138,2.534)--(10.920,2.534)--cycle;
\gpfill{rgb color={1.000,0.682,0.537}} (10.920,2.533)--(11.138,2.533)--(11.138,2.562)--(10.920,2.562)--cycle;
\gpfill{rgb color={1.000,0.675,0.531}} (10.920,2.561)--(11.138,2.561)--(11.138,2.590)--(10.920,2.590)--cycle;
\gpfill{rgb color={1.000,0.668,0.526}} (10.920,2.589)--(11.138,2.589)--(11.138,2.618)--(10.920,2.618)--cycle;
\gpfill{rgb color={1.000,0.661,0.520}} (10.920,2.617)--(11.138,2.617)--(11.138,2.646)--(10.920,2.646)--cycle;
\gpfill{rgb color={1.000,0.654,0.515}} (10.920,2.645)--(11.138,2.645)--(11.138,2.674)--(10.920,2.674)--cycle;
\gpfill{rgb color={1.000,0.647,0.509}} (10.920,2.673)--(11.138,2.673)--(11.138,2.702)--(10.920,2.702)--cycle;
\gpfill{rgb color={1.000,0.640,0.504}} (10.920,2.701)--(11.138,2.701)--(11.138,2.730)--(10.920,2.730)--cycle;
\gpfill{rgb color={1.000,0.633,0.498}} (10.920,2.729)--(11.138,2.729)--(11.138,2.758)--(10.920,2.758)--cycle;
\gpfill{rgb color={1.000,0.626,0.493}} (10.920,2.757)--(11.138,2.757)--(11.138,2.786)--(10.920,2.786)--cycle;
\gpfill{rgb color={1.000,0.619,0.487}} (10.920,2.785)--(11.138,2.785)--(11.138,2.814)--(10.920,2.814)--cycle;
\gpfill{rgb color={1.000,0.612,0.482}} (10.920,2.813)--(11.138,2.813)--(11.138,2.842)--(10.920,2.842)--cycle;
\gpfill{rgb color={1.000,0.605,0.476}} (10.920,2.841)--(11.138,2.841)--(11.138,2.870)--(10.920,2.870)--cycle;
\gpfill{rgb color={1.000,0.598,0.471}} (10.920,2.869)--(11.138,2.869)--(11.138,2.892)--(10.920,2.892)--cycle;
\gpfill{rgb color={1.000,0.592,0.467}} (10.920,2.891)--(11.138,2.891)--(11.138,2.898)--(10.920,2.898)--cycle;
\gpfill{rgb color={1.000,0.590,0.466}} (10.920,2.897)--(11.138,2.897)--(11.138,2.926)--(10.920,2.926)--cycle;
\gpfill{rgb color={1.000,0.581,0.462}} (10.920,2.925)--(11.138,2.925)--(11.138,2.954)--(10.920,2.954)--cycle;
\gpfill{rgb color={1.000,0.573,0.458}} (10.920,2.953)--(11.138,2.953)--(11.138,2.982)--(10.920,2.982)--cycle;
\gpfill{rgb color={1.000,0.564,0.454}} (10.920,2.981)--(11.138,2.981)--(11.138,3.010)--(10.920,3.010)--cycle;
\gpfill{rgb color={1.000,0.555,0.450}} (10.920,3.009)--(11.138,3.009)--(11.138,3.038)--(10.920,3.038)--cycle;
\gpfill{rgb color={1.000,0.546,0.446}} (10.920,3.037)--(11.138,3.037)--(11.138,3.066)--(10.920,3.066)--cycle;
\gpfill{rgb color={1.000,0.538,0.442}} (10.920,3.065)--(11.138,3.065)--(11.138,3.095)--(10.920,3.095)--cycle;
\gpfill{rgb color={1.000,0.529,0.438}} (10.920,3.094)--(11.138,3.094)--(11.138,3.123)--(10.920,3.123)--cycle;
\gpfill{rgb color={1.000,0.520,0.434}} (10.920,3.122)--(11.138,3.122)--(11.138,3.151)--(10.920,3.151)--cycle;
\gpfill{rgb color={1.000,0.511,0.430}} (10.920,3.150)--(11.138,3.150)--(11.138,3.179)--(10.920,3.179)--cycle;
\gpfill{rgb color={1.000,0.503,0.426}} (10.920,3.178)--(11.138,3.178)--(11.138,3.207)--(10.920,3.207)--cycle;
\gpfill{rgb color={1.000,0.494,0.422}} (10.920,3.206)--(11.138,3.206)--(11.138,3.235)--(10.920,3.235)--cycle;
\gpfill{rgb color={1.000,0.485,0.418}} (10.920,3.234)--(11.138,3.234)--(11.138,3.263)--(10.920,3.263)--cycle;
\gpfill{rgb color={1.000,0.476,0.414}} (10.920,3.262)--(11.138,3.262)--(11.138,3.291)--(10.920,3.291)--cycle;
\gpfill{rgb color={1.000,0.468,0.410}} (10.920,3.290)--(11.138,3.290)--(11.138,3.319)--(10.920,3.319)--cycle;
\gpfill{rgb color={1.000,0.459,0.406}} (10.920,3.318)--(11.138,3.318)--(11.138,3.347)--(10.920,3.347)--cycle;
\gpfill{rgb color={1.000,0.450,0.402}} (10.920,3.346)--(11.138,3.346)--(11.138,3.375)--(10.920,3.375)--cycle;
\gpfill{rgb color={1.000,0.441,0.398}} (10.920,3.374)--(11.138,3.374)--(11.138,3.403)--(10.920,3.403)--cycle;
\gpfill{rgb color={1.000,0.433,0.394}} (10.920,3.402)--(11.138,3.402)--(11.138,3.431)--(10.920,3.431)--cycle;
\gpfill{rgb color={1.000,0.424,0.390}} (10.920,3.430)--(11.138,3.430)--(11.138,3.459)--(10.920,3.459)--cycle;
\gpfill{rgb color={1.000,0.415,0.386}} (10.920,3.458)--(11.138,3.458)--(11.138,3.471)--(10.920,3.471)--cycle;
\gpfill{rgb color={1.000,0.412,0.384}} (10.920,3.470)--(11.138,3.470)--(11.138,3.487)--(10.920,3.487)--cycle;
\gpfill{rgb color={0.998,0.407,0.383}} (10.920,3.486)--(11.138,3.486)--(11.138,3.515)--(10.920,3.515)--cycle;
\gpfill{rgb color={0.995,0.400,0.381}} (10.920,3.514)--(11.138,3.514)--(11.138,3.543)--(10.920,3.543)--cycle;
\gpfill{rgb color={0.992,0.393,0.378}} (10.920,3.542)--(11.138,3.542)--(11.138,3.571)--(10.920,3.571)--cycle;
\gpfill{rgb color={0.988,0.385,0.376}} (10.920,3.570)--(11.138,3.570)--(11.138,3.599)--(10.920,3.599)--cycle;
\gpfill{rgb color={0.985,0.378,0.374}} (10.920,3.598)--(11.138,3.598)--(11.138,3.627)--(10.920,3.627)--cycle;
\gpfill{rgb color={0.982,0.370,0.372}} (10.920,3.626)--(11.138,3.626)--(11.138,3.655)--(10.920,3.655)--cycle;
\gpfill{rgb color={0.979,0.363,0.369}} (10.920,3.654)--(11.138,3.654)--(11.138,3.683)--(10.920,3.683)--cycle;
\gpfill{rgb color={0.975,0.356,0.367}} (10.920,3.682)--(11.138,3.682)--(11.138,3.711)--(10.920,3.711)--cycle;
\gpfill{rgb color={0.972,0.348,0.365}} (10.920,3.710)--(11.138,3.710)--(11.138,3.739)--(10.920,3.739)--cycle;
\gpfill{rgb color={0.969,0.341,0.362}} (10.920,3.738)--(11.138,3.738)--(11.138,3.767)--(10.920,3.767)--cycle;
\gpfill{rgb color={0.966,0.333,0.360}} (10.920,3.766)--(11.138,3.766)--(11.138,3.795)--(10.920,3.795)--cycle;
\gpfill{rgb color={0.963,0.326,0.358}} (10.920,3.794)--(11.138,3.794)--(11.138,3.823)--(10.920,3.823)--cycle;
\gpfill{rgb color={0.959,0.319,0.356}} (10.920,3.822)--(11.138,3.822)--(11.138,3.851)--(10.920,3.851)--cycle;
\gpfill{rgb color={0.956,0.311,0.353}} (10.920,3.850)--(11.138,3.850)--(11.138,3.879)--(10.920,3.879)--cycle;
\gpfill{rgb color={0.953,0.304,0.351}} (10.920,3.878)--(11.138,3.878)--(11.138,3.907)--(10.920,3.907)--cycle;
\gpfill{rgb color={0.950,0.296,0.349}} (10.920,3.906)--(11.138,3.906)--(11.138,3.935)--(10.920,3.935)--cycle;
\gpfill{rgb color={0.946,0.289,0.347}} (10.920,3.934)--(11.138,3.934)--(11.138,3.963)--(10.920,3.963)--cycle;
\gpfill{rgb color={0.943,0.282,0.344}} (10.920,3.962)--(11.138,3.962)--(11.138,3.992)--(10.920,3.992)--cycle;
\gpfill{rgb color={0.940,0.274,0.342}} (10.920,3.991)--(11.138,3.991)--(11.138,4.020)--(10.920,4.020)--cycle;
\gpfill{rgb color={0.937,0.266,0.340}} (10.920,4.019)--(11.138,4.019)--(11.138,4.048)--(10.920,4.048)--cycle;
\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.047)--(11.138,4.047)--(11.138,4.049)--(10.920,4.049)--cycle;
\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.048)--(11.138,4.048)--(11.138,4.076)--(10.920,4.076)--cycle;
\gpfill{rgb color={0.928,0.252,0.334}} (10.920,4.075)--(11.138,4.075)--(11.138,4.104)--(10.920,4.104)--cycle;
\gpfill{rgb color={0.923,0.246,0.332}} (10.920,4.103)--(11.138,4.103)--(11.138,4.132)--(10.920,4.132)--cycle;
\gpfill{rgb color={0.918,0.239,0.329}} (10.920,4.131)--(11.138,4.131)--(11.138,4.160)--(10.920,4.160)--cycle;
\gpfill{rgb color={0.912,0.232,0.326}} (10.920,4.159)--(11.138,4.159)--(11.138,4.188)--(10.920,4.188)--cycle;
\gpfill{rgb color={0.907,0.226,0.323}} (10.920,4.187)--(11.138,4.187)--(11.138,4.216)--(10.920,4.216)--cycle;
\gpfill{rgb color={0.902,0.219,0.320}} (10.920,4.215)--(11.138,4.215)--(11.138,4.244)--(10.920,4.244)--cycle;
\gpfill{rgb color={0.896,0.213,0.317}} (10.920,4.243)--(11.138,4.243)--(11.138,4.272)--(10.920,4.272)--cycle;
\gpfill{rgb color={0.891,0.206,0.315}} (10.920,4.271)--(11.138,4.271)--(11.138,4.300)--(10.920,4.300)--cycle;
\gpfill{rgb color={0.886,0.199,0.312}} (10.920,4.299)--(11.138,4.299)--(11.138,4.328)--(10.920,4.328)--cycle;
\gpfill{rgb color={0.880,0.193,0.309}} (10.920,4.327)--(11.138,4.327)--(11.138,4.356)--(10.920,4.356)--cycle;
\gpfill{rgb color={0.875,0.186,0.306}} (10.920,4.355)--(11.138,4.355)--(11.138,4.384)--(10.920,4.384)--cycle;
\gpfill{rgb color={0.870,0.179,0.303}} (10.920,4.383)--(11.138,4.383)--(11.138,4.412)--(10.920,4.412)--cycle;
\gpfill{rgb color={0.864,0.173,0.300}} (10.920,4.411)--(11.138,4.411)--(11.138,4.440)--(10.920,4.440)--cycle;
\gpfill{rgb color={0.859,0.166,0.297}} (10.920,4.439)--(11.138,4.439)--(11.138,4.468)--(10.920,4.468)--cycle;
\gpfill{rgb color={0.854,0.159,0.295}} (10.920,4.467)--(11.138,4.467)--(11.138,4.496)--(10.920,4.496)--cycle;
\gpfill{rgb color={0.848,0.153,0.292}} (10.920,4.495)--(11.138,4.495)--(11.138,4.524)--(10.920,4.524)--cycle;
\gpfill{rgb color={0.843,0.146,0.289}} (10.920,4.523)--(11.138,4.523)--(11.138,4.552)--(10.920,4.552)--cycle;
\gpfill{rgb color={0.838,0.139,0.286}} (10.920,4.551)--(11.138,4.551)--(11.138,4.580)--(10.920,4.580)--cycle;
\gpfill{rgb color={0.833,0.133,0.283}} (10.920,4.579)--(11.138,4.579)--(11.138,4.608)--(10.920,4.608)--cycle;
\gpfill{rgb color={0.827,0.126,0.280}} (10.920,4.607)--(11.138,4.607)--(11.138,4.628)--(10.920,4.628)--cycle;
\gpfill{rgb color={0.823,0.121,0.278}} (10.920,4.627)--(11.138,4.627)--(11.138,4.636)--(10.920,4.636)--cycle;
\gpfill{rgb color={0.822,0.120,0.277}} (10.920,4.635)--(11.138,4.635)--(11.138,4.664)--(10.920,4.664)--cycle;
\gpfill{rgb color={0.815,0.115,0.272}} (10.920,4.663)--(11.138,4.663)--(11.138,4.692)--(10.920,4.692)--cycle;
\gpfill{rgb color={0.809,0.111,0.267}} (10.920,4.691)--(11.138,4.691)--(11.138,4.720)--(10.920,4.720)--cycle;
\gpfill{rgb color={0.802,0.106,0.262}} (10.920,4.719)--(11.138,4.719)--(11.138,4.748)--(10.920,4.748)--cycle;
\gpfill{rgb color={0.796,0.101,0.256}} (10.920,4.747)--(11.138,4.747)--(11.138,4.776)--(10.920,4.776)--cycle;
\gpfill{rgb color={0.789,0.096,0.251}} (10.920,4.775)--(11.138,4.775)--(11.138,4.804)--(10.920,4.804)--cycle;
\gpfill{rgb color={0.783,0.092,0.246}} (10.920,4.803)--(11.138,4.803)--(11.138,4.832)--(10.920,4.832)--cycle;
\gpfill{rgb color={0.776,0.087,0.241}} (10.920,4.831)--(11.138,4.831)--(11.138,4.860)--(10.920,4.860)--cycle;
\gpfill{rgb color={0.770,0.082,0.236}} (10.920,4.859)--(11.138,4.859)--(11.138,4.889)--(10.920,4.889)--cycle;
\gpfill{rgb color={0.763,0.077,0.231}} (10.920,4.888)--(11.138,4.888)--(11.138,4.917)--(10.920,4.917)--cycle;
\gpfill{rgb color={0.757,0.073,0.225}} (10.920,4.916)--(11.138,4.916)--(11.138,4.945)--(10.920,4.945)--cycle;
\gpfill{rgb color={0.750,0.068,0.220}} (10.920,4.944)--(11.138,4.944)--(11.138,4.973)--(10.920,4.973)--cycle;
\gpfill{rgb color={0.744,0.063,0.215}} (10.920,4.972)--(11.138,4.972)--(11.138,5.001)--(10.920,5.001)--cycle;
\gpfill{rgb color={0.737,0.058,0.210}} (10.920,5.000)--(11.138,5.000)--(11.138,5.029)--(10.920,5.029)--cycle;
\gpfill{rgb color={0.731,0.054,0.205}} (10.920,5.028)--(11.138,5.028)--(11.138,5.057)--(10.920,5.057)--cycle;
\gpfill{rgb color={0.725,0.049,0.200}} (10.920,5.056)--(11.138,5.056)--(11.138,5.085)--(10.920,5.085)--cycle;
\gpfill{rgb color={0.718,0.044,0.195}} (10.920,5.084)--(11.138,5.084)--(11.138,5.113)--(10.920,5.113)--cycle;
\gpfill{rgb color={0.712,0.039,0.190}} (10.920,5.112)--(11.138,5.112)--(11.138,5.141)--(10.920,5.141)--cycle;
\gpfill{rgb color={0.705,0.035,0.184}} (10.920,5.140)--(11.138,5.140)--(11.138,5.169)--(10.920,5.169)--cycle;
\gpfill{rgb color={0.699,0.030,0.179}} (10.920,5.168)--(11.138,5.168)--(11.138,5.197)--(10.920,5.197)--cycle;
\gpfill{rgb color={0.692,0.025,0.174}} (10.920,5.196)--(11.138,5.196)--(11.138,5.207)--(10.920,5.207)--cycle;
\gpfill{rgb color={0.690,0.024,0.172}} (10.920,5.206)--(11.138,5.206)--(11.138,5.225)--(10.920,5.225)--cycle;
\gpfill{rgb color={0.686,0.023,0.167}} (10.920,5.224)--(11.138,5.224)--(11.138,5.253)--(10.920,5.253)--cycle;
\gpfill{rgb color={0.678,0.022,0.159}} (10.920,5.252)--(11.138,5.252)--(11.138,5.281)--(10.920,5.281)--cycle;
\gpfill{rgb color={0.671,0.020,0.150}} (10.920,5.280)--(11.138,5.280)--(11.138,5.309)--(10.920,5.309)--cycle;
\gpfill{rgb color={0.664,0.019,0.142}} (10.920,5.308)--(11.138,5.308)--(11.138,5.337)--(10.920,5.337)--cycle;
\gpfill{rgb color={0.657,0.018,0.134}} (10.920,5.336)--(11.138,5.336)--(11.138,5.365)--(10.920,5.365)--cycle;
\gpfill{rgb color={0.650,0.017,0.125}} (10.920,5.364)--(11.138,5.364)--(11.138,5.393)--(10.920,5.393)--cycle;
\gpfill{rgb color={0.643,0.016,0.117}} (10.920,5.392)--(11.138,5.392)--(11.138,5.421)--(10.920,5.421)--cycle;
\gpfill{rgb color={0.636,0.015,0.109}} (10.920,5.420)--(11.138,5.420)--(11.138,5.449)--(10.920,5.449)--cycle;
\gpfill{rgb color={0.629,0.014,0.100}} (10.920,5.448)--(11.138,5.448)--(11.138,5.477)--(10.920,5.477)--cycle;
\gpfill{rgb color={0.622,0.013,0.092}} (10.920,5.476)--(11.138,5.476)--(11.138,5.505)--(10.920,5.505)--cycle;
\gpfill{rgb color={0.615,0.011,0.083}} (10.920,5.504)--(11.138,5.504)--(11.138,5.533)--(10.920,5.533)--cycle;
\gpfill{rgb color={0.608,0.010,0.075}} (10.920,5.532)--(11.138,5.532)--(11.138,5.561)--(10.920,5.561)--cycle;
\gpfill{rgb color={0.601,0.009,0.067}} (10.920,5.560)--(11.138,5.560)--(11.138,5.589)--(10.920,5.589)--cycle;
\gpfill{rgb color={0.594,0.008,0.058}} (10.920,5.588)--(11.138,5.588)--(11.138,5.617)--(10.920,5.617)--cycle;
\gpfill{rgb color={0.587,0.007,0.050}} (10.920,5.616)--(11.138,5.616)--(11.138,5.645)--(10.920,5.645)--cycle;
\gpfill{rgb color={0.580,0.006,0.042}} (10.920,5.644)--(11.138,5.644)--(11.138,5.673)--(10.920,5.673)--cycle;
\gpfill{rgb color={0.573,0.005,0.033}} (10.920,5.672)--(11.138,5.672)--(11.138,5.701)--(10.920,5.701)--cycle;
\gpfill{rgb color={0.566,0.003,0.025}} (10.920,5.700)--(11.138,5.700)--(11.138,5.729)--(10.920,5.729)--cycle;
\gpfill{rgb color={0.559,0.002,0.017}} (10.920,5.728)--(11.138,5.728)--(11.138,5.757)--(10.920,5.757)--cycle;
\gpfill{rgb color={0.552,0.001,0.008}} (10.920,5.756)--(11.138,5.756)--(11.138,5.785)--(10.920,5.785)--cycle;
\draw[gp path] (10.920,2.197)--(11.138,2.197)--(11.138,5.785)--(10.920,5.785)--cycle;
\draw[gp path] (11.138,2.197)--(10.958,2.197);
\node[gp node left] at (11.139,2.197) {0};
\draw[gp path] (10.920,2.197)--(11.100,2.197);
\draw[gp path] (11.138,2.557)--(10.958,2.557);
\node[gp node left] at (11.139,2.557) {1};
\draw[gp path] (10.920,2.557)--(11.100,2.557);
\draw[gp path] (11.138,3.393)--(10.958,3.393);
\node[gp node left] at (11.139,3.393) {10};
\draw[gp path] (10.920,3.393)--(11.100,3.393);
\draw[gp path] (11.138,4.589)--(10.958,4.589);
\node[gp node left] at (11.139,4.589) {$10^2$};
\draw[gp path] (10.920,4.589)--(11.100,4.589);
\draw[gp path] (11.138,5.785)--(10.958,5.785);
\node[gp node left] at (11.139,5.785) {$\ge10^3$};
\draw[gp path] (10.920,5.785)--(11.100,5.785);
\node[gp node center] at (8.574,5.426) {Unlabelled};
%% coordinates of the plot area
\gpdefrectangularnode{gp plot 2}{\pgfpoint{6.780cm}{2.197cm}}{\pgfpoint{10.368cm}{5.785cm}}
\end{tikzpicture}
%% gnuplot variables

### 2016-04-07 paper/gen-graph-unconnected-heatmap.tex
Include generated stuff for now, to make it easier to build

\begin{tikzpicture}[gnuplot]
%% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
%% Thu 07 Apr 2016 11:12:12 BST
\tikzset{every node/.append style={font={\scriptsize}}}
% \path (0.000,0.000) rectangle (10.922,7.366);
\gpcolor{color=gp lt color border}
\gpsetlinetype{gp lt border}
\gpsetdashtype{gp dt solid}
\gpsetlinewidth{1.00}
\draw[gp path] (1.320,5.785)--(1.320,2.197)--(4.908,2.197);
\node[gp node center,rotate=-270] at (0.246,3.991) {Clique Runtime (ms)};
\node[gp node center] at (3.114,1.427) {MAC Runtime (ms)};
\begin{scope}
\clip (1.320,5.785) rectangle (4.908,2.197);
\def\gprawrgbimagedata{%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffff8c72ff9f7d%
  ffac88ff8c72ff9f7dff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffd01d45ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ca1941ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffac88ffffffffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffc6163effffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffc6163dffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffc6163effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffffffffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffc1133affffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffc7173fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
  ffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffc6163effffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffffffffffff%
  c91840ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffac88ffffffffffffffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffac88ffffffffffffffffffffac88c4143cffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7d%
  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff9f7dffac88ffffffc3143b%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88%
  ffac88ffffffff9f7dffffffc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88%
  ffac88ffac88ffffffffac88ffffffffffffffffffffac88ffffffc4153cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffff9f7dff9f7dff9f7dffac88ffffffc2143bffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9576ff9f7dff9f7dffac88%
  ffffffffffffffac88c6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffff%
  ffffffffffffff9576ffac88ff9576ffffffff8c72ffffffc11239ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffff9f7dffffffffac88ffac88ffffffff9f7dff9f7dffffffff9f7dffffffff9f7dc5153cffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffffff8c72ffffffff9576%
  ffffffff9576bd1037ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffffff%
  ffac88ffac88ff9576ff9f7dff9f7dff9576ffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
  ffac88ff9f7dffac88ffffffffac88ff9f7dff9f7dff9f7dff9f7dff9576ffac88ff9f7dc2133bffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffff9576ffac88ffac88ffffffffac88ff8c72ffffffffac88ff8c72ff8c72%
  ffffffc01239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7dffac88ffac88ffac88ffffffffac88ff9f7dffac88%
  ff9f7dffac88ff9576ff9f7dff9f7dff9f7dc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffac88%
  ffac88ff8c72ff9576ffac88ffac88ff9f7dff9576ff846effac88ff846eff846ec4143cffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffffff%
  ffac88ffac88ff9f7dff9f7dff9576ff9f7dff9f7dff9576ff9f7dff9576ff9f7dff9576ffac88ff9576ff9f7dff8c72%
  c1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9576ffac88ffac88ff846effac88ff9f7d%
  ff9f7dff9576ff9f7dffffffff9576bd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff9f7dffac88ff9f7dff9f7dff9f7dff9576ffffff%
  ffac88ffac88ffffffff9576ffffffff9576ff846eff9f7dffac88ff9f7dc11239ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576%
  ff8c72ffffffff9f7dff9f7dff9576ff8c72ff9f7dff9f7dffac88ff9f7dff9f7dff9576ff9f7dff9576ff9576bf1138%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffffffffac88ffffff%
  ffffffff9f7dffffffffffffff9f7dff9576ff9576ff9576ffac88ff9576ffffffffffffffac88ff846eff9f7dff9576%
  ff846effffffffac88ff9f7dc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffff9f7dffffffffffffffac88ffffffffffffff9f7dff9f7dffffffffac88ff8c72ff8c72ff9f7dff7e6cff9f7d%
  ff8c72ffffffff9576ffac88ff7e6cff9576ff7e6cff846eff7869c2133affffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffac88ffac88ffac88ffac88%
  ff9576ffac88ff9f7dffac88ff9f7dffac88ff8c72ffac88ff9576ffac88ff9576ff8c72ff7e6cff846ec2133affffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
  ffffffffffffff9f7dffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffffff%
  ffac88ff846eff9576ff9f7dff9f7dffac88ff8c72ffac88ff9576ffac88ff7869ff8c72ff846eff9f7dff9f7dff846e%
  ff7e6cff6b63ffffffc5163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ff9f7dffac88ffac88ffac88ffffffff9576ffac88ff9576ff846eff9576ff9576ff8c72ff9576ff9f7d%
  ff8c72ff9f7dff7869ff846eff7e6cff7e6cff8c72ff8c72c1133affffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffffffffac88ffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff846effac88%
  ff8c72ff9f7dff8c72ff9576ff846eff846effac88ff7367ff7e6cff8c72ffffffff7367ff8c72c2133bffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ff9f7dffffffffac88ffac88ff846eff8c72%
  ffac88ffac88ff7e6cff9f7dff9576ff846eff9576ff9f7dff9f7dff9f7dff7869ff7367ff846eff9576ff846eff7e6c%
  ff7e6cff7e6cc4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
  ffac88ffac88ffffffff9576ffffffff9f7dff9576ff9576ffffffff9576ff8c72ff8c72ff7869ff9576ff8c72ff8c72%
  ff8c72ff9576ff7e6cff7e6cff7367ff9f7dff7e6cc7173effffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88%
  ffac88ffffffff9f7dffffffffffffffffffff9f7dffffffff9f7dffac88ff9576ff9576ff846eff9576ff7869ff8c72%
  ffffffffac88ffac88ff8c72ff9576ff7e6cff9576ff7e6cfe6862ff9f7dff9f7dff7367c6163effffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffffffffac88ffac88ffffffff9f7dffffffff9f7dffffffff9f7dffffffffac88ff9576%
  ff9576ff8c72ff9576ff8c72ff9576ff7e6cff8c72ff8c72ff8c72ff9576ff8c72ff846eff7e6cff846eff7e6cff7367%
  ff7869c6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ff9f7dff8c72%
  ff9576ff9576ffac88ff9f7dff9f7dff8c72ff9576ff9f7dff7e6cffac88ff7e6cff9f7dff846eff7e6cff7869ff8c72%
  ff8c72ff6f65ff7367ff9576ff8c72ff7e6ccd1b43ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576%
  ffac88ffac88ffac88ff9f7dffac88ff9576ff9f7dff9f7dff8c72ff9f7dff7e6cff846eff7869ff7e6cff9f7dff846e%
  ff846eff8c72ff9f7dff8c72ff7869ff846eff7e6cff9f7dff7e6cff7e6cff9f7dc91940ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffff%
  ffac88ffffffffffffffac88ffac88ff9f7dff9f7dff9f7dff9f7dffac88ffffffff846eff9576ff846eff9f7dff8c72%
  ff9576ff9f7dff8c72ff8c72ff7869ff9f7dfd6561ff7869ff8c72ff846eff7367ffac88ff9576ff8c72ff9576ff7367%
  ca1940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffac88ffffffffffffff9576ff9576ffffffffffffff9576ffffffffac88ffffff%
  ffac88ff8c72ff9f7dff9f7dff8c72ffac88fe6862ff7e6cff8c72ff9f7dff7e6cff8c72ff9f7dff7869ff9576ff846e%
  ff8c72ff7e6cff9f7dfd6561ff7869ca1940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ff9f7d%
  ff9f7dff846eff8c72ff9576ff9576ff846eff9576ff9f7dff846eff9f7dff9f7dff6b63ff7e6cff9576ff846effac88%
  ff846eff8c72ff9576ff846eff7e6cff9576ff9576ff846eff8c72ff7367c91840ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7d%
  ffffffffac88ffffffff9f7dffffffff8c72ffac88ff9f7dff9576ffac88ffffffffac88ff9576ff9f7dffac88ff7367%
  ff7869ffac88ff8c72ff9576ff7869ff9f7dfd6561ff9576ff9f7dff846efc6260ff7367ff6f65ff846eff846ec7173e%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffffffffac88ffffffff9f7dff9f7dffffffffffffffac88ff9f7dff9576ff9f7dff9f7dff9f7dff9f7dffac88%
  ff6b63ff7e6cff846eff7e6cff7e6cff6f65ff7367ff7869ff7e6cff8c72ff7869ff9f7dff9f7dff7e6cff9576ff9f7d%
  ff9f7dff846efe6862ff9576c91940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffff%
  ffac88ffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88ff9f7dff9576ff9f7dffac88ff9f7dffffff%
  ffffffffac88ff846effac88ff9f7dff9576ff7869ff9f7dff7367ff6f65ff7869ff6f65ff846eff7367ff7367ff846e%
  ff846eff7367ff7367ff7869ff8c72ff8c72ff7e6cff7367ff9f7dce1c44ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffac88ffac88ffffffffffffffac88ffac88ffac88ffac88ffac88ffac88ffac88ffffffff9f7dffac88%
  ffffffff9f7dff8c72ff9f7dff8c72ffffffff9576ff846eff8c72ff8c72ff9576ff846eff7869ff7869ff7367ff7869%
  ff7367fe6862ff8c72ff7367ff846eff7e6cff8c72ff8c72ff7869ff846eff6f65ffac88fd6561ff846eca1941ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88%
  ffac88ff9f7dffffffff9f7dffffffffac88ff9576ff9f7dff9f7dff9f7dff7e6cffac88ff846eff7869ff846eff9576%
  ff846eff7e6cff6b63ff846eff7869ff6b63ff9576ff9576ff6f65ff846eff846eff7367ffac88ff6b63ff7e6cff7e6c%
  ffac88ff8c72ff846ecc1b42ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffff%
  ffffffffffffff9f7dffffffff9f7dffac88ffac88ffffffffffffffac88ffac88ffac88ff9f7dff9f7dff8c72ff9576%
  ff8c72ff9576ff8c72ff7869ff9576ff6f65ff6f65ff7367ff9576ff846eff8c72ff846eff7869ff7367ff6f65ff7869%
  ff7e6cff6f65ff9576ff8c72ff7869ff7367ff6f65ff9576ca1941ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffff%
  ffac88ffffffffac88ffffffffac88ffac88ffac88ffac88ffac88ffffffff9f7dff9f7dffffffffac88ff9576ff9576%
  ffac88ffac88ff9f7dff9576ff9576ff9f7dffac88ff7367ffac88ff7869ff7e6cff6f65ff8c72fc6260fe6862ff9576%
  ff6b63ff8c72ff7367ff7869ff7869ff6f65ff7e6cff7869ff7367ff7869ff8c72ff7e6cff7e6cd52349ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9f7dff9576ffffffff9576%
  ff9f7dffac88ffac88ff9f7dff9f7dff9576ff9576ff9576ff9f7dffac88ff8c72ff7e6cff6f65ff8c72ff7869ff7869%
  ff7869ff7e6cff6b63ff8c72ff7869ff846eff7e6cff7869ff7869ff846eff7367ff8c72ff7e6cff7367ff6f65ff7869%
  ff6f65ff9576d32148ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffac88ffac88ffac88ffffffffffffffffffffac88ff9f7dffffffffac88ffffff%
  ff8c72ffac88ff9576ff9576ff9f7dffffffffac88ff9f7dffac88ff9576ff9f7dff9f7dff9576ffac88ff8c72ff8c72%
  ff8c72ff7869ff7367fd6561ff6f65fe6862ff7869ff7e6cff846eff6b63ff7869ff846eff7869ff6f65ff7e6cff6f65%
  ff6b63ff9576ff7869fe6862ff7367ff7869ff846ed42248ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
  ffffffffffffffffffffffffff9576ffffffff9576ffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff846e%
  ff9f7dffac88ff7367ff846eff7869ff8c72ff8c72ff7e6cff7e6cfd6561ff6f65ff6b63ff9576ff7e6cff9576ff7e6c%
  ff6f65ff7869ff7e6cff6b63ff7869ff846eff6b63ff846eff7869ff7869ff846eff8c72d42248ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ff9576ffac88ff9f7dffac88ffac88ffac88%
  ffffffff9f7dffac88ffac88ffac88ffac88ff8c72ff7367ff846eff6f65ff6b63ff7e6cff8c72ff7e6cff7e6cfb605f%
  ff6b63ff7367ff9576ff7367ff7869ff9576ff6f65fd6561ff846eff9576ff8c72ff9576ff7367ff7e6cff7367ff7367%
  fe6862d11e46ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff9576ffffffff846e%
  ffffffff9f7dffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff8c72ff9f7dff846eff9576ff7367ff8c72%
  ff8c72fe6862ff8c72fc6260ff6b63ffac88ff7869ff7367ff8c72ff846eff6f65ff7e6cff8c72ff7367ff6b63ff6f65%
  ff9576ff8c72ff7869ff846eff846eff7e6cd32047ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9f7d%
  ff9576ffffffffffffff9576ff9f7dff9f7dff8c72ff9576ff9f7dffac88ff8c72ff8c72ff9576ff846effac88ffac88%
  ff9576ff846eff8c72ff6f65fd6561fe6862ff6b63ff846eff6f65fe6862ff6b63ff7e6cfb605fff9576ff7869ff9576%
  ff7367ff7367ff846eff7869ff7367f85a5dff846eff8c72ff7869fe6862ff846ed7254affffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffff%
  ffac88ffffffffffffffac88ffac88ffffffff9576ff9f7dffffffffac88ffac88ff9f7dff9f7dff9576ffffffffac88%
  ff9576ff9576ffac88ff9576ff846eff6f65ff846eff7367ff7367ff9576ff8c72fe6862fd6561ff6f65fb605fff8c72%
  ff7367ff7367ff7869ff846eff7869ff7e6cff7e6cfe6862ff846eff7367ff846eff8c72ff8c72ff7e6cff846efd6561%
  da294bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffff9f7dffffffffac88ffffffffac88ff9f7dff9f7dffffffffffffffac88ff8c72ff9576ff9f7dff9576ff9576%
  ffac88ff9f7dff8c72ff8c72ff9f7dff9f7dff7869ff846eff7869ff7e6cff6f65ff846eff846eff6f65ff7367ff6f65%
  ff846efd6561fe6862fc6260ff7367ff7367ff7e6cfe6862ff846eff9f7dff6b63ff7367ff7869ff7869ff6b63ff6f65%
  ff6b63ff6f65ff6f65ff7367ff6f65da2a4cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffffffac88ff8c72ffffffff846e%
  ff8c72ff8c72ffffffff8c72ff8c72ff846eff9576ff8c72ff6b63ff846eff9576ff8c72fe6862ff846eff7e6cff6f65%
  ff7367ff7869ff7367ff6f65ff7367ff6b63fe6862f95c5efd6561ff9576ff6b63ff846eff6f65ff7e6cff7e6cff846e%
  ff6f65ff7e6cff9f7dff6b63fe6862ff7367ff7367ff6f65ff7367ff7e6cd8274affffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffff%
  ffac88ffac88ff9f7dffac88ffffffff9576ff7e6cff8c72ff9f7dff9576ffac88ff846eff9f7dffac88ff9f7dff9f7d%
  ff7869ff7e6cfd6561ff846eff7869fe6862ff6f65f85a5dff7869ff9576ff846efe6862fd6561ff7367fd6561fe6862%
  ff7367ff6f65fb605ffd6561ff6b63ff6f65ff8c72ff8c72fd6561ff6f65ff7367ff846eff8c72ff846eff7367d8264a%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7d%
  ffac88ffffffffac88ffac88ffffffffac88ffffffff7e6cff8c72ff846eff8c72ff9f7dff8c72ff9f7dff8c72ff9f7d%
  ff6f65ff846eff6f65fa5e5fff846eff846eff7e6cff8c72ff7869ff9576ff7367ff7869fc6260ff6b63fc6260fe6862%
  ff6b63fe6862ff846efd6561ff7367fc6260f85a5dff6f65fe6862ff8c72fe6862fe6862ff6b63fe6862ff7869ff846e%
  ff8c72ff846eff8c72ff7e6cde2e4effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88%
  ffac88ffffffffffffffac88ffffffffac88ffac88ff9f7dff9576ff9f7dff9f7dff846eff9f7dff9576ff9576ff9f7d%
  ff9576ff846eff9576ff8c72ff7e6cff6f65ff7869ff6b63ff7367ff7367ff7869ff7869ff6f65ff6f65fd6561ff9576%
  ff6f65ff7367fe6862ff6b63f7565cff7367ff846ef95c5efb605fff6b63fe6862ff7e6cff6b63ff6f65fa5e5ffd6561%
  fa5e5fff846eff6b63fd6561ff6f65fe6862ff7869ff7869ff846ede2e4effffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ff8c72%
  ff9f7dffffffff7869ff846effac88ff846eff8c72ff8c72ff8c72ff8c72ff7e6cff7869ff6f65ff7367ff7869ff7e6c%
  ff9f7dff7e6cff7e6cff7869ff7869ff9576ff6f65fd6561fe6862fe6862ff7367fc6260ff7869fc6260ff6b63ff6f65%
  ff6f65ff6b63fe6862fd6561fc6260fa5e5ffe6862fb605fff846eff9576ff7367ff7869ff6f65ff7e6cdf2f4effffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffff9f7dffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffff9f7dff9f7dff7869ff9f7dff9f7dff8c72ff846eff7869ff7869ff9f7dff846eff6f65ff8c72fe6862%
  ff7e6cfd6561ff6b63ff6b63fd6561ff6b63fe6862ff6f65f7585dfc6260ff6f65fe6862ff7869f95c5efd6561ff846e%
  fe6862fb605ffc6260f6545cfc6260ff7367ff6b63fd6561ff7869fa5e5fff7869fd6561fc6260ff7367ff6f65ff6f65%
  ff7869fe6862ff7869e23350ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ff9f7d%
  ffac88ffac88ffac88ffac88ffac88ff9f7dff9576ff9f7dffac88ffac88ff846eff9576fe6862ff6b63ff7869ff8c72%
  ff7367fb605ffd6561ff6f65fd6561fb605fff7869fc6260ff7367ff7367fe6862fe6862f95c5eff7e6cff7367f5535b%
  fb605fff6b63ff7367f7585dfe6862ff6b63fc6260fe6862fb605ff7565cf85a5dfe6862f7585dff7e6cff6b63ff7367%
  ff6b63ff846eff6b63ff6f65ff6b63ff7e6cff8c72ff846ee63852ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff9f7dff9f7dffffffff9576ff8c72ffac88%
  ff9576ff9f7dff9f7dff9f7dff9576ffffffff9f7dff9576ffffffffac88ff9f7dff9576ff9f7dffffffffffffff9f7d%
  ffac88ffffffff8c72ffffffffffffff9576ffac88ff9f7dff9576ffac88ff9576ff8c72ff846eff9f7dff7e6cff7367%
  ff9576ff9576ff846efc6260f95c5efd6561ff6b63f95c5eff7367ff7e6cff7367ff6b63fc6260fd6561fa5e5fff6b63%
  ff6f65fb605ffb605ff7565cfc6260f7565cf7565cf14958f7565cfc6260fb605ff34e5af5515bfa5e5ff5515bfb605f%
  fc6260fd6561fe6862ff6f65ff8c72fa5e5ffe6862ff8c72ff6b63ff7367fe6862ff846eff7869e73a52ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88fa5e5ffd6561fd6561fc6260%
  f5515bfa5e5ffc6260f7585dff6b63fc6260fc6260ff9576ff6f65ff6f65ff7367ff846eff9576ff846eff846effac88%
  ffac88ff9f7dff8c72ff7e6cffac88ff9576ffac88ff9f7dff846eff846eff9576ffac88ff7367ff7e6cff846eff9f7d%
  ff846eff7869ff8c72fe6862ff8c72ff6f65ff6f65fa5e5ffe6862fb605ff34d59f85a5df7585df7565cff6f65fd6561%
  fd6561fc6260fb605ff95c5efb605ffe6862f7565cf95c5efb605ffa5e5ff5535bf85a5df5515bf5535bfe6862fd6561%
  f95c5ef5515bf14958fc6260f95c5eff9576fb605ffa5e5ffd6561ff7e6cfb605fff6b63ff7367ff7367ff6f65ff6f65%
  fe6862ff7367ea3d54ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  fc6260ec3f55f14858f24b59f34e5ae33550f14858f34d59f95c5ef4505af5535bfe6862ff6b63ff7367ff6b63ff6f65%
  ff6f65fa5e5fff7367ff6b63ff7e6cff6f65ff7869ff7869ff6f65ff8c72ff846eff8c72ff7e6cff8c72ff6f65ff846e%
  ff9576ff846eff7e6cff6b63ff9576ff6f65ff7869fd6561fe6862ff7e6cfb605ffe6862ff7367fa5e5ff95c5ef5515b%
  f7585dfb605ffd6561f85a5dff7869fa5e5ffd6561ff6b63fb605ff7585dfc6260fb605ffc6260fa5e5ff6545cf85a5d%
  f6545cf14958f4505af7565cfb605ff4505af5535bfa5e5ff95c5efb605ffb605ff5535bfb605fff846eff7e6cff7869%
  f85a5dfc6260ff8c72ff6b63ffffffff7869ff9576e63852ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88f5515be73952e2324fe73952ea3d54ea3d54e73952ea3d54f34d59f34d59f5535b%
  f7585df7585df5535bf7565cff6f65fa5e5ff85a5dfc6260fd6561ff7367fb605fff7367ff6b63ff6f65ff8c72ff8c72%
  ff7869ff6f65ff7869ff7367fb605fff846eff8c72ff7367fc6260fc6260fa5e5ffb605fff6f65f95c5eff7367fd6561%
  f7585dfa5e5ff4505af34d59fe6862f34e5af7565cf95c5ef34e5afc6260f5515bff6b63fc6260f7585df5535bf7585d%
  f7565cf85a5df85a5df7565cf7565cf5535bf85a5dfd6561fe6862fc6260f6545cfa5e5ff7565cff6b63fa5e5ffd6561%
  fc6260fa5e5fff6b63ff6b63ff6f65ff6b63ff7e6cff7367ff7e6cff6b63ff846effac88e53651ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff7e6cf5535bef4356e33450ee4256f04757ee4156f34d59%
  f7565cf95c5ef85a5dfd6561fc6260f95c5eff6f65ff7869ff6f65ff6f65fc6260ff6f65ff846eff6b63ff7e6cff6b63%
  fe6862ff6f65ff6b63ff7367ff7367fe6862ff6f65fa5e5fff6b63fe6862ff6b63fa5e5fff7367f5535bfc6260f7585d%
  fd6561f85a5df7585df14858f7565cf5535bfc6260f34e5af85a5df7565cf5535bf7565cf95c5eff7869fd6561fe6862%
  f7585dfa5e5ff7585dfb605ff6545cf24b59f95c5efc6260fc6260f5515bfa5e5ff7565cfb605fff6b63fc6260fb605f%
  fa5e5ff7585df85a5dff6f65ff6b63ff7869fe6862fd6561fd6561ff8c72ff846efd6561ff7869ff7869ff9576ff8c72%
  ff9f7deb3e54ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88f04557e33550e33550%
  ec4055ec3f55ef4457f34d59f6545cfa5e5ffe6862f34d59f7585dfb605fff6f65ff7869ff7367fc6260fa5e5ffc6260%
  fe6862ff846eff6f65ff6b63f95c5ef34d59ff846ef95c5efd6561f7565cf7565cf85a5dfc6260f34e5afc6260f7585d%
  f95c5ef5535bf4505af95c5ef6545cf4505af14858f34d59f7565cf34d59f7585df7585df7585df24b59fa5e5ff7585d%
  fa5e5ff6545cf7585df6545cf95c5efa5e5ff7585dfb605ff34e5af7585df7565cf85a5df4505af24a59fc6260f5535b%
  f6545cf4505af7585dff6b63f7585df95c5ef7585dfd6561fd6561ff6b63ff6b63fd6561fc6260fe6862ff7e6cfe6862%
  ff6b63ff6b63ff846eff846eff6f65ff7869e83b53ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ff9576f95c5ee1324fe0314fe23450e33550e43651ea3d54ef4457f04757f24a59f7585dfb605ffa5e5ffc6260f95c5e%
  fa5e5fff6b63fa5e5ff7585dff7367fd6561fb605ff7565cfe6862fa5e5ffb605ff7585df95c5ef7585df7565cf34e5a%
  f04757f34d59f34e5af4505af04757f5535bf24a59f34d59f14858f34d59f04757f14958f24b59f04757f14958f4505a%
  f24a59f04557f7585def4457f14958fc6260f5535bf34e5af85a5df7565cf04757f34e5af5535bf7565cf6545cf85a5d%
  ff6b63f4505af7565cf95c5ef7585dfe6862fd6561fa5e5ffa5e5ff5535bf34e5afa5e5ffc6260fe6862fa5e5fff6b63%
  fd6561ff6f65fe6862ff7e6cff6f65ff7869ff7869fe6862ff8c72ff6f65ff8c72e73a52ffffffffffffffffffffffff%
  fffffffffffffffffffffffffe6862e43551df2f4ecc1b42d9284bdd2d4dde2e4ee43551e33450ec4055f14858f5515b%
  f4505af5515bff6b63f4505afb605ff6545cf85a5df5535bfb605ffb605ff6545cfc6260f85a5dfb605ff24a59f6545c%
  f85a5df5515bf5535bf5535bf14858ef4457ec4055f4505aeb3e54f34e5aef4356ef4457f24b59ee4156ee4256e83a53%
  e63852ec3f55ee4156f14958e73a52e83b53e83a53ec3f55ea3d54e53751ef4356f14958ef4356f5515bed4155f95c5e%
  f34d59f14958f6545cee4156f5515bf7565cf6545cf04557f5535bfb605ff34d59f7565cf34e5af6545cf24a59fe6862%
  fe6862f85a5dfa5e5ff85a5dfc6260fc6260f85a5dff6f65ff7e6cff7e6cff6f65ff9576ff846eff7e6cff8c72ff6b63%
  ec4055fffffffffffffffffffffffffffffffffffffffffffe6862dc2c4dd21f47cb1a42c8183fdb2a4ce23450e43651%
  ed4155ee4256f24b59f4505afc6260f5515bf4505af5515bf85a5df6545cfd6561f5515bf7565cf85a5df85a5df85a5d%
  ff7e6cf5515bf34e5aff6b63fd6561fa5e5ff14958f95c5ef24a59f24b59f04757f14858f04557f24a59f34d59f04757%
  f4505af04557f04757e93c53f04757e33550e63852e43551ea3d54ea3d54ec3f55e93c53e63852ea3d54ec4055ee4156%
  ea3d54f14958f34d59f6545cf7585df34d59f34e5af14958f14958f6545cf04557f6545cf04557fa5e5ff7565cf95c5e%
  f95c5efd6561fa5e5fff846efc6260ff6b63ff6f65ff7367ff6f65ff6f65ff6b63ff6f65ff7367ff7869ff9576ff846e%
  ff7869ff7367ff7869ff9576ff846ef24a59ffffffffffffffffffffffffffffffffffffffffffde2d4dd01e45c4153c%
  cb1a42ce1c44de2e4ee0314fea3d54f34d59f5515bf5535bf34e5af6545cf34e5afb605ffb605ffa5e5ffc6260fa5e5f%
  fe6862fc6260fa5e5ff5535bfb605ff95c5ef6545cf7565cfc6260f24a59f34e5af24a59f04757ef4457f34d59f14858%
  f04557f14958f4505af34e5af14858e83a53f34d59eb3e54ec3f55ef4457ea3d54ee4156ee4156ea3d54e63852ef4356%
  e83a53ef4356e83b53e73a52f14958ee4156f14958ef4457f14958f14858f5515bf14958f5515bf5515bf4505afa5e5f%
  fc6260ff7869f4505afd6561fa5e5fff6f65f85a5dff8c72ff6f65ff7869ff9f7dff7869ff8c72ff9576ff846eff7e6c%
  ff9f7dff9576ffac88ff846effac88ff9f7dffac88ffac88ffac88ffac88ff9f7dffffffffffffffffffffffffffffff%
  ffffffff9576c4153cc11239c3143bd11e46d52349e0304edf304ee63852f14958f14858f34e5afb605ff34d59f34e5a%
  f34e5af24a59f34e5af24a59ee4256f5515bf34e5aef4457f4505af7565cf24a59f34d59f24a59f04557e53751ea3d54%
  e83b53e63852ee4256ea3d54ef4356e93c53ec3f55e33550f14858f04757ef4356ea3d54eb3e54e93c53e63852f04557%
  e73a52ea3d54e83b53eb3e54ee4156ed4155e83a53ed4155f04757f14958ee4156f14958f5515bfd6561f5515bf6545c%
  f4505afd6561f85a5df85a5dfc6260ff6b63ff7869fe6862ff7e6cff846eff8c72ff846effac88ff9576ffac88ff8c72%
  ff8c72ffac88ff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffff4505ac8183fcb1a42e93c53dd2d4ded4155ef4457f04757f14958f14858%
  f34d59f24a59fb605ff34d59f14958f85a5df04557f34d59f14858f24a59f7565cf85a5dfd6561f24b59ef4356f5535b%
  f4505af14958e83b53f04757f04557ec3f55f34d59f14958f24a59ed4155ec3f55f04757f24b59f14958f34d59f34d59%
  e43651ef4457ee4256f14858f24a59f04757fa5e5ff04557ef4457f14858ef4356f5535bf14958f7585df85a5df95c5e%
  f85a5dfc6260f7585dff7367ff7e6cff7869ff7367ff7367ff846eff8c72ffac88ff9576ffac88ffffffffffffffac88%
  ffac88ffac88ff9f7dffffffff9576ff9576ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576e83b53d42248e1324ff14958f24b59%
  f24b59f4505af7565cf7565cf95c5ef95c5eff6b63fa5e5ffa5e5ff5535bf4505af34d59f34d59f6545cf85a5dfc6260%
  fe6862f7585df6545cf5535bf34e5af4505af6545cf7565cf95c5ef85a5dfa5e5fff8c72fa5e5ff14858fa5e5ff14858%
  f7585df34e5af34d59f34d59f34e5af4505af4505af4505af6545cf95c5ef34d59f7585df34e5af24b59fe6862fe6862%
  f6545cf7565cf85a5dff7367f95c5eff7869ff6b63ff7e6cff7869ff7869ff846effac88ff7e6cff9576ff9f7dffffff%
  ff846eff846eff9576ffac88ffffffffac88ff9576ff9f7dffffffffac88ffffffffffffffffffffffffffac88ffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff4505a%
  d21f47d52248db2a4ce33550e23350e73952f24a59ee4256e73952f04757ef4457ee4156ef4457ef4356eb3e54f14858%
  ef4457f34e5af85a5df4505afb605ffa5e5feb3e54e83a53f04757f04757f04557ea3d54f4505afb605ff4505aef4356%
  f24a59f14858f14858f14858ee4156e83a53e83a53ee4256e73a52e83a53e93c53e83a53e83b53f04557f24b59ef4457%
  e93c53ec3f55eb3e54ed4155f34d59ef4457fc6260f24b59f5515bf5515bf95c5efb605ffa5e5ffe6862ff8c72ff7e6c%
  ff846eff7869ff9576ffffffffac88ff8c72ff9576ff9576ffac88ffac88ff9f7dffac88ffffffffffffffac88ff9f7d%
  ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff8c72dd2d4dcb1a42e2324ff14858ef4356f6545cf5535bf4505af5535bf5515bfb605ff34d59%
  f34d59f4505af5535bf7585df5515bfa5e5fff7367f95c5efc6260f7565cfb605ff24a59ef4356ef4356f14858f5535b%
  f24b59f7565cf6545cfd6561f5515bf24a59ee4156f4505af24b59ef4356ef4356ef4356f34d59ea3d54ee4256f04757%
  f14858ef4356f04557ef4356f7565cf34e5af24b59f95c5ef5515bf95c5ef5515bfa5e5ffc6260ff7e6cff7e6cff846e%
  ff7869ff9576ff846eff7869ff846eff9576ff8c72ff9f7dffac88ffac88ffac88ffac88ffffffffac88ffffffffffff%
  ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffff34d59e1324ff04557fd6561ff7869fd6561ff9f7dff7869%
  ff9576fc6260ff8c72fc6260ff6f65ff6f65fd6561ff846eff7e6cfb605fff6f65ff7367ff8c72ff8c72fa5e5ffc6260%
  fd6561ff6b63ff6f65fa5e5ffe6862fb605ffd6561ff6f65ff7e6cfb605ffd6561ff6b63fc6260ff7e6cfb605ff5515b%
  f24b59ff7e6cfd6561ff6f65fd6561f95c5efc6260fd6561fd6561ff6f65ff7e6cff6f65ff9576ff846eff6b63ff9f7d%
  ff9f7dffac88ffac88ff9f7dff9f7dff9576ff9f7dffffffffac88ffac88ffffffff9f7dffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88e53751bc0f36c4153cda294b%
  ea3d54ec3f55f6545cf24a59f7565cf34e5af6545cf24a59f14958f34d59f34e5af34d59f34e5af04757f4505af04757%
  f24a59f04557eb3e54ec4055e83a53f34d59ef4457ef4457ef4356ef4356ee4156ec4055ea3d54ee4156f34d59ee4156%
  f24a59f14858ed4155f14858f14958f04557ef4457f4505af34d59f4505af7585df5535bfb605ff85a5dff6f65fd6561%
  f85a5dff6b63ff8c72ff9f7dff846effac88ff846effac88ff846eff9576ffffffffffffffffffffac88ffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
  ff9576d7254ac7173edd2d4dee4256f5515bf5515bfc6260f4505af24a59f34d59f5535bf6545cf24a59f34e5af4505a%
  f04557f04757f34d59f34d59ee4256f04557f14958f5535bf7565cf14958f14858f6545cef4457ef4457f04557f24a59%
  f14958f4505aec4055ef4457f34e5af95c5eef4356f14858fd6561fa5e5ff24b59f85a5df95c5efc6260f85a5dfa5e5f%
  ff846eff8c72ff846eff6b63ff846eff8c72ff9f7dffac88ffffffff9f7dffffffffac88ff9f7dffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff8c72ff6f65fe6862d7254ad01e46ef4457f24b59f04757f04557f4505ae83b53ef4457f34d59%
  f34d59f34e5af04757f24b59f4505af5515bef4356f04757f34e5aef4457ef4457ec3f55f04557e53751ee4156f24b59%
  f24b59ef4356f14958f14858e93c53ea3d54ea3d54eb3e54f34e5af04557f4505af24a59f4505af7585dff6f65fc6260%
  fd6561fe6862ff7367ff8c72ff7869ff7367ff8c72ff8c72ff9f7dffffffff9f7dff9f7dff9f7dffac88ffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffff7585df34e5ae0304ed11e46da294be2324fe63852e23450%
  e23350e73a52e43651ea3d54ea3d54e73952e93c53ef4457ef4457f14858ef4356eb3e54e73952e83a53ea3d54e2324f%
  e73a52e73a52ed4155ee4156ea3d54ef4356ec4055f34d59f24b59e83b53ee4156ef4356ee4156f34e5af34d59f5515b%
  f7565cff7367f85a5dff9576ff7e6cff846eff9576ff8c72ff8c72ff9576ff8c72ffffffffffffffffffffac88ffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff24a59db2a4cc2133a%
  c01138cd1c43d21f47d62449d62449d8274ad42248d42148d7264ada294bdb2a4cdc2c4ddc2c4cd9284bde2d4dde2e4d%
  e1314fde2d4de23450e0314fda294bdc2c4de1314fdb2b4cda294be23450d9274be23450e0314fe33550e73a52eb3e54%
  ee4156f14858f24b59f4505afe6862f34e5aff7e6cff7367ff9f7dff7869ff9576ff9576ffac88ff8c72ff9f7dffffff%
  ffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffcc1b42c1133aba0e34ca1940d32047d52349d11e46d01e45d62449%
  d7254ad62449d52349da294bd7254add2d4dda2a4cd8264ad32148d7254ad62449da294bdc2b4cd7254ad8264ad7264a%
  db2a4cd62449d42248d52349e0304ee43551e1314fe83b53e83b53ea3d54f4505af95c5eff7869ff7367ff6f65ff7e6c%
  ff7367ff7869ff9576ffac88ff9f7dffac88ffac88ffac88ff9576ffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffff9a0212af062bb80c32c01138cb1a42cf1d45d32047d52349d21f47d62449d8264ad9284bd42148d7254ad22047%
  d01e46d21f47d32047d01e46d11f46d9274bd32047d8264ad9284bd7264ad8264adc2c4cdc2b4ce1314fe73a52e63852%
  ea3d54f24b59f34d59fb605fff6f65ff7869ff7869ff8c72ff9576ff9576ffac88ffffffff9f7dffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000b70b32b50a30b60b31b70b32%
  bb0e35bc0f36bf1138c01239bf1138bf1138ba0d34bf1138c1133ac1133ac91840c9183fca1941c6163dca1941c91840%
  cd1b43d11e46d01d45d52248dc2c4cda2a4ce53751e73a52ec3f55f34e5afa5e5fff6b63ff7e6cff846effac88ff9f7d%
  ff9576ff9f7dffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000%
  b3082eae062aac0527aa0525ac0527b0062cb4092fba0e34bd1037c5163dc7173eca1940d21f47d7264ade2e4deb3e54%
  ed4155fb605ff5515bff6b63ff9576ff7367ff9f7dff8c72ffac88ffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff8b0000ff6b63ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff}%
\gprawimage{rgb}{1.302}{2.179}{101}{101}{3.624}{3.624}{\gprawrgbimagedata}{}
\end{scope}
\gpcolor{rgb color={0.000,0.000,0.000}}
\draw[gp path] (1.320,2.197)--(1.356,2.233)--(1.392,2.269)--(1.429,2.306)--(1.465,2.342)%
  --(1.501,2.378)--(1.537,2.414)--(1.574,2.451)--(1.610,2.487)--(1.646,2.523)--(1.682,2.559)%
  --(1.719,2.596)--(1.755,2.632)--(1.791,2.668)--(1.827,2.704)--(1.864,2.741)--(1.900,2.777)%
  --(1.936,2.813)--(1.972,2.849)--(2.009,2.886)--(2.045,2.922)--(2.081,2.958)--(2.117,2.994)%
  --(2.154,3.031)--(2.190,3.067)--(2.226,3.103)--(2.262,3.139)--(2.299,3.176)--(2.335,3.212)%
  --(2.371,3.248)--(2.407,3.284)--(2.444,3.321)--(2.480,3.357)--(2.516,3.393)--(2.552,3.429)%
  --(2.588,3.465)--(2.625,3.502)--(2.661,3.538)--(2.697,3.574)--(2.733,3.610)--(2.770,3.647)%
  --(2.806,3.683)--(2.842,3.719)--(2.878,3.755)--(2.915,3.792)--(2.951,3.828)--(2.987,3.864)%
  --(3.023,3.900)--(3.060,3.937)--(3.096,3.973)--(3.132,4.009)--(3.168,4.045)--(3.205,4.082)%
  --(3.241,4.118)--(3.277,4.154)--(3.313,4.190)--(3.350,4.227)--(3.386,4.263)--(3.422,4.299)%
  --(3.458,4.335)--(3.495,4.372)--(3.531,4.408)--(3.567,4.444)--(3.603,4.480)--(3.640,4.517)%
  --(3.676,4.553)--(3.712,4.589)--(3.748,4.625)--(3.784,4.661)--(3.821,4.698)--(3.857,4.734)%
  --(3.893,4.770)--(3.929,4.806)--(3.966,4.843)--(4.002,4.879)--(4.038,4.915)--(4.074,4.951)%
  --(4.111,4.988)--(4.147,5.024)--(4.183,5.060)--(4.219,5.096)--(4.256,5.133)--(4.292,5.169)%
  --(4.328,5.205)--(4.364,5.241)--(4.401,5.278)--(4.437,5.314)--(4.473,5.350)--(4.509,5.386)%
  --(4.546,5.423)--(4.582,5.459)--(4.618,5.495)--(4.654,5.531)--(4.691,5.568)--(4.727,5.604)%
  --(4.763,5.640)--(4.799,5.676)--(4.836,5.713)--(4.872,5.749)--(4.908,5.785);
\gpcolor{color=gp lt color border}
\draw[gp path] (1.320,2.197)--(1.500,2.197);
\node[gp node right] at (1.136,2.197) {1};
\draw[gp path] (1.320,2.744)--(1.500,2.744);
\node[gp node right] at (1.136,2.744) {10};
\draw[gp path] (1.320,5.481)--(1.500,5.481);
\draw[gp path] (1.320,5.785)--(1.500,5.785);
\node[gp node right] at (1.136,5.785) {1h};
\draw[gp path] (1.320,2.197)--(1.500,2.197);
\draw[gp path] (1.320,2.362)--(1.410,2.362);
\draw[gp path] (1.320,2.580)--(1.410,2.580);
\draw[gp path] (1.320,2.691)--(1.410,2.691);
\draw[gp path] (1.320,2.744)--(1.500,2.744);
\draw[gp path] (1.320,2.909)--(1.410,2.909);
\draw[gp path] (1.320,3.127)--(1.410,3.127);
\draw[gp path] (1.320,3.238)--(1.410,3.238);
\draw[gp path] (1.320,3.292)--(1.500,3.292);
\node[gp node right] at (1.136,3.292) {$10^{2}$};
\draw[gp path] (1.320,3.456)--(1.410,3.456);
\draw[gp path] (1.320,3.674)--(1.410,3.674);
\draw[gp path] (1.320,3.786)--(1.410,3.786);
\draw[gp path] (1.320,3.839)--(1.500,3.839);
\node[gp node right] at (1.136,3.839) {$10^{3}$};
\draw[gp path] (1.320,4.004)--(1.410,4.004);
\draw[gp path] (1.320,4.221)--(1.410,4.221);
\draw[gp path] (1.320,4.333)--(1.410,4.333);
\draw[gp path] (1.320,4.386)--(1.500,4.386);
\node[gp node right] at (1.136,4.386) {$10^{4}$};
\draw[gp path] (1.320,4.551)--(1.410,4.551);
\draw[gp path] (1.320,4.769)--(1.410,4.769);
\draw[gp path] (1.320,4.880)--(1.410,4.880);
\draw[gp path] (1.320,4.933)--(1.500,4.933);
\node[gp node right] at (1.136,4.933) {$10^{5}$};
\draw[gp path] (1.320,5.098)--(1.410,5.098);
\draw[gp path] (1.320,5.316)--(1.410,5.316);
\draw[gp path] (1.320,5.428)--(1.410,5.428);
\draw[gp path] (1.320,5.481)--(1.500,5.481);
\draw[gp path] (1.320,5.645)--(1.410,5.645);
\draw[gp path] (1.320,2.197)--(1.320,2.377);
\node[gp node center] at (1.320,1.889) {1};
\draw[gp path] (1.867,2.197)--(1.867,2.377);
\node[gp node center] at (1.867,1.889) {10};
\draw[gp path] (4.604,2.197)--(4.604,2.377);
\draw[gp path] (4.908,2.197)--(4.908,2.377);
\node[gp node center] at (4.908,1.889) {1h};
\draw[gp path] (1.320,2.197)--(1.320,2.377);
\draw[gp path] (1.485,2.197)--(1.485,2.287);
\draw[gp path] (1.703,2.197)--(1.703,2.287);
\draw[gp path] (1.814,2.197)--(1.814,2.287);
\draw[gp path] (1.867,2.197)--(1.867,2.377);
\draw[gp path] (2.032,2.197)--(2.032,2.287);
\draw[gp path] (2.250,2.197)--(2.250,2.287);
\draw[gp path] (2.361,2.197)--(2.361,2.287);
\draw[gp path] (2.415,2.197)--(2.415,2.377);
\node[gp node center] at (2.415,1.889) {$10^{2}$};
\draw[gp path] (2.579,2.197)--(2.579,2.287);
\draw[gp path] (2.797,2.197)--(2.797,2.287);
\draw[gp path] (2.909,2.197)--(2.909,2.287);
\draw[gp path] (2.962,2.197)--(2.962,2.377);
\node[gp node center] at (2.962,1.889) {$10^{3}$};
\draw[gp path] (3.127,2.197)--(3.127,2.287);
\draw[gp path] (3.344,2.197)--(3.344,2.287);
\draw[gp path] (3.456,2.197)--(3.456,2.287);
\draw[gp path] (3.509,2.197)--(3.509,2.377);
\node[gp node center] at (3.509,1.889) {$10^{4}$};
\draw[gp path] (3.674,2.197)--(3.674,2.287);
\draw[gp path] (3.892,2.197)--(3.892,2.287);
\draw[gp path] (4.003,2.197)--(4.003,2.287);
\draw[gp path] (4.056,2.197)--(4.056,2.377);
\node[gp node center] at (4.056,1.889) {$10^{5}$};
\draw[gp path] (4.221,2.197)--(4.221,2.287);
\draw[gp path] (4.439,2.197)--(4.439,2.287);
\draw[gp path] (4.551,2.197)--(4.551,2.287);
\draw[gp path] (4.604,2.197)--(4.604,2.377);
\draw[gp path] (4.768,2.197)--(4.768,2.287);
\draw[gp path] (1.320,5.785)--(1.320,2.197)--(4.908,2.197);
\node[gp node center] at (3.114,5.426) {33\% Labelled};
%% coordinates of the plot area
\gpdefrectangularnode{gp plot 1}{\pgfpoint{1.320cm}{2.197cm}}{\pgfpoint{4.908cm}{5.785cm}}
\draw[gp path] (6.780,5.785)--(6.780,2.197)--(10.368,2.197);
\node[gp node center,rotate=-270] at (5.706,3.991) {Clique Runtime (ms)};
\node[gp node center] at (8.574,1.427) {MAC Runtime (ms)};
\begin{scope}
\clip (6.780,5.785) rectangle (10.368,2.197);
\def\gprawrgbimagedata{%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffffffac88ffac88ffac88%
  ffac88ffac88ff8c72ffffffffac88ff9576ff9f7dff8c72ff7869ff7e6cff7367ff6f65ff8c72ff9576ff6f65ffac88%
  ff846eff846eff9576ff7e6cff7e6cff6f65ff7869fc6260fc6260ff7869fe6862fe6862fc6260f85a5dfb605ff34e5a%
  f7565cfa5e5ff5535bf5515bf04557ec4055ea3d54e83b53e93c53e23450e53651db2a4cdc2b4cd9274bdb2a4cd7254a%
  d8264ad32047d32048d11f468b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
  ffac88ffffffffffffff9576ffac88ffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffff9576ff9f7dff9576ff8c72ff9f7dff9576ffac88ff9f7dff7e6cff9f7dff9f7dffac88%
  ffac88ff7367ff846efe6862ff8c72ff7e6cff846eff846eff7367ef4356ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffff9f7dff9f7dffffffffffffff9f7dffffffffffffffac88ffffffff9f7dff9f7dff846eff8c72ff9f7d%
  ff8c72ff9576ff9f7dff7869ffffffffac88ff6f65ff7869ff8c72ff9f7dff7869ff9f7dff7e6cff7869f5515bffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dffffffff9f7dffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffff9f7dff9f7dffffffffffffffac88ffffffffffffff9f7d%
  ffac88ffac88ff9f7dff9f7dff9576ff9576ff846eff7e6cff9f7dff8c72ffffffff7869ff8c72ff7869ff7367ff9f7d%
  ff9576fa5e5fff7e6cfd6561ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffac88ffac88ffffff%
  ffffffff9f7dffffffffac88ffffffffac88ffffffff9f7dff9576ffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffffffffffffff9f7dffac88ff9576ff846eff9576ff9576ff9f7dff9576ff8c72ff9576ffac88ff7e6cff6b63%
  ffac88ff846eff7e6cffffffff9f7dff6f65ff7367ff846efd6561ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffff%
  ffffffffac88ffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ff9f7dff9576ffac88ffac88ff9f7dff7e6cffac88ff9f7dff846eff8c72ff8c72%
  ff8c72ff846eff7869ff846eff8c72ff9576ff8c72ff7e6cffac88ff7367ff8c72ff7367ff7e6cfd6561ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffff9f7dffac88ff9f7dffffffffffffffffffff9f7dffac88ffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffff9f7dffac88ffac88ff9f7dffac88ff9f7dffac88ffac88ffffffff8c72ff9576ff8c72%
  ff9576ff9f7dff9576ff6b63ff846eff7e6cff8c72ff7869ffffffff7e6cff8c72ff7e6cff7e6cff8c72ff8c72ff7367%
  ff7e6cff9576ff7869ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffffffffac88ffffffffffffff9f7dffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffff9f7dff9f7dff9f7d%
  ff9576ff9576ff7e6cffac88ff8c72ff9f7dff846eff6b63ff9f7dff7869fd6561ff7e6cff846eff7869ff9576ff9576%
  ff846eff7869ff7869ff7e6cff9f7dff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffac88ffac88ffffffff9f7dffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88%
  ff7e6cffac88ff9f7dff9f7dff9576ff9f7dfe6862ff8c72ff7367ff846efd6561fc6260ff8c72fc6260ff6b63ff7869%
  ff7367ff9576ff7e6cff8c72ffac88ff8c72ffac88ff7e6cff9576ff8c72ff9576ffac88ff9576ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffffffffffac88%
  ffac88ffffffff9f7dffffffff846effac88ff9576ffffffff8c72ffac88ff8c72ffac88fd6561ff8c72ff8c72ff7367%
  ff7367ff7869ff7367ff6f65fe6862ff6b63fd6561ff7367ff9576ff7869ff9576ff846eff846eff9f7dff9f7dff9576%
  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffac88ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffff%
  ffffffff9576ff9f7dffac88ff9f7dffffffff9576ffffffff9f7dff846eff9f7dff9f7dff9576ff9576ff8c72ff846e%
  ff846eff7367ff6b63ff6b63fc6260ff846efd6561ff6b63fb605ff95c5ef7585dff6b63ff7367ff7e6cff8c72ff9f7d%
  ff9f7dff9576ffffffff846eff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffff8c72ff9f7dffffffff9f7dff9576%
  ff846eff9f7dff8c72ffac88ff7e6cff846efe6862fd6561fe6862ff7367ff6b63f7565cf7585dff6b63fc6260fb605f%
  ff6b63ff7e6cff7e6cff8c72ff846effac88ffffffff7e6cffffffff9f7dffac88ff9576ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffff9f7d%
  ffac88ffffffff8c72ffac88ff9f7dff7869ff6b63ff9576ff9576ff7e6cff7e6cff6f65fe6862fd6561f7565cf95c5e%
  fa5e5ff24b59f7565cf34e5afd6561fc6260ff7869fe6862ff9f7dff846eff9f7dffac88ffac88ffffffffac88ffffff%
  ff6b63ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffac88ffac88ff9576ffac88ffffffffffffffffff%
  ffac88ffac88ffffffff9576ffffffff9576ff9576ffffffff8c72ff9576ff846eff8c72ffffffff8c72ff7869fd6561%
  ff846eff6f65fe6862fd6561f85a5df7565cff6b63fd6561f6545cfd6561f85a5dff846eff9576ff8c72ff9f7dff9f7d%
  ffac88ff9f7dffffffffffffff9576e93c53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffac88ff9f7dffac88ffac88ff9f7d%
  ffffffffffffffffffff846effac88ffffffffffffffac88ff9f7dff7367ffac88ff9f7dff846eff8c72ff8c72ff9f7d%
  ff846eff846eff9576ff7e6cff7869f95c5efa5e5ffe6862fb605ff85a5dfd6561fb605fff7e6cf85a5df95c5efd6561%
  ff7e6cff7869ff846eff9576ffac88ff9576ff9f7dff9576ffac88ff9f7de33550ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9576ffffffffffffff9f7d%
  ffffffffffffff9576ffffffffac88ffffffffffffffac88ffac88ffac88ff9f7dffffffff9f7dff9576ff9f7dffac88%
  ffac88ff9f7dff8c72ff8c72ff846eff7367ff7e6cff9576ff7869ff6b63fa5e5ffc6260f4505afa5e5ff5515bf5535b%
  f95c5efb605ff5515bf4505afb605ffc6260ff846eff9576ffac88ffac88ffffffffffffff9f7dff8c72ff7e6ce83a53%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffffac88%
  ffffffff8c72ffac88ffac88ffffffffac88ffffffff9f7dff9f7dffffffffac88ff9576ffffffff9f7dffac88ff9576%
  ff846effac88ff9f7dff8c72ffac88ff9576ff8c72ff8c72ff7869ff8c72ff7367ff846eff7869ff7e6cff7e6cff6b63%
  ff6b63fe6862f6545cf7565cfe6862f7585df7585df5535bfe6862fc6260ff7e6cff8c72ffac88ff9f7dff9f7dff9f7d%
  ffac88ff8c72ff846efe6862f14858ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffffffffffffffffff%
  ffac88ffac88ffffffffffffff9f7dffac88ffac88ffac88ffffffffac88ff9576ffffffff9f7dffac88ffffffffac88%
  ff9f7dff9f7dffac88ffac88ff9576ff8c72ff9f7dff9f7dff9f7dff8c72ff9f7dff7e6cffffffff7367ff8c72ff7e6c%
  ff846eff7e6cfa5e5ffe6862ff7367fe6862f85a5dfd6561fb605ffb605ff5535bf5535bf7585dfb605fff846eff7869%
  ff846eff8c72ff9576ffffffff846eff9f7dff7e6cff7e6cfe6862fb605fffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffffffffffff%
  ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffffac88ffac88ff9f7dff9f7dff846eff9576ff9f7d%
  ff9f7dff8c72ff7869ff846eff8c72ff7869ff7869ff7869ff7869fd6561fd6561f34e5af7585dfd6561f4505af95c5e%
  fc6260fa5e5ffc6260ff7e6cff8c72ff846effac88ffac88ff9f7dff9f7dff9f7dff7e6cff7e6cff7367ff9576ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffffffffac88%
  ffffffffffffff9f7dffffffff9f7dffffffffac88ffac88ffac88ffffffffac88ffac88ff8c72ff9f7dff9f7dff846e%
  ffac88ffac88ff7e6cff9f7dff9f7dff846eff9576ff9f7dff8c72ff7869ff6f65ff7869ff7e6cff7869fe6862fb605f%
  fe6862fa5e5ffb605ffd6561f85a5dfd6561ff7869ff7869ff846eff8c72ff9576ff846eff9f7dffac88ff9f7dff9f7d%
  ff9f7dff9f7dff9f7dff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
  ff9f7dffffffff8c72ff9576ff9f7dffffffffffffff9f7dff9f7dffac88ff9576ff9f7dffffffff9f7dffffffffac88%
  ff9f7dffac88ff9f7dff9576ff8c72ff9f7dff9f7dff8c72ff7869ff9f7dff7869ff9576ff846eff7869fa5e5fff9576%
  ff7e6cff7869ff7869fe6862fd6561fb605ffa5e5ff95c5ef7565cf7585dfa5e5fff7869fe6862ff9576ffac88ff9576%
  ffffffffac88ff9f7dffac88ffffffff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff9f7dff9576ff9f7dffffffffac88ffffffffac88ffac88%
  ff9f7dff9f7dffffffffffffff9f7dffac88ffac88ffffffff9576ffffffffac88ff7869ff9576ff9f7dffac88ff9576%
  ff7869ff7e6cff9576ff9f7dff6f65ff7869fb605fff7e6cff6f65fd6561fb605ffb605fff7e6cff7869fe6862ff6b63%
  ff846eff7869ffac88ff846eff9f7dff9f7dff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dffac88ff7e6cff8c72ffac88ff846eff846effac88%
  ffffffffac88ff9f7dffffffffac88ffffffffac88ffffffffffffffffffffac88ff9f7dff8c72ffffffff846eff9f7d%
  ff9576ff8c72ff9576ff9576ff7e6cff9576ff9576ff846eff7e6cff6f65fd6561ff6f65fe6862fc6260fe6862ff7367%
  fd6561ff6f65ff6b63ff9576ff9576ff7e6cff9576ffac88ffffffff9f7dff9f7dffac88ffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9576ff9f7dff9f7dff8c72%
  ffac88ff7869ffac88ff9f7dffac88ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff846e%
  ffac88ffac88ff9576ff8c72ff9576ffffffff9f7dff9f7dff846eff9f7dff8c72ff9f7dff8c72ff8c72ff846eff846e%
  ff7869fc6260fa5e5fff6b63fd6561ff6f65ff7367ff7e6cff846effac88ff846effac88ff8c72ffac88ffac88ff9576%
  ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffff%
  ff9f7dff9f7dff8c72ff9f7dffac88ff9576ff8c72ff8c72ff7e6cff9f7dff9576ff9f7dffffffffac88ffac88ff9f7d%
  ffffffffffffff9f7dffffffffffffffffffff7869ffac88ff7e6cff9f7dffffffff9f7dff7e6cff9576ff8c72ffac88%
  ff8c72ff8c72ff6f65ff9576ff7367ff6f65ff7367ff7869fc6260ff7e6cff7367ff6f65ff7e6cff7e6cff7e6cff8c72%
  ff9f7dff9f7dffffffffac88ffffffff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88%
  ffffffff9f7dffac88ffac88ffac88ffac88ff9f7dff8c72ff9f7dff8c72ff7e6cff8c72ffac88ffac88ff9576ffac88%
  ffac88ff9f7dffac88ff9f7dffffffffac88ffac88ff9576ff9f7dff8c72ff8c72ff9f7dffffffff8c72ff9f7dffffff%
  ff846eff8c72ff7367ff8c72ff9f7dff9576ff7e6cff7367ff9576ff6f65fd6561ff9576ff6f65ff6f65ff7367fe6862%
  ff7e6cff8c72ff8c72ff9576ff9576ff8c72ffac88ffac88ff9f7dff9f7dffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffff9f7dffffffff9f7dffffffffffffff8c72ffac88ff7e6cff8c72ff8c72ff9576ff846e%
  ffac88ff846effffffffffffff8c72ffffffffffffffac88ffffffff9576ffffffffffffffac88ffac88ff8c72ff9576%
  ff9f7dff9f7dffac88ff8c72ff9f7dff7e6cff7869ff9f7dff9f7dff8c72ff846eff9576ff7367ffac88ff7367ff7367%
  fe6862ff7367ff6b63fe6862ff6f65ff6f65ff9f7dff9f7dff846eff9576ff9f7dff9f7dff9f7dff9f7dffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff8c72ffffffff7869%
  ff846eff8c72ff9576ff8c72ff9576ffffffff9f7dffffffff9f7dffac88ffffffffffffffffffffac88ff9f7dffac88%
  ff9f7dff9f7dff9f7dff8c72ff9576ff9f7dff9576ff9576ff8c72ff6b63ff9f7dff6f65ff9576ff6f65ff846eff8c72%
  ff9576ff8c72ff846eff9576fd6561fd6561ff8c72ff8c72ff9576ff846eff7e6cff6f65ff9576ffffffffac88ffac88%
  ff9f7dffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9f7dff9576ffac88ffac88ff9f7d%
  ffac88ff8c72ff9f7dffac88ffac88ff9f7dff9576ffac88ffac88ff8c72ff9f7dffffffffac88ff9f7dffffffffac88%
  ff9f7dff8c72ffffffff9f7dff9576ffac88ff9576ffac88ff9f7dff9576ff8c72ff9576ff9f7dff9f7dff7e6cff6f65%
  ff7869ff7869ff7e6cff8c72ff7e6cff8c72ff9576ff7e6cff8c72ff846eff7869ff6f65ff6f65ff7e6cff6b63ff7869%
  ff846eff9f7dff9f7dff9f7dff9f7dff9f7dffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffac88ffac88ff9f7dffac88ff9f7dffffffffac88ff8c72ff9f7dffac88ff9576ff8c72ff8c72%
  ff9f7dff9f7dff9f7dffac88ffffffffffffffac88ff9f7dff8c72ffffffff9f7dffac88ff9576ffac88ff9576ff9f7d%
  ff8c72ff9576ff7e6cff7367fd6561ff9f7dff7869ff9576ff846eff8c72ff846eff8c72ff7e6cff8c72ff7869ff846e%
  ff7e6cff6f65ff7367ff9576ff846eff846eff9576ff7e6cffffffff9f7dff8c72ffac88ffac88ffac88ffffffffffff%
  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffffff9576ff9576ffac88ff9576ff9f7d%
  ff9576ffac88ffac88ffac88ffac88ffffffffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffff8c72ff9f7d%
  ff9576ffffffff9f7dff846effac88ff8c72ff9576ff7367ff7869ff8c72ff8c72ff7367ffac88ff846eff8c72ff9f7d%
  ff8c72ff9576ff7e6cff7e6cffac88ff9f7dfb605fff846eff9f7dff8c72ff9576ff9576ff9f7dff7e6cff8c72ffffff%
  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffff9f7dff9f7dffac88%
  ffac88ffac88ffffffff9f7dffac88ffac88ffac88ff9f7dffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
  ffac88ff9f7dffac88ffac88ffac88ffac88ff9576ff9f7dff9576ff8c72ffac88ff9576ff9576ff7e6cff7869ff8c72%
  ff6f65ff9576ff8c72ff7e6cff9576ff8c72ff846eff8c72ffac88ff7e6cff8c72ff6f65ff8c72ff9f7dff8c72ff7367%
  ff9576ff846ef6545cff7e6cffac88ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
  ffac88ff8c72ffac88ff9f7dff846effffffffffffffffffffac88ffffffffac88ff9f7dff9576ff9576ff9576ff7e6c%
  ffffffffac88ffac88ffffffffffffff9576ff9f7dff846eff9576ffac88ff8c72ff9576ff846eff8c72ff9576ff7869%
  ff9f7dff9576ff7e6cff9576ff8c72ff7869ff9576ff9f7dffffffff846eff7367ff7869ff7e6cff846eff9f7dff7e6c%
  ff846eff9576ff9576ff6f65ff7367ff846ef6545cf95c5eff9f7dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffac88ffac88ffac88ff9f7dffac88ffac88%
  ffffffff8c72ff7869ff6f65ff7e6cff9f7dff8c72ffac88ff9f7dffffffff7869ffffffff9f7dffac88ff9576ff846e%
  ff8c72ff8c72ff7367ff7367ff7367ff6f65ff9576ff846eff9576ff846eff7367ff8c72ff8c72ff8c72ff9f7dff9576%
  ff7e6cff846eff7e6cff8c72ffac88ffac88ff8c72ff7e6cfa5e5ffd6561fd6561f24a59ff7e6cffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9f7dffffffffffffff9f7dff9f7d%
  ffffffffac88ff9576ffac88ffffffffffffff9576ff8c72ff6f65fe6862ff8c72ff9f7dff9576ffffffffffffff8c72%
  ff8c72ff8c72ff846eff8c72ffac88ff8c72ff9576ff7367ff846eff9576ff7367ff7e6cff7869ff846eff9f7dff846e%
  ffac88ff9f7dff846eff7e6cff8c72ff846eff7367ff9f7dff846eff846eff9f7dff7e6cff7367f7565cfe6862ff7367%
  ff7367ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
  ffac88ffffffffac88ffffffffffffffac88ffffffffac88ffffffff9576ffffffffac88ff9576ff7e6cff846effffff%
  ffac88ff9f7dff9576ffac88ff9f7dff9576ffac88ff7e6cff846eff7869ff7869ff6b63ff846eff6f65fe6862ff6b63%
  ff7869ff6b63ff7e6cff6f65ff7869ff8c72ff7e6cff9576ff7e6cff8c72ffac88ff9f7dffffffffffffff8c72ffac88%
  ff7e6cff6f65ff6b63ff846eff7e6cffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ff9f7dff9f7dffac88ffac88ffffffffffffff9f7dffffffffac88ffac88ffffffffac88ffac88ff9f7dffffff%
  ffffffff9f7dffac88ffffffff9576ffffffffffffffffffffac88ffffffff9f7dffac88ff7e6cff9576ff846eff7e6c%
  fd6561ff7367fc6260ff6f65fe6862ff6b63ff6f65ff6b63ff7367ff846eff8c72ff9f7dff9576ff9576ffac88ff846e%
  ff9f7dffffffffac88ffac88ff9f7dff8c72ff8c72ff846eff9576ffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffffffff9f7dffffffffac88ffac88ffffff%
  ffac88ffffffffac88ffac88ffac88ff9576ff9576ff9f7dffac88ff9f7dff9f7dff9576ff8c72ffac88ff9576ff8c72%
  ff9576ff8c72ff7869ff7367fd6561fa5e5fff6b63ff6f65f95c5efd6561f6545cf85a5df5515bfa5e5fff6f65ff7869%
  ff9576ff8c72ff9f7dff846eff8c72ff9f7dff8c72ff9576ffffffffffffffffffff9f7dffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
  ff9f7dffac88ffac88ff7e6cffac88ff9f7dffffffff9f7dffffffffffffffffffff9f7dffffffffac88ffac88ff9f7d%
  ff9f7dffffffffac88ff7869ff7e6cff846eff7869ff846eff846eff6f65fc6260f95c5efc6260f85a5df34d59f6545c%
  f4505af5535bfd6561ff7e6cff7869ff7e6cff846effac88ffac88ffac88ff9f7dffac88ffac88ffac88ff9f7dffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88%
  ffffffffffffffac88ffffffffac88ffffffffffffffac88ffffffff9f7dffac88ffac88ffffffffffffffac88ffffff%
  ff9f7dffac88ffffffffac88ff9576ff7e6cff9f7dff9f7dff9576ffac88ff8c72ff7869fe6862ff6f65ff7367ff6f65%
  fa5e5ff85a5df34d59fb605ffa5e5ff7585dfc6260f95c5eff6f65ff6b63ff9576ff9f7dff9f7dffac88ffffffffac88%
  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffffffff9f7dffffffffac88ffffff%
  ffac88ffac88ffac88ffffffffffffffffffffffffffffffffac88ffac88ff9f7dff846eff7e6cff7367ff7e6cff8c72%
  ff7869ff846eff7367fd6561f95c5ef7585df7565cf4505af6545cf5515bf4505af85a5dfe6862ff8c72ff9576ff7869%
  ff9f7dff8c72ff9f7dffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88%
  ffac88ffac88ff9f7dffffffffffffff9f7dffffffffffffffffffffffffffac88ff9576ff9f7dff9576ffac88ffffff%
  ffac88ffac88ff6f65ff8c72ff846efd6561ff7869fb605ff7585df5515bfc6260f34e5af7585df6545cf4505af7565c%
  f95c5eff6b63ff7e6cff9576ff846eff8c72ff9f7dff7869ffffffffffffffac88ffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffac88ff9f7dffffffff9f7dff9f7dff9f7dffffffff846effac88ffffffffffffffffffffac88ffac88ff9576%
  ffac88ffffffff9f7dff9576ff8c72ffffffff7e6cff846eff7869ff7367fe6862ff7e6cf5535bfd6561f34e5afb605f%
  f5515bf7585df4505af5515bf5515bff6b63ff6f65ff8c72ff9576ff9f7dff9f7dffac88ffac88ffac88ffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ff9f7dff8c72ff9f7dff9f7dffac88ffffffffffff%
  ffac88ffffffffffffffffffffffffff9f7dffac88ffac88ff9576ff8c72ff7869ff846eff8c72ff846eff7869f7565c%
  ff6b63f7585df6545cf6545cf95c5ef24b59f04757f5535bfd6561f5535bfd6561ff7367ff7367ff7e6cff846eff9f7d%
  ff8c72ff8c72ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7dff9f7dff846e%
  ff7e6cff9f7dff9f7dff9f7dffffffffffffffac88ff9f7dffffffff9576ffac88ffac88ff9f7dff9f7dff846eff9f7d%
  ff9f7dff9576ff7869ff7367fc6260fe6862fc6260fa5e5ff34d59fb605ff7565cf5535bf6545cf7585dff7367ff7869%
  ff7367ff7869ff6f65ff7e6cffffffff9f7dff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ff7869ff9f7dff9f7dff9f7dffac88ff9f7dffffffffffffffffffff9f7dffac88ff9576%
  ffac88ff9f7dff846eff9576ff8c72ff7367ff7869ff6f65ff7869ff7e6cfb605ffa5e5ffa5e5ff7585df7565cf5515b%
  f7565cf4505afe6862ff7367ff6f65ff7367ff9f7dffac88ff9576ff9f7dff9f7dff9f7dffffffffac88ffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ff9f7dff9f7dff9f7dffac88ff9f7dff8c72ff7869ff846eff8c72ffffffffffffffac88%
  ffffffffffffffffffff9f7dffffffff8c72ff9576ffffffffac88ff7367ff846eff7367ff846eff7869fc6260f5535b%
  fb605ff85a5df7565cf85a5dfe6862fa5e5ffc6260ff7e6cff846eff7367ffac88ff9f7dffac88ffac88ff9f7dff8c72%
  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff9576ffac88ffac88ff9576ff846effac88ff8c72%
  ffac88ffac88ffac88ffffffffffffffffffff9f7dff9f7dff8c72ffffffffffffff9f7dffac88ff9f7dff7e6cff8c72%
  ff846eff6b63fc6260fe6862f7565cf4505afd6561fa5e5ffa5e5ffa5e5ffd6561ff7367ff8c72ff846eff6f65ff7367%
  ffac88ff9576ffac88ff9f7dffac88ffffffffffffffffffffffffff9576ffffffffac88ffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff9f7dff9576ff8c72ff846e%
  ff8c72ff9f7dff9576ffac88ff9f7dff9f7dffffffffffffffffffff9f7dffffffff9f7dffac88ffffffffac88ff9576%
  ff846eff9576ff8c72ff9f7dff7e6cff7869ff6b63ff7367fd6561f6545cfe6862f95c5ef7565cf5535bff6b63fe6862%
  ff7367ff846eff9f7dff7367f95c5eff7367ffac88ff9f7dff9f7dffac88ff9f7dffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffffffffffff%
  ff9576ffffffff7869ff846eff9576ff9f7dff9f7dffac88ffac88ffac88ffac88ffffffffac88ffac88ff9f7dffac88%
  ff9f7dffac88ff9576ffffffff9576ffac88ffac88ff7e6cff6f65ff8c72ff7869ff9576fd6561f85a5dfb605ffb605f%
  f5515bfb605ffc6260fc6260fb605fff846eff846efc6260f34e5af5535bff9576ff9f7dffac88ffffffffffffff9f7d%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffff9576ffffffffac88ffac88ff9576ff9576ff8c72ffffffff9f7dffac88ffffffff9576ffac88ffac88ff7e6c%
  ff7869ff7e6cff9576ffac88ff9f7dff9576ffac88ffac88ffac88ffac88ffac88ffffffffac88ff9576ffffffff9f7d%
  ff7e6cff8c72ff7367ff6b63fe6862fd6561f7585dfa5e5fff6f65fd6561ff8c72fe6862f7565cea3d54f34d59ff9576%
  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffff9f7dffffffff9576ffac88ff9576ffac88ff9f7dffac88ff9576ff9576%
  ffffffff9576ffffffff6b63ff7869f95c5eff7e6cff7e6cff8c72ff9f7dffac88ffac88ff846eff8c72ff9f7dff9576%
  ff8c72ff9576ff9f7dff8c72ff846eff8c72ff7869ff846eff9576ff7367fc6260fe6862f5535bfe6862ff6f65ff7e6c%
  fe6862f7585def4457ff6b63ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff8c72ffac88ffac88ffac88%
  ff9f7dffffffffac88ffac88ffffffffac88ffac88ffac88ff9f7dff7367ff7e6cff9f7dff9f7dffac88ff9f7dffac88%
  ffffffffac88ff8c72ffac88ff9576ff9f7dff8c72ff9576ff846eff7e6cff7e6cfe6862ff846eff6f65ff6f65ff6f65%
  fd6561fd6561fd6561ff7e6cff9f7dff6b63fd6561ff7e6cff9f7dffac88ffffffffffffffffffffffffffffffffac88%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ff8c72ffffffffac88ffffffff9f7dffac88ffffffffffffffac88ffac88ffffffff9f7dff846eff9576ff9f7dff9f7d%
  ffffffff9f7dffac88ffac88ffffffffffffff9576ffffffff8c72ff9576ff9f7dffac88ff9f7dff9576ff9576ff9576%
  fd6561fd6561ff7869ff7e6cff7e6cf7565cff7367ff7869ff6f65ff8c72ff9576ff8c72ff9576ffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ffffffff9f7dffffffffffffffffffffac88%
  ffac88ff9f7dff9f7dff9f7dffac88ffac88ffffffffffffff9f7dff8c72ffac88ffac88ffac88ff9576ff7e6cff6b63%
  ff9f7dff9576ff9f7dff8c72ff9576ff9576ff846eff7367ff7e6cff7367ff7869ff8c72ff7869ff8c72ffac88ff9576%
  ff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffac88%
  ffac88ffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffffffffff9f7dffffffff9f7dffac88ff8c72ff9f7d%
  ff9576ff9576ff7869ff846eff9f7dff9f7dffffffff7e6cff9f7dff7e6cff846eff6b63ff6f65ff7e6cffac88ff846e%
  ff8c72ff9576ff7e6cffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9576ffffffffac88ffffffffac88ffffffff9576ffac88ff9f7dff9f7dffac88ff9f7dffffff%
  ff9f7dffac88ff9576ff9576ff9576ff9f7dff9576ff8c72ff8c72ff9576ff7367ff7367ff7e6cff7869ff8c72ff8c72%
  ff7869ff7e6cff846effac88ffac88ff9f7dff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ff9f7dffac88ffac88ffffffffffffffac88ffac88%
  ff846effac88ffffffffac88ffffffff9f7dffac88ffac88ff9f7dff846effac88ff9576ff8c72ff8c72ff7869ff9f7d%
  ff8c72ffac88ff7e6cff6f65ff7e6cff846eff846eff6f65ff846effac88ffac88ffac88ffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffff%
  ff9f7dffac88ffffffff9576ff8c72ffac88ff846eff9f7dffac88ff9f7dff9f7dff8c72ff9576ff9576ff9f7dffac88%
  ff8c72ff9f7dff9f7dff9f7dffac88ffac88ff9f7dff9576ff8c72ff9576ff7e6cff846effffffff9f7dff9f7dffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffac88ffac88ff9576ff9f7dff846eff9f7dff9576ff8c72ffac88ff9576ff8c72ffac88ff9576ff9f7dffac88%
  ff9f7dff8c72ff9f7dff6f65ff8c72ff8c72ff9576ff846eff9576ffac88ffac88ff7e6cff8c72ff8c72ff7e6cff7869%
  ff9f7dff8c72ffffffffac88ffac88ffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7dff8c72ff7869ff7367ff7e6cff9f7dffffffff8c72ff846e%
  ff9f7dffac88ffffffffffffffffffff846eff7e6cff7e6cff9576ff8c72ffac88ff846eff9f7dff846effffffff9f7d%
  ff7869ffac88ff9f7dff8c72ffac88ffac88ffac88ff9576ffac88ffac88ffac88ffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff7869ff8c72ff7367fa5e5f%
  ff9f7dffac88ff9f7dffffffff9576ffac88ffac88ff9576ff8c72ff9f7dff9f7dff7e6cff7869ff7e6cff8c72fb605f%
  ff846eff846effac88ff846eff846effac88ff9576ffac88ff9f7dffac88ffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffff%
  ff9576ffffffff7367ff7869ff7e6cff8c72ff846eff9f7dff846eff9f7dffac88ff9576ff8c72ff8c72ff9576ff846e%
  ff8c72fc6260ff7367fb605ffc6260ff7367fe6862ff6f65ff846eff8c72ff7e6cff9f7dffffffff9f7dffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffac88ff8c72ff8c72ffffffff8c72ff846eff7e6cff8c72ff9576ff9576ff9576ffffffffffffffffff%
  ff846eff9576ff846eff7e6cfb605ffe6862fd6561f95c5ef6545cfb605fff6b63f7565cff7869ff846effffffff8c72%
  ff8c72ffac88ffac88ffac88ffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff7e6cff9f7dff9576ff9576ffffffffac88ff9576%
  ff9576ff9576ff8c72ff7367ff7e6cff9576ff8c72ff9576f6545cff6b63f14958f95c5ef14958fc6260f5535bf4505a%
  fa5e5ff95c5eff8c72ff846eff9576ff9f7dffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff9f7dff9f7d%
  ff9f7dffac88ff9f7dff8c72ffac88ff846effac88ff9576ff7869ff8c72ff6f65ff6f65ff7869fb605ffb605ff24a59%
  f5515bf24a59fa5e5ff5515bf95c5eff7869ff7367ff8c72ffac88ffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffffffffffffffac88ff9576%
  ffffffffac88ff8c72ffac88ff9576ffac88ff846eff9f7dff9576ff9f7dff8c72ff846eff7e6cff7869ff9f7dff9f7d%
  fc6260ff6b63f85a5df6545cf7565cf14958ef4457f14958fa5e5ffe6862ff6b63fd6561ff9f7dffac88ffac88ffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffac88ffffffffffffffac88ff9576ff8c72ff6b63fa5e5ff5535bff7869ff7869ff7e6c%
  ff6f65ff7367ff7367ff7367ff7367ff6f65ff6f65f85a5df24b59f4505af04757f04557f24b59f4505aff6b63ff8c72%
  ff8c72ff8c72ff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9576ff7e6cfb605f%
  f34d59f7585dfc6260ff7e6cff7869ff6b63ff7869fd6561fc6260ff7e6cf95c5eff6b63f5535bf6545ced4155ef4457%
  f34e5af6545cf5535bfd6561fe6862ff846eff7869ff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9576ff9f7dffffffff9576ffac88%
  ff9576ff8c72ff7e6cff6f65ff7869ff8c72ff6b63ff7869fc6260ff6f65ff7869ff6f65fc6260fc6260f95c5eff6b63%
  f34e5af4505af14958ef4356f4505af34e5af14958f34e5af7565cfe6862ff9576ff7869ff9f7dffac88ffffffffffff%
  ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
  ff9576ff846effac88ffffffff846eff8c72ff7367ff7367fd6561ff7869ff6f65ff7869ff7367ff7e6cff7e6cf85a5d%
  fb605fff7367f6545cf95c5ef85a5df85a5df7565cf24a59f5515bf7585df34e5af24a59ef4457fe6862ff6b63ff6f65%
  ff846effffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
  ff9f7dffffffffffffffffffff9576ff9f7dffac88ffac88ffac88ff6f65ff8c72ff9576ff9f7dff7367fe6862ff7367%
  ff7869ff7869ff7869fe6862ff7869ff6b63ff8c72fb605ffe6862f85a5df7565cfa5e5ff04757f6545cf34d59f14858%
  e73952f24b59fd6561ff8c72ff9576ff9f7dffffffff9576ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffff9f7dffac88ff9576ffac88ff7e6cff846eff8c72ff846eff7869ff7e6cff9f7d%
  ff9576ff6f65fd6561ff6b63ff8c72fe6862ff8c72ff846eff7e6cfe6862ff6f65ff7869fd6561fc6260f7565cf95c5e%
  f14858f34d59f7585df95c5ef24a59f7585df7585dff6b63ff9576ff9576ffffffffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ffffffff7869ff846eff8c72ff8c72%
  ff8c72ff7869ff846eff846eff7869ff7367fe6862ff7367ff9576fc6260ff846efe6862f7585dfe6862ff7367fe6862%
  f95c5efe6862f85a5df5535bf7565cf24b59f5535bf7585df7585df95c5eff6f65ff8c72ff9576ff7e6cffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff846effac88ff9576%
  ff846eff7869ff9576ff846eff7367ff7e6cff9576ff846eff7e6cff7869ff6b63ff6b63ff7869fe6862f85a5dff6b63%
  ff6f65ff7367fa5e5ff6545cf95c5efa5e5ff5535bf85a5df5515bf7585def4356f85a5df7585dfd6561fe6862ff8c72%
  ff9f7dffac88ff9f7dffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffac88ffac88ffac88ff9f7dffffffffac88ff846eff9576ff8c72ff9576ff7e6cff846eff7e6cff846eff7869ff6b63%
  ff846eff846eff846efc6260fe6862fd6561fb605ff4505afd6561f7585df7565cfd6561fc6260f95c5ef6545cfe6862%
  ff7367ffac88ffac88ffffffffac88ff9f7dffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9f7dffffffffac88ffac88ffac88ffffffff846eff7e6cff6f65ff9576ff8c72ff7869ff6f65%
  ff7367ff9576ff7e6cff7367ff7367ff6f65fe6862fc6260ff6b63f7565cf85a5df34e5af7565cf24a59f7565cff6f65%
  fa5e5ffa5e5ffb605fff7e6cff9576ff7869ff8c72ffffffffffffff9f7dffac88ffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576ffffffff7e6cff7367fc6260%
  fa5e5ffa5e5ffc6260f7585df95c5eff7e6cff846eff8c72ff6f65ff7e6cfe6862fd6561fc6260fd6561f5535bf85a5d%
  f7565cfb605ffe6862ff7367ff7869ff7869ff8c72ff7e6cff846eff9f7dffac88ff9576ffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
  ffffffff9576ff9f7dff8c72ff7367ff9576ff6b63fd6561f7585df7565cff9576ff7869ffac88ff8c72ff846eff9576%
  ff6f65ff7869ff6f65ff6b63ff846eff9576ff846eff9576ff9f7dffac88ffac88ff9576ff9576ffffffffac88ffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffac88ff9576ff6f65ff9576ff7869f95c5ef34e5af04557fd6561%
  ff7869ff7367ff9f7dffac88ff846effac88ff9f7dff9f7dffac88ffac88ff9f7dffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffac88ffac88ffac88ffffffffffffffffffffffff%
  ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9f7dffac88ffffffffac88ffac88ff9f7d%
  ffac88ffffffffac88ffac88ff9f7dff9576ff9576ff7869ffffffff8c72ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff8c72ffac88%
  ffffffffffffffac88ff9f7dff9f7dffffffffac88ff9f7dff9576ff846eff7869ff6f65ff7367ff846eff8c72ffac88%
  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ff8c72ff7869ff6f65ff7e6cff8c72ff7e6cff7e6cf95c5eff6b63f7585df24b59ef4457e63852e43551df304e%
  e73952e53651f14858f95c5eff6b63ff8c72ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffff9f7dff8c72ff7367ff6b63f7565cf85a5df24b59f14858f14858f4505ae53751%
  ea3d54e33450da294bda2a4cd8274adc2b4cdd2d4dee4156ff6b63ff9576ffac88ff9f7dffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ff8c72ff9576ff7367fe6862f7585dee4256f24a59eb3e54%
  ef4356e73952e23350e23450de2e4ee43651dc2c4cdc2c4cd62449d01d45d52349d9274bf04557fa5e5ffc6260ff8c72%
  ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9f7dff7367ff8c72ff7869%
  f24b59ef4457e63852df304ee0314fe33550ea3d54e2324fe43651df2f4ee0314fe1314fe1314fdf304ee53651eb3e54%
  ff7367ff8c72ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffac88ff9f7dff9576f95c5efd6561fd6561f5515bf95c5efc6260f95c5efa5e5ffe6862fd6561ff7e6cff7869%
  fd6561ff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000%
  ae062ab2072db80c32c1133ac91840ea3d54ff6b63ff7e6cff9f7dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff}%
\gprawimage{rgb}{6.762}{2.179}{101}{101}{3.624}{3.624}{\gprawrgbimagedata}{}
\end{scope}
\gpcolor{rgb color={0.000,0.000,0.000}}
\draw[gp path] (6.780,2.197)--(6.816,2.233)--(6.852,2.269)--(6.889,2.306)--(6.925,2.342)%
  --(6.961,2.378)--(6.997,2.414)--(7.034,2.451)--(7.070,2.487)--(7.106,2.523)--(7.142,2.559)%
  --(7.179,2.596)--(7.215,2.632)--(7.251,2.668)--(7.287,2.704)--(7.324,2.741)--(7.360,2.777)%
  --(7.396,2.813)--(7.432,2.849)--(7.469,2.886)--(7.505,2.922)--(7.541,2.958)--(7.577,2.994)%
  --(7.614,3.031)--(7.650,3.067)--(7.686,3.103)--(7.722,3.139)--(7.759,3.176)--(7.795,3.212)%
  --(7.831,3.248)--(7.867,3.284)--(7.904,3.321)--(7.940,3.357)--(7.976,3.393)--(8.012,3.429)%
  --(8.048,3.465)--(8.085,3.502)--(8.121,3.538)--(8.157,3.574)--(8.193,3.610)--(8.230,3.647)%
  --(8.266,3.683)--(8.302,3.719)--(8.338,3.755)--(8.375,3.792)--(8.411,3.828)--(8.447,3.864)%
  --(8.483,3.900)--(8.520,3.937)--(8.556,3.973)--(8.592,4.009)--(8.628,4.045)--(8.665,4.082)%
  --(8.701,4.118)--(8.737,4.154)--(8.773,4.190)--(8.810,4.227)--(8.846,4.263)--(8.882,4.299)%
  --(8.918,4.335)--(8.955,4.372)--(8.991,4.408)--(9.027,4.444)--(9.063,4.480)--(9.100,4.517)%
  --(9.136,4.553)--(9.172,4.589)--(9.208,4.625)--(9.244,4.661)--(9.281,4.698)--(9.317,4.734)%
  --(9.353,4.770)--(9.389,4.806)--(9.426,4.843)--(9.462,4.879)--(9.498,4.915)--(9.534,4.951)%
  --(9.571,4.988)--(9.607,5.024)--(9.643,5.060)--(9.679,5.096)--(9.716,5.133)--(9.752,5.169)%
  --(9.788,5.205)--(9.824,5.241)--(9.861,5.278)--(9.897,5.314)--(9.933,5.350)--(9.969,5.386)%
  --(10.006,5.423)--(10.042,5.459)--(10.078,5.495)--(10.114,5.531)--(10.151,5.568)--(10.187,5.604)%
  --(10.223,5.640)--(10.259,5.676)--(10.296,5.713)--(10.332,5.749)--(10.368,5.785);
\gpcolor{color=gp lt color border}
\draw[gp path] (6.780,2.197)--(6.960,2.197);
\node[gp node right] at (6.596,2.197) {1};
\draw[gp path] (6.780,2.744)--(6.960,2.744);
\node[gp node right] at (6.596,2.744) {10};
\draw[gp path] (6.780,5.481)--(6.960,5.481);
\draw[gp path] (6.780,5.785)--(6.960,5.785);
\node[gp node right] at (6.596,5.785) {1h};
\draw[gp path] (6.780,2.197)--(6.960,2.197);
\draw[gp path] (6.780,2.362)--(6.870,2.362);
\draw[gp path] (6.780,2.580)--(6.870,2.580);
\draw[gp path] (6.780,2.691)--(6.870,2.691);
\draw[gp path] (6.780,2.744)--(6.960,2.744);
\draw[gp path] (6.780,2.909)--(6.870,2.909);
\draw[gp path] (6.780,3.127)--(6.870,3.127);
\draw[gp path] (6.780,3.238)--(6.870,3.238);
\draw[gp path] (6.780,3.292)--(6.960,3.292);
\node[gp node right] at (6.596,3.292) {$10^{2}$};
\draw[gp path] (6.780,3.456)--(6.870,3.456);
\draw[gp path] (6.780,3.674)--(6.870,3.674);
\draw[gp path] (6.780,3.786)--(6.870,3.786);
\draw[gp path] (6.780,3.839)--(6.960,3.839);
\node[gp node right] at (6.596,3.839) {$10^{3}$};
\draw[gp path] (6.780,4.004)--(6.870,4.004);
\draw[gp path] (6.780,4.221)--(6.870,4.221);
\draw[gp path] (6.780,4.333)--(6.870,4.333);
\draw[gp path] (6.780,4.386)--(6.960,4.386);
\node[gp node right] at (6.596,4.386) {$10^{4}$};
\draw[gp path] (6.780,4.551)--(6.870,4.551);
\draw[gp path] (6.780,4.769)--(6.870,4.769);
\draw[gp path] (6.780,4.880)--(6.870,4.880);
\draw[gp path] (6.780,4.933)--(6.960,4.933);
\node[gp node right] at (6.596,4.933) {$10^{5}$};
\draw[gp path] (6.780,5.098)--(6.870,5.098);
\draw[gp path] (6.780,5.316)--(6.870,5.316);
\draw[gp path] (6.780,5.428)--(6.870,5.428);
\draw[gp path] (6.780,5.481)--(6.960,5.481);
\draw[gp path] (6.780,5.645)--(6.870,5.645);
\draw[gp path] (6.780,2.197)--(6.780,2.377);
\node[gp node center] at (6.780,1.889) {1};
\draw[gp path] (7.327,2.197)--(7.327,2.377);
\node[gp node center] at (7.327,1.889) {10};
\draw[gp path] (10.064,2.197)--(10.064,2.377);
\draw[gp path] (10.368,2.197)--(10.368,2.377);
\node[gp node center] at (10.368,1.889) {1h};
\draw[gp path] (6.780,2.197)--(6.780,2.377);
\draw[gp path] (6.945,2.197)--(6.945,2.287);
\draw[gp path] (7.163,2.197)--(7.163,2.287);
\draw[gp path] (7.274,2.197)--(7.274,2.287);
\draw[gp path] (7.327,2.197)--(7.327,2.377);
\draw[gp path] (7.492,2.197)--(7.492,2.287);
\draw[gp path] (7.710,2.197)--(7.710,2.287);
\draw[gp path] (7.821,2.197)--(7.821,2.287);
\draw[gp path] (7.875,2.197)--(7.875,2.377);
\node[gp node center] at (7.875,1.889) {$10^{2}$};
\draw[gp path] (8.039,2.197)--(8.039,2.287);
\draw[gp path] (8.257,2.197)--(8.257,2.287);
\draw[gp path] (8.369,2.197)--(8.369,2.287);
\draw[gp path] (8.422,2.197)--(8.422,2.377);
\node[gp node center] at (8.422,1.889) {$10^{3}$};
\draw[gp path] (8.587,2.197)--(8.587,2.287);
\draw[gp path] (8.804,2.197)--(8.804,2.287);
\draw[gp path] (8.916,2.197)--(8.916,2.287);
\draw[gp path] (8.969,2.197)--(8.969,2.377);
\node[gp node center] at (8.969,1.889) {$10^{4}$};
\draw[gp path] (9.134,2.197)--(9.134,2.287);
\draw[gp path] (9.352,2.197)--(9.352,2.287);
\draw[gp path] (9.463,2.197)--(9.463,2.287);
\draw[gp path] (9.516,2.197)--(9.516,2.377);
\node[gp node center] at (9.516,1.889) {$10^{5}$};
\draw[gp path] (9.681,2.197)--(9.681,2.287);
\draw[gp path] (9.899,2.197)--(9.899,2.287);
\draw[gp path] (10.011,2.197)--(10.011,2.287);
\draw[gp path] (10.064,2.197)--(10.064,2.377);
\draw[gp path] (10.228,2.197)--(10.228,2.287);
\draw[gp path] (6.780,5.785)--(6.780,2.197)--(10.368,2.197);
\gpfill{rgb color={1.000,0.998,0.996}} (10.920,2.197)--(11.138,2.197)--(11.138,2.226)--(10.920,2.226)--cycle;
\gpfill{rgb color={1.000,0.934,0.895}} (10.920,2.225)--(11.138,2.225)--(11.138,2.254)--(10.920,2.254)--cycle;
\gpfill{rgb color={1.000,0.871,0.793}} (10.920,2.253)--(11.138,2.253)--(11.138,2.282)--(10.920,2.282)--cycle;
\gpfill{rgb color={1.000,0.807,0.692}} (10.920,2.281)--(11.138,2.281)--(11.138,2.310)--(10.920,2.310)--cycle;
\gpfill{rgb color={1.000,0.743,0.590}} (10.920,2.309)--(11.138,2.309)--(11.138,2.313)--(10.920,2.313)--cycle;
\gpfill{rgb color={1.000,0.737,0.580}} (10.920,2.312)--(11.138,2.312)--(11.138,2.338)--(10.920,2.338)--cycle;
\gpfill{rgb color={1.000,0.731,0.575}} (10.920,2.337)--(11.138,2.337)--(11.138,2.366)--(10.920,2.366)--cycle;
\gpfill{rgb color={1.000,0.724,0.570}} (10.920,2.365)--(11.138,2.365)--(11.138,2.394)--(10.920,2.394)--cycle;
\gpfill{rgb color={1.000,0.717,0.564}} (10.920,2.393)--(11.138,2.393)--(11.138,2.422)--(10.920,2.422)--cycle;
\gpfill{rgb color={1.000,0.710,0.559}} (10.920,2.421)--(11.138,2.421)--(11.138,2.450)--(10.920,2.450)--cycle;
\gpfill{rgb color={1.000,0.703,0.553}} (10.920,2.449)--(11.138,2.449)--(11.138,2.478)--(10.920,2.478)--cycle;
\gpfill{rgb color={1.000,0.696,0.548}} (10.920,2.477)--(11.138,2.477)--(11.138,2.506)--(10.920,2.506)--cycle;
\gpfill{rgb color={1.000,0.689,0.542}} (10.920,2.505)--(11.138,2.505)--(11.138,2.534)--(10.920,2.534)--cycle;
\gpfill{rgb color={1.000,0.682,0.537}} (10.920,2.533)--(11.138,2.533)--(11.138,2.562)--(10.920,2.562)--cycle;
\gpfill{rgb color={1.000,0.675,0.531}} (10.920,2.561)--(11.138,2.561)--(11.138,2.590)--(10.920,2.590)--cycle;
\gpfill{rgb color={1.000,0.668,0.526}} (10.920,2.589)--(11.138,2.589)--(11.138,2.618)--(10.920,2.618)--cycle;
\gpfill{rgb color={1.000,0.661,0.520}} (10.920,2.617)--(11.138,2.617)--(11.138,2.646)--(10.920,2.646)--cycle;
\gpfill{rgb color={1.000,0.654,0.515}} (10.920,2.645)--(11.138,2.645)--(11.138,2.674)--(10.920,2.674)--cycle;
\gpfill{rgb color={1.000,0.647,0.509}} (10.920,2.673)--(11.138,2.673)--(11.138,2.702)--(10.920,2.702)--cycle;
\gpfill{rgb color={1.000,0.640,0.504}} (10.920,2.701)--(11.138,2.701)--(11.138,2.730)--(10.920,2.730)--cycle;
\gpfill{rgb color={1.000,0.633,0.498}} (10.920,2.729)--(11.138,2.729)--(11.138,2.758)--(10.920,2.758)--cycle;
\gpfill{rgb color={1.000,0.626,0.493}} (10.920,2.757)--(11.138,2.757)--(11.138,2.786)--(10.920,2.786)--cycle;
\gpfill{rgb color={1.000,0.619,0.487}} (10.920,2.785)--(11.138,2.785)--(11.138,2.814)--(10.920,2.814)--cycle;
\gpfill{rgb color={1.000,0.612,0.482}} (10.920,2.813)--(11.138,2.813)--(11.138,2.842)--(10.920,2.842)--cycle;
\gpfill{rgb color={1.000,0.605,0.476}} (10.920,2.841)--(11.138,2.841)--(11.138,2.870)--(10.920,2.870)--cycle;
\gpfill{rgb color={1.000,0.598,0.471}} (10.920,2.869)--(11.138,2.869)--(11.138,2.892)--(10.920,2.892)--cycle;
\gpfill{rgb color={1.000,0.592,0.467}} (10.920,2.891)--(11.138,2.891)--(11.138,2.898)--(10.920,2.898)--cycle;
\gpfill{rgb color={1.000,0.590,0.466}} (10.920,2.897)--(11.138,2.897)--(11.138,2.926)--(10.920,2.926)--cycle;
\gpfill{rgb color={1.000,0.581,0.462}} (10.920,2.925)--(11.138,2.925)--(11.138,2.954)--(10.920,2.954)--cycle;
\gpfill{rgb color={1.000,0.573,0.458}} (10.920,2.953)--(11.138,2.953)--(11.138,2.982)--(10.920,2.982)--cycle;
\gpfill{rgb color={1.000,0.564,0.454}} (10.920,2.981)--(11.138,2.981)--(11.138,3.010)--(10.920,3.010)--cycle;
\gpfill{rgb color={1.000,0.555,0.450}} (10.920,3.009)--(11.138,3.009)--(11.138,3.038)--(10.920,3.038)--cycle;
\gpfill{rgb color={1.000,0.546,0.446}} (10.920,3.037)--(11.138,3.037)--(11.138,3.066)--(10.920,3.066)--cycle;
\gpfill{rgb color={1.000,0.538,0.442}} (10.920,3.065)--(11.138,3.065)--(11.138,3.095)--(10.920,3.095)--cycle;
\gpfill{rgb color={1.000,0.529,0.438}} (10.920,3.094)--(11.138,3.094)--(11.138,3.123)--(10.920,3.123)--cycle;
\gpfill{rgb color={1.000,0.520,0.434}} (10.920,3.122)--(11.138,3.122)--(11.138,3.151)--(10.920,3.151)--cycle;
\gpfill{rgb color={1.000,0.511,0.430}} (10.920,3.150)--(11.138,3.150)--(11.138,3.179)--(10.920,3.179)--cycle;
\gpfill{rgb color={1.000,0.503,0.426}} (10.920,3.178)--(11.138,3.178)--(11.138,3.207)--(10.920,3.207)--cycle;
\gpfill{rgb color={1.000,0.494,0.422}} (10.920,3.206)--(11.138,3.206)--(11.138,3.235)--(10.920,3.235)--cycle;
\gpfill{rgb color={1.000,0.485,0.418}} (10.920,3.234)--(11.138,3.234)--(11.138,3.263)--(10.920,3.263)--cycle;
\gpfill{rgb color={1.000,0.476,0.414}} (10.920,3.262)--(11.138,3.262)--(11.138,3.291)--(10.920,3.291)--cycle;
\gpfill{rgb color={1.000,0.468,0.410}} (10.920,3.290)--(11.138,3.290)--(11.138,3.319)--(10.920,3.319)--cycle;
\gpfill{rgb color={1.000,0.459,0.406}} (10.920,3.318)--(11.138,3.318)--(11.138,3.347)--(10.920,3.347)--cycle;
\gpfill{rgb color={1.000,0.450,0.402}} (10.920,3.346)--(11.138,3.346)--(11.138,3.375)--(10.920,3.375)--cycle;
\gpfill{rgb color={1.000,0.441,0.398}} (10.920,3.374)--(11.138,3.374)--(11.138,3.403)--(10.920,3.403)--cycle;
\gpfill{rgb color={1.000,0.433,0.394}} (10.920,3.402)--(11.138,3.402)--(11.138,3.431)--(10.920,3.431)--cycle;
\gpfill{rgb color={1.000,0.424,0.390}} (10.920,3.430)--(11.138,3.430)--(11.138,3.459)--(10.920,3.459)--cycle;
\gpfill{rgb color={1.000,0.415,0.386}} (10.920,3.458)--(11.138,3.458)--(11.138,3.471)--(10.920,3.471)--cycle;
\gpfill{rgb color={1.000,0.412,0.384}} (10.920,3.470)--(11.138,3.470)--(11.138,3.487)--(10.920,3.487)--cycle;
\gpfill{rgb color={0.998,0.407,0.383}} (10.920,3.486)--(11.138,3.486)--(11.138,3.515)--(10.920,3.515)--cycle;
\gpfill{rgb color={0.995,0.400,0.381}} (10.920,3.514)--(11.138,3.514)--(11.138,3.543)--(10.920,3.543)--cycle;
\gpfill{rgb color={0.992,0.393,0.378}} (10.920,3.542)--(11.138,3.542)--(11.138,3.571)--(10.920,3.571)--cycle;
\gpfill{rgb color={0.988,0.385,0.376}} (10.920,3.570)--(11.138,3.570)--(11.138,3.599)--(10.920,3.599)--cycle;
\gpfill{rgb color={0.985,0.378,0.374}} (10.920,3.598)--(11.138,3.598)--(11.138,3.627)--(10.920,3.627)--cycle;
\gpfill{rgb color={0.982,0.370,0.372}} (10.920,3.626)--(11.138,3.626)--(11.138,3.655)--(10.920,3.655)--cycle;
\gpfill{rgb color={0.979,0.363,0.369}} (10.920,3.654)--(11.138,3.654)--(11.138,3.683)--(10.920,3.683)--cycle;
\gpfill{rgb color={0.975,0.356,0.367}} (10.920,3.682)--(11.138,3.682)--(11.138,3.711)--(10.920,3.711)--cycle;
\gpfill{rgb color={0.972,0.348,0.365}} (10.920,3.710)--(11.138,3.710)--(11.138,3.739)--(10.920,3.739)--cycle;
\gpfill{rgb color={0.969,0.341,0.362}} (10.920,3.738)--(11.138,3.738)--(11.138,3.767)--(10.920,3.767)--cycle;
\gpfill{rgb color={0.966,0.333,0.360}} (10.920,3.766)--(11.138,3.766)--(11.138,3.795)--(10.920,3.795)--cycle;
\gpfill{rgb color={0.963,0.326,0.358}} (10.920,3.794)--(11.138,3.794)--(11.138,3.823)--(10.920,3.823)--cycle;
\gpfill{rgb color={0.959,0.319,0.356}} (10.920,3.822)--(11.138,3.822)--(11.138,3.851)--(10.920,3.851)--cycle;
\gpfill{rgb color={0.956,0.311,0.353}} (10.920,3.850)--(11.138,3.850)--(11.138,3.879)--(10.920,3.879)--cycle;
\gpfill{rgb color={0.953,0.304,0.351}} (10.920,3.878)--(11.138,3.878)--(11.138,3.907)--(10.920,3.907)--cycle;
\gpfill{rgb color={0.950,0.296,0.349}} (10.920,3.906)--(11.138,3.906)--(11.138,3.935)--(10.920,3.935)--cycle;
\gpfill{rgb color={0.946,0.289,0.347}} (10.920,3.934)--(11.138,3.934)--(11.138,3.963)--(10.920,3.963)--cycle;
\gpfill{rgb color={0.943,0.282,0.344}} (10.920,3.962)--(11.138,3.962)--(11.138,3.992)--(10.920,3.992)--cycle;
\gpfill{rgb color={0.940,0.274,0.342}} (10.920,3.991)--(11.138,3.991)--(11.138,4.020)--(10.920,4.020)--cycle;
\gpfill{rgb color={0.937,0.266,0.340}} (10.920,4.019)--(11.138,4.019)--(11.138,4.048)--(10.920,4.048)--cycle;
\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.047)--(11.138,4.047)--(11.138,4.049)--(10.920,4.049)--cycle;
\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.048)--(11.138,4.048)--(11.138,4.076)--(10.920,4.076)--cycle;
\gpfill{rgb color={0.928,0.252,0.334}} (10.920,4.075)--(11.138,4.075)--(11.138,4.104)--(10.920,4.104)--cycle;
\gpfill{rgb color={0.923,0.246,0.332}} (10.920,4.103)--(11.138,4.103)--(11.138,4.132)--(10.920,4.132)--cycle;
\gpfill{rgb color={0.918,0.239,0.329}} (10.920,4.131)--(11.138,4.131)--(11.138,4.160)--(10.920,4.160)--cycle;
\gpfill{rgb color={0.912,0.232,0.326}} (10.920,4.159)--(11.138,4.159)--(11.138,4.188)--(10.920,4.188)--cycle;
\gpfill{rgb color={0.907,0.226,0.323}} (10.920,4.187)--(11.138,4.187)--(11.138,4.216)--(10.920,4.216)--cycle;
\gpfill{rgb color={0.902,0.219,0.320}} (10.920,4.215)--(11.138,4.215)--(11.138,4.244)--(10.920,4.244)--cycle;
\gpfill{rgb color={0.896,0.213,0.317}} (10.920,4.243)--(11.138,4.243)--(11.138,4.272)--(10.920,4.272)--cycle;
\gpfill{rgb color={0.891,0.206,0.315}} (10.920,4.271)--(11.138,4.271)--(11.138,4.300)--(10.920,4.300)--cycle;
\gpfill{rgb color={0.886,0.199,0.312}} (10.920,4.299)--(11.138,4.299)--(11.138,4.328)--(10.920,4.328)--cycle;
\gpfill{rgb color={0.880,0.193,0.309}} (10.920,4.327)--(11.138,4.327)--(11.138,4.356)--(10.920,4.356)--cycle;
\gpfill{rgb color={0.875,0.186,0.306}} (10.920,4.355)--(11.138,4.355)--(11.138,4.384)--(10.920,4.384)--cycle;
\gpfill{rgb color={0.870,0.179,0.303}} (10.920,4.383)--(11.138,4.383)--(11.138,4.412)--(10.920,4.412)--cycle;
\gpfill{rgb color={0.864,0.173,0.300}} (10.920,4.411)--(11.138,4.411)--(11.138,4.440)--(10.920,4.440)--cycle;
\gpfill{rgb color={0.859,0.166,0.297}} (10.920,4.439)--(11.138,4.439)--(11.138,4.468)--(10.920,4.468)--cycle;
\gpfill{rgb color={0.854,0.159,0.295}} (10.920,4.467)--(11.138,4.467)--(11.138,4.496)--(10.920,4.496)--cycle;
\gpfill{rgb color={0.848,0.153,0.292}} (10.920,4.495)--(11.138,4.495)--(11.138,4.524)--(10.920,4.524)--cycle;
\gpfill{rgb color={0.843,0.146,0.289}} (10.920,4.523)--(11.138,4.523)--(11.138,4.552)--(10.920,4.552)--cycle;
\gpfill{rgb color={0.838,0.139,0.286}} (10.920,4.551)--(11.138,4.551)--(11.138,4.580)--(10.920,4.580)--cycle;
\gpfill{rgb color={0.833,0.133,0.283}} (10.920,4.579)--(11.138,4.579)--(11.138,4.608)--(10.920,4.608)--cycle;
\gpfill{rgb color={0.827,0.126,0.280}} (10.920,4.607)--(11.138,4.607)--(11.138,4.628)--(10.920,4.628)--cycle;
\gpfill{rgb color={0.823,0.121,0.278}} (10.920,4.627)--(11.138,4.627)--(11.138,4.636)--(10.920,4.636)--cycle;
\gpfill{rgb color={0.822,0.120,0.277}} (10.920,4.635)--(11.138,4.635)--(11.138,4.664)--(10.920,4.664)--cycle;
\gpfill{rgb color={0.815,0.115,0.272}} (10.920,4.663)--(11.138,4.663)--(11.138,4.692)--(10.920,4.692)--cycle;
\gpfill{rgb color={0.809,0.111,0.267}} (10.920,4.691)--(11.138,4.691)--(11.138,4.720)--(10.920,4.720)--cycle;
\gpfill{rgb color={0.802,0.106,0.262}} (10.920,4.719)--(11.138,4.719)--(11.138,4.748)--(10.920,4.748)--cycle;
\gpfill{rgb color={0.796,0.101,0.256}} (10.920,4.747)--(11.138,4.747)--(11.138,4.776)--(10.920,4.776)--cycle;
\gpfill{rgb color={0.789,0.096,0.251}} (10.920,4.775)--(11.138,4.775)--(11.138,4.804)--(10.920,4.804)--cycle;
\gpfill{rgb color={0.783,0.092,0.246}} (10.920,4.803)--(11.138,4.803)--(11.138,4.832)--(10.920,4.832)--cycle;
\gpfill{rgb color={0.776,0.087,0.241}} (10.920,4.831)--(11.138,4.831)--(11.138,4.860)--(10.920,4.860)--cycle;
\gpfill{rgb color={0.770,0.082,0.236}} (10.920,4.859)--(11.138,4.859)--(11.138,4.889)--(10.920,4.889)--cycle;
\gpfill{rgb color={0.763,0.077,0.231}} (10.920,4.888)--(11.138,4.888)--(11.138,4.917)--(10.920,4.917)--cycle;
\gpfill{rgb color={0.757,0.073,0.225}} (10.920,4.916)--(11.138,4.916)--(11.138,4.945)--(10.920,4.945)--cycle;
\gpfill{rgb color={0.750,0.068,0.220}} (10.920,4.944)--(11.138,4.944)--(11.138,4.973)--(10.920,4.973)--cycle;
\gpfill{rgb color={0.744,0.063,0.215}} (10.920,4.972)--(11.138,4.972)--(11.138,5.001)--(10.920,5.001)--cycle;
\gpfill{rgb color={0.737,0.058,0.210}} (10.920,5.000)--(11.138,5.000)--(11.138,5.029)--(10.920,5.029)--cycle;
\gpfill{rgb color={0.731,0.054,0.205}} (10.920,5.028)--(11.138,5.028)--(11.138,5.057)--(10.920,5.057)--cycle;
\gpfill{rgb color={0.725,0.049,0.200}} (10.920,5.056)--(11.138,5.056)--(11.138,5.085)--(10.920,5.085)--cycle;
\gpfill{rgb color={0.718,0.044,0.195}} (10.920,5.084)--(11.138,5.084)--(11.138,5.113)--(10.920,5.113)--cycle;
\gpfill{rgb color={0.712,0.039,0.190}} (10.920,5.112)--(11.138,5.112)--(11.138,5.141)--(10.920,5.141)--cycle;
\gpfill{rgb color={0.705,0.035,0.184}} (10.920,5.140)--(11.138,5.140)--(11.138,5.169)--(10.920,5.169)--cycle;
\gpfill{rgb color={0.699,0.030,0.179}} (10.920,5.168)--(11.138,5.168)--(11.138,5.197)--(10.920,5.197)--cycle;
\gpfill{rgb color={0.692,0.025,0.174}} (10.920,5.196)--(11.138,5.196)--(11.138,5.207)--(10.920,5.207)--cycle;
\gpfill{rgb color={0.690,0.024,0.172}} (10.920,5.206)--(11.138,5.206)--(11.138,5.225)--(10.920,5.225)--cycle;
\gpfill{rgb color={0.686,0.023,0.167}} (10.920,5.224)--(11.138,5.224)--(11.138,5.253)--(10.920,5.253)--cycle;
\gpfill{rgb color={0.678,0.022,0.159}} (10.920,5.252)--(11.138,5.252)--(11.138,5.281)--(10.920,5.281)--cycle;
\gpfill{rgb color={0.671,0.020,0.150}} (10.920,5.280)--(11.138,5.280)--(11.138,5.309)--(10.920,5.309)--cycle;
\gpfill{rgb color={0.664,0.019,0.142}} (10.920,5.308)--(11.138,5.308)--(11.138,5.337)--(10.920,5.337)--cycle;
\gpfill{rgb color={0.657,0.018,0.134}} (10.920,5.336)--(11.138,5.336)--(11.138,5.365)--(10.920,5.365)--cycle;
\gpfill{rgb color={0.650,0.017,0.125}} (10.920,5.364)--(11.138,5.364)--(11.138,5.393)--(10.920,5.393)--cycle;
\gpfill{rgb color={0.643,0.016,0.117}} (10.920,5.392)--(11.138,5.392)--(11.138,5.421)--(10.920,5.421)--cycle;
\gpfill{rgb color={0.636,0.015,0.109}} (10.920,5.420)--(11.138,5.420)--(11.138,5.449)--(10.920,5.449)--cycle;
\gpfill{rgb color={0.629,0.014,0.100}} (10.920,5.448)--(11.138,5.448)--(11.138,5.477)--(10.920,5.477)--cycle;
\gpfill{rgb color={0.622,0.013,0.092}} (10.920,5.476)--(11.138,5.476)--(11.138,5.505)--(10.920,5.505)--cycle;
\gpfill{rgb color={0.615,0.011,0.083}} (10.920,5.504)--(11.138,5.504)--(11.138,5.533)--(10.920,5.533)--cycle;
\gpfill{rgb color={0.608,0.010,0.075}} (10.920,5.532)--(11.138,5.532)--(11.138,5.561)--(10.920,5.561)--cycle;
\gpfill{rgb color={0.601,0.009,0.067}} (10.920,5.560)--(11.138,5.560)--(11.138,5.589)--(10.920,5.589)--cycle;
\gpfill{rgb color={0.594,0.008,0.058}} (10.920,5.588)--(11.138,5.588)--(11.138,5.617)--(10.920,5.617)--cycle;
\gpfill{rgb color={0.587,0.007,0.050}} (10.920,5.616)--(11.138,5.616)--(11.138,5.645)--(10.920,5.645)--cycle;
\gpfill{rgb color={0.580,0.006,0.042}} (10.920,5.644)--(11.138,5.644)--(11.138,5.673)--(10.920,5.673)--cycle;
\gpfill{rgb color={0.573,0.005,0.033}} (10.920,5.672)--(11.138,5.672)--(11.138,5.701)--(10.920,5.701)--cycle;
\gpfill{rgb color={0.566,0.003,0.025}} (10.920,5.700)--(11.138,5.700)--(11.138,5.729)--(10.920,5.729)--cycle;
\gpfill{rgb color={0.559,0.002,0.017}} (10.920,5.728)--(11.138,5.728)--(11.138,5.757)--(10.920,5.757)--cycle;
\gpfill{rgb color={0.552,0.001,0.008}} (10.920,5.756)--(11.138,5.756)--(11.138,5.785)--(10.920,5.785)--cycle;
\draw[gp path] (10.920,2.197)--(11.138,2.197)--(11.138,5.785)--(10.920,5.785)--cycle;
\draw[gp path] (11.138,2.197)--(10.958,2.197);
\node[gp node left] at (11.139,2.197) {0};
\draw[gp path] (10.920,2.197)--(11.100,2.197);
\draw[gp path] (11.138,2.557)--(10.958,2.557);
\node[gp node left] at (11.139,2.557) {1};
\draw[gp path] (10.920,2.557)--(11.100,2.557);
\draw[gp path] (11.138,3.393)--(10.958,3.393);
\node[gp node left] at (11.139,3.393) {10};
\draw[gp path] (10.920,3.393)--(11.100,3.393);
\draw[gp path] (11.138,4.589)--(10.958,4.589);
\node[gp node left] at (11.139,4.589) {$10^2$};
\draw[gp path] (10.920,4.589)--(11.100,4.589);
\draw[gp path] (11.138,5.785)--(10.958,5.785);
\node[gp node left] at (11.139,5.785) {$\ge10^3$};
\draw[gp path] (10.920,5.785)--(11.100,5.785);
\node[gp node center] at (8.574,5.426) {Unlabelled};
%% coordinates of the plot area
\gpdefrectangularnode{gp plot 2}{\pgfpoint{6.780cm}{2.197cm}}{\pgfpoint{10.368cm}{5.785cm}}
\end{tikzpicture}
%% gnuplot variables

### 2016-04-08 paper/paper.tex
Reorder, and reduce the figures
Rework definitions, and reorder

@@
 \renewcommand{\bottomfraction}{0.8}
+\newcommand{\christine}[1]{{\color{green} Christine:#1}}
 
@@
 
-\begin{figure}[b] % first page if possible
+Maximum common subgraph problems arise in biology and chemistry
+\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
+\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
+\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
+designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
+and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
+measuring the similarity or difference between two graphs
+\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}.
+
+\paragraph{Definition of the Maximum Common (Connected) Subgraph Problem.}
+We introduce definitions and algorithms on undirected and unlabelled graphs.
+The extension to directed or labelled graphs is straightforward and discussed in Section \ref{extension}.
+An undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq N_G\times N_G$ such that each edge is an undirected pair of nodes.
+
+Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$.
+A graph $G$ is \emph{connected} if every pair of nodes is connected by a path.
+
+A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function $f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G, \{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
+
+A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a \emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
+In this definition, we only remove edges incident to removed nodes.
+This is usually called induced subgraph in the litterature.
+We may also allow to remove edges which are not incident to removed nodes, thus leading to partial subgraphs.
+In this paper, we only consider induced subgraphs.
+However, all algorithms may be extended to the partial case, as explained in \cite{DBLP:conf/cp/NdiayeS11}.
+
+A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and $G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
+A \emph{Maximum Common Subgraph} (MCS) (resp.
+\emph{Maximum Common Connected Subgraph} (MCCS) is a common subgraph (resp.
+common connected subgraph) which has a maximum number of nodes.
+Examples of MCS and MCCS are given in Fig.
+\ref{figure:mcsexample}.
+
+\begin{figure}[t] % first page if possible
     \centering
@@
 
-Maximum common subgraph problems arise in biology and chemistry
-\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
-\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
-\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
-designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
-and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
-measuring the similarity or difference between two graphs
-\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
-variants of the problem in \cref{figure:mcsexample}.
+\paragraph{Overview of the paper.} In Section \ref{existing}, we review existing approaches for solving the MCS problem, with a specific focus on Constraint Programming (CP)-based approaches and on clique-based approaches that reduce the problem to finding a maximum clique in an association graph.
 
-Throughout this paper we will be working with graphs which may be directed, which may have labels
-associated with vertices, edges, or both, and which may contain loops. To simplify notation, we will
-work with a very broad definition: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of
-vertices $V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling
-function $e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex
-(or edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also
-use a distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices; vertices
-$v$ and $w$ are said to be \emph{adjacent} if $e(v, w) \ne \bot$ or $e(w, v) \ne \bot$. We write
-$\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
-of a vertex $v$ (that is, the set of vertices adjacent to $v$); a vertex is \emph{isolated} if its
-neighbourhood is empty. A (weak) \emph{path} between two vertices $v$ and $w$ is a sequence of $n$
-vertices $v = v_1, v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $v_m$ is
-adjacent to $v_{m + 1}$. A graph is (weakly) \emph{connected} if a path exists between each distinct
-pair of vertices.
+Conventional wisdom is that clique-based approaches are less effective in practice, but previous experimental evaluations have used weak clique algorithms, or even maximal clique enumeration algorithms.
+Therefore, in Section \ref{eval1}, we  re-evaluate the clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive with CP on non labelled graphs.
 
-Given two graphs $G_1 = (V_1, \ell_1, e_1)$ and $G_2 = (V_2, \ell_2, e_2)$, we say two pairs of
-vertices $(v_1, w_1) \in \operatorname{V}(G_1) \times \operatorname{V}(G_1)$ and $(v_2, w_2) \in
-\operatorname{V}(G_2) \times \operatorname{V}(G_2)$ are \emph{compatible}, written $(v_1, w_1)
-\simeq (v_2, w_2)$, if both $e_1(v_1, w_1) = e_2(v_2, w_2)$ and $e_1(w_1, v_1) = e_2(w_2, v_2)$. We
-say two vertices $v \in \operatorname{V}(G_1)$ and $w \in \operatorname{V}(G_2)$ are
-\emph{compatible}, written $v \simeq w$, if $\ell_1(v) = \ell_2(w)$ and $(v, v) \simeq (w, w)$.
+Then, in Section \ref{mccs}, we consider the MCCS problem.
+For the CP approach, we may add a global connectedness constraint to the model.
+Alternatively, we may use a special branching rule to grow connected subgraphs only, as proposed in \cite{DBLP:conf/mco/VismaraV08}.
+These two techniques may be combined, and we experimentally show that the best results are obtained when combining them.
+When solving the MCCS problem with a clique-based approach, neither technique seems directly viable with an association graph encoding.
+However, we show that it is possible to adapt the combined branching and bounding rule used by modern clique algorithms to preserve connectedness during search.
+We compare the clique-based approach with the best CP variant for the MCCS, and we show that it outperforms CP on non labelled graphs, whereas it is outperformed by CP on labelled graphs.
 
-An \emph{induced subgraph isomorphism} from a graph $G$ to a graph $H$ is an injective function $i :
-\operatorname{V}(G) \rightarrow \operatorname{V}(H)$ such that for every vertex $v \in
-\operatorname{V}(G)$, $v \simeq i(v)$, and for every pair of vertices $(v, w) \in
-\operatorname{V}(G) \times \operatorname{V}(G)$, $(v, w) \simeq (i(v), i(w))$. A \emph{common
-induced subgraph isomorphism} between two graphs $G_1$ and $G_2$ is a graph $G$, together with a
-pair of induced subgraph isomorphisms $i_1 : G \rightarrow G_1$ and $i_2 : G \rightarrow G_2$. A
-\emph{common induced subgraph} of $G_1$ and $G_2$ is a graph $G$ which has a common subgraph
-isomorphism to $G_1$ and $G_2$. A \emph{maximum common (connected) induced subgraph} is a common
-(connected) induced subgraph with the largest possible number of vertices.  (The distinction between
-a common subgraph and a common subgraph isomorphism is relevant when counting distinct solutions,
-which we do not consider in this paper; in \cref{figure:mcsexample} on the left, there is only one
-maximum common subgraph, but four different maximum common subgraph isomorphisms are possible.)
+\section{Existing Complete Approaches for MCS}\label{existing}
 
-There is also a non-induced version of these problems, which is commonly known as the \emph{maximum
-common partial subgraph} problem: here, if $e(v, w) = \bot$, then $e_1(i_1(v), i_1(w))$ and
-$e_2(i_2(v), i_2(w))$ may take any value, and we must maximise the number of non-$\bot$ vertex pairs
-(i.e.\ edges) in $G$ instead (it is not entirely clear what the objective should be in directed
-graphs, or when loops are present). We restrict ourselves to the induced version in this paper.
+There exist two main approaches for solving MCS: The first approach (described in \ref{CP}) is based on CP; The second approach (described in \ref{clique}) is based on a reformulation of MCS into a maximum clique problem.
+Both approaches are described for non directed and non labelled graphs.
+Their extension to directed or labelled graphs is discussed in Section \ref{extension}
 
-\subsection{Existing Approaches}
+\subsection{CP model for MCS}
+\label{CP}
 
-One approach to maximum common subgraph problems is via constraint programming
-\cite{DBLP:conf/mco/VismaraV08,DBLP:conf/cp/NdiayeS11}. The models are based upon constructing an
-injective mapping from the vertices of one graph (typically the smaller) to the other, in a similar
-manner to subgraph isomorphism algorithms
-\cite{DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}. However, to
-allow for a partial mapping, a special $\bot$ value is added to each domain (and so we are
-constructing a maximum common subgraph isomorphism, where the common subgraph is implicitly the
-subgraph of the first graph given by taking the vertices which are not assigned to $\bot$, and the
-first subgraph isomorphism is the inclusion map). The objective is then to minimise the number of
-variables given the $\bot$ value---for best results, a special propagator for the injectivity
-condition is used, which simultaneously enforces that all variables taking non-$\bot$ are different,
-and restricts the number of $\bot$ values which may be used based upon the objective
-\cite{DBLP:conf/cp/PetitRB01}.  Unfortunately, the addition of $\bot$ also invalidates many of the
-invariants used for subgraph isomorphism---we may no longer reason using the degree of vertices, for
-example, and so maximum common subgraph problems can be much more challenging in practice.
+McGregor \cite{McGreg82} proposed a Branch \& Bound approach: Each branch of the search tree corresponds to the matching of two nodes, and a  bounding function evaluates the number of nodes that still may be matched so that the current branch is pruned as soon as this bound becomes lower than the size of the largest known common subgraph.
+CP approaches may be viewed as enhancements of this Branch \& Bound approach.
 
-Another widely studied approach ?? cite is to reduce the problem to finding a maximum clique (or sometimes,
-equivalently, an independent set or a vertex cover ?? cite) in an association graph \cite{LeviG}; we describe
-this below. Conventional wisdom is that this model is less effective in practice, but previous
-experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
-algorithms. Maximum clique algorithms are an active research area
-\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10,DBLP:journals/cor/SegundoRJ11,DBLP:journals/algorithms/Prosser12,DBLP:journals/ol/SegundoMRH13,DBLP:conf/ictai/LiFX13,DBLP:journals/cor/SegundoT14,DBLP:conf/lion/SegundoLB14,DBLP:conf/cp/McCreeshP14,DBLP:journals/jco/BatsynGMP14,DBLP:journals/cor/SegundoNB15,DBLP:conf/lion/NikolaevBS15,DBLP:conf/lion/LiJX15,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16},
-and so the first half of this paper re-evaluates the association graph model using a modern
-algorithm.
+Vismara and Valery  \cite{DBLP:conf/mco/VismaraV08} introduced a first CP model.
+Given two graphs $G$ and $G'$, this model associates a variable $x_u$ with every node $u$ of $G$, and the domain of this variable contains all nodes of $G'$, plus an additional value $\bot$: variable $x_u$ is assigned to $\bot$ if node $u$ is not matched to any node of $G'$; otherwise $x_u$ is assigned to the node of $G'$ it is matched with.
+Edge constraints are introduced in order to ensure that variable assignments preserve edges between matched nodes, {\em i.e.},
+$\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee (\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'})$.
+Difference constraints are introduced in order to ensure that each node of $G'$ is assigned to at most one variable, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee (x_u\neq x_v)$.
 
-(Other approaches have been tried, including dedicated algorithms ?? cite, mixed integer programming
-\cite{DBLP:journals/anor/PivaS12}, and heuristics \cite{DBLP:journals/jcisd/EnglertK15}; SAT
-encodings seem to struggle even for subgraph isomorphism \cite{UpcomingIJCAIPaper}.)
+This CP model is improved in \cite{DBLP:conf/cp/NdiayeS11} by replacing binary difference constraints with a soft global allDifferent constraint which maximizes the number of $x_u$ variables that are assigned to values different from $\bot$, while ensuring they are all different when they are not assigned to $\bot$.
+Different constraint propagation techniques are compared in \cite{DBLP:conf/cp/NdiayeS11}.
+The combination ``MAC+Bound'' (resp.
+``FC+Bound'') obtains the best results on labelled (resp.
+non labelled) graphs and outperforms the approach of \cite{McGreg82} and the CP model of \cite{DBLP:conf/mco/VismaraV08}.
+The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs forward-checking on these constraints.
+In both combinations, the ``Bound'' filtering checks whether it is possible to assign distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that can be assigned distinct values).
 
-An interesting variant of the maximum common subgraph problem requires the selected subgraph to be
-connected
-\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
-Adding the connectedness requirement makes certain special cases solvable in polynomial time,
-including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
-\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. The second half of
-this paper looks at this variant on arbitrary graphs. In principle, for a constraint programming
-approach, we may simply add a ``forms a connected graph'' global constraint
-\cite{Brown:2005,DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05} to the model. Alternatively, we
-could use a special branching rule to maintain connectedness during search ?? cite. Neither
-technique seems directly viable with an association graph encoding---however, we show that it is
-possible to adapt the combined branching and bounding rule used by modern clique algorithms to
-preserve connectedness during search.
+\subsection{Reformulation of MCS as a maximum clique problem}
+\label{clique}
 
-Our experiments suggest that each model and technique gives broadly similar performance, although
-the association graph works better when graphs have edge labels (and we discuss why), and constraint
-programming models are better when edges are unlabelled. For the constraint programming model, using
-both a global constraint \emph{and} the branching rule in conjunction seems to be the safest
-option---although it is not always fastest, it is very rarely substantially worse than just using
-one or the other, and is often substantially better.
+We may solve MCS by introducing an association graph and searching for a maximum clique in it \cite{bala86,dura99,DBLP:journals/jcamd/RaymondW02a}.
 
-\subsection{Datasets}
+An association graph of two graphs $G$ and $G'$ is an undirected graph $A_{G,G'}$ whose set of nodes is $N_{A_{G,G'}} = N_G \times N_{G'}$.
+To avoid confusing nodes of $A_{G,G'}$ with initial graph nodes, nodes of $A_{G,G'}$ are called matching nodes, as each node $(u,u')$ of $A_{G,G'}$ denotes the matching of $u$ with $u'$.
+Edges of $A_{G,G'}$ connect matching nodes which are compatible, {\em i.e.}, $E_{A_{G,G'}} = \big\{\{(u,u'),(v,v')\}\subseteq N_{A_{G,G'}}$, $(u,u')$ and $(v,v')$ are compatible$\big\}$, where two matching nodes $(u,u')$ and $(v,v')$ of $N_{A_{G,G'}}$ are compatible if $u \neq v$ and $u' \neq v'$, and if they preserve edges (\emph{i.e.}, $\{u,v\} \in E_G \Leftrightarrow \{u',v'\} \in E_{G'}$).
 
-\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}
+A \emph{clique} is a subgraph whose nodes are all linked pairwise.
+A clique is \emph{maximal} if it is not strictly included in any other clique, and it is \emph{maximum} if it is the largest clique of a given graph, with respect to the number of nodes.
 
-?? More? Can we scale to some of the SIP graphs?
+A clique in $A_{G,G'}$ corresponds to a set of compatible matchings. Therefore, such a clique corresponds to a common subgraph, and a maximum clique of $A_{G,G'}$ is a MCS of $G$ and $G'$.
+It follows that any method able to find a maximum clique in a graph can be used to solve the MCS problem.
 
-\section{Re-Evaluating the Clique Model}
+Note that the association graph is a partial subgraph of the microstructure \cite{DBLP:conf/aaai/Jegou93a} associated with the CP model of  \cite{DBLP:conf/mco/VismaraV08}: The microstructure has more matching nodes than the association graph because it has a matching node $(u,\bot)$ for each node $u$ of $G$.
+Each clique of size $|N_G|$ in the microstructure corresponds to a common subgraph the size of which is defined by the number of nodes that do not contain $\bot$.
+
+\subsection{Extension to Labeled or Directed Graphs}\label{extension}
+
+In some applications, nodes and edges are associated with labels.
+We note $\lambda(u)$ and $\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively.
+In this case, the common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if $\lambda_1\simeq\lambda_2$.
+This kind of label compatibility constraint is handled in a straightforward way in both CP and clique-based approaches:
+\begin{itemize}
+\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
+We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.
+
+\item For clique-based approaches, label compatibility is handled through the definition of the association graph, by restricting the set of matching nodes to pairs of nodes with compatible labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
+Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
+\end{itemize} 
+Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.
+
+The extension of MCS algorithms to directed graphs is straightforward: For CP, edge orientation is handled in edge constraints; for clique-based approaches, it is handled in the definition of the association graph edges.
+In both cases, adding orientations to edges usually simplifies the problem: It tightens edge constraints for CP, and it makes the association graph sparser for  clique-based approaches.
+
+\section{Re-Evaluating the Clique Model}\label{eval1}
 
@@
 
-\subsection{Reduction to Maximum Clique in an Association Graph}
+\subsection{Datasets}
 
-Explain association graph \cref{figure:association}, cite history \cite{LeviG}, connections to
-microstructure \cite{DBLP:conf/aaai/Jegou93a}.
+\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}
 
-Discuss how edge labels, vertex labels, directed edges, etc, are handled. Note that we can generally
-only handle very local side constraints, or injectivity (which is decomposable).
-
-\begin{figure}[tb]
-    \centering
-    \begin{tikzpicture}[scale=0.33]%{{{
-        \begin{scope}
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 10) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 8) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 8) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Md) at (4, 8) {\phantom{0}};
-
-            \node [right = 0 of Ma, font=\small] { \vphantom{0}a };
-            \node [below = 0 of Mb, font=\small] { \vphantom{0}b };
-            \node [below = 0 of Mc, font=\small] { \vphantom{0}c };
-            \node [below = 0 of Md, font=\small] { \vphantom{0}d };
-
-            \draw [very thick] (Mb) -- (Mc);
-            \draw [very thick] (Mc) -- (Md);
-            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [color=uofgsandstone!40] (Ma) to [out=150, in=80, looseness=8] (Ma);
-            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
-        \end{scope}
-
-        \begin{scope}
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
-
-            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
-            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
-            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
-            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
-
-            \draw [very thick] (M1) -- (M2);
-            \draw [very thick] (M2) -- (M4);
-            \draw [color=uofgsandstone!40] (M3) -- (M4);
-            \draw [color=uofgsandstone!40] (M1) -- (M3);
-
-            \draw [color=uofgsandstone!40] (M3) to [out=280, in=210, looseness=8] (M3);
-            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
-        \end{scope}
-
-        \begin{scope}[xshift=15cm]
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
-            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
-            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
-            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
-            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Ma1.north west) -- (Ma4.north east)
-            node [midway, above=0.7cm] { $a \mapsto$ };
-
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
-            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
-            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
-            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
-            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mb1.south west) -- (Mb4.north west)
-            node [midway, left=0.7cm] { $b \mapsto$ };
-
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
-            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
-            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
-            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
-            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mc4.south east) -- (Mc1.south west)
-            node [midway, below=0.7cm] { $c \mapsto$ };
-
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
-            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
-            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
-            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
-            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
-            node [midway, right=0.7cm] { $d \mapsto$ };
-
-            \begin{scope}[on background layer]
-                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
-                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
-                \draw [draw=uofgsandstone!40] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
-                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
-                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
-                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
-        \end{scope}
-        \end{scope}
-
-    \end{tikzpicture}
-
-    \caption{A maximum common induced subgraph between the two graphs on the left has three
-        vertices---one solution is highlighted. On the right, the association graph encoding: the
-        highlighted clique of size three shows the same solution. In practice the isolated vertices
-        (corresponding to assignments between incompatible vertices, which are unary constraints) would be
-        omitted.}\label{figure:association}
-\end{figure}
-
-?? Discuss the partial version briefly, cite the reduction.
+?? More? Can we scale to some of the SIP graphs?
 
@@
 
-\section{Find Maximum Common Connected Subgraphs}
+\section{Find Maximum Common Connected Subgraphs}\label{mccs}
 
@@
     \centering
+    \input{gen-graph-connected-cp.tex}
+    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
+    number of instances with these runtimes, with darker colours representing more instances. The
+    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
+    rows are for unlabelled and undirected graphs with up to 35 vertices.}
+        \label{figure:connected-cp}
+\end{figure}
+
+\begin{figure}[p]
+    \centering
     \input{gen-graph-connected-cumulative}
@@
         left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
-\end{figure}
-
-\begin{figure}[p]
-    \centering
-    \input{gen-graph-connected-cp.tex}
-    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
-    number of instances with these runtimes, with darker colours representing more instances. The
-    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
-    rows are for unlabelled and undirected graphs with up to 35 vertices.}
-        \label{figure:connected-cp}
 \end{figure}

### 2016-04-10 paper/paper.tex
Filtering and datasets

@@
 
-\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}
+We consider a randomly generated database described in \cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}. 
+The dataset contains different classes of graphs: Randomly connected graphs with connectivity $\eta\in\{0.05,0.2\}$ (r005 and r02); 2D, 3D, and 4D regular meshes (m2D, m3D, m4D); 2D, 3D, and 4D irregular meshes with $\rho=0.6$ (m2Dr, m3Dr, and m4Dr); regular bounded valence graphs with $V\in\{3,9\}$ (b03 and b09) and irregular bounded valence graphs with $V\in\{3,9\}$ (b03m and b09m).
+Each class contains XXX pairs of graphs: YYY for each of the 5 possible sizes of the MCIS ({\em i.e.}, 10\%, 30\%, 50\%, 70\% and 90\% of the number of nodes of the original graphs).
 
-?? More? Can we scale to some of the SIP graphs?
+For each pair of graphs, there are 3 different labelings such that the number of different labels is equal to 33\%, 50\% or 75\% of the number of nodes.
+In this paper, we report experiments with non labelled graphs (labels are ignored), and with 33\% labellings.
 
 \subsection{Experimental Evaluation}
-
-?? Break this down more by family, size, etc.
 
@@
 
-\subsection{Filtering from Edge Labels}
+Fig. \ref{figure:unconnected-cumulative} displays the cumulative number of instances solved with respect to time. 
+When graphs are labelled (top plot), the clique-based approach clearly outperforms CP. ...develop...
 
@@
 
-Connectedness is not hereditary, but can be built up one vertex at a time. Alternatively,
-connectedness is a constraint.
+In many applications, the common subgraph must be connected.
+As illustrated in Fig.
+\ref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: We need to ensure connectedness during the search.
+In Section \ref{mccs-cp}, we show that this may be done in two different ways that may be combined, and we show in Section \ref{mccs-cp-eval} that the best results are obtained when combining them.
+In Section \ref{mccs-clique}, we introduce a new way for ensuring connectedness in a clique-based approach.
+Finally, we compare CP and our clique-based approach in Section \ref{mccs-eval}.
 
-\subsection{Connectedness as a Constraint}
+\subsection{Ensuring Connectedness in CP}\label{mccs-cp}
 
-Connectedness \cite{Brown:2005}
+\paragraph{Ensuring connectedness with a specific branching rule.}
+In \cite{DBLP:conf/mco/VismaraV08}, the connectedness constraint is ensured by using a specific branching rule, used to select the next variable to be assigned.
+Let $CComp$ be the set of variables already assigned to values different from $\bot$.
+The next variable to be assigned is chosen within the set of non assigned variables which are neighbor of at least one vertex of $CComp$.
+When this set is empty, all remaining non assigned variables are assigned to $\bot$.
 
-Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}
+\paragraph{Ensuring connectedness with a specific filtering.}
+Another way to ensure connectedness is to filter domains to ensure connectedness consistency.
+Let us consider two graphs $G$ and $G'$, and let $D$ be the current domains (we suppose that $D(x_u)$ is a singleton when $x_u$ is assigned).
+Let $C$ (resp.
+$C'$) be the set of nodes of $G$ (resp.
+$G'$) which may belong to the common subgraph, {\em i.e.}, $C=\{ u\in N_{G}, D(x_u)\neq\{\bot\}\}$ (resp.
+$C' = \{u'\in N_{G'}, \exists u\in N_G, u'\in D(x_u)\}$).
+Let $G_{\downarrow C}$ (resp.
+$G'_{\downarrow C'}$) be the subgraph of $G$ induced by $C$ (resp.
+the subgraph of $G'$ induced by $C'$).
+The connectedness consistency ensures that both $G_{\downarrow C}$ and $G'_{\downarrow C'}$ are connected graphs.
 
-\subsection{Connectedness via Restricted Branching}
+Connectedness consistency is not ensured at the root node of the search.
+It is ensured only once a first variable has been assigned.
+Let $x_u$ be the first assigned variable and $u'$ the value assigned to $x_u$.
+To ensure connectedness consistency, we perform a traversal of $G$ (resp.
+$G'$), starting from $u$ (resp.
+$u'$), and we initialize $C$ (resp.
+$C'$) with all visited nodes.
+Then, for each node $v\in N_G\setminus C$ (resp.
+$v'\in N_{G'}\setminus C'$), we assign $x_v$ to $\bot$ (resp., we remove $v'$ from all domains it belongs to).
+
+During the search, each time a variable is assigned to $\bot$, we remove the corresponding node from $C$ and perform a new traversal of $G_{\downarrow C}$ starting from the initial node $u$.
+For each node $v\in C$ that is not visited by the traversal, we remove $v$ from $C$ and assign $x_v$ to $\bot$.
+Also, each time a value is removed from a domain so that this value no longer belongs to any domain, we remove it from $C'$, and perform a new traversal of $G'_{\downarrow C'}$ starting from the initial node $u'$.
+For each node $v'$ that is not visited by the traversal, we remove $v'$ from $C'$, and remove $v'$ from all domains it belong to.
+
+\christine{We have to relate this basic filtering with existing work: Connectedness \cite{Brown:2005} Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}.
+
+Samba and I have tried to find more clever ways for doing this filtering (in an incremental way).
+But we failed in finding something cheaper than performing a traversal each time a set of values are removed.
+In particular, we tried to adapt ideas from the paper of Patrick, but the problem is that we have to maintain counters on edges, and these counters must be restored when backtracking, and this is as expensive as performing a traversal (?).
+Any brilliant idea to share with us on this point?}
+
+\paragraph{Combining both approaches.} The two approaches for ensuring connectedness (branching and filtering) are complementary and may be combined: At each step of the search, we select the next variable to be assigned within the neighbors of $CComp$, and each time a node of $G'$ is removed from a domain we filter domains to ensure connectedness consistency.
+
+\subsection{ Experimental comparison of CP models}\label{mccs-cp-eval}
+
+\begin{figure}[p]
+    \centering
+    \input{gen-graph-connected-cp.tex}
+    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
+    number of instances with these runtimes, with darker colours representing more instances. The
+    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
+    rows are for unlabelled and undirected graphs with up to 35 vertices.}
+        \label{figure:connected-cp}
+\end{figure}
+
+\christine{I propose that we report results only for the FC variant (or only for the MAC variant) as the conclusion is the same in both cases?}
+
+Fig.
+\ref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by specific branching (Branch), by specific filtering (Filter), or by combining specific branching and filtering (Both).
+We only report results obtained with the "FC+Bound" combination as the effect of the three approaches are very similar when combining them with "MAC+Bound".
+
+On labelled graphs, we observe that Branch often outperforms Filter, and that combining both Branch and Filter is rarely much worse than just doing one or the other, and is often much better, even if on average it's slightly slower.
+
+On unlabelled graphs, we observe that the three variants have rather similar performance.
+
+\christine{Could we have the number of instances solved within 1 hour for each approach, and also the average solving time (for instances that are solved by the three approaches), so that we can give an idea of how much faster an approach is?}
+
+\subsection{Ensuring Connectedness in a clique-based approach}\label{mccs-clique}
+
+\christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}
 
@@
 ?? Patrick reckons this reminds him of Prim's algorithm for minimum spanning trees.
-
-\subsection{Connectedness in an Association Graph Algorithm}
 
@@
 
-\subsection{Experimental Evaluation}
+\subsection{Experimental comparison of CP with the Clique-based Approach}\label{mccs-eval}
 
@@
 difficulties, and result sizes?
-
-\begin{figure}[p]
-    \centering
-    \input{gen-graph-connected-cp.tex}
-    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
-    number of instances with these runtimes, with darker colours representing more instances. The
-    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
-    rows are for unlabelled and undirected graphs with up to 35 vertices.}
-        \label{figure:connected-cp}
-\end{figure}
 

### 2016-04-11 paper/paper.tex
Muck around with the graphs a bit, add some FC

@@
         labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
-        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the two
-        models, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
-        the right.} \label{figure:unconnected-cumulative}
+        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the clique
+        model with the best CP model, with 33\% labelled graphs (with MAC) on the left, and
+        unlabelled and undirected graphs (with FC) on the right.} \label{figure:unconnected-cumulative}
 \end{figure}

### 2016-04-12 paper/gen-graph-unconnected-heatmap.tex
Muck around with the graphs a bit, add some FC
More FC data

@@
 %% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
-%% Thu 07 Apr 2016 11:12:12 BST
+%% Tue 12 Apr 2016 14:19:16 AEST
 \tikzset{every node/.append style={font={\scriptsize}}}
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffff8c72ff9f7d%
-  ffac88ff8c72ff9f7dff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffd01d45ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ca1941ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dff9f7dffac88ff9f7d%
+  ff9f7dffac88ff9576ff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffcf1d45ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffca1941ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffc6163dffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffc6163effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ff9576ffffffffac88c7173fffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffffffc1133affffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffac88%
+  ffffffffffffffffffffffffffffffffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ff9f7dc6163effffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88%
+  ffffffffffffffac88ffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffc4143cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffac88ffac88ff9f7dffac88ff9f7dffffffc3143b%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffff9f7d%
+  ffac88ffffffffffffff9f7dc1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffac88ffffff%
+  ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88c4153cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffff9576ffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88c2133affffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffffffff9576ffac88%
+  ff9576ffffffff9f7dc6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
+  ffac88ffffffffac88ffac88ffffffffac88ffac88ff846ec01239ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7d%
+  ffffffffffffffffffffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffc4153cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
+  ffffffff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
+  ff9f7dffffffbd0f36ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88%
+  ff9f7dffac88ff9576ff9f7dff9576ffffffffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffac88%
+  ffac88ffffffff9f7dffffffffac88ffac88ff9576ffffffffac88ff9f7dff9576ffffffc1133affffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffff%
+  ff9f7dffffffffffffffffffffac88ffffffffffffffac88ff9f7dff9576ffffffffac88ffffffff9f7dff9f7dff8c72%
+  ff9f7dc01238ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffac88ffffffffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffc6163effffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffc6163dffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffc6163effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffac88ffffffffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffc1133affffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffffffffffffff9f7dffffffff9576ffac88ffac88%
+  ffac88ff9f7dff9576ff846effac88ffac88c1133affffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffffffffffffffac88ff9f7d%
+  ffffffff9f7dff9576ff9f7dffac88ff9576ffac88ff9f7dff846eff8c72ff8c72c3143bffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ffac88ffac88%
+  ffffffff9f7dff9f7dff9f7dff9f7dffac88ff9f7dffac88ffac88ffac88ff846eff9576ff9f7dff9f7dff9f7dff9576%
+  c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffffffac88ffac88ffac88ff9576ffac88ffffffffac88%
+  ff9576ff9576ff846eff846effffffbd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9576ff846eff9f7dffffffff9f7d%
+  ffffffffffffff9f7dffffffff9f7dffffffff9576ff9576ffac88ffac88c01239ffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffc7173fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9576%
+  ffac88ffac88ff9f7dff846effffffffac88ff846eff9576ff9576ffac88ff8c72ff9f7dff8c72ffffffff9f7dbf1138%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffac88ffffff%
+  ffffffffac88ffffffffac88ffffffff9576ff9f7dffac88ff8c72ff9576ff8c72ffac88ffac88ff9f7dff9f7dffac88%
+  ffffffff8c72ff846effac88c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ffffffff9f7dff9f7dffac88ffac88ff8c72ff9f7dff9f7d%
+  ff8c72ff9576ff8c72ff9f7dff8c72ff9f7dff846eff8c72ff7e6cc11239ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffac88ff9f7dffac88%
+  ffac88ffac88ff9f7dff7e6cffac88ff9f7dffffffff9576ff9f7dff9576ff9f7dff9576ffac88fb605fc2133bffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffac88%
+  ffffffffac88ffffffff846eff846eff9576ffac88ff846effffffff8c72ff9576ff9f7dff9576ff846effac88ff7869%
+  ff7e6cff9576ff8c72c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
+  ffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffac88ff846eff846eff9576ff7869ffffffff8c72ffffff%
+  ff8c72ffac88ff8c72ff7e6cff9576ff8c72ff846eff9576c01239ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffac88ff9f7dffac88ff9576%
+  ffac88ffffffff846eff9f7dff8c72ff846eff7e6cff9f7dff7869ff9576ff7e6cff8c72ff7e6cc1133affffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576%
+  ff8c72ff9576ffac88ff7e6cffac88ff9f7dffac88ff846eff8c72ff9f7dff9576ff9576ff7367ff6f65ff846eff8c72%
+  ff7e6cff7e6cc3143bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ffffffffac88ffac88ff9576ffac88ffffffffac88ffac88ff9576ff9f7dffac88ff7869ffac88ff9f7dff8c72ff7869%
+  ff8c72ff9f7dff7367ff7e6cff9576ff6f65ff7e6cc6163dffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffac88ffffff%
+  ffffffffffffffffffffffffff9576ffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9f7dffac88ff846eff7e6c%
+  ff7869ff846effac88ffac88ffac88ff9f7dff7e6cffac88ff846eff7869ff8c72ff8c72c4153cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffac88ffffffffac88ff8c72ffffffffffff%
+  ff8c72ff9f7dff9f7dff9576ff7869ff9f7dff7e6cff7869ff8c72ffac88ff7869ffac88ff8c72ff8c72ff7869ff7e6c%
+  ff9576c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ff9f7dff9f7dffffffffac88ffffff%
+  ff9f7dffac88ff8c72ff8c72ff9576ffffffff9f7dffac88ff846eff7869ff9576ffffffff846eff9576ff8c72ff7869%
+  ff846eff9576ff7e6cff6b63ff7e6cff8c72cb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88%
+  ff9f7dff9f7dff9f7dff9576ffac88ffffffff8c72ff9f7dffac88ff8c72ff9f7dff8c72ff9576ff7e6cff7869ffac88%
+  ff8c72ff9576ff7869ff846eff7e6cff6b63ffac88ff9576ff846eff9576ff8c72c8183fffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ff9f7dffac88%
+  ffffffffffffffffffffffffffffffffac88ffac88ffffffff846effffffffffffffac88ff9f7dff7869ff8c72ff8c72%
+  ff9576ff8c72ff846eff9576ff7e6cff846eff846eff7e6cff7367ff7e6cff9576ff7e6cff8c72ff9f7dff9f7dff7e6c%
+  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dff9f7dffffffffac88ff9576ffac88ffac88%
+  ff9f7dffffffffac88ff846effffffffac88ff9f7dff846eff6f65ff7367ff846eff9576ff8c72ff846eff846eff7e6c%
+  ff9576ff846eff8c72ff8c72ff6b63c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffffffffffffac88ffffff%
+  ffffffffffffffac88ff7e6cff846eff9576ff846eff9f7dff846eff7e6cff9f7dff7e6cff7869ff8c72ff7e6cff9f7d%
+  ff846eff8c72ff9f7dffac88ff9576ff846eff8c72ff7367ff846effac88c7173effffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
+  ffac88ffffffffffffffffffffac88ffac88ff9576ff9576ffac88ffac88ff9576ff9576ffac88ff9f7dff9576ff9576%
+  ff9576ff7e6cff9576ff7e6cff7e6cff846eff8c72ff9576ff7869ff8c72ff7869ff7e6cfd6561fe6862ff7e6cc6163e%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
+  ff9f7dffffffffffffffac88ffffffffac88ff9f7dffac88ffffffffffffffac88ffac88ff8c72ffac88ff846effac88%
+  ff846eff7e6cff8c72ff7e6cff7e6cff846eff8c72fd6561ff7869ff7869ff9576ff7e6cff9576ff8c72ff7e6cffffff%
+  ff9576ff7869ff8c72ff7367c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
+  ffffffffffffff9f7dffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff8c72ffac88%
+  ffac88ff9f7dffffffff7e6cff9f7dffac88ff9576ff846eff7e6cfe6862ff846eff7869ff8c72ff6f65ff7367ff9576%
+  ff7869ff846eff9f7dff7e6cfc6260ff9f7dff7869ff8c72ff7869cc1a42ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffffffffac88ffffffffac88ffffffffffffffac88ffac88ffffffffac88ffffffffac88ff9f7dffffffffac88%
+  ff9f7dff9f7dffffffffac88ff8c72ff9f7dff846effac88ff846eff9f7dff846eff9576ff8c72ff7e6cff6f65ff7869%
+  ff7367ff846eff7869fe6862ff9576ff7869ff7e6cff6b63ff7e6cff7e6cff9576ff846eff7869ff846ec8183fffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffff%
+  ff9f7dffffffffffffffac88ffac88ff9f7dff9f7dff9576ffac88ffffffffac88ff8c72ff7869ff7869ff8c72ff9576%
+  ff7367ff7869ff8c72ff8c72ff7367ff846eff7869ff846eff6f65ff846eff846eff7e6cff7869ff8c72fd6561ff9f7d%
+  ff9576ff846eff9f7dcb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
+  ff8c72ffac88ffffffffffffffffffffac88ffac88ffffffffffffffac88ffac88ff9f7dffac88ffffffffac88ff8c72%
+  ff9576ff8c72ff9576ff9576ff7e6cff9f7dff6f65ff7869ff6b63ff7869ff7869ff846effac88ff846eff7367ff7e6c%
+  ff6b63ff7869ff6f65ff8c72ff846eff846eff6b63fe6862ca1940ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9f7dffffff%
+  ffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffffffff9f7dff9f7dffffff%
+  ffac88ff9f7dffffffff9f7dff9576ff846effffffff8c72ff8c72ff9576ff6f65ff7e6cff6b63ff7e6cff846efe6862%
+  ff6f65ff8c72ff6b63ff846eff7869ff8c72ff7869ff9576ff7869ff7869fe6862ff6f65ff6f65d42148ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
+  ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffff9f7dffffffffac88ffac88ff9f7dff9576ffac88%
+  ffac88ffac88ffffffff8c72ff9f7dff9f7dffac88ff8c72ff8c72ff9f7dffac88ff846eff9576ff8c72ff7e6cff7367%
+  ff7367ff7e6cff7e6cff6f65ff7e6cff7367ff7869ff7e6cff7869ff8c72ff7367ff846eff8c72ff7869ff7e6cff7367%
+  ff6b63ff9576d11e46ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffac88ffac88ffac88ffac88ffac88ffffff%
+  ffac88ffac88ffffffff9f7dffac88ff9576ff846eff9f7dffac88ff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7d%
+  ff8c72ff7869ff7869ff7e6cff846efd6561fd6561ff6f65fe6862ff7869ff7367ff8c72ff7869ff7367ff7869ff8c72%
+  fe6862ff8c72ff846eff7367ff6b63ff846eff7e6cd11e46ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ffac88ffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dffac88ffac88ffffffffac88ff9576ffffff%
+  ff9f7dff8c72ff9f7dff8c72ff8c72ff9f7dff7869ff7e6cff846eff6b63ff846eff6b63fb605fff7e6cff9576ff8c72%
+  ff7869ff7869ff7e6cff846eff6f65ff7869ff7869ff6b63ff6f65ff9f7dff7367ff846ed21f47ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffff9576ffac88ffac88ffac88ffac88ffac88ff9f7dffac88%
+  ffffffffac88ffac88ffffffffffffff9f7dffac88ff9576ff6b63ff7e6cff9f7dff7869ff7e6cff9576fe6862ff846e%
+  fd6561ff6b63ff6f65ff846efe6862ff6b63ff9576ff6b63fd6561ff846eff9576ff8c72ff846eff8c72ff7e6cff7869%
+  ff7869cd1c43ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ff9576ff9f7d%
+  ff9f7dff9576ffac88ffffffffac88ff9576ffac88ffffffff9f7dffffffffffffff8c72ff9576ff9576ff846eff7869%
+  ff9576ff9576ff6f65ff7e6cff6f65ff7367ff846eff7869ff6f65ff846eff7869ff6f65ff8c72ff9f7dff6f65ff7367%
+  ff6f65ff6f65ff8c72ff9f7dff7e6cff846ed01e45ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ff9f7d%
+  ffac88ffac88ff9f7dffac88ffffffff9f7dff9f7dff8c72ffffffff7e6cff9576ff8c72ffac88ff9f7dff9576ff9576%
+  ff8c72ffffffff9f7dff846eff6b63fe6862ff7e6cfa5e5ffd6561ff6f65ff7869fd6561ff6f65ff6f65ff9576ff9576%
+  ff6f65ff846eff7367ff846eff6f65ff7e6cfd6561ff6f65fd6561ff846eff7e6cd52248ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88%
+  ffac88ffffffffffffffffffffac88ffac88ff9f7dffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffac88%
+  ff8c72ff9f7dff9576ffac88ff9f7dff846eff8c72ff846eff7367ff7e6cff6f65ff8c72ff846eff6b63fe6862f95c5e%
+  ff7367ff6f65ff846eff9f7dff7e6cff6f65ff7e6cff7869fe6862ff7e6cff7869ff9f7dfe6862ff846eff846eff7e6c%
+  d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffac88ffffffff9576ffac88ffffffff9576ffffffffac88ff8c72ff9576ff846effffff%
+  ffffffff6f65ffac88ffffffff9f7dff9576ff9f7dff9f7dff846eff6f65ff7367ff7869ff846eff846eff8c72ff7367%
+  fc6260ff7e6cfe6862ff6f65ff6b63ff6f65ff7367ff6b63fe6862ff6b63ff846eff6f65ff7869ff7869ff7367ff7869%
+  ff7869ff6f65ff7e6cff7367fe6862d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ff9f7dff7e6cffac88%
+  ff9f7dffac88ffac88ffffffff6f65ff9576ff7367ffac88ff846effac88ff846eff7e6cff7e6cff7e6cff6f65ff7367%
+  ff8c72fe6862ff7869ff7869fb605fff7e6cff6f65ff7367ff7367fc6260fc6260ff846eff7869ff7367ff7869ff7367%
+  ff846efd6561ff7869ff846eff6b63ff7367ff7869ff7367ff846eff7367d62449ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ff9f7dff8c72ff9f7dffac88ff8c72ffac88ff9576ff8c72ff9576ff8c72ff9576ff9576ff8c72%
+  ff9f7dff9576ff8c72ff7869ff7869ff6b63fd6561ff6b63ff7367ff7367ff7869ff7367ff7869fe6862fb605fff6b63%
+  ff6b63fd6561ff7869fe6862ff7367ff6f65ff6f65ff7367fe6862ff6b63ff6f65fe6862ff9576ff9f7dff7e6cd62449%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
-  ffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffc6163effffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffffffffffff%
-  c91840ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffac88ffffffffffffffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff9f7dffac88ffffffffffffffffffffac88c4143cffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7d%
-  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff9f7dffac88ffffffc3143b%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88%
-  ffac88ffffffff9f7dffffffc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88%
-  ffac88ffac88ffffffffac88ffffffffffffffffffffac88ffffffc4153cffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffff9f7dff9f7dff9f7dffac88ffffffc2143bffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9576ff9f7dff9f7dffac88%
-  ffffffffffffffac88c6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffff%
-  ffffffffffffff9576ffac88ff9576ffffffff8c72ffffffc11239ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffff9f7dffffffffac88ffac88ffffffff9f7dff9f7dffffffff9f7dffffffff9f7dc5153cffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffffff8c72ffffffff9576%
-  ffffffff9576bd1037ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffffff%
-  ffac88ffac88ff9576ff9f7dff9f7dff9576ffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
-  ffac88ff9f7dffac88ffffffffac88ff9f7dff9f7dff9f7dff9f7dff9576ffac88ff9f7dc2133bffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffff9576ffac88ffac88ffffffffac88ff8c72ffffffffac88ff8c72ff8c72%
-  ffffffc01239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7dffac88ffac88ffac88ffffffffac88ff9f7dffac88%
-  ff9f7dffac88ff9576ff9f7dff9f7dff9f7dc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffac88%
-  ffac88ff8c72ff9576ffac88ffac88ff9f7dff9576ff846effac88ff846eff846ec4143cffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffffff%
-  ffac88ffac88ff9f7dff9f7dff9576ff9f7dff9f7dff9576ff9f7dff9576ff9f7dff9576ffac88ff9576ff9f7dff8c72%
-  c1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9576ffac88ffac88ff846effac88ff9f7d%
-  ff9f7dff9576ff9f7dffffffff9576bd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff9f7dffac88ff9f7dff9f7dff9f7dff9576ffffff%
-  ffac88ffac88ffffffff9576ffffffff9576ff846eff9f7dffac88ff9f7dc11239ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576%
-  ff8c72ffffffff9f7dff9f7dff9576ff8c72ff9f7dff9f7dffac88ff9f7dff9f7dff9576ff9f7dff9576ff9576bf1138%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffffffffac88ffffff%
-  ffffffff9f7dffffffffffffff9f7dff9576ff9576ff9576ffac88ff9576ffffffffffffffac88ff846eff9f7dff9576%
-  ff846effffffffac88ff9f7dc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9f7dffffffffffffffac88ffffffffffffff9f7dff9f7dffffffffac88ff8c72ff8c72ff9f7dff7e6cff9f7d%
-  ff8c72ffffffff9576ffac88ff7e6cff9576ff7e6cff846eff7869c2133affffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffac88ffac88ffac88ffac88%
-  ff9576ffac88ff9f7dffac88ff9f7dffac88ff8c72ffac88ff9576ffac88ff9576ff8c72ff7e6cff846ec2133affffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
-  ffffffffffffff9f7dffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffffff%
-  ffac88ff846eff9576ff9f7dff9f7dffac88ff8c72ffac88ff9576ffac88ff7869ff8c72ff846eff9f7dff9f7dff846e%
-  ff7e6cff6b63ffffffc5163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ff9f7dffac88ffac88ffac88ffffffff9576ffac88ff9576ff846eff9576ff9576ff8c72ff9576ff9f7d%
-  ff8c72ff9f7dff7869ff846eff7e6cff7e6cff8c72ff8c72c1133affffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffffffffac88ffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff846effac88%
-  ff8c72ff9f7dff8c72ff9576ff846eff846effac88ff7367ff7e6cff8c72ffffffff7367ff8c72c2133bffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ff9f7dffffffffac88ffac88ff846eff8c72%
-  ffac88ffac88ff7e6cff9f7dff9576ff846eff9576ff9f7dff9f7dff9f7dff7869ff7367ff846eff9576ff846eff7e6c%
-  ff7e6cff7e6cc4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
-  ffac88ffac88ffffffff9576ffffffff9f7dff9576ff9576ffffffff9576ff8c72ff8c72ff7869ff9576ff8c72ff8c72%
-  ff8c72ff9576ff7e6cff7e6cff7367ff9f7dff7e6cc7173effffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88%
-  ffac88ffffffff9f7dffffffffffffffffffff9f7dffffffff9f7dffac88ff9576ff9576ff846eff9576ff7869ff8c72%
-  ffffffffac88ffac88ff8c72ff9576ff7e6cff9576ff7e6cfe6862ff9f7dff9f7dff7367c6163effffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7d%
+  ffac88ffac88ffffffffffffffac88ffac88ffac88ffac88ffffffff846eff9f7dff8c72ff8c72ff9576ff7869ff8c72%
+  ff7367ff9f7dff8c72ff7367ff6b63ff846eff6f65ff9576ff7e6cff8c72ff7367ff6f65ff7e6cff6f65ff6b63ff6b63%
+  ff6f65fe6862fd6561ff7869fe6862ff6f65f7585dfb605ffb605fff6f65ff7367fd6561ff6f65ff6f65ff7367ff8c72%
+  ff7367ff9f7dff7e6cff8c72db2a4cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
+  ffac88ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ffffffffac88ff7e6cffac88ff8c72ff9f7dff8c72%
+  ffac88ff8c72ff7367ff9576ff9576ff846eff9f7dff8c72ff6b63ff846efd6561ff846efe6862ff7869fc6260ff6f65%
+  ff7869ff6f65ff6f65ff6b63ff6f65fb605ffc6260ff7367fd6561f95c5eff6f65ff7367ff7367ff7367ff6f65fb605f%
+  f6545cff7869ff7869ff6b63ff6b63fc6260fc6260ff8c72ff7367db2a4cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9576ff9f7d%
+  ffac88ff846effac88ffac88ffac88ff7e6cff9f7dff7869ff846eff8c72ff846eff7367ff8c72ff7869ff7e6cff7869%
+  ff7e6cff8c72ff9f7dff7e6cff8c72ff6b63ff6f65fe6862ff7367fa5e5fff846efc6260ff7869ff6b63ff6b63ff7367%
+  fe6862ff7869ff6b63fe6862f95c5ef95c5eff7869ff6b63fe6862ff6f65fe6862ff7869ff846eff7e6cda294bffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ffffffffffffffffff%
+  ffac88ffac88ffac88ff9576ffac88ff7e6cff9f7dff846eff9576ff8c72ff7367ff846eff846eff6b63ffac88ff7e6c%
+  ff7869ffac88ff6b63fd6561ff7367fd6561fd6561ff6b63fa5e5ff95c5eff6b63ff7869fc6260ff6f65ff6b63ff6f65%
+  fe6862fc6260ff7367fb605ff85a5df7565cff6b63ff6f65ff6b63fc6260fe6862fd6561ff7367fb605fff6f65ff7367%
+  ff7869fe6862ff6f65de2d4dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffff%
+  ffac88ffac88ffac88ff9f7dffac88ff9f7dffac88ffac88ff846eff9576ffac88ff9f7dff7e6cff6b63ff7e6cff846e%
+  ff6f65ff7e6cfd6561ff6f65ff6b63f95c5efe6862fd6561ff9576fc6260ff6b63ff6f65ff7367fe6862ff7367fc6260%
+  f85a5df95c5efc6260f95c5efc6260fa5e5fff6f65ff7367fe6862fa5e5fff6f65f7565cfd6561ff7367fb605ff85a5d%
+  fe6862ff7367fd6561ff7367ff846eff9576ff7869ff7869e1324fffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffffffff8c72ffac88ff9576%
+  ff9576ff9f7dff7e6cff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7dffffffff8c72ffffffffffffff9f7dffac88%
+  ff9f7dff9576ff9f7dff9f7dffffffff9f7dffffffff9576ff9f7dffac88ff9f7dff9576ff9f7dff8c72ff9f7dff7367%
+  ff9f7dff846eff7869ff7869ff7869ff9576ff7367f7585df7585dfe6862ff6f65ff7869fe6862fb605fff6b63ff9576%
+  fe6862fd6561f95c5efa5e5ff7585dfc6260f7585df5515bf14958f6545cf95c5ef95c5ef14958ff6f65f6545cf7585d%
+  f95c5ef85a5dfe6862ff7e6cff7869fe6862ff6f65ff6b63ff7869ff6b63ff6b63ff6f65ff6b63e1324fffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7e6cff846eff6b63ff7367%
+  ff6f65ff6b63ff6f65ff7869fd6561f5515bff6b63ff7869ff7367ff6b63ff7869ff7869ff846eff6f65ff6b63ff7e6c%
+  ff9576ff7367ff9576ff7367ff9576ff9576ff9576ff8c72ff846eff8c72ff846eff9f7dffac88ff846eff9576ff7869%
+  ff9576ffac88ff9576ff9f7dff7e6cfb605fff7e6cfd6561ff7367fc6260f95c5ef95c5ef7585df34d59f6545cfb605f%
+  ff7e6cf95c5eff6b63ff6b63fd6561fb605ff5535bf95c5ef34d59f85a5df85a5df7585df95c5efa5e5ff7585df95c5e%
+  f7585dfa5e5ff85a5df4505af7585dfb605ffa5e5ffe6862fe6862fb605fff6f65fa5e5fff6f65ff6b63ff7367fe6862%
+  fd6561ff7e6ce23350ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ff9f7dff6b63f5515bf7585dfc6260f7565cf34d59f34d59f5515bfd6561f5535bfb605ffa5e5ffb605ffd6561fe6862%
+  fd6561fa5e5fff6b63fc6260f85a5dff6b63ff7e6cfb605fff6b63ff7367fd6561ff6b63ff6f65ff7367ff6f65ff7e6c%
+  ff8c72ff7869ff8c72ff9f7dff8c72ff6f65fe6862fd6561ff6b63ff7367ff7869ff6b63f85a5dfd6561fc6260fd6561%
+  f95c5efa5e5ff34e5af85a5df85a5dfd6561fc6260fc6260fa5e5ff7565cfa5e5ffd6561fa5e5ffd6561f7585df95c5e%
+  f7565cf5535bf5535bf6545cf04757f7585df5515bf4505afa5e5ff85a5df7585df7565cfd6561fa5e5fff7869ff6f65%
+  fd6561fa5e5fff7e6cff846eff846eff846eff6f65e33550ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ff8c72f95c5ef34e5af34d59f04757f14858ef4356ee4256f5535bef4457f4505a%
+  f5535bf5535bfe6862f34d59f4505afa5e5ff85a5df6545cfb605ff85a5dfa5e5ffb605fff6f65f7585dff7e6cff7869%
+  ff6b63fe6862ff7367ff7367ff7e6cff7869fe6862fc6260fe6862fe6862fc6260fc6260f7565cff7367f85a5df85a5d%
+  fb605ffc6260f85a5df34e5af24b59f34e5afa5e5ff5515bf34d59f7585dfa5e5ff7585df6545cf7565cf24a59f95c5e%
+  f6545cf7585df24b59f95c5ef7565cf95c5ef5515bfa5e5fff6f65f5515bf7565cf6545cfa5e5ffb605ff95c5efc6260%
+  fa5e5ffd6561fd6561fe6862fe6862ff6b63ff7869ff7367ff8c72ff6b63ff7869ff9f7de0314fffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff846eff7869fd6561fb605ff7565cf7565cf4505afc6260%
+  fd6561fc6260ff6b63fd6561fc6260fd6561fb605fff7e6cff6b63f95c5efd6561fc6260ff7e6cff6f65ff7367ff7869%
+  ff7367fc6260ff6f65fc6260ff7e6cff6f65ff6b63fe6862fb605ffa5e5ff7565cff6f65f7565cf85a5dfa5e5ff6545c%
+  f5535bff6b63f5515bf5535bf95c5ef14958f04557f95c5ef5515bf24a59f85a5df34e5af7565cf34e5afb605ff7565c%
+  fa5e5ffc6260f6545cf95c5ef7585dfc6260f34e5af95c5ef4505af5535bf95c5ef95c5ef85a5dfa5e5ff6545cf95c5e%
+  f7565cf5515bfa5e5ffa5e5fff6f65f95c5efc6260fc6260fe6862ff7869ff7367ff7367ff6f65ff7e6cff7869ff8c72%
+  ff7e6ce83a53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff6f65f24b59f85a5d%
+  f7585df5535bf7585df24a59fb605ff95c5efb605ffe6862f85a5dff7869fa5e5ffe6862fd6561fa5e5ffd6561ff7869%
+  ff6b63ff9576fe6862fd6561fa5e5ff7565cff846eff7367fb605fff6b63fd6561f85a5dfb605ffd6561f6545cf7565c%
+  f4505aef4457f24b59f14958f24b59f14858f95c5ef14858f24a59f34e5af24b59f04757fd6561f24a59f7585df34e5a%
+  f14958f7585df04557f34d59f5515bf7585df34e5afb605ff34e5af6545cf7565cf7585df24a59f7565cf34d59f34e5a%
+  f34d59fc6260f24b59f85a5dff6f65f85a5df7585dfa5e5ffb605ffa5e5fff6f65f95c5efc6260fb605fff6b63ff6f65%
+  f95c5eff6b63fb605fff6f65ff8c72ff7869df2f4effffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ff9576ff6f65fb605ff14858f24b59f14858ef4457f04757f5515bef4457f6545cfb605ffe6862fa5e5ffb605ffa5e5f%
+  fe6862ff6b63fa5e5ffa5e5fff6b63fa5e5fff6b63f7565cfa5e5fff6b63f85a5df7565cfa5e5ffb605ffc6260f14958%
+  f14958f14858f14858f34e5af95c5ef04557ee4156f04757ef4457ef4356f5515bf04757f34e5af14858ef4457ed4155%
+  e73a52ee4156f4505aef4356f14858f04557f7585df24a59f7565cf14958f5535bf14858f34e5af34d59fa5e5ff7565c%
+  f24a59fa5e5ff14958f85a5df4505af95c5efa5e5ff6545cf85a5df95c5ef34d59f14958ff7e6cff6b63fb605ffd6561%
+  ff7367ff6f65fb605ffa5e5ffd6561fb605ffc6260ff6f65ff6f65ff6f65ff6f65db2b4cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffff6f65f04757ec4055ec4055e73a52e83b53ea3d54e33550ed4155f14858ee4256f5515b%
+  fa5e5ff85a5df6545cf5535bf6545cfe6862fa5e5ff85a5dfb605ffb605ffc6260fb605ff95c5ef6545cf34d59f5515b%
+  f7565cf7585df5535bf4505af34d59f5535bf5515bf5535bee4156f04757e73952e63852ec3f55ed4155ea3d54ec3f55%
+  e73a52e83a53ea3d54ea3d54e83a53e83a53e83a53ec3f55e53751e63852ec4055e63852e63852f24a59f04757ef4457%
+  ef4356f14858ed4155e93c53ee4256f5515bf24a59f4505af24a59f34d59fd6561ef4356f34d59f34e5ae93c53f7585d%
+  fd6561f85a5df85a5df24b59f7565cf7565cf7585df7585dff7367ff6f65ff6f65ff9f7dff7e6cff6f65ff6f65ff7869%
+  db2b4cffffffffffffffffffffffffffffffffffffffffffff7869e63852da2a4cdc2b4ce43551ea3d54e43551ec4055%
+  eb3e54f34e5aee4256f34d59f14858f5535bf34e5af95c5ef85a5dfc6260fc6260fe6862fd6561fb605ff34d59ff6b63%
+  f4505afa5e5ff7565cfc6260fc6260f5515bf85a5df5535bfc6260f4505aea3d54f14858f34d59ee4256e83b53ed4155%
+  ed4155ee4156f34e5ae83a53e53751e43651ec3f55e63852e73a52e23350ea3d54ea3d54e73a52eb3e54e63852e73a52%
+  e73952e53751ec4055ee4156f04757ef4457f6545ceb3e54ef4356f04757f4505af7585df04557f4505af5535bef4457%
+  f5515bf24b59fc6260ff6b63fd6561fe6862fa5e5ffc6260ff6b63fe6862fe6862f85a5dff7367ff7869ff6f65ff7869%
+  ff6f65ff6f65ff846eff7869ff846ee33450ffffffffffffffffffffffffffffffffffffffac88e63852da2a4cd11e46%
+  d7264ae2324fdc2b4ce53651e83b53f24a59f34e5af85a5dff7869f7565cfb605ff4505aff7367f85a5df5515bff7367%
+  ff7367ff6b63f95c5eff6b63f85a5df7585df5515bf14958fe6862f7565cf95c5ef5535bf34d59f14958ef4356f04757%
+  f04557f04557f34e5af14858f7585dea3d54ec3f55ee4256ef4356eb3e54e43651e63852e23350f14958e43551e53751%
+  e43651ee4156ec4055e33450e93c53ea3d54ec3f55eb3e54f34d59eb3e54ef4457ee4156ef4457ee4256f5535bf5515b%
+  f4505af5515bf5535bf7585dff6b63f7585df5535bfc6260ff6f65fc6260ff8c72ff6b63fe6862ff7367ff846eff8c72%
+  ff7367ff7869ff9576ff7869ff8c72ff9576ff846eff9f7dff9576ff9f7df34d59ffffffffffffffffffffffffffffff%
+  ffffffff7e6cd01e45ce1c44d21f47d7254ae2324fe83b53eb3e54e83a53f14858f34d59f14958f7585df7565cf7565c%
+  fe6862f95c5efb605ff5535bf5515bf5535bf7585df7565cf14858ef4457e93c53f24b59e93c53f24a59e83a53ee4256%
+  f14958e63852e83b53e73952ea3d54ea3d54e73952e83b53ed4155e23450e43651e73a52e63852e73952e63852e53651%
+  e83a53e93c53e73952e73a52ea3d54e63852e73a52e43551ee4156ee4256ec4055e43551ef4356ec4055f24a59f34e5a%
+  ff6f65f34d59ff6b63f5515bf85a5df85a5dfb605ffd6561fa5e5fff7367ff6b63ff7869ff6f65ff7e6cff8c72ff8c72%
+  ff7367ff7869ff9f7dff9f7dff9576ff9f7dff9f7dff9576ff9576ff9f7dff9f7dff9f7dffffffffac88ffffffe73a52%
+  ffffffffffffffffffffffffffffffffffffff7367d52349db2b4ce73952e73952f14858fb605ff5515bfa5e5ffa5e5f%
+  ff6b63ff6b63fa5e5ffd6561fa5e5ffb605ffa5e5ff5515bf7585df6545cf5535bf34d59f24a59f04757f34d59f4505a%
+  f24a59f4505aef4457f14958ea3d54ed4155e93c53f04557f04557e93c53ea3d54e93c53ec3f55ea3d54ee4256ef4356%
+  f24a59e93c53e63852ea3d54ea3d54ef4457f34d59f04557f04757ee4156f04557ee4256f5515bf14958f85a5df04757%
+  f34d59fb605ff85a5df7585df95c5efa5e5ffd6561fe6862ff7e6cff846eff7869ff9576ffac88ff7e6cff8c72ff9f7d%
+  ff7869ff9f7dffac88ff8c72ffac88ffac88ff7367ff9576ff9f7dff9576ff8c72ffac88ff9576ffac88ffac88ffac88%
+  ff9f7dffac88ffffffff9f7dee4156ffffffffffffffffffffffffffffffff9f7df95c5eea3d54f24a59f14858f5535b%
+  fc6260fa5e5ffa5e5ff7565cfc6260ff7869f7585df85a5dff6b63ff7869ff6f65f34e5afe6862fe6862fa5e5ff7585d%
+  f34d59f5515bf85a5df6545cfa5e5ff24a59f7585def4457fc6260f7565cf24a59f14858f85a5def4457f34d59f5515b%
+  f04557f14958f5515bf14958f04757ef4457f14858f14958f24b59f7585df34e5af34d59f34d59f14958f34d59ff6b63%
+  fb605ff6545cf04557fb605ffe6862fc6260fc6260ff7869fe6862ff7e6cfe6862ff846eff846effac88ff7e6cff8c72%
+  ff8c72ff9576ff7367ff7869ff9576ffac88ffffffff846effac88ff9f7dffac88ffac88ffffffff9f7dffac88ffffff%
+  ffffffffac88ffac88ffffffffac88ffffffffac88ffac88ffffffff9576ffffffffffffffffffffffffffffffff6b63%
+  e23350df2f4ef04557ee4156ee4256f04757f5535bf7565cf95c5ef34d59f24b59f6545cf24b59f24b59e83b53f7585d%
+  f34d59ee4156f14958f5515bf34d59f14858f04557f14858f14858ec4055f04557ef4356ea3d54ea3d54f34d59e83a53%
+  ec4055e73952ec3f55e83b53ee4156e93c53e53751e83a53e23450e73952ea3d54e73a52e53651ea3d54ea3d54e83a53%
+  ed4155e93c53e73a52ef4457e83a53ed4155f04757f5535bf7585df14858f34d59f4505afa5e5ff5535bff8c72fc6260%
+  ff7869ff846eff7869ff8c72ff7e6cff9576ff8c72ff846eff9f7dff7e6cffffffff9576ff9576ffac88ffac88ff9576%
+  ffac88ffffffffac88ffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffff9576ee4156df304ef04757f4505af95c5ef85a5dfa5e5ffe6862fc6260fb605ffd6561fa5e5f%
+  fb605ffb605ff5535bf5515bf5515bf34d59f14958f34e5af85a5df14958f34d59f04557f04757f34d59ef4457f34d59%
+  ee4256f34e5af34d59ec4055f04557eb3e54f34e5aee4156ef4457eb3e54ee4256f24b59f04557eb3e54ee4256e83a53%
+  f04557f04557ef4457f04757f24b59f24a59f14858ec4055f04557f95c5ef85a5df6545cfc6260f85a5dff846eff7367%
+  ff6f65ff6f65ff7869ff8c72ff846eff8c72ff8c72ff7e6cff9f7dffac88ffffffffac88ff9f7dffffffffffffffffff%
+  ffffffffffffffffffffac88ff9f7dffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  fffffffffffffffffffffffffffffffffffffffffffffffff5515bf14858f85a5dff6b63fb605fff7e6cff846eff9f7d%
+  ff9f7dff8c72ff9576ff9576ff7869ff7367ff6f65ff6f65ff7e6cff6b63fd6561ff6f65fb605ffb605fff6b63fd6561%
+  f95c5eff6b63ff6b63fc6260fb605fff7367fa5e5ff7585dff6b63fd6561f7565cfd6561ff7869fc6260fb605fff6f65%
+  fa5e5ff95c5efa5e5ff7585dfb605ffd6561fe6862f7585dfa5e5ffc6260fb605fff7367ff7869ff7869fe6862ff846e%
+  ff7e6cff8c72ff9f7dff9576ffac88ffac88ffac88ff9576ffffffffac88ff9f7dff9f7dffffffffffffff9f7dffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88e53751c2133ad11e46e1324f%
+  ec3f55f14958f34d59f7565cff6b63f7585dff6f65ff6b63fa5e5ff34d59f7585dee4256f7585dec4055f5515bee4256%
+  f24b59ed4155eb3e54e83b53eb3e54e23450f04557ee4256e63852f04757f04557e93c53e93c53f14958ef4457ef4457%
+  f04557e53651ec4055ee4156ef4457ef4457f24a59ec4055f34d59ee4156f14858fb605ff5515bf4505af7565cfd6561%
+  fc6260fc6260fb605ffb605ffb605fff8c72ff9576ff846eff9576ff8c72ff9f7dff846effffffff9f7dffffffffffff%
+  ff9f7dffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576%
+  ff9f7ddd2d4dd42248dc2c4ded4155f34d59fb605ff5515bfc6260fb605ff7585df5515bf7585df85a5df34e5af24a59%
+  f24a59ec4055f14858f5515bf24b59ed4155ed4155f6545cf04757f4505af24a59ea3d54ef4457ee4256f24a59f04757%
+  f14958f04757ee4256ef4457eb3e54ef4356f24a59f24b59f4505af95c5ef7585df5535bff6f65f7565cf95c5efd6561%
+  fe6862fb605fff7367fe6862ff7869ff6b63ff9f7dff8c72ff7e6cffffffff9f7dff9576ffffffff9f7dff9f7dffffff%
+  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ff846efa5e5fdf2f4ee63852ef4457f24b59f85a5df14858f24b59ee4256f24a59ee4256%
+  ea3d54fb605fef4356ef4457f04557ef4457f34e5af04757f04757f04557f04557ee4156ef4356f04757ec4055e53651%
+  ef4457ee4256ef4457ef4457ee4156ea3d54e73a52e83a53f14958ef4356f24a59f04557f7565cf14858f24b59fb605f%
+  fb605fff6f65ff7e6cff6f65fc6260ff7869ff7e6cff7869ff7e6cff9f7dff9576ffac88ffac88ffac88ff9576ffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff9576f34e5ae43551d7264ae43651e73952eb3e54e83b53%
+  e83b53ec3f55e43551eb3e54e43551ed4155e93c53e63852e53651eb3e54ec4055e63852ec4055eb3e54e73a52ee4256%
+  e73a52e43551e83b53ec4055e63852ea3d54ed4155eb3e54ec3f55ec4055f24a59f24b59ee4256ea3d54f24b59f04557%
+  f95c5ef5515bf7565cfc6260ff7367ff7367ff6f65ff9f7dff846eff846eff846eff9576ff9f7dffac88ffffffffffff%
+  ff9f7dffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffd6561de2d4dc8173f%
+  d01e46d42148d7264ad62449d9284bd52248d7254ad8264ad42248d42148d8274ade2e4ddc2c4dd52248dc2c4dd9274b%
+  df2f4ede2e4de0304edf2f4edd2d4de0314fdb2a4cdf304ede2e4dd7254ade2d4de1314fdf304edf2f4ee1314fe63852%
+  e43651e83b53f04557f24b59f34e5af4505af85a5df95c5efe6862ff8c72ff7e6cff7e6cff9576ff9576ffac88ffac88%
+  ffffffffac88ffac88ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffe1314fc3143bc9183fd01e45d7254ad32148d52349cd1c43d01e46%
+  d21f47d52349d62449d62449d62449d9274bda294bd9284bd9284bd9284bd42248dc2b4cd9284bd52349d9284bdf2f4e%
+  d9284bd11e46d52349d62449d9284bd7264ae23450e33450e0314fe73a52e83b53ef4457f34e5afb605ffe6862ff6b63%
+  ff6b63ff7367ff7e6cff8c72ffac88ffac88ffffffffac88ff8c72ffffffffffffffac88ff9f7dff9f7dffffffffffff%
   ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffffffffac88ffac88ffffffff9f7dffffffff9f7dffffffff9f7dffffffffac88ff9576%
-  ff9576ff8c72ff9576ff8c72ff9576ff7e6cff8c72ff8c72ff8c72ff9576ff8c72ff846eff7e6cff846eff7e6cff7367%
-  ff7869c6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ff9f7dff8c72%
-  ff9576ff9576ffac88ff9f7dff9f7dff8c72ff9576ff9f7dff7e6cffac88ff7e6cff9f7dff846eff7e6cff7869ff8c72%
-  ff8c72ff6f65ff7367ff9576ff8c72ff7e6ccd1b43ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576%
-  ffac88ffac88ffac88ff9f7dffac88ff9576ff9f7dff9f7dff8c72ff9f7dff7e6cff846eff7869ff7e6cff9f7dff846e%
-  ff846eff8c72ff9f7dff8c72ff7869ff846eff7e6cff9f7dff7e6cff7e6cff9f7dc91940ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffff%
-  ffac88ffffffffffffffac88ffac88ff9f7dff9f7dff9f7dff9f7dffac88ffffffff846eff9576ff846eff9f7dff8c72%
-  ff9576ff9f7dff8c72ff8c72ff7869ff9f7dfd6561ff7869ff8c72ff846eff7367ffac88ff9576ff8c72ff9576ff7367%
-  ca1940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffac88ffffffffffffff9576ff9576ffffffffffffff9576ffffffffac88ffffff%
-  ffac88ff8c72ff9f7dff9f7dff8c72ffac88fe6862ff7e6cff8c72ff9f7dff7e6cff8c72ff9f7dff7869ff9576ff846e%
-  ff8c72ff7e6cff9f7dfd6561ff7869ca1940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ff9f7d%
-  ff9f7dff846eff8c72ff9576ff9576ff846eff9576ff9f7dff846eff9f7dff9f7dff6b63ff7e6cff9576ff846effac88%
-  ff846eff8c72ff9576ff846eff7e6cff9576ff9576ff846eff8c72ff7367c91840ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7d%
-  ffffffffac88ffffffff9f7dffffffff8c72ffac88ff9f7dff9576ffac88ffffffffac88ff9576ff9f7dffac88ff7367%
-  ff7869ffac88ff8c72ff9576ff7869ff9f7dfd6561ff9576ff9f7dff846efc6260ff7367ff6f65ff846eff846ec7173e%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffffffffac88ffffffff9f7dff9f7dffffffffffffffac88ff9f7dff9576ff9f7dff9f7dff9f7dff9f7dffac88%
-  ff6b63ff7e6cff846eff7e6cff7e6cff6f65ff7367ff7869ff7e6cff8c72ff7869ff9f7dff9f7dff7e6cff9576ff9f7d%
-  ff9f7dff846efe6862ff9576c91940ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffff%
-  ffac88ffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88ff9f7dff9576ff9f7dffac88ff9f7dffffff%
-  ffffffffac88ff846effac88ff9f7dff9576ff7869ff9f7dff7367ff6f65ff7869ff6f65ff846eff7367ff7367ff846e%
-  ff846eff7367ff7367ff7869ff8c72ff8c72ff7e6cff7367ff9f7dce1c44ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffac88ffffffffffffffac88ffac88ffac88ffac88ffac88ffac88ffac88ffffffff9f7dffac88%
-  ffffffff9f7dff8c72ff9f7dff8c72ffffffff9576ff846eff8c72ff8c72ff9576ff846eff7869ff7869ff7367ff7869%
-  ff7367fe6862ff8c72ff7367ff846eff7e6cff8c72ff8c72ff7869ff846eff6f65ffac88fd6561ff846eca1941ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88%
-  ffac88ff9f7dffffffff9f7dffffffffac88ff9576ff9f7dff9f7dff9f7dff7e6cffac88ff846eff7869ff846eff9576%
-  ff846eff7e6cff6b63ff846eff7869ff6b63ff9576ff9576ff6f65ff846eff846eff7367ffac88ff6b63ff7e6cff7e6c%
-  ffac88ff8c72ff846ecc1b42ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffff%
-  ffffffffffffff9f7dffffffff9f7dffac88ffac88ffffffffffffffac88ffac88ffac88ff9f7dff9f7dff8c72ff9576%
-  ff8c72ff9576ff8c72ff7869ff9576ff6f65ff6f65ff7367ff9576ff846eff8c72ff846eff7869ff7367ff6f65ff7869%
-  ff7e6cff6f65ff9576ff8c72ff7869ff7367ff6f65ff9576ca1941ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffff%
-  ffac88ffffffffac88ffffffffac88ffac88ffac88ffac88ffac88ffffffff9f7dff9f7dffffffffac88ff9576ff9576%
-  ffac88ffac88ff9f7dff9576ff9576ff9f7dffac88ff7367ffac88ff7869ff7e6cff6f65ff8c72fc6260fe6862ff9576%
-  ff6b63ff8c72ff7367ff7869ff7869ff6f65ff7e6cff7869ff7367ff7869ff8c72ff7e6cff7e6cd52349ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9f7dff9576ffffffff9576%
-  ff9f7dffac88ffac88ff9f7dff9f7dff9576ff9576ff9576ff9f7dffac88ff8c72ff7e6cff6f65ff8c72ff7869ff7869%
-  ff7869ff7e6cff6b63ff8c72ff7869ff846eff7e6cff7869ff7869ff846eff7367ff8c72ff7e6cff7367ff6f65ff7869%
-  ff6f65ff9576d32148ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffac88ffac88ffac88ffffffffffffffffffffac88ff9f7dffffffffac88ffffff%
-  ff8c72ffac88ff9576ff9576ff9f7dffffffffac88ff9f7dffac88ff9576ff9f7dff9f7dff9576ffac88ff8c72ff8c72%
-  ff8c72ff7869ff7367fd6561ff6f65fe6862ff7869ff7e6cff846eff6b63ff7869ff846eff7869ff6f65ff7e6cff6f65%
-  ff6b63ff9576ff7869fe6862ff7367ff7869ff846ed42248ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
-  ffffffffffffffffffffffffff9576ffffffff9576ffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff846e%
-  ff9f7dffac88ff7367ff846eff7869ff8c72ff8c72ff7e6cff7e6cfd6561ff6f65ff6b63ff9576ff7e6cff9576ff7e6c%
-  ff6f65ff7869ff7e6cff6b63ff7869ff846eff6b63ff846eff7869ff7869ff846eff8c72d42248ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ff9576ffac88ff9f7dffac88ffac88ffac88%
-  ffffffff9f7dffac88ffac88ffac88ffac88ff8c72ff7367ff846eff6f65ff6b63ff7e6cff8c72ff7e6cff7e6cfb605f%
-  ff6b63ff7367ff9576ff7367ff7869ff9576ff6f65fd6561ff846eff9576ff8c72ff9576ff7367ff7e6cff7367ff7367%
-  fe6862d11e46ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff9576ffffffff846e%
-  ffffffff9f7dffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff8c72ff9f7dff846eff9576ff7367ff8c72%
-  ff8c72fe6862ff8c72fc6260ff6b63ffac88ff7869ff7367ff8c72ff846eff6f65ff7e6cff8c72ff7367ff6b63ff6f65%
-  ff9576ff8c72ff7869ff846eff846eff7e6cd32047ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9f7d%
-  ff9576ffffffffffffff9576ff9f7dff9f7dff8c72ff9576ff9f7dffac88ff8c72ff8c72ff9576ff846effac88ffac88%
-  ff9576ff846eff8c72ff6f65fd6561fe6862ff6b63ff846eff6f65fe6862ff6b63ff7e6cfb605fff9576ff7869ff9576%
-  ff7367ff7367ff846eff7869ff7367f85a5dff846eff8c72ff7869fe6862ff846ed7254affffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffff%
-  ffac88ffffffffffffffac88ffac88ffffffff9576ff9f7dffffffffac88ffac88ff9f7dff9f7dff9576ffffffffac88%
-  ff9576ff9576ffac88ff9576ff846eff6f65ff846eff7367ff7367ff9576ff8c72fe6862fd6561ff6f65fb605fff8c72%
-  ff7367ff7367ff7869ff846eff7869ff7e6cff7e6cfe6862ff846eff7367ff846eff8c72ff8c72ff7e6cff846efd6561%
-  da294bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9f7dffffffffac88ffffffffac88ff9f7dff9f7dffffffffffffffac88ff8c72ff9576ff9f7dff9576ff9576%
-  ffac88ff9f7dff8c72ff8c72ff9f7dff9f7dff7869ff846eff7869ff7e6cff6f65ff846eff846eff6f65ff7367ff6f65%
-  ff846efd6561fe6862fc6260ff7367ff7367ff7e6cfe6862ff846eff9f7dff6b63ff7367ff7869ff7869ff6b63ff6f65%
-  ff6b63ff6f65ff6f65ff7367ff6f65da2a4cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffffffac88ff8c72ffffffff846e%
-  ff8c72ff8c72ffffffff8c72ff8c72ff846eff9576ff8c72ff6b63ff846eff9576ff8c72fe6862ff846eff7e6cff6f65%
-  ff7367ff7869ff7367ff6f65ff7367ff6b63fe6862f95c5efd6561ff9576ff6b63ff846eff6f65ff7e6cff7e6cff846e%
-  ff6f65ff7e6cff9f7dff6b63fe6862ff7367ff7367ff6f65ff7367ff7e6cd8274affffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffff%
-  ffac88ffac88ff9f7dffac88ffffffff9576ff7e6cff8c72ff9f7dff9576ffac88ff846eff9f7dffac88ff9f7dff9f7d%
-  ff7869ff7e6cfd6561ff846eff7869fe6862ff6f65f85a5dff7869ff9576ff846efe6862fd6561ff7367fd6561fe6862%
-  ff7367ff6f65fb605ffd6561ff6b63ff6f65ff8c72ff8c72fd6561ff6f65ff7367ff846eff8c72ff846eff7367d8264a%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7d%
-  ffac88ffffffffac88ffac88ffffffffac88ffffffff7e6cff8c72ff846eff8c72ff9f7dff8c72ff9f7dff8c72ff9f7d%
-  ff6f65ff846eff6f65fa5e5fff846eff846eff7e6cff8c72ff7869ff9576ff7367ff7869fc6260ff6b63fc6260fe6862%
-  ff6b63fe6862ff846efd6561ff7367fc6260f85a5dff6f65fe6862ff8c72fe6862fe6862ff6b63fe6862ff7869ff846e%
-  ff8c72ff846eff8c72ff7e6cde2e4effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88%
-  ffac88ffffffffffffffac88ffffffffac88ffac88ff9f7dff9576ff9f7dff9f7dff846eff9f7dff9576ff9576ff9f7d%
-  ff9576ff846eff9576ff8c72ff7e6cff6f65ff7869ff6b63ff7367ff7367ff7869ff7869ff6f65ff6f65fd6561ff9576%
-  ff6f65ff7367fe6862ff6b63f7565cff7367ff846ef95c5efb605fff6b63fe6862ff7e6cff6b63ff6f65fa5e5ffd6561%
-  fa5e5fff846eff6b63fd6561ff6f65fe6862ff7869ff7869ff846ede2e4effffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ff8c72%
-  ff9f7dffffffff7869ff846effac88ff846eff8c72ff8c72ff8c72ff8c72ff7e6cff7869ff6f65ff7367ff7869ff7e6c%
-  ff9f7dff7e6cff7e6cff7869ff7869ff9576ff6f65fd6561fe6862fe6862ff7367fc6260ff7869fc6260ff6b63ff6f65%
-  ff6f65ff6b63fe6862fd6561fc6260fa5e5ffe6862fb605fff846eff9576ff7367ff7869ff6f65ff7e6cdf2f4effffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffff9f7dffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffff9f7dff9f7dff7869ff9f7dff9f7dff8c72ff846eff7869ff7869ff9f7dff846eff6f65ff8c72fe6862%
-  ff7e6cfd6561ff6b63ff6b63fd6561ff6b63fe6862ff6f65f7585dfc6260ff6f65fe6862ff7869f95c5efd6561ff846e%
-  fe6862fb605ffc6260f6545cfc6260ff7367ff6b63fd6561ff7869fa5e5fff7869fd6561fc6260ff7367ff6f65ff6f65%
-  ff7869fe6862ff7869e23350ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ff9f7d%
-  ffac88ffac88ffac88ffac88ffac88ff9f7dff9576ff9f7dffac88ffac88ff846eff9576fe6862ff6b63ff7869ff8c72%
-  ff7367fb605ffd6561ff6f65fd6561fb605fff7869fc6260ff7367ff7367fe6862fe6862f95c5eff7e6cff7367f5535b%
-  fb605fff6b63ff7367f7585dfe6862ff6b63fc6260fe6862fb605ff7565cf85a5dfe6862f7585dff7e6cff6b63ff7367%
-  ff6b63ff846eff6b63ff6f65ff6b63ff7e6cff8c72ff846ee63852ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff9f7dff9f7dffffffff9576ff8c72ffac88%
-  ff9576ff9f7dff9f7dff9f7dff9576ffffffff9f7dff9576ffffffffac88ff9f7dff9576ff9f7dffffffffffffff9f7d%
-  ffac88ffffffff8c72ffffffffffffff9576ffac88ff9f7dff9576ffac88ff9576ff8c72ff846eff9f7dff7e6cff7367%
-  ff9576ff9576ff846efc6260f95c5efd6561ff6b63f95c5eff7367ff7e6cff7367ff6b63fc6260fd6561fa5e5fff6b63%
-  ff6f65fb605ffb605ff7565cfc6260f7565cf7565cf14958f7565cfc6260fb605ff34e5af5515bfa5e5ff5515bfb605f%
-  fc6260fd6561fe6862ff6f65ff8c72fa5e5ffe6862ff8c72ff6b63ff7367fe6862ff846eff7869e73a52ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88fa5e5ffd6561fd6561fc6260%
-  f5515bfa5e5ffc6260f7585dff6b63fc6260fc6260ff9576ff6f65ff6f65ff7367ff846eff9576ff846eff846effac88%
-  ffac88ff9f7dff8c72ff7e6cffac88ff9576ffac88ff9f7dff846eff846eff9576ffac88ff7367ff7e6cff846eff9f7d%
-  ff846eff7869ff8c72fe6862ff8c72ff6f65ff6f65fa5e5ffe6862fb605ff34d59f85a5df7585df7565cff6f65fd6561%
-  fd6561fc6260fb605ff95c5efb605ffe6862f7565cf95c5efb605ffa5e5ff5535bf85a5df5515bf5535bfe6862fd6561%
-  f95c5ef5515bf14958fc6260f95c5eff9576fb605ffa5e5ffd6561ff7e6cfb605fff6b63ff7367ff7367ff6f65ff6f65%
-  fe6862ff7367ea3d54ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  fc6260ec3f55f14858f24b59f34e5ae33550f14858f34d59f95c5ef4505af5535bfe6862ff6b63ff7367ff6b63ff6f65%
-  ff6f65fa5e5fff7367ff6b63ff7e6cff6f65ff7869ff7869ff6f65ff8c72ff846eff8c72ff7e6cff8c72ff6f65ff846e%
-  ff9576ff846eff7e6cff6b63ff9576ff6f65ff7869fd6561fe6862ff7e6cfb605ffe6862ff7367fa5e5ff95c5ef5515b%
-  f7585dfb605ffd6561f85a5dff7869fa5e5ffd6561ff6b63fb605ff7585dfc6260fb605ffc6260fa5e5ff6545cf85a5d%
-  f6545cf14958f4505af7565cfb605ff4505af5535bfa5e5ff95c5efb605ffb605ff5535bfb605fff846eff7e6cff7869%
-  f85a5dfc6260ff8c72ff6b63ffffffff7869ff9576e63852ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88f5515be73952e2324fe73952ea3d54ea3d54e73952ea3d54f34d59f34d59f5535b%
-  f7585df7585df5535bf7565cff6f65fa5e5ff85a5dfc6260fd6561ff7367fb605fff7367ff6b63ff6f65ff8c72ff8c72%
-  ff7869ff6f65ff7869ff7367fb605fff846eff8c72ff7367fc6260fc6260fa5e5ffb605fff6f65f95c5eff7367fd6561%
-  f7585dfa5e5ff4505af34d59fe6862f34e5af7565cf95c5ef34e5afc6260f5515bff6b63fc6260f7585df5535bf7585d%
-  f7565cf85a5df85a5df7565cf7565cf5535bf85a5dfd6561fe6862fc6260f6545cfa5e5ff7565cff6b63fa5e5ffd6561%
-  fc6260fa5e5fff6b63ff6b63ff6f65ff6b63ff7e6cff7367ff7e6cff6b63ff846effac88e53651ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff7e6cf5535bef4356e33450ee4256f04757ee4156f34d59%
-  f7565cf95c5ef85a5dfd6561fc6260f95c5eff6f65ff7869ff6f65ff6f65fc6260ff6f65ff846eff6b63ff7e6cff6b63%
-  fe6862ff6f65ff6b63ff7367ff7367fe6862ff6f65fa5e5fff6b63fe6862ff6b63fa5e5fff7367f5535bfc6260f7585d%
-  fd6561f85a5df7585df14858f7565cf5535bfc6260f34e5af85a5df7565cf5535bf7565cf95c5eff7869fd6561fe6862%
-  f7585dfa5e5ff7585dfb605ff6545cf24b59f95c5efc6260fc6260f5515bfa5e5ff7565cfb605fff6b63fc6260fb605f%
-  fa5e5ff7585df85a5dff6f65ff6b63ff7869fe6862fd6561fd6561ff8c72ff846efd6561ff7869ff7869ff9576ff8c72%
-  ff9f7deb3e54ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88f04557e33550e33550%
-  ec4055ec3f55ef4457f34d59f6545cfa5e5ffe6862f34d59f7585dfb605fff6f65ff7869ff7367fc6260fa5e5ffc6260%
-  fe6862ff846eff6f65ff6b63f95c5ef34d59ff846ef95c5efd6561f7565cf7565cf85a5dfc6260f34e5afc6260f7585d%
-  f95c5ef5535bf4505af95c5ef6545cf4505af14858f34d59f7565cf34d59f7585df7585df7585df24b59fa5e5ff7585d%
-  fa5e5ff6545cf7585df6545cf95c5efa5e5ff7585dfb605ff34e5af7585df7565cf85a5df4505af24a59fc6260f5535b%
-  f6545cf4505af7585dff6b63f7585df95c5ef7585dfd6561fd6561ff6b63ff6b63fd6561fc6260fe6862ff7e6cfe6862%
-  ff6b63ff6b63ff846eff846eff6f65ff7869e83b53ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ff9576f95c5ee1324fe0314fe23450e33550e43651ea3d54ef4457f04757f24a59f7585dfb605ffa5e5ffc6260f95c5e%
-  fa5e5fff6b63fa5e5ff7585dff7367fd6561fb605ff7565cfe6862fa5e5ffb605ff7585df95c5ef7585df7565cf34e5a%
-  f04757f34d59f34e5af4505af04757f5535bf24a59f34d59f14858f34d59f04757f14958f24b59f04757f14958f4505a%
-  f24a59f04557f7585def4457f14958fc6260f5535bf34e5af85a5df7565cf04757f34e5af5535bf7565cf6545cf85a5d%
-  ff6b63f4505af7565cf95c5ef7585dfe6862fd6561fa5e5ffa5e5ff5535bf34e5afa5e5ffc6260fe6862fa5e5fff6b63%
-  fd6561ff6f65fe6862ff7e6cff6f65ff7869ff7869fe6862ff8c72ff6f65ff8c72e73a52ffffffffffffffffffffffff%
-  fffffffffffffffffffffffffe6862e43551df2f4ecc1b42d9284bdd2d4dde2e4ee43551e33450ec4055f14858f5515b%
-  f4505af5515bff6b63f4505afb605ff6545cf85a5df5535bfb605ffb605ff6545cfc6260f85a5dfb605ff24a59f6545c%
-  f85a5df5515bf5535bf5535bf14858ef4457ec4055f4505aeb3e54f34e5aef4356ef4457f24b59ee4156ee4256e83a53%
-  e63852ec3f55ee4156f14958e73a52e83b53e83a53ec3f55ea3d54e53751ef4356f14958ef4356f5515bed4155f95c5e%
-  f34d59f14958f6545cee4156f5515bf7565cf6545cf04557f5535bfb605ff34d59f7565cf34e5af6545cf24a59fe6862%
-  fe6862f85a5dfa5e5ff85a5dfc6260fc6260f85a5dff6f65ff7e6cff7e6cff6f65ff9576ff846eff7e6cff8c72ff6b63%
-  ec4055fffffffffffffffffffffffffffffffffffffffffffe6862dc2c4dd21f47cb1a42c8183fdb2a4ce23450e43651%
-  ed4155ee4256f24b59f4505afc6260f5515bf4505af5515bf85a5df6545cfd6561f5515bf7565cf85a5df85a5df85a5d%
-  ff7e6cf5515bf34e5aff6b63fd6561fa5e5ff14958f95c5ef24a59f24b59f04757f14858f04557f24a59f34d59f04757%
-  f4505af04557f04757e93c53f04757e33550e63852e43551ea3d54ea3d54ec3f55e93c53e63852ea3d54ec4055ee4156%
-  ea3d54f14958f34d59f6545cf7585df34d59f34e5af14958f14958f6545cf04557f6545cf04557fa5e5ff7565cf95c5e%
-  f95c5efd6561fa5e5fff846efc6260ff6b63ff6f65ff7367ff6f65ff6f65ff6b63ff6f65ff7367ff7869ff9576ff846e%
-  ff7869ff7367ff7869ff9576ff846ef24a59ffffffffffffffffffffffffffffffffffffffffffde2d4dd01e45c4153c%
-  cb1a42ce1c44de2e4ee0314fea3d54f34d59f5515bf5535bf34e5af6545cf34e5afb605ffb605ffa5e5ffc6260fa5e5f%
-  fe6862fc6260fa5e5ff5535bfb605ff95c5ef6545cf7565cfc6260f24a59f34e5af24a59f04757ef4457f34d59f14858%
-  f04557f14958f4505af34e5af14858e83a53f34d59eb3e54ec3f55ef4457ea3d54ee4156ee4156ea3d54e63852ef4356%
-  e83a53ef4356e83b53e73a52f14958ee4156f14958ef4457f14958f14858f5515bf14958f5515bf5515bf4505afa5e5f%
-  fc6260ff7869f4505afd6561fa5e5fff6f65f85a5dff8c72ff6f65ff7869ff9f7dff7869ff8c72ff9576ff846eff7e6c%
-  ff9f7dff9576ffac88ff846effac88ff9f7dffac88ffac88ffac88ffac88ff9f7dffffffffffffffffffffffffffffff%
-  ffffffff9576c4153cc11239c3143bd11e46d52349e0304edf304ee63852f14958f14858f34e5afb605ff34d59f34e5a%
-  f34e5af24a59f34e5af24a59ee4256f5515bf34e5aef4457f4505af7565cf24a59f34d59f24a59f04557e53751ea3d54%
-  e83b53e63852ee4256ea3d54ef4356e93c53ec3f55e33550f14858f04757ef4356ea3d54eb3e54e93c53e63852f04557%
-  e73a52ea3d54e83b53eb3e54ee4156ed4155e83a53ed4155f04757f14958ee4156f14958f5515bfd6561f5515bf6545c%
-  f4505afd6561f85a5df85a5dfc6260ff6b63ff7869fe6862ff7e6cff846eff8c72ff846effac88ff9576ffac88ff8c72%
-  ff8c72ffac88ff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffff4505ac8183fcb1a42e93c53dd2d4ded4155ef4457f04757f14958f14858%
-  f34d59f24a59fb605ff34d59f14958f85a5df04557f34d59f14858f24a59f7565cf85a5dfd6561f24b59ef4356f5535b%
-  f4505af14958e83b53f04757f04557ec3f55f34d59f14958f24a59ed4155ec3f55f04757f24b59f14958f34d59f34d59%
-  e43651ef4457ee4256f14858f24a59f04757fa5e5ff04557ef4457f14858ef4356f5535bf14958f7585df85a5df95c5e%
-  f85a5dfc6260f7585dff7367ff7e6cff7869ff7367ff7367ff846eff8c72ffac88ff9576ffac88ffffffffffffffac88%
-  ffac88ffac88ff9f7dffffffff9576ff9576ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576e83b53d42248e1324ff14958f24b59%
-  f24b59f4505af7565cf7565cf95c5ef95c5eff6b63fa5e5ffa5e5ff5535bf4505af34d59f34d59f6545cf85a5dfc6260%
-  fe6862f7585df6545cf5535bf34e5af4505af6545cf7565cf95c5ef85a5dfa5e5fff8c72fa5e5ff14858fa5e5ff14858%
-  f7585df34e5af34d59f34d59f34e5af4505af4505af4505af6545cf95c5ef34d59f7585df34e5af24b59fe6862fe6862%
-  f6545cf7565cf85a5dff7367f95c5eff7869ff6b63ff7e6cff7869ff7869ff846effac88ff7e6cff9576ff9f7dffffff%
-  ff846eff846eff9576ffac88ffffffffac88ff9576ff9f7dffffffffac88ffffffffffffffffffffffffffac88ffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff4505a%
-  d21f47d52248db2a4ce33550e23350e73952f24a59ee4256e73952f04757ef4457ee4156ef4457ef4356eb3e54f14858%
-  ef4457f34e5af85a5df4505afb605ffa5e5feb3e54e83a53f04757f04757f04557ea3d54f4505afb605ff4505aef4356%
-  f24a59f14858f14858f14858ee4156e83a53e83a53ee4256e73a52e83a53e93c53e83a53e83b53f04557f24b59ef4457%
-  e93c53ec3f55eb3e54ed4155f34d59ef4457fc6260f24b59f5515bf5515bf95c5efb605ffa5e5ffe6862ff8c72ff7e6c%
-  ff846eff7869ff9576ffffffffac88ff8c72ff9576ff9576ffac88ffac88ff9f7dffac88ffffffffffffffac88ff9f7d%
-  ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff8c72dd2d4dcb1a42e2324ff14858ef4356f6545cf5535bf4505af5535bf5515bfb605ff34d59%
-  f34d59f4505af5535bf7585df5515bfa5e5fff7367f95c5efc6260f7565cfb605ff24a59ef4356ef4356f14858f5535b%
-  f24b59f7565cf6545cfd6561f5515bf24a59ee4156f4505af24b59ef4356ef4356ef4356f34d59ea3d54ee4256f04757%
-  f14858ef4356f04557ef4356f7565cf34e5af24b59f95c5ef5515bf95c5ef5515bfa5e5ffc6260ff7e6cff7e6cff846e%
-  ff7869ff9576ff846eff7869ff846eff9576ff8c72ff9f7dffac88ffac88ffac88ffac88ffffffffac88ffffffffffff%
-  ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffff34d59e1324ff04557fd6561ff7869fd6561ff9f7dff7869%
-  ff9576fc6260ff8c72fc6260ff6f65ff6f65fd6561ff846eff7e6cfb605fff6f65ff7367ff8c72ff8c72fa5e5ffc6260%
-  fd6561ff6b63ff6f65fa5e5ffe6862fb605ffd6561ff6f65ff7e6cfb605ffd6561ff6b63fc6260ff7e6cfb605ff5515b%
-  f24b59ff7e6cfd6561ff6f65fd6561f95c5efc6260fd6561fd6561ff6f65ff7e6cff6f65ff9576ff846eff6b63ff9f7d%
-  ff9f7dffac88ffac88ff9f7dff9f7dff9576ff9f7dffffffffac88ffac88ffffffff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88e53751bc0f36c4153cda294b%
-  ea3d54ec3f55f6545cf24a59f7565cf34e5af6545cf24a59f14958f34d59f34e5af34d59f34e5af04757f4505af04757%
-  f24a59f04557eb3e54ec4055e83a53f34d59ef4457ef4457ef4356ef4356ee4156ec4055ea3d54ee4156f34d59ee4156%
-  f24a59f14858ed4155f14858f14958f04557ef4457f4505af34d59f4505af7585df5535bfb605ff85a5dff6f65fd6561%
-  f85a5dff6b63ff8c72ff9f7dff846effac88ff846effac88ff846eff9576ffffffffffffffffffffac88ffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
-  ff9576d7254ac7173edd2d4dee4256f5515bf5515bfc6260f4505af24a59f34d59f5535bf6545cf24a59f34e5af4505a%
-  f04557f04757f34d59f34d59ee4256f04557f14958f5535bf7565cf14958f14858f6545cef4457ef4457f04557f24a59%
-  f14958f4505aec4055ef4457f34e5af95c5eef4356f14858fd6561fa5e5ff24b59f85a5df95c5efc6260f85a5dfa5e5f%
-  ff846eff8c72ff846eff6b63ff846eff8c72ff9f7dffac88ffffffff9f7dffffffffac88ff9f7dffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff8c72ff6f65fe6862d7254ad01e46ef4457f24b59f04757f04557f4505ae83b53ef4457f34d59%
-  f34d59f34e5af04757f24b59f4505af5515bef4356f04757f34e5aef4457ef4457ec3f55f04557e53751ee4156f24b59%
-  f24b59ef4356f14958f14858e93c53ea3d54ea3d54eb3e54f34e5af04557f4505af24a59f4505af7585dff6f65fc6260%
-  fd6561fe6862ff7367ff8c72ff7869ff7367ff8c72ff8c72ff9f7dffffffff9f7dff9f7dff9f7dffac88ffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffff7585df34e5ae0304ed11e46da294be2324fe63852e23450%
-  e23350e73a52e43651ea3d54ea3d54e73952e93c53ef4457ef4457f14858ef4356eb3e54e73952e83a53ea3d54e2324f%
-  e73a52e73a52ed4155ee4156ea3d54ef4356ec4055f34d59f24b59e83b53ee4156ef4356ee4156f34e5af34d59f5515b%
-  f7565cff7367f85a5dff9576ff7e6cff846eff9576ff8c72ff8c72ff9576ff8c72ffffffffffffffffffffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff24a59db2a4cc2133a%
-  c01138cd1c43d21f47d62449d62449d8274ad42248d42148d7264ada294bdb2a4cdc2c4ddc2c4cd9284bde2d4dde2e4d%
-  e1314fde2d4de23450e0314fda294bdc2c4de1314fdb2b4cda294be23450d9274be23450e0314fe33550e73a52eb3e54%
-  ee4156f14858f24b59f4505afe6862f34e5aff7e6cff7367ff9f7dff7869ff9576ff9576ffac88ff8c72ff9f7dffffff%
-  ffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffcc1b42c1133aba0e34ca1940d32047d52349d11e46d01e45d62449%
-  d7254ad62449d52349da294bd7254add2d4dda2a4cd8264ad32148d7254ad62449da294bdc2b4cd7254ad8264ad7264a%
-  db2a4cd62449d42248d52349e0304ee43551e1314fe83b53e83b53ea3d54f4505af95c5eff7869ff7367ff6f65ff7e6c%
-  ff7367ff7869ff9576ffac88ff9f7dffac88ffac88ffac88ff9576ffac88ffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffa70421b4092fba0d34c5153ccd1c43c8173fcc1b42d21f47d32047d7254ad42248d32148d11e46d42148d52248%
+  d11e46d22047d52349d8264acf1d44d21f47d21f47d42148d52349d8264ad52349dd2d4dd9284bda294bde2e4ddf2f4e%
+  e33550e53651ed4155f04557f5515bfb605fff7e6cfa5e5fff9576ff846eff7869ff8c72ffffffffffffffac88ffffff%
   ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffff9a0212af062bb80c32c01138cb1a42cf1d45d32047d52349d21f47d62449d8264ad9284bd42148d7254ad22047%
-  d01e46d21f47d32047d01e46d11f46d9274bd32047d8264ad9284bd7264ad8264adc2c4cdc2b4ce1314fe73a52e63852%
-  ea3d54f24b59f34d59fb605fff6f65ff7869ff7869ff8c72ff9576ff9576ffac88ffffffff9f7dffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000b70b32b50a30b60b31b70b32%
-  bb0e35bc0f36bf1138c01239bf1138bf1138ba0d34bf1138c1133ac1133ac91840c9183fca1941c6163dca1941c91840%
-  cd1b43d11e46d01d45d52248dc2c4cda2a4ce53751e73a52ec3f55f34e5afa5e5fff6b63ff7e6cff846effac88ff9f7d%
-  ff9576ff9f7dffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000b50a30ba0d34b90d33bb0e34%
+  ba0d34bd0f36bc0f35b80c32ba0e34b90d33bf1138c1133abe1037c01138c6163ec3143bc3143bc91840c7173ecf1d45%
+  cb1a42c91840d11f46d32047d62449d52248d9284bde2e4de43651e73a52e73952f24b59f7585df95c5eff7869ff7869%
+  ff9f7dff9576ff9f7dff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000%
-  b3082eae062aac0527aa0525ac0527b0062cb4092fba0e34bd1037c5163dc7173eca1940d21f47d7264ade2e4deb3e54%
-  ed4155fb605ff5515bff6b63ff9576ff7367ff9f7dff8c72ffac88ffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffff8b0000ff6b63ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  b0062cab0526ae062ab0062cab0526ad0628ac0528b0062cb1072db4092fbb0e35be1037c5153ccb1a41d32048d7254a%
+  de2e4ef24a59f24a59f85a5df85a5dff6b63ff846eff9f7dff8c72ff846eff9576ffffffffffffffffffffac88ffac88%
+  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff8b0000f04757ff6f65ff9576ffac88ff9f7dffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
 \node[gp node center,rotate=-270] at (5.706,3.991) {Clique Runtime (ms)};
-\node[gp node center] at (8.574,1.427) {MAC Runtime (ms)};
+\node[gp node center] at (8.574,1.427) {FC Runtime (ms)};
 \begin{scope}

### 2016-04-14 paper/paper.tex
Move figure back to first page
Bring in Patrick's text

@@
 
-Maximum common subgraph problems arise in biology and chemistry
-\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
-\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
-\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
-designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
-and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
-measuring the similarity or difference between two graphs
-\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}.
-
-\paragraph{Definition of the Maximum Common (Connected) Subgraph Problem.}
-We introduce definitions and algorithms on undirected and unlabelled graphs.
-The extension to directed or labelled graphs is straightforward and discussed in Section \ref{extension}.
-An undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq N_G\times N_G$ such that each edge is an undirected pair of nodes.
-
-Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$.
-A graph $G$ is \emph{connected} if every pair of nodes is connected by a path.
-
-A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function $f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G, \{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
-
-A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a \emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
-In this definition, we only remove edges incident to removed nodes.
-This is usually called induced subgraph in the litterature.
-We may also allow to remove edges which are not incident to removed nodes, thus leading to partial subgraphs.
-In this paper, we only consider induced subgraphs.
-However, all algorithms may be extended to the partial case, as explained in \cite{DBLP:conf/cp/NdiayeS11}.
-
-A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and $G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
-A \emph{Maximum Common Subgraph} (MCS) (resp.
-\emph{Maximum Common Connected Subgraph} (MCCS) is a common subgraph (resp.
-common connected subgraph) which has a maximum number of nodes.
-Examples of MCS and MCCS are given in Fig.
-\ref{figure:mcsexample}.
-
-\begin{figure}[t] % first page if possible
+\begin{figure}[b] % first page if possible
     \centering
@@
 \end{figure}
+
+Maximum common subgraph problems arise in biology and chemistry
+\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
+\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
+\cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
+designs \cite{DBLP:journals/jair/CookH94}, in character recognition problems \cite{SIWEILU1991617},
+and in many other domains \cite{Shasha:2002:AAT:543613.543620}, both directly and as a way of
+measuring the similarity or difference between two graphs
+\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}.
+
+\paragraph{Definition of the Maximum Common (Connected) Subgraph Problem.}
+We introduce definitions and algorithms on undirected and unlabelled graphs.
+The extension to directed or labelled graphs is straightforward and discussed in Section \ref{extension}.
+An undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq N_G\times N_G$ such that each edge is an undirected pair of nodes.
+
+Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$.
+A graph $G$ is \emph{connected} if every pair of nodes is connected by a path.
+
+A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function $f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G, \{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
+
+A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a \emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
+In this definition, we only remove edges incident to removed nodes.
+This is usually called induced subgraph in the litterature.
+We may also allow to remove edges which are not incident to removed nodes, thus leading to partial subgraphs.
+In this paper, we only consider induced subgraphs.
+However, all algorithms may be extended to the partial case, as explained in \cite{DBLP:conf/cp/NdiayeS11}.
+
+A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and $G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
+A \emph{Maximum Common Subgraph} (MCS) (resp.
+\emph{Maximum Common Connected Subgraph} (MCCS) is a common subgraph (resp.
+common connected subgraph) which has a maximum number of nodes.
+Examples of MCS and MCCS are given in Fig.
+\ref{figure:mcsexample}.
 
@@
 \paragraph{Ensuring connectedness with a specific filtering.}
-Another way to ensure connectedness is to filter domains to ensure connectedness consistency.
-Let us consider two graphs $G$ and $G'$, and let $D$ be the current domains (we suppose that $D(x_u)$ is a singleton when $x_u$ is assigned).
-Let $C$ (resp.
-$C'$) be the set of nodes of $G$ (resp.
-$G'$) which may belong to the common subgraph, {\em i.e.}, $C=\{ u\in N_{G}, D(x_u)\neq\{\bot\}\}$ (resp.
-$C' = \{u'\in N_{G'}, \exists u\in N_G, u'\in D(x_u)\}$).
-Let $G_{\downarrow C}$ (resp.
-$G'_{\downarrow C'}$) be the subgraph of $G$ induced by $C$ (resp.
-the subgraph of $G'$ induced by $C'$).
-The connectedness consistency ensures that both $G_{\downarrow C}$ and $G'_{\downarrow C'}$ are connected graphs.
+
+CP(Graph) \cite{DBLP:conf/cp/DoomsDD05} introduces graph domain variables and enforces connectivity via the
+\emph{reachable} constraint, ensuring that there is a path from a specified vertex to a specified
+set of vertices. One such constraint is then posted for each of the vertices in the graph and
+encodes the transitive closure of the graph. Brown et al.\ \cite{Brown:2005} explored the use of
+constraint programming in the generation of connected graphs with specified degree sequences.  Two
+constraints were combined, i.e.\ the graphical constraint (a backtrackable implementation of the
+Havel-Hakimi algorithm) with a connectivity constraint implemented using sets of vertices, where
+vertex sets $A$ and $B$ are combined when there exists a pair of vertices $v \in A$ and $w \in B$
+and an edge $(v,w) \in E$. Residual degree counts are maintained on components and vertices to
+enforce graphicality and connectivity. In \cite{DBLP:conf/ecai/ProsserU06} a connectivity constraint was proposed for
+connected graph generation where decision variables are edges (the search process accepts and
+rejects edges). The constraint employed depth first search to maintain the set of tree edges and
+back edges, associating path counters on these edges. The counters were then used to detect the
+existence of cut-edges and protects these by forcing edges. The complexity of this constraint is
+cubic in the number of vertices.
+
+In all these previous works, the goal is to ensure that a given set of vertices is connected. For
+MCCS, the problem is slightly different: we have to ensure that the number of connected vertices
+that may be matched (in both graphs) is greater than the size of the largest common subgraph
+previously found. Therefore, we introduce a new filtering algorithm to ensure connectedness
+consistency for MCCS.  Let us consider two graphs $G$ and $G'$, and let $D$ be the current domains
+(we suppose that $D(x_u)$ is a singleton when $x_u$ is assigned). Let $C$ (resp. $C'$) be the set of
+nodes of $G$ (resp. $G'$) which may belong to the common subgraph, {\em i.e.}, $C=\{ u\in N_{G},
+D(x_u)\neq\{\bot\}\}$ (resp. $C' = \{u'\in N_{G'}, \exists u\in N_G, u'\in D(x_u)\}$). Let
+$G_{\downarrow C}$ (resp. $G'_{\downarrow C'}$) be the subgraph of $G$ induced by $C$ (resp. the
+subgraph of $G'$ induced by $C'$).  The connectedness consistency ensures that both $G_{\downarrow
+C}$ and $G'_{\downarrow C'}$ are connected graphs.
 
@@
 For each node $v'$ that is not visited by the traversal, we remove $v'$ from $C'$, and remove $v'$ from all domains it belong to.
-
-\christine{We have to relate this basic filtering with existing work: Connectedness \cite{Brown:2005} Reachability \cite{DBLP:conf/cp/DoomsDD05,DBLP:conf/cp/QuesadaRD05}.
-
-Samba and I have tried to find more clever ways for doing this filtering (in an incremental way).
-But we failed in finding something cheaper than performing a traversal each time a set of values are removed.
-In particular, we tried to adapt ideas from the paper of Patrick, but the problem is that we have to maintain counters on edges, and these counters must be restored when backtracking, and this is as expensive as performing a traversal (?).
-Any brilliant idea to share with us on this point?}
 

### 2016-04-15 paper/paper.tex
Refcheck, temporarily
Rewrap text

@@
 \usepackage{placeins}
+
+\usepackage{refcheck}
+
+\makeatletter\@ifpackageloaded{refcheck}{\newcommand{\citesforrefcheck}{\nocite{*}}}{\newcommand{\citesforrefcheck}{}}\makeatother
 
@@
 \paragraph{Definition of the Maximum Common (Connected) Subgraph Problem.}
-We introduce definitions and algorithms on undirected and unlabelled graphs.
-The extension to directed or labelled graphs is straightforward and discussed in Section \ref{extension}.
-An undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq N_G\times N_G$ such that each edge is an undirected pair of nodes.
-
-Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$.
-A graph $G$ is \emph{connected} if every pair of nodes is connected by a path.
-
-A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function $f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G, \{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
-
-A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a \emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
-In this definition, we only remove edges incident to removed nodes.
-This is usually called induced subgraph in the litterature.
-We may also allow to remove edges which are not incident to removed nodes, thus leading to partial subgraphs.
-In this paper, we only consider induced subgraphs.
-However, all algorithms may be extended to the partial case, as explained in \cite{DBLP:conf/cp/NdiayeS11}.
-
-A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and $G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
-A \emph{Maximum Common Subgraph} (MCS) (resp.
-\emph{Maximum Common Connected Subgraph} (MCCS) is a common subgraph (resp.
-common connected subgraph) which has a maximum number of nodes.
-Examples of MCS and MCCS are given in Fig.
-\ref{figure:mcsexample}.
-
-\paragraph{Overview of the paper.} In Section \ref{existing}, we review existing approaches for solving the MCS problem, with a specific focus on Constraint Programming (CP)-based approaches and on clique-based approaches that reduce the problem to finding a maximum clique in an association graph.
-
-Conventional wisdom is that clique-based approaches are less effective in practice, but previous experimental evaluations have used weak clique algorithms, or even maximal clique enumeration algorithms.
-Therefore, in Section \ref{eval1}, we  re-evaluate the clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive with CP on non labelled graphs.
-
-Then, in Section \ref{mccs}, we consider the MCCS problem.
-For the CP approach, we may add a global connectedness constraint to the model.
-Alternatively, we may use a special branching rule to grow connected subgraphs only, as proposed in \cite{DBLP:conf/mco/VismaraV08}.
-These two techniques may be combined, and we experimentally show that the best results are obtained when combining them.
-When solving the MCCS problem with a clique-based approach, neither technique seems directly viable with an association graph encoding.
-However, we show that it is possible to adapt the combined branching and bounding rule used by modern clique algorithms to preserve connectedness during search.
-We compare the clique-based approach with the best CP variant for the MCCS, and we show that it outperforms CP on non labelled graphs, whereas it is outperformed by CP on labelled graphs.
+We introduce definitions and algorithms on undirected and unlabelled graphs. The extension to
+directed or labelled graphs is straightforward and discussed in Section \ref{extension}. An
+undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq
+N_G\times N_G$ such that each edge is an undirected pair of nodes.
+
+Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a
+sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive
+nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$. A graph $G$
+is \emph{connected} if every pair of nodes is connected by a path.
+
+A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function
+$f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G,
+\{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
+
+A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a
+\emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
+In this definition, we only remove edges incident to removed nodes. This is usually called induced
+subgraph in the litterature. We may also allow to remove edges which are not incident to removed
+nodes, thus leading to partial subgraphs. In this paper, we only consider induced subgraphs.
+However, all algorithms may be extended to the partial case, as explained in
+\cite{DBLP:conf/cp/NdiayeS11}.
+
+A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and
+$G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
+A \emph{Maximum Common Subgraph} (MCS) (resp. \emph{Maximum Common Connected Subgraph} (MCCS) is a
+common subgraph (resp. common connected subgraph) which has a maximum number of nodes. Examples of
+MCS and MCCS are given in Fig. \ref{figure:mcsexample}.
+
+\paragraph{Overview of the paper.} In Section \ref{existing}, we review existing approaches for
+solving the MCS problem, with a specific focus on Constraint Programming (CP)-based approaches and
+on clique-based approaches that reduce the problem to finding a maximum clique in an association
+graph.
+
+Conventional wisdom is that clique-based approaches are less effective in practice, but previous
+experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
+algorithms.  Therefore, in Section \ref{eval1}, we  re-evaluate the clique-based approach using a
+modern algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive
+with CP on non labelled graphs.
+
+Then, in Section \ref{mccs}, we consider the MCCS problem. For the CP approach, we may add a global
+connectedness constraint to the model. Alternatively, we may use a special branching rule to grow
+connected subgraphs only, as proposed in \cite{DBLP:conf/mco/VismaraV08}. These two techniques may
+be combined, and we experimentally show that the best results are obtained when combining them.
+When solving the MCCS problem with a clique-based approach, neither technique seems directly viable
+with an association graph encoding.  However, we show that it is possible to adapt the combined
+branching and bounding rule used by modern clique algorithms to preserve connectedness during
+search.  We compare the clique-based approach with the best CP variant for the MCCS, and we show
+that it outperforms CP on non labelled graphs, whereas it is outperformed by CP on labelled graphs.
 
@@
 
-There exist two main approaches for solving MCS: The first approach (described in \ref{CP}) is based on CP; The second approach (described in \ref{clique}) is based on a reformulation of MCS into a maximum clique problem.
-Both approaches are described for non directed and non labelled graphs.
+There exist two main approaches for solving MCS: The first approach (described in \ref{CP}) is based
+on CP; The second approach (described in \ref{clique}) is based on a reformulation of MCS into a
+maximum clique problem. Both approaches are described for non directed and non labelled graphs.
 Their extension to directed or labelled graphs is discussed in Section \ref{extension}
@@
 
-McGregor \cite{McGreg82} proposed a Branch \& Bound approach: Each branch of the search tree corresponds to the matching of two nodes, and a  bounding function evaluates the number of nodes that still may be matched so that the current branch is pruned as soon as this bound becomes lower than the size of the largest known common subgraph.
-CP approaches may be viewed as enhancements of this Branch \& Bound approach.
-
-Vismara and Valery  \cite{DBLP:conf/mco/VismaraV08} introduced a first CP model.
-Given two graphs $G$ and $G'$, this model associates a variable $x_u$ with every node $u$ of $G$, and the domain of this variable contains all nodes of $G'$, plus an additional value $\bot$: variable $x_u$ is assigned to $\bot$ if node $u$ is not matched to any node of $G'$; otherwise $x_u$ is assigned to the node of $G'$ it is matched with.
-Edge constraints are introduced in order to ensure that variable assignments preserve edges between matched nodes, {\em i.e.},
-$\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee (\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'})$.
-Difference constraints are introduced in order to ensure that each node of $G'$ is assigned to at most one variable, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee (x_u\neq x_v)$.
-
-This CP model is improved in \cite{DBLP:conf/cp/NdiayeS11} by replacing binary difference constraints with a soft global allDifferent constraint which maximizes the number of $x_u$ variables that are assigned to values different from $\bot$, while ensuring they are all different when they are not assigned to $\bot$.
-Different constraint propagation techniques are compared in \cite{DBLP:conf/cp/NdiayeS11}.
-The combination ``MAC+Bound'' (resp.
-``FC+Bound'') obtains the best results on labelled (resp.
-non labelled) graphs and outperforms the approach of \cite{McGreg82} and the CP model of \cite{DBLP:conf/mco/VismaraV08}.
-The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs forward-checking on these constraints.
-In both combinations, the ``Bound'' filtering checks whether it is possible to assign distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that can be assigned distinct values).
+McGregor \cite{McGreg82} proposed a Branch \& Bound approach: Each branch of the search tree
+corresponds to the matching of two nodes, and a  bounding function evaluates the number of nodes
+that still may be matched so that the current branch is pruned as soon as this bound becomes lower
+than the size of the largest known common subgraph. CP approaches may be viewed as enhancements of
+this Branch \& Bound approach.
+
+Vismara and Valery  \cite{DBLP:conf/mco/VismaraV08} introduced a first CP model. Given two graphs
+$G$ and $G'$, this model associates a variable $x_u$ with every node $u$ of $G$, and the domain of
+this variable contains all nodes of $G'$, plus an additional value $\bot$: variable $x_u$ is
+assigned to $\bot$ if node $u$ is not matched to any node of $G'$; otherwise $x_u$ is assigned to
+the node of $G'$ it is matched with. Edge constraints are introduced in order to ensure that
+variable assignments preserve edges between matched nodes, {\em i.e.}, $\forall \{u,v\}\subseteq
+N_G, (x_u=\bot)\vee (x_v=\bot) \vee (\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'})$.
+Difference constraints are introduced in order to ensure that each node of $G'$ is assigned to at
+most one variable, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee
+(x_u\neq x_v)$.
+
+This CP model is improved in \cite{DBLP:conf/cp/NdiayeS11} by replacing binary difference
+constraints with a soft global allDifferent constraint which maximizes the number of $x_u$ variables
+that are assigned to values different from $\bot$, while ensuring they are all different when they
+are not assigned to $\bot$.  Different constraint propagation techniques are compared in
+\cite{DBLP:conf/cp/NdiayeS11}. The combination ``MAC+Bound'' (resp. ``FC+Bound'') obtains the best
+results on labelled (resp. non labelled) graphs and outperforms the approach of \cite{McGreg82} and
+the CP model of \cite{DBLP:conf/mco/VismaraV08}. The combination ``MAC+Bound'' maintains arc
+consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs
+forward-checking on these constraints. In both combinations, the ``Bound'' filtering checks whether
+it is possible to assign distinct values to enough $x_u$ variables to surpass the best cost found so
+far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum
+number of variables that can be assigned distinct values).
 
@@
 
-We may solve MCS by introducing an association graph and searching for a maximum clique in it \cite{bala86,dura99,DBLP:journals/jcamd/RaymondW02a}.
-
-An association graph of two graphs $G$ and $G'$ is an undirected graph $A_{G,G'}$ whose set of nodes is $N_{A_{G,G'}} = N_G \times N_{G'}$.
-To avoid confusing nodes of $A_{G,G'}$ with initial graph nodes, nodes of $A_{G,G'}$ are called matching nodes, as each node $(u,u')$ of $A_{G,G'}$ denotes the matching of $u$ with $u'$.
-Edges of $A_{G,G'}$ connect matching nodes which are compatible, {\em i.e.}, $E_{A_{G,G'}} = \big\{\{(u,u'),(v,v')\}\subseteq N_{A_{G,G'}}$, $(u,u')$ and $(v,v')$ are compatible$\big\}$, where two matching nodes $(u,u')$ and $(v,v')$ of $N_{A_{G,G'}}$ are compatible if $u \neq v$ and $u' \neq v'$, and if they preserve edges (\emph{i.e.}, $\{u,v\} \in E_G \Leftrightarrow \{u',v'\} \in E_{G'}$).
-
-A \emph{clique} is a subgraph whose nodes are all linked pairwise.
-A clique is \emph{maximal} if it is not strictly included in any other clique, and it is \emph{maximum} if it is the largest clique of a given graph, with respect to the number of nodes.
-
-A clique in $A_{G,G'}$ corresponds to a set of compatible matchings. Therefore, such a clique corresponds to a common subgraph, and a maximum clique of $A_{G,G'}$ is a MCS of $G$ and $G'$.
-It follows that any method able to find a maximum clique in a graph can be used to solve the MCS problem.
-
-Note that the association graph is a partial subgraph of the microstructure \cite{DBLP:conf/aaai/Jegou93a} associated with the CP model of  \cite{DBLP:conf/mco/VismaraV08}: The microstructure has more matching nodes than the association graph because it has a matching node $(u,\bot)$ for each node $u$ of $G$.
-Each clique of size $|N_G|$ in the microstructure corresponds to a common subgraph the size of which is defined by the number of nodes that do not contain $\bot$.
+We may solve MCS by introducing an association graph and searching for a maximum clique in it
+\cite{bala86,dura99,DBLP:journals/jcamd/RaymondW02a}.
+
+An association graph of two graphs $G$ and $G'$ is an undirected graph $A_{G,G'}$ whose set of nodes
+is $N_{A_{G,G'}} = N_G \times N_{G'}$. To avoid confusing nodes of $A_{G,G'}$ with initial graph
+nodes, nodes of $A_{G,G'}$ are called matching nodes, as each node $(u,u')$ of $A_{G,G'}$ denotes
+the matching of $u$ with $u'$. Edges of $A_{G,G'}$ connect matching nodes which are compatible, {\em
+i.e.}, $E_{A_{G,G'}} = \big\{\{(u,u'),(v,v')\}\subseteq N_{A_{G,G'}}$, $(u,u')$ and $(v,v')$ are
+compatible$\big\}$, where two matching nodes $(u,u')$ and $(v,v')$ of $N_{A_{G,G'}}$ are compatible
+if $u \neq v$ and $u' \neq v'$, and if they preserve edges (\emph{i.e.}, $\{u,v\} \in E_G
+\Leftrightarrow \{u',v'\} \in E_{G'}$).
+
+A \emph{clique} is a subgraph whose nodes are all linked pairwise.  A clique is \emph{maximal} if it
+is not strictly included in any other clique, and it is \emph{maximum} if it is the largest clique
+of a given graph, with respect to the number of nodes.
+
+A clique in $A_{G,G'}$ corresponds to a set of compatible matchings. Therefore, such a clique
+corresponds to a common subgraph, and a maximum clique of $A_{G,G'}$ is a MCS of $G$ and $G'$.  It
+follows that any method able to find a maximum clique in a graph can be used to solve the MCS
+problem.
+
+Note that the association graph is a partial subgraph of the microstructure
+\cite{DBLP:conf/aaai/Jegou93a} associated with the CP model of  \cite{DBLP:conf/mco/VismaraV08}: The
+microstructure has more matching nodes than the association graph because it has a matching node
+$(u,\bot)$ for each node $u$ of $G$. Each clique of size $|N_G|$ in the microstructure corresponds
+to a common subgraph the size of which is defined by the number of nodes that do not contain $\bot$.
 
@@
 
-In some applications, nodes and edges are associated with labels.
-We note $\lambda(u)$ and $\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively.
-In this case, the common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if $\lambda_1\simeq\lambda_2$.
-This kind of label compatibility constraint is handled in a straightforward way in both CP and clique-based approaches:
+In some applications, nodes and edges are associated with labels. We note $\lambda(u)$ and
+$\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively. In this case, the
+common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the
+compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if
+$\lambda_1\simeq\lambda_2$. This kind of label compatibility constraint is handled in a
+straightforward way in both CP and clique-based approaches:
+
 \begin{itemize}
-\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
-We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.
-
-\item For clique-based approaches, label compatibility is handled through the definition of the association graph, by restricting the set of matching nodes to pairs of nodes with compatible labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
-Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
+\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em
+    i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
+    We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall
+    \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow
+    \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.
+
+\item For clique-based approaches, label compatibility is handled through the definition of the
+    association graph, by restricting the set of matching nodes to pairs of nodes with compatible
+    labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
+    Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that
+    $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
 \end{itemize}
-Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.
-
-The extension of MCS algorithms to directed graphs is straightforward: For CP, edge orientation is handled in edge constraints; for clique-based approaches, it is handled in the definition of the association graph edges.
-In both cases, adding orientations to edges usually simplifies the problem: It tightens edge constraints for CP, and it makes the association graph sparser for  clique-based approaches.
+
+Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels
+reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels
+tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.
+
+The extension of MCS algorithms to directed graphs is straightforward: For CP, edge orientation is
+handled in edge constraints; for clique-based approaches, it is handled in the definition of the
+association graph edges. In both cases, adding orientations to edges usually simplifies the problem:
+It tightens edge constraints for CP, and it makes the association graph sparser for  clique-based
+approaches.
 
@@
 
-We consider a randomly generated database described in \cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}. 
-The dataset contains different classes of graphs: Randomly connected graphs with connectivity $\eta\in\{0.05,0.2\}$ (r005 and r02); 2D, 3D, and 4D regular meshes (m2D, m3D, m4D); 2D, 3D, and 4D irregular meshes with $\rho=0.6$ (m2Dr, m3Dr, and m4Dr); regular bounded valence graphs with $V\in\{3,9\}$ (b03 and b09) and irregular bounded valence graphs with $V\in\{3,9\}$ (b03m and b09m).
-Each class contains XXX pairs of graphs: YYY for each of the 5 possible sizes of the MCIS ({\em i.e.}, 10\%, 30\%, 50\%, 70\% and 90\% of the number of nodes of the original graphs).
-
-For each pair of graphs, there are 3 different labelings such that the number of different labels is equal to 33\%, 50\% or 75\% of the number of nodes.
-In this paper, we report experiments with non labelled graphs (labels are ignored), and with 33\% labellings.
+We consider a randomly generated database described in
+\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.
+The dataset contains different classes of graphs: Randomly connected graphs with connectivity
+$\eta\in\{0.05,0.2\}$ (r005 and r02); 2D, 3D, and 4D regular meshes (m2D, m3D, m4D); 2D, 3D, and 4D
+irregular meshes with $\rho=0.6$ (m2Dr, m3Dr, and m4Dr); regular bounded valence graphs with
+$V\in\{3,9\}$ (b03 and b09) and irregular bounded valence graphs with $V\in\{3,9\}$ (b03m and b09m).
+Each class contains XXX pairs of graphs: YYY for each of the 5 possible sizes of the MCIS ({\em
+i.e.}, 10\%, 30\%, 50\%, 70\% and 90\% of the number of nodes of the original graphs).
+
+For each pair of graphs, there are 3 different labelings such that the number of different labels is
+equal to 33\%, 50\% or 75\% of the number of nodes. In this paper, we report experiments with non
+labelled graphs (labels are ignored), and with 33\% labellings.
 
@@
 
-In many applications, the common subgraph must be connected.
-As illustrated in Fig.
-\ref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: We need to ensure connectedness during the search.
-In Section \ref{mccs-cp}, we show that this may be done in two different ways that may be combined, and we show in Section \ref{mccs-cp-eval} that the best results are obtained when combining them.
-In Section \ref{mccs-clique}, we introduce a new way for ensuring connectedness in a clique-based approach.
-Finally, we compare CP and our clique-based approach in Section \ref{mccs-eval}.
+In many applications, the common subgraph must be connected. As illustrated in Fig.
+\ref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: We need to ensure connectedness
+during the search. In Section \ref{mccs-cp}, we show that this may be done in two different ways
+that may be combined, and we show in Section \ref{mccs-cp-eval} that the best results are obtained
+when combining them. In Section \ref{mccs-clique}, we introduce a new way for ensuring connectedness
+in a clique-based approach. Finally, we compare CP and our clique-based approach in Section
+\ref{mccs-eval}.
 
@@
 
-\paragraph{Ensuring connectedness with a specific branching rule.}
-In \cite{DBLP:conf/mco/VismaraV08}, the connectedness constraint is ensured by using a specific branching rule, used to select the next variable to be assigned.
-Let $CComp$ be the set of variables already assigned to values different from $\bot$.
-The next variable to be assigned is chosen within the set of non assigned variables which are neighbor of at least one vertex of $CComp$.
-When this set is empty, all remaining non assigned variables are assigned to $\bot$.
+\paragraph{Ensuring connectedness with a specific branching rule.} In
+\cite{DBLP:conf/mco/VismaraV08}, the connectedness constraint is ensured by using a specific
+branching rule, used to select the next variable to be assigned. Let $CComp$ be the set of variables
+already assigned to values different from $\bot$. The next variable to be assigned is chosen within
+the set of non assigned variables which are neighbor of at least one vertex of $CComp$. When this
+set is empty, all remaining non assigned variables are assigned to $\bot$.
 
@@
 
-Connectedness consistency is not ensured at the root node of the search.
-It is ensured only once a first variable has been assigned.
-Let $x_u$ be the first assigned variable and $u'$ the value assigned to $x_u$.
-To ensure connectedness consistency, we perform a traversal of $G$ (resp.
-$G'$), starting from $u$ (resp.
-$u'$), and we initialize $C$ (resp.
-$C'$) with all visited nodes.
-Then, for each node $v\in N_G\setminus C$ (resp.
-$v'\in N_{G'}\setminus C'$), we assign $x_v$ to $\bot$ (resp., we remove $v'$ from all domains it belongs to).
-
-During the search, each time a variable is assigned to $\bot$, we remove the corresponding node from $C$ and perform a new traversal of $G_{\downarrow C}$ starting from the initial node $u$.
-For each node $v\in C$ that is not visited by the traversal, we remove $v$ from $C$ and assign $x_v$ to $\bot$.
-Also, each time a value is removed from a domain so that this value no longer belongs to any domain, we remove it from $C'$, and perform a new traversal of $G'_{\downarrow C'}$ starting from the initial node $u'$.
-For each node $v'$ that is not visited by the traversal, we remove $v'$ from $C'$, and remove $v'$ from all domains it belong to.
-
-\paragraph{Combining both approaches.} The two approaches for ensuring connectedness (branching and filtering) are complementary and may be combined: At each step of the search, we select the next variable to be assigned within the neighbors of $CComp$, and each time a node of $G'$ is removed from a domain we filter domains to ensure connectedness consistency.
+Connectedness consistency is not ensured at the root node of the search. It is ensured only once a
+first variable has been assigned. Let $x_u$ be the first assigned variable and $u'$ the value
+assigned to $x_u$. To ensure connectedness consistency, we perform a traversal of $G$ (resp. $G'$),
+starting from $u$ (resp. $u'$), and we initialize $C$ (resp. $C'$) with all visited nodes. Then, for
+each node $v\in N_G\setminus C$ (resp. $v'\in N_{G'}\setminus C'$), we assign $x_v$ to $\bot$
+(resp., we remove $v'$ from all domains it belongs to).
+
+During the search, each time a variable is assigned to $\bot$, we remove the corresponding node from
+$C$ and perform a new traversal of $G_{\downarrow C}$ starting from the initial node $u$. For each
+node $v\in C$ that is not visited by the traversal, we remove $v$ from $C$ and assign $x_v$ to
+$\bot$. Also, each time a value is removed from a domain so that this value no longer belongs to any
+domain, we remove it from $C'$, and perform a new traversal of $G'_{\downarrow C'}$ starting from
+the initial node $u'$. For each node $v'$ that is not visited by the traversal, we remove $v'$ from
+$C'$, and remove $v'$ from all domains it belong to.
+
+\paragraph{Combining both approaches.} The two approaches for ensuring connectedness (branching and
+filtering) are complementary and may be combined: At each step of the search, we select the next
+variable to be assigned within the neighbors of $CComp$, and each time a node of $G'$ is removed
+from a domain we filter domains to ensure connectedness consistency.
 
@@
 
-\christine{I propose that we report results only for the FC variant (or only for the MAC variant) as the conclusion is the same in both cases?}
-
-Fig.
-\ref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by specific branching (Branch), by specific filtering (Filter), or by combining specific branching and filtering (Both).
-We only report results obtained with the "FC+Bound" combination as the effect of the three approaches are very similar when combining them with "MAC+Bound".
-
-On labelled graphs, we observe that Branch often outperforms Filter, and that combining both Branch and Filter is rarely much worse than just doing one or the other, and is often much better, even if on average it's slightly slower.
+\christine{I propose that we report results only for the FC variant (or only for the MAC variant) as
+the conclusion is the same in both cases?}
+
+Fig. \ref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
+specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
+filtering (Both). We only report results obtained with the "FC+Bound" combination as the effect of
+the three approaches are very similar when combining them with "MAC+Bound".
+
+On labelled graphs, we observe that Branch often outperforms Filter, and that combining both Branch
+and Filter is rarely much worse than just doing one or the other, and is often much better, even if
+on average it's slightly slower.
 
@@
 
-\christine{Could we have the number of instances solved within 1 hour for each approach, and also the average solving time (for instances that are solved by the three approaches), so that we can give an idea of how much faster an approach is?}
+\christine{Could we have the number of instances solved within 1 hour for each approach, and also
+the average solving time (for instances that are solved by the three approaches), so that we can
+give an idea of how much faster an approach is?}
 
@@
 
-\FloatBarrier
+\citesforrefcheck
+
 \bibliographystyle{splncs}

### 2016-04-15 paper/paper.tex
Christine's abstract

@@
     clique problem. We evaluate these two models using modern algorithms, and see that the best
-    choice depends mainly upon whether the graphs have labelled edges. We also investigate a
-    restricted branching technique for the connected version of the problem, show how to implement
-    this in constraint-based and clique-inspired algorithms, and compare it to conventional
-    propagation.
+    choice depends mainly upon whether the graphs have labelled edges. We also study a variant of
+    this problem where the subgraph is required to be connected. We introduce a filtering algorithm
+    for this property and show that it may be combined with a restricted branching technique for the
+    constraint-based approach. We show how to implement a similar branching technique in
+    clique-inspired algorithms.  Finally, we experimentally compare approaches for the connected
+    version, and see again that the best choice depends on whether graphs have labels.
 \end{abstract}

### 2016-04-18 paper/paper.tex
Far too much mucking around (needs checking...)

@@
 % \usepackage{showframe}
+% \usepackage{refcheck}
 
@@
 \usepackage{amsmath}                   % \operatorname
-\usepackage{amsfonts}                  % \mathbb
+\usepackage{amssymb}                   % \triangledown
 \usepackage{hyperref}                  % clicky links
@@
 \usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
-\usepackage{placeins}
-
-\usepackage{refcheck}
 
@@
 
-\renewcommand{\floatpagefraction}{0.8}
+\renewcommand{\textfraction}{0.1}
+\renewcommand{\floatpagefraction}{0.85}
 \renewcommand{\topfraction}{0.9}
 \renewcommand{\bottomfraction}{0.8}
+
 \newcommand{\christine}[1]{{\color{green} Christine:#1}}
+
+\newcommand{\modularproduct}{\operatorname{\triangledown}}
 
@@
 measuring the similarity or difference between two graphs
-\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}.
-
-\paragraph{Definition of the Maximum Common (Connected) Subgraph Problem.}
-We introduce definitions and algorithms on undirected and unlabelled graphs. The extension to
-directed or labelled graphs is straightforward and discussed in Section \ref{extension}. An
-undirected graph $G$ is defined by a finite set of nodes $N_G$ and a set of edges $E_G\subseteq
-N_G\times N_G$ such that each edge is an undirected pair of nodes.
-
-Given a graph $G$, two nodes $n_s, n_e \in N_G$ are connected by a path in $G$ if there exists a
-sequence of nodes $<n_0,\ldots n_k>$ such that $n_0=n_s$, $n_k=n_e$ and each couple of successive
-nodes is connected by an edge, {\em i.e.}, $\forall i\in [1,k], \{n_{i-1},n_i\}\in E_G$. A graph $G$
-is \emph{connected} if every pair of nodes is connected by a path.
-
-A graph $G$ is \emph{isomorphic} to another graph $G'$ if there exists a bijective function
-$f:N_G\rightarrow N_{G'}$ which preserves edges, \emph{i.e.}, $\forall (u,v)\in N_G\times N_G,
-\{u,v\}\in E_G\Leftrightarrow \{f(u),f(v)\}\in E_{G'}$.
-
-A {\em subgraph} is obtained by removing nodes, and all their incident edges, {\em i.e.}, $G'$ is a
-\emph{subgraph} of $G$ if $N_{G'}\subseteq N_G$ and $E_{G'}=E_G\cap(N_{G'}\times N_{G'})$.
-In this definition, we only remove edges incident to removed nodes. This is usually called induced
-subgraph in the litterature. We may also allow to remove edges which are not incident to removed
-nodes, thus leading to partial subgraphs. In this paper, we only consider induced subgraphs.
-However, all algorithms may be extended to the partial case, as explained in
-\cite{DBLP:conf/cp/NdiayeS11}.
-
-A \emph{common subgraph} of two graphs $G$ and $G'$ is a graph isomorphic to subgraphs of $G$ and
-$G'$. A \emph{common connected subgraph} is a common subgraph which is connected.
-A \emph{Maximum Common Subgraph} (MCS) (resp. \emph{Maximum Common Connected Subgraph} (MCCS) is a
-common subgraph (resp. common connected subgraph) which has a maximum number of nodes. Examples of
-MCS and MCCS are given in Fig. \ref{figure:mcsexample}.
-
-\paragraph{Overview of the paper.} In Section \ref{existing}, we review existing approaches for
-solving the MCS problem, with a specific focus on Constraint Programming (CP)-based approaches and
-on clique-based approaches that reduce the problem to finding a maximum clique in an association
-graph.
+\cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
+variants of this problem in \cref{figure:mcsexample}.
+
+\subsection{Definitions and Notation}
+
+We introduce definitions and algorithms on undirected and unlabelled graphs without loops; the
+extension to general graphs is straightforward and is discussed in \cref{extension}. An undirected
+graph $G$ is defined by a finite set of vertices $\operatorname{V}(G)$ and a set of undirected edges
+$\operatorname{E}(G) \subseteq \operatorname{V}(G) \times \operatorname{V}(G)$, where $(u, v) \in
+\operatorname{E}(G) \Rightarrow (v, u) \in \operatorname{E}(G) \wedge u \ne v$. The neighbourhood of
+a vertex $v$, written $\operatorname{N}(G, v)$, is the set of vertices to which it is adjacent.
+Given a graph $G$, two vertices $v_s, v_e \in \operatorname{V}(G)$ are connected by a path in $G$ if
+there exists a sequence of vertices $(v_0, v_1, \ldots, v_k)$ such that $v_0 = v_s$, $v_k = v_e$,
+and each pair of successive vertices is connected by an edge, i.e.\ $\forall i\in \{1 \ldots k \},
+\{v_{i-1},v_i\}\in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every pair of vertices
+is connected by a path.
+
+The \emph{subgraph} of a graph $G$ \emph{induced by} a set $H \subseteq \operatorname{V}(G)$,
+written $G[H]$, is the graph with vertex set $H$, and with every edge in $G$ which has both
+endpoints in $G$, i.e.\ $\operatorname{E}(H) = \operatorname{E}(G) \cap (\operatorname{V}(H) \times
+\operatorname{V}(H))$. We will consider only subgraphs which are induced by some set. It is also
+possible to permit removing edges which are not incident to removed vertices, thus leading to
+partial subgraphs---we do not consider this possibility in this paper, although everything we
+discuss may be extended to the partial case \cite{DBLP:conf/cp/NdiayeS11}.
+
+A graph $G$ is \emph{isomorphic} to another graph $H$ if there exists a bijective function $f :
+\operatorname{V}(G) \rightarrow \operatorname{V}(H)$ which preserves edges and non-edges, i.e.\
+$\forall (u, v) \in \operatorname{V}(G) \times \operatorname{V}(G), (u, v) \in \operatorname{E}(G)
+\Leftrightarrow (f(u),f(v)) \in \operatorname{E}(H)$.  A \emph{common subgraph} of two graphs $G$
+and $H$ is a graph isomorphic to subgraphs of $G$ and $H$. A \emph{common connected subgraph} is a
+common subgraph which is connected.  A \emph{Maximum Common Subgraph} (MCS) (resp. \emph{Maximum
+Common Connected Subgraph} (MCCS) is a common subgraph (resp.\ common connected subgraph) which has
+a maximum number of vertices.
+
+\subsection{Overview}
+
+In \cref{existing}, we review existing approaches for solving the MCS problem, with a specific focus
+on Constraint Programming (CP)-based approaches, and on approaches that reduce the problem to
+finding a maximum clique in an association graph.
 
@@
 experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
-algorithms.  Therefore, in Section \ref{eval1}, we  re-evaluate the clique-based approach using a
-modern algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive
-with CP on non labelled graphs.
-
-Then, in Section \ref{mccs}, we consider the MCCS problem. For the CP approach, we may add a global
-connectedness constraint to the model. Alternatively, we may use a special branching rule to grow
-connected subgraphs only, as proposed in \cite{DBLP:conf/mco/VismaraV08}. These two techniques may
+algorithms.  Therefore, in \cref{eval1}, we  re-evaluate the clique-based approach using a modern
+algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive with CP
+on unlabelled graphs.
+
+Then, in \cref{mccs}, we consider the MCCS problem. For the CP approach, we may add a global
+connectedness constraint to the model. Alternatively, we may use a special branching rule
+\cite{DBLP:conf/mco/VismaraV08} to grow connected subgraphs only. These two techniques may
 be combined, and we experimentally show that the best results are obtained when combining them.
@@
 with an association graph encoding.  However, we show that it is possible to adapt the combined
-branching and bounding rule used by modern clique algorithms to preserve connectedness during
+branching and bounding rule used by modern clique algorithms to maintain connectedness during
 search.  We compare the clique-based approach with the best CP variant for the MCCS, and we show
-that it outperforms CP on non labelled graphs, whereas it is outperformed by CP on labelled graphs.
+that it outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.
 
@@
 
-There exist two main approaches for solving MCS: The first approach (described in \ref{CP}) is based
-on CP; The second approach (described in \ref{clique}) is based on a reformulation of MCS into a
-maximum clique problem. Both approaches are described for non directed and non labelled graphs.
-Their extension to directed or labelled graphs is discussed in Section \ref{extension}
-
-\subsection{CP model for MCS}
-\label{CP}
-
-McGregor \cite{McGreg82} proposed a Branch \& Bound approach: Each branch of the search tree
-corresponds to the matching of two nodes, and a  bounding function evaluates the number of nodes
-that still may be matched so that the current branch is pruned as soon as this bound becomes lower
-than the size of the largest known common subgraph. CP approaches may be viewed as enhancements of
-this Branch \& Bound approach.
-
-Vismara and Valery  \cite{DBLP:conf/mco/VismaraV08} introduced a first CP model. Given two graphs
-$G$ and $G'$, this model associates a variable $x_u$ with every node $u$ of $G$, and the domain of
-this variable contains all nodes of $G'$, plus an additional value $\bot$: variable $x_u$ is
-assigned to $\bot$ if node $u$ is not matched to any node of $G'$; otherwise $x_u$ is assigned to
-the node of $G'$ it is matched with. Edge constraints are introduced in order to ensure that
-variable assignments preserve edges between matched nodes, {\em i.e.}, $\forall \{u,v\}\subseteq
-N_G, (x_u=\bot)\vee (x_v=\bot) \vee (\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'})$.
-Difference constraints are introduced in order to ensure that each node of $G'$ is assigned to at
-most one variable, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee
-(x_u\neq x_v)$.
-
-This CP model is improved in \cite{DBLP:conf/cp/NdiayeS11} by replacing binary difference
-constraints with a soft global allDifferent constraint which maximizes the number of $x_u$ variables
-that are assigned to values different from $\bot$, while ensuring they are all different when they
-are not assigned to $\bot$.  Different constraint propagation techniques are compared in
-\cite{DBLP:conf/cp/NdiayeS11}. The combination ``MAC+Bound'' (resp. ``FC+Bound'') obtains the best
-results on labelled (resp. non labelled) graphs and outperforms the approach of \cite{McGreg82} and
-the CP model of \cite{DBLP:conf/mco/VismaraV08}. The combination ``MAC+Bound'' maintains arc
-consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs
-forward-checking on these constraints. In both combinations, the ``Bound'' filtering checks whether
-it is possible to assign distinct values to enough $x_u$ variables to surpass the best cost found so
-far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum
-number of variables that can be assigned distinct values).
-
-\subsection{Reformulation of MCS as a maximum clique problem}
-\label{clique}
-
-We may solve MCS by introducing an association graph and searching for a maximum clique in it
-\cite{bala86,dura99,DBLP:journals/jcamd/RaymondW02a}.
-
-An association graph of two graphs $G$ and $G'$ is an undirected graph $A_{G,G'}$ whose set of nodes
-is $N_{A_{G,G'}} = N_G \times N_{G'}$. To avoid confusing nodes of $A_{G,G'}$ with initial graph
-nodes, nodes of $A_{G,G'}$ are called matching nodes, as each node $(u,u')$ of $A_{G,G'}$ denotes
-the matching of $u$ with $u'$. Edges of $A_{G,G'}$ connect matching nodes which are compatible, {\em
-i.e.}, $E_{A_{G,G'}} = \big\{\{(u,u'),(v,v')\}\subseteq N_{A_{G,G'}}$, $(u,u')$ and $(v,v')$ are
-compatible$\big\}$, where two matching nodes $(u,u')$ and $(v,v')$ of $N_{A_{G,G'}}$ are compatible
-if $u \neq v$ and $u' \neq v'$, and if they preserve edges (\emph{i.e.}, $\{u,v\} \in E_G
-\Leftrightarrow \{u',v'\} \in E_{G'}$).
-
-A \emph{clique} is a subgraph whose nodes are all linked pairwise.  A clique is \emph{maximal} if it
-is not strictly included in any other clique, and it is \emph{maximum} if it is the largest clique
-of a given graph, with respect to the number of nodes.
-
-A clique in $A_{G,G'}$ corresponds to a set of compatible matchings. Therefore, such a clique
-corresponds to a common subgraph, and a maximum clique of $A_{G,G'}$ is a MCS of $G$ and $G'$.  It
-follows that any method able to find a maximum clique in a graph can be used to solve the MCS
-problem.
+There are two main approaches for solving MCS. The first approach (described in \cref{CP}) is based
+on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
+maximum clique problem. Both approaches are described for non directed and non labelled graphs;
+their extension to directed or labelled graphs is discussed in \cref{extension}.
+
+\subsection{Constraint Programming Models for MCS} \label{CP}
+
+McGregor \cite{McGreg82} proposed a branch and bound approach: each branch of the search tree
+corresponds to the matching of two vertices, and a bounding function evaluates the number of
+vertices that still may be matched so that the current branch is pruned as soon as this bound
+becomes lower than the size of the largest known common subgraph. CP approaches may be viewed as
+enhancements of this branch and bound algorithm.
+
+Vismara and Valery  \cite{DBLP:conf/mco/VismaraV08} introduced the first explicit CP model. Given
+two graphs $G$ and $H$, this model associates a variable $x_v$ with every vertex $v$ of $G$, and the
+domain of this variable contains all vertices of $H$, plus an additional value $\bot$: variable
+$x_v$ is assigned to $\bot$ if vertex $v$ is not matched to any vertex of $H$; otherwise $x_v$ is
+assigned to the vertex of $H$ to which it is matched. Edge constraints are introduced in order to
+ensure that variable assignments preserve edges and non-edges between matched vertices, i.e.\ $\forall u, v \in
+\operatorname{V}(G), (x_u = \bot) \vee (x_v = \bot) \vee ((u, v) \in \operatorname{E}(G)
+\Leftrightarrow (x_u, x_v) \in \operatorname{E}(H))$.  Difference constraints are introduced in
+order to ensure that each vertex of $H$ is assigned to at most one variable, i.e.\ $\forall u, v \in
+\operatorname{V}(G)~\textnormal{distinct,}~ (x_u = \bot) \vee (x_v = \bot) \vee (x_u \neq x_v)$.
+
+This CP model is improved by Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11} by replacing binary
+difference constraints with a soft global allDifferent constraint which maximizes the number of
+$x_u$ variables that are assigned to values different from $\bot$, while ensuring they are all
+different when they are not assigned to $\bot$. They find that the combination ``MAC+Bound'' (resp.
+``FC+Bound'') obtains the best results on labelled (resp. non labelled) graphs and outperforms the
+two previous approaches. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of
+edge constraints, whereas the combination ``FC+Bound'' simply performs forward-checking on these
+constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign
+distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker
+version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that
+can be assigned distinct values).
+
+\subsection{Reformulation of MCS to a Maximum Clique Problem}\label{clique}
+
+An alternative approach to MCS is to reduce the problem to finding a maximum clique in an
+association graph \cite{LeviG,bala86,dura99,DBLP:journals/jcamd/RaymondW02a}.
+An association graph (or compatibility graph, or weak modular product) of two graphs $G$ and $H$ is
+an undirected graph $G \modularproduct H$ with vertex set $\operatorname{V}(G \modularproduct H) =
+\operatorname{V}(G) \times \operatorname{V}(G)$---to avoid confusing vertices of $G \modularproduct
+H$ with vertices of the two original graphs, we call vertices of $G \modularproduct H$
+\emph{matching nodes}, as each vertex $(u, v)$ of $G \modularproduct H$ denotes the matching of $u$
+with $v$. The edges of $G \modularproduct H$ connect matching nodes which denote compatible
+assignments, so two matching nodes $(u, u')$ and  $(v, v')$ are adjacent if $u \neq v$ and $u' \neq
+v'$, and if they preserve both edges and non-edges, so $(u, v) \in \operatorname{E}(G) \Leftrightarrow
+(u', v') \in \operatorname{E}(H)$.
+
+A \emph{clique} is a subgraph whose vertices are all pairwise adjacent. A clique is \emph{maximal}
+if it is not strictly included in any other clique, and it is \emph{maximum} if it is a largest
+clique of a given graph, with respect to the number of vertices.  A clique in an association graph
+corresponds to a set of compatible matchings. Therefore, such a clique corresponds to a common
+subgraph, and a maximum clique of $G \modularproduct H$ is an MCS of $G$ and $H$.  It follows that
+any method able to find a maximum clique in a graph can be used to solve the MCS problem.
 
 Note that the association graph is a partial subgraph of the microstructure
-\cite{DBLP:conf/aaai/Jegou93a} associated with the CP model of  \cite{DBLP:conf/mco/VismaraV08}: The
-microstructure has more matching nodes than the association graph because it has a matching node
-$(u,\bot)$ for each node $u$ of $G$. Each clique of size $|N_G|$ in the microstructure corresponds
-to a common subgraph the size of which is defined by the number of nodes that do not contain $\bot$.
-
-\subsection{Extension to Labeled or Directed Graphs}\label{extension}
-
-In some applications, nodes and edges are associated with labels. We note $\lambda(u)$ and
-$\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively. In this case, the
-common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the
-compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if
-$\lambda_1\simeq\lambda_2$. This kind of label compatibility constraint is handled in a
-straightforward way in both CP and clique-based approaches:
-
-\begin{itemize}
-\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em
-    i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
-    We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall
-    \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow
-    \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.
-
-\item For clique-based approaches, label compatibility is handled through the definition of the
-    association graph, by restricting the set of matching nodes to pairs of nodes with compatible
-    labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
-    Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that
-    $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
-\end{itemize}
-
-Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels
-reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels
-tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.
-
-The extension of MCS algorithms to directed graphs is straightforward: For CP, edge orientation is
-handled in edge constraints; for clique-based approaches, it is handled in the definition of the
-association graph edges. In both cases, adding orientations to edges usually simplifies the problem:
-It tightens edge constraints for CP, and it makes the association graph sparser for  clique-based
-approaches.
+\cite{DBLP:conf/aaai/Jegou93a} associated with the CP model of  Vismara and Valery
+\cite{DBLP:conf/mco/VismaraV08}: the microstructure has more matching nodes than the association
+graph because it has a matching node $(u,\bot)$ for each vertex $u$ of $G$. Each clique of size
+$\left|\operatorname{V}(G)\right|$ in the microstructure corresponds to a common subgraph, the size
+of which is defined by the number of matching nodes that do not contain $\bot$.
+
+\subsection{Extension to Labelled or Directed Graphs, and Loops}\label{extension}
+
+In some applications, labels may be associated with vertices or edges. We denote $\lambda(u)$ and
+$\lambda((u, v))$ the label of a vertex $u$ and an edge $(u, v)$, respectively. Where graphs are
+labelled, any isomorphism $f$ must additionally preserve labels, so we require $\lambda(f(v)) =
+\lambda(v)$ for any vertex $v$, and $\lambda((f(u), f(v))) = \lambda((u, v))$ for any edge $(u, v)$.
+This kind of label compatibility constraint is handled in a straightforward way in both CP and
+clique-based approaches to MCS.  For CP, we restrict the domain of every variable $x_u$ to vertices
+with compatible labels, and ensure that edge labels are preserved in edge constraints.
+For clique-based approaches, label compatibility is handled through the definition of the
+association graph, by restricting the set of matching nodes to pairs of vertices with compatible
+labels, and the set of matching edges to pairs of edges with compatible labels.
+
+The extension of MCS algorithms to directed graphs, where isomorphisms must preserve directed edges,
+is similarly straightforward.
+Finally, some datasets contain loops (self-adjacent vertices). In this case vertices with loops must
+be mapped to vertices with loops (with the same labels, if appropriate), and vertices without loops
+may not be mapped to vertices with loops.
+
+Labels, directed edges and loops usually simplify the solution process, both for CP and clique-based
+approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in the
+association graphs; edge labels tighten edge constraints for CP, and make the association graph
+sparser for clique-based approaches.
+
+?? More on AC here? If we think carefully about the size of the domains of the objective variable:
+tightening the constraints doesn't really help unless you've made an assignment, right?
 
@@
 
-Previous experimental work has used a maximal clique enumeration algorithm, even for the
-maximisation problem. ?? check this! I recall someone using a bad max clique algorithm too.
-\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}
-
-We instead use a maximum clique algorithm.
-
-Also sparse stuff, but association graphs aren't sparse enough.
-
-Say which clique algorithm we're using.
-
-\subsection{Datasets}
-
-We consider a randomly generated database described in
-\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.
-The dataset contains different classes of graphs: Randomly connected graphs with connectivity
-$\eta\in\{0.05,0.2\}$ (r005 and r02); 2D, 3D, and 4D regular meshes (m2D, m3D, m4D); 2D, 3D, and 4D
-irregular meshes with $\rho=0.6$ (m2Dr, m3Dr, and m4Dr); regular bounded valence graphs with
-$V\in\{3,9\}$ (b03 and b09) and irregular bounded valence graphs with $V\in\{3,9\}$ (b03m and b09m).
-Each class contains XXX pairs of graphs: YYY for each of the 5 possible sizes of the MCIS ({\em
-i.e.}, 10\%, 30\%, 50\%, 70\% and 90\% of the number of nodes of the original graphs).
-
-For each pair of graphs, there are 3 different labelings such that the number of different labels is
-equal to 33\%, 50\% or 75\% of the number of nodes. In this paper, we report experiments with non
-labelled graphs (labels are ignored), and with 33\% labellings.
-
-\subsection{Experimental Evaluation}
+Previous experimental evaluations of the association graph model have used either maximal clique
+enumeration algorithms \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08} (even when the
+maximisation problem was being considered), or very simple maximum clique algorithms
+\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}. Thus we re-evaluate the approach
+using a modern maximum clique algorithm. Association graphs are dense, even if the input is sparse,
+so we will using (the single-threaded, bit-parallel version of) the maximum clique solver by
+McCreesh and Prosser \cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
+\cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita
+\textit{et al.}\
+\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
+bitset encoding due to San Segundo \textit{et al.}\
+\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the CP
+implementation of Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on
+machines with Intel Xeon E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and
+a timeout of one hour was used.
+
+We consider a randomly generated database
+\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07} commonly used for benchmarking
+maximum common subgraph problems.  The dataset contains different classes of graphs: randomly
+connected graphs with different densities; 2D, 3D, and 4D regular and irregular meshes; regular
+bounded valence graphs, and irregular bounded valence graphs.  For each pair of graphs, there are 3
+different labellings such that the number of different labels is equal to 33\%, 50\% or 75\% of the
+number of vertices. In this paper, we report experiments with unlabelled graphs (labels are
+ignored), and with 33\% labellings. For unlabelled graphs, we select the 27,500 graph pairs where the
+number of vertices in each graph is no more than 35; for labelled graphs, which we find less
+computationally challenging, we select all 81,400 graph pairs, to include graphs with up to 100
+vertices.
 
@@
     \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
-        labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
-        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the clique
-        model with the best CP model, with 33\% labelled graphs (with MAC) on the left, and
-        unlabelled and undirected graphs (with FC) on the right.} \label{figure:unconnected-cumulative}
+        labelled graphs, and in the middle, unlabelled and undirected graphs. On the bottom row, an
+        instance-by-instance comparison of the clique model with the best CP model, with 33\%
+        labelled graphs (with MAC) on the left, and unlabelled and undirected graphs (with FC) on
+    the right.} \label{figure:unconnected-cumulative}
 \end{figure}
 
-Fig. \ref{figure:unconnected-cumulative} displays the cumulative number of instances solved with respect to time.
-When graphs are labelled (top plot), the clique-based approach clearly outperforms CP. ...develop...
-
-\subsection{Parallel Search}
-
-\cite{DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16}
-
-?? Stuff on EHPs, how work stealing matters here too \cite{DBLP:journals/jco/BatsynGMP14}
+The top two plots of \cref{figure:unconnected-cumulative} display the cumulative number of instances
+solved with respect to time.  When graphs are labelled, the clique-based approach clearly
+outperforms either CP model, and MAC has a slight advantage over FC. For unlabelled graphs, the
+three approaches are broadly comparable, and ultimately FC beats MAC, which beats the clique
+approach. The bottom row gives a per-instance comparison of the best CP approach with the clique
+approach: the heatmaps are similar to scatter plots, but due to the large number of instances, we
+colour each point according to the density of solutions around that point. For labelled graphs, the
+clique approach comes close to dominating MAC on non-trivial instances (which suggests that there is
+unlikely to be scope for per-instance algorithm selection here). For unlabelled graphs, there is
+still a broad correlation between the runtimes; the clique approach rarely wins by more than one
+order of magnitude, but is sometimes much worse.
+
+A closer inspection of the data suggests that the different randomness models have little effect on
+the runtimes for either approach. However, the relative size of the solution matters, particularly
+for the clique algorithm: if the solution is large (i.e.\ the two input graphs are very similar),
+the clique approach finds nearly every labelled instance trivial.
 
@@
 
-In many applications, the common subgraph must be connected. As illustrated in Fig.
-\ref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: We need to ensure connectedness
-during the search. In Section \ref{mccs-cp}, we show that this may be done in two different ways
-that may be combined, and we show in Section \ref{mccs-cp-eval} that the best results are obtained
-when combining them. In Section \ref{mccs-clique}, we introduce a new way for ensuring connectedness
-in a clique-based approach. Finally, we compare CP and our clique-based approach in Section
-\ref{mccs-eval}.
+In many applications, the common subgraph must be connected. As illustrated in
+\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
+during the search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
+may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
+combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
+clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.
 
 \subsection{Ensuring Connectedness in CP}\label{mccs-cp}
-
-\paragraph{Ensuring connectedness with a specific branching rule.} In
-\cite{DBLP:conf/mco/VismaraV08}, the connectedness constraint is ensured by using a specific
-branching rule, used to select the next variable to be assigned. Let $CComp$ be the set of variables
-already assigned to values different from $\bot$. The next variable to be assigned is chosen within
-the set of non assigned variables which are neighbor of at least one vertex of $CComp$. When this
-set is empty, all remaining non assigned variables are assigned to $\bot$.
-
-\paragraph{Ensuring connectedness with a specific filtering.}
-
-CP(Graph) \cite{DBLP:conf/cp/DoomsDD05} introduces graph domain variables and enforces connectivity via the
-\emph{reachable} constraint, ensuring that there is a path from a specified vertex to a specified
-set of vertices. One such constraint is then posted for each of the vertices in the graph and
-encodes the transitive closure of the graph. Brown et al.\ \cite{Brown:2005} explored the use of
-constraint programming in the generation of connected graphs with specified degree sequences.  Two
-constraints were combined, i.e.\ the graphical constraint (a backtrackable implementation of the
-Havel-Hakimi algorithm) with a connectivity constraint implemented using sets of vertices, where
-vertex sets $A$ and $B$ are combined when there exists a pair of vertices $v \in A$ and $w \in B$
-and an edge $(v,w) \in E$. Residual degree counts are maintained on components and vertices to
-enforce graphicality and connectivity. In \cite{DBLP:conf/ecai/ProsserU06} a connectivity constraint was proposed for
-connected graph generation where decision variables are edges (the search process accepts and
-rejects edges). The constraint employed depth first search to maintain the set of tree edges and
-back edges, associating path counters on these edges. The counters were then used to detect the
-existence of cut-edges and protects these by forcing edges. The complexity of this constraint is
-cubic in the number of vertices.
-
-In all these previous works, the goal is to ensure that a given set of vertices is connected. For
-MCCS, the problem is slightly different: we have to ensure that the number of connected vertices
-that may be matched (in both graphs) is greater than the size of the largest common subgraph
-previously found. Therefore, we introduce a new filtering algorithm to ensure connectedness
-consistency for MCCS.  Let us consider two graphs $G$ and $G'$, and let $D$ be the current domains
-(we suppose that $D(x_u)$ is a singleton when $x_u$ is assigned). Let $C$ (resp. $C'$) be the set of
-nodes of $G$ (resp. $G'$) which may belong to the common subgraph, {\em i.e.}, $C=\{ u\in N_{G},
-D(x_u)\neq\{\bot\}\}$ (resp. $C' = \{u'\in N_{G'}, \exists u\in N_G, u'\in D(x_u)\}$). Let
-$G_{\downarrow C}$ (resp. $G'_{\downarrow C'}$) be the subgraph of $G$ induced by $C$ (resp. the
-subgraph of $G'$ induced by $C'$).  The connectedness consistency ensures that both $G_{\downarrow
-C}$ and $G'_{\downarrow C'}$ are connected graphs.
-
-Connectedness consistency is not ensured at the root node of the search. It is ensured only once a
-first variable has been assigned. Let $x_u$ be the first assigned variable and $u'$ the value
-assigned to $x_u$. To ensure connectedness consistency, we perform a traversal of $G$ (resp. $G'$),
-starting from $u$ (resp. $u'$), and we initialize $C$ (resp. $C'$) with all visited nodes. Then, for
-each node $v\in N_G\setminus C$ (resp. $v'\in N_{G'}\setminus C'$), we assign $x_v$ to $\bot$
-(resp., we remove $v'$ from all domains it belongs to).
-
-During the search, each time a variable is assigned to $\bot$, we remove the corresponding node from
-$C$ and perform a new traversal of $G_{\downarrow C}$ starting from the initial node $u$. For each
-node $v\in C$ that is not visited by the traversal, we remove $v$ from $C$ and assign $x_v$ to
-$\bot$. Also, each time a value is removed from a domain so that this value no longer belongs to any
-domain, we remove it from $C'$, and perform a new traversal of $G'_{\downarrow C'}$ starting from
-the initial node $u'$. For each node $v'$ that is not visited by the traversal, we remove $v'$ from
-$C'$, and remove $v'$ from all domains it belong to.
-
-\paragraph{Combining both approaches.} The two approaches for ensuring connectedness (branching and
-filtering) are complementary and may be combined: At each step of the search, we select the next
-variable to be assigned within the neighbors of $CComp$, and each time a node of $G'$ is removed
-from a domain we filter domains to ensure connectedness consistency.
-
-\subsection{ Experimental comparison of CP models}\label{mccs-cp-eval}
-
-\begin{figure}[p]
-    \centering
-    \input{gen-graph-connected-cp.tex}
-    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
-    number of instances with these runtimes, with darker colours representing more instances. The
-    top two rows are for 33\% labelled undirected graphs with up to 100 vertices, and the bottom two
-    rows are for unlabelled and undirected graphs with up to 35 vertices.}
-        \label{figure:connected-cp}
-\end{figure}
-
-\christine{I propose that we report results only for the FC variant (or only for the MAC variant) as
-the conclusion is the same in both cases?}
-
-Fig. \ref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
-specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
-filtering (Both). We only report results obtained with the "FC+Bound" combination as the effect of
-the three approaches are very similar when combining them with "MAC+Bound".
-
-On labelled graphs, we observe that Branch often outperforms Filter, and that combining both Branch
-and Filter is rarely much worse than just doing one or the other, and is often much better, even if
-on average it's slightly slower.
-
-On unlabelled graphs, we observe that the three variants have rather similar performance.
-
-\christine{Could we have the number of instances solved within 1 hour for each approach, and also
-the average solving time (for instances that are solved by the three approaches), so that we can
-give an idea of how much faster an approach is?}
-
-\subsection{Ensuring Connectedness in a clique-based approach}\label{mccs-clique}
-
-\christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}
 
@@
 
-        \begin{scope}[xshift=13cm]
+        \begin{scope}[xshift=12.8cm]
             \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
@@
 
-        \begin{scope}[xshift=26cm]
+        \begin{scope}[xshift=25.6cm]
             \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
@@
 
-        \begin{scope}[xshift=13cm, yshift=-9cm]
+        \begin{scope}[xshift=12.8cm, yshift=-9cm]
             \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
@@
 
-\cref{figure:restricted} The key idea is that whenever we branch (except for the first choice we
-make), we select only from variables which correspond to vertices which are adjacent to at least one
-other variable which has been instantiated to a value other than $\bot$. If no such variables
-remain, the subgraph we are building cannot grow any further, and all remaining variables must be
-instantiated to $\bot$.
-
-?? Patrick reckons this reminds him of Prim's algorithm for minimum spanning trees.
-
-\begin{algorithm}[p] \DontPrintSemicolon
+Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
+specific branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
+set of variables already assigned to values different from $\bot$. The next variable to be assigned
+is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
+$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
+$\bot$. We illustrate this in \cref{figure:restricted}.
+
+A more conventional CP approach would be to express connectedness as a conventional constraint. For
+example, CP(Graph) \cite{DBLP:conf/cp/DoomsDD05} introduces graph domain variables and enforces
+connectivity via the \emph{reachable} constraint, ensuring that there is a path from a specified
+vertex to a specified set of vertices. One such constraint is then posted for each of the vertices
+in the graph and encodes the transitive closure of the graph. Brown et al.\ \cite{Brown:2005}
+explored the use of constraint programming in the generation of connected graphs with specified
+degree sequences.  Two constraints were combined, i.e.\ the graphical constraint (a backtrackable
+implementation of the Havel-Hakimi algorithm) with a connectivity constraint implemented using sets
+of vertices, where vertex sets $A$ and $B$ are combined when there exists a pair of vertices $v \in
+A$ and $w \in B$ and an edge $(v,w) \in E$. Residual degree counts are maintained on components and
+vertices to enforce graphicality and connectivity. Prosser and Unsworth
+\cite{DBLP:conf/ecai/ProsserU06} proposed a connectivity constraint for connected graph generation
+where decision variables are edges (the search process accepts and rejects edges). The constraint
+employed depth first search to maintain the set of tree edges and back edges, associating path
+counters on these edges. The counters were then used to detect the existence of cut-edges and
+protects these by forcing edges; the complexity of this constraint is cubic in the number of
+vertices.
+
+In all these previous works, the goal was to ensure that a given set of vertices is connected. For
+MCCS, the problem is slightly different: we have to ensure that the number of connected vertices
+that may be matched (in both graphs) is greater than the size of the largest common subgraph
+previously found. Therefore, we introduce a new filtering algorithm to ensure connectedness) (resp.
+consistency for MCCS.  Let us consider two graphs $G$ and $H$, and let $D$ be the current domains
+(we suppose that $D(x_u)$ is a singleton when $x_u$ is assigned). Let $S$ and $T$ be the sets of
+vertices of $G$ and $H$ respectively which may belong to the common subgraph, i.e.\ $S=\{ u\in
+\operatorname{V}(G) : D(x_u)\neq\{\bot\}\}$, and $T = \cup_{u\in \operatorname{V}(G)} D(x_u)
+\setminus \{ \bot \}$. Connectedness consistency ensures that both $G[S]$ and $H[T]$ are
+connected graphs.
+
+Connectedness consistency is not ensured at the root node of the search---it is ensured only once a
+first variable has been assigned. Let $x_u$ be the first assigned variable, and $v$ the value
+assigned to $x_u$. To ensure connectedness consistency, we perform a traversal of $G$ (resp.\ $H$),
+starting from $u$ (resp.\ $v$), and we initialize $S$ (resp.\ $T$) with all visited vertices. Then,
+for each vertex $v\in \operatorname{V}(G) \setminus S$, we set $x_v$ to $\bot$, and for each $w
+\in \operatorname{V}(H) \setminus T$, we remove $w$ from all domains to which it belongs.
+
+During the search, each time a variable is assigned to $\bot$, we remove the corresponding vertex
+from $S$ and perform a new traversal of $G[S]$ starting from the initial vertex $u$. For each vertex
+$w\in S$ that is not visited by the traversal, we remove $w$ from $S$ and assign $x_w$ to $\bot$.
+Also, each time a value is removed from a domain so that this value no longer belongs to any domain,
+we remove it from $T$, and perform a new traversal of $H[T]$ starting from the initial vertex $v$.
+For each vertex $w$ that is not visited by the traversal, we remove $w$ from $T$, and remove $w$
+from all domains to which it belongs.
+
+Finally, the two approaches for ensuring connectedness (branching and filtering) are complementary
+and may be combined: at each step of the search, we select the next variable to be assigned within
+the neighbors of $\mathit{CComp}$, and each time a vertex of $H$ is removed from a domain we filter
+domains to ensure connectedness consistency.
+
+\begin{figure}[tb]
+    \centering
+    \input{gen-graph-connected-cumulative-cp}
+
+    \vspace*{1em}
+    \centering
+    \input{gen-graph-connected-cp}
+    \caption{A pairwise comparison of different CP techniques. ?? This looks horrible! Make it look
+        better.} \label{figure:connected-cp}
+\end{figure}
+
+\subsection{Experimental Comparison of CP Models}\label{mccs-cp-eval}
+
+\Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
+specific branching (Branching), by specific filtering (Filtering), or by combining specific
+branching and filtering (Both). We show only results using MAC for labelled graphs, and FC for
+unlabelled graphs, as the other results are very similar.  On labelled graphs, we observe that
+branching often outperforms filtering, and that combining both is rarely much worse than just doing
+one or the other, and is often much better, even if on average it is slightly slower.  On unlabelled
+graphs, we observe that the three variants have rather similar performance.
+
+\subsection{Ensuring Connectedness in a clique-based approach}\label{mccs-clique}
+
+\christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}
+
+\begin{algorithm}[tb] \DontPrintSemicolon
 \nl $\FuncSty{associationMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
@@
     \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \label{incumbent} \;
-    \nl $G \gets \FuncSty{associationGraph}(G_1, G_2)$ \label{buildassoc} \;
+    \nl $G \gets G_1 \modularproduct G_2$ \label{buildassoc} \;
     \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \label{firstsearch} \;
@@
 }
-\vspace{0.9ex}
+\vspace{1ex}
 \nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
@@
             \mathit{solution}'$ \label{newincumbent}}
-            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \FuncSty{connected}(G, v)$ \label{addtobranchable} \;
+            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \{ w \in G : \FuncSty{first}(w)
+            \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \label{addtobranchable} \;
             \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \label{filterremaining} \;
@@
 }
-\vspace{0.9ex}
+\vspace{0.5ex}
 \nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;
@@
 }
-\vspace{0.9ex}
-\nl $\FuncSty{connected}$ :: (Graph $G$, Vertex $v$) $\rightarrow$ Set \;
-\nl \Begin{
-    \nl $\KwSty{return} ~ \{ w \in G : \FuncSty{first}(w) \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \;
-}
-\vspace{0.9ex}
-\nl $\FuncSty{associationGraph}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Graph \;
-\nl \Begin{
-    \nl $V \gets \{ (v_1, v_2) \in G_1 \times G_2 : v_1 \simeq v_2 \}$ \;
-    \nl $E \gets \{ ((v_1, v_2), (w_1, w_2)) \in V \times V : (v_1, w_1) \simeq (v_2, w_2) \}$ \;
-    \nl $\KwSty{return} ~ (V, v \mapsto 1, (v, w) \mapsto 1~\KwSty{if}~(v, w) \in E~\KwSty{otherwise}~\bot )$ \;
-}
 \caption{An algorithm for a maximum common connected induced subgraph isomorphism via an association graph.}
@@
 \end{algorithm}
+
+It is not possible to determine connectedness from a raw association graph. However, we can take a
+maximum clique algorithm and mimic the branching strategy if we have access to the underlying graphs
+and can determine the ``meaning'' of the association graph vertices.
+
+Most modern maximum clique algorithms for dense graphs use some variation of greedy graph colouring
+as a bound---the underlying observation is that each vertex in a clique must be given a different
+colour in a colouring, so if we can colour a subset of vertices using $k$ colours then a maximum
+clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
+heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
+last colour class created. Because of this coupling of branching and the bound (which is important
+in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
+viewed as variables \cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for
+branching at each stage inside a clique algorithm, we would lose completeness. Thus we must adapt
+the bound to take into account restricted branching.
+
+In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
+connected induced subgraph isomorphism via an association graph. If the additional branching
+restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm
+used in the previous section (and we refer the reader to the previously cited works for
+implementation details on how to use bitsets and other data structures to implement the colouring
+stage with very low constant factors).
+
+We begin by building the association graph (\lineref{buildassoc}). The main part of the algorithm
+then works by building up candidate cliques in the $\mathit{solution}$ variable, by recursive calls
+to the $\mathit{search}$ procedure---starting from the empty set (\lineref{firstsearch}), each
+recursive subcall adds one vertex to $\mathit{solution}$ (\lineref{addv}) in such a way that
+$\mathit{solution}$ is always a clique which corresponds to a connected common subgraph. The
+$\mathit{remaining}$ set contains the set of vertices which are adjacent to every vertex in
+$\mathit{solution}$, and which have not yet been accepted or rejected (and so initially it contains
+every vertex). The main loops in the $\FuncSty{search}$ procedure
+(\twolinesref{outerloop}{innerloop}) have the effect of iterating over each vertex in this set in a
+particular order---each vertex $v$ is selected in turn, and then a recursive call is made to
+consider the effects of including $v$ in $\mathit{solution}$ (\lineref{recursesearch}), followed by
+the next iteration where $v$ is instead rejected. When $v$ is accepted, we add it to the new
+$\mathit{solution'}$ (\lineref{addvtosolution}), and create a new $\mathit{remaining'}$ containing
+only the vertices in $\mathit{remaining}$ which are adjacent to $v$ (\lineref{filterremaining}).
+
+The $\mathit{branchable}$ set contains the set of association graph vertices which correspond to
+vertices adjacent to an already-accepted vertex in the first input graph---in constraint programming terms, it is the
+set of assignments which could be made next which maintain connectedness. (Using only one of the two
+input graphs is sufficient for correctness, and has the advantage that the $\FuncSty{connected}$
+function may be implemented as a simple lookup into a precomputed array which maps each vertex in
+the first input graph to a bitset.) At the top of search, this set is empty, and is not used (our
+first vertex selection is special, and does not care about connectedness). At subsequent depths, we
+may only accept vertices which are in this set, and if no such vertices remain then we return
+immediately (\lineref{acceptbranchable}). When recursing, we extend $\mathit{branchable}$ with the
+new vertices permitted by our acceptance of the branching $v$ (\lineref{addtobranchable}). Note that
+we are assuming that inside the main loops, we encounter every vertex in $\mathit{remaining} \cap
+\mathit{connected}$ before any vertex in $\mathit{remaining} \setminus \mathit{connected}$.
+
+As we proceed, we keep track of the best solution we have found so far---this is stored in the
+$\mathit{incumbent}$ variable (\twolinesref{incumbent}{newincumbent}). We use the incumbent,
+together with a colour bound, to prune portions of the search space which cannot contain a better
+solution. The colour bound operates as follows: at each entry to the $\FuncSty{search}$ procedure,
+we produce a greedy colouring of the vertices in $\mathit{remaining}$ (\lineref{makecolours}). This
+greedy colouring gives us a list of colour classes, each of which is a list of pairwise non-adjacent
+vertices. The two loops (\twolinesref{outerloop}{innerloop}) then iterate over each colour class,
+from last to first, and then over each vertex in that colour class, again from last to first.
+(Rather than actually using a list of lists and removing items, this process should be implemented
+using a pair of immutable flat arrays. This technique is described elsewhere
+\cite{DBLP:conf/cp/McCreeshP14}, so we do not discuss it here.) Finally, if at any point the number
+of remaining colour classes plus the number of vertices currently present in $\mathit{solution}$ is
+not strictly greater than the size of the incumbent, then we may backtrack immediately
+(\lineref{bound}).
 
@@
             \stepcounter{stepcounter2}\roman{stepcounter2}) Search variables after guessing $a \mapsto 1$
-            \\[0.4cm]
+            \\[0.2cm]
             \begin{tikzpicture}[scale=0.33]
-                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 3) {\phantom{0}};
-                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
+                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
                     \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
@@
             \begin{tikzpicture}[scale=0.33]
-                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 3) {\phantom{0}};
-                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 3) {\phantom{0}};
+                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 2) {\phantom{0}};
+                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 2) {\phantom{0}};
                     \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
@@
         };
-    \end{tikzpicture}\\[0.3cm]\begin{tikzpicture}[scale=0.33]
+    \end{tikzpicture}\\[0.1cm]\begin{tikzpicture}[scale=0.33]
         \matrix (m) [matrix of nodes] {
@@
             \end{tikzpicture}
-            \\[0.1cm]
+            \\[0.05cm]
             \stepcounter{stepcounter2}\roman{stepcounter2}) The resulting $\mathit{colourClasses}$ variable.
@@
 
-It is not possible to determine connectedness from a raw association graph. However, we can take a
-maximum clique algorithm and mimic the branching strategy if we have access to the underlying graphs
-and can determine the ``meaning'' of the association graph vertices.
-
-Most modern maximum clique algorithms for dense graphs use some variation of greedy graph colouring
-as a bound---the underlying observation is that each vertex in a clique must be given a different
-colour in a colouring, so if we can colour a subset of vertices using $k$ colours then a maximum
-clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
-heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
-last colour class created. Because of this coupling of branching and the bound (which is important
-in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
-viewed as variables \cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for
-branching at each stage inside a clique algorithm, we would lose completeness. Thus we must adapt
-the bound to take into account restricted branching.
-
-In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
-connected induced subgraph isomorphism via an
-association graph. If the additional
-branching restrictions are removed, the core of the algorithm is what Prosser
-\cite{DBLP:journals/algorithms/Prosser12} calls the ``MCSa1'' variant of a series of algorithms due
-to Tomita \textit{et al.}\
-\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
-bitset encoding due to San Segundo \textit{et al.}\
-\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13} (and we refer the reader to these
-papers for implementation details on how to use bitsets and other data structures to implement the
-colouring stage with very low constant factors).
-
-We begin by building the association graph (\lineref{buildassoc}). The main part of the algorithm
-then works by building up candidate cliques in the $\mathit{solution}$ variable, by recursive calls
-to the $\mathit{search}$ procedure---starting from the empty set (\lineref{firstsearch}), each
-recursive subcall adds one vertex to $\mathit{solution}$ (\lineref{addv}) in such a way that
-$\mathit{solution}$ is always a clique which corresponds to a connected common subgraph. The
-$\mathit{remaining}$ set contains the set of vertices which are adjacent to every vertex in
-$\mathit{solution}$, and which have not yet been accepted or rejected (and so initially it contains
-every vertex). The main loops in the $\FuncSty{search}$ procedure
-(\twolinesref{outerloop}{innerloop}) have the effect of iterating over each vertex in this set in a
-particular order---each vertex $v$ is selected in turn, and then a recursive call is made to
-consider the effects of including $v$ in $\mathit{solution}$ (\lineref{recursesearch}), followed by
-the next iteration where $v$ is instead rejected. When $v$ is accepted, we add it to the new
-$\mathit{solution'}$ (\lineref{addvtosolution}), and create a new $\mathit{remaining'}$ containing
-only the vertices in $\mathit{remaining}$ which are adjacent to $v$ (\lineref{filterremaining}).
-
-The $\mathit{branchable}$ set contains the set of association graph vertices which correspond to
-vertices adjacent to an already-accepted vertex in the first input graph---in constraint programming terms, it is the
-set of assignments which could be made next which preserve connectedness. (Using only one of the two
-input graphs is sufficient for correctness, and has the advantage that the $\FuncSty{connected}$
-function may be implemented as a simple lookup into a precomputed array which maps each vertex in
-the first input graph to a bitset.) At the top of search, this set is empty, and is not used (our
-first vertex selection is special, and does not care about connectedness). At subsequent depths, we
-may only accept vertices which are in this set, and if no such vertices remain then we return
-immediately (\lineref{acceptbranchable}). When recursing, we extend $\mathit{branchable}$ with the
-new vertices permitted by our acceptance of the branching $v$ (\lineref{addtobranchable}). Note that
-we are assuming that inside the main loops, we encounter every vertex in $\mathit{remaining} \cap
-\mathit{connected}$ before any vertex in $\mathit{remaining} \setminus \mathit{connected}$.
-
-As we proceed, we keep track of the best solution we have found so far---this is stored in the
-$\mathit{incumbent}$ variable (\twolinesref{incumbent}{newincumbent}). We use the incumbent,
-together with a colour bound, to prune portions of the search space which cannot contain a better
-solution. The colour bound operates as follows: at each entry to the $\FuncSty{search}$ procedure,
-we produce a greedy colouring of the vertices in $\mathit{remaining}$ (\lineref{makecolours}). This
-greedy colouring gives us a list of colour classes, each of which is a list of pairwise non-adjacent
-vertices. The two loops (\twolinesref{outerloop}{innerloop}) then iterate over each colour class,
-from last to first, and then over each vertex in that colour class, again from last to first.
-(Rather than actually using a list of lists and removing items, this process should be implemented
-using a pair of immutable flat arrays. This technique is described elsewhere
-\cite{DBLP:conf/cp/McCreeshP14}, so we do not discuss it here.) Finally, if at any point the number
-of remaining colour classes plus the number of vertices currently present in $\mathit{solution}$ is
-not strictly greater than the size of the incumbent, then we may backtrack immediately
-(\lineref{bound}).
-
-Finally, we describe the colouring process. In conventional clique algorithms, a simple greedy
-sequential colouring is used (possibly with the help of previous colourings to reduce the
-computational cost \cite{DBLP:conf/lion/NikolaevBS15}, and possibly with shortcuts taken for certain
-vertices \cite{DBLP:journals/cor/SegundoT14}, and possibly followed by a repair step to
-improve the colouring \cite{DBLP:conf/walcom/TomitaSHTW10}, or stronger bounding rules based upon
-MaxSAT inference \cite{DBLP:conf/ictai/LiFX13,DBLP:conf/lion/LiJX15,DBLP:journals/cor/SegundoNB15}).
-Such colourings will not give us the required property that vertices in $\mathit{remaining} \cap
-\mathit{connected}$ come last (so they are selected first by the reverse branching order). Thus we
-produce two greedy sequential colourings, first considering the non-branching vertices in
-$\mathit{remaining} \setminus \mathit{connected}$, followed by the branching vertices, and
-concatenate them (\lineref{makecolours}). This produces a valid colouring, since we do not merge any
-colour classes between the two stages, although it may use more colours than a single colouring
-would\footnote{What if we did not guarantee that vertices in $\mathit{remaining} \cap
-    \mathit{connected}$ came last, and just used a conventional colouring with the branching rule?
-    Suppose we had four vertices in $\mathit{remaining}$, and produced a colouring $[[v_1, v_2],
-    [v_3], [v_4]]$, and suppose that extending $\mathit{solution}$ with $\{ v_1, v_3, v_4 \}$ gives
-an optimal solution. If $v_4$ was not $\mathit{connected}$ yet, we would not branch on that subtree,
-and the bound could eliminate branching on $v_3$ and $v_1$, so we would miss the solution. Thus we
-cannot simply add the branching rule without also adapting the combined bound / ordering heuristic.}.
+Finally, we describe the colouring process---an example is shown in \cref{figure:assocrestricted}.
+In conventional clique algorithms, a simple greedy sequential colouring is used (possibly with the
+help of previous colourings to reduce the computational cost \cite{DBLP:conf/lion/NikolaevBS15}, and
+possibly with shortcuts taken for certain vertices \cite{DBLP:journals/cor/SegundoT14}, and possibly
+followed by a repair step to improve the colouring \cite{DBLP:conf/walcom/TomitaSHTW10}, or stronger
+bounding rules based upon MaxSAT inference
+\cite{DBLP:conf/ictai/LiFX13,DBLP:conf/lion/LiJX15,DBLP:journals/cor/SegundoNB15}).  Such colourings
+will not give us the required property that vertices in $\mathit{remaining} \cap \mathit{connected}$
+come last (so they are selected first by the reverse branching order). Thus we produce two greedy
+sequential colourings, first considering the non-branching vertices in $\mathit{remaining} \setminus
+\mathit{connected}$, followed by the branching vertices, and concatenate them
+(\lineref{makecolours}). This produces a valid colouring, since we do not merge any colour classes
+between the two stages, although it may use more colours than a single colouring would\footnote{What
+    if we did not guarantee that vertices in $\mathit{remaining} \cap \mathit{connected}$ came last,
+    and just used a conventional colouring with the branching rule?  Suppose we had four vertices in
+    $\mathit{remaining}$, and produced a colouring $[[v_1, v_2], [v_3], [v_4]]$, and suppose that
+    extending $\mathit{solution}$ with $\{ v_1, v_3, v_4 \}$ gives an optimal solution. If $v_4$ was
+    not $\mathit{connected}$ yet, we would not branch on that subtree, and the bound could eliminate
+    branching on $v_3$ and $v_1$, so we would miss the solution. Thus we cannot simply add the
+branching rule without also adapting the combined bound / ordering heuristic.}.
 
@@
 
-\paragraph{Connected, Undirected, 33\% Labelled}
-
-\paragraph{Connected, Undirected, Unlabelled}
-
-?? My gut feeling is that if we have edge labels, the clique model wins, and if we don't, it's
-likely to lose. So maybe I should run some experiments with vertex labels but not edge labels to
-test this.
-
-\paragraph{By family} ?? Break this down more by family, size, etc.
-
-\paragraph{Does connected make instances easier or harder?} We could plot connected vs not connected
-difficulties, and result sizes?
-
 \begin{figure}[p]
@@
 
-\subsection{Parallel Search}
-
-\cite{DBLP:conf/ictai/MinotNS15}
+\cref{figure:connected-cumulative}
 
@@
 
+SIP invariants when very similar graphs (except these are easy).
+
 We haven't discussed partial subgraphs, or connected directed.
@@
 Better instances.
+
+Parallel.
+??
+Stuff on EHPs, how work stealing matters here too \cite{DBLP:journals/jco/BatsynGMP14,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16}
+
+\cite{DBLP:conf/ictai/MinotNS15}
 

### 2016-04-19 paper/paper.tex
Feedback from Christine and Patrick

@@
 and each pair of successive vertices is connected by an edge, i.e.\ $\forall i\in \{1 \ldots k \},
-\{v_{i-1},v_i\}\in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every pair of vertices
+(v_{i-1}, v_i) \in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every pair of vertices
 is connected by a path.
@@
 an undirected graph $G \modularproduct H$ with vertex set $\operatorname{V}(G \modularproduct H) =
-\operatorname{V}(G) \times \operatorname{V}(G)$---to avoid confusing vertices of $G \modularproduct
+\operatorname{V}(G) \times \operatorname{V}(H)$---to avoid confusing vertices of $G \modularproduct
 H$ with vertices of the two original graphs, we call vertices of $G \modularproduct H$
-\emph{matching nodes}, as each vertex $(u, v)$ of $G \modularproduct H$ denotes the matching of $u$
-with $v$. The edges of $G \modularproduct H$ connect matching nodes which denote compatible
+\emph{matching nodes}, as each vertex $(u, u')$ of $G \modularproduct H$ denotes the matching of $u$
+with $u'$. The edges of $G \modularproduct H$ connect matching nodes which denote compatible
 assignments, so two matching nodes $(u, u')$ and  $(v, v')$ are adjacent if $u \neq v$ and $u' \neq
@@
 be mapped to vertices with loops (with the same labels, if appropriate), and vertices without loops
-may not be mapped to vertices with loops.
+must be mapped to vertices without loops.
 
@@
 association graphs; edge labels tighten edge constraints for CP, and make the association graph
-sparser for clique-based approaches.
-
-?? More on AC here? If we think carefully about the size of the domains of the objective variable:
-tightening the constraints doesn't really help unless you've made an assignment, right?
-
-\section{Re-Evaluating the Clique Model}\label{eval1}
+sparser for clique-based approaches. It is worth noting that edge constraints do not help CP
+approaches to do more filtering so long as $\bot$ remains in variable domains: every pair of
+variables $(x_i, x_j)$ having  $D(x_i) \neq \emptyset$ and $\bot \in D(x_j)$ is arc consistent,
+since $\bot$ is a support for any value $u \in D(x_i)$. However, as soon as $\bot$ is removed from
+domains (i.e.\ when the number of variables assigned to $\bot$ has reached the best known bound on
+the size of the MCS), maintaining arc consistency may filter values, and tighter constraints
+increase the opportunities for filtering.
+
+\section{Re-Evaluating the Clique Model for MCS}\label{eval1}
 
@@
 bitset encoding due to San Segundo \textit{et al.}\
-\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the CP
-implementation of Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on
-machines with Intel Xeon E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and
-a timeout of one hour was used.
+\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
+``FC+Bound'' and ``MAC+Bound'' (simply referred to has FC and MAC) CP implementations of Ndiaye and
+Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
+E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
+used.
 
@@
 
-A more conventional CP approach would be to express connectedness as a conventional constraint. For
+A more traditional CP approach would be to express connectedness as a conventional constraint. For
 example, CP(Graph) \cite{DBLP:conf/cp/DoomsDD05} introduces graph domain variables and enforces
@@
 that may be matched (in both graphs) is greater than the size of the largest common subgraph
-previously found. Therefore, we introduce a new filtering algorithm to ensure connectedness) (resp.
+previously found. Therefore, we introduce a new filtering algorithm to ensure connectedness
 consistency for MCCS.  Let us consider two graphs $G$ and $H$, and let $D$ be the current domains
@@
 \Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
-specific branching (Branching), by specific filtering (Filtering), or by combining specific
-branching and filtering (Both). We show only results using MAC for labelled graphs, and FC for
-unlabelled graphs, as the other results are very similar.  On labelled graphs, we observe that
-branching often outperforms filtering, and that combining both is rarely much worse than just doing
-one or the other, and is often much better, even if on average it is slightly slower.  On unlabelled
-graphs, we observe that the three variants have rather similar performance.
+specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
+filtering (Both). We show only results using the best variant for each class, i.e.\ MAC for labelled
+graphs, and FC for unlabelled graphs, as the other results are very similar.  On labelled graphs, we
+observe that branching often outperforms filtering, and that combining both is rarely much worse
+than just doing one or the other, and is often much better, even if on average it is slightly
+slower.  On unlabelled graphs, we observe that the three variants have rather similar performance.
 
@@
 It is not possible to determine connectedness from a raw association graph. However, we can take a
-maximum clique algorithm and mimic the branching strategy if we have access to the underlying graphs
+maximum clique algorithm and mimic the CP branching strategy if we have access to the underlying graphs
 and can determine the ``meaning'' of the association graph vertices.
@@
 in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
-viewed as variables \cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for
-branching at each stage inside a clique algorithm, we would lose completeness. Thus we must adapt
-the bound to take into account restricted branching.
+viewed as variables, without requiring a new bound to be calculated for every iteration
+\cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for branching at
+each stage inside a clique algorithm, we would lose completeness. Thus we must adapt the bound to
+take into account restricted branching.
 
@@
 solution. The colour bound operates as follows: at each entry to the $\FuncSty{search}$ procedure,
-we produce a greedy colouring of the vertices in $\mathit{remaining}$ (\lineref{makecolours}). This
-greedy colouring gives us a list of colour classes, each of which is a list of pairwise non-adjacent
-vertices. The two loops (\twolinesref{outerloop}{innerloop}) then iterate over each colour class,
-from last to first, and then over each vertex in that colour class, again from last to first.
-(Rather than actually using a list of lists and removing items, this process should be implemented
-using a pair of immutable flat arrays. This technique is described elsewhere
-\cite{DBLP:conf/cp/McCreeshP14}, so we do not discuss it here.) Finally, if at any point the number
-of remaining colour classes plus the number of vertices currently present in $\mathit{solution}$ is
-not strictly greater than the size of the incumbent, then we may backtrack immediately
-(\lineref{bound}).
+we produce a greedy colouring of the vertices in $\mathit{remaining}$ (\lineref{makecolours},
+discussed further below). This greedy colouring gives us a list of colour classes, each of which is
+a list of pairwise non-adjacent vertices. The two loops (\twolinesref{outerloop}{innerloop}) then
+iterate over each colour class, from last to first, and then over each vertex in that colour class,
+again from last to first.  (Rather than actually using a list of lists and removing items, this
+process should be implemented using a pair of immutable flat arrays. This technique is described
+elsewhere \cite{DBLP:conf/cp/McCreeshP14}, so we do not discuss it here.) Finally, if at any point
+the number of remaining colour classes plus the number of vertices currently present in
+$\mathit{solution}$ is not strictly greater than the size of the incumbent, then we may backtrack
+immediately (\lineref{bound}).
 

### 2016-04-19 paper/gen-graph-connected-heatmap.tex
Muck around with the graphs a bit, add some FC
More FC data
More gratuitous mucking around with the figures

@@
 %% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
-%% Thu 07 Apr 2016 11:12:14 BST
+%% Tue 19 Apr 2016 13:37:03 AEST
 \tikzset{every node/.append style={font={\scriptsize}}}
@@
 \node[gp node center,rotate=-270] at (5.706,3.991) {Association Runtime (ms)};
-\node[gp node center] at (8.574,1.427) {MAC Both Runtime (ms)};
+\node[gp node center] at (8.574,1.427) {FC Both Runtime (ms)};
 \begin{scope}
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576ff9f7dff9f7dffffffffac88ff9f7d%
-  ffffffff9f7dffac88ffffffff8c72ff8c72ffac88ffac88ffac88ff9f7dff846eff846efd6561fa5e5ffe6862ff7e6c%
-  fe6862f85a5df7585df4505aef4457f04557e73952df2f4ee2324fd9284bd62449d42148d21f47d21f47cf1d44cd1b43%
-  cc1b43d11e46d21f47cc1b43c7173ed01e46ca1940cd1c43cf1d45ce1c44d52349d42248dc2c4cda2a4cde2d4dd22047%
-  d42248d8264ad7254ad7264aa00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ffffffffac88ff9576ffac88ffac88ffac88ffac88ffac88ff9f7dffac88ffffffffac88ffffffffac88ffffffff9f7d%
+  ffffffff9576ff846eff9f7dff9576ffac88ff846eff9576ff7869ff6b63fb605ff7565cf95c5efd6561f95c5ef04757%
+  f04557ec4055ea3d54e73952e93c53de2e4ed8264ad9284bd7254ad21f47d62449d01e45d32048d11e46d22047cf1d45%
+  d52349cc1b42cf1d44d52349cb1a42cf1d44d11e46d42148d9274bdd2d4ddc2b4cde2d4de53751dc2c4cde2d4dd32148%
+  d7254ad52349da294be0304ea00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffac88ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7d%
+  ffac88ffac88ffac88ff9576ff9f7dff9f7dffac88ff9f7dff9576ff9f7dff9576ffffffff9576ffffffff846eff9f7d%
+  ffffffff9576ff846eff846eff9f7dffac88ffffffff9f7dffac88ffffffffac88ffac88ffac88ffac88ffac88ff9f7d%
+  ff9f7dffac88ffac88ffac88ffac88ffac88ffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffffff%
+  ff9f7dff9f7dffac88ffac88ff8c72ffac88ffffffff9f7dffac88ff9576ffac88ff9576ff9f7dffac88ffffffff9576%
+  ff9f7dffffffff9f7dff9576ff9576ffac88ff7869ff6f65ff8c72ff9f7dff7e6cff846eff7367ff8c72ff9f7dffac88%
+  ffac88ff8c72ffac88ff9f7dffac88ff9576ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffff9f7dffffffffffffff9f7dff9576ffac88ff9f7dffac88ffac88ff9576ffac88ffac88ffffff%
+  ff9f7dffac88ffac88ff9f7dffffffff846eff9576ff9f7dff846eff7e6cff7e6cff7367ff846eff7367ff6f65ff6b63%
+  ff8c72ff846eff8c72ff7869ffac88ff846eff9576ff9f7dffac88ffffffff9f7dffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffe83b53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffffff%
+  ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88ffffffffac88%
+  ffffffff9f7dff9f7dff8c72ffffffff9576ff9f7dffffffffac88ff8c72ffac88ff8c72ff846efd6561fc6260fd6561%
+  fa5e5ffa5e5fff7869ff7869ff6f65ff6b63ff9576ff846eff6f65ff7e6cff7e6cff8c72ff9f7dffffffff9f7dffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffe73952ffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffac88ff9f7dffffffff9f7dffffffffac88ff9f7dff9f7dffac88ffac88ffac88ff8c72ff6f65ff9f7dffac88ffac88%
-  ff9f7dff8c72ff9f7dff7e6cff9576ff9576ffffffff9f7dff9f7dffffffffac88ffac88ffac88ffffffff9f7dff9f7d%
-  ff9f7dffac88ffac88ff9f7dffac88ffffffffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%
+  ff9f7dff9576ff7869ff9f7dff9f7dffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
+  ffac88ffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff8c72ffac88ff846eff7869ff8c72ff7869ff7869%
+  f95c5efe6862fc6260f5535bf5535bf5515bf85a5dfa5e5ffa5e5ffb605fff6f65ff7367ff6b63ff7e6cf95c5efc6260%
+  ff846eff9576ff9f7dffffffffffffffac88ff9f7dffffffffffffffffffffffffffffffffac88f04557ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffff9f7dffac88ffac88ff9576ffffffffffffffffffffac88ffffffffffffffffffffac88%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9576ffffffffac88ff8c72ff7e6cff846eff7869%
+  ff9576ff7e6cff846efc6260f95c5efe6862f7565cf7585dfa5e5ff5535bfa5e5ff95c5efa5e5fff6b63ff8c72fa5e5f%
+  fe6862f6545cfb605ffd6561ff6b63ffac88ff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
+  fffffffffffffb605fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dff8c72ff9f7dff9f7dff9f7dff9f7dff8c72%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffac88ff9f7dffffffff8c72%
+  ff8c72ff8c72ff6f65ff7367ff6f65ff6f65fb605ffb605ff7565cf7585df85a5dfe6862fa5e5fff6f65f04757fb605f%
+  fa5e5ffa5e5ffd6561f5515bfa5e5fff7367fb605ffe6862ff7e6cff9576ff9576ffac88ffffffffffffffffffffac88%
+  ffffffffffffffffffffffffffffffffffffffffffff8c72ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffac88ff846e%
+  ffac88ffac88ffffffffffffffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
+  ffffffff9f7dffac88ff9576ff8c72ff846eff846efb605fff7869ff7367ff7367f5535bfd6561f95c5efd6561f95c5e%
+  f85a5df85a5df95c5efb605ffe6862ff6f65fa5e5ff85a5df7565cf85a5dfa5e5ffd6561ff846eff7e6cffac88ffac88%
+  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffff8c72ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88%
+  ffac88ffffffff8c72ff9576ff9576ffffffff8c72ff9576ffffffffffffff8c72ffffffffffffffffffffac88ffffff%
+  ffac88ffac88ffffffffffffffac88ffac88ff9f7dffac88ff8c72ff846eff7869ff7e6cff6f65fa5e5ff6545cf7565c%
+  f95c5ef7565cf95c5ef7565cf7585dfb605ff5515bff6f65ff7869ffac88ff7367fd6561f24a59fa5e5ffe6862ff6b63%
+  ff846eff9576ff9576ff9576ffac88ff9f7dffffffffffffff9576ffffffffac88ffffffffffffffac88ffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffac88ffac88ffac88ffffffffac88ffac88ff9576ffac88ff9576ff9f7dff9576ffac88ffac88%
+  ffac88ffac88ffffffffac88ffffffffffffffac88ff8c72ff8c72ffffffff9576ff9576ff7e6cff6f65fe6862fa5e5f%
+  ff6b63fa5e5ff7585df5535bf7565cf95c5efc6260f95c5eff7869ff7869ff6b63ff6f65fe6862ff846efe6862ff7869%
+  fd6561f85a5dfe6862ff6f65ff8c72ff9576ffac88ffac88ff9f7dffffffffffffff9f7dffac88ffffffffac88ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ff9576ffac88ff9f7dffac88ffffffffac88%
+  ff9576ff9576ffac88ffac88ffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ffac88ff9576ff9576%
+  ff7e6cff7e6cfe6862fd6561fa5e5ff34e5af14958f85a5df7565cfc6260ff7869ff6f65fa5e5fff7e6cff7e6cff7e6c%
+  ff7e6cff8c72ff9576ff6b63ff8c72fa5e5ffd6561ff6f65ff7869ff846eff9576ffac88ffffffffffffff9f7dffffff%
+  ffac88ffffffff9f7dffffffff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffac88%
+  ffac88ffffffff9f7dffac88ffac88ff9576ffffffff8c72ff9f7dffffffffffffffffffff9f7dffac88ffffffff9f7d%
+  ffac88ff9f7dff9576ff9576ff7e6cff6b63ff8c72f6545cf5515bf6545cfa5e5fff6b63f6545cf7565cfb605fff6b63%
+  ff846eff7869ff8c72ff8c72ff8c72ff6f65ff7e6cff7367ff7367ff846eff7367ff7367ff7869ffffffff8c72ffac88%
+  ffac88ffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffac88ffac88ffffff%
+  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88%
+  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ffffffff9f7dffffffffffffffac88ffac88ff9f7dffffff%
+  ff9f7dffac88ffac88ffffffffac88ffac88ff9f7dff9576ff7e6cff7367fc6260ff7367fc6260f95c5ef95c5ef6545c%
+  f85a5dfb605fff6f65fb605fff6b63ff7367ff7e6cff7367ffffffff9f7dff6b63ff7869fe6862ff7869ff9f7dff9576%
+  ff7e6cff8c72ffffffff8c72ffac88ff9f7dffac88ffac88ffac88ff9f7dff9576ffac88ffffffffffffff9f7dffffff%
+  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dff9f7dffffffffac88ff9f7dffffffff9f7d%
+  ffffffff9576ffffffff9f7dffac88ffac88ffac88ff9f7dffac88ff9576ff9576ff9576ff8c72ff7e6cff7367ff6b63%
+  f5515bfa5e5ff85a5df6545cf5535bf7565cff7e6cfc6260ff7869ff9f7dff7e6cff9576ff7e6cff8c72ff8c72ff7367%
+  ff7367ff7367ffac88ff9f7dff9f7dffac88ffac88ffac88ffac88ff9f7dffac88ff846eff9576ffffffffac88ff9f7d%
+  ff8c72ff8c72ffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffac88%
+  ff9f7dffac88ffac88ffac88ffac88ff9f7dffac88ffffffff9576ff8c72ffac88ff9f7dffac88ffac88ffffffff846e%
+  ff9576ff8c72ff7869ff9576fb605ff5535bfb605ff7585dff6b63fd6561ff7367ff7869ff7869ff846eff9f7dff7e6c%
+  ff6f65ff9576ff7367ff8c72fc6260ff7e6cff846eff7e6cff8c72ff9f7dff9576ffffffffac88ffac88ff846eff846e%
+  ff6f65ff9576ffac88ffffffffac88ffffffffffffffffffffffffff9f7dffffffff9f7dffffffffffffffac88ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dff9f7d%
+  ffac88ffac88ffffffff8c72ffac88ffffffffac88ffac88ffffffffac88ffffffff9576ff9f7dffac88ffac88ff9576%
+  ff9f7dffac88ff846eff9f7dff9576ff846eff846eff7e6cff6b63fa5e5ffd6561fd6561fd6561fa5e5ffb605fff7869%
+  ff9576ff9576ff8c72ff8c72fc6260fd6561fc6260ff846eff7869ff7e6cff7e6cff846effac88ff9f7dff9f7dff9576%
+  ffac88ffffffff9f7dff8c72fd6561ff7e6cff846effffffff9576ffac88ff9f7dffffffffffffffffffffac88ffffff%
+  ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ff9f7dff9576ffffff%
+  ffffffff9f7dffffffff7e6cff9576ff9576ff9576ffac88ff9f7dff7869ff7869ff9576ff7367fe6862fc6260ff846e%
+  fc6260fd6561ff7367ff8c72ff9576ff6f65ff8c72ff9f7dffac88ff6f65fe6862ffac88ff9f7dff7869ff6f65ff7e6c%
+  ff9f7dffac88ffffffffac88ffac88ff9f7dffac88ff7869ff7e6cff7e6cff7e6cff9f7dff9576ffac88ff9f7dff9576%
+  ffffffff9f7dff9f7dff8c72ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffffffffffac88ff9576ff9576%
+  ffac88ff9f7dffac88ffac88ff9f7dffac88ff9f7dff846eff7e6cffac88ff846eff8c72ff8c72ff846eff7869ff6f65%
+  ff8c72ff9576ff6f65ff6b63ff6f65ff8c72ff7869ff846eff7e6cff846eff9576ff846eff9576ff9576ff8c72ff7869%
+  ff9f7dff9576ff7e6cff9576ff9f7dff9576ffffffffac88ff8c72ffffffffac88ffac88ff9576ff6f65ff7869ff9f7d%
+  ff9f7dff8c72ffffffff9f7dff8c72ff9f7dff7e6cf85a5df85a5dffac88ffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ff9f7d%
+  ffffffff9f7dffac88ffffffffffffffac88ffffffffffffff8c72ff7e6cff846effac88ff9f7dff8c72ff9f7dff9576%
+  ff846eff846eff846eff846eff8c72ff846eff9576ff6b63ff6f65ff8c72ff7e6cff6f65ff9576ff8c72ff7e6cff846e%
+  ffac88ff846eff9576ff7869ff7e6cff846eff9576ff9f7dff9576ff8c72ffffffffffffffac88ffac88ffac88ffac88%
+  ff9576ffac88fe6862ff9576ff9f7dffffffffffffffac88ff9576ff7869ff9f7dfe6862f6545cfe6862ffffffffac88%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffff%
+  ffac88ffac88ffffffff9f7dff9f7dffffffffffffffac88ff9f7dffac88ffac88ffac88ffac88ffac88ffffffff9f7d%
+  ff8c72ffac88ff8c72ff846eff9f7dff8c72ff7e6cffac88ff9576ff7e6cff7869ff846eff7e6cff7869ff8c72ff6b63%
+  ff7e6cff7367ff7869ff846eff9f7dff9576ff9f7dff8c72ff7e6cff9576ffac88ffac88ff9f7dffac88ffffffffffff%
+  ff9576ff8c72ff7869ffac88ff9576ffac88ff9576ffac88ffac88ff9f7dffffffff8c72ff7e6cfb605fff7367ff7869%
+  f5535bf85a5dff9f7dffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffac88ffac88ff9f7dffac88ff9576ffffffffac88ffac88ffac88ff9f7dffac88%
+  ffac88ff7e6cffffffffffffff7e6cff7e6cff8c72ff7367ff8c72ff7e6cff9576ffac88ff9f7dff8c72ff7e6cff7869%
+  ff7869ff7e6cff7869ff7367ff7869ff7e6cff846eff9576ff9576ff846eff9576ff9f7dff9f7dff9576ff9f7dffffff%
+  ffffffff9f7dff9f7dff9f7dffac88ffac88ffac88ff8c72ff8c72ff7e6cffac88ff9f7dffac88ff9f7dff9f7dffffff%
+  ff9576ff6b63fc6260fd6561ff7367fd6561ff8c72ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ffffffffffffffffffffffffffffffff9f7dffffffff9f7d%
+  ffffffff9f7dff9576ffac88ff846eff9576ff9576ff9f7dffac88ffffffff8c72ff7e6cff9576ff8c72ffac88ff846e%
+  ffac88ff9576ff8c72ffac88ff8c72ff7e6cff9f7dff9f7dff9f7dff9f7dff846eff8c72ff9576ff846effffffff9f7d%
+  ff9576ff7e6cff9f7dffffffffac88ffffffff9f7dff9f7dffffffff9f7dff9f7dff7e6cff8c72ff846eff9f7dff9576%
+  ffffffffffffffac88ffffffffac88ff9576ff6b63fb605fff7869ff7367ff8c72ffac88ffffffffffffffffffffffff%
+  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
+  ffac88ff9f7dffffffff9f7dff9f7dffac88ff9f7dffffffffac88ffac88ffac88ffac88ff9f7dffffffff846eff7869%
+  ff6f65ff846eff8c72ff9576ff7e6cff7e6cff9576ff9576ff8c72ff8c72ff8c72ff9576ff9576ffac88ffac88ff846e%
+  ff8c72ff9f7dffac88ff9576ff846effac88ff8c72ffffffffac88ffac88ffac88ffffffffffffffffffffac88ffffff%
+  ff8c72ff8c72ffffffffac88ffac88ff9f7dff9f7dffffffffac88ffffffff8c72ff9576ff7869ff8c72ffac88ffac88%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
+  ff9f7dff9f7dffffffffac88ffffffffffffffffffff9f7dff8c72ff8c72ff9576ffac88ff8c72ffac88ffffffffac88%
+  ff9f7dff9f7dff9576ffac88ffffffff7869ff9576ff846eff7869ff9576ff7367ff846eff9f7dff9f7dff8c72ffac88%
+  ff9f7dff7869ff9576ff846eff9576ffffffffac88ff9576ff9f7dff9576ffac88ff9f7dffffffffffffffac88ffac88%
+  ffffffffffffffffffff9f7dffac88ff9f7dff8c72ff9576ff9f7dff9f7dffffffffac88ff9f7dffffffffffffffac88%
+  ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9576ff9f7dff9576ffac88ff9576%
+  ffac88ffac88ff9f7dff9576ffac88ff846effac88ffac88ff9f7dffac88ff8c72ff9f7dff846eff8c72ff8c72ff9f7d%
+  ffac88ffac88ff8c72ffac88ff8c72ff9576ff846eff9f7dff9576ff9576ff9576ffffffff8c72ffffffff9576ffffff%
+  ffffffff9576ff9f7dffac88ffffffff9f7dffffffff9f7dff7e6cff9576ff9576ff9f7dffffffffac88ffac88ffac88%
+  ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffffffffffffffffff%
+  ff9f7dff9f7dffac88ffac88ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffff9f7dff9f7dffffffff8c72%
+  ffac88ffffffff9f7dff9f7dffffffff9f7dff9f7dffac88ff9f7dffac88ff846eff9576ff7e6cff846eff9576ff7e6c%
+  ff846eff8c72ff8c72ff9f7dff8c72ffac88ffac88ffac88ffac88ffffffff9576ff9576ffac88ffac88ff846effffff%
+  ff9576ffffffffac88ffac88ffac88ffffffffffffff9f7dff9f7dffffffff9f7dffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ffffffffac88ffffffffac88ffac88ff9f7dff8c72ff7e6cff8c72ff9576ff9576ff8c72ffffffffac88ff9f7dffffff%
+  ff9f7dffffffffffffff9f7dffffffffffffff9f7dff8c72ff846eff9f7dffac88ffac88ff9576ff7869ffac88ff7e6c%
+  ff9576ff9f7dff9576ff8c72ff7e6cff846eff7869ff6b63ff846eff8c72ff8c72ffffffffffffffac88ff9f7dff9f7d%
+  ffffffff9f7dffac88ff9f7dffac88ffac88ffac88ff9576ffffffffac88ffffffffac88ffffffffac88ffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ff9f7dffffffffac88ff9f7dff9f7dff8c72ff7367ffac88ff846eff8c72ffac88%
+  ffac88ffffffff9f7dffac88ff9f7dffffffffac88ffffffff9576ffac88ff9f7dff9f7dffffffffac88ffac88ff9f7d%
+  ffac88ffffffff846eff9576ff9f7dff8c72ff7367ff7367ff7367ff7869fa5e5ffe6862f7585dff6f65ff846eff9576%
+  ffac88ffac88ff8c72ffac88ffffffffac88ff9f7dff9f7dffffffff9576ffac88ffac88ff8c72ff9f7dffac88ffac88%
+  ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dff8c72ff7e6c%
+  ff7e6cff8c72ff7e6cff9576ff846eff9f7dff9f7dff9f7dffffffffffffffac88ffffffffac88ff9576ffffffff9576%
+  ffffffff9576ffac88ff9f7dffac88ff9576ff846eff7e6cff846eff6b63ff7367f7585df6545cfc6260f7585df7565c%
+  fb605ff95c5efe6862ff8c72ff9f7dffac88ffac88ffac88ff9f7dff9f7dffac88ff9576ffac88ff8c72ffffffff9f7d%
+  ffffffff9576ff9f7dffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
-  ffffffffffffff9576ffffffff9576ffffffffac88ffffffffffffff9576ffac88ffac88ff9576ff846eff9576ff9f7d%
-  ffac88ff8c72ffffffffac88ff9576ff9576ff846eff846eff846eff7869ff7e6cff7869ff7e6cff846eff9576ff9f7d%
-  ffac88ff846effffffff9f7dff9576ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffffac88ff8c72ffffffff9f7dff9f7dffffffff9f7dffac88ffffffff9576%
-  ff9576ffffffffac88ffffffff9f7dffac88ff9576ff7869ff9576ff9576ff846eff8c72ff6f65ff7367fd6561ff7e6c%
-  fd6561ff8c72ff846eff7869ff9f7dff846eff9f7dff9576ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffe83b53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ff9f7dff8c72ff8c72ff846eff846eff8c72ff846eff8c72ff9f7dffac88ffac88ffac88ffac88ffac88ffffff%
+  ff9f7dffac88ffffffffac88ff8c72ff7e6cff846effac88ff8c72ff7e6cff7869ff7367fe6862ff6b63fe6862fa5e5f%
+  f7565cf24a59f34d59f5535bf14958f4505af7565cff6f65ff846eff9576ffffffffffffffac88ffac88ffac88ff9576%
+  ff8c72ff9f7dff9f7dff9576ffac88ffffffff8c72ffffffffffffffffffffac88ffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576ff9f7dff8c72ff846eff9576ffac88ffffff%
+  ffffffffffffffffffffac88ffac88ff9f7dff8c72ff9f7dff9576ff9f7dff7869fe6862ff7e6cff9576fd6561ff7e6c%
+  ff6f65fb605ffd6561f7565cfd6561f85a5df24b59fa5e5ffa5e5ff34d59f7585df4505afb605fff846effac88ff9f7d%
+  ff9576ffac88ffac88ffac88ffffffff9f7dff846eff8c72ff9f7dffffffffac88ff9f7dffac88ffffffffffffffffff%
+  ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ff9f7dff9f7d%
+  ffffffffac88ffac88ffac88ffac88ffac88ffffffffac88ff9f7dffffffff846effac88ff7869ff846eff7e6cff8c72%
+  ff6b63fd6561ff846efe6862f95c5efc6260ff7869fa5e5ffb605ff34e5af5535bf5515bff6b63f4505af85a5df5535b%
+  ff6b63ff7367ff8c72ff9f7dff9f7dffffffffffffffffffff9f7dff9f7dff846eff8c72ffffffff9f7dff9f7dff9f7d%
+  ff9576ffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffff%
+  ffac88ffac88ffffffff9f7dff9576ffac88ffffffffac88ffffffffffffffac88ffffffff9f7dff9f7dff9f7dff8c72%
+  ffac88ff9576ff7e6cff7367ff6b63f5515bfa5e5ffd6561f6545cfe6862fe6862ff6b63f85a5dfd6561f5515bf6545c%
+  fb605ffb605ff7585df85a5df7565cfc6260fe6862ff8c72ff9576ff9f7dffffffffffffff9f7dffffffffac88ff9f7d%
+  ff8c72ffffffffffffff9f7dffffffffffffff9576ffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffff9f7dffac88ffffffffac88ffac88ffffffffac88ffffffffac88ff9f7dffffffffffff%
+  ffffffffac88ffffffff9576ff9576ff8c72ff7367fa5e5ffc6260f95c5ef95c5ef95c5ef6545cf7585dff7367fd6561%
+  f7585dfd6561ff6b63fe6862fc6260f5535bff6f65fd6561ff7869ff8c72ff846eff9576ff9576ff9f7dff8c72ff9f7d%
+  ff9f7dff9f7dffac88ffac88ffac88ffffffff9f7dffac88ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffff9f7dffac88ff9f7dffffff%
+  ffac88ffffffffffffffffffff9f7dff9576ff9f7dff9576ff846eff846efd6561ff6b63f7565cf5515bf14958f85a5d%
+  fa5e5ffb605fff7367fc6260ff846eff7869fb605ffd6561fb605ffe6862fc6260ff7869ff6b63f85a5dfe6862ff7869%
+  ffac88ffac88ffffffff9f7dff8c72ffac88ffac88ffffffffac88ffffffff9f7dffac88ffffffffffffffac88ff9f7d%
+  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
+  ffffffffac88ffffffffffffffffffffac88ffac88ff9f7dffffffffac88ffac88ff8c72ff7e6cff6f65ff6b63ff6b63%
+  f6545cfa5e5ff14858f7565cfb605ff85a5dff7367ff7367ff6f65ff6f65ff9f7dff7869ff7367ff7367fd6561fc6260%
+  fe6862fc6260fe6862ff7e6cff9576ff9f7dffac88ffffffffac88ffffffff846effac88ffffffff9576ff8c72ff9f7d%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
+  ffffffffffffff9576ffffffffac88ff9f7dffffffff9f7dffffffffac88ffac88ffffffff9f7dff9576ff9f7dff9f7d%
+  ff9576ff846eff7367f4505afc6260f5535bf7585df4505af5515bf7585dfe6862ff7869ff7e6cff8c72ff846eff9576%
+  ff8c72ff7869fc6260fe6862f7585dfb605fff6b63ff7367ff7367ff8c72ffac88ff9576ffffffff9f7dffac88ff8c72%
+  ffac88ff8c72fe6862ff7869ff846effac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffffffffffffff9576ffffffff9f7d%
+  ffac88ff9576ff7e6cff9576ff846eff7367ff6f65ff6b63f95c5efb605ff4505af7585dfb605ffb605fff7367fd6561%
+  ff7367ff8c72ff9576ff9f7dff9576ff7367ff7367ff7e6cf7585dff6f65ff7367ff9576ff9f7dff846eff8c72ff846e%
+  ff7869ff9576ff9f7dff8c72ff9f7dff7869f95c5eed4155f85a5dff846effac88ff9f7dffffffffffffffffffffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffffff%
+  ff9f7dffac88ffac88ffac88ffac88ffffffff9f7dff9576ff846eff9576ff7e6cff7869ff846eff6f65ff6b63fa5e5f%
+  ff6f65ff846eff7e6cff7869ff7e6cff9f7dff9f7dff8c72ff9576ff7367ff846eff7869ff7869ff846eff7e6cff9576%
+  ffac88ff8c72ff6b63ff7869ff7e6cfd6561ff7e6cff8c72ff9576ff9576fb605feb3e54ee4156fd6561ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
+  ffac88ffffffff9f7dffffffff8c72ffac88ffac88ffffffffffffff8c72ff8c72ff8c72ff8c72ff8c72ff8c72ff846e%
+  ff7367ff6f65ff7869fd6561ff6f65ff7869ff8c72ffac88ff7e6cffac88ff9576ff9f7dff8c72ff8c72ff9576ff846e%
+  ff7869ff7e6cff8c72ff8c72ff9f7dff8c72ffffffff7e6cfe6862fc6260ff7869ff846effac88ff7869ff9f7df5535b%
+  f85a5dff6f65ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
+  ffffffffffffffffffffac88ff9f7dffac88ffac88ffffffffffffffac88ffac88ff9f7dffffffffffffff9f7dff9576%
+  ff8c72ff6f65ff7869ff6f65ff8c72ff7e6cff846eff7367ff7367ff7e6cff7e6cff9f7dff9576ff9f7dff9576ffac88%
+  ff8c72ff9576ffffffffffffff846effffffff8c72ffac88ff7e6cff8c72ffac88ff9576ff7e6cfd6561fe6862ff7367%
+  ff7367ff9f7dff9576ff846eff8c72ff7869ffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffff9f7dffffffffffffffac88ffac88ff9576ffffffffffffff9f7dffffffff9f7dffffff%
+  ffffffff9f7dffac88ffac88ff9576ff9576ff7e6cff6f65fe6862ff846eff846eff9576ff7869ff9576ff846eff8c72%
+  ff7e6cff8c72ff7869ff846eff7367ff9576ff9f7dff9576ff9f7dffac88ff8c72ff7869ff9f7dff7e6cff9576ff9f7d%
+  ff8c72ff6b63ff7869ff9f7dff846effac88ff8c72ff9f7dff9f7dff9f7dffac88ffac88ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
+  ffac88ffffffffffffffffffffffffffffffff846effffffff9f7dffac88ff9576ff846eff9576ff7367ff7869ff8c72%
+  ffac88ff8c72ff9f7dff9576ff8c72ff9f7dff7e6cfd6561ff7869ff8c72ff846eff846eff9576ff9f7dffac88ffffff%
+  ff9576ff9f7dffffffffac88ff8c72ff9576ff9f7dff7e6cffac88ff7869ff9f7dffac88ffac88ff9f7dffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88%
+  ffffffff9f7dffac88ffac88ff9576ffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffac88ff8c72%
+  ff9f7dff846eff9576ff9576ff9576ff8c72ffac88ff9576ff9f7dff8c72ff8c72ff846eff8c72ff9f7dff846eff9f7d%
+  ff9576ffffffff7869ff9f7dffac88ff9f7dff7e6cff9f7dff9f7dff6b63ff9576ff9576ffffffff9f7dffffffff9576%
+  ff9f7dff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffffffffffffffff9576ff9576ff9576ff8c72ffac88ffac88ff9576ffffffff8c72%
+  ff9576ff8c72ffffffff9f7dff8c72ff9576ff9576ff9f7dffac88ff9576ff9f7dff9f7dff9f7dff6f65ff846eff9f7d%
+  ff9f7dff9576ff9f7dffffffffac88ff9576ff9576ffffffffffffffac88ff9f7dff7869ff846eff846eff9576ff846e%
+  ffffffff8c72ff9f7dff9576ffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9576ffac88ffac88ff9f7dff9576ff8c72ff9576%
+  ff8c72ff9f7dff7e6cffac88ff9576ff9f7dffac88ff9f7dff9f7dff9f7dffac88ff9f7dffac88ffac88ffac88ff9f7d%
+  ff9f7dff8c72ffffffff846effac88ff9576ff8c72ff9f7dffac88ffffffff9576ff9f7dffac88ff9f7dff9f7dff9f7d%
+  ff9f7dff8c72ff7869ff7e6cff7869ff9576ff8c72ffffffffac88ff9f7dffffffffffffffac88ffffffffac88ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dff9f7d%
+  ff9f7dff9f7dff8c72ffac88ff9f7dff7869fb605fff846eff9576ff9f7dffac88ffffffffac88ffffffffffffffac88%
+  ffac88ffffffff9576ff9576ff8c72ff9f7dff8c72ff8c72ff9f7dff9f7dffac88ffac88ffac88ff9f7dffffffff9f7d%
+  ffac88ffac88ff9f7dffac88ff9f7dff9576ff7e6cff7869ff9576ff8c72ff7e6cff8c72ffffffffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffff9f7dffac88ff9f7dff9f7dffffffff9576ff9576ffac88ff7e6cff7367ff9f7dffffffffffffff9576%
+  ffac88ffac88ffffffff9576ffffffffffffff9f7dff9f7dffffffffac88ffffffff9f7dff9576ffac88ff9f7dffffff%
+  ffac88ffac88ff9f7dffac88ffffffffffffff9576ff8c72ffffffff9576ffffffff7869ff8c72ff9f7dff8c72ffac88%
+  ffffffff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffff9f7dff7e6cff9f7dff846eff9f7dff9f7dff9576ff846eff9576%
+  ff8c72ff9f7dffac88ffffffff9f7dff9576ffffffffac88ffac88ffac88ffac88ffac88ffffffff9576ff9f7dff9f7d%
+  ff9f7dff9f7dffac88ffac88ffac88ff8c72ffac88ff9f7dff9f7dffffffff9576ffffffff9f7dff8c72ff9f7dff846e%
+  ffac88ffffffff9f7dff9576ffac88ff9f7dffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9f7dffac88%
+  ffac88ff9576ff9576ff9576ff9f7dff9576ff9f7dffffffff9f7dffffffffffffffffffffffffff9f7dffac88ffac88%
+  ff9576ffac88ffffffff9f7dff8c72ffffffff9f7dffac88ff9f7dff9f7dffac88ffac88ffffffff9576ffffffffffff%
+  ffac88ffac88ff9f7dff9f7dffffffffac88ff9f7dffac88ffac88ff9576ffffffffffffffffffffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ff9f7dffffffff9576ff7e6cff9f7dff9576ffffffffffffff9f7dff9576ffffffffac88ffac88ffac88ffffff%
+  ffffffff9f7dff9f7dffac88ffac88ffac88ff8c72ff9f7dffac88ff9f7dff9576ffac88ff9576ff9576ffac88ff7e6c%
+  ff9f7dff8c72ff9f7dff7e6cff9576ffac88ffffffff7869ff9f7dffac88ffffffffac88ffac88ffac88ffac88ffffff%
+  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7dffac88ff9f7dffac88ffffffffffffffffffffac88%
+  ffffffff9f7dffac88ffac88ff9f7dffac88ffac88ff9576ffac88ffac88ff9576ff9576ffffffff8c72ff7e6cff846e%
+  ff8c72ff7e6cff9576ffac88ff9f7dff7869ff8c72ff9f7dff846eff8c72ff9576ff9f7dff8c72ff9f7dffac88ffffff%
+  ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffffff9f7dffffffffac88ffac88%
+  ff9f7dffac88ffffffff9f7dffffffffac88ff9f7dffac88ff9f7dffac88ffffffff9576ff9576ffac88ff8c72ff846e%
+  ff846eff7e6cff846eff846eff7367ff846eff7e6cff7869ff846effac88ff8c72ff7869ff6f65ff8c72ff7e6cff7869%
+  ff8c72ff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88%
+  ffac88ffffffffffffff9f7dffffffffac88ffffffff9576ffac88ffffffffac88ff9576ffac88ff9576ff7e6cff8c72%
+  ff8c72ff9576ff846efe6862ff7e6cfd6561fb605ff95c5efe6862fe6862fc6260ff6f65ff6f65ff8c72ff7869ff846e%
+  ff7e6cff7869ff7e6cff7869ffac88ffac88ffac88ff9576ffac88ffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffac88ff9f7d%
+  ff8c72ff9576ff9f7dff7e6cff9f7dff846eff7367fd6561ff7869f7585df34d59f5515bf14958f34e5af95c5eff6f65%
+  f7585dff7367ff9f7dff846eff9576ffac88ff846eff7367ff8c72ff9f7dffffffffac88ffac88ffffffffffffffac88%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffff%
+  ffac88ffac88ff9f7dffffffff9576ff846eff8c72ff6b63ff7e6cff846efa5e5ffb605ffa5e5ff5515bf5535bf5515b%
+  f14858f4505af5515bf95c5ef7585df7565cfe6862ff9576ff7869ff7e6cff9f7dff9f7dff9576ffac88ffac88ffffff%
+  ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffff9f7dffac88ff9f7dff9576ff9f7dff9576ff8c72ff6f65ff6b63fa5e5ff7565cfa5e5f%
+  f24a59f24b59ef4457f34e5af14958f7585df24b59fe6862f85a5dfe6862f85a5dff6b63ff7e6cff8c72ff9576ffac88%
+  ffac88ff9576ff9f7dff9f7dff7367ff8c72ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffac88ffffffffffffff9576ffac88ff9f7dff9576ffac88ff7e6cff9576ff846e%
+  fc6260f95c5ef5535bf5535bf24b59f5515bf4505af34d59f04557f5535bfa5e5ffc6260ff6b63fd6561ff6b63ff6b63%
+  ff7869ff8c72ff9576ff8c72ff8c72ff8c72ff9576ff9f7dff846eff8c72ffac88ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7dff8c72%
+  ff8c72ff8c72ff6b63ff6b63fd6561f7585df7565cf7585df5515bf85a5df6545cf85a5df7585dfe6862f5535bff7367%
+  fe6862fe6862ff7869ff7869ff9576ff846eff7869ff7367ff6b63ff7367ff7e6cff6b63ff6f65ff846effffffff9f7d%
+  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ff9f7dff9f7dff8c72ff7e6cff6f65ff846eff6f65f85a5df4505af5515bf24a59f5515bf95c5ef95c5ef7585dfa5e5f%
+  fb605ff95c5efc6260ff7367ff7367ff6f65ff7869ff6f65ff8c72ff846efa5e5fff7869f85a5dfd6561f6545cfa5e5f%
+  fe6862ff8c72ff7869ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88%
+  ffffffff9f7dffac88ff9f7dffac88ff846eff8c72ff9576ff7e6cff8c72fd6561fa5e5ff4505af7565cf4505af6545c%
+  f5535bf85a5df7565cff7869ff7869ff6f65ff6b63ff7367ff9576ff846eff7e6cff7869ff9576ff9576ff7367ff846e%
+  fa5e5ff85a5dfa5e5ff7585dff6f65ff8c72ff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffff9f7dffffffffffffff9576ff9576ff846eff8c72fe6862fe6862ff7367fb605ff34e5a%
+  f34e5af5535bfc6260f7585dfb605ffd6561f95c5efd6561ff7869fc6260ff8c72ff846eff846eff8c72ff846efe6862%
+  fa5e5fff7e6cff8c72fe6862ff6b63ff7367fb605ff7585dff6f65fc6260ff846effffffff9f7dffac88ffffffffffff%
+  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dff9576ff8c72ff846eff8c72%
+  ff7869fa5e5ffb605ff95c5efb605ff6545cf7565cf85a5dfa5e5ffb605ffc6260ff6b63ff7e6cff7e6cff7e6cffac88%
+  ff7e6cff9576ff7e6cff7e6cff8c72ff8c72ff846eff7367ff7869ff8c72ff7e6cff7869ff846eff7869ffac88ff8c72%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffffffffac88ff7e6c%
+  ff9f7dff8c72ff7367ff6b63ff7e6cff7e6cff7367fd6561fe6862ff7367fe6862fa5e5ff85a5dfc6260ff7869ff7e6c%
+  ff7e6cff7367ff9576ff8c72ff6b63ff7e6cfc6260ff6b63ff6b63fd6561ff6f65ff7869ff6f65ff9f7dfa5e5fff846e%
+  ff8c72ff9576ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
+  ffac88ff9576ff8c72ffac88ff846effac88ff8c72ff9576fb605fff7e6cfe6862fe6862ff7367ff6f65f95c5eff7367%
+  fb605fff6b63fe6862fd6561ff7367ff846eff846eff7367ff9576ff8c72fd6561ff6f65ff8c72fc6260ff7869ff7367%
+  ff8c72ff846eff6f65ffac88ffac88ff846effac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffff8c72ff9576ff8c72ff9f7dff7367ff9f7dff846eff846eff9576ff846eff9576ffac88%
+  ff6b63fe6862ff6f65ff8c72fc6260ff6f65fc6260ff7367ff846eff8c72ff846eff7e6cff7e6cfe6862ff8c72ff6f65%
+  ff6f65fd6561fd6561ff6b63ff6b63ff7367ff7e6cff9576ff9576ff9f7dff9576ffac88ffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ff8c72ff9576ffac88ff846eff7367ff6f65ff8c72%
+  ff7e6cff9576ff9576ff7869ff6f65ff6f65ff8c72ff7e6cff6f65ff9576ff7e6cff9f7dff7e6cff8c72ff8c72ff8c72%
+  ff7367ff7869ff846eff7869ff846efc6260fc6260fc6260ff6b63ff7367ff8c72ff8c72ff9576ff9f7dffac88ffac88%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9576ff8c72%
+  ff7e6cff846eff6f65ff8c72ff846eff7e6cff7e6cff846eff9576ff9f7dff9576ff7367ff846eff9576ffac88ffffff%
+  ff8c72ff7367ff8c72ff8c72ff7e6cff7367ff7367ff7367fe6862ff9576ff7367ff9576ff846eff8c72ff9576ffac88%
+  ff8c72ffac88ff9f7dffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ff846eff9576ffac88ff9576ff9576ff846eff846eff7e6cff846eff9576ff8c72ff8c72ff9f7d%
+  ff8c72ff8c72ff9f7dff8c72ffac88ff7869ff7e6cff846eff8c72ff6b63fd6561fb605ffc6260ff7e6cff7e6cff8c72%
+  ff7e6cff7869ff7e6cff9f7dff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffff846eff9f7dff7869ff8c72ff6f65ff6f65fd6561ff9576%
+  ff7e6cff6f65ff7e6cff8c72ff8c72ffac88ffac88ffffffff9576ff9576ff9576ff8c72ff7869ff7869ff8c72fa5e5f%
+  ff7367ff7367ff8c72ff846eff9576ff9f7dffac88ffac88ff9f7dff9f7dffac88ffffffffffffffffffffac88ffac88%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffffff%
+  ff9576ff6f65fb605fff6b63ff6f65ff7367ff8c72ff846eff9f7dff9f7dffac88ff9576ffac88ff9f7dffac88ffac88%
+  ff9f7dff9576ff7e6cff9576ff7367ff8c72ff9f7dff8c72ff9f7dff9576ffffffffac88ffac88ffac88ffffffff9f7d%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
+  ffffffff9f7dff9576ff9576ffac88ffac88ff7869ff846eff7869ffffffff846effac88ff9576ff9f7dffac88ff9f7d%
+  ffffffffac88ffffffff8c72ffac88ff9576ff9f7dff9f7dffffffff9576ff8c72ffffffff9576ff9576ffac88ffac88%
+  ff9f7dff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffff9f7dff846eff8c72ff8c72ff846eff9f7dff8c72ff9f7dff9f7d%
+  ff9576ffffffff8c72ffac88ffffffff9f7dffffffffac88ffac88ff9f7dffac88ffffffffac88ff9576ff7e6cffffff%
+  ff846eff9f7dffffffffffffffffffff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ffffffff9f7d%
+  ff9576ff9f7dff7e6cf95c5eff7e6cff7e6cff7367ff846eff9f7dff9f7dffffffffac88ffffffff9f7dffac88ffac88%
+  ffffffff9f7dffffffffac88ff9f7dffffffff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffac88ffac88ffac88ff846eff7e6cf85a5dfc6260ff846eff7367ff7367ffac88ff9576ffac88ffffff%
+  ffffffffac88ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dff846eff9f7d%
+  ff9576ffffffff9f7dff846eff6f65ff9576ff9f7dff9f7dff9576ffffffff8c72ffffffffac88ffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9576%
+  ff846eff846eff8c72ff7e6cfb605fff7e6cfc6260ff7367fe6862ff7e6cff7e6cff7367ff8c72ff7e6cff9576ff8c72%
+  ffac88ff9f7dffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffff9f7dff9f7dffffffff9f7dff8c72ff6b63fe6862fe6862f95c5ef85a5dfb605ff85a5df24b59f85a5df7565c%
+  ff6f65ff6f65ff7869ff6f65ff9f7dff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffac88ffffffffffffff9f7dff8c72ff9576ff9f7dff846efd6561f6545cf5515bec3f55ef4356ee4156%
+  e33550e83a53ef4356f5535bf04757f34d59f5515bf5535bfb605ffc6260ff7e6cff846eff8c72ffac88ffac88ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ff8c72ff9f7dff9576ff6b63fe6862fd6561f4505a%
+  f34d59f14858ee4256e63852ee4156ec3f55ed4155f04757ee4256f14858ee4156f24a59ee4156f6545cfc6260ff6f65%
+  ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88ff9576ff9f7dffac88ff7e6cff7869%
+  ff7869ff6b63ff6f65fc6260f7565cf14958f5535bf6545cf24b59ef4457f6545cf04757f14858f5515bef4356f4505a%
+  f24b59f6545cf34d59ff6f65ff846effac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
+  ff846eff7869ff846efe6862f04757f85a5dfc6260f24a59f24b59f24b59f14858e93c53ee4256f6545cef4457ef4356%
+  f24a59ef4356ea3d54ea3d54e93c53e73952ee4256f7565cff6f65ff7367ffac88ffffffffac88ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffac88ff8c72ff846eff846eff7e6cff7367fa5e5ff7585dfe6862ff6b63ff7367fb605fff7367f7565c%
+  f7565cf6545cf24b59f7585df7565cf5535bf7565cf7585df85a5df5535bf85a5dff846eff9f7dff9f7dffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffff7e6cffac88ff7e6cffffffff9576ff7e6cff7e6c%
+  ff6f65ff6b63ff7869ff7869fc6260fe6862fa5e5ffc6260f95c5efa5e5ff5535bfb605ffd6561ff846eff9576ff9576%
+  ff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dff7869%
+  ff9576ff6b63fb605ff14958f4505aff7869fe6862fb605fff6b63f95c5eff6f65fe6862fc6260fb605ff95c5eff6b63%
+  ff7e6cff7e6cff9f7dff9576ff9f7dffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffac88ffffffff9576ffac88ffffffff9576ff9576ffac88ffffffff9f7dffffffffffffffac88ffffffff9f7d%
+  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffac88ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88%
-  ffac88ffffffffac88ffffffff846eff9f7dffffffffac88ff9576ffac88ff9f7dff8c72ff9576ff7e6cff7367f95c5e%
-  fb605ffa5e5ffb605fff7367ff7367fc6260ff7869ff7367ff7869ff7e6cff7367ff9576ff9f7dff9f7dffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffe73952ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff846eff9f7dff7e6cffffffff9f7dffffffffffffffac88ffffffffac88%
-  ff9576ffffffffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff9f7dffac88ff8c72ff7869ff8c72ff7e6c%
-  ff7869fd6561f95c5ef95c5ef7565cf7585df5515bf14958fa5e5ff85a5dfb605fff6f65ff7367ff6b63f95c5efb605f%
-  ff8c72ff8c72ffac88ffffffffac88ffffffff9f7dffffffffffffffffffffffffffac88fffffff04557ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9576ffac88ffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffff9576ff9f7dff7e6cff8c72%
-  ffac88ff7e6cff6f65ff6f65ff7869ff7367f6545cfa5e5ff7585df5535bf24b59f85a5df5535bfc6260ff7e6cfc6260%
-  f85a5df95c5ef6545cff6f65ff6f65ff9f7dff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffb605fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7d%
-  ff9f7dff9576ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ff9576ffac88ffffffff9576ffffffff8c72%
-  ff9f7dff9576ff846effac88ff8c72ff846eff7367f7585dff6b63f7585df85a5df24a59fb605fff6b63f6545cf24b59%
-  f5535bf85a5df85a5df5535bf7585dff6b63f7565cff7367ff7e6cff9f7dff9576ffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffff8c72ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ff8c72ff9576ff9f7dffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88%
-  ff9f7dffac88ffac88ffffffff9576ff8c72ff8c72ff9f7dff7e6cff7e6cf95c5eff7869ff6b63f7565cf5515bfe6862%
-  fc6260f5515bf7585df95c5ef7565cfa5e5ff85a5dfd6561f5515bf7585df7565cfd6561ff7e6cff8c72ff9f7dffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffff8c72ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff8c72ff9f7dff9576ff9f7dffac88ffac88ffffff%
-  ff9f7dffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dff9f7dffac88ff9f7dff9f7dff7367ff7367fd6561f7565c%
-  fe6862f85a5df5515bf7565cf85a5df14958f5535bf85a5dfa5e5fff846eff6b63ff7e6cf24b59fa5e5ff85a5dfd6561%
-  ff9576ff9576ff8c72ff9576ff9f7dffac88ffffffff9f7dffac88ffac88ffffffffffffffac88ffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff9576%
-  ffac88ff9576ffac88ffffffffffffff9576ff9f7dffac88ff9f7dff9f7dff8c72ff8c72ff8c72ff9576ff8c72ff7869%
-  fe6862ff6f65fc6260fa5e5ff7565cf6545cfb605ff5535bf14958ff7e6cfc6260fd6561ff6f65fc6260fe6862ff7869%
-  fe6862f7585dfc6260ff6b63ff846eff9576ff9f7dffac88ffac88ffffffffac88ff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88%
-  ffac88ff8c72ffac88ffac88ffffffffffffffac88ffffffff9f7dffac88ff9576ffffffff9f7dff9f7dff9f7dffffff%
-  ffffffff8c72ff7367ff7367ff8c72ff6f65f34e5af4505af34e5af85a5df6545cfb605ffa5e5ffc6260fb605fff846e%
-  ff6f65ff7e6cff8c72ff7e6cff7367fb605ffc6260ff6f65ff6b63ff9576ff9576ffac88ffffffffac88ffac88ffffff%
-  ffac88ffac88ffac88ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffac88ffac88ff9f7dffffffffffffff9f7dffffffffac88ffffffffffffff8c72ff9f7d%
-  ff9f7dff9576ff9576ff9f7dffac88ff846eff7e6cff8c72ff6f65fc6260f7585df7565cf85a5df4505af7565cf6545c%
-  f95c5eff7869ff7869fe6862ff846eff7367ff7869ff7367ff7367ff7869ff7e6cff6f65ff7869ff9f7dff8c72ffffff%
-  ffac88ffffffff9f7dffffffffffffffffffffffffffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
   ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ff9f7dffac88ffac88ff9f7dff9576ffac88ff9f7dff9576ff9f7dff9576ff9f7dff7367ff9576ff6f65f7565cf7585d%
-  f85a5df6545cf7585df85a5dff7367fc6260fb605ffe6862ff6f65ff9576ff8c72fc6260ff7367ff7e6cff846eff846e%
-  ff7e6cff9576ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ff8c72ffffffffac88ffffffffac88ffac88ffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffff%
-  ffffffff9f7dffac88ffac88ff9576ffac88ffffffffffffff9576ff9576ff9f7dffac88ff846eff846eff9576ff9576%
-  ff7e6cff6b63fd6561f7585df85a5dfb605ff04757f4505afd6561fc6260ff6f65ff7869ff8c72ff7869ff8c72ff6f65%
-  ff8c72fe6862ff9f7dff9576ff9576ffffffff9f7dffffffff9576ffac88ff8c72ff9576ffac88ffac88ffac88ff846e%
-  ff9f7dff9576ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7dff9576ffffffffac88ff9f7dffac88ffac88ffffffff9f7dffac88ff9576ffac88ff9f7dff9576%
-  ffac88ffffffff9f7dff7869ff9576ff7e6cff6f65f85a5dfc6260f34e5af95c5efe6862fc6260ff6f65ff7869ff846e%
-  ff6f65ff6f65ff7e6cff7e6cff7869ff6b63ff7869ff7367ff9576ff8c72ffac88ffac88ffffffff846eff7e6cff7869%
-  ff846effac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffac88ff9576ffac88ffac88ffffffff9f7dffac88ff9f7dffffffffac88ffac88ffac88%
-  ffffffff846effac88ffac88ff9f7dff9576ff8c72ff8c72ff7367fd6561ff846eff6f65fa5e5ffe6862fb605ff7565c%
-  fb605fff6f65ff846eff8c72ff6b63f95c5efc6260ff7e6cff7367ff7e6cff7e6cff846eff9576ffac88ff9576ff9f7d%
-  ff9f7dff9f7dff9f7dff7367ff6f65ff846eff9576ff9576ffffffff9576ffffffffffffffffffffac88ffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576%
-  ff9f7dffac88ffac88ff9576ff9f7dffac88ffac88ff8c72ff9576ff9576ffac88ff846eff9f7dff846eff7e6cff7869%
-  ff6b63fc6260f85a5dfb605ffd6561ff7e6cff7e6cff7869ff9f7dff6b63ff7869ff7e6cff9576ff8c72ff7367ff7367%
-  ff9576ffac88ffffffff9f7dffac88ffac88ff846eff7e6cff7869ff7869ff9f7dff9576ff9f7dffac88ff9576ffac88%
-  ff9f7dffac88ff846effffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
-  ffffffffffffffac88ffffffffffffff9576ffac88ff9576ffac88ff8c72ff9576ff9576ff7e6cff7e6cff846eff7e6c%
-  ff9f7dff9576ff6f65fd6561ff7869ff846ef95c5eff8c72ff7869ff9576ff7e6cff6f65ff7869ff9576ff7367ff9f7d%
-  ff846eff9f7dff7e6cff8c72ff9576ff9576ffffffff9f7dff9576ffffffffac88ff9576ff7869ff846eff7869ffffff%
-  ff7e6cffffffff9f7dff9576ff9f7dff7e6cf85a5df85a5dff9f7dffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ff9f7dffac88ff9576ffac88ffffffffffffffac88ffffffffac88ffac88ffac88ffac88ff7e6cff846eff9576ffffff%
-  ffac88ff9f7dff8c72ff9f7dff846eff7869ff8c72ff7367fd6561ff9576ff7e6cff6b63ff7367ff6b63ff8c72ff7869%
-  ff7e6cff8c72ff9576ff846eff7869ff7869ff9576ff9576ff9576ff9576ffac88ffac88ffffffff9f7dffffffff9f7d%
-  ff9f7dff6f65ff7e6cff9f7dffffffffffffffac88ff9f7dff7e6cff9576fd6561f6545cff6b63ffac88ffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ff9f7dffffffffffffffffffffac88ffffffff9f7dff9f7dffffffffffffffac88ffffffffffffff9576%
-  ffac88ff9f7dff7e6cff9f7dff9f7dff9576ff7e6cff9f7dffac88ff8c72ff8c72ff9f7dff7367ff7e6cff6b63ff846e%
-  ff7367fd6561ff6f65ff6f65ff7e6cff9576ff8c72ff8c72ff846eff9576ff9f7dffac88ff9f7dffac88ffffffffffff%
-  ff9576ff846eff7e6cff9576ffac88ff8c72ffffffffac88ff9f7dffac88ffac88ff7e6cfc6260fd6561ff7367f95c5e%
-  f6545cff9576ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ffac88ff9576ffffff%
-  ff8c72ff9f7dffac88ffffffff9f7dff9576ff9576ffac88ff846eff7367ff846eff7869ff7e6cff9576ff9576ff7e6c%
-  ff8c72ff6b63ff7e6cff6f65ff7869ff7e6cff7367ff7367ff8c72ff8c72ff9576ff8c72ff9f7dffac88ff8c72ffffff%
-  ffffffff9f7dff9f7dff9f7dff9f7dffffffff8c72ff8c72ff846eff9f7dff9f7dffac88ffac88ff8c72ffffffff9576%
-  ff6f65fc6260fd6561ff6f65fd6561ff8c72ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88%
-  ffffffffffffff9f7dffffffffac88ffffffff9f7dff9576ff8c72ff9f7dff7e6cff9576ff846eff9f7dff7869ff8c72%
-  ff9576ff846effac88ff9f7dff9f7dff9f7dff846eff846eff9576ff846eff9576ff9576ff9576ff7e6cff9f7dff9f7d%
-  ff8c72ff8c72ffac88ffac88ff9f7dffffffffac88ff9576ffffffff9576ff9f7dff7e6cff846eff846effac88ff9f7d%
-  ffffffffac88ffffffffac88ff9576ff6f65fd6561ff6b63ff7869ff7e6cffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ff9576ffffffff9f7dff9576ff9f7dffffffffffffff9576ffac88ffac88ffac88ff9f7d%
-  ff9576ff846eff846eff6f65ff7e6cff6b63ffac88ff7e6cff8c72ff846effffffff7869ff8c72ff9f7dff8c72ff9f7d%
-  ffac88ff7367ffac88ff9576ff846effac88ff9576ffac88ffac88ff9f7dffffffffffffffffffffac88ffffffffac88%
-  ff846eff9f7dffffffff9f7dff9f7dffac88ffac88ffffffffac88ff8c72ff9576ff846eff7e6cffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dff9f7dff8c72ffffffff9576ff9576%
-  ffac88ff9576ffffffffac88ff9576ff9f7dff9f7dff6b63ff8c72ff7869ff9576ff846eff7869ff9f7dff9f7dff846e%
-  ff9576ff846eff8c72ff846eff9576ff9576ffac88ff8c72ffac88ff9576ff9f7dffac88ffac88ffffffffac88ffac88%
-  ffffffffffffffac88ffac88ff9f7dffac88ff7e6cff9576ffac88ffac88ffac88ff9f7dffffffffffffffffffff9f7d%
-  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88%
-  ffac88ff9f7dff9f7dff9576ff9576ff9576ff9f7dffffffff9f7dff8c72ff8c72ff9f7dff9576ff8c72ff7367ffac88%
-  ff9576ff9f7dff9f7dffffffff8c72ff7e6cff8c72ff9576ff8c72ff9576ff9576ff9576ffac88ffac88ffffffffffff%
-  ff8c72ff9f7dff9576ffffffffffffff9f7dffffffff7e6cff9f7dff7e6cff9f7dffffffffac88ffffffff9f7dff9576%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffac88ffac88ffffffffffffff9f7dffffffff9f7dffffffffffffffac88ffffffff9576ffac88ffac88ff9f7d%
-  ff9576ff9576ff9f7dff9f7dffac88ffac88ff9f7dffffffff8c72ffac88ff9f7dff7367ff9576ff8c72ff9576ff846e%
-  ff7e6cff7e6cff9576ff9576ff9576ff8c72ffac88ffffffffffffffac88ff8c72ff9f7dffac88ff9576ff9576ffac88%
-  ff9f7dffac88ffffffff9f7dffffffffffffffac88ff9576ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffff9576ff8c72ff9576ffac88ff9f7dff8c72%
-  ff9576ff8c72ff8c72ff9576ff9f7dffac88ffac88ff9576ff7e6cffffffff8c72ff9576ff9f7dffac88ff846eff9576%
-  ff7e6cff9576ffac88ff7869ff8c72ff7367ff7e6cff7869ff6f65ff9576ff8c72ffffffffffffffac88ff9576ffac88%
-  ffac88ffac88ff9576ffac88ffffffff9f7dff9576ffffffffac88ffffffffac88ffffffffac88ffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ff9f7d%
-  ff8c72ff7e6cff9576ffac88ff9f7dff9576ff9576ff9576ff9f7dff9f7dff9576ffffffffac88ff9f7dffac88ff9f7d%
-  ffac88ff8c72ff9f7dffffffff9f7dff8c72ff7e6cff6b63ff846efc6260fc6260fb605ff95c5efd6561ff8c72ff9f7d%
-  ff9f7dff8c72ff9f7dffffffffffffff9576ff9f7dffffffff9f7dffac88ffac88ff9576ff8c72ffffffff9f7dff9f7d%
-  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffff9576ff9576ff8c72ff7e6cffac88ff8c72ff9576ff846eff7e6cff9576ff846eff9f7dff9f7d%
-  ffffffff9f7dffffffff9f7dff8c72ff9f7dff9576ff8c72ff8c72ff846efb605ff95c5ef7585df85a5df5515bf85a5d%
-  fb605ff6545cfe6862ff846eff9f7dffac88ff9f7dffffffff9f7dff9576ff9f7dff9f7dff8c72ffffffffac88ffac88%
-  ff9f7dff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffac88ffffffffac88ff9f7dff7367ff7367ff8c72ff846effffffffac88ff9576%
-  ff7e6cff9576ff9f7dffffffffffffff7869ffac88ff9f7dff9f7dff846eff7367ff846eff7e6cfd6561f7585df95c5e%
-  fa5e5ff5535bf04557f34d59f14958f24b59f5515bff6b63ff7e6cff9f7dffffffffffffff9f7dffffffff9576ff8c72%
-  ffac88ff846eff9f7dffffffffac88ff9576ffac88ffffffffffffffac88ffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ff9f7dff7869%
-  ff9f7dffac88ffac88ff846eff9576ff9f7dffac88ff8c72ff9576ffac88ff8c72ff7e6cff846eff7367ff7e6cff7367%
-  ff7367ff6b63fa5e5ff7565cf95c5efa5e5ff34e5af4505af95c5ef24a59f5515bf4505afc6260ff8c72ffac88ff9576%
-  ff9576ffac88ffffffffac88ff9f7dff846eff9576ff9576ffffffffac88ff9f7dffac88ffffffffffffffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffac88ff9576ffac88ffac88ffffffffac88ff9f7dff8c72ff9576ff9f7dff9f7dff9576ff8c72ff7e6c%
-  ff846eff6f65ff6b63ff7367ff6b63fe6862fc6260f85a5df85a5df6545cf4505af4505af7585df5535bf4505af4505a%
-  fc6260ff7e6cffac88ff9576ff9f7dffffffffffffff9f7dffac88ff8c72ff8c72ff9f7dff9f7dff9f7dff9f7dff9f7d%
-  ff9f7dffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffff9f7dffffffffac88ffac88ffffffffffffff9f7dffffffffffffffffffff9f7dff9576ff8c72%
-  ff9f7dff9f7dff9576ff846eff8c72ff6b63f85a5df95c5ef7585dff6b63fa5e5ffd6561fb605ff6545cf6545cf34e5a%
-  f7565cf4505af5515bfb605ff4505afb605fff7869ff8c72ff9f7dffac88ffffffffac88ffac88ffac88ff9f7dff9f7d%
-  ff9f7dffffffff9f7dffffffffffffff9576ffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffffffffac88ffffff%
-  ff9f7dffac88ffac88ffac88ff9f7dff9576ff846eff6f65fe6862ff7367fb605ff7585df95c5efc6260f6545cfe6862%
-  f6545cf95c5efc6260f95c5efb605ff5515bf7585dff6f65ff7367ff8c72ff7e6cff9f7dff9576ff9f7dff9f7dff8c72%
-  ff9f7dff9f7dffffffff9f7dffffffffac88ff9f7dffac88ffffffff9f7dffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7d%
-  ffffffffac88ff9f7dff9f7dffffffffac88ffffffffac88ff846eff9f7dff8c72ff7e6cfe6862f95c5ef7565cf14958%
-  f4505afd6561fa5e5ff7585dfe6862ff7367ff6f65f7585dfb605fff6b63f7565cff6b63fa5e5ffa5e5ffc6260ff846e%
-  ffac88ffffffffffffff8c72ff9576ffac88ffffffffac88ffffffffffffff9576ffffffffffffffffffff9f7dff9f7d%
-  ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ff9f7dff9576ff846eff9576ff846e%
-  f85a5dff6b63f7565cf95c5ef4505af6545cf5535bff6b63fe6862ff6b63ff7e6cfe6862ff6b63ff6b63fe6862fb605f%
-  f95c5eff6b63fe6862ff7e6cff846effffffffffffff9f7dffffffff7e6cffffffffffffff9576ff846effac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7dffac88ffffffffac88ff8c72ff9f7d%
-  ff9f7dff9f7dff9f7dff7e6cfe6862fd6561f7565cf85a5df34d59f14958f95c5efa5e5ffe6862fd6561ff7367ff7e6c%
-  ff7e6cff7e6cfb605ffd6561f6545cf85a5dff6f65ff6f65ff7e6cff9f7dff9576ffac88ff9f7dffac88ff8c72ffac88%
-  ff7e6cff6b63ff6f65ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffffffff9f7dff9f7d%
-  ffac88ffffffff9576ff9576ff9576ff9f7dff7869ff7e6cff7e6cfb605ff85a5dfa5e5ff7565cf5515bf95c5efc6260%
-  ff6b63fe6862ff7e6cff7e6cff846eff9576fd6561ff6b63f95c5eff6b63ff6f65ffac88ff846eff8c72ff846eff7869%
-  ff9576ff9576ff8c72ff9f7dff7367f7585ded4155f95c5eff9576ff9f7dff9f7dffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
-  ffffffffffffffac88ffac88ffac88ffffffff9576ffac88ff9576ffac88ff8c72ffac88ff846eff6f65ff7e6cfe6862%
-  fe6862fe6862ff7367fb605fff7869ff846eff9576ff846eff9576ff846eff7869ff6b63ff7869ff7367ff8c72ff9576%
-  ff8c72ff6f65ff7869ff7e6cfd6561ff7e6cff846eff846eff8c72fa5e5fed4155eb3e54ff7367ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffffffff9576ffac88ff9f7dffac88ffac88ff9f7dff9f7dffac88ff9f7dff9f7dff7869%
-  ff7e6cff7e6cff7367ff7869fc6260fb605fff7367ff9576ff7869ffac88ff9576ff8c72ff8c72ff8c72ff846eff8c72%
-  ff6f65ff7869ff9576ff846effac88ff9576ff846eff6b63fa5e5fff7869ff8c72ff9f7dff7e6cff7e6cf7585df7585d%
-  ff7869ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9576ffac88ffffffffac88%
-  ff9f7dffac88ff9576ff6f65ff7367ff7367fe6862ff846eff8c72ff7869ff6f65ff7869ff9f7dff8c72ff846effac88%
-  ff8c72ff8c72ffac88ffffffff8c72ff9f7dff9576ff9f7dff7e6cff9576ff9f7dff7e6cfe6862fd6561ff7869ff6b63%
-  ff9576ff9576ff846eff8c72ff7e6cff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffffffffffac88ff9576%
-  ffffffff9576ffffffffffffff8c72ffffffff9576ff9576ff7e6cff6f65ff6b63ff6f65ff9576ff7e6cff7e6cff9576%
-  ff846eff7e6cff7869ff6f65ff846eff7e6cff8c72ff9f7dffac88ff9f7dff846eff7869ff9576ff8c72ff846eff9f7d%
-  ff7367ff6f65ff8c72ff846effac88ff9576ff9f7dff9576ff9f7dffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9f7dffffffffffffffac88ffffffffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9576ff9576ff7869ff7367%
-  ff9576ff7367ff9576ff9f7dff846eff8c72ff9f7dff6f65ff6b63ff7367ff8c72ff9f7dff846eff9576ffac88ffac88%
-  ff9576ffffffff9f7dff8c72ff9f7dff9f7dff7e6cff9f7dff846eff9576ff9f7dffac88ff9f7dffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffff9f7dff846effac88ffac88ffffffff9f7dff9f7dffac88ff9f7dffffff%
-  ffffffffac88ff7869ffac88ff8c72ff8c72ff7869ffac88ff8c72ff9f7dff846eff7367ff9f7dff846eff8c72ffac88%
-  ff9576ff9576ff846eff9f7dffac88ff9576ff9576ff9576ff7869ff7869ffac88ffac88ff9576ffac88ff9f7dff9576%
-  ff9f7dff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ff9576ff6b63%
-  ffac88ff7e6cffffffff9f7dff7869ffac88ff9f7dff9576ff9576ff9576ffac88ff8c72ff7e6cff9f7dff8c72ff846e%
-  ff9576ff9576ff9576ffac88ffffffff9f7dff9f7dff9f7dffffffff9f7dff9576ff7e6cff846eff846eff7e6cffffff%
-  ff9576ffac88ff9f7dff9576ff9f7dffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffff9f7d%
-  ffffffff9f7dff8c72ff7e6cff9576fe6862ff9576ffffffff9f7dff9576ff9f7dff9576ffac88ffac88ff846effac88%
-  ff9576ffac88ffac88ffac88ff8c72ff8c72ff9f7dff9576ff9f7dffffffff9f7dff9576ffffffff8c72ff9576ffac88%
-  ff9f7dff7869ff7367ff9576ff7e6cff9f7dff9576ff9f7dffac88ffac88ffffffffffffffac88ffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ff9f7dffffffffac88ff9576ff9576ff8c72fc6260ff7367ff6b63ffac88ffac88ffac88ffac88ff9f7d%
-  ff9f7dffac88ffffffff846effffffff9f7dff7e6cff9576ff9576ffac88ff9f7dffffffffac88ff9f7dffffffff9f7d%
-  ffffffff9f7dffffffff846eff9f7dff8c72ff7869ffac88ff7367ff9576ff9576ff9576ff9576ffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffff9f7dffffffff9f7dffffffff9576ffac88ff9f7dffac88ff846eff7e6cff7869%
-  ffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dffac88ffac88ffac88ff846effac88ffffffff9f7dffac88ffffff%
-  ffffffffac88ff9f7dffac88ffac88ff9f7dffac88ff8c72ffffffffffffff846eff9f7dff7367ffffffff846effffff%
-  ffac88ff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff8c72ff9f7dffac88ff846effac88%
-  ff9576ff9576ff846eff6f65ff9f7dff8c72ffac88ff9576ff9f7dffffffffffffff9f7dffac88ffffffffffffff9576%
-  ff846eff9f7dffac88ffac88ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ffac88ff9576ffac88ff9576ff9f7d%
-  ff846effffffff9f7dff9576ff9576ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
-  ff9f7dffac88ffffffff9576ff9576ff9f7dff9576ff9f7dff846eff9f7dffffffff9f7dffac88ffffffff9576ffffff%
-  ffac88ff9f7dff9f7dff9576ffac88ffffffffffffff9576ffffffffac88ff9576ffffffff8c72ffac88ffffffffffff%
-  ffffffff9576ff9576ffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffff9f7dffffffffffffffffffffffffff8c72ff846effac88ff8c72ff9f7dff9f7dff9576ffffff%
-  ffac88ffac88ffac88ff9576ff9f7dff9576ffac88ff9f7dffac88ff9f7dff9f7dff8c72ffac88ff9576ffac88ff9576%
-  ff8c72ff846eff9f7dff7367ff9f7dffffffff9f7dff7e6cffac88ffffffffac88ff9f7dffffffff9f7dffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dff9576%
-  ffac88ff9576ff9f7dffac88ff9f7dffffffff9f7dffac88ffac88ff8c72ffac88ff9576ff9f7dff9576ff7869ff8c72%
-  ff9f7dff846eff9576ff9576ff846eff8c72ff8c72ff8c72ff9f7dff846eff8c72ff9576ffffffff846effffffffffff%
-  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffffac88%
-  ffac88ff9f7dff9f7dffac88ffac88ffac88ffffffffac88ff9576ff9576ff9f7dff9f7dff9f7dff9576ff9576ff846e%
-  ff7e6cff7e6cff7e6cff7e6cff7e6cff7367ff7367ff9576ff9576ffac88ff846eff7869ff7869ff6f65ff9576ff7e6c%
-  ff9576ff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9576ffffffffac88ffffffffac88ffffffff8c72ffac88ff8c72ff9576ff9576ff9f7dff8c72%
-  ff846eff7e6cff7e6cff6f65fd6561ff6b63fb605ffd6561fa5e5fff7367fd6561fc6260ff8c72ff6b63ffac88ff846e%
-  ff7869ff7869ff7367ff9576ff9576ff9f7dffffffff9576ffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffff9f7d%
-  ff8c72ff8c72ff9576ff9f7dff846eff7367ff7869ff7e6cfb605ff7585df24b59f24a59f34d59f34e5afb605ffc6260%
-  fd6561ff8c72ff7e6cff7e6cffac88ffac88ff7e6cff7367ffac88ff9f7dffac88ffac88ffac88ffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ff9576ffac88ff9576ff9576ff9576ff6f65ff846efc6260fc6260fa5e5ffc6260f85a5df5535bef4356%
-  f4505af34e5aef4457f85a5df4505aff6b63ff846eff7e6cff7e6cff9f7dff8c72ff9f7dffffffff9576ff9f7dffffff%
-  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff6b63ff7869ff8c72ff7367fd6561f95c5ef34d59%
-  f5515bf14958f04757f04557f6545cf04757f34e5af5515bff6b63fc6260fb605fff8c72ff7367ff9576ff9f7dffac88%
-  ffac88ff9f7dff7869ff846eff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff9576ffffffff9576ff9f7dff8c72ff8c72ff8c72%
-  ff7869f85a5df5515bf24b59f6545cf24b59f5515bee4256f14958f85a5df5535bf95c5eff7367fb605fff7869ff6f65%
-  ff7367ff9576ff8c72ff8c72ff9576ff9f7dff7e6cff9f7dff846effac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
-  ff8c72ff9f7dff7869ff7e6cfb605ff7585df7585df4505af5515bfa5e5ff24b59f95c5ef34e5af85a5df85a5dff6f65%
-  fc6260ff7869ff7367ff8c72ff846eff6b63ff7e6cff6f65ff6f65ff7e6cff6f65ff6f65ff846eff9f7dffac88ffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffff9f7dff9576ff8c72ff846eff8c72ff6f65fc6260fc6260f4505af34e5aec3f55f14958f95c5ef7565cf85a5d%
-  fc6260fa5e5ffe6862fd6561fe6862ff8c72ff6f65ff7e6cff6f65fb605fff7367fe6862fa5e5ff5535bf85a5dff7367%
-  ff8c72ff7869ff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
-  ffffffffac88ffffffffac88ffffffff8c72ff9576ff9576ff9f7dff7367ff7869fd6561fc6260f24b59f34e5af14958%
-  f24a59f85a5dfa5e5ffc6260ff6b63ff6f65ff6f65ff7869ff8c72ff7869ff846eff7e6cff846eff7e6cff7e6cfc6260%
-  f85a5dfa5e5ffd6561fb605fff7e6cff8c72ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffff9f7dffac88ffffffff9f7dff9f7dff8c72ff846eff6f65ff6b63fa5e5ffe6862%
-  f5515bf34d59f5535bf85a5df7585df7585dfc6260f7585dfc6260fe6862ff7869ff8c72ff8c72ff7e6cff6f65fc6260%
-  fc6260ff9576fe6862ff7367ff6b63ff6f65f85a5dfd6561fd6561ff7367ffac88ffac88ffac88ffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffff846effac88ff7869%
-  ff7e6cfe6862ff9576f95c5efc6260f24b59f34d59f7565cf34e5afa5e5ffa5e5fff7869ff7869ff7e6cffac88ff846e%
-  ff7367ffac88ff7367ff846eff9576ff7367ff6b63ff7e6cff9f7dff7869ff6f65ff7367ffac88ff8c72ff9f7dffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffac88%
-  ff9576ffac88ff8c72ff8c72fd6561ff7869ff6b63ff6b63ff7869fa5e5ffb605ffc6260f85a5dfc6260ff6b63ff7367%
-  ff7869ff7869ff6b63ff9576ff7367ff6b63f95c5eff6f65ff7869f95c5eff6f65ff846eff7869fd6561ff9576ff7869%
-  ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7dff8c72ff9f7dff9576ff9576ff8c72ff846efe6862ff7e6cff7367fa5e5ffa5e5ffd6561fa5e5f%
-  ff7367f85a5dff7367ff6b63fc6260ff7869ff7e6cff7367ff846eff6f65ff7869ff7e6cf95c5eff7e6cff7367ff846e%
-  ff8c72ff7869ff8c72ff8c72ff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff9f7dffffffff9f7dff9576ffac88ff846eff7e6cff846eff7e6cff9f7dff8c72ff846e%
-  fe6862ff7e6cfd6561ff7e6cfc6260fa5e5fff7869ff7869ff7367ff7e6cff8c72ff7367fe6862ff7367fe6862ff8c72%
-  f95c5efb605fff6b63ff7869ff7869ff7869ff846eff9576ffac88ffffffff8c72ffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff846effac88ff8c72ff846eff846eff8c72%
-  ff846eff8c72fd6561ff8c72ff846eff7367ff8c72ff6b63ff6f65ff7e6cff7e6cff8c72ff6b63ff9576ff8c72ff846e%
-  ff6f65ff7367ff846eff7367ff7367f85a5dff6f65fd6561ff7367ff6f65ff9f7dff9576ffac88ffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9f7d%
-  ff846eff9f7dff8c72ff9576ff7869fd6561ff7367ff8c72ff8c72ff8c72ff9576ff846eff7e6cff7367ffac88ffac88%
-  ff9576ff7367ff8c72ff846efd6561ff6b63ff6f65ff7367ff7e6cff8c72ff9576ff7869ff9576ff8c72ffac88ff9f7d%
-  ffac88ff8c72ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ff9f7dff9f7dffac88ff9576ff8c72ff8c72ff846eff6b63ff846eff9576ff846eff8c72%
-  ff9f7dff8c72ff846eff9576ff7e6cff6f65ff9576ff7e6cff6f65fc6260f85a5dfe6862ff7869ff7869ff9576ff846e%
-  ff7e6cff846eff9f7dff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9576ff9f7dff7e6cff846eff7869ff7869ff7367%
-  fb605fff6f65ff7367ff846eff9576ff8c72ffac88ffffffff8c72ff9576ff846eff8c72fc6260ff846eff6f65fe6862%
-  ff7367ff9576ff7869ff9f7dff9f7dffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
-  ff9576ffac88ff9f7dff9f7dfe6862f7585df6545cff7e6cff8c72ff9f7dff9576ffffffff9576ff9576ffffffff9f7d%
-  ff7e6cff9576ff7869ff846eff9576ff9f7dff7869ff9f7dffffffffac88ff9f7dffffffffac88ffac88ffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ff9f7dffac88ffffffffac88ffffffff8c72ff8c72ff8c72ff8c72ff9576ff846eff7869ff7e6cffffffffffffff9576%
-  ffac88ffac88ffffffff8c72ff8c72ffac88ff9f7dffffffff8c72ff9576ffac88ff9f7dff9576ff9f7dffac88ffac88%
-  ffac88ffac88ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff8c72ff9f7dff9f7dff7367ff8c72ff846eff9576%
-  ff9576ff9f7dff9f7dff9f7dff9f7dffffffffffffffffffff9576ffffffffac88ff9f7dff9f7dff7e6cffffffff9576%
-  ff9576ffac88ffac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9576ff8c72ff7869ff7367ff8c72f7585dff7367ff9576ff8c72ff9576ffac88ffac88ffffffffac88ffffffffac88%
-  ffac88ffac88ff9576ffffffff9576ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffac88ff9f7dff846eff7367f85a5df6545cfe6862ff8c72ffac88ffac88ffffff%
-  ffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffac88ff9f7dff8c72ff9f7dff9576%
-  ff7e6cff7869ff846eff8c72ff9f7dffac88ff9576ffac88ffac88ffac88ffac88ffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9576%
-  ff7367ff7e6cfe6862fc6260ff6f65ff6f65ff7869fd6561ff6b63ff7869ff846eff7e6cff9576ff8c72ffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9576ffffffffac88ff846eff7e6cff6b63fd6561f7565cf34e5af85a5df5535bf4505af5515bfb605ffe6862%
-  ff6f65ff7869ff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffac88ff9576ff9576ff846efc6260f6545cf5535bf14958e53651e53751e93c53%
-  ec3f55e63852f14858f24b59f34d59f24a59f85a5dfe6862ff846eff9576ff9f7dff9576ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffac88ff846eff7367fd6561f6545cf14858%
-  eb3e54e93c53ea3d54e73a52e53751f04557ea3d54ea3d54f04557ea3d54f14858f34d59ff7367ff8c72ff8c72ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576ff8c72ff9576ff9f7dff846e%
-  ff7e6cfe6862f95c5ef7585df5535bf34e5aed4155ef4356eb3e54f24b59f34e5aef4457f24b59f14858ef4356ef4356%
-  f7565cff7e6cffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ff9576ff9576ff7869fd6561fb605ff5535bf04557f5515bef4457e93c53ea3d54e63852ea3d54ed4155f04557ee4256%
-  f04757ea3d54e23450e73a52ee4156f7565cff7367ff7e6cffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffff9f7dff9f7dff9576ffffffff7e6cff6b63fe6862f7565cfe6862f34e5afb605ff7585df7585df7565c%
-  f7585de83b53f5535bfa5e5ff6545cf85a5df34e5afb605ff7585dff6f65ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7dff9576ff9576ff846efc6260%
-  fa5e5ffc6260ff6f65ff6f65fa5e5ffa5e5ff7585df7585df7585df85a5df95c5eff7869ff8c72ffffffffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ff8c72fc6260ff6f65f5515bf04557f6545cf5515bff6f65ff6b63f95c5ef95c5efa5e5ffd6561f7585dff7e6cff6b63%
-  ff9f7dffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffac88ff8c72ff9f7dff9576ffac88ffffffffac88ffffffffffffffac88ffffffff9576%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffb3082eda294bd11f46d42248dc2b4c%
-  df304eea3d54f6545cff6b63ff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff900106%
-  bb0e35b3082ebb0e35c3143bc8183fd52349e0314ffb605fffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffbd1036e23450d7254ad8274ad7264a%
+  de2e4edf2f4ee43651ea3d54f6545cfd6561ff7869ff8c72ff9576ffac88ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9b0314%
+  bf1138ba0d34b90d33c3143bc1133acd1b43ce1c44d32048de2d4df14958ff6b63ff9f7dffac88ffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%

### 2016-04-19 paper/paper.tex
More gratuitous mucking around with the figures

@@
 \usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
+\usepackage{placeins}                  % \FloatBarrier
 
@@
     \input{gen-graph-unconnected-heatmap}
-    \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
+    \caption{The cumulative number of MCS instances solved in under a certain time: on the top, 33\%
         labelled graphs, and in the middle, unlabelled and undirected graphs. On the bottom row, an
@@
 
+?? Connected, not strongly connected. No directed graphs.
+
 \subsection{Ensuring Connectedness in CP}\label{mccs-cp}
+
+Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
+specific branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
+set of variables already assigned to values different from $\bot$. The next variable to be assigned
+is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
+$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
+$\bot$. We illustrate this in \cref{figure:restricted}.
 
@@
 \end{figure}
-
-Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
-specific branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
-set of variables already assigned to values different from $\bot$. The next variable to be assigned
-is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
-$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
-$\bot$. We illustrate this in \cref{figure:restricted}.
 
@@
     \input{gen-graph-connected-cp}
-    \caption{A pairwise comparison of different CP techniques. ?? This looks horrible! Make it look
-        better.} \label{figure:connected-cp}
+    \caption{On top, the cumulative number of MCCS instances solved in under a certain time using
+        different CP techniques. Below, instance-by-instance comparisons.}
+        \label{figure:connected-cp}
 \end{figure}
 
-\subsection{Experimental Comparison of CP Models}\label{mccs-cp-eval}
+\subsection{Experimental Comparison of CP Connectedness Techniques}\label{mccs-cp-eval}
 
@@
 specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
-filtering (Both). We show only results using the best variant for each class, i.e.\ MAC for labelled
-graphs, and FC for unlabelled graphs, as the other results are very similar.  On labelled graphs, we
-observe that branching often outperforms filtering, and that combining both is rarely much worse
-than just doing one or the other, and is often much better, even if on average it is slightly
-slower.  On unlabelled graphs, we observe that the three variants have rather similar performance.
-
-\subsection{Ensuring Connectedness in a clique-based approach}\label{mccs-clique}
+filtering (Both). We show only results using the best variant for each class---that is, MAC for
+labelled graphs, and FC for unlabelled graphs (the other results are very similar).  On labelled
+graphs, we see many instances which are solved by branching but not filtering, and vice versa.
+However, combining both is rarely much worse than just doing one or the other, and is often much
+better, even if on average it is slightly slower.  On unlabelled graphs, we observe that the three
+variants have rather similar performance.
+
+\subsection{Ensuring Connectedness in a Clique-Based Approach}\label{mccs-clique}
 
@@
 (\lineref{makecolours}). This produces a valid colouring, since we do not merge any colour classes
-between the two stages, although it may use more colours than a single colouring would\footnote{What
-    if we did not guarantee that vertices in $\mathit{remaining} \cap \mathit{connected}$ came last,
-    and just used a conventional colouring with the branching rule?  Suppose we had four vertices in
-    $\mathit{remaining}$, and produced a colouring $[[v_1, v_2], [v_3], [v_4]]$, and suppose that
-    extending $\mathit{solution}$ with $\{ v_1, v_3, v_4 \}$ gives an optimal solution. If $v_4$ was
-    not $\mathit{connected}$ yet, we would not branch on that subtree, and the bound could eliminate
-    branching on $v_3$ and $v_1$, so we would miss the solution. Thus we cannot simply add the
-branching rule without also adapting the combined bound / ordering heuristic.}.
+between the two stages, although it may use more colours than a single colouring would.
+
+(What if we did not guarantee that vertices in $\mathit{remaining} \cap \mathit{connected}$ came
+last, and just used a conventional colouring with the branching rule?  Suppose we had four vertices
+in $\mathit{remaining}$, and produced a colouring $[[v_1, v_2], [v_3], [v_4]]$, and suppose that
+extending $\mathit{solution}$ with $\{ v_1, v_3, v_4 \}$ gives an optimal solution. If $v_4$ was not
+$\mathit{connected}$ yet, we would not branch on that subtree, and the bound could eliminate
+branching on $v_3$ and $v_1$, so we would miss the solution. Thus we cannot simply add the branching
+rule without also adapting the combined bound / ordering heuristic.)
 
@@
 
-\subsection{Experimental comparison of CP with the Clique-based Approach}\label{mccs-eval}
+\subsection{Experimental Comparison of the CP and Clique Approaches}\label{mccs-eval}
 
@@
         and undirected graphs with up to 35 vertices. On the bottom row, an instance-by-instance
-        comparison of the association and ``MAC both'' approaches, with 33\% labelled graphs on the
+        comparison of the association and CP Both approaches, with 33\% labelled graphs on the
         left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
@@
 
-\cref{figure:connected-cumulative}
+In \cref{figure:connected-cumulative} we compare the clique-based approach to the connected problem
+with both CP Both approaches. The trend is broadly similar to the unconnected problem: for labelled
+graphs, the clique-based approach is the clear winner, but for unlabelled graphs the clique approach
+lags somewhat.
+
+The heatmaps show a more detailed picture. As before, in the unlabelled case, the association
+approach is almost never more than an order of magnitude better, and is often much worse. In the
+labelled case, however, there are now many instances where the CP approach does much better than the
+association approach, despite the association approach remaining much better overall.
+
+?? Can we figure out why? Is it time-to-find or time-to-prove? Assume that this will take up a few
+sentences of space.
 
@@
 
+Adapting clique algorithms: specialised inference, association-aware bound function, .
+
 SIP invariants when very similar graphs (except these are easy).
@@
 
+Better instances.
+
 Possibly portfolios.
-
-Better instances.
 
@@
 
+\FloatBarrier % looks better this way...
 \bibliographystyle{splncs}

### 2016-04-19 paper/paper.tex
Flesh out conclusion a bit

@@
 
-Some immoral perspectives on closely coupling branching with a particular constraint. Whether this
-is useful for other things, like ASP.
-
-Adapting clique algorithms: specialised inference, association-aware bound function, .
-
-SIP invariants when very similar graphs (except these are easy).
+We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
+problems, particularly when edge labels are involved.
+
+We believe there is further scope for tailoring clique algorithms for association graphs.
+Specialised inference, association-aware bound function. Treating the first branch specially, since
+it will eliminate so much of the search space \cite{DBLP:conf/cocoon/SutersAZSSL05}.
+
+For CP models for the connected version of the problem, we saw the benefits of combining
+conventional filtering with a special branching rule. Using a branching rule for correctness, rather
+than simply as an ordering heuristic, is unconventional and does not cleanly fit into the
+abstractions used by toolkits.
+
+We looked only at single-threaded versions of these algorithms. Maximum clique algorithms have been
+extended for thread-parallel search
+\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16}.
+In particular, EHPs \cite{DBLP:journals/topc/McCreeshP15}. On the CP side, decomposition \cite{DBLP:conf/ictai/MinotNS15}.
 
@@
 
+Symmetries. Dynamic.
+
 Better instances.
-
-Possibly portfolios.
-
-Parallel.
-??
-Stuff on EHPs, how work stealing matters here too \cite{DBLP:journals/jco/BatsynGMP14,DBLP:journals/jcc/KoncDTRJ12,DBLP:journals/algorithms/McCreeshP13,DBLP:journals/topc/McCreeshP15,DBLP:journals/cor/SegundoLP16}
-
-\cite{DBLP:conf/ictai/MinotNS15}
 

### 2016-04-19 paper/paper.tex
Despecificify

@@
 Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
-specific branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
+branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
 set of variables already assigned to values different from $\bot$. The next variable to be assigned
@@
 \Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
-specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
+branching (Branch), by filtering (Filter), or by combining branching and
 filtering (Both). We show only results using the best variant for each class---that is, MAC for

### 2016-04-19 paper/heatmapify.rb
Handle headers on first line

@@ -7,7 +7,8 @@ granularity = 100
 xmul = ARGV[3].to_i
 ymul = ARGV[4].to_i
 
-IO.readlines(ARGV[0]).each do | line |
+IO.readlines(ARGV[0]).each_with_index do | line, index |
+    if index == 0 then next end
     words = line.split(' ')
 
     x = words[ARGV[1].to_i].sub('1e10', (3600 / xmul).to_s).to_f * xmul

### 2016-04-19 paper/paper.tex
Handle headers on first line
Wording tweak

@@
 on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
-maximum clique problem. Both approaches are described for non directed and non labelled graphs;
-their extension to directed or labelled graphs is discussed in \cref{extension}.
+maximum clique problem. Both approaches are described for undirected, unlabelled graphs without
+loops; their extension to richer graphs is discussed in \cref{extension}.
 
@@
 domains (i.e.\ when the number of variables assigned to $\bot$ has reached the best known bound on
-the size of the MCS), maintaining arc consistency may filter values, and tighter constraints
+the size of the MCS), maintaining arc consistency may filter values, and then the tighter constraints
 increase the opportunities for filtering.

### 2016-04-19 paper/paper.tex
MCCS + directed

@@
 
-?? Connected, not strongly connected. No directed graphs.
+For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
+undirected). For directed graphs, there is more that one notion of connectivity, and it is not clear
+which should be selected---our approach extends easily to weakly connected directed graphs, but not
+to the strongly connected case.
 
@@
 
-We haven't discussed partial subgraphs, or connected directed.
+We haven't discussed partial or weighted subgraphs, or strongly connected directed.
 

### 2016-04-19 paper/paper.tex
Conclude

@@
 \usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
-\usepackage{placeins}                  % \FloatBarrier
 
@@
 We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
-problems, particularly when edge labels are involved.
-
-We believe there is further scope for tailoring clique algorithms for association graphs.
-Specialised inference, association-aware bound function. Treating the first branch specially, since
-it will eliminate so much of the search space \cite{DBLP:conf/cocoon/SutersAZSSL05}.
-
-For CP models for the connected version of the problem, we saw the benefits of combining
-conventional filtering with a special branching rule. Using a branching rule for correctness, rather
-than simply as an ordering heuristic, is unconventional and does not cleanly fit into the
-abstractions used by toolkits.
+problems, particularly when edge labels are involved.  We believe there is further scope for
+tailoring clique algorithms for association graphs, including specialised inference, a bound
+function which is aware that it is working on an association graph, and better initial vertex
+orderings. Treating the first branch specially may also be beneficial, since the first branch has an
+unusually large effect on the search space with association graphs
+\cite{DBLP:conf/cocoon/SutersAZSSL05}.
+
+For CP models, using a branching rule for correctness, rather than simply as an ordering heuristic,
+is unconventional and does not cleanly fit into the abstractions used by toolkits. However, we saw
+that combining conventional filtering and the special branching rule was beneficial.
 
@@
 extended for thread-parallel search
-\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16}.
-In particular, EHPs \cite{DBLP:journals/topc/McCreeshP15}. On the CP side, decomposition \cite{DBLP:conf/ictai/MinotNS15}.
-
-We haven't discussed partial or weighted subgraphs, or strongly connected directed.
-
-Symmetries. Dynamic.
-
-Better instances.
+\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16},
+and in particular, work stealing strategies designed to eliminate exceptionally hard instances by
+forcing diversity at the top of search \cite{DBLP:journals/topc/McCreeshP15} could be beneficial in
+eliminating some of the rare cases where the clique algorithm is many orders of magnitude worse than
+the CP models. On the CP side, the focus for parallelism has been on decomposition
+\cite{DBLP:conf/ictai/MinotNS15}, rather than fully dynamic work stealing---it would be interesting
+to compare these approaches.
+
+Finally, we intend to investigate larger and more diverse sets of instances, and other variants of
+the problem. We have yet to investigate partial or weighted graphs. Nor have we considered strongly
+connected common subgraphs---this would make the branching approach impossible, and filtering would
+be much more complicated. From the datasets we selected, there appears to be little scope for
+per-instance algorithm selection, but other families of input data could lead to a different
+conclusion.
 
@@
 
-\FloatBarrier % looks better this way...
 \bibliographystyle{splncs}

### 2016-04-20 paper/paper.tex
Gain us some space

@@
 
-\begin{figure}[p]
+\begin{figure}[tb]
     \centering
@@
     \caption{The cumulative number of MCS instances solved in under a certain time: on the top, 33\%
-        labelled graphs, and in the middle, unlabelled and undirected graphs. On the bottom row, an
+        labelled graphs, and then unlabelled and undirected graphs. On the bottom, an
         instance-by-instance comparison of the clique model with the best CP model, with 33\%
@@
 
-The top two plots of \cref{figure:unconnected-cumulative} display the cumulative number of instances
+The two plots on the top of \cref{figure:unconnected-cumulative} display the cumulative number of instances
 solved with respect to time.  When graphs are labelled, the clique-based approach clearly
@@
     \caption{The cumulative number of connected instances solved in under a certain time: on the
-        top, 33\% labelled undirected graphs with up to 100 vertices, and in the middle, unlabelled
-        and undirected graphs with up to 35 vertices. On the bottom row, an instance-by-instance
+        top, 33\% labelled undirected graphs with up to 100 vertices, and then unlabelled
+        and undirected graphs with up to 35 vertices. On the bottom, an instance-by-instance
         comparison of the association and CP Both approaches, with 33\% labelled graphs on the

### 2016-04-20 paper/paper.tex
Colouring is described elsewhere

@@
 \newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.85}
-\renewcommand{\topfraction}{0.9}
-\renewcommand{\bottomfraction}{0.8}
 
@@
 
-    \vspace*{1em}
+    \vspace*{0.5em}
     \centering
@@
 \christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}
+
+It is not possible to determine connectedness from a raw association graph. However, we can take a
+maximum clique algorithm and mimic the CP branching strategy if we have access to the underlying graphs
+and can determine the ``meaning'' of the association graph vertices.
+
+Most modern maximum clique algorithms for dense graphs use some variation of greedy graph colouring
+as a bound---the underlying observation is that each vertex in a clique must be given a different
+colour in a colouring, so if we can colour a subset of vertices using $k$ colours then a maximum
+clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
+heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
+last colour class created. Because of this coupling of branching and the bound (which is important
+in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
+viewed as variables, without requiring a new bound to be calculated for every iteration
+\cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for branching at
+each stage inside a clique algorithm, we would lose completeness. Thus we must adapt the bound to
+take into account restricted branching.
 
@@
 \nl \Begin{
-    \nl $\mathit{result} \gets []$ \;
-    \nl \While{$\mathit{uncoloured} \ne \emptyset$\label{whileuncoloured}}{
-        \nl $\mathit{colourClass} \gets []$ \label{newcolourclass} \;
-        \nl $\mathit{colourable} \gets \mathit{uncoloured}$ \;
-        \nl \While{$\mathit{colourable} \ne \emptyset$}{
-            \nl $v \gets \textnormal{the first vertex from}~\mathit{uncoloured}~\textnormal{by
-            static degree order from}~G$ \label{selectvtocolour} \;
-            \nl $\FuncSty{append}(\mathit{colourClass}, v)$ \label{addtocolourclass} \;
-            \nl $uncoloured \gets uncoloured \setminus \{ v \}$ \;
-            \nl $\mathit{colourable} \gets \mathit{colourable} \setminus \operatorname{N}(G, v)$ \;
-        }
-        \nl $\FuncSty{append}(\mathit{result}, \mathit{colourClass})$ \;
-    }
-    \nl $\KwSty{return} ~ \mathit{result}$ \;
+    \nl $\KwSty{return}$ a greedy sequential colouring of the vertices in $\mathit{uncoloured}$,
+    using the procedure of San Segundo et al.\ \cite{DBLP:journals/cor/SegundoRJ11} with a static
+    degree order from $G$ and $k_{min} = 0$. \;
 }
@@
 \end{algorithm}
-
-It is not possible to determine connectedness from a raw association graph. However, we can take a
-maximum clique algorithm and mimic the CP branching strategy if we have access to the underlying graphs
-and can determine the ``meaning'' of the association graph vertices.
-
-Most modern maximum clique algorithms for dense graphs use some variation of greedy graph colouring
-as a bound---the underlying observation is that each vertex in a clique must be given a different
-colour in a colouring, so if we can colour a subset of vertices using $k$ colours then a maximum
-clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
-heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
-last colour class created. Because of this coupling of branching and the bound (which is important
-in practice because it mimics a ``smallest domain first'' branching heuristic if colour classes are
-viewed as variables, without requiring a new bound to be calculated for every iteration
-\cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for branching at
-each stage inside a clique algorithm, we would lose completeness. Thus we must adapt the bound to
-take into account restricted branching.
 
@@
         colours, since we cannot simultaneously map $c$ to $2$ and $d$ to $3$, or vice-versa. Thus
-        $\mathit{colourClasses}$ becomes a list of four colour classes, the first three containing
-        two vertices each, and the last containing four vertices. This tells us that if we hope to
+        $\mathit{colourClasses}$ becomes a list of four colour classes. This tells us that if we hope to
         extend the current common subgraph by another four vertices, we
-        must pick one assignment from each of the four colour classes (which is not actually possible, so we
-    see the bound here gives an overestimate). The algorithm thus guesses $d \mapsto 3$ as its next
+        must pick one assignment from each of the four colour classes (which is not actually
+        possible, so the bound here gives an overestimate). The algorithm thus guesses $d \mapsto 3$ as its next
 assignment, and if that fails, $d \mapsto 2$, and so on; once $b \mapsto 3$ is reached, the bound
@@
 branching on $v_3$ and $v_1$, so we would miss the solution. Thus we cannot simply add the branching
-rule without also adapting the combined bound / ordering heuristic.)
-
-Our $\FuncSty{colour}$ procedure is the same as the bit-parallel algorithm introduced by San Segundo
-\textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}. While we have remaining vertices to colour
-(\lineref{whileuncoloured}), we start a new colour class (\lineref{newcolourclass}), and then
-repeatedly pick a legal vertex to add to that colour class (\lineref{addtocolourclass}).  The
-selection of the next vertex to colour (\lineref{selectvtocolour}) may be performed efficiently in
-hardware if the association graph is permuted to be in degree order at the top of search. Other
-initial vertex orderings have been considered on general clique problems
-\cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}; it is possible that special
-properties of the association graph could be exploited in this step.
+rule without also adapting the combined bound and ordering heuristic.)
+
+Our $\FuncSty{colour}$ procedure is a simple greedy sequential colouring. We use the bit-parallel
+algorithm introduced by San Segundo \textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}, with the
+$k_{min}$ parameter set to $0$, so we do not present it here. We use a simple static degree
+ordering; other initial vertex orderings have been considered on general clique problems
+\cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}, and it is possible that
+special properties of the association graph could be exploited in this step (for example, it is
+always possible to colour the initial association graph using
+$\operatorname{min}(\left|\operatorname{V}(G_1)\right|, \left|\operatorname{V}(G_2)\right|)$
+colours, but with certain initial vertex orderings, a greedy sequential colouring will sometimes use
+many more colours).
 

### 2016-04-20 paper/gen-graph-connected-heatmap.tex
Handle headers on first line
Green / blue instead of blood splatters

--- 2016-04-07 paper/gen-graph-connected-heatmap.tex
@@
 %% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
-%% Thu 07 Apr 2016 11:12:14 BST
+%% Wed 20 Apr 2016 12:04:43 AEST
 \tikzset{every node/.append style={font={\scriptsize}}}
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff846eff6f65ff846eff7e6cff6f65ff8c72ff7367ff7e6cff8c72ff7869ffffffffac88ff9576%
-  ff9576ff7869ff8c72ffac88ff846eff9576ff9576ff9f7dff8c72ff9f7dff8c72ff9576ffac88ff9f7dff8c72ff8c72%
-  ff8c72ff9576ff8c72ff9f7dff8c72ffffffff9f7dff9576ff9f7dff9576ff9576ff9576ff7e6cff9f7dff9f7dffffff%
-  ff9f7dffac88ff9f7dffffffff7e6cffac88ffffffffffffffffffff9f7dff9f7dffffffffffffffac88ffac88ffac88%
-  ff9576ffac88ffffffffac88ffffffffffffff9f7dffac88ff9f7dffffffff9f7dffac88ff9f7dff9576ff6f65ff7869%
-  ff7e6cfc6260fc6260ff6b63ac0527ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffac88%
-  ffffffffffffffac88ffac88ffffffffac88ff9f7dffffffff9f7dee4156ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffac88ffac88ffffffffac88ff9f7ded4155ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7d%
-  ff8c72ff9f7dff9f7dec3f55ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9576ffffffff9f7dffffff%
-  ffac88ffffffffac88ff9f7dff9f7dff9576ff9f7dffac88e93c53ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ffac88ffac88ffffffff9f7dff8c72ff9576ff9f7dff9f7dff9f7dffffffffffffec4055ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffff7e6cffac88ffac88ff7e6cff9f7d%
-  ff9f7dff9576e33450ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffffffff9576%
-  ffac88ff846effac88ffac88ffac88ffac88ff9576ec3f55ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffac88ffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffac88ffac88%
-  ff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9576ffac88ffac88ffac88ee4156ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffff9576%
-  ffac88ffffffff9f7dff9f7dffac88ffac88ff9f7dff9f7dff9576ffffffff9f7dff9576ffffffff9576ffffffff9f7d%
-  ffac88e1314fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ff9f7dff9f7dffac88ff8c72ff7e6c%
-  ff9576ffffffff9576ff9576ff846eff9576de2e4dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ffac88ffffffffffffffffffff9f7dffac88ff9f7dff9f7dffffffff9f7dff9f7dff8c72ffac88ffffffff9576ff9f7d%
-  ff9f7dff8c72ffffffff9576ffffffff8c72ffac88ffffffffffffff8c72ff9576dd2d4dffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffff9f7dff9f7dffac88%
-  ffffffffac88ff9576ffffffffac88ff9576ffac88ff9576ffac88ff9f7dff846effac88ff8c72ff846eff8c72ff8c72%
-  d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffffffff%
-  ffac88ffac88ffffffffac88ffffffffac88ff9576ff9f7dffac88ff9f7dffac88ffac88ff9f7dffac88ffac88ff9f7d%
-  ff9f7dff9576ff9f7dff8c72ffac88da294bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ff9576ffac88ffac88%
-  ffffffff9f7dff8c72ffac88ff9f7dffac88ff846effac88ff846efe6862da294bffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffac88ffac88ffac88ff9f7dffffffff8c72%
-  ffac88ffffffffffffff9f7dffffffff9f7dff9f7dffac88ff8c72ff8c72ffffffff9576ff7869ff7367ff8c72d7264a%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffac88ffffff%
-  ffffffffac88ffffffffac88ffffffff9f7dffac88ff9f7dff9f7dffac88ffffffff9f7dff9f7dff7e6cff9576ff9f7d%
-  ff9576ff7869ff7869ff6f65d62449ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dff9f7dff9f7dff9f7dff9f7dffffff%
-  ff9f7dff9576ff8c72ff9576ff9576ff7869ff7e6cf6545cfc6260d52349ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffff9f7dffffffffffffff8c72ff9f7dffac88ff9576%
-  ffac88ff9576ff8c72ff9f7dff9f7dff9f7dff8c72ff9576ff6f65ff846eff6f65ff6b63fd6561fd6561d21f47ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffff9f7dff9f7dff8c72ff9f7dffffffffac88ff9576ff7e6cff846eff846efe6862ff6b63%
-  fe6862f7565cfc6260d8264affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88ffffffffac88%
-  ffffffffffffff9576ffffffffac88ffac88ff9f7dffffffffac88ff8c72ffffffff9576ffac88ffac88ffac88ff7367%
-  ff6f65ff7e6cfe6862fe6862f7585dfb605ffe6862f95c5ed32148ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9576ffac88ff9f7dffffffff9f7d%
-  ff9f7dff9f7dff9576ff7e6cff8c72ff9576ff6f65ff6b63ff6b63fb605ffd6561ff6b63f85a5dda294bffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ff9f7dff9f7dffac88ffac88%
-  ffffffffffffff9f7dff9f7dff9f7dffac88ff9f7dff9576ff6f65ff8c72ff7e6cff6b63fe6862ff6f65f34d59fe6862%
-  f85a5dff6f65d7254affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffff%
-  ffac88ffac88ff9f7dffac88ffac88ff9576ff8c72ff9576ffac88ff9576ff846eff9576ff8c72ff846efa5e5ffb605f%
-  fa5e5ff7585dfb605ff7565cf85a5dfe6862fc6260d8264affffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffffff%
-  ffffffff9576ffffffffac88ffffffffffffffac88ffac88ffac88ff8c72ff9f7dff8c72ffac88ff8c72ff846eff7869%
-  ff7e6cfd6561fd6561fd6561fa5e5ffd6561fa5e5fff6b63f85a5dfd6561fb605fff7e6ce1314fffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffff9f7dffac88ff9576ffac88ffac88ffffffffac88ffffffff9f7dff7e6cff9576%
-  ff7367ffac88ff7869ff7869fe6862ff6b63fc6260fd6561ff7367fe6862fc6260fe6862f85a5df7585dfe6862ff6f65%
-  ff6b63e73952ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffac88ffffffffffffffffffffffffffac88ffffffff9f7dffac88ffac88ff9f7dff9576%
-  ffffffff9576ffac88ff8c72ff846eff9576ff846eff6f65ff846eff846eff7367f85a5dfb605ffc6260f7585df7565c%
-  fd6561ff7367ff6f65fe6862ff7e6cff846eef4356ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffac88ffffffffac88ffffff%
-  ffac88ff9f7dff9576ffffffffffffff8c72ffac88ff9576ff9576ff9576ff9576ff9576ff9f7dff7e6cff846efe6862%
-  ff7869ff8c72fe6862ff6b63ff7367ff7869ff8c72ff846eff846eff9576ff9f7de83b53ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88%
-  ffffffffac88ffac88ffffffffffffffffffff9576ff9f7dff8c72ff9576ff9f7dff846effac88ff9576ff8c72ffac88%
-  ff7e6cff7e6cff8c72ff8c72ff6b63ff846eff6f65ff7869ff7367ff9f7dff9576ff7e6cff846eff9f7dff8c72ff8c72%
-  ed4155ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9f7dff9576ff846eff9f7dffac88ff8c72ffac88%
-  ff9576ff9576ff9f7dff846eff8c72ff7e6cfe6862ff6f65fc6260ff9576ff8c72ff846eff7e6cff9576ff9f7dff9576%
-  ffffffff8c72ffac88ffac88ffac88f24a59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffff8c72ffffffff9f7dff9576%
-  ff8c72ff9f7dffac88ffac88ff9f7dff846eff7869ff9f7dff7e6cff7e6cff7367ff6f65fd6561ff7e6cfe6862fe6862%
-  ff9576ff8c72ff9f7dff846effffffff9f7dff9f7dff9f7dffac88ffffffe93c53ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dff9f7d%
-  ffffffff9f7dff9576ff9f7dffac88ffac88ff9576ff8c72ff9f7dff9f7dff846efe6862ff6b63fd6561ff7367f95c5e%
-  fe6862ff6f65ff846eff7e6cff7869ff6b63ff846eff9f7dff9f7dff846eff8c72ff9f7dff8c72ffffffff9f7df34d59%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ff9f7dff7e6cff8c72ff9576ff8c72ff846eff8c72ff8c72%
-  fd6561ff7e6cfc6260ff846eff7869fd6561f95c5ef95c5eff6f65ff7e6cff9f7dff846eff9576ff9f7dff9576ffac88%
-  ffac88ff8c72ff9576ff9f7def4457ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff9f7dffffffffffffffffffffac88ffac88ffac88ff9f7dff9f7dff9576ff8c72ff9f7d%
-  ff8c72ff7367ff8c72fe6862ff7367ff6b63fb605ffc6260fe6862f85a5dfd6561f7565cff6f65fe6862ff6f65ff7869%
-  ff8c72ff9576ff8c72ff9576ffac88ffffffffac88ffac88ff9f7df14858ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffac88ffac88%
-  ff8c72ff7869ff9f7dff9f7df95c5eff7869fe6862fd6561ff7367fa5e5ff95c5ef7565cf5515bf6545cf7585dfc6260%
-  fb605fff6f65fc6260ff6f65ff6b63ff846eff8c72ff9f7dff9576ffac88ffac88ffac88ff9576ffac88ef4356ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
-  ff9576ffac88ffac88ff7367ff846eff7367fe6862ff6f65fb605ffd6561f95c5eff6f65f7585dff6b63f95c5ef85a5d%
-  f7565cf24a59f5535bf4505aff6b63f7585dfa5e5fff6f65ff6b63ff7e6cff8c72ff8c72ffac88ff9f7dff9f7dff8c72%
-  ffffffff8c72ff846ef14958ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffff%
-  ffac88ffffffffffffffffffffac88ffac88ffac88ff9576ff9576ff7e6cff8c72ff7367f95c5eff7869f85a5dfb605f%
-  fb605ff85a5df85a5dfc6260f6545cfa5e5ff7585dfd6561fa5e5ffc6260ff6b63ff7869ff7e6cff8c72fd6561ff846e%
-  ffac88ffac88ff9f7dffac88ff9576ff9f7dff9576ff846ef7585dffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffffff846eff8c72ff7e6cff846eff7e6c%
-  ff6f65fb605ffe6862ff6b63fc6260f95c5efb605ff85a5df7585dfa5e5ffd6561fe6862fb605ffd6561fe6862ff6b63%
-  ff6f65ff846eff7e6cff9f7dff8c72ff9576ff9f7dffac88ff9576ff9576ffac88ff9f7dffac88f24b59ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dff846effffff%
-  ff846eff9576ff8c72ff7869ff7e6cff7367ff7367fa5e5ffc6260f7585dfb605ffb605ff95c5efe6862fc6260fb605f%
-  ff7869ff6b63fe6862ff7367ff7869ff8c72ff9576ff7e6cff9576ff9576ff9f7dff9f7dff9f7dff8c72ff8c72ff7869%
-  ff846eff9576f04557ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ffac88ffffffffac88ff9f7dff8c72ff9576ff846eff7367ff6f65ff7e6cf95c5efc6260fe6862fd6561fc6260fb605f%
-  f95c5ef95c5ef95c5eff6f65fd6561ff8c72fd6561ff7e6cff6f65ff846eff8c72ff7869ff8c72ff9576ff9f7dffffff%
-  ff846eff8c72ff9f7dffac88ff9f7dff846eff9f7df5515bffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffac88ff9576ffac88ffac88ff9576ff846eff846eff7e6cff7367fb605ffe6862ff6b63%
-  fc6260fd6561ff846efb605fff8c72ff7e6cfb605fff6f65ff7869ff8c72ff7869ff6f65ff846eff6f65ff7e6cff846e%
-  ff9576ff9576ff9576ff9576ff9576ff846eff846eff9576ff846eff9576ff9576ff9f7df24a59ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffff9f7dff9576ffffffff9576ff9f7dff846efe6862%
-  f7565cff6f65f7565cf95c5eff7367fc6260fa5e5fff7367fe6862ff7869ff7869ff7e6cff7e6cff846eff7367ff9576%
-  ff7e6cff7e6cff8c72ff846eff846eff9576ff7869ff7869ff8c72ff8c72ff9f7dff846eff9576ff7869ffffffff9576%
-  ff9576e93c53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dff9f7dffac88ffac88%
-  ff9f7dff9576ff9f7dff8c72fe6862fd6561fd6561fc6260ff7367ff7367ff7869ff7869fd6561ff6b63ff6b63ff7367%
-  ff7e6cff846eff7367ff7869ff846eff7869ff7869ff846eff9f7dff7367ff8c72ff8c72ff8c72ff9576ff9f7dff9576%
-  ff9f7dff8c72ff9576ff9576ff9f7dff9f7df34d59ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffac88%
-  ffac88ff9f7dffffffffac88ffac88ffac88ff9f7dff8c72ff846eff7e6cff9576f85a5dff6f65ff6b63ff6b63ff7869%
-  fc6260fd6561fe6862ff6b63fd6561ff6b63ff846eff7e6cff9576ff9f7dff8c72ff9576ff8c72ff7869ff8c72ff7e6c%
-  ff8c72ffac88ff9f7dffac88ffac88ff9576ff9576ff9576ff8c72ff9576ffac88f4505affffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffac88ffac88ffffffffffffffac88ff8c72ff9f7dff8c72ff7367ff846eff846eff7e6cff7869ff8c72%
-  fc6260ff7e6cff7367fb605fff7869ff7e6cff7367ff7e6cff7367ff7869ff8c72ff7e6cff8c72ffac88ff8c72ff7869%
-  ff9576ff7367ff846eff7367ff7367ff7e6cff8c72ffac88ffac88ff7869ff846effffffff9576ff9576ff9f7dff9576%
-  f14958ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ff8c72ff846eff9576ff9576ff9576%
-  ff7869ff6b63ff846eff7869ff7e6cff7e6cfb605fff7367ff7e6cff9576ff8c72ff9576ff8c72ff8c72ff9576ff7367%
-  ff6f65ff6f65ff7367ff8c72ff9576ff9576ff9f7dff7e6cff846eff7e6cff7e6cff846effac88ff9576ff9576ff9f7d%
-  ff8c72ff9f7dffffffffac88ff9576ef4457ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffff9f7dffffffff9f7dffffffffffffffffffffac88ffffffff9f7dffac88ff9f7d%
-  ff9f7dff846eff846eff8c72ff7367ff6f65ffac88ff6b63ff7869ff7869ff8c72ff9f7dff9f7dff7e6cff7e6cff8c72%
-  ff8c72ff9576fe6862ffac88ff7869ff8c72ffac88ff7e6cff9576ff846eff7e6cff8c72ff7e6cff8c72ff7367ffac88%
-  ff8c72ff8c72ff7869ff8c72ff9f7dff9576ffac88ff9f7dffac88ff846ef24a59ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88%
-  ffac88ff846eff9576ff8c72ff9576ff9f7dff9f7dff846eff7e6cff7367ff7e6cff7869ff7e6cffac88ff9576ff6f65%
-  ff9576ff7e6cff846eff9576ff7e6cff7e6cff7e6cff846eff7e6cff8c72ff8c72ff7869ff9f7dffac88ff9f7dff9f7d%
-  ff8c72ff9576ff846eff9576ff7869ff8c72ff6f65ff846eff9576ff846eff9576ffac88ff846eff9f7dffac88f14958%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88%
-  ffffffffffffffffffff9f7dffac88ffac88ffffffffac88ff8c72ff846eff9f7dff8c72ff8c72ff7e6cff7869ff7869%
-  ff8c72ff6f65ff846eff7e6cff6f65ff7e6cff8c72ff846efb605fff7e6cff6b63ffac88ff846eff9576ff846eff8c72%
-  ff9576ff8c72ff7869ff9f7dff9f7dff846eff8c72ff9f7dff8c72ff8c72ff9576ff846eff846eff9576ff9576ff9f7d%
-  ff9576ff9f7dff7e6cff9f7df24a59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ff9576ffffffff9f7dffac88ffffffffac88ff9f7dff8c72ff9576ffac88ff8c72%
-  ff9576ff7367ff7367ff7869ff9576ff8c72ff9576ff8c72ff7e6cff846efe6862ff7869ff7367ffac88ff6f65ff7e6c%
-  ff7e6cff7e6cff846eff7e6cff846eff8c72ff8c72ff7869ff9576ff846eff846eff8c72ff846eff7e6cff8c72ff9576%
-  ff9576ff9576ff9576ffac88ff9576ff8c72ffac88ff846efffffff85a5dffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffff9576ff9576ffffffff846eff9f7dffac88%
-  ff7869ff9576ff7e6cfe6862ff7869fe6862ff7367fd6561ff9576ff7367ff7367ff7367ff846eff9576fa5e5fff7e6c%
-  fb605fff7367fe6862ff846eff6f65ff846eff8c72fd6561ff8c72ff7869ff846eff6f65ffffffff9f7dff8c72ff846e%
-  ff7e6cff7869ff9576ff9576ff8c72ff9576ff8c72ff9f7dff7e6cff846eff9f7dff9f7dff8c72ffac88f85a5dffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffffffffffffffac88%
-  ff9576ffffffff9576ff8c72ffac88ff7367ff7869ff9576fc6260ff6b63fe6862ff846eff846eff846eff6f65ff7869%
-  ff6f65ff8c72ff9f7dff7e6cff846efd6561ff6b63ff846eff7869ff7e6cff7e6cff9f7dff7869ff846eff7e6cff846e%
-  ff8c72ff846eff9576ff9f7dff9576ff6f65ff9f7dff846eff9f7dff7e6cffac88ff9576ff9576ff8c72ff8c72ffffff%
-  ffac88ffac88ff9f7df24b59ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ff9576ff846effffffff9576ff9576ff9576ffac88ff846eff846eff7e6cff6b63ff7367fe6862ff7869ff6f65%
-  ff7e6cff7869ff7e6cff7869ff846effac88ff846eff7367ff9576fd6561ff7869ff7367ff6f65ff7869ff7869ff846e%
-  ff846effac88ff7367ff8c72ff846eff8c72ff7367ffac88ff846eff7e6cff846eff7869ff7869ff846eff846eff9576%
-  ff9f7dff8c72ffac88ffffffffac88ff9576ff846eff9576f7565cffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffac88ffac88ffffffffffffffffffffac88ffac88ff9576ffffffff9576ff8c72ff9576ffac88fa5e5f%
-  ff846eff7367ff7e6cff846eff9f7dff6f65ff7367ff9576ff9f7dff9576ff7869ff7869fd6561ff7367fb605fff846e%
-  fe6862ff9576ffac88ff7367ff7e6cff7869ff7e6cff9576ff9576ff7869ff6f65ff846eff6f65ff9576ff7869ff7e6c%
-  ff846eff846eff6b63ff7e6cff9576ff8c72ff9f7dffac88ff9576ff7869ff9f7dffac88ff9576f34e5affffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9f7dffac88ffac88ffffffff9f7dffffffff9f7dffffffff9f7dff9576ff846eff9576ff8c72%
-  ff9576ff9f7dff846eff846eff7e6cff9f7dff8c72ffac88ff7869ff7e6cff9f7dff9f7dff9576ff846eff8c72ff6f65%
-  ff7367ff6b63ff7367ff846eff6b63fe6862ff846eff8c72ff6b63ff9576ff9f7dff9576ff7869ff846eff9576ff846e%
-  ff846eff7869ff8c72ff7869ff6f65ff7e6cff8c72ff9576ff9576ff8c72ff9576ffac88ff9576ff9f7dff8c72ff846e%
-  ff9576ffac88f5535bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dff8c72ffffffffac88ffffffff9f7d%
-  ffac88ff8c72ff9f7dff9576ff9576ff846eff846eff7e6cff7869ff8c72ff7869ff9f7dff846eff7e6cff9576ff9f7d%
-  ff8c72ffac88ff9f7dff846eff7367ff6b63ff846eff7869ff6f65ff7367ff9576ff846eff7367ff846eff8c72ff7e6c%
-  fe6862ff6b63ff9576ff7e6cff7e6cffac88ffffffff846eff7e6cff8c72fe6862ff6f65ff7e6cffffffff8c72ff846e%
-  ff9576ff846eff9576ff8c72ff9576ffffffffac88f24b59ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88%
-  ffffffff8c72ffac88ff9f7dffac88ff9f7dff9f7dff7e6cff9f7dff7869ff846eff7e6cff9f7dff7367ff9576ff7869%
-  ff7e6cff8c72ff6b63ff846eff7869ff9f7dff7e6cff846eff8c72ff7367ff7e6cff9f7dff7367ffac88ff7869ff846e%
-  ffffffff8c72ff8c72ff8c72ff846effffffff7869ff9576ff7367ff7367ff9576fd6561ff7e6cff846effac88ff9f7d%
-  ff8c72ff9576ff9576ff9f7dff6f65ff9576ffac88ff7869ff846eff9f7dff9576ff9576f6545cffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffff7367ff7e6cff9576ffffffff8c72ff8c72ff7e6c%
-  ff7e6cff7869ff7e6cff846eff6b63ff7367ff7869ff7869ff7869ff7367ff9576ff846eff846eff846eff8c72fe6862%
-  ff6b63ff7869ff846eff8c72ff9576ff9576ff846eff9576ff7e6cff846eff846eff846eff7367ff9576ff7e6cff6b63%
-  ff846eff8c72ff9f7dff8c72ff9576ff846eff9576ff9f7dff7e6cff846eff9f7dff9f7dff8c72ff7869ff9576ffac88%
-  ffac88f04557ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ff9576ffffffffac88ff9576ff9f7dff9576ff9576%
-  ff9f7dff9f7dff8c72ffac88ff9576ff7869ff7869ff7869fd6561ff7869ff6b63ff7869fb605fff846eff7869ff8c72%
-  ff7e6cff8c72ff846eff7e6cff8c72ff6f65ff7e6cff9576ff9576ff9576ff9f7dff846eff7869ff846eff9576ff7869%
-  f85a5dff846eff7869ff7869ff846eff846eff7869ff846eff6f65ff8c72ffac88ff846eff9f7dffac88ff8c72ff8c72%
-  ff9f7dff9f7dff9576ff9f7dffac88fffffff95c5effffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffac88ffffff%
-  ff9f7dff846eff8c72ff9f7dff6f65ff9576ff7367fe6862ff7e6cff846eff7869ff6b63ff7367fd6561f85a5df85a5d%
-  ff6b63ff7367ff7367ff7e6cff7869ff8c72ff8c72ff846eff8c72ff8c72ff846eff846eff8c72ff846eff7e6cff6b63%
-  ff6f65ff7367ff9576ff7869ff6f65ff9576ff9576ff7e6cff846eff7367ff8c72ff7e6cff8c72ff9f7dff8c72ff9576%
-  ff9576ff9576ff846eff9f7dff9576ff8c72ffac88ff8c72ff8c72ff8c72ffac88ff6b63ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffac88ffac88ff8c72ffffffffac88ff9576fe6862ff9576ff6f65ff9576ff7367ff7e6cff6f65ff6f65%
-  f7585df7585dfd6561fa5e5fff7367ff7869ff6f65ff6f65ff846efe6862ff846eff9576ff8c72fe6862ff7869ff7367%
-  ff7e6cff9f7dff7e6cff9576ff8c72ff8c72ff8c72ff7869ff9f7dff846eff6b63ff6f65ff7367ff7869fb605fff846e%
-  ff6b63ff8c72ff9f7dff9576ff7e6cff7e6cff846eff7367ff7e6cff7e6cff9576ff8c72ff8c72ff9f7dff846eff9f7d%
-  fa5e5fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9576ff9576ff846eff8c72ff7869ff9576ff7367%
-  ff846eff7e6cff6f65fb605ff5515bf4505af4505af5535bf95c5eff6f65ff7869fe6862ff7869ff6f65ff846eff7e6c%
-  ff846eff6f65ff7e6cff846eff7367ff7e6cff9f7dffac88ff846eff9f7dff846eff7e6cff7e6cff846eff9576fd6561%
-  fd6561ff9576ff7367ff7869ff7869ff8c72ff846eff846eff7e6cffac88ff7e6cff9f7dff9f7dff846eff8c72ff9f7d%
-  ff7e6cff8c72ff9576ff9576fffffffe6862ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffffff9f7dff9576ffffffff9576%
-  ff9576ff7367ff846eff7869fa5e5ffa5e5ffe6862fa5e5ff24b59f5535bf4505af34d59fc6260f7565cff7e6cfc6260%
-  ff6f65fe6862ff7869ff8c72ff7367ff846eff9576ff8c72ff9576ff846eff846eff6b63ff7367ff9f7dff6f65ff8c72%
-  ff6f65ff7869ff846eff846eff7367ff7e6cff7e6cff7869ff8c72ff846eff7869ff9f7dff9576ff846eff7869ff846e%
-  ffac88ff9f7dffac88ff8c72ff8c72ff9576ff846eff9576ff8c72ff9576ff7367ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffff9f7dffac88%
-  ffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffff9f7dffac88ffffffff9f7dff9f7dff9576ffac88%
-  ffffffff9f7dff8c72ffffffff8c72ff7869ff8c72ff8c72fa5e5ff85a5dff6f65fa5e5ff85a5df24b59fa5e5ff5535b%
-  f14958fb605ff85a5dfc6260ff7e6cff6b63ff6b63ff7869ff7e6cff7367ff9f7dff7367ff7e6cff846eff6f65ff7869%
-  ff7869ff9576fe6862ff7869ff7869ff7e6cff7e6cff6f65ff7367ff7367ff8c72ff846eff6b63ffac88ffffffff846e%
-  ff7869ff7e6cffac88ff9576ff9576ffffffffffffffac88ffac88ffac88ff9f7dff9576ffac88ffffffffac88ff7869%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
-  ff7e6cff9576ff8c72fc6260ff7367ff9f7dff7367ff9576ff9f7dff9576ff7869ff8c72ff9f7dff8c72ffffffff8c72%
-  ff7869ff8c72ff9f7dff9576ff9576ff9576ff8c72ff9576ff9576fd6561ff8c72ff9f7dff7869fb605ff85a5dfc6260%
-  f5515bf4505aee4256f5535bf34d59f04757f34e5af6545cf85a5dfb605ffd6561fb605fff7e6cff7869ff7e6cfe6862%
-  ff7869ff7e6cff7367ff7367fe6862fe6862ff9576ff6b63ff6f65fc6260ff7869ff6b63ff7367ff6f65ff7869ff7869%
-  ff7869ff846eff7367ffac88fe6862ff7367ff8c72ff9f7dff846eff9576ffac88ff9f7dff9576ff9576ff9f7dffffff%
-  ffffffff9576ff9576ffffffff6b63ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff7367fe6862ff7367f95c5efc6260f95c5ef95c5eff6b63fa5e5ffc6260fe6862f5515b%
-  fc6260fa5e5ffd6561ff7367ff7367fe6862ff846eff9f7dff846eff7367ff7367ff846eff6b63fe6862fe6862fd6561%
-  ff7367ff6b63fe6862f14958f4505aee4256f4505af04757f14958ef4356f04557f14958f4505afa5e5ff95c5ef95c5e%
-  ff7367fe6862ff846efd6561fe6862ff7e6cfc6260ff846eff7e6cfd6561fd6561ff7869fe6862ff6f65f95c5eff6b63%
-  ff7869ff8c72ff8c72ff7367ff7869ff9576ff8c72ff846eff846eff9576ff846eff9576ff846eff8c72ff9f7dff7e6c%
-  ff9f7dffac88ff9576ff9f7dff9576ff9f7dffac88ffac88ffac88ff7869ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88fe6862f5535bf7585df7565cf34e5af14858f14858%
-  f7565cf7565cf5515bf7565cfa5e5ff34d59f34d59f34e5afc6260f4505af5535bfd6561ff7367fe6862fc6260ff6f65%
-  fc6260fa5e5ffc6260f7565cff6b63f4505af7565cf5535bf34d59f24a59ee4256f04557ef4356ed4155ef4457f04557%
-  ea3d54f04757ee4156f5515bf5535bf6545cf7565cff846eff846eff6f65f95c5efc6260f85a5df6545cfd6561fc6260%
-  fd6561fc6260fe6862fb605fff6b63ff7367ff846eff7367ff7869ff9576ff846eff9f7dff9f7dff846eff9576ff7869%
-  ffac88ff7869ff9576ff9576ff8c72ff9576ff8c72ff9f7dffac88ff9576ff8c72ffac88ffffffff9f7df7585dffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff6b63fc6260f6545c%
-  f5535bf14858f04557f7565cfa5e5ff5515bf6545cf95c5ef7565ced4155de2e4ed62449df2f4eef4457f14858f95c5e%
-  f5515bf85a5dff7367f5535bfa5e5fff6b63f85a5df5535bf85a5dfb605ff5535bf14858ef4356e83a53eb3e54eb3e54%
-  f14958e83b53e73952ee4156ec3f55ec3f55ee4156ed4155f85a5df04757f14858f14858f34d59f4505af5535bfe6862%
-  f4505af5515bfa5e5ffd6561fc6260f6545cff6f65ff6b63fc6260fd6561ff6b63fc6260ff6f65ff7e6cff6b63ff9f7d%
-  ff9f7dff7869ff7367ff9576ff7869ff7e6cff8c72ff846eff7869ff9f7dff9576ff846eff8c72ff9576ff9576ffac88%
-  ffffffff9f7dffffffe63852ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffac88fa5e5ffc6260f95c5ef95c5eff6b63fe6862ff6f65fc6260ff7e6cfd6561ff7e6cfe6862f5515bd9284bbe1037%
-  b80c32d21f47db2a4ce33550f24b59f6545cf7585df24a59f4505af6545cfe6862fa5e5ff6545cf6545cec4055ed4155%
-  e83a53df304ee33450e73a52ef4356e83a53e63852e73952e73a52eb3e54f4505aed4155ef4457fb605ff4505aef4457%
-  ee4256f5515bf7585df14958f4505afb605ff85a5dff6f65fe6862fe6862fa5e5ffe6862ff846eff7367ff7e6cfb605f%
-  fe6862ff7e6cff6b63ff846eff7367ff7869ff9576ff8c72ff9f7dff8c72ff9576ff7e6cff9576ff8c72ff7e6cff8c72%
-  ff9f7dffac88ff7e6cff9576ff9f7dffac88ff7e6cff9f7dec4055ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffff7e6cf04757f7585df5535bf34d59f34e5aff7367fb605ffd6561fd6561ff6f65%
-  fd6561fd6561ff6b63e43651d7254ad7254ae83b53f34e5af24b59f5515bef4457f34e5aee4256f7565cf5515bf85a5d%
-  f04757ef4356e73a52ea3d54e2324fd8264adb2b4ce23350e63852e43651ee4156e83a53e43651ea3d54e73a52e43651%
-  f04757f04757ef4356f7565cf14858f14858f34d59f34e5af14858f34e5afa5e5ffa5e5ff5515bfa5e5ff6545cfa5e5f%
-  ff7367ff7367ff6f65ff7e6cfe6862ff7e6cff846eff6b63ff7367ff7869ff8c72ff7869ff7367ff7e6cff7869ff8c72%
-  ff6f65ff7869ff846eff9576ff846eff8c72ff846effffffff9576ffac88ff9f7dffac88ff9f7df24b59ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7869ee4156e93c53f04557f14958e73a52%
-  ec4055ec3f55f24b59fb605ff5515bf5515bf34e5af34e5aec4055f24a59f7585df24b59fc6260f5515bf95c5ef6545c%
-  f6545cf6545cf14958ed4155e93c53ed4155e43651e33450e2324fdb2a4cde2e4de63852e33550e73a52ee4156e53751%
-  ea3d54ec3f55ed4155ec4055e93c53ed4155e93c53f04557ee4256f14858f34d59f5515bef4457f24a59ef4356f85a5d%
-  fa5e5ff95c5efc6260f7585dfe6862fa5e5ff85a5df85a5dff6f65ff6b63fe6862ff7e6cff6b63ff6b63ff6b63ff7869%
-  ff7e6cfd6561ff8c72ff7367ff7367ff7367ff7e6cff8c72ff8c72ff7e6cff9f7dff9f7dff8c72ff9576ffac88ff9f7d%
-  ff9576ffffffee4156ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff6b63%
-  ec4055e73a52ef4356e83a53f34e5af14858f24b59fb605ff6545cf7585dea3d54d21f47ca1941c7173ed62449e63852%
-  f34d59f85a5def4457f7565cf5515bf14858f4505af24a59f14858eb3e54e33550e73a52e53651e0314fdf2f4ee53751%
-  dc2c4de43551e63852e53751ea3d54f24a59e83a53ee4256f04757ea3d54e63852ef4457ec4055ef4356f14958f14858%
-  eb3e54f7565cf24a59f04557f4505af24b59fa5e5ff6545cf85a5df6545cf5535bf95c5ef7565cf5535bfc6260f7585d%
-  ff8c72ff7e6cff9576ff6f65ff7e6cff7869ff9576ff7e6cff7367ff9576ff7869ff8c72ff7869ff846eff8c72ff846e%
-  ff846eff9576ff9f7dff9f7dff9576ff9576ff9f7de53651ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ee4156f85a5df4505afd6561ff7869fa5e5fff846efb605fff846eff7e6cff9576fb605fda2a4c%
-  c7173ebe1037c2133bd42248e53751eb3e54f04757f85a5df34e5af34e5aef4356f04557ee4256eb3e54e1314fe23450%
-  e63852ea3d54e63852e43651e63852e1324feb3e54e23350ee4156f24a59ef4356f04757f14958f14858ed4155ee4256%
-  f4505af04557f04557ee4156f5535bf6545cf4505af34d59f6545cfb605ffe6862f6545cfc6260fc6260fb605ff7565c%
-  ff6b63fa5e5fff6f65ff6b63ff6f65ff7e6cff6b63ff9f7dff6f65ff8c72ff9576ff9576ffffffffac88ffac88ff8c72%
-  ff9576ff7e6cffac88ff9f7dff9f7dff9f7dff846eff8c72ffac88ff8c72ff9f7dff9576e0314fffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff846ed21f47d11e46e2324fe53651ec4055ee4156f34d59f5515bff7367%
-  f95c5efe6862fb605ff4505ae93c53e63852d8264ac6163ecf1d45d42148d9284be33450ea3d54e73952e23450d9284b%
-  df2f4ee63852df2f4edd2d4ddc2c4cdf2f4ee43651e33550ea3d54e63852ea3d54eb3e54e93c53f4505aef4356ef4356%
-  ef4356f14858f04757f5515bf5535bf24b59f6545cf24a59fc6260f7585df5535bf5515bfa5e5ff7565cff6b63ff7869%
-  ff7367ff7e6cff6b63ff8c72ff7869ff6f65ff7869ff7367ff9f7dffac88ffac88ff7e6cffac88ff9f7dff9576ff8c72%
-  ffffffff9f7dffffffffffffffac88ffac88ff9576ff8c72ffac88ffac88ffac88ff9f7dffac88ff9576ffac88ff9f7d%
-  ffac88f7585dffffffffffffffffffffffffffffffffffffffffffffffffff7367e33450bd1036d11e46d62449dd2d4d%
-  e23350e93c53ef4356f14858f24a59f7585df7585ded4155e0314fe23450de2d4dca1940c01239c91840d42148d7254a%
-  e53651db2a4ce73952e33450dc2b4cda294be33450e2324fe2324fe63852df304ee0304ee43551ee4156e23450ed4155%
-  f04757ee4256ef4457f24b59ea3d54e1324fed4155ee4256ef4356f04557fa5e5ff5535bf5515bf6545cff7869fc6260%
-  fe6862ff6f65ff7367ff7367ff7869ff8c72ff7e6cff9576ff9576ffac88ff7e6cff9576ff9576ff9f7dff9576ff9f7d%
-  ffac88ffac88ffac88ff8c72ffac88ffffffff8c72ffffffff9576ffffffffffffffac88ffac88ffffffffffffffac88%
-  ffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffd52248%
-  d42248df2f4ee83a53ee4256f5515bf14858fe6862fc6260f5535bee4256dd2d4de23350d52248ca1941c8183fd52349%
-  da294bdb2b4ce0304ee33550e43551e73952e83b53e53751e83a53e43551e43551de2e4de23450e53651e53751ec4055%
-  e93c53ea3d54ef4356ed4155f14958f14858f5535bef4356ef4356ee4256f85a5df85a5df7565cfa5e5ff7565cfd6561%
-  ff6b63ff7367ff7869ff7869ff8c72ff9576ffac88ff9576ffffffff8c72ff9576ff9f7dffffffff9f7dff9f7dff9f7d%
-  ff9f7dff8c72ffac88ff9f7dff8c72ffac88ffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9f7dffac88ff9f7d%
-  ffffffffffffffac88ffac88ffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffff7e6cc4153cce1c44d9274bdc2b4cea3d54f24b59f24b59f7565ce23450d8264ad42248d52349%
-  d7264ad42148c7173ecb1a42d32048da294bea3d54de2e4de2324fdf304ee1324fe1324fdb2a4cdc2b4cdb2a4ce1314f%
-  dd2d4de43551e73a52e93c53e33450f14958ef4457f24a59f34d59f4505af4505af7565cf5535bf6545cf85a5df85a5d%
-  fe6862fd6561f85a5dff9576f7585dfd6561ff6f65ff6b63ff9576ff7367ff846eff8c72ff9576ff9f7dffac88ffac88%
-  ffac88ffac88ffffffffffffff9f7dffffffffac88ffffffffac88ff9f7dffffffffac88ff9f7dffac88ffac88ffac88%
-  ff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffb605fe23450e53651f04557f04557f6545cfa5e5ffa5e5f%
-  fd6561d32148c5163dd7254aee4156f04757ee4256e93c53e73952ec3f55e1324fe2324fe73a52e43551dc2c4de23450%
-  d9274bdb2a4ce0304edd2d4ddc2c4cdf2f4eeb3e54f4505af34e5af04757f24b59f34d59fb605ffd6561ff6f65fa5e5f%
-  ff6b63f95c5ef7565cfc6260f95c5eff6f65fd6561ff9576ff7367ff7367ff6f65ff7e6cff9576ff9f7dff9f7dff9f7d%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffec4055d42148e33450%
-  ed4155f34d59f7585df95c5ef7585df4505ae63852ee4156f24b59f24a59f14858ec3f55ef4356ec4055ee4156e63852%
-  e83a53ec4055df2f4ee73952e43651e53651e73a52e83b53e33450ef4457f5535bf5515bf7565cf6545cfa5e5ff95c5e%
-  ff6f65fa5e5ff5535bf4505afb605ff7565cfc6260fe6862ff7367fd6561fc6260ff6f65ff7e6cff7367ff8c72ff7e6c%
-  ffac88ff8c72ff9f7dffac88ff9f7dff9f7dffac88ff8c72ffac88ffffffffffffffffffff9f7dffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ff846eff7367e93c53e73a52ef4457fd6561f95c5efd6561fb605fff7869e93c53da294be33550ef4457e1314fde2e4d%
-  e63852f04757f04757f24a59ef4457e43551ea3d54e63852ec3f55e63852ee4156ea3d54eb3e54f04557ef4356f34e5a%
-  f24b59ec3f55f5535bf14958f5535bf7565cf7585df85a5df7565cf7565cf85a5dff6f65f85a5dff6b63ff6b63ff6b63%
-  ff846eff6b63fb605fff7869ff9f7dff9576ff846effac88ff8c72ffac88ff9f7dffac88ff9576ffac88ffac88ffac88%
-  ffac88ff9f7dffffffffac88ffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffff7585df04557fd6561fd6561ff846eff8c72ff846eff7e6cff9576fa5e5fd11f46%
-  d11e46e2324fe83b53dd2d4dd62449e93c53f5535bf7585dec3f55f24a59e83b53e73a52ef4356ee4156e73a52f14958%
-  f04757f95c5ef14958f5535bf85a5dfd6561fb605ffe6862fb605ffb605fff7e6cfc6260ff7e6cff7869ff9576ff9576%
-  ff9f7dff8c72ffac88ffac88ff8c72ff9f7dffac88ffac88ffac88ffffffffffffffac88ff9f7dffac88ffac88ff9f7d%
-  ffffffffac88ffffffffac88ffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffff7e6ce0314fe33450ec3f55ff6b63ff7e6cff846e%
-  ff7869fb605fff7367ef4457d9274be73a52ed4155e0314fdf2f4ee63852f04757f24b59f4505af14858ef4356ea3d54%
-  ea3d54f14858f34d59ec4055f14858f6545cf7585df95c5ef85a5dfd6561ff9576ff8c72ff846effac88ff846eff9f7d%
-  ffac88ffffffffffffff9f7dffffffffffffffac88ffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffdb2a4cc01239%
-  cb1a42d9274be73952f14958f14958ec4055e0304ee1324fdc2c4dd52248d8264ad32148cd1b43d01d45d42148d52349%
-  dc2c4ddd2d4dd62449d52349d42248dc2c4cdb2b4cdd2d4ddd2d4dea3d54e83a53f6545cf6545cfc6260ff7367ff8c72%
-  ff9f7dff7e6cffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7ded4155d7254ae23350e83b53ee4156f04757f6545cd52248c3143bd11e46d52248d7254aca1941%
-  d11e46d01e45d62449da294bda294bdc2c4dda294bdd2d4de2324fe63852e83b53eb3e54f04557f34e5af7585dfb605f%
-  ff7367fe6862ff7367ff846eff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffff846ef95c5ef7565cf7585dff7367ff7e6cff7367f5535bdb2a4c%
-  e1324fec4055ef4457e83b53e93c53ea3d54ed4155ef4356f24b59f24b59f04757f14858e53751f7565cf7585dfa5e5f%
-  ff6f65fa5e5fff7869ff9576ff9576ff7367ffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7565cda2a4cd21f47de2e4de23450%
-  e93c53e53751e33550d72549ce1c44d01e46d9274bdf2f4ed42248da294bde2d4dd9284be53751e43551df304edf2f4e%
-  db2a4cea3d54f7565cfb605ff85a5dff6f65ff9576ff8c72ffffffffffffffac88ff9576ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576%
-  e83b53d42148da294bdc2c4ce23450df2f4ede2e4dd42248d42248cd1b43d52349d62449d7254ad72549dc2c4ce73a52%
-  e83a53e23450ec3f55e93c53ec3f55f5535bf5535bfd6561fc6260ff7e6cff846eff8c72ff8c72ff9f7dffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffa5e5fd52349d32047d9284bdc2b4cd8274ad7264ace1c44c6163dc5153dc9183fc8183f%
-  ce1c44d11f46d21f47d42148da294bdc2c4dde2e4de2324fe53651f24a59f24a59fc6260fd6561ff6f65ff7367ff846e%
-  ffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88e43651c3143bd32047de2d4dd9284bd52248c6163d%
-  c01239bf1138c01138be1037c2133bc5163dc91840cc1b42cb1a42d32048cf1d45d62449e23450eb3e54f34e5af95c5e%
-  fd6561ff7869ff7e6cffffffff9576ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffd6561c91840bb0e35%
-  d21f47d21f47d62449c91840c9183fc91840c6163dc3143bc3143bc7173ec7173ec91840c91840cc1a42cf1d45d22047%
-  de2e4de53751ee4256f5515bf95c5eff9f7dffac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffde2e4dbb0e35b2072dc8183fd01d45d52248cd1b43c4143cc3143b%
-  bc0f36b90d33bf1138c4143cc3143bce1c44d32047d62449df2f4ee43651ec3f55f6545cff7e6cff7367ff9576ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffad0528c01239c01238c5163dc11239b80c33b3082eb40930b3082fb4092fba0d34bc0f36c1133acb1a41d72549%
-  e33450ec4055f24a59f95c5eff6b63ff6b63ff7e6cffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8e0104a4041d9b0313990211980210%
-  96020d97020ea1041ba90524b2082ebd1037c6163dd42248e53651f7565cff7e6cff9f7dffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffdc2b4c%
-  f04757ea3d54e0314fe0304ee73952dc2c4ce43551e23350ea3d54ef4457fb605fff6b63ff9f7dff9576ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffff8b0000f85a5dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff6cc78c5ab5896cc78c67c28b5ab58972cd8d5eb98a67c28b72cd8d62bd8bffffff9cea9c79d48d%
+  79d48d62bd8b72cd8d9cea9c6cc78c79d48d79d48d85de9172cd8d85de9172cd8d79d48d9cea9c85de9172cd8d72cd8d%
+  72cd8d79d48d72cd8d85de9172cd8dffffff85de9179d48d85de9179d48d79d48d79d48d67c28b85de9185de91ffffff%
+  85de919cea9c85de91ffffff67c28b9cea9cffffffffffffffffff85de9185de91ffffffffffff9cea9c9cea9c9cea9c%
+  79d48d9cea9cffffff9cea9cffffffffffff85de919cea9c85de91ffffff85de919cea9c85de9179d48d5ab58962bd8b%
+  67c28b4da9874da98756b289233281ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffff85de919cea9c%
+  ffffffffffff9cea9c9cea9cffffff9cea9c85de91ffffff85de91228b82ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffff9cea9c9cea9c9cea9c9cea9cffffff9cea9c85de91208a82ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c9cea9c85de91%
+  72cd8d85de9185de911e8982ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff79d48dffffff85de91ffffff%
+  9cea9cffffff9cea9c85de9185de9179d48d85de919cea9c1e8582ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffff9cea9c9cea9c9cea9cffffff85de9172cd8d79d48d85de9185de9185de91ffffffffffff1f8a82ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffff67c28b9cea9c9cea9c67c28b85de91%
+  85de9179d48d1f7c82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de91ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff9cea9cffffff9cea9c9cea9cffffffffffff79d48d%
+  9cea9c6cc78c9cea9c9cea9c9cea9c9cea9c79d48d1e8982ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff9cea9c9cea9cffffffffffff9cea9cffffff9cea9c85de919cea9c85de919cea9c9cea9c%
+  85de91ffffffffffffffffff9cea9c9cea9c9cea9c85de9179d48d9cea9c9cea9c9cea9c228b82ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff79d48d%
+  9cea9cffffff85de9185de919cea9c9cea9c85de9185de9179d48dffffff85de9179d48dffffff79d48dffffff85de91%
+  9cea9c1f7881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c9cea9c85de9185de919cea9c72cd8d67c28b%
+  79d48dffffff79d48d79d48d6cc78c79d48d1f7481ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffff85de919cea9c85de9185de91ffffff85de9185de9172cd8d9cea9cffffff79d48d85de91%
+  85de9172cd8dffffff79d48dffffff72cd8d9cea9cffffffffffff72cd8d79d48d1f7381ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff9cea9cffffffffffff85de9185de919cea9c%
+  ffffff9cea9c79d48dffffff9cea9c79d48d9cea9c79d48d9cea9c85de916cc78c9cea9c72cd8d6cc78c72cd8d72cd8d%
+  216881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffffffffffffffff%
+  9cea9c9cea9cffffff9cea9cffffff9cea9c79d48d85de919cea9c85de919cea9c9cea9c85de919cea9c9cea9c85de91%
+  85de9179d48d85de9172cd8d9cea9c206e81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff9cea9c79d48d9cea9c9cea9c%
+  ffffff85de9172cd8d9cea9c85de919cea9c6cc78c9cea9c6cc78c53af88206e81ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff85de91ffffffffffff9cea9c9cea9c9cea9c85de91ffffff72cd8d%
+  9cea9cffffffffffff85de91ffffff85de9185de919cea9c72cd8d72cd8dffffff79d48d62bd8b5eb98a72cd8d206a81%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9c9cea9c9cea9cffffff%
+  ffffff9cea9cffffff9cea9cffffff85de919cea9c85de9185de919cea9cffffff85de9185de9167c28b79d48d85de91%
+  79d48d62bd8b62bd8b5ab589216881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff%
+  9cea9cffffffffffffffffff85de91ffffff9cea9cffffffffffff9cea9c85de9185de9185de9185de9185de91ffffff%
+  85de9179d48d72cd8d79d48d79d48d62bd8b67c28b3b9c854da987216781ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  9cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffff85de91ffffffffffff72cd8d85de919cea9c79d48d%
+  9cea9c79d48d72cd8d85de9185de9185de9172cd8d79d48d5ab5896cc78c5ab58956b28950ac8850ac88226281ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffff85de9185de9172cd8d85de91ffffff9cea9c79d48d67c28b6cc78c6cc78c53af8856b289%
+  53af883e9d854da987206b81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff79d48dffffff9cea9cffffff9cea9c%
+  ffffffffffff79d48dffffff9cea9c9cea9c85de91ffffff9cea9c72cd8dffffff79d48d9cea9c9cea9c9cea9c5eb98a%
+  5ab58967c28b53af8853af88409f864aa78753af8845a286226481ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c79d48d9cea9c85de91ffffff85de91%
+  85de9185de9179d48d67c28b72cd8d79d48d5ab58956b28956b2894aa78750ac8856b28943a186206e81ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c85de9185de919cea9c9cea9c%
+  ffffffffffff85de9185de9185de919cea9c85de9179d48d5ab58972cd8d67c28b56b28953af885ab58931958453af88%
+  43a1865ab589206981ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9cffffffffffff%
+  9cea9c9cea9c85de919cea9c9cea9c79d48d72cd8d79d48d9cea9c79d48d6cc78c79d48d72cd8d6cc78c48a5864aa787%
+  48a586409f864aa7873e9d8543a18653af884da987206b81ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff85de91ffffffffffff%
+  ffffff79d48dffffff9cea9cffffffffffff9cea9c9cea9c9cea9c72cd8d85de9172cd8d9cea9c72cd8d6cc78c62bd8b%
+  67c28b50ac8850ac8850ac8848a58650ac8848a58656b28943a18650ac884aa78767c28b1f7881ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff85de919cea9c79d48d9cea9c9cea9cffffff9cea9cffffff85de9167c28b79d48d%
+  5eb98a9cea9c62bd8b62bd8b53af8856b2894da98750ac885eb98a53af884da98753af8843a186409f8653af885ab589%
+  56b2891e8282ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c9cea9c9cea9cffffffffffffffffffffffff9cea9cffffff85de919cea9c9cea9c85de9179d48d%
+  ffffff79d48d9cea9c72cd8d6cc78c79d48d6cc78c5ab5896cc78c6cc78c5eb98a43a1864aa7874da987409f863e9d85%
+  50ac885eb98a5ab58953af8867c28b6cc78c248d83ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff9cea9cffffff9cea9cffffff9cea9cffffff%
+  9cea9c85de9179d48dffffffffffff72cd8d9cea9c79d48d79d48d79d48d79d48d79d48d85de9167c28b6cc78c53af88%
+  62bd8b72cd8d53af8856b2895eb98a62bd8b72cd8d6cc78c6cc78c79d48d85de911e8482ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9c%
+  ffffff9cea9c9cea9cffffffffffffffffff79d48d85de9172cd8d79d48d85de916cc78c9cea9c79d48d72cd8d9cea9c%
+  67c28b67c28b72cd8d72cd8d56b2896cc78c5ab58962bd8b5eb98a85de9179d48d67c28b6cc78c85de9172cd8d72cd8d%
+  208a82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff9cea9cffffff9cea9c85de919cea9c9cea9c85de9179d48d6cc78c85de919cea9c72cd8d9cea9c%
+  79d48d79d48d85de916cc78c72cd8d67c28b53af885ab5894da98779d48d72cd8d6cc78c67c28b79d48d85de9179d48d%
+  ffffff72cd8d9cea9c9cea9c9cea9c2e9384ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9cffffff72cd8dffffff85de9179d48d%
+  72cd8d85de919cea9c9cea9c85de916cc78c62bd8b85de9167c28b67c28b5eb98a5ab58950ac8867c28b53af8853af88%
+  79d48d72cd8d85de916cc78cffffff85de9185de9185de919cea9cffffff1e8582ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de9185de91%
+  ffffff85de9179d48d85de919cea9c9cea9c79d48d72cd8d85de9185de916cc78c53af8856b28950ac885eb98a45a286%
+  53af885ab5896cc78c67c28b62bd8b56b2896cc78c85de9185de916cc78c72cd8d85de9172cd8dffffff85de91319584%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9c85de9167c28b72cd8d79d48d72cd8d6cc78c72cd8d72cd8d%
+  50ac8867c28b4da9876cc78c62bd8b50ac8845a28645a2865ab58967c28b85de916cc78c79d48d85de9179d48d9cea9c%
+  9cea9c72cd8d79d48d85de91268e83ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff85de91ffffffffffffffffff9cea9c9cea9c9cea9c85de9185de9179d48d72cd8d85de91%
+  72cd8d5eb98a72cd8d53af885eb98a56b2894aa7874da98753af8843a18650ac883e9d855ab58953af885ab58962bd8b%
+  72cd8d79d48d72cd8d79d48d9cea9cffffff9cea9c9cea9c85de912a9183ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de91ffffff9cea9c9cea9c%
+  72cd8d62bd8b85de9185de9145a28662bd8b53af8850ac885eb98a48a58645a2863e9d853799853b9c85409f864da987%
+  4aa7875ab5894da9875ab58956b2896cc78c72cd8d85de9179d48d9cea9c9cea9c9cea9c79d48d9cea9c248d83ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffff9cea9c%
+  79d48d9cea9c9cea9c5eb98a6cc78c5eb98a53af885ab5894aa78750ac8845a2865ab589409f8656b28945a28643a186%
+  3e9d852e9384399a8535988456b289409f8648a5865ab58956b28967c28b72cd8d72cd8d9cea9c85de9185de9172cd8d%
+  ffffff72cd8d6cc78c2c9283ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff%
+  9cea9cffffffffffffffffff9cea9c9cea9c9cea9c79d48d79d48d67c28b72cd8d5eb98a45a28662bd8b43a1864aa787%
+  4aa78743a18643a1864da9873b9c8548a586409f8650ac8848a5864da98756b28962bd8b67c28b72cd8d50ac886cc78c%
+  9cea9c9cea9c85de919cea9c79d48d85de9179d48d6cc78c409f86ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de919cea9cffffffffffff6cc78c72cd8d67c28b6cc78c67c28b%
+  5ab5894aa78753af8856b2894da98745a2864aa78743a186409f8648a58650ac8853af884aa78750ac8853af8856b289%
+  5ab5896cc78c67c28b85de9172cd8d79d48d85de919cea9c79d48d79d48d9cea9c85de919cea9c2f9484ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff85de916cc78cffffff%
+  6cc78c79d48d72cd8d62bd8b67c28b5eb98a5eb98a48a5864da987409f864aa7874aa78745a28653af884da9874aa787%
+  62bd8b56b28953af885eb98a62bd8b72cd8d79d48d67c28b79d48d79d48d85de9185de9185de9172cd8d72cd8d62bd8b%
+  6cc78c79d48d278f83ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9cffffff9cea9c85de9172cd8d79d48d6cc78c5eb98a5ab58967c28b45a2864da98753af8850ac884da9874aa787%
+  45a28645a28645a2865ab58950ac8872cd8d50ac8867c28b5ab5896cc78c72cd8d62bd8b72cd8d79d48d85de91ffffff%
+  6cc78c72cd8d85de919cea9c85de916cc78c85de91379985ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffff9cea9c79d48d9cea9c9cea9c79d48d6cc78c6cc78c67c28b5eb98a4aa78753af8856b289%
+  4da98750ac886cc78c4aa78772cd8d67c28b4aa7875ab58962bd8b72cd8d62bd8b5ab5896cc78c5ab58967c28b6cc78c%
+  79d48d79d48d79d48d79d48d79d48d6cc78c6cc78c79d48d6cc78c79d48d79d48d85de912e9384ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffff85de9179d48dffffff79d48d85de916cc78c53af88%
+  3e9d855ab5893e9d8545a2865eb98a4da98748a5865eb98a53af8862bd8b62bd8b67c28b67c28b6cc78c5eb98a79d48d%
+  67c28b67c28b72cd8d6cc78c6cc78c79d48d62bd8b62bd8b72cd8d72cd8d85de916cc78c79d48d62bd8bffffff79d48d%
+  79d48d1e8582ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff85de9185de919cea9c9cea9c%
+  85de9179d48d85de9172cd8d53af8850ac8850ac884da9875eb98a5eb98a62bd8b62bd8b50ac8856b28956b2895eb98a%
+  67c28b6cc78c5eb98a62bd8b6cc78c62bd8b62bd8b6cc78c85de915eb98a72cd8d72cd8d72cd8d79d48d85de9179d48d%
+  85de9172cd8d79d48d79d48d85de9185de91319584ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff85de919cea9c%
+  9cea9c85de91ffffff9cea9c9cea9c9cea9c85de9172cd8d6cc78c67c28b79d48d43a1865ab58956b28956b28962bd8b%
+  4da98750ac8853af8856b28950ac8856b2896cc78c67c28b79d48d85de9172cd8d79d48d72cd8d62bd8b72cd8d67c28b%
+  72cd8d9cea9c85de919cea9c9cea9c79d48d79d48d79d48d72cd8d79d48d9cea9c359884ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9c9cea9cffffffffffff9cea9c72cd8d85de9172cd8d5eb98a6cc78c6cc78c67c28b62bd8b72cd8d%
+  4da98767c28b5eb98a4aa78762bd8b67c28b5eb98a67c28b5eb98a62bd8b72cd8d67c28b72cd8d9cea9c72cd8d62bd8b%
+  79d48d5eb98a6cc78c5eb98a5eb98a67c28b72cd8d9cea9c9cea9c62bd8b6cc78cffffff79d48d79d48d85de9179d48d%
+  2c9283ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c85de919cea9c72cd8d6cc78c79d48d79d48d79d48d%
+  62bd8b56b2896cc78c62bd8b67c28b67c28b4aa7875eb98a67c28b79d48d72cd8d79d48d72cd8d72cd8d79d48d5eb98a%
+  5ab5895ab5895eb98a72cd8d79d48d79d48d85de9167c28b6cc78c67c28b67c28b6cc78c9cea9c79d48d79d48d85de91%
+  72cd8d85de91ffffff9cea9c79d48d268e83ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff85de91ffffff85de91ffffffffffffffffff9cea9cffffff85de919cea9c85de91%
+  85de916cc78c6cc78c72cd8d5eb98a5ab5899cea9c56b28962bd8b62bd8b72cd8d85de9185de9167c28b67c28b72cd8d%
+  72cd8d79d48d53af889cea9c62bd8b72cd8d9cea9c67c28b79d48d6cc78c67c28b72cd8d67c28b72cd8d5eb98a9cea9c%
+  72cd8d72cd8d62bd8b72cd8d85de9179d48d9cea9c85de919cea9c6cc78c2e9384ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff9cea9c%
+  9cea9c6cc78c79d48d72cd8d79d48d85de9185de916cc78c67c28b5eb98a67c28b62bd8b67c28b9cea9c79d48d5ab589%
+  79d48d67c28b6cc78c79d48d67c28b67c28b67c28b6cc78c67c28b72cd8d72cd8d62bd8b85de919cea9c85de9185de91%
+  72cd8d79d48d6cc78c79d48d62bd8b72cd8d5ab5896cc78c79d48d6cc78c79d48d9cea9c6cc78c85de919cea9c2c9283%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de91ffffff9cea9c%
+  ffffffffffffffffff85de919cea9c9cea9cffffff9cea9c72cd8d6cc78c85de9172cd8d72cd8d67c28b62bd8b62bd8b%
+  72cd8d5ab5896cc78c67c28b5ab58967c28b72cd8d6cc78c4aa78767c28b56b2899cea9c6cc78c79d48d6cc78c72cd8d%
+  79d48d72cd8d62bd8b85de9185de916cc78c72cd8d85de9172cd8d72cd8d79d48d6cc78c6cc78c79d48d79d48d85de91%
+  79d48d85de9167c28b85de912e9384ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff9cea9c79d48dffffff85de919cea9cffffff9cea9c85de9172cd8d79d48d9cea9c72cd8d%
+  79d48d5eb98a5eb98a62bd8b79d48d72cd8d79d48d72cd8d67c28b6cc78c53af8862bd8b5eb98a9cea9c5ab58967c28b%
+  67c28b67c28b6cc78c67c28b6cc78c72cd8d72cd8d62bd8b79d48d6cc78c6cc78c72cd8d6cc78c67c28b72cd8d79d48d%
+  79d48d79d48d79d48d9cea9c79d48d72cd8d9cea9c6cc78cffffff43a186ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff85de91ffffffffffffffffff79d48d79d48dffffff6cc78c85de919cea9c%
+  62bd8b79d48d67c28b53af8862bd8b53af885eb98a50ac8879d48d5eb98a5eb98a5eb98a6cc78c79d48d48a58667c28b%
+  4aa7875eb98a53af886cc78c5ab5896cc78c72cd8d50ac8872cd8d62bd8b6cc78c5ab589ffffff85de9172cd8d6cc78c%
+  67c28b62bd8b79d48d79d48d72cd8d79d48d72cd8d85de9167c28b6cc78c85de9185de9172cd8d9cea9c43a186ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c85de91ffffffffffff9cea9c%
+  79d48dffffff79d48d72cd8d9cea9c5eb98a62bd8b79d48d4da98756b28953af886cc78c6cc78c6cc78c5ab58962bd8b%
+  5ab58972cd8d85de9167c28b6cc78c50ac8856b2896cc78c62bd8b67c28b67c28b85de9162bd8b6cc78c67c28b6cc78c%
+  72cd8d6cc78c79d48d85de9179d48d5ab58985de916cc78c85de9167c28b9cea9c79d48d79d48d72cd8d72cd8dffffff%
+  9cea9c9cea9c85de912f9484ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c79d48d6cc78cffffff79d48d79d48d79d48d9cea9c6cc78c6cc78c67c28b56b2895eb98a53af8862bd8b5ab589%
+  67c28b62bd8b67c28b62bd8b6cc78c9cea9c6cc78c5eb98a79d48d50ac8862bd8b5eb98a5ab58962bd8b62bd8b6cc78c%
+  6cc78c9cea9c5eb98a72cd8d6cc78c72cd8d5eb98a9cea9c6cc78c67c28b6cc78c62bd8b62bd8b6cc78c6cc78c79d48d%
+  85de9172cd8d9cea9cffffff9cea9c79d48d6cc78c79d48d3e9d85ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9c9cea9cffffffffffffffffff9cea9c9cea9c79d48dffffff79d48d72cd8d79d48d9cea9c48a586%
+  6cc78c5eb98a67c28b6cc78c85de915ab5895eb98a79d48d85de9179d48d62bd8b62bd8b50ac885eb98a4aa7876cc78c%
+  53af8879d48d9cea9c5eb98a67c28b62bd8b67c28b79d48d79d48d62bd8b5ab5896cc78c5ab58979d48d62bd8b67c28b%
+  6cc78c6cc78c56b28967c28b79d48d72cd8d85de919cea9c79d48d62bd8b85de919cea9c79d48d339684ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff85de919cea9c9cea9cffffff85de91ffffff85de91ffffff85de9179d48d6cc78c79d48d72cd8d%
+  79d48d85de916cc78c6cc78c67c28b85de9172cd8d9cea9c62bd8b67c28b85de9185de9179d48d6cc78c72cd8d5ab589%
+  5eb98a56b2895eb98a6cc78c56b28953af886cc78c72cd8d56b28979d48d85de9179d48d62bd8b6cc78c79d48d6cc78c%
+  6cc78c62bd8b72cd8d62bd8b5ab58967c28b72cd8d79d48d79d48d72cd8d79d48d9cea9c79d48d85de9172cd8d6cc78c%
+  79d48d9cea9c399a85ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff85de9172cd8dffffff9cea9cffffff85de91%
+  9cea9c72cd8d85de9179d48d79d48d6cc78c6cc78c67c28b62bd8b72cd8d62bd8b85de916cc78c67c28b79d48d85de91%
+  72cd8d9cea9c85de916cc78c5eb98a56b2896cc78c62bd8b5ab5895eb98a79d48d6cc78c5eb98a6cc78c72cd8d67c28b%
+  53af8856b28979d48d67c28b67c28b9cea9cffffff6cc78c67c28b72cd8d53af885ab58967c28bffffff72cd8d6cc78c%
+  79d48d6cc78c79d48d72cd8d79d48dffffff9cea9c2f9484ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c%
+  ffffff72cd8d9cea9c85de919cea9c85de9185de9167c28b85de9162bd8b6cc78c67c28b85de915eb98a79d48d62bd8b%
+  67c28b72cd8d56b2896cc78c62bd8b85de9167c28b6cc78c72cd8d5eb98a67c28b85de915eb98a9cea9c62bd8b6cc78c%
+  ffffff72cd8d72cd8d72cd8d6cc78cffffff62bd8b79d48d5eb98a5eb98a79d48d50ac8867c28b6cc78c9cea9c85de91%
+  72cd8d79d48d79d48d85de915ab58979d48d9cea9c62bd8b6cc78c85de9179d48d79d48d3b9c85ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff5eb98a67c28b79d48dffffff72cd8d72cd8d67c28b%
+  67c28b62bd8b67c28b6cc78c56b2895eb98a62bd8b62bd8b62bd8b5eb98a79d48d6cc78c6cc78c6cc78c72cd8d53af88%
+  56b28962bd8b6cc78c72cd8d79d48d79d48d6cc78c79d48d67c28b6cc78c6cc78c6cc78c5eb98a79d48d67c28b56b289%
+  6cc78c72cd8d85de9172cd8d79d48d6cc78c79d48d85de9167c28b6cc78c85de9185de9172cd8d62bd8b79d48d9cea9c%
+  9cea9c278f83ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9c79d48dffffff9cea9c79d48d85de9179d48d79d48d%
+  85de9185de9172cd8d9cea9c79d48d62bd8b62bd8b62bd8b50ac8862bd8b56b28962bd8b4aa7876cc78c62bd8b72cd8d%
+  67c28b72cd8d6cc78c67c28b72cd8d5ab58967c28b79d48d79d48d79d48d85de916cc78c62bd8b6cc78c79d48d62bd8b%
+  43a1866cc78c62bd8b62bd8b6cc78c6cc78c62bd8b6cc78c5ab58972cd8d9cea9c6cc78c85de919cea9c72cd8d72cd8d%
+  85de9185de9179d48d85de919cea9cffffff45a286ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff85de91ffffff9cea9cffffff%
+  85de916cc78c72cd8d85de915ab58979d48d5eb98a53af8867c28b6cc78c62bd8b56b2895eb98a50ac8843a18643a186%
+  56b2895eb98a5eb98a67c28b62bd8b72cd8d72cd8d6cc78c72cd8d72cd8d6cc78c6cc78c72cd8d6cc78c67c28b56b289%
+  5ab5895eb98a79d48d62bd8b5ab58979d48d79d48d67c28b6cc78c5eb98a72cd8d67c28b72cd8d85de9172cd8d79d48d%
+  79d48d79d48d6cc78c85de9179d48d72cd8d9cea9c72cd8d72cd8d72cd8d9cea9c56b289ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9c9cea9c72cd8dffffff9cea9c79d48d53af8879d48d5ab58979d48d5eb98a67c28b5ab5895ab589%
+  409f86409f8650ac8848a5865eb98a62bd8b5ab5895ab5896cc78c53af886cc78c79d48d72cd8d53af8862bd8b5eb98a%
+  67c28b85de9167c28b79d48d72cd8d72cd8d72cd8d62bd8b85de916cc78c56b2895ab5895eb98a62bd8b4aa7876cc78c%
+  56b28972cd8d85de9179d48d67c28b67c28b6cc78c5eb98a67c28b67c28b79d48d72cd8d72cd8d85de916cc78c85de91%
+  48a586ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c79d48d79d48d6cc78c72cd8d62bd8b79d48d5eb98a%
+  6cc78c67c28b5ab5894aa787379985359884359884399a8545a2865ab58962bd8b53af8862bd8b5ab5896cc78c67c28b%
+  6cc78c5ab58967c28b6cc78c5eb98a67c28b85de919cea9c6cc78c85de916cc78c67c28b67c28b6cc78c79d48d50ac88%
+  50ac8879d48d5eb98a62bd8b62bd8b72cd8d6cc78c6cc78c67c28b9cea9c67c28b85de9185de916cc78c72cd8d85de91%
+  67c28b72cd8d79d48d79d48dffffff53af88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffff85de91ffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffff85de91ffffffffffff85de9179d48dffffff79d48d%
+  79d48d5eb98a6cc78c62bd8b48a58648a58653af8848a5862f9484399a853598843195844da9873e9d8567c28b4da987%
+  5ab58953af8862bd8b72cd8d5eb98a6cc78c79d48d72cd8d79d48d6cc78c6cc78c56b2895eb98a85de915ab58972cd8d%
+  5ab58962bd8b6cc78c6cc78c5eb98a67c28b67c28b62bd8b72cd8d6cc78c62bd8b85de9179d48d6cc78c62bd8b6cc78c%
+  9cea9c85de919cea9c72cd8d72cd8d79d48d6cc78c79d48d72cd8d79d48d5eb98affffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de91ffffff85de919cea9c%
+  ffffffffffffffffff9cea9c9cea9c9cea9cffffff9cea9cffffff85de919cea9cffffff85de9185de9179d48d9cea9c%
+  ffffff85de9172cd8dffffff72cd8d62bd8b72cd8d72cd8d48a58643a1865ab58948a58643a1862f948448a586399a85%
+  2c92834aa78743a1864da98767c28b56b28956b28962bd8b67c28b5eb98a85de915eb98a67c28b6cc78c5ab58962bd8b%
+  62bd8b79d48d53af8862bd8b62bd8b67c28b67c28b5ab5895eb98a5eb98a72cd8d6cc78c56b2899cea9cffffff6cc78c%
+  62bd8b67c28b9cea9c79d48d79d48dffffffffffff9cea9c9cea9c9cea9c85de9179d48d9cea9cffffff9cea9c62bd8b%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91%
+  67c28b79d48d72cd8d4da9875eb98a85de915eb98a79d48d85de9179d48d62bd8b72cd8d85de9172cd8dffffff72cd8d%
+  62bd8b72cd8d85de9179d48d79d48d79d48d72cd8d79d48d79d48d50ac8872cd8d85de9162bd8b4aa78743a1864da987%
+  379985359884238c83399a853195842990833396843b9c8543a1864aa78750ac884aa78767c28b62bd8b67c28b53af88%
+  62bd8b67c28b5eb98a5eb98a53af8853af8879d48d56b2895ab5894da98762bd8b56b2895eb98a5ab58962bd8b62bd8b%
+  62bd8b6cc78c5eb98a9cea9c53af885eb98a72cd8d85de916cc78c79d48d9cea9c85de9179d48d79d48d85de91ffffff%
+  ffffff79d48d79d48dffffff56b289ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff5eb98a53af885eb98a45a2864da98745a28645a28656b28948a5864da98753af88379985%
+  4da98748a58650ac885eb98a5eb98a53af886cc78c85de916cc78c5eb98a5eb98a6cc78c56b28953af8853af8850ac88%
+  5eb98a56b28953af882c9283359884238c833598842990832c9283248d83278f832c928335988448a58645a28645a286%
+  5eb98a53af886cc78c50ac8853af8867c28b4da9876cc78c67c28b50ac8850ac8862bd8b53af885ab58945a28656b289%
+  62bd8b72cd8d72cd8d5eb98a62bd8b79d48d72cd8d6cc78c6cc78c79d48d6cc78c79d48d6cc78c72cd8d85de9167c28b%
+  85de919cea9c79d48d85de9179d48d85de919cea9c9cea9c9cea9c62bd8bffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c53af88399a85409f863e9d853396842a91832a9183%
+  3e9d853e9d853799853e9d8548a5863195843195843396844da987359884399a8550ac885eb98a53af884da9875ab589%
+  4da98748a5864da9873e9d8556b2893598843e9d85399a853195842e9384238c83278f83248d83208a82268e83278f83%
+  1e8682299083228b82379985399a853b9c853e9d856cc78c6cc78c5ab58945a2864da98743a1863b9c8550ac884da987%
+  50ac884da98753af884aa78756b2895eb98a6cc78c5eb98a62bd8b79d48d6cc78c85de9185de916cc78c79d48d62bd8b%
+  9cea9c62bd8b79d48d79d48d72cd8d79d48d72cd8d85de919cea9c79d48d72cd8d9cea9cffffff85de91409f86ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c56b2894da9873b9c85%
+  399a852a9183278f833e9d8548a5863799853b9c8545a2863e9d85208a821f75812168811f7681268e832a918345a286%
+  37998543a1865eb98a399a8548a58656b28943a186399a8543a1864aa787399a852a9183248d831e83821e88821e8882%
+  2c92831e84821e8282228b821e89821e8982228b82208a8243a1862990832a91832a9183319584359884399a8553af88%
+  35988437998548a58650ac884da9873b9c855ab58956b2894da98750ac8856b2894da9875ab58967c28b56b28985de91%
+  85de9162bd8b5eb98a79d48d62bd8b67c28b72cd8d6cc78c62bd8b85de9179d48d6cc78c72cd8d79d48d79d48d9cea9c%
+  ffffff85de91ffffff1f8182ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  9cea9c48a5864da98745a28645a28656b28953af885ab5894da98767c28b50ac8867c28b53af88379985206d81284981%
+  264181226281206f811f7c822f94843b9c85409f862e93843598843b9c8553af8848a5863b9c853b9c851f8a82208a82%
+  1e83821f76811f7c821e8282248d831e83821f81821e82821e82821e8882359884208a82268e834aa787359884268e83%
+  238c83379985409f862c92833598844aa78743a1865ab58953af8853af8848a58653af886cc78c5eb98a67c28b4aa787%
+  53af8867c28b56b2896cc78c5eb98a62bd8b79d48d72cd8d85de9172cd8d79d48d67c28b79d48d72cd8d67c28b72cd8d%
+  85de919cea9c67c28b79d48d85de919cea9c67c28b85de911f8a82ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff67c28b299083409f86399a853195843396845eb98a4aa78750ac8850ac885ab589%
+  50ac8850ac8856b2891f7e822069812069811e84823396842f9484379985268e83339684238c833e9d8537998543a186%
+  299083248d831e82821e86821f7a82206b812070811f7a821f80821f7e82228b821e83821f7e821e86821e82821f7e82%
+  299083299083248d833e9d852a91832a91833195843396842a918333968448a58648a58637998548a5863b9c8548a586%
+  5eb98a5eb98a5ab58967c28b53af8867c28b6cc78c56b2895eb98a62bd8b72cd8d62bd8b5eb98a67c28b62bd8b72cd8d%
+  5ab58962bd8b6cc78c79d48d6cc78c72cd8d6cc78cffffff79d48d9cea9c85de919cea9c85de912f9484ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff62bd8b228b821e8582278f832c92831e8282%
+  1f8a821e89822f94844aa7873799853799853396843396841f8a822e9384409f862f94844da98737998545a2863b9c85%
+  3b9c853b9c852c9283208a821e8582208a821f7e821f7c821f7a82206f811f74811f80821f7c821e8282228b821f7f82%
+  1e86821e8982208a821f8a821e8582208a821e8582278f83238c832a9183319584379985268e832e9384248d8343a186%
+  48a58645a2864da987409f8653af8848a58643a18643a1865ab58956b28953af8867c28b56b28956b28956b28962bd8b%
+  67c28b50ac8872cd8d5eb98a5eb98a5eb98a67c28b72cd8d72cd8d67c28b85de9185de9172cd8d79d48d9cea9c85de91%
+  79d48dffffff228b82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c56b289%
+  1f8a821e8282248d831e83823396842a91832f94844aa7873b9c85409f861e87822262812558812654812068811f8182%
+  31958443a186268e833e9d853799852a91833598842e93842a91831e88821f7c821e82821f7f821f78811f75811f7f82%
+  1f72811f7d821f81821f7f821e86822e93841e8382238c832990831e87821f8182268e831f8a82248d832c92832a9183%
+  1e88823e9d852e9384278f833598842f948448a5863b9c8543a1863b9c85399a8545a2863e9d85399a854da987409f86%
+  72cd8d67c28b79d48d5ab58967c28b62bd8b79d48d67c28b5eb98a79d48d62bd8b72cd8d62bd8b6cc78c72cd8d6cc78c%
+  6cc78c79d48d85de9185de9179d48d79d48d85de911f7f82ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c228b8243a18635988450ac8862bd8b48a5866cc78c4aa7876cc78c67c28b79d48d4aa787206f81%
+  265481284981274e812166811f7f821e888229908343a186339684339684248d83278f83238c831e88821f78811f7b82%
+  1f80821e87821f81821f7e821f80821f79811e88821f7a82228b822e9384248d832990832c92832a9183208a82238c83%
+  359884278f83278f83228b82399a853b9c853598843195843b9c854aa78753af883b9c854da9874da9874aa7873e9d85%
+  56b28948a5865ab58956b2895ab58967c28b56b28985de915ab58972cd8d79d48d79d48dffffff9cea9c9cea9c72cd8d%
+  79d48d67c28b9cea9c85de9185de9185de916cc78c72cd8d9cea9c72cd8d85de9179d48d1f7881ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff6cc78c2262812261811f7a821f7f821f8a82228b823195843799855eb98a%
+  45a28653af884aa7873598841e85821f8182206b81265381235f81216481206d811f7c821e86821e82821f7b82206c81%
+  1f76811f81821f75811f73812071811f75811f7e821f7c821e87821f81821e87821e88821e8582359884248d83248d83%
+  248d832a9183299083379985399a852f94843b9c852e93844da987409f86399a8537998548a5863e9d8556b28962bd8b%
+  5eb98a67c28b56b28972cd8d62bd8b5ab58962bd8b5eb98a85de919cea9c9cea9c67c28b9cea9c85de9179d48d72cd8d%
+  ffffff85de91ffffffffffff9cea9c9cea9c79d48d72cd8d9cea9c9cea9c9cea9c85de919cea9c79d48d9cea9c85de91%
+  9cea9c409f86ffffffffffffffffffffffffffffffffffffffffffffffff5eb98a1f7c822748812360812168811f7281%
+  1f7a821e8582248d832a91832e9384409f86409f86208a821f78811f7b821f7481255881284c81255681216481206a81%
+  1f7f822070811e82821f7c82207181206e811f7c821f7a821f7a821f81821f76811f77811f7d82228b821f7b82208a82%
+  299083238c83268e832f94841e86821f7981208a82238c83248d83278f8348a586399a853799853b9c8562bd8b4da987%
+  53af885ab5895eb98a5eb98a62bd8b72cd8d67c28b79d48d79d48d9cea9c67c28b79d48d79d48d85de9179d48d85de91%
+  9cea9c9cea9c9cea9c72cd8d9cea9cffffff72cd8dffffff79d48dffffffffffff9cea9c9cea9cffffffffffff9cea9c%
+  ffffffffffff9cea9c9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff216681%
+  2166811f75811e8382238c833799852a918353af884da987399a85238c831f73811f7a82216681255981255681216781%
+  206e812070811f77811f7c821f7d821e82821e84821f7f821e83821f7d821f7d821f74811f7b821f7f821f7f821f8a82%
+  1e85821e8682248d83208a822c92832a9183399a85248d83248d83238c8343a18643a1863e9d8548a5863e9d8550ac88%
+  56b2895eb98a62bd8b62bd8b72cd8d79d48d9cea9c79d48dffffff72cd8d79d48d85de91ffffff85de9185de9185de91%
+  85de9172cd8d9cea9c85de9172cd8d9cea9cffffff9cea9c85de91ffffff9cea9c85de919cea9c85de919cea9c85de91%
+  ffffffffffff9cea9c9cea9cffffff9cea9cffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffff67c28b265181235d81206c812071811e87822f94842f94843e9d851f7b82206b81216681216681%
+  206a81216581265481245981226481206e811e86821f74811f7a821f76811f79811f7981207081207181206f811f7881%
+  1f72811f7d821e82821e85821f7c822c9283268e832e93843195843598843598843e9d85399a853b9c8543a18643a186%
+  53af8850ac8843a18679d48d409f8650ac885ab58956b28979d48d5eb98a6cc78c72cd8d79d48d85de919cea9c9cea9c%
+  9cea9c9cea9cffffffffffff85de91ffffff9cea9cffffff9cea9c85de91ffffff9cea9c85de919cea9c9cea9c9cea9c%
+  85de91ffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff4aa7871f7b821f7f82278f83278f833b9c8548a58648a586%
+  50ac88226481265281206981228b82299083238c831e85821e82821e89821f79811f7a821e82821f7d821f72811f7b82%
+  206c81206f811f77811f72812071811f75811e88823598843396842990832f94843195844aa78750ac885ab58948a586%
+  56b28945a2863e9d854da98745a2865ab58950ac8879d48d5eb98a5eb98a5ab58967c28b79d48d85de9185de9185de91%
+  9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff1f8a822164811f7c82%
+  208a82319584409f8645a286409f863598841f8182228b822f94842e93842a91831e8982248d831f8a82228b821f8182%
+  1e83821f8a821f76811e82821f7e821f7f821e82821e84821f7c82268e83399a853799853e9d853b9c8548a58645a286%
+  5ab58948a586399a853598844aa7873e9d854da98753af885eb98a50ac884da9875ab58967c28b5eb98a72cd8d67c28b%
+  9cea9c72cd8d85de919cea9c85de9185de919cea9c72cd8d9cea9cffffffffffffffffff85de91ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  6cc78c5eb98a1e85821e8282268e8350ac8845a28650ac884aa78762bd8b1e8582206e811f7c82268e831f78811f7481%
+  1f80822990832990832e9384268e831f7d821e86821f80821e89821f8182228b821e86821e8882278f83248d83339684%
+  2f94841e8982399a852c9283399a853e9d85409f8643a1863e9d853e9d8543a1865ab58943a18656b28956b28956b289%
+  6cc78c56b2894aa78762bd8b85de9179d48d6cc78c9cea9c72cd8d9cea9c85de919cea9c79d48d9cea9c9cea9c9cea9c%
+  9cea9c85de91ffffff9cea9c9cea9c9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff409f86278f8350ac8850ac886cc78c72cd8d6cc78c67c28b79d48d48a586226181%
+  2360811f7a821e84821f72812068811e8582399a85409f861e89822e93841e84821e8282248d83228b821e82822c9283%
+  29908345a2862c9283399a8543a18650ac884aa78753af884aa7874aa78767c28b4da98767c28b62bd8b79d48d79d48d%
+  85de9172cd8d9cea9c9cea9c72cd8d85de919cea9c9cea9c9cea9cffffffffffff9cea9c85de919cea9c9cea9c85de91%
+  ffffff9cea9cffffff9cea9c9cea9cffffffffffff85de91ffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff67c28b1f78811f7c821e898256b28967c28b6cc78c%
+  62bd8b4aa7875eb98a268e83206c811e8282208a821f78811f76811f81822990832f94843598842a9183248d831e8682%
+  1e86822a91833195841f8a822a91833b9c85409f8645a28643a18650ac8879d48d72cd8d6cc78c9cea9c6cc78c85de91%
+  9cea9cffffffffffff85de91ffffffffffff9cea9cffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff207081284c81%
+  245a81206c811e82822c92832c92831f8a821f77811f79811f7281216681206b81226481245c81235f81216481216781%
+  1f72811f72812168812166812165812071812070811f72811f73811e86821e83823b9c853b9c854da9875eb98a72cd8d%
+  85de9167c28b9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff85de91208a82206a811f7a821e8482228b822990833b9c85216681274f81236081216681206a81255881%
+  226181236081216881206e81206e811f7281206e811f73811f7a821f80821e84821e8882278f83339684409f864aa787%
+  5eb98a53af885eb98a6cc78c85de919cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff6cc78c45a2863e9d85409f865eb98a67c28b5eb98a399a85206f81%
+  1f79811f8a82268e831e84821e85821e8782208a82248d832f94842f94842990832a91831f7f823e9d85409f8648a586%
+  5ab58948a58662bd8b79d48d79d48d5eb98a9cea9c9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff3e9d85206f812262811f74811f7b82%
+  1e85821f7f821f7c82206981235d81236081206c811f7681216681206e811f7481206d811f7f821f7d821f76811f7581%
+  2070811e87823e9d854aa78743a1865ab58979d48d72cd8dffffffffffff9cea9c79d48dffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d%
+  1e8482216481206e812071811f7b821f75811f7481216581216581245c812167812068812069812069812071811e8282%
+  1e83821f7b821e89821e85821e8982399a85399a8550ac884da98767c28b6cc78c72cd8d72cd8d85de91ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff48a586216681226381206d81207181206b81206a81235d81265281265281255681255581%
+  235e81226181226281216481206e811f72811f74811f7a821f7f822e93842e93844da98750ac885ab5895eb98a6cc78c%
+  ffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c1f7e82274f812263811f7481206d81216681265381%
+  284c81284a81284b81284981274e81265281255781245b81245a81226481235f812168811f7b821e888233968445a286%
+  50ac8862bd8b67c28bffffff79d48d9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff50ac88255681274581%
+  226281226281216881255681255681255781265381274f81274f81265481265481255781255681245a81235e81226381%
+  1f74811f7f82238c8337998545a28685de919cea9cffffff85de91ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff1f7481274581243981255681235f81216681245b81275081274f81%
+  274781264381284b81275081274f81235d812263812168811f75811f7e821e89823b9c8567c28b5eb98a79d48dffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff233381284c81284b81265281284d81264281243a81253d81253b81253c81264381274781274d81245981206981%
+  1f7c821f8a822e938445a28656b28956b28967c28bffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff0405801e2781141a81111681101580%
+  0d11800e13801b2481222e81243a812748812653812166811f7f823e9d8567c28b85de91ffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff207181%
+  2990831e87821f78811f77811e82822071811f7d821f7a821e8782268e834aa78756b28985de9179d48dffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff00008043a1869cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576ff9f7dff9f7dffffffffac88ff9f7d%
-  ffffffff9f7dffac88ffffffff8c72ff8c72ffac88ffac88ffac88ff9f7dff846eff846efd6561fa5e5ffe6862ff7e6c%
-  fe6862f85a5df7585df4505aef4457f04557e73952df2f4ee2324fd9284bd62449d42148d21f47d21f47cf1d44cd1b43%
-  cc1b43d11e46d21f47cc1b43c7173ed01e46ca1940cd1c43cf1d45ce1c44d52349d42248dc2c4cda2a4cde2d4dd22047%
-  d42248d8264ad7254ad7264aa00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffac88ff9f7dffffffff9f7dffffffffac88ff9f7dff9f7dffac88ffac88ffac88ff8c72ff6f65ff9f7dffac88ffac88%
-  ff9f7dff8c72ff9f7dff7e6cff9576ff9576ffffffff9f7dff9f7dffffffffac88ffac88ffac88ffffffff9f7dff9f7d%
-  ff9f7dffac88ffac88ff9f7dffac88ffffffffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
-  ffffffffffffff9576ffffffff9576ffffffffac88ffffffffffffff9576ffac88ffac88ff9576ff846eff9576ff9f7d%
-  ffac88ff8c72ffffffffac88ff9576ff9576ff846eff846eff846eff7869ff7e6cff7869ff7e6cff846eff9576ff9f7d%
-  ffac88ff846effffffff9f7dff9576ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffffac88ff8c72ffffffff9f7dff9f7dffffffff9f7dffac88ffffffff9576%
-  ff9576ffffffffac88ffffffff9f7dffac88ff9576ff7869ff9576ff9576ff846eff8c72ff6f65ff7367fd6561ff7e6c%
-  fd6561ff8c72ff846eff7869ff9f7dff846eff9f7dff9576ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffe83b53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffac88ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88%
-  ffac88ffffffffac88ffffffff846eff9f7dffffffffac88ff9576ffac88ff9f7dff8c72ff9576ff7e6cff7367f95c5e%
-  fb605ffa5e5ffb605fff7367ff7367fc6260ff7869ff7367ff7869ff7e6cff7367ff9576ff9f7dff9f7dffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffe73952ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff846eff9f7dff7e6cffffffff9f7dffffffffffffffac88ffffffffac88%
-  ff9576ffffffffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff9f7dffac88ff8c72ff7869ff8c72ff7e6c%
-  ff7869fd6561f95c5ef95c5ef7565cf7585df5515bf14958fa5e5ff85a5dfb605fff6f65ff7367ff6b63f95c5efb605f%
-  ff8c72ff8c72ffac88ffffffffac88ffffffff9f7dffffffffffffffffffffffffffac88fffffff04557ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9576ffac88ffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffff9576ff9f7dff7e6cff8c72%
-  ffac88ff7e6cff6f65ff6f65ff7869ff7367f6545cfa5e5ff7585df5535bf24b59f85a5df5535bfc6260ff7e6cfc6260%
-  f85a5df95c5ef6545cff6f65ff6f65ff9f7dff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffb605fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7d%
-  ff9f7dff9576ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ff9576ffac88ffffffff9576ffffffff8c72%
-  ff9f7dff9576ff846effac88ff8c72ff846eff7367f7585dff6b63f7585df85a5df24a59fb605fff6b63f6545cf24b59%
-  f5535bf85a5df85a5df5535bf7585dff6b63f7565cff7367ff7e6cff9f7dff9576ffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffff8c72ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ff8c72ff9576ff9f7dffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88%
-  ff9f7dffac88ffac88ffffffff9576ff8c72ff8c72ff9f7dff7e6cff7e6cf95c5eff7869ff6b63f7565cf5515bfe6862%
-  fc6260f5515bf7585df95c5ef7565cfa5e5ff85a5dfd6561f5515bf7585df7565cfd6561ff7e6cff8c72ff9f7dffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffff8c72ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff8c72ff9f7dff9576ff9f7dffac88ffac88ffffff%
-  ff9f7dffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dff9f7dffac88ff9f7dff9f7dff7367ff7367fd6561f7565c%
-  fe6862f85a5df5515bf7565cf85a5df14958f5535bf85a5dfa5e5fff846eff6b63ff7e6cf24b59fa5e5ff85a5dfd6561%
-  ff9576ff9576ff8c72ff9576ff9f7dffac88ffffffff9f7dffac88ffac88ffffffffffffffac88ffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff9576%
-  ffac88ff9576ffac88ffffffffffffff9576ff9f7dffac88ff9f7dff9f7dff8c72ff8c72ff8c72ff9576ff8c72ff7869%
-  fe6862ff6f65fc6260fa5e5ff7565cf6545cfb605ff5535bf14958ff7e6cfc6260fd6561ff6f65fc6260fe6862ff7869%
-  fe6862f7585dfc6260ff6b63ff846eff9576ff9f7dffac88ffac88ffffffffac88ff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88%
-  ffac88ff8c72ffac88ffac88ffffffffffffffac88ffffffff9f7dffac88ff9576ffffffff9f7dff9f7dff9f7dffffff%
-  ffffffff8c72ff7367ff7367ff8c72ff6f65f34e5af4505af34e5af85a5df6545cfb605ffa5e5ffc6260fb605fff846e%
-  ff6f65ff7e6cff8c72ff7e6cff7367fb605ffc6260ff6f65ff6b63ff9576ff9576ffac88ffffffffac88ffac88ffffff%
-  ffac88ffac88ffac88ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffac88ffac88ff9f7dffffffffffffff9f7dffffffffac88ffffffffffffff8c72ff9f7d%
-  ff9f7dff9576ff9576ff9f7dffac88ff846eff7e6cff8c72ff6f65fc6260f7585df7565cf85a5df4505af7565cf6545c%
-  f95c5eff7869ff7869fe6862ff846eff7367ff7869ff7367ff7367ff7869ff7e6cff6f65ff7869ff9f7dff8c72ffffff%
-  ffac88ffffffff9f7dffffffffffffffffffffffffffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ff9f7dffac88ffac88ff9f7dff9576ffac88ff9f7dff9576ff9f7dff9576ff9f7dff7367ff9576ff6f65f7565cf7585d%
-  f85a5df6545cf7585df85a5dff7367fc6260fb605ffe6862ff6f65ff9576ff8c72fc6260ff7367ff7e6cff846eff846e%
-  ff7e6cff9576ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ff8c72ffffffffac88ffffffffac88ffac88ffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffff%
-  ffffffff9f7dffac88ffac88ff9576ffac88ffffffffffffff9576ff9576ff9f7dffac88ff846eff846eff9576ff9576%
-  ff7e6cff6b63fd6561f7585df85a5dfb605ff04757f4505afd6561fc6260ff6f65ff7869ff8c72ff7869ff8c72ff6f65%
-  ff8c72fe6862ff9f7dff9576ff9576ffffffff9f7dffffffff9576ffac88ff8c72ff9576ffac88ffac88ffac88ff846e%
-  ff9f7dff9576ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7dff9576ffffffffac88ff9f7dffac88ffac88ffffffff9f7dffac88ff9576ffac88ff9f7dff9576%
-  ffac88ffffffff9f7dff7869ff9576ff7e6cff6f65f85a5dfc6260f34e5af95c5efe6862fc6260ff6f65ff7869ff846e%
-  ff6f65ff6f65ff7e6cff7e6cff7869ff6b63ff7869ff7367ff9576ff8c72ffac88ffac88ffffffff846eff7e6cff7869%
-  ff846effac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffac88ff9576ffac88ffac88ffffffff9f7dffac88ff9f7dffffffffac88ffac88ffac88%
-  ffffffff846effac88ffac88ff9f7dff9576ff8c72ff8c72ff7367fd6561ff846eff6f65fa5e5ffe6862fb605ff7565c%
-  fb605fff6f65ff846eff8c72ff6b63f95c5efc6260ff7e6cff7367ff7e6cff7e6cff846eff9576ffac88ff9576ff9f7d%
-  ff9f7dff9f7dff9f7dff7367ff6f65ff846eff9576ff9576ffffffff9576ffffffffffffffffffffac88ffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576%
-  ff9f7dffac88ffac88ff9576ff9f7dffac88ffac88ff8c72ff9576ff9576ffac88ff846eff9f7dff846eff7e6cff7869%
-  ff6b63fc6260f85a5dfb605ffd6561ff7e6cff7e6cff7869ff9f7dff6b63ff7869ff7e6cff9576ff8c72ff7367ff7367%
-  ff9576ffac88ffffffff9f7dffac88ffac88ff846eff7e6cff7869ff7869ff9f7dff9576ff9f7dffac88ff9576ffac88%
-  ff9f7dffac88ff846effffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
-  ffffffffffffffac88ffffffffffffff9576ffac88ff9576ffac88ff8c72ff9576ff9576ff7e6cff7e6cff846eff7e6c%
-  ff9f7dff9576ff6f65fd6561ff7869ff846ef95c5eff8c72ff7869ff9576ff7e6cff6f65ff7869ff9576ff7367ff9f7d%
-  ff846eff9f7dff7e6cff8c72ff9576ff9576ffffffff9f7dff9576ffffffffac88ff9576ff7869ff846eff7869ffffff%
-  ff7e6cffffffff9f7dff9576ff9f7dff7e6cf85a5df85a5dff9f7dffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ff9f7dffac88ff9576ffac88ffffffffffffffac88ffffffffac88ffac88ffac88ffac88ff7e6cff846eff9576ffffff%
-  ffac88ff9f7dff8c72ff9f7dff846eff7869ff8c72ff7367fd6561ff9576ff7e6cff6b63ff7367ff6b63ff8c72ff7869%
-  ff7e6cff8c72ff9576ff846eff7869ff7869ff9576ff9576ff9576ff9576ffac88ffac88ffffffff9f7dffffffff9f7d%
-  ff9f7dff6f65ff7e6cff9f7dffffffffffffffac88ff9f7dff7e6cff9576fd6561f6545cff6b63ffac88ffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ff9f7dffffffffffffffffffffac88ffffffff9f7dff9f7dffffffffffffffac88ffffffffffffff9576%
-  ffac88ff9f7dff7e6cff9f7dff9f7dff9576ff7e6cff9f7dffac88ff8c72ff8c72ff9f7dff7367ff7e6cff6b63ff846e%
-  ff7367fd6561ff6f65ff6f65ff7e6cff9576ff8c72ff8c72ff846eff9576ff9f7dffac88ff9f7dffac88ffffffffffff%
-  ff9576ff846eff7e6cff9576ffac88ff8c72ffffffffac88ff9f7dffac88ffac88ff7e6cfc6260fd6561ff7367f95c5e%
-  f6545cff9576ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ffac88ff9576ffffff%
-  ff8c72ff9f7dffac88ffffffff9f7dff9576ff9576ffac88ff846eff7367ff846eff7869ff7e6cff9576ff9576ff7e6c%
-  ff8c72ff6b63ff7e6cff6f65ff7869ff7e6cff7367ff7367ff8c72ff8c72ff9576ff8c72ff9f7dffac88ff8c72ffffff%
-  ffffffff9f7dff9f7dff9f7dff9f7dffffffff8c72ff8c72ff846eff9f7dff9f7dffac88ffac88ff8c72ffffffff9576%
-  ff6f65fc6260fd6561ff6f65fd6561ff8c72ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88%
-  ffffffffffffff9f7dffffffffac88ffffffff9f7dff9576ff8c72ff9f7dff7e6cff9576ff846eff9f7dff7869ff8c72%
-  ff9576ff846effac88ff9f7dff9f7dff9f7dff846eff846eff9576ff846eff9576ff9576ff9576ff7e6cff9f7dff9f7d%
-  ff8c72ff8c72ffac88ffac88ff9f7dffffffffac88ff9576ffffffff9576ff9f7dff7e6cff846eff846effac88ff9f7d%
-  ffffffffac88ffffffffac88ff9576ff6f65fd6561ff6b63ff7869ff7e6cffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ff9576ffffffff9f7dff9576ff9f7dffffffffffffff9576ffac88ffac88ffac88ff9f7d%
-  ff9576ff846eff846eff6f65ff7e6cff6b63ffac88ff7e6cff8c72ff846effffffff7869ff8c72ff9f7dff8c72ff9f7d%
-  ffac88ff7367ffac88ff9576ff846effac88ff9576ffac88ffac88ff9f7dffffffffffffffffffffac88ffffffffac88%
-  ff846eff9f7dffffffff9f7dff9f7dffac88ffac88ffffffffac88ff8c72ff9576ff846eff7e6cffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dff9f7dff8c72ffffffff9576ff9576%
-  ffac88ff9576ffffffffac88ff9576ff9f7dff9f7dff6b63ff8c72ff7869ff9576ff846eff7869ff9f7dff9f7dff846e%
-  ff9576ff846eff8c72ff846eff9576ff9576ffac88ff8c72ffac88ff9576ff9f7dffac88ffac88ffffffffac88ffac88%
-  ffffffffffffffac88ffac88ff9f7dffac88ff7e6cff9576ffac88ffac88ffac88ff9f7dffffffffffffffffffff9f7d%
-  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88%
-  ffac88ff9f7dff9f7dff9576ff9576ff9576ff9f7dffffffff9f7dff8c72ff8c72ff9f7dff9576ff8c72ff7367ffac88%
-  ff9576ff9f7dff9f7dffffffff8c72ff7e6cff8c72ff9576ff8c72ff9576ff9576ff9576ffac88ffac88ffffffffffff%
-  ff8c72ff9f7dff9576ffffffffffffff9f7dffffffff7e6cff9f7dff7e6cff9f7dffffffffac88ffffffff9f7dff9576%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffac88ffac88ffffffffffffff9f7dffffffff9f7dffffffffffffffac88ffffffff9576ffac88ffac88ff9f7d%
-  ff9576ff9576ff9f7dff9f7dffac88ffac88ff9f7dffffffff8c72ffac88ff9f7dff7367ff9576ff8c72ff9576ff846e%
-  ff7e6cff7e6cff9576ff9576ff9576ff8c72ffac88ffffffffffffffac88ff8c72ff9f7dffac88ff9576ff9576ffac88%
-  ff9f7dffac88ffffffff9f7dffffffffffffffac88ff9576ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffff9576ff8c72ff9576ffac88ff9f7dff8c72%
-  ff9576ff8c72ff8c72ff9576ff9f7dffac88ffac88ff9576ff7e6cffffffff8c72ff9576ff9f7dffac88ff846eff9576%
-  ff7e6cff9576ffac88ff7869ff8c72ff7367ff7e6cff7869ff6f65ff9576ff8c72ffffffffffffffac88ff9576ffac88%
-  ffac88ffac88ff9576ffac88ffffffff9f7dff9576ffffffffac88ffffffffac88ffffffffac88ffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ff9f7d%
-  ff8c72ff7e6cff9576ffac88ff9f7dff9576ff9576ff9576ff9f7dff9f7dff9576ffffffffac88ff9f7dffac88ff9f7d%
-  ffac88ff8c72ff9f7dffffffff9f7dff8c72ff7e6cff6b63ff846efc6260fc6260fb605ff95c5efd6561ff8c72ff9f7d%
-  ff9f7dff8c72ff9f7dffffffffffffff9576ff9f7dffffffff9f7dffac88ffac88ff9576ff8c72ffffffff9f7dff9f7d%
-  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffff9576ff9576ff8c72ff7e6cffac88ff8c72ff9576ff846eff7e6cff9576ff846eff9f7dff9f7d%
-  ffffffff9f7dffffffff9f7dff8c72ff9f7dff9576ff8c72ff8c72ff846efb605ff95c5ef7585df85a5df5515bf85a5d%
-  fb605ff6545cfe6862ff846eff9f7dffac88ff9f7dffffffff9f7dff9576ff9f7dff9f7dff8c72ffffffffac88ffac88%
-  ff9f7dff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffac88ffffffffac88ff9f7dff7367ff7367ff8c72ff846effffffffac88ff9576%
-  ff7e6cff9576ff9f7dffffffffffffff7869ffac88ff9f7dff9f7dff846eff7367ff846eff7e6cfd6561f7585df95c5e%
-  fa5e5ff5535bf04557f34d59f14958f24b59f5515bff6b63ff7e6cff9f7dffffffffffffff9f7dffffffff9576ff8c72%
-  ffac88ff846eff9f7dffffffffac88ff9576ffac88ffffffffffffffac88ffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ff9f7dff7869%
-  ff9f7dffac88ffac88ff846eff9576ff9f7dffac88ff8c72ff9576ffac88ff8c72ff7e6cff846eff7367ff7e6cff7367%
-  ff7367ff6b63fa5e5ff7565cf95c5efa5e5ff34e5af4505af95c5ef24a59f5515bf4505afc6260ff8c72ffac88ff9576%
-  ff9576ffac88ffffffffac88ff9f7dff846eff9576ff9576ffffffffac88ff9f7dffac88ffffffffffffffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffac88ff9576ffac88ffac88ffffffffac88ff9f7dff8c72ff9576ff9f7dff9f7dff9576ff8c72ff7e6c%
-  ff846eff6f65ff6b63ff7367ff6b63fe6862fc6260f85a5df85a5df6545cf4505af4505af7585df5535bf4505af4505a%
-  fc6260ff7e6cffac88ff9576ff9f7dffffffffffffff9f7dffac88ff8c72ff8c72ff9f7dff9f7dff9f7dff9f7dff9f7d%
-  ff9f7dffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffff9f7dffffffffac88ffac88ffffffffffffff9f7dffffffffffffffffffff9f7dff9576ff8c72%
-  ff9f7dff9f7dff9576ff846eff8c72ff6b63f85a5df95c5ef7585dff6b63fa5e5ffd6561fb605ff6545cf6545cf34e5a%
-  f7565cf4505af5515bfb605ff4505afb605fff7869ff8c72ff9f7dffac88ffffffffac88ffac88ffac88ff9f7dff9f7d%
-  ff9f7dffffffff9f7dffffffffffffff9576ffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffffffffac88ffffff%
-  ff9f7dffac88ffac88ffac88ff9f7dff9576ff846eff6f65fe6862ff7367fb605ff7585df95c5efc6260f6545cfe6862%
-  f6545cf95c5efc6260f95c5efb605ff5515bf7585dff6f65ff7367ff8c72ff7e6cff9f7dff9576ff9f7dff9f7dff8c72%
-  ff9f7dff9f7dffffffff9f7dffffffffac88ff9f7dffac88ffffffff9f7dffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7d%
-  ffffffffac88ff9f7dff9f7dffffffffac88ffffffffac88ff846eff9f7dff8c72ff7e6cfe6862f95c5ef7565cf14958%
-  f4505afd6561fa5e5ff7585dfe6862ff7367ff6f65f7585dfb605fff6b63f7565cff6b63fa5e5ffa5e5ffc6260ff846e%
-  ffac88ffffffffffffff8c72ff9576ffac88ffffffffac88ffffffffffffff9576ffffffffffffffffffff9f7dff9f7d%
-  ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ff9f7dff9576ff846eff9576ff846e%
-  f85a5dff6b63f7565cf95c5ef4505af6545cf5535bff6b63fe6862ff6b63ff7e6cfe6862ff6b63ff6b63fe6862fb605f%
-  f95c5eff6b63fe6862ff7e6cff846effffffffffffff9f7dffffffff7e6cffffffffffffff9576ff846effac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ff9f7dffac88ffffffffac88ff8c72ff9f7d%
-  ff9f7dff9f7dff9f7dff7e6cfe6862fd6561f7565cf85a5df34d59f14958f95c5efa5e5ffe6862fd6561ff7367ff7e6c%
-  ff7e6cff7e6cfb605ffd6561f6545cf85a5dff6f65ff6f65ff7e6cff9f7dff9576ffac88ff9f7dffac88ff8c72ffac88%
-  ff7e6cff6b63ff6f65ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffffffff9f7dff9f7d%
-  ffac88ffffffff9576ff9576ff9576ff9f7dff7869ff7e6cff7e6cfb605ff85a5dfa5e5ff7565cf5515bf95c5efc6260%
-  ff6b63fe6862ff7e6cff7e6cff846eff9576fd6561ff6b63f95c5eff6b63ff6f65ffac88ff846eff8c72ff846eff7869%
-  ff9576ff9576ff8c72ff9f7dff7367f7585ded4155f95c5eff9576ff9f7dff9f7dffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
-  ffffffffffffffac88ffac88ffac88ffffffff9576ffac88ff9576ffac88ff8c72ffac88ff846eff6f65ff7e6cfe6862%
-  fe6862fe6862ff7367fb605fff7869ff846eff9576ff846eff9576ff846eff7869ff6b63ff7869ff7367ff8c72ff9576%
-  ff8c72ff6f65ff7869ff7e6cfd6561ff7e6cff846eff846eff8c72fa5e5fed4155eb3e54ff7367ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffffffff9576ffac88ff9f7dffac88ffac88ff9f7dff9f7dffac88ff9f7dff9f7dff7869%
-  ff7e6cff7e6cff7367ff7869fc6260fb605fff7367ff9576ff7869ffac88ff9576ff8c72ff8c72ff8c72ff846eff8c72%
-  ff6f65ff7869ff9576ff846effac88ff9576ff846eff6b63fa5e5fff7869ff8c72ff9f7dff7e6cff7e6cf7585df7585d%
-  ff7869ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9576ffac88ffffffffac88%
-  ff9f7dffac88ff9576ff6f65ff7367ff7367fe6862ff846eff8c72ff7869ff6f65ff7869ff9f7dff8c72ff846effac88%
-  ff8c72ff8c72ffac88ffffffff8c72ff9f7dff9576ff9f7dff7e6cff9576ff9f7dff7e6cfe6862fd6561ff7869ff6b63%
-  ff9576ff9576ff846eff8c72ff7e6cff9576ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffffffffffac88ff9576%
-  ffffffff9576ffffffffffffff8c72ffffffff9576ff9576ff7e6cff6f65ff6b63ff6f65ff9576ff7e6cff7e6cff9576%
-  ff846eff7e6cff7869ff6f65ff846eff7e6cff8c72ff9f7dffac88ff9f7dff846eff7869ff9576ff8c72ff846eff9f7d%
-  ff7367ff6f65ff8c72ff846effac88ff9576ff9f7dff9576ff9f7dffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9f7dffffffffffffffac88ffffffffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9576ff9576ff7869ff7367%
-  ff9576ff7367ff9576ff9f7dff846eff8c72ff9f7dff6f65ff6b63ff7367ff8c72ff9f7dff846eff9576ffac88ffac88%
-  ff9576ffffffff9f7dff8c72ff9f7dff9f7dff7e6cff9f7dff846eff9576ff9f7dffac88ff9f7dffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffff9f7dff846effac88ffac88ffffffff9f7dff9f7dffac88ff9f7dffffff%
-  ffffffffac88ff7869ffac88ff8c72ff8c72ff7869ffac88ff8c72ff9f7dff846eff7367ff9f7dff846eff8c72ffac88%
-  ff9576ff9576ff846eff9f7dffac88ff9576ff9576ff9576ff7869ff7869ffac88ffac88ff9576ffac88ff9f7dff9576%
-  ff9f7dff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ff9576ff6b63%
-  ffac88ff7e6cffffffff9f7dff7869ffac88ff9f7dff9576ff9576ff9576ffac88ff8c72ff7e6cff9f7dff8c72ff846e%
-  ff9576ff9576ff9576ffac88ffffffff9f7dff9f7dff9f7dffffffff9f7dff9576ff7e6cff846eff846eff7e6cffffff%
-  ff9576ffac88ff9f7dff9576ff9f7dffffffffffffffac88ffffffffac88ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffff9f7d%
-  ffffffff9f7dff8c72ff7e6cff9576fe6862ff9576ffffffff9f7dff9576ff9f7dff9576ffac88ffac88ff846effac88%
-  ff9576ffac88ffac88ffac88ff8c72ff8c72ff9f7dff9576ff9f7dffffffff9f7dff9576ffffffff8c72ff9576ffac88%
-  ff9f7dff7869ff7367ff9576ff7e6cff9f7dff9576ff9f7dffac88ffac88ffffffffffffffac88ffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ff9f7dffffffffac88ff9576ff9576ff8c72fc6260ff7367ff6b63ffac88ffac88ffac88ffac88ff9f7d%
-  ff9f7dffac88ffffffff846effffffff9f7dff7e6cff9576ff9576ffac88ff9f7dffffffffac88ff9f7dffffffff9f7d%
-  ffffffff9f7dffffffff846eff9f7dff8c72ff7869ffac88ff7367ff9576ff9576ff9576ff9576ffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffff9f7dffffffff9f7dffffffff9576ffac88ff9f7dffac88ff846eff7e6cff7869%
-  ffac88ff9f7dffac88ffac88ff9f7dffffffff9f7dffac88ffac88ffac88ff846effac88ffffffff9f7dffac88ffffff%
-  ffffffffac88ff9f7dffac88ffac88ff9f7dffac88ff8c72ffffffffffffff846eff9f7dff7367ffffffff846effffff%
-  ffac88ff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff8c72ff9f7dffac88ff846effac88%
-  ff9576ff9576ff846eff6f65ff9f7dff8c72ffac88ff9576ff9f7dffffffffffffff9f7dffac88ffffffffffffff9576%
-  ff846eff9f7dffac88ffac88ff9f7dff9f7dff9f7dff9f7dffac88ffac88ffac88ffac88ff9576ffac88ff9576ff9f7d%
-  ff846effffffff9f7dff9576ff9576ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
-  ff9f7dffac88ffffffff9576ff9576ff9f7dff9576ff9f7dff846eff9f7dffffffff9f7dffac88ffffffff9576ffffff%
-  ffac88ff9f7dff9f7dff9576ffac88ffffffffffffff9576ffffffffac88ff9576ffffffff8c72ffac88ffffffffffff%
-  ffffffff9576ff9576ffffffffffffffac88ff9f7dffac88ff9f7dffac88ffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffff9f7dffffffffffffffffffffffffff8c72ff846effac88ff8c72ff9f7dff9f7dff9576ffffff%
-  ffac88ffac88ffac88ff9576ff9f7dff9576ffac88ff9f7dffac88ff9f7dff9f7dff8c72ffac88ff9576ffac88ff9576%
-  ff8c72ff846eff9f7dff7367ff9f7dffffffff9f7dff7e6cffac88ffffffffac88ff9f7dffffffff9f7dffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dff9576%
-  ffac88ff9576ff9f7dffac88ff9f7dffffffff9f7dffac88ffac88ff8c72ffac88ff9576ff9f7dff9576ff7869ff8c72%
-  ff9f7dff846eff9576ff9576ff846eff8c72ff8c72ff8c72ff9f7dff846eff8c72ff9576ffffffff846effffffffffff%
-  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffffac88%
-  ffac88ff9f7dff9f7dffac88ffac88ffac88ffffffffac88ff9576ff9576ff9f7dff9f7dff9f7dff9576ff9576ff846e%
-  ff7e6cff7e6cff7e6cff7e6cff7e6cff7367ff7367ff9576ff9576ffac88ff846eff7869ff7869ff6f65ff9576ff7e6c%
-  ff9576ff9576ffffffffac88ffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9576ffffffffac88ffffffffac88ffffffff8c72ffac88ff8c72ff9576ff9576ff9f7dff8c72%
-  ff846eff7e6cff7e6cff6f65fd6561ff6b63fb605ffd6561fa5e5fff7367fd6561fc6260ff8c72ff6b63ffac88ff846e%
-  ff7869ff7869ff7367ff9576ff9576ff9f7dffffffff9576ffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffff9f7d%
-  ff8c72ff8c72ff9576ff9f7dff846eff7367ff7869ff7e6cfb605ff7585df24b59f24a59f34d59f34e5afb605ffc6260%
-  fd6561ff8c72ff7e6cff7e6cffac88ffac88ff7e6cff7367ffac88ff9f7dffac88ffac88ffac88ffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ff9576ffac88ff9576ff9576ff9576ff6f65ff846efc6260fc6260fa5e5ffc6260f85a5df5535bef4356%
-  f4505af34e5aef4457f85a5df4505aff6b63ff846eff7e6cff7e6cff9f7dff8c72ff9f7dffffffff9576ff9f7dffffff%
-  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff6b63ff7869ff8c72ff7367fd6561f95c5ef34d59%
-  f5515bf14958f04757f04557f6545cf04757f34e5af5515bff6b63fc6260fb605fff8c72ff7367ff9576ff9f7dffac88%
-  ffac88ff9f7dff7869ff846eff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff9576ffffffff9576ff9f7dff8c72ff8c72ff8c72%
-  ff7869f85a5df5515bf24b59f6545cf24b59f5515bee4256f14958f85a5df5535bf95c5eff7367fb605fff7869ff6f65%
-  ff7367ff9576ff8c72ff8c72ff9576ff9f7dff7e6cff9f7dff846effac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffff9576ffac88%
-  ff8c72ff9f7dff7869ff7e6cfb605ff7585df7585df4505af5515bfa5e5ff24b59f95c5ef34e5af85a5df85a5dff6f65%
-  fc6260ff7869ff7367ff8c72ff846eff6b63ff7e6cff6f65ff6f65ff7e6cff6f65ff6f65ff846eff9f7dffac88ffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffff9f7dff9576ff8c72ff846eff8c72ff6f65fc6260fc6260f4505af34e5aec3f55f14958f95c5ef7565cf85a5d%
-  fc6260fa5e5ffe6862fd6561fe6862ff8c72ff6f65ff7e6cff6f65fb605fff7367fe6862fa5e5ff5535bf85a5dff7367%
-  ff8c72ff7869ff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
-  ffffffffac88ffffffffac88ffffffff8c72ff9576ff9576ff9f7dff7367ff7869fd6561fc6260f24b59f34e5af14958%
-  f24a59f85a5dfa5e5ffc6260ff6b63ff6f65ff6f65ff7869ff8c72ff7869ff846eff7e6cff846eff7e6cff7e6cfc6260%
-  f85a5dfa5e5ffd6561fb605fff7e6cff8c72ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffff9f7dffac88ffffffff9f7dff9f7dff8c72ff846eff6f65ff6b63fa5e5ffe6862%
-  f5515bf34d59f5535bf85a5df7585df7585dfc6260f7585dfc6260fe6862ff7869ff8c72ff8c72ff7e6cff6f65fc6260%
-  fc6260ff9576fe6862ff7367ff6b63ff6f65f85a5dfd6561fd6561ff7367ffac88ffac88ffac88ffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffffff846effac88ff7869%
-  ff7e6cfe6862ff9576f95c5efc6260f24b59f34d59f7565cf34e5afa5e5ffa5e5fff7869ff7869ff7e6cffac88ff846e%
-  ff7367ffac88ff7367ff846eff9576ff7367ff6b63ff7e6cff9f7dff7869ff6f65ff7367ffac88ff8c72ff9f7dffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffac88%
-  ff9576ffac88ff8c72ff8c72fd6561ff7869ff6b63ff6b63ff7869fa5e5ffb605ffc6260f85a5dfc6260ff6b63ff7367%
-  ff7869ff7869ff6b63ff9576ff7367ff6b63f95c5eff6f65ff7869f95c5eff6f65ff846eff7869fd6561ff9576ff7869%
-  ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7dff8c72ff9f7dff9576ff9576ff8c72ff846efe6862ff7e6cff7367fa5e5ffa5e5ffd6561fa5e5f%
-  ff7367f85a5dff7367ff6b63fc6260ff7869ff7e6cff7367ff846eff6f65ff7869ff7e6cf95c5eff7e6cff7367ff846e%
-  ff8c72ff7869ff8c72ff8c72ff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff9f7dffffffff9f7dff9576ffac88ff846eff7e6cff846eff7e6cff9f7dff8c72ff846e%
-  fe6862ff7e6cfd6561ff7e6cfc6260fa5e5fff7869ff7869ff7367ff7e6cff8c72ff7367fe6862ff7367fe6862ff8c72%
-  f95c5efb605fff6b63ff7869ff7869ff7869ff846eff9576ffac88ffffffff8c72ffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff846effac88ff8c72ff846eff846eff8c72%
-  ff846eff8c72fd6561ff8c72ff846eff7367ff8c72ff6b63ff6f65ff7e6cff7e6cff8c72ff6b63ff9576ff8c72ff846e%
-  ff6f65ff7367ff846eff7367ff7367f85a5dff6f65fd6561ff7367ff6f65ff9f7dff9576ffac88ffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9f7d%
-  ff846eff9f7dff8c72ff9576ff7869fd6561ff7367ff8c72ff8c72ff8c72ff9576ff846eff7e6cff7367ffac88ffac88%
-  ff9576ff7367ff8c72ff846efd6561ff6b63ff6f65ff7367ff7e6cff8c72ff9576ff7869ff9576ff8c72ffac88ff9f7d%
-  ffac88ff8c72ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ff9f7dff9f7dffac88ff9576ff8c72ff8c72ff846eff6b63ff846eff9576ff846eff8c72%
-  ff9f7dff8c72ff846eff9576ff7e6cff6f65ff9576ff7e6cff6f65fc6260f85a5dfe6862ff7869ff7869ff9576ff846e%
-  ff7e6cff846eff9f7dff9f7dffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9576ff9f7dff7e6cff846eff7869ff7869ff7367%
-  fb605fff6f65ff7367ff846eff9576ff8c72ffac88ffffffff8c72ff9576ff846eff8c72fc6260ff846eff6f65fe6862%
-  ff7367ff9576ff7869ff9f7dff9f7dffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffff%
-  ff9576ffac88ff9f7dff9f7dfe6862f7585df6545cff7e6cff8c72ff9f7dff9576ffffffff9576ff9576ffffffff9f7d%
-  ff7e6cff9576ff7869ff846eff9576ff9f7dff7869ff9f7dffffffffac88ff9f7dffffffffac88ffac88ffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ff9f7dffac88ffffffffac88ffffffff8c72ff8c72ff8c72ff8c72ff9576ff846eff7869ff7e6cffffffffffffff9576%
-  ffac88ffac88ffffffff8c72ff8c72ffac88ff9f7dffffffff8c72ff9576ffac88ff9f7dff9576ff9f7dffac88ffac88%
-  ffac88ffac88ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff8c72ff9f7dff9f7dff7367ff8c72ff846eff9576%
-  ff9576ff9f7dff9f7dff9f7dff9f7dffffffffffffffffffff9576ffffffffac88ff9f7dff9f7dff7e6cffffffff9576%
-  ff9576ffac88ffac88ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9576ff8c72ff7869ff7367ff8c72f7585dff7367ff9576ff8c72ff9576ffac88ffac88ffffffffac88ffffffffac88%
-  ffac88ffac88ff9576ffffffff9576ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffac88ff9f7dff846eff7367f85a5df6545cfe6862ff8c72ffac88ffac88ffffff%
-  ffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffac88ff9f7dff8c72ff9f7dff9576%
-  ff7e6cff7869ff846eff8c72ff9f7dffac88ff9576ffac88ffac88ffac88ffac88ffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9576%
-  ff7367ff7e6cfe6862fc6260ff6f65ff6f65ff7869fd6561ff6b63ff7869ff846eff7e6cff9576ff8c72ffac88ffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9576ffffffffac88ff846eff7e6cff6b63fd6561f7565cf34e5af85a5df5535bf4505af5515bfb605ffe6862%
-  ff6f65ff7869ff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffac88ff9576ff9576ff846efc6260f6545cf5535bf14958e53651e53751e93c53%
-  ec3f55e63852f14858f24b59f34d59f24a59f85a5dfe6862ff846eff9576ff9f7dff9576ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffac88ff846eff7367fd6561f6545cf14858%
-  eb3e54e93c53ea3d54e73a52e53751f04557ea3d54ea3d54f04557ea3d54f14858f34d59ff7367ff8c72ff8c72ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576ff8c72ff9576ff9f7dff846e%
-  ff7e6cfe6862f95c5ef7585df5535bf34e5aed4155ef4356eb3e54f24b59f34e5aef4457f24b59f14858ef4356ef4356%
-  f7565cff7e6cffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ff9576ff9576ff7869fd6561fb605ff5535bf04557f5515bef4457e93c53ea3d54e63852ea3d54ed4155f04557ee4256%
-  f04757ea3d54e23450e73a52ee4156f7565cff7367ff7e6cffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffff9f7dff9f7dff9576ffffffff7e6cff6b63fe6862f7565cfe6862f34e5afb605ff7585df7585df7565c%
-  f7585de83b53f5535bfa5e5ff6545cf85a5df34e5afb605ff7585dff6f65ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7dff9576ff9576ff846efc6260%
-  fa5e5ffc6260ff6f65ff6f65fa5e5ffa5e5ff7585df7585df7585df85a5df95c5eff7869ff8c72ffffffffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ff8c72fc6260ff6f65f5515bf04557f6545cf5515bff6f65ff6b63f95c5ef95c5efa5e5ffd6561f7585dff7e6cff6b63%
-  ff9f7dffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffac88ff8c72ff9f7dff9576ffac88ffffffffac88ffffffffffffffac88ffffffff9576%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffb3082eda294bd11f46d42248dc2b4c%
-  df304eea3d54f6545cff6b63ff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff900106%
-  bb0e35b3082ebb0e35c3143bc8183fd52349e0314ffb605fffac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffff9cea9c79d48d9cea9c9cea9c9cea9c9cea9c9cea9c85de919cea9cffffff9cea9cffffff9cea9cffffff85de91%
+  ffffff79d48d6cc78c85de9179d48d9cea9c6cc78c79d48d62bd8b56b2894aa7873e9d8545a28650ac8845a286299083%
+  278f831f8a821e86821e82821e85821f7581206b81206c81206981226281216881236081226481226181226381235f81%
+  216681245b81235e81216781245981235e81226181216481206c811f73812071811f74811f7f822071811f7481226481%
+  206a81216781206e811f77811a2281ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c9cea9cffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff85de91%
+  9cea9c9cea9c9cea9c79d48d85de9185de919cea9c85de9179d48d85de9179d48dffffff79d48dffffff6cc78c85de91%
+  ffffff79d48d6cc78c6cc78c85de919cea9cffffff85de919cea9cffffff9cea9c9cea9c9cea9c9cea9c9cea9c85de91%
+  85de919cea9c9cea9c9cea9c9cea9c9cea9cffffffffffff9cea9c1f7881ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9cffffff%
+  85de9185de919cea9c9cea9c72cd8d9cea9cffffff85de919cea9c79d48d9cea9c79d48d85de919cea9cffffff79d48d%
+  85de91ffffff85de9179d48d79d48d9cea9c62bd8b5ab58972cd8d85de9167c28b6cc78c5eb98a72cd8d85de919cea9c%
+  9cea9c72cd8d9cea9c85de919cea9c79d48d85de919cea9cffffffffffffffffffffffffffffffffffff1f7a82ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffff85de91ffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff85de91ffffffffffff85de9179d48d9cea9c85de919cea9c9cea9c79d48d9cea9c9cea9cffffff%
+  85de919cea9c9cea9c85de91ffffff6cc78c79d48d85de916cc78c67c28b67c28b5eb98a6cc78c5eb98a5ab58956b289%
+  72cd8d6cc78c72cd8d62bd8b9cea9c6cc78c79d48d85de919cea9cffffff85de91ffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffff1e8482ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c9cea9cffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9cffffffffffffffffff9cea9c9cea9cffffff9cea9c%
+  ffffff85de9185de9172cd8dffffff79d48d85de91ffffff9cea9c72cd8d9cea9c72cd8d6cc78c50ac884da98750ac88%
+  48a58648a58662bd8b62bd8b5ab58956b28979d48d6cc78c5ab58967c28b67c28b72cd8d85de91ffffff85de91ffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffff1e8282ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  85de9179d48d62bd8b85de9185de919cea9cffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c%
+  9cea9cffffff9cea9c9cea9c9cea9c9cea9c85de919cea9c85de9172cd8d9cea9c6cc78c62bd8b72cd8d62bd8b62bd8b%
+  45a28653af884da987399a85399a8537998543a18648a58648a5864aa7875ab5895eb98a56b28967c28b45a2864da987%
+  6cc78c79d48d85de91ffffffffffff9cea9c85de91ffffffffffffffffffffffffffffff9cea9c278f83ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff85de919cea9c9cea9c79d48dffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c79d48dffffff9cea9c72cd8d67c28b6cc78c62bd8b%
+  79d48d67c28b6cc78c4da98745a28653af883e9d85409f8648a586399a8548a58645a28648a58656b28972cd8d48a586%
+  53af883b9c854aa78750ac8856b2899cea9c72cd8dffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff4aa787ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de9172cd8d85de9185de9185de9185de9172cd8d%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9c9cea9c9cea9c85de91ffffff72cd8d%
+  72cd8d72cd8d5ab5895eb98a5ab5895ab5894aa7874aa7873e9d85409f8643a18653af8848a5865ab5892990834aa787%
+  48a58648a58650ac8837998548a5865eb98a4aa78753af8867c28b79d48d79d48d9cea9cffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffff72cd8dffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de919cea9c9cea9c6cc78c%
+  9cea9c9cea9cffffffffffff9cea9c85de919cea9cffffffffffffffffffffffffffffffffffff85de91ffffffffffff%
+  ffffff85de919cea9c79d48d72cd8d6cc78c6cc78c4aa78762bd8b5eb98a5eb98a399a8550ac8845a28650ac8845a286%
+  43a18643a18645a2864aa78753af885ab58948a58643a1863e9d8543a18648a58650ac886cc78c67c28b9cea9c9cea9c%
+  ffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffff72cd8dffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c9cea9c%
+  9cea9cffffff72cd8d79d48d79d48dffffff72cd8d79d48dffffffffffff72cd8dffffffffffffffffff9cea9cffffff%
+  9cea9c9cea9cffffffffffff9cea9c9cea9c85de919cea9c72cd8d6cc78c62bd8b67c28b5ab58948a5863b9c853e9d85%
+  45a2863e9d8545a2863e9d85409f864aa7873799855ab58962bd8b9cea9c5eb98a50ac882e938448a58653af8856b289%
+  6cc78c79d48d79d48d79d48d9cea9c85de91ffffffffffff79d48dffffff9cea9cffffffffffff9cea9cffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c9cea9c9cea9c9cea9cffffff9cea9c9cea9c79d48d9cea9c79d48d85de9179d48d9cea9c9cea9c%
+  9cea9c9cea9cffffff9cea9cffffffffffff9cea9c72cd8d72cd8dffffff79d48d79d48d67c28b5ab58953af8848a586%
+  56b28948a586409f86399a853e9d8545a2864da98745a28662bd8b62bd8b56b2895ab58953af886cc78c53af8862bd8b%
+  50ac8843a18653af885ab58972cd8d79d48d9cea9c9cea9c85de91ffffffffffff85de919cea9cffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de91ffffff79d48d79d48d9cea9c85de919cea9cffffff9cea9c%
+  79d48d79d48d9cea9c9cea9cffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c9cea9c9cea9c79d48d79d48d%
+  67c28b67c28b53af8850ac8848a5863396842c928343a1863e9d854da98762bd8b5ab58948a58667c28b67c28b67c28b%
+  67c28b72cd8d79d48d56b28972cd8d48a58650ac885ab58962bd8b6cc78c79d48d9cea9cffffffffffff85de91ffffff%
+  9cea9cffffff85de91ffffff85de9185de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de919cea9c%
+  9cea9cffffff85de919cea9c9cea9c79d48dffffff72cd8d85de91ffffffffffffffffff85de919cea9cffffff85de91%
+  9cea9c85de9179d48d79d48d67c28b56b28972cd8d3b9c853799853b9c8548a58656b2893b9c853e9d854aa78756b289%
+  6cc78c62bd8b72cd8d72cd8d72cd8d5ab58967c28b5eb98a5eb98a6cc78c5eb98a5eb98a62bd8bffffff72cd8d9cea9c%
+  9cea9c9cea9cffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9c9cea9c9cea9cffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffff9cea9c85de9179d48dffffff85de91ffffffffffff9cea9c9cea9c85de91ffffff%
+  85de919cea9c9cea9cffffff9cea9c9cea9c85de9179d48d67c28b5eb98a4da9875eb98a4da98745a28645a2863b9c85%
+  43a1864aa7875ab5894aa78756b2895eb98a67c28b5eb98affffff85de9156b28962bd8b53af8862bd8b85de9179d48d%
+  67c28b72cd8dffffff72cd8d9cea9c85de919cea9c9cea9c9cea9c85de9179d48d9cea9cffffffffffff85de91ffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffff85de9185de91ffffff9cea9c85de91ffffff85de91%
+  ffffff79d48dffffff85de919cea9c9cea9c9cea9c85de919cea9c79d48d79d48d79d48d72cd8d67c28b5eb98a56b289%
+  37998548a58643a1863b9c85399a853e9d8567c28b4da98762bd8b85de9167c28b79d48d67c28b72cd8d72cd8d5eb98a%
+  5eb98a5eb98a9cea9c85de9185de919cea9c9cea9c9cea9c9cea9c85de919cea9c6cc78c79d48dffffff9cea9c85de91%
+  72cd8d72cd8d9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de91ffffff9cea9c9cea9c%
+  85de919cea9c9cea9c9cea9c9cea9c85de919cea9cffffff79d48d72cd8d9cea9c85de919cea9c9cea9cffffff6cc78c%
+  79d48d72cd8d62bd8b79d48d4aa787399a854aa787409f8656b28950ac885eb98a62bd8b62bd8b6cc78c85de9167c28b%
+  5ab58979d48d5eb98a72cd8d4da98767c28b6cc78c67c28b72cd8d85de9179d48dffffff9cea9c9cea9c6cc78c6cc78c%
+  5ab58979d48d9cea9cffffff9cea9cffffffffffffffffffffffff85de91ffffff85de91ffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff85de9185de91%
+  9cea9c9cea9cffffff72cd8d9cea9cffffff9cea9c9cea9cffffff9cea9cffffff79d48d85de919cea9c9cea9c79d48d%
+  85de919cea9c6cc78c85de9179d48d6cc78c6cc78c67c28b56b28948a58650ac8850ac8850ac8848a5864aa78762bd8b%
+  79d48d79d48d72cd8d72cd8d4da98750ac884da9876cc78c62bd8b67c28b67c28b6cc78c9cea9c85de9185de9179d48d%
+  9cea9cffffff85de9172cd8d50ac8867c28b6cc78cffffff79d48d9cea9c85de91ffffffffffffffffff9cea9cffffff%
+  85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c9cea9c85de9179d48dffffff%
+  ffffff85de91ffffff67c28b79d48d79d48d79d48d9cea9c85de9162bd8b62bd8b79d48d5eb98a53af884da9876cc78c%
+  4da98750ac885eb98a72cd8d79d48d5ab58972cd8d85de919cea9c5ab58953af889cea9c85de9162bd8b5ab58967c28b%
+  85de919cea9cffffff9cea9c9cea9c85de919cea9c62bd8b67c28b67c28b67c28b85de9179d48d9cea9c85de9179d48d%
+  ffffff85de9185de9172cd8dffffff9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de91ffffffffffff9cea9c79d48d79d48d%
+  9cea9c85de919cea9c9cea9c85de919cea9c85de916cc78c67c28b9cea9c6cc78c72cd8d72cd8d6cc78c62bd8b5ab589%
+  72cd8d79d48d5ab58956b2895ab58972cd8d62bd8b6cc78c67c28b6cc78c79d48d6cc78c79d48d79d48d72cd8d62bd8b%
+  85de9179d48d67c28b79d48d85de9179d48dffffff9cea9c72cd8dffffff9cea9c9cea9c79d48d5ab58962bd8b85de91%
+  85de9172cd8dffffff85de9172cd8d85de9167c28b43a18643a1869cea9cffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff9cea9cffffff9cea9c9cea9c85de91%
+  ffffff85de919cea9cffffffffffff9cea9cffffffffffff72cd8d67c28b6cc78c9cea9c85de9172cd8d85de9179d48d%
+  6cc78c6cc78c6cc78c6cc78c72cd8d6cc78c79d48d56b2895ab58972cd8d67c28b5ab58979d48d72cd8d67c28b6cc78c%
+  9cea9c6cc78c79d48d62bd8b67c28b6cc78c79d48d85de9179d48d72cd8dffffffffffff9cea9c9cea9c9cea9c9cea9c%
+  79d48d9cea9c53af8879d48d85de91ffffffffffff9cea9c79d48d62bd8b85de9153af883b9c8553af88ffffff9cea9c%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffff%
+  9cea9c9cea9cffffff85de9185de91ffffffffffff9cea9c85de919cea9c9cea9c9cea9c9cea9c9cea9cffffff85de91%
+  72cd8d9cea9c72cd8d6cc78c85de9172cd8d67c28b9cea9c79d48d67c28b62bd8b6cc78c67c28b62bd8b72cd8d56b289%
+  67c28b5eb98a62bd8b6cc78c85de9179d48d85de9172cd8d67c28b79d48d9cea9c9cea9c85de919cea9cffffffffffff%
+  79d48d72cd8d62bd8b9cea9c79d48d9cea9c79d48d9cea9c9cea9c85de91ffffff72cd8d67c28b4aa7875eb98a62bd8b%
+  399a8543a18685de91ffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffff9cea9c9cea9c85de919cea9c79d48dffffff9cea9c9cea9c9cea9c85de919cea9c%
+  9cea9c67c28bffffffffffff67c28b67c28b72cd8d5eb98a72cd8d67c28b79d48d9cea9c85de9172cd8d67c28b62bd8b%
+  62bd8b67c28b62bd8b5eb98a62bd8b67c28b6cc78c79d48d79d48d6cc78c79d48d85de9185de9179d48d85de91ffffff%
+  ffffff85de9185de9185de919cea9c9cea9c9cea9c72cd8d72cd8d67c28b9cea9c85de919cea9c85de9185de91ffffff%
+  79d48d56b2894da98750ac885eb98a50ac8872cd8dffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c85de9179d48dffffffffffffffffffffffffffffff85de91ffffff85de91%
+  ffffff85de9179d48d9cea9c6cc78c79d48d79d48d85de919cea9cffffff72cd8d67c28b79d48d72cd8d9cea9c6cc78c%
+  9cea9c79d48d72cd8d9cea9c72cd8d67c28b85de9185de9185de9185de916cc78c72cd8d79d48d6cc78cffffff85de91%
+  79d48d67c28b85de91ffffff9cea9cffffff85de9185de91ffffff85de9185de9167c28b72cd8d6cc78c85de9179d48d%
+  ffffffffffff9cea9cffffff9cea9c79d48d56b2894aa78762bd8b5eb98a72cd8d9cea9cffffffffffffffffffffffff%
+  9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9c%
+  9cea9c85de91ffffff85de9185de919cea9c85de91ffffff9cea9c9cea9c9cea9c9cea9c85de91ffffff6cc78c62bd8b%
+  5ab5896cc78c72cd8d79d48d67c28b67c28b79d48d79d48d72cd8d72cd8d72cd8d79d48d79d48d9cea9c9cea9c6cc78c%
+  72cd8d85de919cea9c79d48d6cc78c9cea9c72cd8dffffff9cea9c9cea9c9cea9cffffffffffffffffff9cea9cffffff%
+  72cd8d72cd8dffffff9cea9c9cea9c85de9185de91ffffff9cea9cffffff72cd8d79d48d62bd8b72cd8d9cea9c9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  85de9185de91ffffff9cea9cffffffffffffffffff85de9172cd8d72cd8d79d48d9cea9c72cd8d9cea9cffffff9cea9c%
+  85de9185de9179d48d9cea9cffffff62bd8b79d48d6cc78c62bd8b79d48d5eb98a6cc78c85de9185de9172cd8d9cea9c%
+  85de9162bd8b79d48d6cc78c79d48dffffff9cea9c79d48d85de9179d48d9cea9c85de91ffffffffffff9cea9c9cea9c%
+  ffffffffffffffffff85de919cea9c85de9172cd8d79d48d85de9185de91ffffff9cea9c85de91ffffffffffff9cea9c%
+  85de919cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff79d48d85de9179d48d9cea9c79d48d%
+  9cea9c9cea9c85de9179d48d9cea9c6cc78c9cea9c9cea9c85de919cea9c72cd8d85de916cc78c72cd8d72cd8d85de91%
+  9cea9c9cea9c72cd8d9cea9c72cd8d79d48d6cc78c85de9179d48d79d48d79d48dffffff72cd8dffffff79d48dffffff%
+  ffffff79d48d85de919cea9cffffff85de91ffffff85de9167c28b79d48d79d48d85de91ffffff9cea9c9cea9c9cea9c%
+  79d48dffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffff9cea9cffffffffffffffffffffffffffffff%
+  85de9185de919cea9c9cea9c85de919cea9c9cea9cffffff9cea9cffffffffffffffffff85de9185de91ffffff72cd8d%
+  9cea9cffffff85de9185de91ffffff85de9185de919cea9c85de919cea9c6cc78c79d48d67c28b6cc78c79d48d67c28b%
+  6cc78c72cd8d72cd8d85de9172cd8d9cea9c9cea9c9cea9c9cea9cffffff79d48d79d48d9cea9c9cea9c6cc78cffffff%
+  79d48dffffff9cea9c9cea9c9cea9cffffffffffff85de9185de91ffffff85de91ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffff9cea9cffffff9cea9c9cea9c85de9172cd8d67c28b72cd8d79d48d79d48d72cd8dffffff9cea9c85de91ffffff%
+  85de91ffffffffffff85de91ffffffffffff85de9172cd8d6cc78c85de919cea9c9cea9c79d48d62bd8b9cea9c67c28b%
+  79d48d85de9179d48d72cd8d67c28b6cc78c62bd8b56b2896cc78c72cd8d72cd8dffffffffffff9cea9c85de9185de91%
+  ffffff85de919cea9c85de919cea9c9cea9c9cea9c79d48dffffff9cea9cffffff9cea9cffffff9cea9cffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9c85de91ffffff9cea9c85de9185de9172cd8d5eb98a9cea9c6cc78c72cd8d9cea9c%
+  9cea9cffffff85de919cea9c85de91ffffff9cea9cffffff79d48d9cea9c85de9185de91ffffff9cea9c9cea9c85de91%
+  9cea9cffffff6cc78c79d48d85de9172cd8d5eb98a5eb98a5eb98a62bd8b48a58653af88409f865ab5896cc78c79d48d%
+  9cea9c9cea9c72cd8d9cea9cffffff9cea9c85de9185de91ffffff79d48d9cea9c9cea9c72cd8d85de919cea9c9cea9c%
+  85de919cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de9172cd8d67c28b%
+  67c28b72cd8d67c28b79d48d6cc78c85de9185de9185de91ffffffffffff9cea9cffffff9cea9c79d48dffffff79d48d%
+  ffffff79d48d9cea9c85de919cea9c79d48d6cc78c67c28b6cc78c56b2895eb98a409f863b9c854da987409f863e9d85%
+  4aa78745a28653af8872cd8d85de919cea9c9cea9c9cea9c85de9185de919cea9c79d48d9cea9c72cd8dffffff85de91%
+  ffffff79d48d85de91ffffff9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  9cea9c85de9172cd8d72cd8d6cc78c6cc78c72cd8d6cc78c72cd8d85de919cea9c9cea9c9cea9c9cea9c9cea9cffffff%
+  85de919cea9cffffff9cea9c72cd8d67c28b6cc78c9cea9c72cd8d67c28b62bd8b5eb98a53af8856b28953af8848a586%
+  3e9d852e9384319584399a852c92833598843e9d855ab5896cc78c79d48dffffffffffff9cea9c9cea9c9cea9c79d48d%
+  72cd8d85de9185de9179d48d9cea9cffffff72cd8dffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffff85de91ffffff9cea9c85de9179d48d85de9172cd8d6cc78c79d48d9cea9cffffff%
+  ffffffffffffffffff9cea9c9cea9c85de9172cd8d85de9179d48d85de9162bd8b53af8867c28b79d48d50ac8867c28b%
+  5ab5894aa78750ac883e9d8550ac8843a1862f948448a58648a586319584409f863598844aa7876cc78c9cea9c85de91%
+  79d48d9cea9c9cea9c9cea9cffffff85de916cc78c72cd8d85de91ffffff9cea9c85de919cea9cffffffffffffffffff%
+  85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9c85de9185de91%
+  ffffff9cea9c9cea9c9cea9c9cea9c9cea9cffffff9cea9c85de91ffffff6cc78c9cea9c62bd8b6cc78c67c28b72cd8d%
+  56b28950ac886cc78c53af8845a2864da98762bd8b48a5864aa787339684399a8537998556b28935988443a186399a85%
+  56b2895eb98a72cd8d85de9185de91ffffffffffffffffff85de9185de916cc78c72cd8dffffff85de9185de9185de91%
+  79d48d9cea9cffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff%
+  9cea9c9cea9cffffff85de9179d48d9cea9cffffff9cea9cffffffffffff9cea9cffffff85de9185de9185de9172cd8d%
+  9cea9c79d48d67c28b5eb98a56b28937998548a58650ac883b9c8553af8853af8856b28943a18650ac883799853b9c85%
+  4aa7874aa787409f8643a1863e9d854da98753af8872cd8d79d48d85de91ffffffffffff85de91ffffff9cea9c85de91%
+  72cd8dffffffffffff85de91ffffffffffff79d48dffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff85de919cea9cffffff9cea9c9cea9cffffff9cea9cffffff9cea9c85de91ffffffffffff%
+  ffffff9cea9cffffff79d48d79d48d72cd8d5eb98a48a5864da98745a28645a28645a2863b9c85409f865eb98a50ac88%
+  409f8650ac8856b28953af884da987399a855ab58950ac8862bd8b72cd8d6cc78c79d48d79d48d85de9172cd8d85de91%
+  85de9185de919cea9c9cea9c9cea9cffffff85de919cea9c9cea9cffffff85de91ffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c85de91ffffff9cea9cffffffffffff85de919cea9c85de91ffffff%
+  9cea9cffffffffffffffffff85de9179d48d85de9179d48d6cc78c6cc78c50ac8856b2893e9d853799852c928343a186%
+  48a5864aa7875eb98a4da9876cc78c62bd8b4aa78750ac884aa78753af884da98762bd8b56b28943a18653af8862bd8b%
+  9cea9c9cea9cffffff85de9172cd8d9cea9c9cea9cffffff9cea9cffffff85de919cea9cffffffffffff9cea9c85de91%
+  85de919cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c%
+  ffffff9cea9cffffffffffffffffff9cea9c9cea9c85de91ffffff9cea9c9cea9c72cd8d67c28b5ab58956b28956b289%
+  3b9c8548a5862a91833e9d854aa78743a1865eb98a5eb98a5ab5895ab58985de9162bd8b5eb98a5eb98a50ac884da987%
+  53af884da98753af8867c28b79d48d85de919cea9cffffff9cea9cffffff6cc78c9cea9cffffff79d48d72cd8d85de91%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffff79d48dffffff9cea9c85de91ffffff85de91ffffff9cea9c9cea9cffffff85de9179d48d85de9185de91%
+  79d48d6cc78c5eb98a3598844da987399a85409f86359884379985409f8653af8862bd8b67c28b72cd8d6cc78c79d48d%
+  72cd8d62bd8b4da98753af88409f864aa78756b2895eb98a5eb98a72cd8d9cea9c79d48dffffff85de919cea9c72cd8d%
+  9cea9c72cd8d53af8862bd8b6cc78c9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff85de91ffffff9cea9cffffffffffffffffffffffffffffff79d48dffffffffffffffffff79d48dffffff85de91%
+  9cea9c79d48d67c28b79d48d6cc78c5eb98a5ab58956b28945a2864aa787359884409f864aa7874aa7875eb98a50ac88%
+  5eb98a72cd8d79d48d85de9179d48d5eb98a5eb98a67c28b409f865ab5895eb98a79d48d85de916cc78c72cd8d6cc78c%
+  62bd8b79d48d85de9172cd8d85de9162bd8b45a286208a8243a1866cc78c9cea9c85de91ffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff85de91ffffff%
+  85de919cea9c9cea9c9cea9c9cea9cffffff85de9179d48d6cc78c79d48d67c28b62bd8b6cc78c5ab58956b28948a586%
+  5ab5896cc78c67c28b62bd8b67c28b85de9185de9172cd8d79d48d5eb98a6cc78c62bd8b62bd8b6cc78c67c28b79d48d%
+  9cea9c72cd8d56b28962bd8b67c28b50ac8867c28b72cd8d79d48d79d48d4aa7871e8882228b8250ac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  9cea9cffffff85de91ffffff72cd8d9cea9c9cea9cffffffffffff72cd8d72cd8d72cd8d72cd8d72cd8d72cd8d6cc78c%
+  5eb98a5ab58962bd8b50ac885ab58962bd8b72cd8d9cea9c67c28b9cea9c79d48d85de9172cd8d72cd8d79d48d6cc78c%
+  62bd8b67c28b72cd8d72cd8d85de9172cd8dffffff67c28b53af884da98762bd8b6cc78c9cea9c62bd8b85de91399a85%
+  43a1865ab589ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff%
+  ffffffffffffffffff9cea9c85de919cea9c9cea9cffffffffffff9cea9c9cea9c85de91ffffffffffff85de9179d48d%
+  72cd8d5ab58962bd8b5ab58972cd8d67c28b6cc78c5eb98a5eb98a67c28b67c28b85de9179d48d85de9179d48d9cea9c%
+  72cd8d79d48dffffffffffff6cc78cffffff72cd8d9cea9c67c28b72cd8d9cea9c79d48d67c28b50ac8853af885eb98a%
+  5eb98a85de9179d48d6cc78c72cd8d62bd8b9cea9c85de91ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff85de91ffffffffffff9cea9c9cea9c79d48dffffffffffff85de91ffffff85de91ffffff%
+  ffffff85de919cea9c9cea9c79d48d79d48d67c28b5ab58953af886cc78c6cc78c79d48d62bd8b79d48d6cc78c72cd8d%
+  67c28b72cd8d62bd8b6cc78c5eb98a79d48d85de9179d48d85de919cea9c72cd8d62bd8b85de9167c28b79d48d85de91%
+  72cd8d56b28962bd8b85de916cc78c9cea9c72cd8d85de9185de9185de919cea9c9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffffffffffffffff6cc78cffffff85de919cea9c79d48d6cc78c79d48d5eb98a62bd8b72cd8d%
+  9cea9c72cd8d85de9179d48d72cd8d85de9167c28b50ac8862bd8b72cd8d6cc78c6cc78c79d48d85de919cea9cffffff%
+  79d48d85de91ffffff9cea9c72cd8d79d48d85de9167c28b9cea9c62bd8b85de919cea9c9cea9c85de91ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c%
+  ffffff85de919cea9c9cea9c79d48d9cea9c9cea9cffffff9cea9cffffff79d48dffffff9cea9c9cea9c9cea9c72cd8d%
+  85de916cc78c79d48d79d48d79d48d72cd8d9cea9c79d48d85de9172cd8d72cd8d6cc78c72cd8d85de916cc78c85de91%
+  79d48dffffff62bd8b85de919cea9c85de9167c28b85de9185de9156b28979d48d79d48dffffff85de91ffffff79d48d%
+  85de9172cd8dffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff79d48d79d48d79d48d72cd8d9cea9c9cea9c79d48dffffff72cd8d%
+  79d48d72cd8dffffff85de9172cd8d79d48d79d48d85de919cea9c79d48d85de9185de9185de915ab5896cc78c85de91%
+  85de9179d48d85de91ffffff9cea9c79d48d79d48dffffffffffff9cea9c85de9162bd8b6cc78c6cc78c79d48d6cc78c%
+  ffffff72cd8d85de9179d48d9cea9cffffff9cea9cffffffffffffffffff9cea9c9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffff79d48d9cea9c9cea9c85de9179d48d72cd8d79d48d%
+  72cd8d85de9167c28b9cea9c79d48d85de919cea9c85de9185de9185de919cea9c85de919cea9c9cea9c9cea9c85de91%
+  85de9172cd8dffffff6cc78c9cea9c79d48d72cd8d85de919cea9cffffff79d48d85de919cea9c85de9185de9185de91%
+  85de9172cd8d62bd8b67c28b62bd8b79d48d72cd8dffffff9cea9c85de91ffffffffffff9cea9cffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de9185de91%
+  85de9185de9172cd8d9cea9c85de9162bd8b4aa7876cc78c79d48d85de919cea9cffffff9cea9cffffffffffff9cea9c%
+  9cea9cffffff79d48d79d48d72cd8d85de9172cd8d72cd8d85de9185de919cea9c9cea9c9cea9c85de91ffffff85de91%
+  9cea9c9cea9c85de919cea9c85de9179d48d67c28b62bd8b79d48d72cd8d67c28b72cd8dffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff85de919cea9c85de9185de91ffffff79d48d79d48d9cea9c67c28b5eb98a85de91ffffffffffff79d48d%
+  9cea9c9cea9cffffff79d48dffffffffffff85de9185de91ffffff9cea9cffffff85de9179d48d9cea9c85de91ffffff%
+  9cea9c9cea9c85de919cea9cffffffffffff79d48d72cd8dffffff79d48dffffff62bd8b72cd8d85de9172cd8d9cea9c%
+  ffffff85de9185de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de9167c28b85de916cc78c85de9185de9179d48d6cc78c79d48d%
+  72cd8d85de919cea9cffffff85de9179d48dffffff9cea9c9cea9c9cea9c9cea9c9cea9cffffff79d48d85de9185de91%
+  85de9185de919cea9c9cea9c9cea9c72cd8d9cea9c85de9185de91ffffff79d48dffffff85de9172cd8d85de916cc78c%
+  9cea9cffffff85de9179d48d9cea9c85de919cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c85de919cea9c%
+  9cea9c79d48d79d48d79d48d85de9179d48d85de91ffffff85de91ffffffffffffffffffffffff85de919cea9c9cea9c%
+  79d48d9cea9cffffff85de9172cd8dffffff85de919cea9c85de9185de919cea9c9cea9cffffff79d48dffffffffffff%
+  9cea9c9cea9c85de9185de91ffffff9cea9c85de919cea9c9cea9c79d48dffffffffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c85de91ffffff79d48d67c28b85de9179d48dffffffffffff85de9179d48dffffff9cea9c9cea9c9cea9cffffff%
+  ffffff85de9185de919cea9c9cea9c9cea9c72cd8d85de919cea9c85de9179d48d9cea9c79d48d79d48d9cea9c67c28b%
+  85de9172cd8d85de9167c28b79d48d9cea9cffffff62bd8b85de919cea9cffffff9cea9c9cea9c9cea9c9cea9cffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c9cea9c85de919cea9c85de919cea9cffffffffffffffffff9cea9c%
+  ffffff85de919cea9c9cea9c85de919cea9c9cea9c79d48d9cea9c9cea9c79d48d79d48dffffff72cd8d67c28b6cc78c%
+  72cd8d67c28b79d48d9cea9c85de9162bd8b72cd8d85de916cc78c72cd8d79d48d85de9172cd8d85de919cea9cffffff%
+  9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9cffffffffffff85de91ffffff9cea9c9cea9c%
+  85de919cea9cffffff85de91ffffff9cea9c85de919cea9c85de919cea9cffffff79d48d79d48d9cea9c72cd8d6cc78c%
+  6cc78c67c28b6cc78c6cc78c5eb98a6cc78c67c28b62bd8b6cc78c9cea9c72cd8d62bd8b5ab58972cd8d67c28b62bd8b%
+  72cd8d85de919cea9cffffff9cea9cffffff9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c%
+  9cea9cffffffffffff85de91ffffff9cea9cffffff79d48d9cea9cffffff9cea9c79d48d9cea9c79d48d67c28b72cd8d%
+  72cd8d79d48d6cc78c53af8867c28b50ac884aa78745a28653af8853af884da9875ab5895ab58972cd8d62bd8b6cc78c%
+  67c28b62bd8b67c28b62bd8b9cea9c9cea9c9cea9c79d48d9cea9c9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9c85de91%
+  72cd8d79d48d85de9167c28b85de916cc78c5eb98a50ac8862bd8b409f863195843799852c928333968445a2865ab589%
+  409f865eb98a85de916cc78c79d48d9cea9c6cc78c5eb98a72cd8d85de91ffffff9cea9c9cea9cffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff85de91ffffff9cea9cffffffffffff%
+  9cea9c9cea9c85de91ffffff79d48d6cc78c72cd8d56b28967c28b6cc78c48a5864aa78748a586379985399a85379985%
+  2a918335988437998545a286409f863e9d8553af8879d48d62bd8b67c28b85de9185de9179d48d9cea9c9cea9cffffff%
+  79d48dffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff85de919cea9c85de9179d48d85de9179d48d72cd8d5ab58956b28948a5863e9d8548a586%
+  2e93842f9484268e833396842c9283409f862f948453af8843a18653af8843a18656b28967c28b72cd8d79d48d9cea9c%
+  9cea9c79d48d85de9185de915eb98a72cd8dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9c9cea9cffffffffffff79d48d9cea9c85de9179d48d9cea9c67c28b79d48d6cc78c%
+  4da98745a286399a85399a852f9484379985359884319584278f83399a8548a5864da98756b28950ac8856b28956b289%
+  62bd8b72cd8d79d48d72cd8d72cd8d72cd8d79d48d85de916cc78c72cd8d9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c85de9172cd8d%
+  72cd8d72cd8d56b28956b28950ac88409f863e9d85409f8637998543a1863b9c8543a186409f8653af88399a855eb98a%
+  53af8853af8862bd8b62bd8b79d48d6cc78c62bd8b5eb98a56b2895eb98a67c28b56b2895ab5896cc78cffffff85de91%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  85de9185de9172cd8d67c28b5ab5896cc78c5ab58943a1863598843799852e938437998545a28645a286409f8648a586%
+  4aa78745a2864da9875eb98a5eb98a5ab58962bd8b5ab58972cd8d6cc78c48a58662bd8b43a18650ac883b9c8548a586%
+  53af8872cd8d62bd8b85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  ffffff85de919cea9c85de919cea9c6cc78c72cd8d79d48d67c28b72cd8d50ac8848a5863598843e9d853598843b9c85%
+  399a8543a1863e9d8562bd8b62bd8b5ab58956b2895eb98a79d48d6cc78c67c28b62bd8b79d48d79d48d5eb98a6cc78c%
+  48a58643a18648a586409f865ab58972cd8d79d48d85de91ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff85de91ffffffffffff79d48d79d48d6cc78c72cd8d53af8853af885eb98a4aa787339684%
+  339684399a854da987409f864aa78750ac8845a28650ac8862bd8b4da98772cd8d6cc78c6cc78c72cd8d6cc78c53af88%
+  48a58667c28b72cd8d53af8856b2895eb98a4aa787409f865ab5894da9876cc78cffffff85de919cea9cffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff85de91ffffff9cea9cffffffffffff9cea9c85de9179d48d72cd8d6cc78c72cd8d%
+  62bd8b48a5864aa78745a2864aa7873b9c853e9d8543a18648a5864aa7874da98756b28967c28b67c28b67c28b9cea9c%
+  67c28b79d48d67c28b67c28b72cd8d72cd8d6cc78c5eb98a62bd8b72cd8d67c28b62bd8b6cc78c62bd8b9cea9c72cd8d%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff85de91ffffff9cea9c67c28b%
+  85de9172cd8d5eb98a56b28967c28b67c28b5eb98a50ac8853af885eb98a53af8848a58643a1864da98762bd8b67c28b%
+  67c28b5eb98a79d48d72cd8d56b28967c28b4da98756b28956b28950ac885ab58962bd8b5ab58985de9148a5866cc78c%
+  72cd8d79d48d9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9c79d48d72cd8d9cea9c6cc78c9cea9c72cd8d79d48d4aa78767c28b53af8853af885eb98a5ab58945a2865eb98a%
+  4aa78756b28953af8850ac885eb98a6cc78c6cc78c5eb98a79d48d72cd8d50ac885ab58972cd8d4da98762bd8b5eb98a%
+  72cd8d6cc78c5ab5899cea9c9cea9c6cc78c9cea9cffffff85de91ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff72cd8d79d48d72cd8d85de915eb98a85de916cc78c6cc78c79d48d6cc78c79d48d9cea9c%
+  56b28953af885ab58972cd8d4da9875ab5894da9875eb98a6cc78c72cd8d6cc78c67c28b67c28b53af8872cd8d5ab589%
+  5ab58950ac8850ac8856b28956b2895eb98a67c28b79d48d79d48d85de9179d48d9cea9c9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c72cd8d79d48d9cea9c6cc78c5eb98a5ab58972cd8d%
+  67c28b79d48d79d48d62bd8b5ab5895ab58972cd8d67c28b5ab58979d48d67c28b85de9167c28b72cd8d72cd8d72cd8d%
+  5eb98a62bd8b6cc78c62bd8b6cc78c4da9874da9874da98756b2895eb98a72cd8d72cd8d79d48d85de919cea9c9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c79d48d72cd8d%
+  67c28b6cc78c5ab58972cd8d6cc78c67c28b67c28b6cc78c79d48d85de9179d48d5eb98a6cc78c79d48d9cea9cffffff%
+  72cd8d5eb98a72cd8d72cd8d67c28b5eb98a5eb98a5eb98a53af8879d48d5eb98a79d48d6cc78c72cd8d79d48d9cea9c%
+  72cd8d9cea9c85de919cea9c85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c6cc78c79d48d9cea9c79d48d79d48d6cc78c6cc78c67c28b6cc78c79d48d72cd8d72cd8d85de91%
+  72cd8d72cd8d85de9172cd8d9cea9c62bd8b67c28b6cc78c72cd8d56b28950ac884aa7874da98767c28b67c28b72cd8d%
+  67c28b62bd8b67c28b85de9185de919cea9c9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff6cc78c85de9162bd8b72cd8d5ab5895ab58950ac8879d48d%
+  67c28b5ab58967c28b72cd8d72cd8d9cea9c9cea9cffffff79d48d79d48d79d48d72cd8d62bd8b62bd8b72cd8d48a586%
+  5eb98a5eb98a72cd8d6cc78c79d48d85de919cea9c9cea9c85de9185de919cea9cffffffffffffffffff9cea9c9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff79d48dffffff%
+  79d48d5ab5894aa78756b2895ab5895eb98a72cd8d6cc78c85de9185de919cea9c79d48d9cea9c85de919cea9c9cea9c%
+  85de9179d48d67c28b79d48d5eb98a72cd8d85de9172cd8d85de9179d48dffffff9cea9c9cea9c9cea9cffffff85de91%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffff85de9179d48d79d48d9cea9c9cea9c62bd8b6cc78c62bd8bffffff6cc78c9cea9c79d48d85de919cea9c85de91%
+  ffffff9cea9cffffff72cd8d9cea9c79d48d85de9185de91ffffff79d48d72cd8dffffff79d48d79d48d9cea9c9cea9c%
+  85de9185de919cea9cffffff9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de916cc78c72cd8d72cd8d6cc78c85de9172cd8d85de9185de91%
+  79d48dffffff72cd8d9cea9cffffff85de91ffffff9cea9c9cea9c85de919cea9cffffff9cea9c79d48d67c28bffffff%
+  6cc78c85de91ffffffffffffffffff85de919cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48dffffff85de91%
+  79d48d85de9167c28b45a28667c28b67c28b5eb98a6cc78c85de9185de91ffffff9cea9cffffff85de919cea9c9cea9c%
+  ffffff85de91ffffff9cea9c85de91ffffff85de919cea9c9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9c9cea9c9cea9c6cc78c67c28b43a1864da9876cc78c5eb98a5eb98a9cea9c79d48d9cea9cffffff%
+  ffffff9cea9c9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffff85de916cc78c85de91%
+  79d48dffffff85de916cc78c5ab58979d48d85de9185de9179d48dffffff72cd8dffffff9cea9c9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff79d48d%
+  6cc78c6cc78c72cd8d67c28b4aa78767c28b4da9875eb98a53af8867c28b67c28b5eb98a72cd8d67c28b79d48d72cd8d%
+  9cea9c85de91ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff85de9185de91ffffff85de9172cd8d56b28953af8853af8845a28643a1864aa78743a1862f948443a1863e9d85%
+  5ab5895ab58962bd8b5ab58985de9179d48d85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffff85de9172cd8d79d48d85de916cc78c50ac883b9c853799851e8982248d83228b82%
+  1f7c821e8382248d83399a85299083319584379985399a854aa7874da98767c28b6cc78c72cd8d9cea9c9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c72cd8d85de9179d48d56b28953af8850ac88359884%
+  3195842a9183238c831f8182228b821e8982208a82299083238c832a9183228b822e9384228b823b9c854da9875ab589%
+  79d48dffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d9cea9c79d48d85de919cea9c67c28b62bd8b%
+  62bd8b56b2895ab5894da9873e9d852c9283399a853b9c852f9484268e833b9c852990832a9183379985248d83359884%
+  2f94843b9c853195845ab5896cc78c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  6cc78c62bd8b6cc78c53af8829908343a1864da9872e93842f94842f94842a91831e8582238c833b9c85268e83248d83%
+  2e9384248d831e86821e87821e85821e8282238c833e9d855ab5895eb98a9cea9cffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9c72cd8d6cc78c6cc78c67c28b5eb98a48a586409f8653af8856b2895eb98a4aa7875eb98a3e9d85%
+  3e9d853b9c852f9484409f863e9d85399a853e9d85409f8643a186399a8543a1866cc78c85de9185de91ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff67c28b9cea9c67c28bffffff79d48d67c28b67c28b%
+  5ab58956b28962bd8b62bd8b4da98753af8848a5864da98745a28648a586399a854aa78750ac886cc78c79d48d79d48d%
+  79d48d9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de9162bd8b%
+  79d48d56b2894aa7872c928335988462bd8b53af884aa78756b28945a2865ab58953af884da9874aa78745a28656b289%
+  67c28b67c28b85de9179d48d85de91ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff79d48d9cea9cffffff79d48d79d48d9cea9cffffff85de91ffffffffffff9cea9cffffff85de91%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff2748811f7b82206981206b81206a81%
+  1f75811f75811f7e821e87823b9c8550ac8862bd8b72cd8d79d48d9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff141a81%
+  284a81264481264381274f81274d81245c81235d812264811f74812c928356b28985de919cea9cffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
 \draw[gp path] (6.780,5.785)--(6.780,2.197)--(10.368,2.197);
-\gpfill{rgb color={1.000,0.998,0.996}} (10.920,2.197)--(11.138,2.197)--(11.138,2.226)--(10.920,2.226)--cycle;
-\gpfill{rgb color={1.000,0.934,0.895}} (10.920,2.225)--(11.138,2.225)--(11.138,2.254)--(10.920,2.254)--cycle;
-\gpfill{rgb color={1.000,0.871,0.793}} (10.920,2.253)--(11.138,2.253)--(11.138,2.282)--(10.920,2.282)--cycle;
-\gpfill{rgb color={1.000,0.807,0.692}} (10.920,2.281)--(11.138,2.281)--(11.138,2.310)--(10.920,2.310)--cycle;
-\gpfill{rgb color={1.000,0.743,0.590}} (10.920,2.309)--(11.138,2.309)--(11.138,2.313)--(10.920,2.313)--cycle;
-\gpfill{rgb color={1.000,0.737,0.580}} (10.920,2.312)--(11.138,2.312)--(11.138,2.338)--(10.920,2.338)--cycle;
-\gpfill{rgb color={1.000,0.731,0.575}} (10.920,2.337)--(11.138,2.337)--(11.138,2.366)--(10.920,2.366)--cycle;
-\gpfill{rgb color={1.000,0.724,0.570}} (10.920,2.365)--(11.138,2.365)--(11.138,2.394)--(10.920,2.394)--cycle;
-\gpfill{rgb color={1.000,0.717,0.564}} (10.920,2.393)--(11.138,2.393)--(11.138,2.422)--(10.920,2.422)--cycle;
-\gpfill{rgb color={1.000,0.710,0.559}} (10.920,2.421)--(11.138,2.421)--(11.138,2.450)--(10.920,2.450)--cycle;
-\gpfill{rgb color={1.000,0.703,0.553}} (10.920,2.449)--(11.138,2.449)--(11.138,2.478)--(10.920,2.478)--cycle;
-\gpfill{rgb color={1.000,0.696,0.548}} (10.920,2.477)--(11.138,2.477)--(11.138,2.506)--(10.920,2.506)--cycle;
-\gpfill{rgb color={1.000,0.689,0.542}} (10.920,2.505)--(11.138,2.505)--(11.138,2.534)--(10.920,2.534)--cycle;
-\gpfill{rgb color={1.000,0.682,0.537}} (10.920,2.533)--(11.138,2.533)--(11.138,2.562)--(10.920,2.562)--cycle;
-\gpfill{rgb color={1.000,0.675,0.531}} (10.920,2.561)--(11.138,2.561)--(11.138,2.590)--(10.920,2.590)--cycle;
-\gpfill{rgb color={1.000,0.668,0.526}} (10.920,2.589)--(11.138,2.589)--(11.138,2.618)--(10.920,2.618)--cycle;
-\gpfill{rgb color={1.000,0.661,0.520}} (10.920,2.617)--(11.138,2.617)--(11.138,2.646)--(10.920,2.646)--cycle;
-\gpfill{rgb color={1.000,0.654,0.515}} (10.920,2.645)--(11.138,2.645)--(11.138,2.674)--(10.920,2.674)--cycle;
-\gpfill{rgb color={1.000,0.647,0.509}} (10.920,2.673)--(11.138,2.673)--(11.138,2.702)--(10.920,2.702)--cycle;
-\gpfill{rgb color={1.000,0.640,0.504}} (10.920,2.701)--(11.138,2.701)--(11.138,2.730)--(10.920,2.730)--cycle;
-\gpfill{rgb color={1.000,0.633,0.498}} (10.920,2.729)--(11.138,2.729)--(11.138,2.758)--(10.920,2.758)--cycle;
-\gpfill{rgb color={1.000,0.626,0.493}} (10.920,2.757)--(11.138,2.757)--(11.138,2.786)--(10.920,2.786)--cycle;
-\gpfill{rgb color={1.000,0.619,0.487}} (10.920,2.785)--(11.138,2.785)--(11.138,2.814)--(10.920,2.814)--cycle;
-\gpfill{rgb color={1.000,0.612,0.482}} (10.920,2.813)--(11.138,2.813)--(11.138,2.842)--(10.920,2.842)--cycle;
-\gpfill{rgb color={1.000,0.605,0.476}} (10.920,2.841)--(11.138,2.841)--(11.138,2.870)--(10.920,2.870)--cycle;
-\gpfill{rgb color={1.000,0.598,0.471}} (10.920,2.869)--(11.138,2.869)--(11.138,2.892)--(10.920,2.892)--cycle;
-\gpfill{rgb color={1.000,0.592,0.467}} (10.920,2.891)--(11.138,2.891)--(11.138,2.898)--(10.920,2.898)--cycle;
-\gpfill{rgb color={1.000,0.590,0.466}} (10.920,2.897)--(11.138,2.897)--(11.138,2.926)--(10.920,2.926)--cycle;
-\gpfill{rgb color={1.000,0.581,0.462}} (10.920,2.925)--(11.138,2.925)--(11.138,2.954)--(10.920,2.954)--cycle;
-\gpfill{rgb color={1.000,0.573,0.458}} (10.920,2.953)--(11.138,2.953)--(11.138,2.982)--(10.920,2.982)--cycle;
-\gpfill{rgb color={1.000,0.564,0.454}} (10.920,2.981)--(11.138,2.981)--(11.138,3.010)--(10.920,3.010)--cycle;
-\gpfill{rgb color={1.000,0.555,0.450}} (10.920,3.009)--(11.138,3.009)--(11.138,3.038)--(10.920,3.038)--cycle;
-\gpfill{rgb color={1.000,0.546,0.446}} (10.920,3.037)--(11.138,3.037)--(11.138,3.066)--(10.920,3.066)--cycle;
-\gpfill{rgb color={1.000,0.538,0.442}} (10.920,3.065)--(11.138,3.065)--(11.138,3.095)--(10.920,3.095)--cycle;
-\gpfill{rgb color={1.000,0.529,0.438}} (10.920,3.094)--(11.138,3.094)--(11.138,3.123)--(10.920,3.123)--cycle;
-\gpfill{rgb color={1.000,0.520,0.434}} (10.920,3.122)--(11.138,3.122)--(11.138,3.151)--(10.920,3.151)--cycle;
-\gpfill{rgb color={1.000,0.511,0.430}} (10.920,3.150)--(11.138,3.150)--(11.138,3.179)--(10.920,3.179)--cycle;
-\gpfill{rgb color={1.000,0.503,0.426}} (10.920,3.178)--(11.138,3.178)--(11.138,3.207)--(10.920,3.207)--cycle;
-\gpfill{rgb color={1.000,0.494,0.422}} (10.920,3.206)--(11.138,3.206)--(11.138,3.235)--(10.920,3.235)--cycle;
-\gpfill{rgb color={1.000,0.485,0.418}} (10.920,3.234)--(11.138,3.234)--(11.138,3.263)--(10.920,3.263)--cycle;
-\gpfill{rgb color={1.000,0.476,0.414}} (10.920,3.262)--(11.138,3.262)--(11.138,3.291)--(10.920,3.291)--cycle;
-\gpfill{rgb color={1.000,0.468,0.410}} (10.920,3.290)--(11.138,3.290)--(11.138,3.319)--(10.920,3.319)--cycle;
-\gpfill{rgb color={1.000,0.459,0.406}} (10.920,3.318)--(11.138,3.318)--(11.138,3.347)--(10.920,3.347)--cycle;
-\gpfill{rgb color={1.000,0.450,0.402}} (10.920,3.346)--(11.138,3.346)--(11.138,3.375)--(10.920,3.375)--cycle;
-\gpfill{rgb color={1.000,0.441,0.398}} (10.920,3.374)--(11.138,3.374)--(11.138,3.403)--(10.920,3.403)--cycle;
-\gpfill{rgb color={1.000,0.433,0.394}} (10.920,3.402)--(11.138,3.402)--(11.138,3.431)--(10.920,3.431)--cycle;
-\gpfill{rgb color={1.000,0.424,0.390}} (10.920,3.430)--(11.138,3.430)--(11.138,3.459)--(10.920,3.459)--cycle;
-\gpfill{rgb color={1.000,0.415,0.386}} (10.920,3.458)--(11.138,3.458)--(11.138,3.471)--(10.920,3.471)--cycle;
-\gpfill{rgb color={1.000,0.412,0.384}} (10.920,3.470)--(11.138,3.470)--(11.138,3.487)--(10.920,3.487)--cycle;
-\gpfill{rgb color={0.998,0.407,0.383}} (10.920,3.486)--(11.138,3.486)--(11.138,3.515)--(10.920,3.515)--cycle;
-\gpfill{rgb color={0.995,0.400,0.381}} (10.920,3.514)--(11.138,3.514)--(11.138,3.543)--(10.920,3.543)--cycle;
-\gpfill{rgb color={0.992,0.393,0.378}} (10.920,3.542)--(11.138,3.542)--(11.138,3.571)--(10.920,3.571)--cycle;
-\gpfill{rgb color={0.988,0.385,0.376}} (10.920,3.570)--(11.138,3.570)--(11.138,3.599)--(10.920,3.599)--cycle;
-\gpfill{rgb color={0.985,0.378,0.374}} (10.920,3.598)--(11.138,3.598)--(11.138,3.627)--(10.920,3.627)--cycle;
-\gpfill{rgb color={0.982,0.370,0.372}} (10.920,3.626)--(11.138,3.626)--(11.138,3.655)--(10.920,3.655)--cycle;
-\gpfill{rgb color={0.979,0.363,0.369}} (10.920,3.654)--(11.138,3.654)--(11.138,3.683)--(10.920,3.683)--cycle;
-\gpfill{rgb color={0.975,0.356,0.367}} (10.920,3.682)--(11.138,3.682)--(11.138,3.711)--(10.920,3.711)--cycle;
-\gpfill{rgb color={0.972,0.348,0.365}} (10.920,3.710)--(11.138,3.710)--(11.138,3.739)--(10.920,3.739)--cycle;
-\gpfill{rgb color={0.969,0.341,0.362}} (10.920,3.738)--(11.138,3.738)--(11.138,3.767)--(10.920,3.767)--cycle;
-\gpfill{rgb color={0.966,0.333,0.360}} (10.920,3.766)--(11.138,3.766)--(11.138,3.795)--(10.920,3.795)--cycle;
-\gpfill{rgb color={0.963,0.326,0.358}} (10.920,3.794)--(11.138,3.794)--(11.138,3.823)--(10.920,3.823)--cycle;
-\gpfill{rgb color={0.959,0.319,0.356}} (10.920,3.822)--(11.138,3.822)--(11.138,3.851)--(10.920,3.851)--cycle;
-\gpfill{rgb color={0.956,0.311,0.353}} (10.920,3.850)--(11.138,3.850)--(11.138,3.879)--(10.920,3.879)--cycle;
-\gpfill{rgb color={0.953,0.304,0.351}} (10.920,3.878)--(11.138,3.878)--(11.138,3.907)--(10.920,3.907)--cycle;
-\gpfill{rgb color={0.950,0.296,0.349}} (10.920,3.906)--(11.138,3.906)--(11.138,3.935)--(10.920,3.935)--cycle;
-\gpfill{rgb color={0.946,0.289,0.347}} (10.920,3.934)--(11.138,3.934)--(11.138,3.963)--(10.920,3.963)--cycle;
-\gpfill{rgb color={0.943,0.282,0.344}} (10.920,3.962)--(11.138,3.962)--(11.138,3.992)--(10.920,3.992)--cycle;
-\gpfill{rgb color={0.940,0.274,0.342}} (10.920,3.991)--(11.138,3.991)--(11.138,4.020)--(10.920,4.020)--cycle;
-\gpfill{rgb color={0.937,0.266,0.340}} (10.920,4.019)--(11.138,4.019)--(11.138,4.048)--(10.920,4.048)--cycle;
-\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.047)--(11.138,4.047)--(11.138,4.049)--(10.920,4.049)--cycle;
-\gpfill{rgb color={0.933,0.259,0.337}} (10.920,4.048)--(11.138,4.048)--(11.138,4.076)--(10.920,4.076)--cycle;
-\gpfill{rgb color={0.928,0.252,0.334}} (10.920,4.075)--(11.138,4.075)--(11.138,4.104)--(10.920,4.104)--cycle;
-\gpfill{rgb color={0.923,0.246,0.332}} (10.920,4.103)--(11.138,4.103)--(11.138,4.132)--(10.920,4.132)--cycle;
-\gpfill{rgb color={0.918,0.239,0.329}} (10.920,4.131)--(11.138,4.131)--(11.138,4.160)--(10.920,4.160)--cycle;
-\gpfill{rgb color={0.912,0.232,0.326}} (10.920,4.159)--(11.138,4.159)--(11.138,4.188)--(10.920,4.188)--cycle;
-\gpfill{rgb color={0.907,0.226,0.323}} (10.920,4.187)--(11.138,4.187)--(11.138,4.216)--(10.920,4.216)--cycle;
-\gpfill{rgb color={0.902,0.219,0.320}} (10.920,4.215)--(11.138,4.215)--(11.138,4.244)--(10.920,4.244)--cycle;
-\gpfill{rgb color={0.896,0.213,0.317}} (10.920,4.243)--(11.138,4.243)--(11.138,4.272)--(10.920,4.272)--cycle;
-\gpfill{rgb color={0.891,0.206,0.315}} (10.920,4.271)--(11.138,4.271)--(11.138,4.300)--(10.920,4.300)--cycle;
-\gpfill{rgb color={0.886,0.199,0.312}} (10.920,4.299)--(11.138,4.299)--(11.138,4.328)--(10.920,4.328)--cycle;
-\gpfill{rgb color={0.880,0.193,0.309}} (10.920,4.327)--(11.138,4.327)--(11.138,4.356)--(10.920,4.356)--cycle;
-\gpfill{rgb color={0.875,0.186,0.306}} (10.920,4.355)--(11.138,4.355)--(11.138,4.384)--(10.920,4.384)--cycle;
-\gpfill{rgb color={0.870,0.179,0.303}} (10.920,4.383)--(11.138,4.383)--(11.138,4.412)--(10.920,4.412)--cycle;
-\gpfill{rgb color={0.864,0.173,0.300}} (10.920,4.411)--(11.138,4.411)--(11.138,4.440)--(10.920,4.440)--cycle;
-\gpfill{rgb color={0.859,0.166,0.297}} (10.920,4.439)--(11.138,4.439)--(11.138,4.468)--(10.920,4.468)--cycle;
-\gpfill{rgb color={0.854,0.159,0.295}} (10.920,4.467)--(11.138,4.467)--(11.138,4.496)--(10.920,4.496)--cycle;
-\gpfill{rgb color={0.848,0.153,0.292}} (10.920,4.495)--(11.138,4.495)--(11.138,4.524)--(10.920,4.524)--cycle;
-\gpfill{rgb color={0.843,0.146,0.289}} (10.920,4.523)--(11.138,4.523)--(11.138,4.552)--(10.920,4.552)--cycle;
-\gpfill{rgb color={0.838,0.139,0.286}} (10.920,4.551)--(11.138,4.551)--(11.138,4.580)--(10.920,4.580)--cycle;
-\gpfill{rgb color={0.833,0.133,0.283}} (10.920,4.579)--(11.138,4.579)--(11.138,4.608)--(10.920,4.608)--cycle;
-\gpfill{rgb color={0.827,0.126,0.280}} (10.920,4.607)--(11.138,4.607)--(11.138,4.628)--(10.920,4.628)--cycle;
-\gpfill{rgb color={0.823,0.121,0.278}} (10.920,4.627)--(11.138,4.627)--(11.138,4.636)--(10.920,4.636)--cycle;
-\gpfill{rgb color={0.822,0.120,0.277}} (10.920,4.635)--(11.138,4.635)--(11.138,4.664)--(10.920,4.664)--cycle;
-\gpfill{rgb color={0.815,0.115,0.272}} (10.920,4.663)--(11.138,4.663)--(11.138,4.692)--(10.920,4.692)--cycle;
-\gpfill{rgb color={0.809,0.111,0.267}} (10.920,4.691)--(11.138,4.691)--(11.138,4.720)--(10.920,4.720)--cycle;
-\gpfill{rgb color={0.802,0.106,0.262}} (10.920,4.719)--(11.138,4.719)--(11.138,4.748)--(10.920,4.748)--cycle;
-\gpfill{rgb color={0.796,0.101,0.256}} (10.920,4.747)--(11.138,4.747)--(11.138,4.776)--(10.920,4.776)--cycle;
-\gpfill{rgb color={0.789,0.096,0.251}} (10.920,4.775)--(11.138,4.775)--(11.138,4.804)--(10.920,4.804)--cycle;
-\gpfill{rgb color={0.783,0.092,0.246}} (10.920,4.803)--(11.138,4.803)--(11.138,4.832)--(10.920,4.832)--cycle;
-\gpfill{rgb color={0.776,0.087,0.241}} (10.920,4.831)--(11.138,4.831)--(11.138,4.860)--(10.920,4.860)--cycle;
-\gpfill{rgb color={0.770,0.082,0.236}} (10.920,4.859)--(11.138,4.859)--(11.138,4.889)--(10.920,4.889)--cycle;
-\gpfill{rgb color={0.763,0.077,0.231}} (10.920,4.888)--(11.138,4.888)--(11.138,4.917)--(10.920,4.917)--cycle;
-\gpfill{rgb color={0.757,0.073,0.225}} (10.920,4.916)--(11.138,4.916)--(11.138,4.945)--(10.920,4.945)--cycle;
-\gpfill{rgb color={0.750,0.068,0.220}} (10.920,4.944)--(11.138,4.944)--(11.138,4.973)--(10.920,4.973)--cycle;
-\gpfill{rgb color={0.744,0.063,0.215}} (10.920,4.972)--(11.138,4.972)--(11.138,5.001)--(10.920,5.001)--cycle;
-\gpfill{rgb color={0.737,0.058,0.210}} (10.920,5.000)--(11.138,5.000)--(11.138,5.029)--(10.920,5.029)--cycle;
-\gpfill{rgb color={0.731,0.054,0.205}} (10.920,5.028)--(11.138,5.028)--(11.138,5.057)--(10.920,5.057)--cycle;
-\gpfill{rgb color={0.725,0.049,0.200}} (10.920,5.056)--(11.138,5.056)--(11.138,5.085)--(10.920,5.085)--cycle;
-\gpfill{rgb color={0.718,0.044,0.195}} (10.920,5.084)--(11.138,5.084)--(11.138,5.113)--(10.920,5.113)--cycle;
-\gpfill{rgb color={0.712,0.039,0.190}} (10.920,5.112)--(11.138,5.112)--(11.138,5.141)--(10.920,5.141)--cycle;
-\gpfill{rgb color={0.705,0.035,0.184}} (10.920,5.140)--(11.138,5.140)--(11.138,5.169)--(10.920,5.169)--cycle;
-\gpfill{rgb color={0.699,0.030,0.179}} (10.920,5.168)--(11.138,5.168)--(11.138,5.197)--(10.920,5.197)--cycle;
-\gpfill{rgb color={0.692,0.025,0.174}} (10.920,5.196)--(11.138,5.196)--(11.138,5.207)--(10.920,5.207)--cycle;
-\gpfill{rgb color={0.690,0.024,0.172}} (10.920,5.206)--(11.138,5.206)--(11.138,5.225)--(10.920,5.225)--cycle;
-\gpfill{rgb color={0.686,0.023,0.167}} (10.920,5.224)--(11.138,5.224)--(11.138,5.253)--(10.920,5.253)--cycle;
-\gpfill{rgb color={0.678,0.022,0.159}} (10.920,5.252)--(11.138,5.252)--(11.138,5.281)--(10.920,5.281)--cycle;
-\gpfill{rgb color={0.671,0.020,0.150}} (10.920,5.280)--(11.138,5.280)--(11.138,5.309)--(10.920,5.309)--cycle;
-\gpfill{rgb color={0.664,0.019,0.142}} (10.920,5.308)--(11.138,5.308)--(11.138,5.337)--(10.920,5.337)--cycle;
-\gpfill{rgb color={0.657,0.018,0.134}} (10.920,5.336)--(11.138,5.336)--(11.138,5.365)--(10.920,5.365)--cycle;
-\gpfill{rgb color={0.650,0.017,0.125}} (10.920,5.364)--(11.138,5.364)--(11.138,5.393)--(10.920,5.393)--cycle;
-\gpfill{rgb color={0.643,0.016,0.117}} (10.920,5.392)--(11.138,5.392)--(11.138,5.421)--(10.920,5.421)--cycle;
-\gpfill{rgb color={0.636,0.015,0.109}} (10.920,5.420)--(11.138,5.420)--(11.138,5.449)--(10.920,5.449)--cycle;
-\gpfill{rgb color={0.629,0.014,0.100}} (10.920,5.448)--(11.138,5.448)--(11.138,5.477)--(10.920,5.477)--cycle;
-\gpfill{rgb color={0.622,0.013,0.092}} (10.920,5.476)--(11.138,5.476)--(11.138,5.505)--(10.920,5.505)--cycle;
-\gpfill{rgb color={0.615,0.011,0.083}} (10.920,5.504)--(11.138,5.504)--(11.138,5.533)--(10.920,5.533)--cycle;
-\gpfill{rgb color={0.608,0.010,0.075}} (10.920,5.532)--(11.138,5.532)--(11.138,5.561)--(10.920,5.561)--cycle;
-\gpfill{rgb color={0.601,0.009,0.067}} (10.920,5.560)--(11.138,5.560)--(11.138,5.589)--(10.920,5.589)--cycle;
-\gpfill{rgb color={0.594,0.008,0.058}} (10.920,5.588)--(11.138,5.588)--(11.138,5.617)--(10.920,5.617)--cycle;
-\gpfill{rgb color={0.587,0.007,0.050}} (10.920,5.616)--(11.138,5.616)--(11.138,5.645)--(10.920,5.645)--cycle;
-\gpfill{rgb color={0.580,0.006,0.042}} (10.920,5.644)--(11.138,5.644)--(11.138,5.673)--(10.920,5.673)--cycle;
-\gpfill{rgb color={0.573,0.005,0.033}} (10.920,5.672)--(11.138,5.672)--(11.138,5.701)--(10.920,5.701)--cycle;
-\gpfill{rgb color={0.566,0.003,0.025}} (10.920,5.700)--(11.138,5.700)--(11.138,5.729)--(10.920,5.729)--cycle;
-\gpfill{rgb color={0.559,0.002,0.017}} (10.920,5.728)--(11.138,5.728)--(11.138,5.757)--(10.920,5.757)--cycle;
-\gpfill{rgb color={0.552,0.001,0.008}} (10.920,5.756)--(11.138,5.756)--(11.138,5.785)--(10.920,5.785)--cycle;
+\gpfill{rgb color={0.998,1.000,0.998}} (10.920,2.197)--(11.138,2.197)--(11.138,2.226)--(10.920,2.226)--cycle;
+\gpfill{rgb color={0.956,0.994,0.950}} (10.920,2.225)--(11.138,2.225)--(11.138,2.254)--(10.920,2.254)--cycle;
+\gpfill{rgb color={0.913,0.987,0.903}} (10.920,2.253)--(11.138,2.253)--(11.138,2.282)--(10.920,2.282)--cycle;
+\gpfill{rgb color={0.870,0.981,0.855}} (10.920,2.281)--(11.138,2.281)--(11.138,2.310)--(10.920,2.310)--cycle;
+\gpfill{rgb color={0.828,0.975,0.807}} (10.920,2.309)--(11.138,2.309)--(11.138,2.338)--(10.920,2.338)--cycle;
+\gpfill{rgb color={0.785,0.969,0.759}} (10.920,2.337)--(11.138,2.337)--(11.138,2.366)--(10.920,2.366)--cycle;
+\gpfill{rgb color={0.743,0.962,0.711}} (10.920,2.365)--(11.138,2.365)--(11.138,2.394)--(10.920,2.394)--cycle;
+\gpfill{rgb color={0.700,0.956,0.663}} (10.920,2.393)--(11.138,2.393)--(11.138,2.409)--(10.920,2.409)--cycle;
+\gpfill{rgb color={0.678,0.953,0.639}} (10.920,2.408)--(11.138,2.408)--(11.138,2.422)--(10.920,2.422)--cycle;
+\gpfill{rgb color={0.672,0.950,0.636}} (10.920,2.421)--(11.138,2.421)--(11.138,2.450)--(10.920,2.450)--cycle;
+\gpfill{rgb color={0.660,0.943,0.631}} (10.920,2.449)--(11.138,2.449)--(11.138,2.478)--(10.920,2.478)--cycle;
+\gpfill{rgb color={0.648,0.937,0.626}} (10.920,2.477)--(11.138,2.477)--(11.138,2.506)--(10.920,2.506)--cycle;
+\gpfill{rgb color={0.636,0.930,0.620}} (10.920,2.505)--(11.138,2.505)--(11.138,2.534)--(10.920,2.534)--cycle;
+\gpfill{rgb color={0.623,0.924,0.615}} (10.920,2.533)--(11.138,2.533)--(11.138,2.562)--(10.920,2.562)--cycle;
+\gpfill{rgb color={0.611,0.917,0.609}} (10.920,2.561)--(11.138,2.561)--(11.138,2.590)--(10.920,2.590)--cycle;
+\gpfill{rgb color={0.599,0.911,0.604}} (10.920,2.589)--(11.138,2.589)--(11.138,2.618)--(10.920,2.618)--cycle;
+\gpfill{rgb color={0.587,0.904,0.598}} (10.920,2.617)--(11.138,2.617)--(11.138,2.646)--(10.920,2.646)--cycle;
+\gpfill{rgb color={0.575,0.898,0.593}} (10.920,2.645)--(11.138,2.645)--(11.138,2.674)--(10.920,2.674)--cycle;
+\gpfill{rgb color={0.562,0.891,0.587}} (10.920,2.673)--(11.138,2.673)--(11.138,2.702)--(10.920,2.702)--cycle;
+\gpfill{rgb color={0.550,0.885,0.582}} (10.920,2.701)--(11.138,2.701)--(11.138,2.730)--(10.920,2.730)--cycle;
+\gpfill{rgb color={0.538,0.878,0.576}} (10.920,2.729)--(11.138,2.729)--(11.138,2.758)--(10.920,2.758)--cycle;
+\gpfill{rgb color={0.526,0.872,0.571}} (10.920,2.757)--(11.138,2.757)--(11.138,2.786)--(10.920,2.786)--cycle;
+\gpfill{rgb color={0.513,0.865,0.565}} (10.920,2.785)--(11.138,2.785)--(11.138,2.814)--(10.920,2.814)--cycle;
+\gpfill{rgb color={0.501,0.859,0.560}} (10.920,2.813)--(11.138,2.813)--(11.138,2.831)--(10.920,2.831)--cycle;
+\gpfill{rgb color={0.494,0.855,0.557}} (10.920,2.830)--(11.138,2.830)--(11.138,2.842)--(10.920,2.842)--cycle;
+\gpfill{rgb color={0.491,0.852,0.557}} (10.920,2.841)--(11.138,2.841)--(11.138,2.870)--(10.920,2.870)--cycle;
+\gpfill{rgb color={0.484,0.845,0.556}} (10.920,2.869)--(11.138,2.869)--(11.138,2.898)--(10.920,2.898)--cycle;
+\gpfill{rgb color={0.478,0.838,0.555}} (10.920,2.897)--(11.138,2.897)--(11.138,2.926)--(10.920,2.926)--cycle;
+\gpfill{rgb color={0.471,0.831,0.554}} (10.920,2.925)--(11.138,2.925)--(11.138,2.954)--(10.920,2.954)--cycle;
+\gpfill{rgb color={0.464,0.824,0.553}} (10.920,2.953)--(11.138,2.953)--(11.138,2.982)--(10.920,2.982)--cycle;
+\gpfill{rgb color={0.457,0.817,0.553}} (10.920,2.981)--(11.138,2.981)--(11.138,3.010)--(10.920,3.010)--cycle;
+\gpfill{rgb color={0.451,0.810,0.552}} (10.920,3.009)--(11.138,3.009)--(11.138,3.038)--(10.920,3.038)--cycle;
+\gpfill{rgb color={0.444,0.803,0.551}} (10.920,3.037)--(11.138,3.037)--(11.138,3.066)--(10.920,3.066)--cycle;
+\gpfill{rgb color={0.437,0.796,0.550}} (10.920,3.065)--(11.138,3.065)--(11.138,3.095)--(10.920,3.095)--cycle;
+\gpfill{rgb color={0.430,0.788,0.549}} (10.920,3.094)--(11.138,3.094)--(11.138,3.123)--(10.920,3.123)--cycle;
+\gpfill{rgb color={0.423,0.781,0.549}} (10.920,3.122)--(11.138,3.122)--(11.138,3.151)--(10.920,3.151)--cycle;
+\gpfill{rgb color={0.417,0.774,0.548}} (10.920,3.150)--(11.138,3.150)--(11.138,3.179)--(10.920,3.179)--cycle;
+\gpfill{rgb color={0.410,0.767,0.547}} (10.920,3.178)--(11.138,3.178)--(11.138,3.207)--(10.920,3.207)--cycle;
+\gpfill{rgb color={0.403,0.760,0.546}} (10.920,3.206)--(11.138,3.206)--(11.138,3.235)--(10.920,3.235)--cycle;
+\gpfill{rgb color={0.396,0.753,0.546}} (10.920,3.234)--(11.138,3.234)--(11.138,3.253)--(10.920,3.253)--cycle;
+\gpfill{rgb color={0.392,0.749,0.545}} (10.920,3.252)--(11.138,3.252)--(11.138,3.263)--(10.920,3.263)--cycle;
+\gpfill{rgb color={0.389,0.746,0.545}} (10.920,3.262)--(11.138,3.262)--(11.138,3.291)--(10.920,3.291)--cycle;
+\gpfill{rgb color={0.381,0.739,0.543}} (10.920,3.290)--(11.138,3.290)--(11.138,3.319)--(10.920,3.319)--cycle;
+\gpfill{rgb color={0.373,0.731,0.542}} (10.920,3.318)--(11.138,3.318)--(11.138,3.347)--(10.920,3.347)--cycle;
+\gpfill{rgb color={0.365,0.724,0.541}} (10.920,3.346)--(11.138,3.346)--(11.138,3.375)--(10.920,3.375)--cycle;
+\gpfill{rgb color={0.357,0.716,0.539}} (10.920,3.374)--(11.138,3.374)--(11.138,3.403)--(10.920,3.403)--cycle;
+\gpfill{rgb color={0.349,0.708,0.538}} (10.920,3.402)--(11.138,3.402)--(11.138,3.431)--(10.920,3.431)--cycle;
+\gpfill{rgb color={0.341,0.701,0.537}} (10.920,3.430)--(11.138,3.430)--(11.138,3.459)--(10.920,3.459)--cycle;
+\gpfill{rgb color={0.333,0.693,0.535}} (10.920,3.458)--(11.138,3.458)--(11.138,3.487)--(10.920,3.487)--cycle;
+\gpfill{rgb color={0.325,0.686,0.534}} (10.920,3.486)--(11.138,3.486)--(11.138,3.515)--(10.920,3.515)--cycle;
+\gpfill{rgb color={0.316,0.678,0.533}} (10.920,3.514)--(11.138,3.514)--(11.138,3.543)--(10.920,3.543)--cycle;
+\gpfill{rgb color={0.308,0.671,0.532}} (10.920,3.542)--(11.138,3.542)--(11.138,3.571)--(10.920,3.571)--cycle;
+\gpfill{rgb color={0.300,0.663,0.530}} (10.920,3.570)--(11.138,3.570)--(11.138,3.599)--(10.920,3.599)--cycle;
+\gpfill{rgb color={0.292,0.656,0.529}} (10.920,3.598)--(11.138,3.598)--(11.138,3.627)--(10.920,3.627)--cycle;
+\gpfill{rgb color={0.284,0.648,0.528}} (10.920,3.626)--(11.138,3.626)--(11.138,3.655)--(10.920,3.655)--cycle;
+\gpfill{rgb color={0.276,0.641,0.526}} (10.920,3.654)--(11.138,3.654)--(11.138,3.675)--(10.920,3.675)--cycle;
+\gpfill{rgb color={0.270,0.635,0.525}} (10.920,3.674)--(11.138,3.674)--(11.138,3.683)--(10.920,3.683)--cycle;
+\gpfill{rgb color={0.267,0.633,0.525}} (10.920,3.682)--(11.138,3.682)--(11.138,3.711)--(10.920,3.711)--cycle;
+\gpfill{rgb color={0.257,0.627,0.524}} (10.920,3.710)--(11.138,3.710)--(11.138,3.739)--(10.920,3.739)--cycle;
+\gpfill{rgb color={0.247,0.620,0.523}} (10.920,3.738)--(11.138,3.738)--(11.138,3.767)--(10.920,3.767)--cycle;
+\gpfill{rgb color={0.237,0.614,0.522}} (10.920,3.766)--(11.138,3.766)--(11.138,3.795)--(10.920,3.795)--cycle;
+\gpfill{rgb color={0.227,0.607,0.521}} (10.920,3.794)--(11.138,3.794)--(11.138,3.823)--(10.920,3.823)--cycle;
+\gpfill{rgb color={0.217,0.601,0.520}} (10.920,3.822)--(11.138,3.822)--(11.138,3.851)--(10.920,3.851)--cycle;
+\gpfill{rgb color={0.207,0.594,0.519}} (10.920,3.850)--(11.138,3.850)--(11.138,3.879)--(10.920,3.879)--cycle;
+\gpfill{rgb color={0.196,0.588,0.518}} (10.920,3.878)--(11.138,3.878)--(11.138,3.907)--(10.920,3.907)--cycle;
+\gpfill{rgb color={0.186,0.581,0.517}} (10.920,3.906)--(11.138,3.906)--(11.138,3.935)--(10.920,3.935)--cycle;
+\gpfill{rgb color={0.176,0.575,0.516}} (10.920,3.934)--(11.138,3.934)--(11.138,3.963)--(10.920,3.963)--cycle;
+\gpfill{rgb color={0.166,0.568,0.515}} (10.920,3.962)--(11.138,3.962)--(11.138,3.992)--(10.920,3.992)--cycle;
+\gpfill{rgb color={0.156,0.562,0.514}} (10.920,3.991)--(11.138,3.991)--(11.138,4.020)--(10.920,4.020)--cycle;
+\gpfill{rgb color={0.145,0.555,0.513}} (10.920,4.019)--(11.138,4.019)--(11.138,4.048)--(10.920,4.048)--cycle;
+\gpfill{rgb color={0.135,0.549,0.512}} (10.920,4.047)--(11.138,4.047)--(11.138,4.076)--(10.920,4.076)--cycle;
+\gpfill{rgb color={0.125,0.542,0.511}} (10.920,4.075)--(11.138,4.075)--(11.138,4.097)--(10.920,4.097)--cycle;
+\gpfill{rgb color={0.118,0.537,0.510}} (10.920,4.096)--(11.138,4.096)--(11.138,4.104)--(10.920,4.104)--cycle;
+\gpfill{rgb color={0.118,0.535,0.510}} (10.920,4.103)--(11.138,4.103)--(11.138,4.132)--(10.920,4.132)--cycle;
+\gpfill{rgb color={0.118,0.527,0.509}} (10.920,4.131)--(11.138,4.131)--(11.138,4.160)--(10.920,4.160)--cycle;
+\gpfill{rgb color={0.119,0.519,0.509}} (10.920,4.159)--(11.138,4.159)--(11.138,4.188)--(10.920,4.188)--cycle;
+\gpfill{rgb color={0.119,0.511,0.509}} (10.920,4.187)--(11.138,4.187)--(11.138,4.216)--(10.920,4.216)--cycle;
+\gpfill{rgb color={0.120,0.503,0.509}} (10.920,4.215)--(11.138,4.215)--(11.138,4.244)--(10.920,4.244)--cycle;
+\gpfill{rgb color={0.120,0.495,0.508}} (10.920,4.243)--(11.138,4.243)--(11.138,4.272)--(10.920,4.272)--cycle;
+\gpfill{rgb color={0.121,0.487,0.508}} (10.920,4.271)--(11.138,4.271)--(11.138,4.300)--(10.920,4.300)--cycle;
+\gpfill{rgb color={0.121,0.479,0.508}} (10.920,4.299)--(11.138,4.299)--(11.138,4.328)--(10.920,4.328)--cycle;
+\gpfill{rgb color={0.122,0.471,0.508}} (10.920,4.327)--(11.138,4.327)--(11.138,4.356)--(10.920,4.356)--cycle;
+\gpfill{rgb color={0.122,0.463,0.507}} (10.920,4.355)--(11.138,4.355)--(11.138,4.384)--(10.920,4.384)--cycle;
+\gpfill{rgb color={0.123,0.454,0.507}} (10.920,4.383)--(11.138,4.383)--(11.138,4.412)--(10.920,4.412)--cycle;
+\gpfill{rgb color={0.124,0.446,0.507}} (10.920,4.411)--(11.138,4.411)--(11.138,4.440)--(10.920,4.440)--cycle;
+\gpfill{rgb color={0.124,0.438,0.507}} (10.920,4.439)--(11.138,4.439)--(11.138,4.468)--(10.920,4.468)--cycle;
+\gpfill{rgb color={0.125,0.430,0.506}} (10.920,4.467)--(11.138,4.467)--(11.138,4.496)--(10.920,4.496)--cycle;
+\gpfill{rgb color={0.125,0.422,0.506}} (10.920,4.495)--(11.138,4.495)--(11.138,4.519)--(10.920,4.519)--cycle;
+\gpfill{rgb color={0.126,0.416,0.506}} (10.920,4.518)--(11.138,4.518)--(11.138,4.524)--(10.920,4.524)--cycle;
+\gpfill{rgb color={0.126,0.414,0.506}} (10.920,4.523)--(11.138,4.523)--(11.138,4.552)--(10.920,4.552)--cycle;
+\gpfill{rgb color={0.128,0.406,0.506}} (10.920,4.551)--(11.138,4.551)--(11.138,4.580)--(10.920,4.580)--cycle;
+\gpfill{rgb color={0.130,0.398,0.506}} (10.920,4.579)--(11.138,4.579)--(11.138,4.608)--(10.920,4.608)--cycle;
+\gpfill{rgb color={0.132,0.390,0.506}} (10.920,4.607)--(11.138,4.607)--(11.138,4.636)--(10.920,4.636)--cycle;
+\gpfill{rgb color={0.134,0.382,0.506}} (10.920,4.635)--(11.138,4.635)--(11.138,4.664)--(10.920,4.664)--cycle;
+\gpfill{rgb color={0.136,0.374,0.506}} (10.920,4.663)--(11.138,4.663)--(11.138,4.692)--(10.920,4.692)--cycle;
+\gpfill{rgb color={0.138,0.366,0.506}} (10.920,4.691)--(11.138,4.691)--(11.138,4.720)--(10.920,4.720)--cycle;
+\gpfill{rgb color={0.140,0.358,0.506}} (10.920,4.719)--(11.138,4.719)--(11.138,4.748)--(10.920,4.748)--cycle;
+\gpfill{rgb color={0.143,0.350,0.506}} (10.920,4.747)--(11.138,4.747)--(11.138,4.776)--(10.920,4.776)--cycle;
+\gpfill{rgb color={0.145,0.342,0.506}} (10.920,4.775)--(11.138,4.775)--(11.138,4.804)--(10.920,4.804)--cycle;
+\gpfill{rgb color={0.147,0.334,0.506}} (10.920,4.803)--(11.138,4.803)--(11.138,4.832)--(10.920,4.832)--cycle;
+\gpfill{rgb color={0.149,0.325,0.506}} (10.920,4.831)--(11.138,4.831)--(11.138,4.860)--(10.920,4.860)--cycle;
+\gpfill{rgb color={0.151,0.317,0.506}} (10.920,4.859)--(11.138,4.859)--(11.138,4.889)--(10.920,4.889)--cycle;
+\gpfill{rgb color={0.153,0.309,0.506}} (10.920,4.888)--(11.138,4.888)--(11.138,4.917)--(10.920,4.917)--cycle;
+\gpfill{rgb color={0.155,0.301,0.506}} (10.920,4.916)--(11.138,4.916)--(11.138,4.941)--(10.920,4.941)--cycle;
+\gpfill{rgb color={0.157,0.294,0.506}} (10.920,4.940)--(11.138,4.940)--(11.138,4.945)--(10.920,4.945)--cycle;
+\gpfill{rgb color={0.157,0.293,0.506}} (10.920,4.944)--(11.138,4.944)--(11.138,4.973)--(10.920,4.973)--cycle;
+\gpfill{rgb color={0.155,0.285,0.506}} (10.920,4.972)--(11.138,4.972)--(11.138,5.001)--(10.920,5.001)--cycle;
+\gpfill{rgb color={0.153,0.276,0.506}} (10.920,5.000)--(11.138,5.000)--(11.138,5.029)--(10.920,5.029)--cycle;
+\gpfill{rgb color={0.151,0.268,0.506}} (10.920,5.028)--(11.138,5.028)--(11.138,5.057)--(10.920,5.057)--cycle;
+\gpfill{rgb color={0.149,0.260,0.506}} (10.920,5.056)--(11.138,5.056)--(11.138,5.085)--(10.920,5.085)--cycle;
+\gpfill{rgb color={0.147,0.251,0.506}} (10.920,5.084)--(11.138,5.084)--(11.138,5.113)--(10.920,5.113)--cycle;
+\gpfill{rgb color={0.146,0.243,0.506}} (10.920,5.112)--(11.138,5.112)--(11.138,5.141)--(10.920,5.141)--cycle;
+\gpfill{rgb color={0.144,0.235,0.506}} (10.920,5.140)--(11.138,5.140)--(11.138,5.169)--(10.920,5.169)--cycle;
+\gpfill{rgb color={0.142,0.226,0.506}} (10.920,5.168)--(11.138,5.168)--(11.138,5.197)--(10.920,5.197)--cycle;
+\gpfill{rgb color={0.140,0.218,0.506}} (10.920,5.196)--(11.138,5.196)--(11.138,5.225)--(10.920,5.225)--cycle;
+\gpfill{rgb color={0.138,0.210,0.506}} (10.920,5.224)--(11.138,5.224)--(11.138,5.253)--(10.920,5.253)--cycle;
+\gpfill{rgb color={0.137,0.201,0.506}} (10.920,5.252)--(11.138,5.252)--(11.138,5.281)--(10.920,5.281)--cycle;
+\gpfill{rgb color={0.135,0.193,0.506}} (10.920,5.280)--(11.138,5.280)--(11.138,5.309)--(10.920,5.309)--cycle;
+\gpfill{rgb color={0.133,0.185,0.506}} (10.920,5.308)--(11.138,5.308)--(11.138,5.337)--(10.920,5.337)--cycle;
+\gpfill{rgb color={0.131,0.176,0.506}} (10.920,5.336)--(11.138,5.336)--(11.138,5.363)--(10.920,5.363)--cycle;
+\gpfill{rgb color={0.129,0.169,0.506}} (10.920,5.362)--(11.138,5.362)--(11.138,5.365)--(10.920,5.365)--cycle;
+\gpfill{rgb color={0.129,0.168,0.506}} (10.920,5.364)--(11.138,5.364)--(11.138,5.393)--(10.920,5.393)--cycle;
+\gpfill{rgb color={0.120,0.157,0.506}} (10.920,5.392)--(11.138,5.392)--(11.138,5.421)--(10.920,5.421)--cycle;
+\gpfill{rgb color={0.112,0.145,0.505}} (10.920,5.420)--(11.138,5.420)--(11.138,5.449)--(10.920,5.449)--cycle;
+\gpfill{rgb color={0.103,0.134,0.505}} (10.920,5.448)--(11.138,5.448)--(11.138,5.477)--(10.920,5.477)--cycle;
+\gpfill{rgb color={0.094,0.123,0.505}} (10.920,5.476)--(11.138,5.476)--(11.138,5.505)--(10.920,5.505)--cycle;
+\gpfill{rgb color={0.086,0.112,0.505}} (10.920,5.504)--(11.138,5.504)--(11.138,5.533)--(10.920,5.533)--cycle;
+\gpfill{rgb color={0.077,0.101,0.504}} (10.920,5.532)--(11.138,5.532)--(11.138,5.561)--(10.920,5.561)--cycle;
+\gpfill{rgb color={0.069,0.089,0.504}} (10.920,5.560)--(11.138,5.560)--(11.138,5.589)--(10.920,5.589)--cycle;
+\gpfill{rgb color={0.060,0.078,0.504}} (10.920,5.588)--(11.138,5.588)--(11.138,5.617)--(10.920,5.617)--cycle;
+\gpfill{rgb color={0.052,0.067,0.504}} (10.920,5.616)--(11.138,5.616)--(11.138,5.645)--(10.920,5.645)--cycle;
+\gpfill{rgb color={0.043,0.056,0.503}} (10.920,5.644)--(11.138,5.644)--(11.138,5.673)--(10.920,5.673)--cycle;
+\gpfill{rgb color={0.034,0.045,0.503}} (10.920,5.672)--(11.138,5.672)--(11.138,5.701)--(10.920,5.701)--cycle;
+\gpfill{rgb color={0.026,0.034,0.503}} (10.920,5.700)--(11.138,5.700)--(11.138,5.729)--(10.920,5.729)--cycle;
+\gpfill{rgb color={0.017,0.022,0.502}} (10.920,5.728)--(11.138,5.728)--(11.138,5.757)--(10.920,5.757)--cycle;
+\gpfill{rgb color={0.009,0.011,0.502}} (10.920,5.756)--(11.138,5.756)--(11.138,5.785)--(10.920,5.785)--cycle;
 \draw[gp path] (10.920,2.197)--(11.138,2.197)--(11.138,5.785)--(10.920,5.785)--cycle;

### 2016-04-20 paper/gen-graph-unconnected-heatmap.tex
More gratuitous mucking around with the figures
Handle headers on first line
Green / blue instead of blood splatters

@@
 %% generated with GNUPLOT 5.0p0 (Lua 5.2; terminal rev. 99, script rev. 100)
-%% Tue 12 Apr 2016 14:19:16 AEST
+%% Wed 20 Apr 2016 12:04:42 AEST
 \tikzset{every node/.append style={font={\scriptsize}}}
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dff9f7dffac88ff9f7d%
-  ff9f7dffac88ff9576ff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffcf1d45ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffca1941ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffc6163dffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffc6163effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ff9576ffffffffac88c7173fffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffffffc1133affffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ff9f7dc6163effffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88%
-  ffffffffffffffac88ffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffc4143cffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffac88ffac88ff9f7dffac88ff9f7dffffffc3143b%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffff9f7d%
-  ffac88ffffffffffffff9f7dc1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffac88ffffff%
-  ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88c4153cffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9576ffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88c2133affffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffffffff9576ffac88%
-  ff9576ffffffff9f7dc6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
-  ffac88ffffffffac88ffac88ffffffffac88ffac88ff846ec01239ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7d%
-  ffffffffffffffffffffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffc4153cffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
-  ff9f7dffffffbd0f36ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88%
-  ff9f7dffac88ff9576ff9f7dff9576ffffffffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffac88%
-  ffac88ffffffff9f7dffffffffac88ffac88ff9576ffffffffac88ff9f7dff9576ffffffc1133affffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffff%
-  ff9f7dffffffffffffffffffffac88ffffffffffffffac88ff9f7dff9576ffffffffac88ffffffff9f7dff9f7dff8c72%
-  ff9f7dc01238ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffffffffffffff9f7dffffffff9576ffac88ffac88%
-  ffac88ff9f7dff9576ff846effac88ffac88c1133affffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffffffffffffffac88ff9f7d%
-  ffffffff9f7dff9576ff9f7dffac88ff9576ffac88ff9f7dff846eff8c72ff8c72c3143bffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ffac88ffac88%
-  ffffffff9f7dff9f7dff9f7dff9f7dffac88ff9f7dffac88ffac88ffac88ff846eff9576ff9f7dff9f7dff9f7dff9576%
-  c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffffffac88ffac88ffac88ff9576ffac88ffffffffac88%
-  ff9576ff9576ff846eff846effffffbd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9576ff846eff9f7dffffffff9f7d%
-  ffffffffffffff9f7dffffffff9f7dffffffff9576ff9576ffac88ffac88c01239ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9576%
-  ffac88ffac88ff9f7dff846effffffffac88ff846eff9576ff9576ffac88ff8c72ff9f7dff8c72ffffffff9f7dbf1138%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffac88ffffff%
-  ffffffffac88ffffffffac88ffffffff9576ff9f7dffac88ff8c72ff9576ff8c72ffac88ffac88ff9f7dff9f7dffac88%
-  ffffffff8c72ff846effac88c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ffffffff9f7dff9f7dffac88ffac88ff8c72ff9f7dff9f7d%
-  ff8c72ff9576ff8c72ff9f7dff8c72ff9f7dff846eff8c72ff7e6cc11239ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffac88ff9f7dffac88%
-  ffac88ffac88ff9f7dff7e6cffac88ff9f7dffffffff9576ff9f7dff9576ff9f7dff9576ffac88fb605fc2133bffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffac88%
-  ffffffffac88ffffffff846eff846eff9576ffac88ff846effffffff8c72ff9576ff9f7dff9576ff846effac88ff7869%
-  ff7e6cff9576ff8c72c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
-  ffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffac88ff846eff846eff9576ff7869ffffffff8c72ffffff%
-  ff8c72ffac88ff8c72ff7e6cff9576ff8c72ff846eff9576c01239ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffac88ff9f7dffac88ff9576%
-  ffac88ffffffff846eff9f7dff8c72ff846eff7e6cff9f7dff7869ff9576ff7e6cff8c72ff7e6cc1133affffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576%
-  ff8c72ff9576ffac88ff7e6cffac88ff9f7dffac88ff846eff8c72ff9f7dff9576ff9576ff7367ff6f65ff846eff8c72%
-  ff7e6cff7e6cc3143bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffac88ffac88ff9576ffac88ffffffffac88ffac88ff9576ff9f7dffac88ff7869ffac88ff9f7dff8c72ff7869%
-  ff8c72ff9f7dff7367ff7e6cff9576ff6f65ff7e6cc6163dffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffff9576ffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9f7dffac88ff846eff7e6c%
-  ff7869ff846effac88ffac88ffac88ff9f7dff7e6cffac88ff846eff7869ff8c72ff8c72c4153cffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffac88ffffffffac88ff8c72ffffffffffff%
-  ff8c72ff9f7dff9f7dff9576ff7869ff9f7dff7e6cff7869ff8c72ffac88ff7869ffac88ff8c72ff8c72ff7869ff7e6c%
-  ff9576c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ff9f7dff9f7dffffffffac88ffffff%
-  ff9f7dffac88ff8c72ff8c72ff9576ffffffff9f7dffac88ff846eff7869ff9576ffffffff846eff9576ff8c72ff7869%
-  ff846eff9576ff7e6cff6b63ff7e6cff8c72cb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88%
-  ff9f7dff9f7dff9f7dff9576ffac88ffffffff8c72ff9f7dffac88ff8c72ff9f7dff8c72ff9576ff7e6cff7869ffac88%
-  ff8c72ff9576ff7869ff846eff7e6cff6b63ffac88ff9576ff846eff9576ff8c72c8183fffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ff9f7dffac88%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffff846effffffffffffffac88ff9f7dff7869ff8c72ff8c72%
-  ff9576ff8c72ff846eff9576ff7e6cff846eff846eff7e6cff7367ff7e6cff9576ff7e6cff8c72ff9f7dff9f7dff7e6c%
-  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dff9f7dffffffffac88ff9576ffac88ffac88%
-  ff9f7dffffffffac88ff846effffffffac88ff9f7dff846eff6f65ff7367ff846eff9576ff8c72ff846eff846eff7e6c%
-  ff9576ff846eff8c72ff8c72ff6b63c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffac88ff7e6cff846eff9576ff846eff9f7dff846eff7e6cff9f7dff7e6cff7869ff8c72ff7e6cff9f7d%
-  ff846eff8c72ff9f7dffac88ff9576ff846eff8c72ff7367ff846effac88c7173effffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
-  ffac88ffffffffffffffffffffac88ffac88ff9576ff9576ffac88ffac88ff9576ff9576ffac88ff9f7dff9576ff9576%
-  ff9576ff7e6cff9576ff7e6cff7e6cff846eff8c72ff9576ff7869ff8c72ff7869ff7e6cfd6561fe6862ff7e6cc6163e%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ff9f7dffffffffffffffac88ffffffffac88ff9f7dffac88ffffffffffffffac88ffac88ff8c72ffac88ff846effac88%
-  ff846eff7e6cff8c72ff7e6cff7e6cff846eff8c72fd6561ff7869ff7869ff9576ff7e6cff9576ff8c72ff7e6cffffff%
-  ff9576ff7869ff8c72ff7367c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
-  ffffffffffffff9f7dffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff8c72ffac88%
-  ffac88ff9f7dffffffff7e6cff9f7dffac88ff9576ff846eff7e6cfe6862ff846eff7869ff8c72ff6f65ff7367ff9576%
-  ff7869ff846eff9f7dff7e6cfc6260ff9f7dff7869ff8c72ff7869cc1a42ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffac88ffffffffac88ffffffffffffffac88ffac88ffffffffac88ffffffffac88ff9f7dffffffffac88%
-  ff9f7dff9f7dffffffffac88ff8c72ff9f7dff846effac88ff846eff9f7dff846eff9576ff8c72ff7e6cff6f65ff7869%
-  ff7367ff846eff7869fe6862ff9576ff7869ff7e6cff6b63ff7e6cff7e6cff9576ff846eff7869ff846ec8183fffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffff%
-  ff9f7dffffffffffffffac88ffac88ff9f7dff9f7dff9576ffac88ffffffffac88ff8c72ff7869ff7869ff8c72ff9576%
-  ff7367ff7869ff8c72ff8c72ff7367ff846eff7869ff846eff6f65ff846eff846eff7e6cff7869ff8c72fd6561ff9f7d%
-  ff9576ff846eff9f7dcb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
-  ff8c72ffac88ffffffffffffffffffffac88ffac88ffffffffffffffac88ffac88ff9f7dffac88ffffffffac88ff8c72%
-  ff9576ff8c72ff9576ff9576ff7e6cff9f7dff6f65ff7869ff6b63ff7869ff7869ff846effac88ff846eff7367ff7e6c%
-  ff6b63ff7869ff6f65ff8c72ff846eff846eff6b63fe6862ca1940ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9f7dffffff%
-  ffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffffffff9f7dff9f7dffffff%
-  ffac88ff9f7dffffffff9f7dff9576ff846effffffff8c72ff8c72ff9576ff6f65ff7e6cff6b63ff7e6cff846efe6862%
-  ff6f65ff8c72ff6b63ff846eff7869ff8c72ff7869ff9576ff7869ff7869fe6862ff6f65ff6f65d42148ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffff9f7dffffffffac88ffac88ff9f7dff9576ffac88%
-  ffac88ffac88ffffffff8c72ff9f7dff9f7dffac88ff8c72ff8c72ff9f7dffac88ff846eff9576ff8c72ff7e6cff7367%
-  ff7367ff7e6cff7e6cff6f65ff7e6cff7367ff7869ff7e6cff7869ff8c72ff7367ff846eff8c72ff7869ff7e6cff7367%
-  ff6b63ff9576d11e46ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffac88ffac88ffac88ffac88ffac88ffffff%
-  ffac88ffac88ffffffff9f7dffac88ff9576ff846eff9f7dffac88ff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7d%
-  ff8c72ff7869ff7869ff7e6cff846efd6561fd6561ff6f65fe6862ff7869ff7367ff8c72ff7869ff7367ff7869ff8c72%
-  fe6862ff8c72ff846eff7367ff6b63ff846eff7e6cd11e46ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dffac88ffac88ffffffffac88ff9576ffffff%
-  ff9f7dff8c72ff9f7dff8c72ff8c72ff9f7dff7869ff7e6cff846eff6b63ff846eff6b63fb605fff7e6cff9576ff8c72%
-  ff7869ff7869ff7e6cff846eff6f65ff7869ff7869ff6b63ff6f65ff9f7dff7367ff846ed21f47ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffff9576ffac88ffac88ffac88ffac88ffac88ff9f7dffac88%
-  ffffffffac88ffac88ffffffffffffff9f7dffac88ff9576ff6b63ff7e6cff9f7dff7869ff7e6cff9576fe6862ff846e%
-  fd6561ff6b63ff6f65ff846efe6862ff6b63ff9576ff6b63fd6561ff846eff9576ff8c72ff846eff8c72ff7e6cff7869%
-  ff7869cd1c43ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ff9576ff9f7d%
-  ff9f7dff9576ffac88ffffffffac88ff9576ffac88ffffffff9f7dffffffffffffff8c72ff9576ff9576ff846eff7869%
-  ff9576ff9576ff6f65ff7e6cff6f65ff7367ff846eff7869ff6f65ff846eff7869ff6f65ff8c72ff9f7dff6f65ff7367%
-  ff6f65ff6f65ff8c72ff9f7dff7e6cff846ed01e45ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ff9f7d%
-  ffac88ffac88ff9f7dffac88ffffffff9f7dff9f7dff8c72ffffffff7e6cff9576ff8c72ffac88ff9f7dff9576ff9576%
-  ff8c72ffffffff9f7dff846eff6b63fe6862ff7e6cfa5e5ffd6561ff6f65ff7869fd6561ff6f65ff6f65ff9576ff9576%
-  ff6f65ff846eff7367ff846eff6f65ff7e6cfd6561ff6f65fd6561ff846eff7e6cd52248ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88%
-  ffac88ffffffffffffffffffffac88ffac88ff9f7dffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffac88%
-  ff8c72ff9f7dff9576ffac88ff9f7dff846eff8c72ff846eff7367ff7e6cff6f65ff8c72ff846eff6b63fe6862f95c5e%
-  ff7367ff6f65ff846eff9f7dff7e6cff6f65ff7e6cff7869fe6862ff7e6cff7869ff9f7dfe6862ff846eff846eff7e6c%
-  d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffff9576ffac88ffffffff9576ffffffffac88ff8c72ff9576ff846effffff%
-  ffffffff6f65ffac88ffffffff9f7dff9576ff9f7dff9f7dff846eff6f65ff7367ff7869ff846eff846eff8c72ff7367%
-  fc6260ff7e6cfe6862ff6f65ff6b63ff6f65ff7367ff6b63fe6862ff6b63ff846eff6f65ff7869ff7869ff7367ff7869%
-  ff7869ff6f65ff7e6cff7367fe6862d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ff9f7dff7e6cffac88%
-  ff9f7dffac88ffac88ffffffff6f65ff9576ff7367ffac88ff846effac88ff846eff7e6cff7e6cff7e6cff6f65ff7367%
-  ff8c72fe6862ff7869ff7869fb605fff7e6cff6f65ff7367ff7367fc6260fc6260ff846eff7869ff7367ff7869ff7367%
-  ff846efd6561ff7869ff846eff6b63ff7367ff7869ff7367ff846eff7367d62449ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ff9f7dff8c72ff9f7dffac88ff8c72ffac88ff9576ff8c72ff9576ff8c72ff9576ff9576ff8c72%
-  ff9f7dff9576ff8c72ff7869ff7869ff6b63fd6561ff6b63ff7367ff7367ff7869ff7367ff7869fe6862fb605fff6b63%
-  ff6b63fd6561ff7869fe6862ff7367ff6f65ff6f65ff7367fe6862ff6b63ff6f65fe6862ff9576ff9f7dff7e6cd62449%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7d%
-  ffac88ffac88ffffffffffffffac88ffac88ffac88ffac88ffffffff846eff9f7dff8c72ff8c72ff9576ff7869ff8c72%
-  ff7367ff9f7dff8c72ff7367ff6b63ff846eff6f65ff9576ff7e6cff8c72ff7367ff6f65ff7e6cff6f65ff6b63ff6b63%
-  ff6f65fe6862fd6561ff7869fe6862ff6f65f7585dfb605ffb605fff6f65ff7367fd6561ff6f65ff6f65ff7367ff8c72%
-  ff7367ff9f7dff7e6cff8c72db2a4cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffac88ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ffffffffac88ff7e6cffac88ff8c72ff9f7dff8c72%
-  ffac88ff8c72ff7367ff9576ff9576ff846eff9f7dff8c72ff6b63ff846efd6561ff846efe6862ff7869fc6260ff6f65%
-  ff7869ff6f65ff6f65ff6b63ff6f65fb605ffc6260ff7367fd6561f95c5eff6f65ff7367ff7367ff7367ff6f65fb605f%
-  f6545cff7869ff7869ff6b63ff6b63fc6260fc6260ff8c72ff7367db2a4cffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9576ff9f7d%
-  ffac88ff846effac88ffac88ffac88ff7e6cff9f7dff7869ff846eff8c72ff846eff7367ff8c72ff7869ff7e6cff7869%
-  ff7e6cff8c72ff9f7dff7e6cff8c72ff6b63ff6f65fe6862ff7367fa5e5fff846efc6260ff7869ff6b63ff6b63ff7367%
-  fe6862ff7869ff6b63fe6862f95c5ef95c5eff7869ff6b63fe6862ff6f65fe6862ff7869ff846eff7e6cda294bffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ffffffffffffffffff%
-  ffac88ffac88ffac88ff9576ffac88ff7e6cff9f7dff846eff9576ff8c72ff7367ff846eff846eff6b63ffac88ff7e6c%
-  ff7869ffac88ff6b63fd6561ff7367fd6561fd6561ff6b63fa5e5ff95c5eff6b63ff7869fc6260ff6f65ff6b63ff6f65%
-  fe6862fc6260ff7367fb605ff85a5df7565cff6b63ff6f65ff6b63fc6260fe6862fd6561ff7367fb605fff6f65ff7367%
-  ff7869fe6862ff6f65de2d4dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffff%
-  ffac88ffac88ffac88ff9f7dffac88ff9f7dffac88ffac88ff846eff9576ffac88ff9f7dff7e6cff6b63ff7e6cff846e%
-  ff6f65ff7e6cfd6561ff6f65ff6b63f95c5efe6862fd6561ff9576fc6260ff6b63ff6f65ff7367fe6862ff7367fc6260%
-  f85a5df95c5efc6260f95c5efc6260fa5e5fff6f65ff7367fe6862fa5e5fff6f65f7565cfd6561ff7367fb605ff85a5d%
-  fe6862ff7367fd6561ff7367ff846eff9576ff7869ff7869e1324fffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffffffff8c72ffac88ff9576%
-  ff9576ff9f7dff7e6cff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7dffffffff8c72ffffffffffffff9f7dffac88%
-  ff9f7dff9576ff9f7dff9f7dffffffff9f7dffffffff9576ff9f7dffac88ff9f7dff9576ff9f7dff8c72ff9f7dff7367%
-  ff9f7dff846eff7869ff7869ff7869ff9576ff7367f7585df7585dfe6862ff6f65ff7869fe6862fb605fff6b63ff9576%
-  fe6862fd6561f95c5efa5e5ff7585dfc6260f7585df5515bf14958f6545cf95c5ef95c5ef14958ff6f65f6545cf7585d%
-  f95c5ef85a5dfe6862ff7e6cff7869fe6862ff6f65ff6b63ff7869ff6b63ff6b63ff6f65ff6b63e1324fffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7e6cff846eff6b63ff7367%
-  ff6f65ff6b63ff6f65ff7869fd6561f5515bff6b63ff7869ff7367ff6b63ff7869ff7869ff846eff6f65ff6b63ff7e6c%
-  ff9576ff7367ff9576ff7367ff9576ff9576ff9576ff8c72ff846eff8c72ff846eff9f7dffac88ff846eff9576ff7869%
-  ff9576ffac88ff9576ff9f7dff7e6cfb605fff7e6cfd6561ff7367fc6260f95c5ef95c5ef7585df34d59f6545cfb605f%
-  ff7e6cf95c5eff6b63ff6b63fd6561fb605ff5535bf95c5ef34d59f85a5df85a5df7585df95c5efa5e5ff7585df95c5e%
-  f7585dfa5e5ff85a5df4505af7585dfb605ffa5e5ffe6862fe6862fb605fff6f65fa5e5fff6f65ff6b63ff7367fe6862%
-  fd6561ff7e6ce23350ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9f7dff6b63f5515bf7585dfc6260f7565cf34d59f34d59f5515bfd6561f5535bfb605ffa5e5ffb605ffd6561fe6862%
-  fd6561fa5e5fff6b63fc6260f85a5dff6b63ff7e6cfb605fff6b63ff7367fd6561ff6b63ff6f65ff7367ff6f65ff7e6c%
-  ff8c72ff7869ff8c72ff9f7dff8c72ff6f65fe6862fd6561ff6b63ff7367ff7869ff6b63f85a5dfd6561fc6260fd6561%
-  f95c5efa5e5ff34e5af85a5df85a5dfd6561fc6260fc6260fa5e5ff7565cfa5e5ffd6561fa5e5ffd6561f7585df95c5e%
-  f7565cf5535bf5535bf6545cf04757f7585df5515bf4505afa5e5ff85a5df7585df7565cfd6561fa5e5fff7869ff6f65%
-  fd6561fa5e5fff7e6cff846eff846eff846eff6f65e33550ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ff8c72f95c5ef34e5af34d59f04757f14858ef4356ee4256f5535bef4457f4505a%
-  f5535bf5535bfe6862f34d59f4505afa5e5ff85a5df6545cfb605ff85a5dfa5e5ffb605fff6f65f7585dff7e6cff7869%
-  ff6b63fe6862ff7367ff7367ff7e6cff7869fe6862fc6260fe6862fe6862fc6260fc6260f7565cff7367f85a5df85a5d%
-  fb605ffc6260f85a5df34e5af24b59f34e5afa5e5ff5515bf34d59f7585dfa5e5ff7585df6545cf7565cf24a59f95c5e%
-  f6545cf7585df24b59f95c5ef7565cf95c5ef5515bfa5e5fff6f65f5515bf7565cf6545cfa5e5ffb605ff95c5efc6260%
-  fa5e5ffd6561fd6561fe6862fe6862ff6b63ff7869ff7367ff8c72ff6b63ff7869ff9f7de0314fffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff846eff7869fd6561fb605ff7565cf7565cf4505afc6260%
-  fd6561fc6260ff6b63fd6561fc6260fd6561fb605fff7e6cff6b63f95c5efd6561fc6260ff7e6cff6f65ff7367ff7869%
-  ff7367fc6260ff6f65fc6260ff7e6cff6f65ff6b63fe6862fb605ffa5e5ff7565cff6f65f7565cf85a5dfa5e5ff6545c%
-  f5535bff6b63f5515bf5535bf95c5ef14958f04557f95c5ef5515bf24a59f85a5df34e5af7565cf34e5afb605ff7565c%
-  fa5e5ffc6260f6545cf95c5ef7585dfc6260f34e5af95c5ef4505af5535bf95c5ef95c5ef85a5dfa5e5ff6545cf95c5e%
-  f7565cf5515bfa5e5ffa5e5fff6f65f95c5efc6260fc6260fe6862ff7869ff7367ff7367ff6f65ff7e6cff7869ff8c72%
-  ff7e6ce83a53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff6f65f24b59f85a5d%
-  f7585df5535bf7585df24a59fb605ff95c5efb605ffe6862f85a5dff7869fa5e5ffe6862fd6561fa5e5ffd6561ff7869%
-  ff6b63ff9576fe6862fd6561fa5e5ff7565cff846eff7367fb605fff6b63fd6561f85a5dfb605ffd6561f6545cf7565c%
-  f4505aef4457f24b59f14958f24b59f14858f95c5ef14858f24a59f34e5af24b59f04757fd6561f24a59f7585df34e5a%
-  f14958f7585df04557f34d59f5515bf7585df34e5afb605ff34e5af6545cf7565cf7585df24a59f7565cf34d59f34e5a%
-  f34d59fc6260f24b59f85a5dff6f65f85a5df7585dfa5e5ffb605ffa5e5fff6f65f95c5efc6260fb605fff6b63ff6f65%
-  f95c5eff6b63fb605fff6f65ff8c72ff7869df2f4effffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff9576ff6f65fb605ff14858f24b59f14858ef4457f04757f5515bef4457f6545cfb605ffe6862fa5e5ffb605ffa5e5f%
-  fe6862ff6b63fa5e5ffa5e5fff6b63fa5e5fff6b63f7565cfa5e5fff6b63f85a5df7565cfa5e5ffb605ffc6260f14958%
-  f14958f14858f14858f34e5af95c5ef04557ee4156f04757ef4457ef4356f5515bf04757f34e5af14858ef4457ed4155%
-  e73a52ee4156f4505aef4356f14858f04557f7585df24a59f7565cf14958f5535bf14858f34e5af34d59fa5e5ff7565c%
-  f24a59fa5e5ff14958f85a5df4505af95c5efa5e5ff6545cf85a5df95c5ef34d59f14958ff7e6cff6b63fb605ffd6561%
-  ff7367ff6f65fb605ffa5e5ffd6561fb605ffc6260ff6f65ff6f65ff6f65ff6f65db2b4cffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff6f65f04757ec4055ec4055e73a52e83b53ea3d54e33550ed4155f14858ee4256f5515b%
-  fa5e5ff85a5df6545cf5535bf6545cfe6862fa5e5ff85a5dfb605ffb605ffc6260fb605ff95c5ef6545cf34d59f5515b%
-  f7565cf7585df5535bf4505af34d59f5535bf5515bf5535bee4156f04757e73952e63852ec3f55ed4155ea3d54ec3f55%
-  e73a52e83a53ea3d54ea3d54e83a53e83a53e83a53ec3f55e53751e63852ec4055e63852e63852f24a59f04757ef4457%
-  ef4356f14858ed4155e93c53ee4256f5515bf24a59f4505af24a59f34d59fd6561ef4356f34d59f34e5ae93c53f7585d%
-  fd6561f85a5df85a5df24b59f7565cf7565cf7585df7585dff7367ff6f65ff6f65ff9f7dff7e6cff6f65ff6f65ff7869%
-  db2b4cffffffffffffffffffffffffffffffffffffffffffff7869e63852da2a4cdc2b4ce43551ea3d54e43551ec4055%
-  eb3e54f34e5aee4256f34d59f14858f5535bf34e5af95c5ef85a5dfc6260fc6260fe6862fd6561fb605ff34d59ff6b63%
-  f4505afa5e5ff7565cfc6260fc6260f5515bf85a5df5535bfc6260f4505aea3d54f14858f34d59ee4256e83b53ed4155%
-  ed4155ee4156f34e5ae83a53e53751e43651ec3f55e63852e73a52e23350ea3d54ea3d54e73a52eb3e54e63852e73a52%
-  e73952e53751ec4055ee4156f04757ef4457f6545ceb3e54ef4356f04757f4505af7585df04557f4505af5535bef4457%
-  f5515bf24b59fc6260ff6b63fd6561fe6862fa5e5ffc6260ff6b63fe6862fe6862f85a5dff7367ff7869ff6f65ff7869%
-  ff6f65ff6f65ff846eff7869ff846ee33450ffffffffffffffffffffffffffffffffffffffac88e63852da2a4cd11e46%
-  d7264ae2324fdc2b4ce53651e83b53f24a59f34e5af85a5dff7869f7565cfb605ff4505aff7367f85a5df5515bff7367%
-  ff7367ff6b63f95c5eff6b63f85a5df7585df5515bf14958fe6862f7565cf95c5ef5535bf34d59f14958ef4356f04757%
-  f04557f04557f34e5af14858f7585dea3d54ec3f55ee4256ef4356eb3e54e43651e63852e23350f14958e43551e53751%
-  e43651ee4156ec4055e33450e93c53ea3d54ec3f55eb3e54f34d59eb3e54ef4457ee4156ef4457ee4256f5535bf5515b%
-  f4505af5515bf5535bf7585dff6b63f7585df5535bfc6260ff6f65fc6260ff8c72ff6b63fe6862ff7367ff846eff8c72%
-  ff7367ff7869ff9576ff7869ff8c72ff9576ff846eff9f7dff9576ff9f7df34d59ffffffffffffffffffffffffffffff%
-  ffffffff7e6cd01e45ce1c44d21f47d7254ae2324fe83b53eb3e54e83a53f14858f34d59f14958f7585df7565cf7565c%
-  fe6862f95c5efb605ff5535bf5515bf5535bf7585df7565cf14858ef4457e93c53f24b59e93c53f24a59e83a53ee4256%
-  f14958e63852e83b53e73952ea3d54ea3d54e73952e83b53ed4155e23450e43651e73a52e63852e73952e63852e53651%
-  e83a53e93c53e73952e73a52ea3d54e63852e73a52e43551ee4156ee4256ec4055e43551ef4356ec4055f24a59f34e5a%
-  ff6f65f34d59ff6b63f5515bf85a5df85a5dfb605ffd6561fa5e5fff7367ff6b63ff7869ff6f65ff7e6cff8c72ff8c72%
-  ff7367ff7869ff9f7dff9f7dff9576ff9f7dff9f7dff9576ff9576ff9f7dff9f7dff9f7dffffffffac88ffffffe73a52%
-  ffffffffffffffffffffffffffffffffffffff7367d52349db2b4ce73952e73952f14858fb605ff5515bfa5e5ffa5e5f%
-  ff6b63ff6b63fa5e5ffd6561fa5e5ffb605ffa5e5ff5515bf7585df6545cf5535bf34d59f24a59f04757f34d59f4505a%
-  f24a59f4505aef4457f14958ea3d54ed4155e93c53f04557f04557e93c53ea3d54e93c53ec3f55ea3d54ee4256ef4356%
-  f24a59e93c53e63852ea3d54ea3d54ef4457f34d59f04557f04757ee4156f04557ee4256f5515bf14958f85a5df04757%
-  f34d59fb605ff85a5df7585df95c5efa5e5ffd6561fe6862ff7e6cff846eff7869ff9576ffac88ff7e6cff8c72ff9f7d%
-  ff7869ff9f7dffac88ff8c72ffac88ffac88ff7367ff9576ff9f7dff9576ff8c72ffac88ff9576ffac88ffac88ffac88%
-  ff9f7dffac88ffffffff9f7dee4156ffffffffffffffffffffffffffffffff9f7df95c5eea3d54f24a59f14858f5535b%
-  fc6260fa5e5ffa5e5ff7565cfc6260ff7869f7585df85a5dff6b63ff7869ff6f65f34e5afe6862fe6862fa5e5ff7585d%
-  f34d59f5515bf85a5df6545cfa5e5ff24a59f7585def4457fc6260f7565cf24a59f14858f85a5def4457f34d59f5515b%
-  f04557f14958f5515bf14958f04757ef4457f14858f14958f24b59f7585df34e5af34d59f34d59f14958f34d59ff6b63%
-  fb605ff6545cf04557fb605ffe6862fc6260fc6260ff7869fe6862ff7e6cfe6862ff846eff846effac88ff7e6cff8c72%
-  ff8c72ff9576ff7367ff7869ff9576ffac88ffffffff846effac88ff9f7dffac88ffac88ffffffff9f7dffac88ffffff%
-  ffffffffac88ffac88ffffffffac88ffffffffac88ffac88ffffffff9576ffffffffffffffffffffffffffffffff6b63%
-  e23350df2f4ef04557ee4156ee4256f04757f5535bf7565cf95c5ef34d59f24b59f6545cf24b59f24b59e83b53f7585d%
-  f34d59ee4156f14958f5515bf34d59f14858f04557f14858f14858ec4055f04557ef4356ea3d54ea3d54f34d59e83a53%
-  ec4055e73952ec3f55e83b53ee4156e93c53e53751e83a53e23450e73952ea3d54e73a52e53651ea3d54ea3d54e83a53%
-  ed4155e93c53e73a52ef4457e83a53ed4155f04757f5535bf7585df14858f34d59f4505afa5e5ff5535bff8c72fc6260%
-  ff7869ff846eff7869ff8c72ff7e6cff9576ff8c72ff846eff9f7dff7e6cffffffff9576ff9576ffac88ffac88ff9576%
-  ffac88ffffffffac88ffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffff9576ee4156df304ef04757f4505af95c5ef85a5dfa5e5ffe6862fc6260fb605ffd6561fa5e5f%
-  fb605ffb605ff5535bf5515bf5515bf34d59f14958f34e5af85a5df14958f34d59f04557f04757f34d59ef4457f34d59%
-  ee4256f34e5af34d59ec4055f04557eb3e54f34e5aee4156ef4457eb3e54ee4256f24b59f04557eb3e54ee4256e83a53%
-  f04557f04557ef4457f04757f24b59f24a59f14858ec4055f04557f95c5ef85a5df6545cfc6260f85a5dff846eff7367%
-  ff6f65ff6f65ff7869ff8c72ff846eff8c72ff8c72ff7e6cff9f7dffac88ffffffffac88ff9f7dffffffffffffffffff%
-  ffffffffffffffffffffac88ff9f7dffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffff5515bf14858f85a5dff6b63fb605fff7e6cff846eff9f7d%
-  ff9f7dff8c72ff9576ff9576ff7869ff7367ff6f65ff6f65ff7e6cff6b63fd6561ff6f65fb605ffb605fff6b63fd6561%
-  f95c5eff6b63ff6b63fc6260fb605fff7367fa5e5ff7585dff6b63fd6561f7565cfd6561ff7869fc6260fb605fff6f65%
-  fa5e5ff95c5efa5e5ff7585dfb605ffd6561fe6862f7585dfa5e5ffc6260fb605fff7367ff7869ff7869fe6862ff846e%
-  ff7e6cff8c72ff9f7dff9576ffac88ffac88ffac88ff9576ffffffffac88ff9f7dff9f7dffffffffffffff9f7dffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88e53751c2133ad11e46e1324f%
-  ec3f55f14958f34d59f7565cff6b63f7585dff6f65ff6b63fa5e5ff34d59f7585dee4256f7585dec4055f5515bee4256%
-  f24b59ed4155eb3e54e83b53eb3e54e23450f04557ee4256e63852f04757f04557e93c53e93c53f14958ef4457ef4457%
-  f04557e53651ec4055ee4156ef4457ef4457f24a59ec4055f34d59ee4156f14858fb605ff5515bf4505af7565cfd6561%
-  fc6260fc6260fb605ffb605ffb605fff8c72ff9576ff846eff9576ff8c72ff9f7dff846effffffff9f7dffffffffffff%
-  ff9f7dffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576%
-  ff9f7ddd2d4dd42248dc2c4ded4155f34d59fb605ff5515bfc6260fb605ff7585df5515bf7585df85a5df34e5af24a59%
-  f24a59ec4055f14858f5515bf24b59ed4155ed4155f6545cf04757f4505af24a59ea3d54ef4457ee4256f24a59f04757%
-  f14958f04757ee4256ef4457eb3e54ef4356f24a59f24b59f4505af95c5ef7585df5535bff6f65f7565cf95c5efd6561%
-  fe6862fb605fff7367fe6862ff7869ff6b63ff9f7dff8c72ff7e6cffffffff9f7dff9576ffffffff9f7dff9f7dffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ff846efa5e5fdf2f4ee63852ef4457f24b59f85a5df14858f24b59ee4256f24a59ee4256%
-  ea3d54fb605fef4356ef4457f04557ef4457f34e5af04757f04757f04557f04557ee4156ef4356f04757ec4055e53651%
-  ef4457ee4256ef4457ef4457ee4156ea3d54e73a52e83a53f14958ef4356f24a59f04557f7565cf14858f24b59fb605f%
-  fb605fff6f65ff7e6cff6f65fc6260ff7869ff7e6cff7869ff7e6cff9f7dff9576ffac88ffac88ffac88ff9576ffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9576f34e5ae43551d7264ae43651e73952eb3e54e83b53%
-  e83b53ec3f55e43551eb3e54e43551ed4155e93c53e63852e53651eb3e54ec4055e63852ec4055eb3e54e73a52ee4256%
-  e73a52e43551e83b53ec4055e63852ea3d54ed4155eb3e54ec3f55ec4055f24a59f24b59ee4256ea3d54f24b59f04557%
-  f95c5ef5515bf7565cfc6260ff7367ff7367ff6f65ff9f7dff846eff846eff846eff9576ff9f7dffac88ffffffffffff%
-  ff9f7dffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffd6561de2d4dc8173f%
-  d01e46d42148d7264ad62449d9284bd52248d7254ad8264ad42248d42148d8274ade2e4ddc2c4dd52248dc2c4dd9274b%
-  df2f4ede2e4de0304edf2f4edd2d4de0314fdb2a4cdf304ede2e4dd7254ade2d4de1314fdf304edf2f4ee1314fe63852%
-  e43651e83b53f04557f24b59f34e5af4505af85a5df95c5efe6862ff8c72ff7e6cff7e6cff9576ff9576ffac88ffac88%
-  ffffffffac88ffac88ff9f7dffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffe1314fc3143bc9183fd01e45d7254ad32148d52349cd1c43d01e46%
-  d21f47d52349d62449d62449d62449d9274bda294bd9284bd9284bd9284bd42248dc2b4cd9284bd52349d9284bdf2f4e%
-  d9284bd11e46d52349d62449d9284bd7264ae23450e33450e0314fe73a52e83b53ef4457f34e5afb605ffe6862ff6b63%
-  ff6b63ff7367ff7e6cff8c72ffac88ffac88ffffffffac88ff8c72ffffffffffffffac88ff9f7dff9f7dffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffa70421b4092fba0d34c5153ccd1c43c8173fcc1b42d21f47d32047d7254ad42248d32148d11e46d42148d52248%
-  d11e46d22047d52349d8264acf1d44d21f47d21f47d42148d52349d8264ad52349dd2d4dd9284bda294bde2e4ddf2f4e%
-  e33550e53651ed4155f04557f5515bfb605fff7e6cfa5e5fff9576ff846eff7869ff8c72ffffffffffffffac88ffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000b50a30ba0d34b90d33bb0e34%
-  ba0d34bd0f36bc0f35b80c32ba0e34b90d33bf1138c1133abe1037c01138c6163ec3143bc3143bc91840c7173ecf1d45%
-  cb1a42c91840d11f46d32047d62449d52248d9284bde2e4de43651e73a52e73952f24b59f7585df95c5eff7869ff7869%
-  ff9f7dff9576ff9f7dff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000%
-  b0062cab0526ae062ab0062cab0526ad0628ac0528b0062cb1072db4092fbb0e35be1037c5153ccb1a41d32048d7254a%
-  de2e4ef24a59f24a59f85a5df85a5dff6b63ff846eff9f7dff8c72ff846eff9576ffffffffffffffffffffac88ffac88%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffff8b0000f04757ff6f65ff9576ffac88ff9f7dffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff85de9185de9185de919cea9c85de91%
+  85de919cea9c79d48d79d48d000080ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff235f81ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9cffffff255881ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff265481ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff9cea9c265481ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffff265381ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff265381ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c79d48dffffff9cea9c255581ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffff85de919cea9cffffffffffff274d81ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9cffffff9cea9c9cea9c%
+  ffffffffffffffffffffffffffffffffffff255581ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffff9cea9c9cea9cffffffffffffffffffffffff9cea9cffffff9cea9c85de91265381ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c%
+  ffffffffffff9cea9cffffff9cea9c265181ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff275081ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffff9cea9cffffff9cea9c9cea9cffffff9cea9c9cea9c85de919cea9c85de91ffffff274f81%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff9cea9cffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffffffffff85de91%
+  9cea9cffffffffffff85de91274d81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffff9cea9cffffff%
+  ffffff9cea9c9cea9cffffff9cea9cffffffffffff9cea9c9cea9c265181ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff79d48dffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c274e81ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9cffffff79d48d9cea9c%
+  79d48dffffff85de91265381ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff%
+  9cea9cffffff9cea9c9cea9cffffff9cea9c9cea9c6cc78c284c81ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de91%
+  ffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff79d48dffffff9cea9c9cea9cffffff265181ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffff85de91ffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de9185de91ffffffffffff9cea9c85de91%
+  85de91ffffff274881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff79d48dffffff9cea9c%
+  85de919cea9c79d48d85de9179d48dffffff9cea9c274e81ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff9cea9cffffffffffffffffff9cea9c%
+  9cea9cffffff85de91ffffff9cea9c9cea9c79d48dffffff9cea9c85de9179d48dffffff274d81ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff%
+  85de91ffffffffffffffffff9cea9cffffffffffff9cea9c85de9179d48dffffff9cea9cffffff85de9185de9172cd8d%
+  85de91284b81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffff85de919cea9c9cea9cffffffffffff85de91ffffff79d48d9cea9c9cea9c%
+  9cea9c85de9179d48d6cc78c9cea9c9cea9c284d81ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de91ffffffffffff9cea9c85de91%
+  ffffff85de9179d48d85de919cea9c79d48d9cea9c85de916cc78c72cd8d72cd8d274f81ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c85de91ffffff9cea9c9cea9c9cea9c%
+  ffffff85de9185de9185de9185de919cea9c85de919cea9c9cea9c9cea9c6cc78c79d48d85de9185de9185de9179d48d%
+  284d81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9c9cea9cffffffffffff85de919cea9cffffffffffff9cea9c9cea9c9cea9c79d48d9cea9cffffff9cea9c%
+  79d48d79d48d6cc78c6cc78cffffff274881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c9cea9c9cea9c79d48d6cc78c85de91ffffff85de91%
+  ffffffffffff85de91ffffff85de91ffffff79d48d79d48d9cea9c9cea9c284b81ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff79d48d%
+  9cea9c9cea9c85de916cc78cffffff9cea9c6cc78c79d48d79d48d9cea9c72cd8d85de9172cd8dffffff85de91284a81%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff79d48dffffff9cea9cffffff%
+  ffffff9cea9cffffff9cea9cffffff79d48d85de919cea9c72cd8d79d48d72cd8d9cea9c9cea9c85de9185de919cea9c%
+  ffffff72cd8d6cc78c9cea9c284c81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffff85de9185de919cea9cffffff85de9185de919cea9c9cea9c72cd8d85de9185de91%
+  72cd8d79d48d72cd8d85de9172cd8d85de916cc78c72cd8d67c28b284c81ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c9cea9c85de919cea9c%
+  9cea9c9cea9c85de9167c28b9cea9c85de91ffffff79d48d85de9179d48d85de9179d48d9cea9c4aa787274e81ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffff85de919cea9c9cea9c%
+  ffffff9cea9cffffff6cc78c6cc78c79d48d9cea9c6cc78cffffff72cd8d79d48d85de9179d48d6cc78c9cea9c62bd8b%
+  67c28b79d48d72cd8d265181ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c%
+  ffffffffffffffffffffffff85de9185de919cea9cffffff9cea9c6cc78c6cc78c79d48d62bd8bffffff72cd8dffffff%
+  72cd8d9cea9c72cd8d67c28b79d48d72cd8d6cc78c79d48d284b81ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff85de91ffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff85de91ffffff9cea9c9cea9c85de919cea9c79d48d%
+  9cea9cffffff6cc78c85de9172cd8d6cc78c67c28b85de9162bd8b79d48d67c28b72cd8d67c28b274d81ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffff85de91ffffff9cea9c85de9179d48d%
+  72cd8d79d48d9cea9c67c28b9cea9c85de919cea9c6cc78c72cd8d85de9179d48d79d48d5eb98a5ab5896cc78c72cd8d%
+  67c28b67c28b274f81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffff9cea9c9cea9c79d48d9cea9cffffff9cea9c9cea9c79d48d85de919cea9c62bd8b9cea9c85de9172cd8d62bd8b%
+  72cd8d85de915eb98a67c28b79d48d5ab58967c28b265381ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffff79d48dffffffffffff85de919cea9c85de919cea9c79d48d85de919cea9c6cc78c67c28b%
+  62bd8b6cc78c9cea9c9cea9c9cea9c85de9167c28b9cea9c6cc78c62bd8b72cd8d72cd8d265181ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9c9cea9cffffff9cea9c72cd8dffffffffffff%
+  72cd8d85de9185de9179d48d62bd8b85de9167c28b62bd8b72cd8d9cea9c62bd8b9cea9c72cd8d72cd8d62bd8b67c28b%
+  79d48d275081ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c85de9185de91ffffff9cea9cffffff%
+  85de919cea9c72cd8d72cd8d79d48dffffff85de919cea9c6cc78c62bd8b79d48dffffff6cc78c79d48d72cd8d62bd8b%
+  6cc78c79d48d67c28b56b28967c28b72cd8d245981ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c9cea9cffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  85de9185de9185de9179d48d9cea9cffffff72cd8d85de919cea9c72cd8d85de9172cd8d79d48d67c28b62bd8b9cea9c%
+  72cd8d79d48d62bd8b6cc78c67c28b56b2899cea9c79d48d6cc78c79d48d72cd8d255581ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c9cea9cffffff9cea9c85de919cea9c%
+  ffffffffffffffffffffffffffffff9cea9c9cea9cffffff6cc78cffffffffffff9cea9c85de9162bd8b72cd8d72cd8d%
+  79d48d72cd8d6cc78c79d48d67c28b6cc78c6cc78c67c28b5eb98a67c28b79d48d67c28b72cd8d85de9185de9167c28b%
+  255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffff9cea9cffffffffffffffffff9cea9cffffffffffff85de91ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffff85de9185de91ffffff9cea9c79d48d9cea9c9cea9c%
+  85de91ffffff9cea9c6cc78cffffff9cea9c85de916cc78c5ab5895eb98a6cc78c79d48d72cd8d6cc78c6cc78c67c28b%
+  79d48d6cc78c72cd8d72cd8d56b289255581ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffff9cea9cffffff9cea9cffffff9cea9cffffffffffffffffff9cea9cffffff%
+  ffffffffffff9cea9c67c28b6cc78c79d48d6cc78c85de916cc78c67c28b85de9167c28b62bd8b72cd8d67c28b85de91%
+  6cc78c72cd8d85de919cea9c79d48d6cc78c72cd8d5eb98a6cc78c9cea9c265481ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffff9cea9c9cea9c79d48d79d48d9cea9c9cea9c79d48d79d48d9cea9c85de9179d48d79d48d%
+  79d48d67c28b79d48d67c28b67c28b6cc78c72cd8d79d48d62bd8b72cd8d62bd8b67c28b50ac8853af8867c28b265381%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  85de91ffffffffffff9cea9cffffff9cea9c85de919cea9cffffffffffff9cea9c9cea9c72cd8d9cea9c6cc78c9cea9c%
+  6cc78c67c28b72cd8d67c28b67c28b6cc78c72cd8d50ac8862bd8b62bd8b79d48d67c28b79d48d72cd8d67c28bffffff%
+  79d48d62bd8b72cd8d5eb98a255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff%
+  ffffffffffff85de919cea9cffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c85de9172cd8d9cea9c%
+  9cea9c85de91ffffff67c28b85de919cea9c79d48d6cc78c67c28b53af886cc78c62bd8b72cd8d5ab5895eb98a79d48d%
+  62bd8b6cc78c85de9167c28b4da98785de9162bd8b72cd8d62bd8b245a81ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffff9cea9cffffff9cea9cffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9c85de91ffffff9cea9c%
+  85de9185de91ffffff9cea9c72cd8d85de916cc78c9cea9c6cc78c85de916cc78c79d48d72cd8d67c28b5ab58962bd8b%
+  5eb98a6cc78c62bd8b53af8879d48d62bd8b67c28b56b28967c28b67c28b79d48d6cc78c62bd8b6cc78c255681ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9c9cea9cffffffffffffffffff%
+  85de91ffffffffffff9cea9c9cea9c85de9185de9179d48d9cea9cffffff9cea9c72cd8d62bd8b62bd8b72cd8d79d48d%
+  5eb98a62bd8b72cd8d72cd8d5eb98a6cc78c62bd8b6cc78c5ab5896cc78c6cc78c67c28b62bd8b72cd8d50ac8885de91%
+  79d48d6cc78c85de91245981ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff%
+  72cd8d9cea9cffffffffffffffffff9cea9c9cea9cffffffffffff9cea9c9cea9c85de919cea9cffffff9cea9c72cd8d%
+  79d48d72cd8d79d48d79d48d67c28b85de915ab58962bd8b56b28962bd8b62bd8b6cc78c9cea9c6cc78c5eb98a67c28b%
+  56b28962bd8b5ab58972cd8d6cc78c6cc78c56b28953af88255781ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff85de91ffffff%
+  ffffffffffff9cea9cffffffffffff9cea9c85de91ffffff9cea9c85de919cea9c79d48dffffff85de9185de91ffffff%
+  9cea9c85de91ffffff85de9179d48d6cc78cffffff72cd8d72cd8d79d48d5ab58967c28b56b28967c28b6cc78c53af88%
+  5ab58972cd8d56b2896cc78c62bd8b72cd8d62bd8b79d48d62bd8b62bd8b53af885ab5895ab589216581ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffff9cea9cffffff9cea9cffffff9cea9cffffff85de91ffffff9cea9c9cea9c85de9179d48d9cea9c%
+  9cea9c9cea9cffffff72cd8d85de9185de919cea9c72cd8d72cd8d85de919cea9c6cc78c79d48d72cd8d67c28b5eb98a%
+  5eb98a67c28b67c28b5ab58967c28b5eb98a62bd8b67c28b62bd8b72cd8d5eb98a6cc78c72cd8d62bd8b67c28b5eb98a%
+  56b28979d48d236081ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff9cea9cffffffffffffffffff85de91ffffff9cea9c9cea9c9cea9c9cea9c9cea9cffffff%
+  9cea9c9cea9cffffff85de919cea9c79d48d6cc78c85de919cea9c85de919cea9c85de9185de919cea9c85de9185de91%
+  72cd8d62bd8b62bd8b67c28b6cc78c50ac8850ac885ab58953af8862bd8b5eb98a72cd8d62bd8b5eb98a62bd8b72cd8d%
+  53af8872cd8d6cc78c5eb98a56b2896cc78c67c28b226181ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  9cea9c9cea9cffffff9cea9c9cea9c9cea9cffffff9cea9c9cea9c85de919cea9c9cea9cffffff9cea9c79d48dffffff%
+  85de9172cd8d85de9172cd8d72cd8d85de9162bd8b67c28b6cc78c56b2896cc78c56b2894aa78767c28b79d48d72cd8d%
+  62bd8b62bd8b67c28b6cc78c5ab58962bd8b62bd8b56b2895ab58985de915eb98a6cc78c226281ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffff79d48d9cea9c9cea9c9cea9c9cea9c9cea9c85de919cea9c%
+  ffffff9cea9c9cea9cffffffffffff85de919cea9c79d48d56b28967c28b85de9162bd8b67c28b79d48d53af886cc78c%
+  50ac8856b2895ab5896cc78c53af8856b28979d48d56b28950ac886cc78c79d48d72cd8d6cc78c72cd8d67c28b62bd8b%
+  62bd8b245c81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff9cea9c79d48d85de91%
+  85de9179d48d9cea9cffffff9cea9c79d48d9cea9cffffff85de91ffffffffffff72cd8d79d48d79d48d6cc78c62bd8b%
+  79d48d79d48d5ab58967c28b5ab5895eb98a6cc78c62bd8b5ab5896cc78c62bd8b5ab58972cd8d85de915ab5895eb98a%
+  5ab5895ab58972cd8d85de9167c28b6cc78c236081ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff9cea9cffffffffffffffffff9cea9c85de91%
+  9cea9c9cea9c85de919cea9cffffff85de9185de9172cd8dffffff67c28b79d48d72cd8d9cea9c85de9179d48d79d48d%
+  72cd8dffffff85de916cc78c56b28953af8867c28b48a58650ac885ab58962bd8b50ac885ab5895ab58979d48d79d48d%
+  5ab5896cc78c5eb98a6cc78c5ab58967c28b50ac885ab58950ac886cc78c67c28b216681ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff9cea9cffffff9cea9c%
+  9cea9cffffffffffffffffff9cea9c9cea9c85de91ffffff9cea9c85de91ffffff9cea9c85de919cea9c79d48d9cea9c%
+  72cd8d85de9179d48d9cea9c85de916cc78c72cd8d6cc78c5eb98a67c28b5ab58972cd8d6cc78c56b28953af8845a286%
+  5eb98a5ab5896cc78c85de9167c28b5ab58967c28b62bd8b53af8867c28b62bd8b85de9153af886cc78c6cc78c67c28b%
+  206981ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffff79d48d9cea9cffffff79d48dffffff9cea9c72cd8d79d48d6cc78cffffff%
+  ffffff5ab5899cea9cffffff85de9179d48d85de9185de916cc78c5ab5895eb98a62bd8b6cc78c6cc78c72cd8d5eb98a%
+  4da98767c28b53af885ab58956b2895ab5895eb98a56b28953af8856b2896cc78c5ab58962bd8b62bd8b5eb98a62bd8b%
+  62bd8b5ab58967c28b5eb98a53af88206981ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de919cea9c9cea9c9cea9c85de9167c28b9cea9c%
+  85de919cea9c9cea9cffffff5ab58979d48d5eb98a9cea9c6cc78c9cea9c6cc78c67c28b67c28b67c28b5ab5895eb98a%
+  72cd8d53af8862bd8b62bd8b4aa78767c28b5ab5895eb98a5eb98a4da9874da9876cc78c62bd8b5eb98a62bd8b5eb98a%
+  6cc78c50ac8862bd8b6cc78c56b2895eb98a62bd8b5eb98a6cc78c5eb98a216881ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de91ffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c85de9172cd8d85de919cea9c72cd8d9cea9c79d48d72cd8d79d48d72cd8d79d48d79d48d72cd8d%
+  85de9179d48d72cd8d62bd8b62bd8b56b28950ac8856b2895eb98a5eb98a62bd8b5eb98a62bd8b53af884aa78756b289%
+  56b28950ac8862bd8b53af885eb98a5ab5895ab5895eb98a53af8856b2895ab58953af8879d48d85de9167c28b216881%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c85de91%
+  9cea9c9cea9cffffffffffff9cea9c9cea9c9cea9c9cea9cffffff6cc78c85de9172cd8d72cd8d79d48d62bd8b72cd8d%
+  5eb98a85de9172cd8d5eb98a56b2896cc78c5ab58979d48d67c28b72cd8d5eb98a5ab58967c28b5ab58956b28956b289%
+  5ab58953af8850ac8862bd8b53af885ab589409f864aa7874aa7875ab5895eb98a50ac885ab5895ab5895eb98a72cd8d%
+  5eb98a85de9167c28b72cd8d206f81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  9cea9c9cea9c85de91ffffff9cea9cffffffffffff9cea9c72cd8dffffff9cea9c67c28b9cea9c72cd8d85de9172cd8d%
+  9cea9c72cd8d5eb98a79d48d79d48d6cc78c85de9172cd8d56b2896cc78c50ac886cc78c53af8862bd8b4da9875ab589%
+  62bd8b5ab5895ab58956b2895ab5894aa7874da9875eb98a50ac8845a2865ab5895eb98a5eb98a5eb98a5ab5894aa787%
+  3b9c8562bd8b62bd8b56b28956b2894da9874da98772cd8d5eb98a207081ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff79d48d85de91%
+  9cea9c6cc78c9cea9c9cea9c9cea9c67c28b85de9162bd8b6cc78c72cd8d6cc78c5eb98a72cd8d62bd8b67c28b62bd8b%
+  67c28b72cd8d85de9167c28b72cd8d56b2895ab58953af885eb98a48a5866cc78c4da98762bd8b56b28956b2895eb98a%
+  53af8862bd8b56b28953af8845a28645a28662bd8b56b28953af885ab58953af8862bd8b6cc78c67c28b206e81ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c9cea9c9cea9cffffffffffffffffff%
+  9cea9c9cea9c9cea9c79d48d9cea9c67c28b85de916cc78c79d48d72cd8d5eb98a6cc78c6cc78c56b2899cea9c67c28b%
+  62bd8b9cea9c56b28950ac885eb98a50ac8850ac8856b28948a58645a28656b28962bd8b4da9875ab58956b2895ab589%
+  53af884da9875eb98a4aa78743a1863e9d8556b2895ab58956b2894da98753af8850ac885eb98a4aa7875ab5895eb98a%
+  62bd8b53af885ab5891f7481ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff9cea9cffffff%
+  9cea9c9cea9c9cea9c85de919cea9c85de919cea9c9cea9c6cc78c79d48d9cea9c85de9167c28b56b28967c28b6cc78c%
+  5ab58967c28b50ac885ab58956b28945a28653af8850ac8879d48d4da98756b2895ab5895eb98a53af885eb98a4da987%
+  43a18645a2864da98745a2864da98748a5865ab5895eb98a53af8848a5865ab5893e9d8550ac885eb98a4aa78743a186%
+  53af885eb98a50ac885eb98a6cc78c79d48d62bd8b62bd8b1f7981ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9cffffff72cd8d9cea9c79d48d%
+  79d48d85de9167c28b85de919cea9c85de9185de919cea9c85de9185de91ffffff72cd8dffffffffffff85de919cea9c%
+  85de9179d48d85de9185de91ffffff85de91ffffff79d48d85de919cea9c85de9179d48d85de9172cd8d85de915eb98a%
+  85de916cc78c62bd8b62bd8b62bd8b79d48d5eb98a409f86409f8653af885ab58962bd8b53af884aa78756b28979d48d%
+  53af8850ac8845a28648a586409f864da987409f863799852c92833b9c8545a28645a2862c92835ab5893b9c85409f86%
+  45a28643a18653af8867c28b62bd8b53af885ab58956b28962bd8b56b28956b2895ab58956b2891f7981ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff67c28b6cc78c56b2895eb98a%
+  5ab58956b2895ab58962bd8b50ac8837998556b28962bd8b5eb98a56b28962bd8b62bd8b6cc78c5ab58956b28967c28b%
+  79d48d5eb98a79d48d5eb98a79d48d79d48d79d48d72cd8d6cc78c72cd8d6cc78c85de919cea9c6cc78c79d48d62bd8b%
+  79d48d9cea9c79d48d85de9167c28b4aa78767c28b50ac885eb98a4da98745a28645a286409f863195843b9c854aa787%
+  67c28b45a28656b28956b28950ac884aa787399a8545a28631958443a18643a186409f8645a28648a586409f8645a286%
+  409f8648a58643a186359884409f864aa78748a58653af8853af884aa7875ab58948a5865ab58956b2895eb98a53af88%
+  50ac8867c28b1f7a82ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  85de9156b289379985409f864da9873e9d8531958431958437998550ac88399a854aa78748a5864aa78750ac8853af88%
+  50ac8848a58656b2894da98743a18656b28967c28b4aa78756b2895eb98a50ac8856b2895ab5895eb98a5ab58967c28b%
+  72cd8d62bd8b72cd8d85de9172cd8d5ab58953af8850ac8856b2895eb98a62bd8b56b28943a18650ac884da98750ac88%
+  45a28648a58633968443a18643a18650ac884da9874da98748a5863e9d8548a58650ac8848a58650ac88409f8645a286%
+  3e9d85399a85399a853b9c85299083409f8637998535988448a58643a186409f863e9d8550ac8848a58662bd8b5ab589%
+  50ac8848a58667c28b6cc78c6cc78c6cc78c5ab5891f7c82ffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9c72cd8d45a2863396843195842990832a9183248d83238c83399a85268e83359884%
+  399a85399a8553af8831958435988448a58643a1863b9c854aa78743a18648a5864aa7875ab589409f8667c28b62bd8b%
+  56b28953af885eb98a5eb98a67c28b62bd8b53af884da98753af8853af884da9874da9873e9d855eb98a43a18643a186%
+  4aa7874da98743a1863396842f948433968448a586379985319584409f8648a586409f863b9c853e9d852e938445a286%
+  3b9c85409f862f948445a2863e9d8545a28637998548a5865ab5893799853e9d853b9c8548a5864aa78745a2864da987%
+  48a58650ac8850ac8853af8853af8856b28962bd8b5eb98a72cd8d56b28962bd8b85de911f7881ffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff6cc78c62bd8b50ac884aa7873e9d853e9d853598844da987%
+  50ac884da98756b28950ac884da98750ac884aa78767c28b56b28945a28650ac884da98767c28b5ab5895eb98a62bd8b%
+  5eb98a4da9875ab5894da98767c28b5ab58956b28953af884aa78748a5863e9d855ab5893e9d8543a18648a5863b9c85%
+  399a8556b289379985399a8545a2862c9283278f8345a2863799852e938443a1863396843e9d853396844aa7873e9d85%
+  48a5864da9873b9c8545a286409f864da98733968445a286359884399a8545a28645a28643a18648a5863b9c8545a286%
+  3e9d8537998548a58648a5865ab58945a2864da9874da98753af8862bd8b5eb98a5eb98a5ab58967c28b62bd8b72cd8d%
+  67c28b1e8382ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de915ab5892f948443a186%
+  409f86399a85409f862e93844aa78745a2864aa78753af8843a18662bd8b48a58653af8850ac8848a58650ac8862bd8b%
+  56b28979d48d53af8850ac8848a5863e9d856cc78c5eb98a4aa78756b28950ac8843a1864aa78750ac883b9c853e9d85%
+  359884268e832f94842c92832f94842a918345a2862a91832e93843396842f948429908350ac882e9384409f86339684%
+  2c9283409f86278f83319584379985409f863396844aa7873396843b9c853e9d85409f862e93843e9d85319584339684%
+  3195844da9872f948443a1865ab58943a186409f8648a5864aa78748a5865ab58945a2864da9874aa78756b2895ab589%
+  45a28656b2894aa7875ab58972cd8d62bd8b1f7581ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  79d48d5ab5894aa7872a91832f94842a9183268e83299083379985268e833b9c854aa78753af8848a5864aa78748a586%
+  53af8856b28948a58648a58656b28948a58656b2893e9d8548a58656b28943a1863e9d8548a5864aa7874da9872c9283%
+  2c92832a91832a918333968445a286278f83228b82299083268e83248d833799852990833396842a9183268e83208a82%
+  1e8282228b82359884248d832a9183278f83409f862e93843e9d852c9283399a852a918333968431958448a5863e9d85%
+  2e938448a5862c928343a18635988445a28648a5863b9c8543a18645a2863195842c928367c28b56b2894aa78750ac88%
+  5eb98a5ab5894aa78748a58650ac884aa7874da9875ab5895ab5895ab5895ab589207081ffffffffffffffffffffffff%
+  ffffffffffffffffffffffff5ab5892990831f8a821f8a821e82821e84821e86821f7c82208a822a9183238c83379985%
+  48a58643a1863b9c85399a853b9c8553af8848a58643a1864aa7874aa7874da9874aa78745a2863b9c85319584379985%
+  3e9d85409f86399a85359884319584399a85379985399a85228b822990831e82821f81821e8982208a821e86821e8982%
+  1e82821e83821e86821e86821e83821e83821e83821e89821f7f821f81821f8a821f81821f81822e9384299083268e83%
+  248d832a9183208a821e8582238c833799852e93843598842e938431958450ac88248d833195843396841e8582409f86%
+  50ac8843a18643a1862f94843e9d853e9d85409f86409f865eb98a5ab5895ab58985de9167c28b5ab5895ab58962bd8b%
+  207081ffffffffffffffffffffffffffffffffffffffffff62bd8b1f8082206f812071811f7d821e86821f7d821f8a82%
+  1e8882339684238c833195842a9183399a8533968445a28643a1864da9874da98753af8850ac884aa78731958456b289%
+  35988448a5863e9d854da9874da98737998543a186399a854da9873598841e87822a9183319584238c831e8482208a82%
+  208a82228b823396841e83821f7f821f7e821e89821f80821e82821f7a821e86821e87821e82821e88821f81821e8282%
+  1e82821f7f821f8a82228b82299083268e833b9c851e8882248d83299083359884409f86278f83359884399a85268e83%
+  3799852f94844da98756b28950ac8853af8848a5864da98756b28953af8853af8843a1865eb98a62bd8b5ab58962bd8b%
+  5ab5895ab5896cc78c62bd8b6cc78c1f7c82ffffffffffffffffffffffffffffffffffff9cea9c1f8182206f81226181%
+  206a811f7a822071811f7f821e84822e938433968443a18662bd8b3e9d854aa7873598845eb98a43a1863799855eb98a%
+  5eb98a56b28945a28656b28943a186409f863799852c928353af883e9d8545a286399a853195842c9283248d83299083%
+  278f83278f833396842a9183409f861e87821e8982238c83248d831e88821f7e821f80821f7a822c92831f7d821f7f82%
+  1f7e82228b821f8a821f7c821e85821e86821e89821e88823195841e8882268e83228b82268e83238c83399a85379985%
+  359884379985399a85409f8656b289409f86399a854da9875ab5894da98772cd8d56b28953af885eb98a6cc78c72cd8d%
+  5eb98a62bd8b79d48d62bd8b72cd8d79d48d6cc78c85de9179d48d85de91319584ffffffffffffffffffffffffffffff%
+  ffffff67c28b236081235d81226281206a811f7a821e84821e88821e83822a91833195842c9283409f863e9d853e9d85%
+  53af8845a2864aa787399a85379985399a85409f863e9d852a9183268e831e85822f94841e85822e93841e8382238c83%
+  2c92831f81821e84821e82821e87821e86821e82821e8482208a821f7b821f7e821e82821f80821e82821f81821f7f82%
+  1e83821e85821e82821e82821e87821f81821e82821f7d82228b82238c831f8a821f7d82248d831f8a822e9384339684%
+  5ab58931958456b28937998543a18643a1864aa78750ac8848a5865eb98a56b28962bd8b5ab58967c28b72cd8d72cd8d%
+  5eb98a62bd8b85de9185de9179d48d85de9185de9179d48d79d48d85de9185de9185de91ffffff9cea9cffffff1e8282%
+  ffffffffffffffffffffffffffffffffffff5eb98a2167812070811e82821e82822a91834aa78737998548a58648a586%
+  56b28956b28948a58650ac8848a5864aa78748a586379985409f863b9c85399a853195842e9384299083319584359884%
+  2e9384359884268e832c92831e8682208a821e8582278f83278f831e85821e86821e85821e89821e8682238c83248d83%
+  2e93841e85821f81821e86821e8782268e83319584278f83299083228b82278f83238c833799852c928343a186299083%
+  3195844aa78743a186409f8645a28648a58650ac8853af8867c28b6cc78c62bd8b79d48d9cea9c67c28b72cd8d85de91%
+  62bd8b85de919cea9c72cd8d9cea9c9cea9c5eb98a79d48d85de9179d48d72cd8d9cea9c79d48d9cea9c9cea9c9cea9c%
+  85de919cea9cffffff85de91228b82ffffffffffffffffffffffffffffff85de9145a2861e86822e93842a9183399a85%
+  4da98748a58648a5863e9d854da98762bd8b409f8643a18656b28962bd8b5ab58933968453af8853af8848a586409f86%
+  31958437998543a1863b9c8548a5862e9384409f86268e834da9873e9d852e93842a918343a186268e83319584379985%
+  278f832c92833799852c9283299083268e832a91832c92832f9484409f863396843195843195842c928331958456b289%
+  4aa7873b9c85278f834aa78753af884da9874da98762bd8b53af8867c28b53af886cc78c6cc78c9cea9c67c28b72cd8d%
+  72cd8d79d48d5eb98a62bd8b79d48d9cea9cffffff6cc78c9cea9c85de919cea9c9cea9cffffff85de919cea9cffffff%
+  ffffff9cea9c9cea9cffffff9cea9cffffff9cea9c9cea9cffffff79d48dffffffffffffffffffffffffffffff56b289%
+  1f7a821f7681278f83228b82238c83299083399a853e9d8545a2863195842f94843b9c852f94842f94841e8482409f86%
+  319584228b822c92833799853195842a9183278f832a91832a91831f8a82278f83248d831e87821e86823195841e8382%
+  1f8a821e82821e89821e8482228b821e85821f7f821e83821f7b821e82821e86821e82821f7f821e86821e87821e8382%
+  208a821e85821e8282268e831e8382208a82299083399a85409f862a918331958435988448a586399a8572cd8d4da987%
+  62bd8b6cc78c62bd8b72cd8d67c28b79d48d72cd8d6cc78c85de9167c28bffffff79d48d79d48d9cea9c9cea9c79d48d%
+  9cea9cffffff9cea9cffffff85de91ffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffff79d48d228b821f768129908335988445a28643a18648a58653af884da9874aa78750ac8848a586%
+  4aa7874aa787399a853799853799853195842c928333968443a1862c9283319584278f83299083319584268e83319584%
+  238c833396843195841f8a82278f831e8882339684228b82268e831e8882238c832f9484278f831e8882238c831e8382%
+  278f83278f83268e832990832f94842e93842a91831f8a82278f8345a28643a1863b9c854da98743a1866cc78c5eb98a%
+  5ab5895ab58962bd8b72cd8d6cc78c72cd8d72cd8d67c28b85de919cea9cffffff9cea9c85de91ffffffffffffffffff%
+  ffffffffffffffffff9cea9c85de91ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff3799852a918343a18656b2894aa78767c28b6cc78c85de91%
+  85de9172cd8d79d48d79d48d62bd8b5eb98a5ab5895ab58967c28b56b28950ac885ab5894aa7874aa78756b28950ac88%
+  45a28656b28956b2894da9874aa7875eb98a48a586409f8656b28950ac883e9d8550ac8862bd8b4da9874aa7875ab589%
+  48a58645a28648a586409f864aa78750ac8853af88409f8648a5864da9874aa7875eb98a62bd8b62bd8b53af886cc78c%
+  67c28b72cd8d85de9179d48d9cea9c9cea9c9cea9c79d48dffffff9cea9c85de9185de91ffffffffffff85de91ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9c1f7f82274e812261811f7981%
+  1e89822c92833195843e9d8556b289409f865ab58956b28948a586319584409f86238c83409f861f8a82379985238c83%
+  2f9484208a821e88821e84821e88821f7b82278f83238c831f8182299083278f831e85821e85822c9283268e83268e83%
+  278f831f7f821f8a82228b82268e83268e832e93841f8a82319584228b822a91834aa7873799853598843e9d8550ac88%
+  4da9874da9874aa7874aa7874aa78772cd8d79d48d6cc78c79d48d72cd8d85de916cc78cffffff85de91ffffffffffff%
+  85de91ffffffffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d%
+  85de911f73812165811f7281208a823195844aa7873799854da9874aa787409f86379985409f8643a1863396842e9384%
+  2e93841f8a822a91833799852f9484208a82208a823b9c852990833598842e93841e8782268e83238c832e9384299083%
+  2c9283299083238c83268e831e8882248d832e93842f948435988445a286409f86399a855ab5893e9d8545a28650ac88%
+  53af884aa7875eb98a53af8862bd8b56b28985de9172cd8d67c28bffffff85de9179d48dffffff85de9185de91ffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c6cc78c48a5861f76811f8082268e832f948443a1862a91832f9484238c832e9384238c83%
+  1e87824aa787248d83268e83278f83268e83339684299083299083278f83278f83228b82248d832990831f8a821f7f82%
+  268e83238c83268e83268e83228b821e87821e82821e83822c9283248d832e9384278f833e9d852a91832f94844aa787%
+  4aa7875ab58967c28b5ab5894da98762bd8b67c28b62bd8b67c28b85de9179d48d9cea9c9cea9c9cea9c79d48dffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff79d48d3396841f7d82206a811f7e821e82821e88821e8482%
+  1e84821e89821f7d821e88821f7d82208a821e85821f81821f7f821e88821f8a821f81821f8a821e88821e8282238c83%
+  1e82821f7d821e84821f8a821f81821e8682208a821e88821e89821f8a822e93842f9484238c831e86822f9484278f83%
+  45a2863799853e9d854da9875eb98a5eb98a5ab58985de916cc78c6cc78c6cc78c79d48d85de919cea9cffffffffffff%
+  85de91ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff50ac881f7481255581%
+  236081216481206a81216881206d81216681206981206b81216581216581206b811f74811f72812166811f7281206c81%
+  1f76811f74811f77811f75811f73811f7881206f811f76811f74812069811f74811f78811f76811f76811f78811f8082%
+  1f7e821e8482278f832f948433968435988443a18645a28653af8872cd8d67c28b67c28b79d48d79d48d9cea9c9cea9c%
+  ffffff9cea9c9cea9c85de919cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff1f7881274f81255681236081206981226481216781245c81236081%
+  226281216781216881216881206881206c81206e81206c81206c81206d81216681207181206d81216781206c811f7681%
+  206c81226181216681206881206d81206a811f7b821f7c821f78811e82821e8482268e833396844aa78753af8856b289%
+  56b2895eb98a67c28b72cd8d9cea9c9cea9cffffff9cea9c72cd8dffffffffffff9cea9c85de9185de91ffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff212c81253c81264481265181245c81255581245b81226281226381206a81216681226481226181216581216681%
+  236081226381216681206b81235e81226281226281216481216781206b812167811f7281206c81206e811f74811f7581%
+  1f7c821f7f82208a82278f833799854aa78767c28b48a58679d48d6cc78c62bd8b72cd8dffffffffffff9cea9cffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff000080253d81264481264381274581%
+  264481274781274681264181274481264381284b81284d81274981284b81265381274f81274f81255781265481235f81%
+  245981255681226181226381216881216681206d811f74811f7e821e82821e82822f9484409f8645a28662bd8b62bd8b%
+  85de9179d48d85de9179d48d85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff000080%
+  243781223081233581233681223181233381233381243781243881253b81274581284981265181245981226481206981%
+  1f75812e93842e938443a18643a18656b2896cc78c85de9172cd8d6cc78c79d48dffffffffffffffffff9cea9c9cea9c%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff0000802990835ab58979d48d9cea9c85de91ffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
@@
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffffffac88ffac88ffac88%
-  ffac88ffac88ff8c72ffffffffac88ff9576ff9f7dff8c72ff7869ff7e6cff7367ff6f65ff8c72ff9576ff6f65ffac88%
-  ff846eff846eff9576ff7e6cff7e6cff6f65ff7869fc6260fc6260ff7869fe6862fe6862fc6260f85a5dfb605ff34e5a%
-  f7565cfa5e5ff5535bf5515bf04557ec4055ea3d54e83b53e93c53e23450e53651db2a4cdc2b4cd9274bdb2a4cd7254a%
-  d8264ad32047d32048d11f468b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
-  ffac88ffffffffffffff9576ffac88ffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffff9576ff9f7dff9576ff8c72ff9f7dff9576ffac88ff9f7dff7e6cff9f7dff9f7dffac88%
-  ffac88ff7367ff846efe6862ff8c72ff7e6cff846eff846eff7367ef4356ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffff9f7dff9f7dffffffffffffff9f7dffffffffffffffac88ffffffff9f7dff9f7dff846eff8c72ff9f7d%
-  ff8c72ff9576ff9f7dff7869ffffffffac88ff6f65ff7869ff8c72ff9f7dff7869ff9f7dff7e6cff7869f5515bffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffff9f7dffffffffac88ffffffffffffffac88ff9f7dffffffff9f7dffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffac88ffffffff9f7dff9f7dffffffffffffffac88ffffffffffffff9f7d%
-  ffac88ffac88ff9f7dff9f7dff9576ff9576ff846eff7e6cff9f7dff8c72ffffffff7869ff8c72ff7869ff7367ff9f7d%
-  ff9576fa5e5fff7e6cfd6561ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffac88ffac88ffffff%
-  ffffffff9f7dffffffffac88ffffffffac88ffffffff9f7dff9576ffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffffffffffffff9f7dffac88ff9576ff846eff9576ff9576ff9f7dff9576ff8c72ff9576ffac88ff7e6cff6b63%
-  ffac88ff846eff7e6cffffffff9f7dff6f65ff7367ff846efd6561ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffff%
-  ffffffffac88ffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ff9f7dff9576ffac88ffac88ff9f7dff7e6cffac88ff9f7dff846eff8c72ff8c72%
-  ff8c72ff846eff7869ff846eff8c72ff9576ff8c72ff7e6cffac88ff7367ff8c72ff7367ff7e6cfd6561ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9f7dffac88ff9f7dffffffffffffffffffff9f7dffac88ffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffff9f7dffac88ffac88ff9f7dffac88ff9f7dffac88ffac88ffffffff8c72ff9576ff8c72%
-  ff9576ff9f7dff9576ff6b63ff846eff7e6cff8c72ff7869ffffffff7e6cff8c72ff7e6cff7e6cff8c72ff8c72ff7367%
-  ff7e6cff9576ff7869ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffffffffffffffffac88ffffffffffffff9f7dffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffffff9f7dff9f7dff9f7d%
-  ff9576ff9576ff7e6cffac88ff8c72ff9f7dff846eff6b63ff9f7dff7869fd6561ff7e6cff846eff7869ff9576ff9576%
-  ff846eff7869ff7869ff7e6cff9f7dff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffac88ffac88ffffffff9f7dffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88%
-  ff7e6cffac88ff9f7dff9f7dff9576ff9f7dfe6862ff8c72ff7367ff846efd6561fc6260ff8c72fc6260ff6b63ff7869%
-  ff7367ff9576ff7e6cff8c72ffac88ff8c72ffac88ff7e6cff9576ff8c72ff9576ffac88ff9576ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88ffffffffffffffac88%
-  ffac88ffffffff9f7dffffffff846effac88ff9576ffffffff8c72ffac88ff8c72ffac88fd6561ff8c72ff8c72ff7367%
-  ff7367ff7869ff7367ff6f65fe6862ff6b63fd6561ff7367ff9576ff7869ff9576ff846eff846eff9f7dff9f7dff9576%
-  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffffac88ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffff%
-  ffffffff9576ff9f7dffac88ff9f7dffffffff9576ffffffff9f7dff846eff9f7dff9f7dff9576ff9576ff8c72ff846e%
-  ff846eff7367ff6b63ff6b63fc6260ff846efd6561ff6b63fb605ff95c5ef7585dff6b63ff7367ff7e6cff8c72ff9f7d%
-  ff9f7dff9576ffffffff846eff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffff8c72ff9f7dffffffff9f7dff9576%
-  ff846eff9f7dff8c72ffac88ff7e6cff846efe6862fd6561fe6862ff7367ff6b63f7565cf7585dff6b63fc6260fb605f%
-  ff6b63ff7e6cff7e6cff8c72ff846effac88ffffffff7e6cffffffff9f7dffac88ff9576ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffff9f7d%
-  ffac88ffffffff8c72ffac88ff9f7dff7869ff6b63ff9576ff9576ff7e6cff7e6cff6f65fe6862fd6561f7565cf95c5e%
-  fa5e5ff24b59f7565cf34e5afd6561fc6260ff7869fe6862ff9f7dff846eff9f7dffac88ffac88ffffffffac88ffffff%
-  ff6b63ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffac88ffac88ff9576ffac88ffffffffffffffffff%
-  ffac88ffac88ffffffff9576ffffffff9576ff9576ffffffff8c72ff9576ff846eff8c72ffffffff8c72ff7869fd6561%
-  ff846eff6f65fe6862fd6561f85a5df7565cff6b63fd6561f6545cfd6561f85a5dff846eff9576ff8c72ff9f7dff9f7d%
-  ffac88ff9f7dffffffffffffff9576e93c53ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffac88ff9f7dffac88ffac88ff9f7d%
-  ffffffffffffffffffff846effac88ffffffffffffffac88ff9f7dff7367ffac88ff9f7dff846eff8c72ff8c72ff9f7d%
-  ff846eff846eff9576ff7e6cff7869f95c5efa5e5ffe6862fb605ff85a5dfd6561fb605fff7e6cf85a5df95c5efd6561%
-  ff7e6cff7869ff846eff9576ffac88ff9576ff9f7dff9576ffac88ff9f7de33550ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9576ffffffffffffff9f7d%
-  ffffffffffffff9576ffffffffac88ffffffffffffffac88ffac88ffac88ff9f7dffffffff9f7dff9576ff9f7dffac88%
-  ffac88ff9f7dff8c72ff8c72ff846eff7367ff7e6cff9576ff7869ff6b63fa5e5ffc6260f4505afa5e5ff5515bf5535b%
-  f95c5efb605ff5515bf4505afb605ffc6260ff846eff9576ffac88ffac88ffffffffffffff9f7dff8c72ff7e6ce83a53%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffac88ffffffffac88%
-  ffffffff8c72ffac88ffac88ffffffffac88ffffffff9f7dff9f7dffffffffac88ff9576ffffffff9f7dffac88ff9576%
-  ff846effac88ff9f7dff8c72ffac88ff9576ff8c72ff8c72ff7869ff8c72ff7367ff846eff7869ff7e6cff7e6cff6b63%
-  ff6b63fe6862f6545cf7565cfe6862f7585df7585df5535bfe6862fc6260ff7e6cff8c72ffac88ff9f7dff9f7dff9f7d%
-  ffac88ff8c72ff846efe6862f14858ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffffffffffffffffff%
-  ffac88ffac88ffffffffffffff9f7dffac88ffac88ffac88ffffffffac88ff9576ffffffff9f7dffac88ffffffffac88%
-  ff9f7dff9f7dffac88ffac88ff9576ff8c72ff9f7dff9f7dff9f7dff8c72ff9f7dff7e6cffffffff7367ff8c72ff7e6c%
-  ff846eff7e6cfa5e5ffe6862ff7367fe6862f85a5dfd6561fb605ffb605ff5535bf5535bf7585dfb605fff846eff7869%
-  ff846eff8c72ff9576ffffffff846eff9f7dff7e6cff7e6cfe6862fb605fffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffffffffffff%
-  ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffffac88ffac88ff9f7dff9f7dff846eff9576ff9f7d%
-  ff9f7dff8c72ff7869ff846eff8c72ff7869ff7869ff7869ff7869fd6561fd6561f34e5af7585dfd6561f4505af95c5e%
-  fc6260fa5e5ffc6260ff7e6cff8c72ff846effac88ffac88ff9f7dff9f7dff9f7dff7e6cff7e6cff7367ff9576ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffffffffac88%
-  ffffffffffffff9f7dffffffff9f7dffffffffac88ffac88ffac88ffffffffac88ffac88ff8c72ff9f7dff9f7dff846e%
-  ffac88ffac88ff7e6cff9f7dff9f7dff846eff9576ff9f7dff8c72ff7869ff6f65ff7869ff7e6cff7869fe6862fb605f%
-  fe6862fa5e5ffb605ffd6561f85a5dfd6561ff7869ff7869ff846eff8c72ff9576ff846eff9f7dffac88ff9f7dff9f7d%
-  ff9f7dff9f7dff9f7dff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffff%
-  ff9f7dffffffff8c72ff9576ff9f7dffffffffffffff9f7dff9f7dffac88ff9576ff9f7dffffffff9f7dffffffffac88%
-  ff9f7dffac88ff9f7dff9576ff8c72ff9f7dff9f7dff8c72ff7869ff9f7dff7869ff9576ff846eff7869fa5e5fff9576%
-  ff7e6cff7869ff7869fe6862fd6561fb605ffa5e5ff95c5ef7565cf7585dfa5e5fff7869fe6862ff9576ffac88ff9576%
-  ffffffffac88ff9f7dffac88ffffffff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff9f7dff9576ff9f7dffffffffac88ffffffffac88ffac88%
-  ff9f7dff9f7dffffffffffffff9f7dffac88ffac88ffffffff9576ffffffffac88ff7869ff9576ff9f7dffac88ff9576%
-  ff7869ff7e6cff9576ff9f7dff6f65ff7869fb605fff7e6cff6f65fd6561fb605ffb605fff7e6cff7869fe6862ff6b63%
-  ff846eff7869ffac88ff846eff9f7dff9f7dff9f7dffac88ffffffffac88ffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dffac88ff7e6cff8c72ffac88ff846eff846effac88%
-  ffffffffac88ff9f7dffffffffac88ffffffffac88ffffffffffffffffffffac88ff9f7dff8c72ffffffff846eff9f7d%
-  ff9576ff8c72ff9576ff9576ff7e6cff9576ff9576ff846eff7e6cff6f65fd6561ff6f65fe6862fc6260fe6862ff7367%
-  fd6561ff6f65ff6b63ff9576ff9576ff7e6cff9576ffac88ffffffff9f7dff9f7dffac88ffac88ffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9576ff9f7dff9f7dff8c72%
-  ffac88ff7869ffac88ff9f7dffac88ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff846e%
-  ffac88ffac88ff9576ff8c72ff9576ffffffff9f7dff9f7dff846eff9f7dff8c72ff9f7dff8c72ff8c72ff846eff846e%
-  ff7869fc6260fa5e5fff6b63fd6561ff6f65ff7367ff7e6cff846effac88ff846effac88ff8c72ffac88ffac88ff9576%
-  ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffff%
-  ff9f7dff9f7dff8c72ff9f7dffac88ff9576ff8c72ff8c72ff7e6cff9f7dff9576ff9f7dffffffffac88ffac88ff9f7d%
-  ffffffffffffff9f7dffffffffffffffffffff7869ffac88ff7e6cff9f7dffffffff9f7dff7e6cff9576ff8c72ffac88%
-  ff8c72ff8c72ff6f65ff9576ff7367ff6f65ff7367ff7869fc6260ff7e6cff7367ff6f65ff7e6cff7e6cff7e6cff8c72%
-  ff9f7dff9f7dffffffffac88ffffffff9576ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88%
-  ffffffff9f7dffac88ffac88ffac88ffac88ff9f7dff8c72ff9f7dff8c72ff7e6cff8c72ffac88ffac88ff9576ffac88%
-  ffac88ff9f7dffac88ff9f7dffffffffac88ffac88ff9576ff9f7dff8c72ff8c72ff9f7dffffffff8c72ff9f7dffffff%
-  ff846eff8c72ff7367ff8c72ff9f7dff9576ff7e6cff7367ff9576ff6f65fd6561ff9576ff6f65ff6f65ff7367fe6862%
-  ff7e6cff8c72ff8c72ff9576ff9576ff8c72ffac88ffac88ff9f7dff9f7dffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffff9f7dffffffff9f7dffffffffffffff8c72ffac88ff7e6cff8c72ff8c72ff9576ff846e%
-  ffac88ff846effffffffffffff8c72ffffffffffffffac88ffffffff9576ffffffffffffffac88ffac88ff8c72ff9576%
-  ff9f7dff9f7dffac88ff8c72ff9f7dff7e6cff7869ff9f7dff9f7dff8c72ff846eff9576ff7367ffac88ff7367ff7367%
-  fe6862ff7367ff6b63fe6862ff6f65ff6f65ff9f7dff9f7dff846eff9576ff9f7dff9f7dff9f7dff9f7dffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ff8c72ffffffff7869%
-  ff846eff8c72ff9576ff8c72ff9576ffffffff9f7dffffffff9f7dffac88ffffffffffffffffffffac88ff9f7dffac88%
-  ff9f7dff9f7dff9f7dff8c72ff9576ff9f7dff9576ff9576ff8c72ff6b63ff9f7dff6f65ff9576ff6f65ff846eff8c72%
-  ff9576ff8c72ff846eff9576fd6561fd6561ff8c72ff8c72ff9576ff846eff7e6cff6f65ff9576ffffffffac88ffac88%
-  ff9f7dffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9f7dff9576ffac88ffac88ff9f7d%
-  ffac88ff8c72ff9f7dffac88ffac88ff9f7dff9576ffac88ffac88ff8c72ff9f7dffffffffac88ff9f7dffffffffac88%
-  ff9f7dff8c72ffffffff9f7dff9576ffac88ff9576ffac88ff9f7dff9576ff8c72ff9576ff9f7dff9f7dff7e6cff6f65%
-  ff7869ff7869ff7e6cff8c72ff7e6cff8c72ff9576ff7e6cff8c72ff846eff7869ff6f65ff6f65ff7e6cff6b63ff7869%
-  ff846eff9f7dff9f7dff9f7dff9f7dff9f7dffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffac88ffac88ff9f7dffac88ff9f7dffffffffac88ff8c72ff9f7dffac88ff9576ff8c72ff8c72%
-  ff9f7dff9f7dff9f7dffac88ffffffffffffffac88ff9f7dff8c72ffffffff9f7dffac88ff9576ffac88ff9576ff9f7d%
-  ff8c72ff9576ff7e6cff7367fd6561ff9f7dff7869ff9576ff846eff8c72ff846eff8c72ff7e6cff8c72ff7869ff846e%
-  ff7e6cff6f65ff7367ff9576ff846eff846eff9576ff7e6cffffffff9f7dff8c72ffac88ffac88ffac88ffffffffffff%
-  ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffffff9576ff9576ffac88ff9576ff9f7d%
-  ff9576ffac88ffac88ffac88ffac88ffffffffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffff8c72ff9f7d%
-  ff9576ffffffff9f7dff846effac88ff8c72ff9576ff7367ff7869ff8c72ff8c72ff7367ffac88ff846eff8c72ff9f7d%
-  ff8c72ff9576ff7e6cff7e6cffac88ff9f7dfb605fff846eff9f7dff8c72ff9576ff9576ff9f7dff7e6cff8c72ffffff%
-  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffff9f7dff9f7dffac88%
-  ffac88ffac88ffffffff9f7dffac88ffac88ffac88ff9f7dffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
-  ffac88ff9f7dffac88ffac88ffac88ffac88ff9576ff9f7dff9576ff8c72ffac88ff9576ff9576ff7e6cff7869ff8c72%
-  ff6f65ff9576ff8c72ff7e6cff9576ff8c72ff846eff8c72ffac88ff7e6cff8c72ff6f65ff8c72ff9f7dff8c72ff7367%
-  ff9576ff846ef6545cff7e6cffac88ffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88%
-  ffac88ff8c72ffac88ff9f7dff846effffffffffffffffffffac88ffffffffac88ff9f7dff9576ff9576ff9576ff7e6c%
-  ffffffffac88ffac88ffffffffffffff9576ff9f7dff846eff9576ffac88ff8c72ff9576ff846eff8c72ff9576ff7869%
-  ff9f7dff9576ff7e6cff9576ff8c72ff7869ff9576ff9f7dffffffff846eff7367ff7869ff7e6cff846eff9f7dff7e6c%
-  ff846eff9576ff9576ff6f65ff7367ff846ef6545cf95c5eff9f7dffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffac88ffac88ffac88ff9f7dffac88ffac88%
-  ffffffff8c72ff7869ff6f65ff7e6cff9f7dff8c72ffac88ff9f7dffffffff7869ffffffff9f7dffac88ff9576ff846e%
-  ff8c72ff8c72ff7367ff7367ff7367ff6f65ff9576ff846eff9576ff846eff7367ff8c72ff8c72ff8c72ff9f7dff9576%
-  ff7e6cff846eff7e6cff8c72ffac88ffac88ff8c72ff7e6cfa5e5ffd6561fd6561f24a59ff7e6cffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9f7dffffffffffffff9f7dff9f7d%
-  ffffffffac88ff9576ffac88ffffffffffffff9576ff8c72ff6f65fe6862ff8c72ff9f7dff9576ffffffffffffff8c72%
-  ff8c72ff8c72ff846eff8c72ffac88ff8c72ff9576ff7367ff846eff9576ff7367ff7e6cff7869ff846eff9f7dff846e%
-  ffac88ff9f7dff846eff7e6cff8c72ff846eff7367ff9f7dff846eff846eff9f7dff7e6cff7367f7565cfe6862ff7367%
-  ff7367ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
-  ffac88ffffffffac88ffffffffffffffac88ffffffffac88ffffffff9576ffffffffac88ff9576ff7e6cff846effffff%
-  ffac88ff9f7dff9576ffac88ff9f7dff9576ffac88ff7e6cff846eff7869ff7869ff6b63ff846eff6f65fe6862ff6b63%
-  ff7869ff6b63ff7e6cff6f65ff7869ff8c72ff7e6cff9576ff7e6cff8c72ffac88ff9f7dffffffffffffff8c72ffac88%
-  ff7e6cff6f65ff6b63ff846eff7e6cffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ff9f7dff9f7dffac88ffac88ffffffffffffff9f7dffffffffac88ffac88ffffffffac88ffac88ff9f7dffffff%
-  ffffffff9f7dffac88ffffffff9576ffffffffffffffffffffac88ffffffff9f7dffac88ff7e6cff9576ff846eff7e6c%
-  fd6561ff7367fc6260ff6f65fe6862ff6b63ff6f65ff6b63ff7367ff846eff8c72ff9f7dff9576ff9576ffac88ff846e%
-  ff9f7dffffffffac88ffac88ff9f7dff8c72ff8c72ff846eff9576ffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffffffff9f7dffffffffac88ffac88ffffff%
-  ffac88ffffffffac88ffac88ffac88ff9576ff9576ff9f7dffac88ff9f7dff9f7dff9576ff8c72ffac88ff9576ff8c72%
-  ff9576ff8c72ff7869ff7367fd6561fa5e5fff6b63ff6f65f95c5efd6561f6545cf85a5df5515bfa5e5fff6f65ff7869%
-  ff9576ff8c72ff9f7dff846eff8c72ff9f7dff8c72ff9576ffffffffffffffffffff9f7dffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
-  ff9f7dffac88ffac88ff7e6cffac88ff9f7dffffffff9f7dffffffffffffffffffff9f7dffffffffac88ffac88ff9f7d%
-  ff9f7dffffffffac88ff7869ff7e6cff846eff7869ff846eff846eff6f65fc6260f95c5efc6260f85a5df34d59f6545c%
-  f4505af5535bfd6561ff7e6cff7869ff7e6cff846effac88ffac88ffac88ff9f7dffac88ffac88ffac88ff9f7dffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffffffffac88ffffffffffffffac88ffffffff9f7dffac88ffac88ffffffffffffffac88ffffff%
-  ff9f7dffac88ffffffffac88ff9576ff7e6cff9f7dff9f7dff9576ffac88ff8c72ff7869fe6862ff6f65ff7367ff6f65%
-  fa5e5ff85a5df34d59fb605ffa5e5ff7585dfc6260f95c5eff6f65ff6b63ff9576ff9f7dff9f7dffac88ffffffffac88%
-  ff9f7dffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ff9576ffac88ffac88ff9f7dffffffff9f7dffffffffac88ffffff%
-  ffac88ffac88ffac88ffffffffffffffffffffffffffffffffac88ffac88ff9f7dff846eff7e6cff7367ff7e6cff8c72%
-  ff7869ff846eff7367fd6561f95c5ef7585df7565cf4505af6545cf5515bf4505af85a5dfe6862ff8c72ff9576ff7869%
-  ff9f7dff8c72ff9f7dffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88%
-  ffac88ffac88ff9f7dffffffffffffff9f7dffffffffffffffffffffffffffac88ff9576ff9f7dff9576ffac88ffffff%
-  ffac88ffac88ff6f65ff8c72ff846efd6561ff7869fb605ff7585df5515bfc6260f34e5af7585df6545cf4505af7565c%
-  f95c5eff6b63ff7e6cff9576ff846eff8c72ff9f7dff7869ffffffffffffffac88ffffffffffffffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffac88ff9f7dffffffff9f7dff9f7dff9f7dffffffff846effac88ffffffffffffffffffffac88ffac88ff9576%
-  ffac88ffffffff9f7dff9576ff8c72ffffffff7e6cff846eff7869ff7367fe6862ff7e6cf5535bfd6561f34e5afb605f%
-  f5515bf7585df4505af5515bf5515bff6b63ff6f65ff8c72ff9576ff9f7dff9f7dffac88ffac88ffac88ffffffffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ff9f7dff8c72ff9f7dff9f7dffac88ffffffffffff%
-  ffac88ffffffffffffffffffffffffff9f7dffac88ffac88ff9576ff8c72ff7869ff846eff8c72ff846eff7869f7565c%
-  ff6b63f7585df6545cf6545cf95c5ef24b59f04757f5535bfd6561f5535bfd6561ff7367ff7367ff7e6cff846eff9f7d%
-  ff8c72ff8c72ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7dff9f7dff846e%
-  ff7e6cff9f7dff9f7dff9f7dffffffffffffffac88ff9f7dffffffff9576ffac88ffac88ff9f7dff9f7dff846eff9f7d%
-  ff9f7dff9576ff7869ff7367fc6260fe6862fc6260fa5e5ff34d59fb605ff7565cf5535bf6545cf7585dff7367ff7869%
-  ff7367ff7869ff6f65ff7e6cffffffff9f7dff9f7dffffffffac88ffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ff7869ff9f7dff9f7dff9f7dffac88ff9f7dffffffffffffffffffff9f7dffac88ff9576%
-  ffac88ff9f7dff846eff9576ff8c72ff7367ff7869ff6f65ff7869ff7e6cfb605ffa5e5ffa5e5ff7585df7565cf5515b%
-  f7565cf4505afe6862ff7367ff6f65ff7367ff9f7dffac88ff9576ff9f7dff9f7dff9f7dffffffffac88ffac88ffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ff9f7dff9f7dff9f7dffac88ff9f7dff8c72ff7869ff846eff8c72ffffffffffffffac88%
-  ffffffffffffffffffff9f7dffffffff8c72ff9576ffffffffac88ff7367ff846eff7367ff846eff7869fc6260f5535b%
-  fb605ff85a5df7565cf85a5dfe6862fa5e5ffc6260ff7e6cff846eff7367ffac88ff9f7dffac88ffac88ff9f7dff8c72%
-  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffffffffff9f7dffac88ff9576ff9576ffac88ffac88ff9576ff846effac88ff8c72%
-  ffac88ffac88ffac88ffffffffffffffffffff9f7dff9f7dff8c72ffffffffffffff9f7dffac88ff9f7dff7e6cff8c72%
-  ff846eff6b63fc6260fe6862f7565cf4505afd6561fa5e5ffa5e5ffa5e5ffd6561ff7367ff8c72ff846eff6f65ff7367%
-  ffac88ff9576ffac88ff9f7dffac88ffffffffffffffffffffffffff9576ffffffffac88ffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff9f7dff9576ff8c72ff846e%
-  ff8c72ff9f7dff9576ffac88ff9f7dff9f7dffffffffffffffffffff9f7dffffffff9f7dffac88ffffffffac88ff9576%
-  ff846eff9576ff8c72ff9f7dff7e6cff7869ff6b63ff7367fd6561f6545cfe6862f95c5ef7565cf5535bff6b63fe6862%
-  ff7367ff846eff9f7dff7367f95c5eff7367ffac88ff9f7dff9f7dffac88ff9f7dffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffffffffffff%
-  ff9576ffffffff7869ff846eff9576ff9f7dff9f7dffac88ffac88ffac88ffac88ffffffffac88ffac88ff9f7dffac88%
-  ff9f7dffac88ff9576ffffffff9576ffac88ffac88ff7e6cff6f65ff8c72ff7869ff9576fd6561f85a5dfb605ffb605f%
-  f5515bfb605ffc6260fc6260fb605fff846eff846efc6260f34e5af5535bff9576ff9f7dffac88ffffffffffffff9f7d%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffff9576ffffffffac88ffac88ff9576ff9576ff8c72ffffffff9f7dffac88ffffffff9576ffac88ffac88ff7e6c%
-  ff7869ff7e6cff9576ffac88ff9f7dff9576ffac88ffac88ffac88ffac88ffac88ffffffffac88ff9576ffffffff9f7d%
-  ff7e6cff8c72ff7367ff6b63fe6862fd6561f7585dfa5e5fff6f65fd6561ff8c72fe6862f7565cea3d54f34d59ff9576%
-  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffff9f7dffffffff9576ffac88ff9576ffac88ff9f7dffac88ff9576ff9576%
-  ffffffff9576ffffffff6b63ff7869f95c5eff7e6cff7e6cff8c72ff9f7dffac88ffac88ff846eff8c72ff9f7dff9576%
-  ff8c72ff9576ff9f7dff8c72ff846eff8c72ff7869ff846eff9576ff7367fc6260fe6862f5535bfe6862ff6f65ff7e6c%
-  fe6862f7585def4457ff6b63ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff8c72ffac88ffac88ffac88%
-  ff9f7dffffffffac88ffac88ffffffffac88ffac88ffac88ff9f7dff7367ff7e6cff9f7dff9f7dffac88ff9f7dffac88%
-  ffffffffac88ff8c72ffac88ff9576ff9f7dff8c72ff9576ff846eff7e6cff7e6cfe6862ff846eff6f65ff6f65ff6f65%
-  fd6561fd6561fd6561ff7e6cff9f7dff6b63fd6561ff7e6cff9f7dffac88ffffffffffffffffffffffffffffffffac88%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ff8c72ffffffffac88ffffffff9f7dffac88ffffffffffffffac88ffac88ffffffff9f7dff846eff9576ff9f7dff9f7d%
-  ffffffff9f7dffac88ffac88ffffffffffffff9576ffffffff8c72ff9576ff9f7dffac88ff9f7dff9576ff9576ff9576%
-  fd6561fd6561ff7869ff7e6cff7e6cf7565cff7367ff7869ff6f65ff8c72ff9576ff8c72ff9576ffac88ffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ffffffff9f7dffffffffffffffffffffac88%
-  ffac88ff9f7dff9f7dff9f7dffac88ffac88ffffffffffffff9f7dff8c72ffac88ffac88ffac88ff9576ff7e6cff6b63%
-  ff9f7dff9576ff9f7dff8c72ff9576ff9576ff846eff7367ff7e6cff7367ff7869ff8c72ff7869ff8c72ffac88ff9576%
-  ff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffac88ffac88%
-  ffac88ffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffffffffff9f7dffffffff9f7dffac88ff8c72ff9f7d%
-  ff9576ff9576ff7869ff846eff9f7dff9f7dffffffff7e6cff9f7dff7e6cff846eff6b63ff6f65ff7e6cffac88ff846e%
-  ff8c72ff9576ff7e6cffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9576ffffffffac88ffffffffac88ffffffff9576ffac88ff9f7dff9f7dffac88ff9f7dffffff%
-  ff9f7dffac88ff9576ff9576ff9576ff9f7dff9576ff8c72ff8c72ff9576ff7367ff7367ff7e6cff7869ff8c72ff8c72%
-  ff7869ff7e6cff846effac88ffac88ff9f7dff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ff9f7dffac88ffac88ffffffffffffffac88ffac88%
-  ff846effac88ffffffffac88ffffffff9f7dffac88ffac88ff9f7dff846effac88ff9576ff8c72ff8c72ff7869ff9f7d%
-  ff8c72ffac88ff7e6cff6f65ff7e6cff846eff846eff6f65ff846effac88ffac88ffac88ffac88ffffffffffffffffff%
-  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffff%
-  ff9f7dffac88ffffffff9576ff8c72ffac88ff846eff9f7dffac88ff9f7dff9f7dff8c72ff9576ff9576ff9f7dffac88%
-  ff8c72ff9f7dff9f7dff9f7dffac88ffac88ff9f7dff9576ff8c72ff9576ff7e6cff846effffffff9f7dff9f7dffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
-  ffffffffac88ffac88ff9576ff9f7dff846eff9f7dff9576ff8c72ffac88ff9576ff8c72ffac88ff9576ff9f7dffac88%
-  ff9f7dff8c72ff9f7dff6f65ff8c72ff8c72ff9576ff846eff9576ffac88ffac88ff7e6cff8c72ff8c72ff7e6cff7869%
-  ff9f7dff8c72ffffffffac88ffac88ffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffff9f7dff9f7dffac88ff9f7dff8c72ff7869ff7367ff7e6cff9f7dffffffff8c72ff846e%
-  ff9f7dffac88ffffffffffffffffffff846eff7e6cff7e6cff9576ff8c72ffac88ff846eff9f7dff846effffffff9f7d%
-  ff7869ffac88ff9f7dff8c72ffac88ffac88ffac88ff9576ffac88ffac88ffac88ffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff7869ff8c72ff7367fa5e5f%
-  ff9f7dffac88ff9f7dffffffff9576ffac88ffac88ff9576ff8c72ff9f7dff9f7dff7e6cff7869ff7e6cff8c72fb605f%
-  ff846eff846effac88ff846eff846effac88ff9576ffac88ff9f7dffac88ffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dffffff%
-  ff9576ffffffff7367ff7869ff7e6cff8c72ff846eff9f7dff846eff9f7dffac88ff9576ff8c72ff8c72ff9576ff846e%
-  ff8c72fc6260ff7367fb605ffc6260ff7367fe6862ff6f65ff846eff8c72ff7e6cff9f7dffffffff9f7dffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffac88ffac88ff8c72ff8c72ffffffff8c72ff846eff7e6cff8c72ff9576ff9576ff9576ffffffffffffffffff%
-  ff846eff9576ff846eff7e6cfb605ffe6862fd6561f95c5ef6545cfb605fff6b63f7565cff7869ff846effffffff8c72%
-  ff8c72ffac88ffac88ffac88ffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff7e6cff9f7dff9576ff9576ffffffffac88ff9576%
-  ff9576ff9576ff8c72ff7367ff7e6cff9576ff8c72ff9576f6545cff6b63f14958f95c5ef14958fc6260f5535bf4505a%
-  fa5e5ff95c5eff8c72ff846eff9576ff9f7dffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff9576ff9f7dff9f7d%
-  ff9f7dffac88ff9f7dff8c72ffac88ff846effac88ff9576ff7869ff8c72ff6f65ff6f65ff7869fb605ffb605ff24a59%
-  f5515bf24a59fa5e5ff5515bf95c5eff7869ff7367ff8c72ffac88ffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffffffffffffffac88ff9576%
-  ffffffffac88ff8c72ffac88ff9576ffac88ff846eff9f7dff9576ff9f7dff8c72ff846eff7e6cff7869ff9f7dff9f7d%
-  fc6260ff6b63f85a5df6545cf7565cf14958ef4457f14958fa5e5ffe6862ff6b63fd6561ff9f7dffac88ffac88ffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ffffffffac88ffffffffac88ffffffffffffffac88ff9576ff8c72ff6b63fa5e5ff5535bff7869ff7869ff7e6c%
-  ff6f65ff7367ff7367ff7367ff7367ff6f65ff6f65f85a5df24b59f4505af04757f04557f24b59f4505aff6b63ff8c72%
-  ff8c72ff8c72ff8c72ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9576ff7e6cfb605f%
-  f34d59f7585dfc6260ff7e6cff7869ff6b63ff7869fd6561fc6260ff7e6cf95c5eff6b63f5535bf6545ced4155ef4457%
-  f34e5af6545cf5535bfd6561fe6862ff846eff7869ff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dff9576ff9f7dffffffff9576ffac88%
-  ff9576ff8c72ff7e6cff6f65ff7869ff8c72ff6b63ff7869fc6260ff6f65ff7869ff6f65fc6260fc6260f95c5eff6b63%
-  f34e5af4505af14958ef4356f4505af34e5af14958f34e5af7565cfe6862ff9576ff7869ff9f7dffac88ffffffffffff%
-  ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7d%
-  ff9576ff846effac88ffffffff846eff8c72ff7367ff7367fd6561ff7869ff6f65ff7869ff7367ff7e6cff7e6cf85a5d%
-  fb605fff7367f6545cf95c5ef85a5df85a5df7565cf24a59f5515bf7585df34e5af24a59ef4457fe6862ff6b63ff6f65%
-  ff846effffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
-  ff9f7dffffffffffffffffffff9576ff9f7dffac88ffac88ffac88ff6f65ff8c72ff9576ff9f7dff7367fe6862ff7367%
-  ff7869ff7869ff7869fe6862ff7869ff6b63ff8c72fb605ffe6862f85a5df7565cfa5e5ff04757f6545cf34d59f14858%
-  e73952f24b59fd6561ff8c72ff9576ff9f7dffffffff9576ffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffffffff9f7dffac88ff9576ffac88ff7e6cff846eff8c72ff846eff7869ff7e6cff9f7d%
-  ff9576ff6f65fd6561ff6b63ff8c72fe6862ff8c72ff846eff7e6cfe6862ff6f65ff7869fd6561fc6260f7565cf95c5e%
-  f14858f34d59f7585df95c5ef24a59f7585df7585dff6b63ff9576ff9576ffffffffac88ffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ffffffff7869ff846eff8c72ff8c72%
-  ff8c72ff7869ff846eff846eff7869ff7367fe6862ff7367ff9576fc6260ff846efe6862f7585dfe6862ff7367fe6862%
-  f95c5efe6862f85a5df5535bf7565cf24b59f5535bf7585df7585df95c5eff6f65ff8c72ff9576ff7e6cffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9576ff846effac88ff9576%
-  ff846eff7869ff9576ff846eff7367ff7e6cff9576ff846eff7e6cff7869ff6b63ff6b63ff7869fe6862f85a5dff6b63%
-  ff6f65ff7367fa5e5ff6545cf95c5efa5e5ff5535bf85a5df5515bf7585def4356f85a5df7585dfd6561fe6862ff8c72%
-  ff9f7dffac88ff9f7dffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
-  ffac88ffac88ffac88ff9f7dffffffffac88ff846eff9576ff8c72ff9576ff7e6cff846eff7e6cff846eff7869ff6b63%
-  ff846eff846eff846efc6260fe6862fd6561fb605ff4505afd6561f7585df7565cfd6561fc6260f95c5ef6545cfe6862%
-  ff7367ffac88ffac88ffffffffac88ff9f7dffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffff9f7dffffffffac88ffac88ffac88ffffffff846eff7e6cff6f65ff9576ff8c72ff7869ff6f65%
-  ff7367ff9576ff7e6cff7367ff7367ff6f65fe6862fc6260ff6b63f7565cf85a5df34e5af7565cf24a59f7565cff6f65%
-  fa5e5ffa5e5ffb605fff7e6cff9576ff7869ff8c72ffffffffffffff9f7dffac88ffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9576ffffffff7e6cff7367fc6260%
-  fa5e5ffa5e5ffc6260f7585df95c5eff7e6cff846eff8c72ff6f65ff7e6cfe6862fd6561fc6260fd6561f5535bf85a5d%
-  f7565cfb605ffe6862ff7367ff7869ff7869ff8c72ff7e6cff846eff9f7dffac88ff9576ffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88%
-  ffffffff9576ff9f7dff8c72ff7367ff9576ff6b63fd6561f7585df7565cff9576ff7869ffac88ff8c72ff846eff9576%
-  ff6f65ff7869ff6f65ff6b63ff846eff9576ff846eff9576ff9f7dffac88ffac88ff9576ff9576ffffffffac88ffac88%
-  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffac88ffac88ff9576ff6f65ff9576ff7869f95c5ef34e5af04557fd6561%
-  ff7869ff7367ff9f7dffac88ff846effac88ff9f7dff9f7dffac88ffac88ff9f7dffffffffffffffffffffffffffac88%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
-  ffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffac88ffac88ffac88ffffffffffffffffffffffff%
-  ffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9f7dffac88ffffffffac88ffac88ff9f7d%
-  ffac88ffffffffac88ffac88ff9f7dff9576ff9576ff7869ffffffff8c72ffac88ffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ff8c72ffac88%
-  ffffffffffffffac88ff9f7dff9f7dffffffffac88ff9f7dff9576ff846eff7869ff6f65ff7367ff846eff8c72ffac88%
-  ffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffac88ff8c72ff7869ff6f65ff7e6cff8c72ff7e6cff7e6cf95c5eff6b63f7585df24b59ef4457e63852e43551df304e%
-  e73952e53651f14858f95c5eff6b63ff8c72ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffff9f7dff8c72ff7367ff6b63f7565cf85a5df24b59f14858f14858f4505ae53751%
-  ea3d54e33450da294bda2a4cd8274adc2b4cdd2d4dee4156ff6b63ff9576ffac88ff9f7dffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ff8c72ff9576ff7367fe6862f7585dee4256f24a59eb3e54%
-  ef4356e73952e23350e23450de2e4ee43651dc2c4cdc2c4cd62449d01d45d52349d9274bf04557fa5e5ffc6260ff8c72%
-  ffac88ffffffffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9f7dff7367ff8c72ff7869%
-  f24b59ef4457e63852df304ee0314fe33550ea3d54e2324fe43651df2f4ee0314fe1314fe1314fdf304ee53651eb3e54%
-  ff7367ff8c72ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
-  ffac88ffac88ff9f7dff9576f95c5efd6561fd6561f5515bf95c5efc6260f95c5efa5e5ffe6862fd6561ff7e6cff7869%
-  fd6561ff9576ff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88%
-  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
-  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff8b0000%
-  ae062ab2072db80c32c1133ac91840ea3d54ff6b63ff7e6cff9f7dffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9cffffffffffff9cea9c9cea9c9cea9c%
+  9cea9c9cea9c72cd8dffffff9cea9c79d48d85de9172cd8d62bd8b67c28b5eb98a5ab58972cd8d79d48d5ab5899cea9c%
+  6cc78c6cc78c79d48d67c28b67c28b5ab58962bd8b4da9874da98762bd8b53af8853af884da98743a1864aa787339684%
+  3e9d8548a586399a85379985278f831f8a821e87821e84821e85821f7b821f7f82207081207181206c81206f81206981%
+  206b81226381226481226181000080ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c%
+  9cea9cffffffffffff79d48d9cea9c9cea9cffffff9cea9cffffffffffff85de91ffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffff79d48d85de9179d48d72cd8d85de9179d48d9cea9c85de9167c28b85de9185de919cea9c%
+  9cea9c5eb98a6cc78c53af8872cd8d67c28b6cc78c6cc78c5eb98a248d83ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  9cea9cffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff85de9185de91ffffffffffff85de91ffffffffffff9cea9cffffff85de9185de916cc78c72cd8d85de91%
+  72cd8d79d48d85de9162bd8bffffff9cea9c5ab58962bd8b72cd8d85de9162bd8b85de9167c28b62bd8b379985ffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffff85de91ffffff9cea9cffffffffffff9cea9c85de91ffffff85de91ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c9cea9cffffff85de9185de91ffffffffffff9cea9cffffffffffff85de91%
+  9cea9c9cea9c85de9185de9179d48d79d48d6cc78c67c28b85de9172cd8dffffff62bd8b72cd8d62bd8b5eb98a85de91%
+  79d48d48a58667c28b50ac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff85de91ffffff9cea9cffffff9cea9c9cea9cffffff%
+  ffffff85de91ffffff9cea9cffffff9cea9cffffff85de9179d48dffffffffffffffffffffffffffffffffffff9cea9c%
+  9cea9cffffffffffff85de919cea9c79d48d6cc78c79d48d79d48d85de9179d48d72cd8d79d48d9cea9c67c28b56b289%
+  9cea9c6cc78c67c28bffffff85de915ab5895eb98a6cc78c50ac88ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffff%
+  ffffff9cea9cffffffffffffffffff9cea9cffffff85de91ffffff9cea9c85de91ffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9c85de9179d48d9cea9c9cea9c85de9167c28b9cea9c85de916cc78c72cd8d72cd8d%
+  72cd8d6cc78c62bd8b6cc78c72cd8d79d48d72cd8d67c28b9cea9c5eb98a72cd8d5eb98a67c28b50ac88ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff85de919cea9c85de91ffffffffffffffffff85de919cea9cffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffff85de919cea9c9cea9c85de919cea9c85de919cea9c9cea9cffffff72cd8d79d48d72cd8d%
+  79d48d85de9179d48d56b2896cc78c67c28b72cd8d62bd8bffffff67c28b72cd8d67c28b67c28b72cd8d72cd8d5eb98a%
+  67c28b79d48d62bd8bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffff85de91ffffffffffffffffff9cea9cffffffffffff85de91ffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffff85de91ffffff85de9185de9185de91%
+  79d48d79d48d67c28b9cea9c72cd8d85de916cc78c56b28985de9162bd8b50ac8867c28b6cc78c62bd8b79d48d79d48d%
+  6cc78c62bd8b62bd8b67c28b85de9185de9185de91ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c85de91ffffff9cea9cffffff9cea9c9cea9cffffff85de91ffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9c%
+  67c28b9cea9c85de9185de9179d48d85de9153af8872cd8d5eb98a6cc78c50ac884da98772cd8d4da98756b28962bd8b%
+  5eb98a79d48d67c28b72cd8d9cea9c72cd8d9cea9c67c28b79d48d72cd8d79d48d9cea9c79d48dffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9cffffffffffff9cea9c%
+  9cea9cffffff85de91ffffff6cc78c9cea9c79d48dffffff72cd8d9cea9c72cd8d9cea9c50ac8872cd8d72cd8d5eb98a%
+  5eb98a62bd8b5eb98a5ab58953af8856b28950ac885eb98a79d48d62bd8b79d48d6cc78c6cc78c85de9185de9179d48d%
+  ffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffff9cea9c85de919cea9c9cea9cffffff9cea9cffffffffffffffffffffffff%
+  ffffff79d48d85de919cea9c85de91ffffff79d48dffffff85de916cc78c85de9185de9179d48d79d48d72cd8d6cc78c%
+  6cc78c5eb98a56b28956b2894da9876cc78c50ac8856b2894aa78745a286409f8656b2895eb98a67c28b72cd8d85de91%
+  85de9179d48dffffff6cc78c79d48dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffff85de91ffffff9cea9cffffff72cd8d85de91ffffff85de9179d48d%
+  6cc78c85de9172cd8d9cea9c67c28b6cc78c53af8850ac8853af885eb98a56b2893e9d85409f8656b2894da9874aa787%
+  56b28967c28b67c28b72cd8d6cc78c9cea9cffffff67c28bffffff85de919cea9c79d48dffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9cffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9cffffff85de91%
+  9cea9cffffff72cd8d9cea9c85de9162bd8b56b28979d48d79d48d67c28b67c28b5ab58953af8850ac883e9d8545a286%
+  48a5862f94843e9d8533968450ac884da98762bd8b53af8885de916cc78c85de919cea9c9cea9cffffff9cea9cffffff%
+  56b289ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  ffffffffffffffffffffffff85de91ffffffffffffffffffffffff9cea9c9cea9c79d48d9cea9cffffffffffffffffff%
+  9cea9c9cea9cffffff79d48dffffff79d48d79d48dffffff72cd8d79d48d6cc78c72cd8dffffff72cd8d62bd8b50ac88%
+  6cc78c5ab58953af8850ac8843a1863e9d8556b28950ac883b9c8550ac8843a1866cc78c79d48d72cd8d85de9185de91%
+  9cea9c85de91ffffffffffff79d48d1e8582ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  9cea9cffffffffffffffffffffffffffffff9cea9cffffff85de919cea9cffffff9cea9c85de919cea9c9cea9c85de91%
+  ffffffffffffffffff6cc78c9cea9cffffffffffff9cea9c85de915eb98a9cea9c85de916cc78c72cd8d72cd8d85de91%
+  6cc78c6cc78c79d48d67c28b62bd8b45a28648a58653af884aa78743a18650ac884aa78767c28b43a18645a28650ac88%
+  67c28b62bd8b6cc78c79d48d9cea9c79d48d85de9179d48d9cea9c85de911f7c82ffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffff79d48dffffffffffff85de91%
+  ffffffffffff79d48dffffff9cea9cffffffffffff9cea9c9cea9c9cea9c85de91ffffff85de9179d48d85de919cea9c%
+  9cea9c85de9172cd8d72cd8d6cc78c5eb98a67c28b79d48d62bd8b56b28948a5864da98735988448a586379985399a85%
+  45a2864aa7873799853598844aa7874da9876cc78c79d48d9cea9c9cea9cffffffffffff85de9172cd8d67c28b1e8382%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff85de91ffffff9cea9cffffff9cea9c%
+  ffffff72cd8d9cea9c9cea9cffffff9cea9cffffff85de9185de91ffffff9cea9c79d48dffffff85de919cea9c79d48d%
+  6cc78c9cea9c85de9172cd8d9cea9c79d48d72cd8d72cd8d62bd8b72cd8d5eb98a6cc78c62bd8b67c28b67c28b56b289%
+  56b28953af883b9c853e9d8553af88409f86409f86399a8553af884da98767c28b72cd8d9cea9c85de9185de9185de91%
+  9cea9c72cd8d6cc78c53af882a9183ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9cffffffffffffffffff%
+  9cea9c9cea9cffffffffffff85de919cea9c9cea9c9cea9cffffff9cea9c79d48dffffff85de919cea9cffffff9cea9c%
+  85de9185de919cea9c9cea9c79d48d72cd8d85de9185de9185de9172cd8d85de9167c28bffffff5eb98a72cd8d67c28b%
+  6cc78c67c28b48a58653af885eb98a53af8843a18650ac884aa7874aa787399a85399a85409f864aa7876cc78c62bd8b%
+  6cc78c72cd8d79d48dffffff6cc78c85de9167c28b67c28b53af884aa787ffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff85de9185de919cea9cffffffffffffffffff%
+  9cea9cffffff9cea9cffffff79d48dffffff9cea9c9cea9cffffff9cea9c9cea9c85de9185de916cc78c79d48d85de91%
+  85de9172cd8d62bd8b6cc78c72cd8d62bd8b62bd8b62bd8b62bd8b50ac8850ac88339684409f8650ac8835988445a286%
+  4da98748a5864da98767c28b72cd8d6cc78c9cea9c9cea9c85de9185de9185de9167c28b67c28b5eb98a79d48dffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9c79d48d9cea9c9cea9c85de91ffffff9cea9c%
+  ffffffffffff85de91ffffff85de91ffffff9cea9c9cea9c9cea9cffffff9cea9c9cea9c72cd8d85de9185de916cc78c%
+  9cea9c9cea9c67c28b85de9185de916cc78c79d48d85de9172cd8d62bd8b5ab58962bd8b67c28b62bd8b53af884aa787%
+  53af8848a5864aa78750ac8843a18650ac8862bd8b62bd8b6cc78c72cd8d79d48d6cc78c85de919cea9c85de9185de91%
+  85de9185de9185de9179d48dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff%
+  85de91ffffff72cd8d79d48d85de91ffffffffffff85de9185de919cea9c79d48d85de91ffffff85de91ffffff9cea9c%
+  85de919cea9c85de9179d48d72cd8d85de9185de9172cd8d62bd8b85de9162bd8b79d48d6cc78c62bd8b48a58679d48d%
+  67c28b62bd8b62bd8b53af8850ac884aa78748a58645a2863e9d85409f8648a58662bd8b53af8879d48d9cea9c79d48d%
+  ffffff9cea9c85de919cea9cffffff85de91ffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  9cea9cffffff9cea9cffffffffffff9cea9c9cea9c85de9185de9179d48d85de91ffffff9cea9cffffff9cea9c9cea9c%
+  85de9185de91ffffffffffff85de919cea9c9cea9cffffff79d48dffffff9cea9c62bd8b79d48d85de919cea9c79d48d%
+  62bd8b67c28b79d48d85de915ab58962bd8b4aa78767c28b5ab58950ac884aa7874aa78767c28b62bd8b53af8856b289%
+  6cc78c62bd8b9cea9c6cc78c85de9185de9185de919cea9cffffff9cea9cffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffff9cea9cffffff85de9185de919cea9c67c28b72cd8d9cea9c6cc78c6cc78c9cea9c%
+  ffffff9cea9c85de91ffffff9cea9cffffff9cea9cffffffffffffffffff9cea9c85de9172cd8dffffff6cc78c85de91%
+  79d48d72cd8d79d48d79d48d67c28b79d48d79d48d6cc78c67c28b5ab58950ac885ab58953af884da98753af885eb98a%
+  50ac885ab58956b28979d48d79d48d67c28b79d48d9cea9cffffff85de9185de919cea9c9cea9cffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c79d48d85de9185de9172cd8d%
+  9cea9c62bd8b9cea9c85de919cea9cffffff9cea9c9cea9cffffff9cea9cffffffffffff9cea9c9cea9c85de916cc78c%
+  9cea9c9cea9c79d48d72cd8d79d48dffffff85de9185de916cc78c85de9172cd8d85de9172cd8d72cd8d6cc78c6cc78c%
+  62bd8b4da98748a58656b28950ac885ab5895eb98a67c28b6cc78c9cea9c6cc78c9cea9c72cd8d9cea9c9cea9c79d48d%
+  9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9cffffff%
+  85de9185de9172cd8d85de919cea9c79d48d72cd8d72cd8d67c28b85de9179d48d85de91ffffff9cea9c9cea9c85de91%
+  ffffffffffff85de91ffffffffffffffffff62bd8b9cea9c67c28b85de91ffffff85de9167c28b79d48d72cd8d9cea9c%
+  72cd8d72cd8d5ab58979d48d5eb98a5ab5895eb98a62bd8b4da98767c28b5eb98a5ab58967c28b67c28b67c28b72cd8d%
+  85de9185de91ffffff9cea9cffffff79d48dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c%
+  ffffff85de919cea9c9cea9c9cea9c9cea9c85de9172cd8d85de9172cd8d67c28b72cd8d9cea9c9cea9c79d48d9cea9c%
+  9cea9c85de919cea9c85de91ffffff9cea9c9cea9c79d48d85de9172cd8d72cd8d85de91ffffff72cd8d85de91ffffff%
+  6cc78c72cd8d5eb98a72cd8d85de9179d48d67c28b5eb98a79d48d5ab58950ac8879d48d5ab5895ab5895eb98a53af88%
+  67c28b72cd8d72cd8d79d48d79d48d72cd8d9cea9c9cea9c85de9185de91ffffffffffffffffff9cea9cffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffff85de91ffffff85de91ffffffffffff72cd8d9cea9c67c28b72cd8d72cd8d79d48d6cc78c%
+  9cea9c6cc78cffffffffffff72cd8dffffffffffff9cea9cffffff79d48dffffffffffff9cea9c9cea9c72cd8d79d48d%
+  85de9185de919cea9c72cd8d85de9167c28b62bd8b85de9185de9172cd8d6cc78c79d48d5eb98a9cea9c5eb98a5eb98a%
+  53af885eb98a56b28953af885ab5895ab58985de9185de916cc78c79d48d85de9185de9185de9185de91ffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c72cd8dffffff62bd8b%
+  6cc78c72cd8d79d48d72cd8d79d48dffffff85de91ffffff85de919cea9cffffffffffffffffff9cea9c85de919cea9c%
+  85de9185de9185de9172cd8d79d48d85de9179d48d79d48d72cd8d56b28985de915ab58979d48d5ab5896cc78c72cd8d%
+  79d48d72cd8d6cc78c79d48d50ac8850ac8872cd8d72cd8d79d48d6cc78c67c28b5ab58979d48dffffff9cea9c9cea9c%
+  85de91ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff85de9179d48d9cea9c9cea9c85de91%
+  9cea9c72cd8d85de919cea9c9cea9c85de9179d48d9cea9c9cea9c72cd8d85de91ffffff9cea9c85de91ffffff9cea9c%
+  85de9172cd8dffffff85de9179d48d9cea9c79d48d9cea9c85de9179d48d72cd8d79d48d85de9185de9167c28b5ab589%
+  62bd8b62bd8b67c28b72cd8d67c28b72cd8d79d48d67c28b72cd8d6cc78c62bd8b5ab5895ab58967c28b56b28962bd8b%
+  6cc78c85de9185de9185de9185de9185de919cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffff%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9c9cea9c9cea9c85de919cea9c85de91ffffff9cea9c72cd8d85de919cea9c79d48d72cd8d72cd8d%
+  85de9185de9185de919cea9cffffffffffff9cea9c85de9172cd8dffffff85de919cea9c79d48d9cea9c79d48d85de91%
+  72cd8d79d48d67c28b5eb98a50ac8885de9162bd8b79d48d6cc78c72cd8d6cc78c72cd8d67c28b72cd8d62bd8b6cc78c%
+  67c28b5ab5895eb98a79d48d6cc78c6cc78c79d48d67c28bffffff85de9172cd8d9cea9c9cea9c9cea9cffffffffffff%
+  9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9cffffffffffff79d48d79d48d9cea9c79d48d85de91%
+  79d48d9cea9c9cea9c9cea9c9cea9cffffffffffffffffffffffff85de919cea9c85de919cea9cffffff72cd8d85de91%
+  79d48dffffff85de916cc78c9cea9c72cd8d79d48d5eb98a62bd8b72cd8d72cd8d5eb98a9cea9c6cc78c72cd8d85de91%
+  72cd8d79d48d67c28b67c28b9cea9c85de914aa7876cc78c85de9172cd8d79d48d79d48d85de9167c28b72cd8dffffff%
+  ffffff9cea9c9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffffffffffffffff85de9185de919cea9c%
+  9cea9c9cea9cffffff85de919cea9c9cea9c9cea9c85de91ffffff9cea9c85de9185de91ffffffffffff9cea9c85de91%
+  9cea9c85de919cea9c9cea9c9cea9c9cea9c79d48d85de9179d48d72cd8d9cea9c79d48d79d48d67c28b62bd8b72cd8d%
+  5ab58979d48d72cd8d67c28b79d48d72cd8d6cc78c72cd8d9cea9c67c28b72cd8d5ab58972cd8d85de9172cd8d5eb98a%
+  79d48d6cc78c3b9c8567c28b9cea9c9cea9c9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c%
+  9cea9c72cd8d9cea9c85de916cc78cffffffffffffffffff9cea9cffffff9cea9c85de9179d48d79d48d79d48d67c28b%
+  ffffff9cea9c9cea9cffffffffffff79d48d85de916cc78c79d48d9cea9c72cd8d79d48d6cc78c72cd8d79d48d62bd8b%
+  85de9179d48d67c28b79d48d72cd8d62bd8b79d48d85de91ffffff6cc78c5eb98a62bd8b67c28b6cc78c85de9167c28b%
+  6cc78c79d48d79d48d5ab5895eb98a6cc78c3b9c8545a28685de91ffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c79d48d9cea9c9cea9c85de919cea9c9cea9c9cea9c85de919cea9c9cea9c%
+  ffffff72cd8d62bd8b5ab58967c28b85de9172cd8d9cea9c85de91ffffff62bd8bffffff85de919cea9c79d48d6cc78c%
+  72cd8d72cd8d5eb98a5eb98a5eb98a5ab58979d48d6cc78c79d48d6cc78c5eb98a72cd8d72cd8d72cd8d85de9179d48d%
+  67c28b6cc78c67c28b72cd8d9cea9c9cea9c72cd8d67c28b48a58650ac8850ac882e938467c28bffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffff9cea9c85de91ffffff9cea9c85de91ffffffffffff85de9185de91%
+  ffffff9cea9c79d48d9cea9cffffffffffff79d48d72cd8d5ab58953af8872cd8d85de9179d48dffffffffffff72cd8d%
+  72cd8d72cd8d6cc78c72cd8d9cea9c72cd8d79d48d5eb98a6cc78c79d48d5eb98a67c28b62bd8b6cc78c85de916cc78c%
+  9cea9c85de916cc78c67c28b72cd8d6cc78c5eb98a85de916cc78c6cc78c85de9167c28b5eb98a3e9d8553af885eb98a%
+  5eb98affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff%
+  9cea9cffffff9cea9cffffffffffff9cea9cffffff9cea9cffffff79d48dffffff9cea9c79d48d67c28b6cc78cffffff%
+  9cea9c85de9179d48d9cea9c85de9179d48d9cea9c67c28b6cc78c62bd8b62bd8b56b2896cc78c5ab58953af8856b289%
+  62bd8b56b28967c28b5ab58962bd8b72cd8d67c28b79d48d67c28b72cd8d9cea9c85de91ffffffffffff72cd8d9cea9c%
+  67c28b5ab58956b2896cc78c67c28b9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c85de9185de919cea9c9cea9cffffffffffff85de91ffffff9cea9c9cea9cffffff9cea9c9cea9c85de91ffffff%
+  ffffff85de919cea9cffffff79d48dffffffffffffffffff9cea9cffffff85de919cea9c67c28b79d48d6cc78c67c28b%
+  50ac885eb98a4da9875ab58953af8856b2895ab58956b2895eb98a6cc78c72cd8d85de9179d48d79d48d9cea9c6cc78c%
+  85de91ffffff9cea9c9cea9c85de9172cd8d72cd8d6cc78c79d48d9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffff85de919cea9cffffff85de91ffffff9cea9c9cea9cffffff%
+  9cea9cffffff9cea9c9cea9c9cea9c79d48d79d48d85de919cea9c85de9185de9179d48d72cd8d9cea9c79d48d72cd8d%
+  79d48d72cd8d62bd8b5eb98a50ac8848a58656b2895ab58945a28650ac883b9c8543a18637998548a5865ab58962bd8b%
+  79d48d72cd8d85de916cc78c72cd8d85de9172cd8d79d48dffffffffffffffffff85de91ffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c%
+  85de919cea9c9cea9c67c28b9cea9c85de91ffffff85de91ffffffffffffffffff85de91ffffff9cea9c9cea9c85de91%
+  85de91ffffff9cea9c62bd8b67c28b6cc78c62bd8b6cc78c6cc78c5ab5894da98745a2864da98743a1863195843b9c85%
+  359884399a8550ac8867c28b62bd8b67c28b6cc78c9cea9c9cea9c9cea9c85de919cea9c9cea9c9cea9c85de919cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff9cea9c%
+  ffffffffffff9cea9cffffff9cea9cffffffffffff9cea9cffffff85de919cea9c9cea9cffffffffffff9cea9cffffff%
+  85de919cea9cffffff9cea9c79d48d67c28b85de9185de9179d48d9cea9c72cd8d62bd8b53af885ab5895eb98a5ab589%
+  48a58643a1863195844aa78748a586409f864da98745a2865ab58956b28979d48d85de9185de919cea9cffffff9cea9c%
+  85de919cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c79d48d9cea9c9cea9c85de91ffffff85de91ffffff9cea9cffffff%
+  9cea9c9cea9c9cea9cffffffffffffffffffffffffffffff9cea9c9cea9c85de916cc78c67c28b5eb98a67c28b72cd8d%
+  62bd8b6cc78c5eb98a50ac8845a286409f863e9d853598843b9c8537998535988443a18653af8872cd8d79d48d62bd8b%
+  85de9172cd8d85de91ffffff9cea9c85de91ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff9cea9c9cea9c%
+  9cea9c9cea9c85de91ffffffffffff85de91ffffffffffffffffffffffff9cea9c79d48d85de9179d48d9cea9cffffff%
+  9cea9c9cea9c5ab58972cd8d6cc78c50ac8862bd8b4aa787409f863799854da987339684409f863b9c853598843e9d85%
+  45a28656b28967c28b79d48d6cc78c72cd8d85de9162bd8bffffffffffff9cea9cffffffffffff9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffff9cea9c85de91ffffff85de9185de9185de91ffffff6cc78c9cea9cffffffffffffffffff9cea9c9cea9c79d48d%
+  9cea9cffffff85de9179d48d72cd8dffffff67c28b6cc78c62bd8b5eb98a53af8867c28b399a8550ac883396844aa787%
+  379985409f8635988437998537998556b2895ab58972cd8d79d48d85de9185de919cea9c9cea9c9cea9cffffff9cea9c%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff85de91ffffff9cea9c85de9172cd8d85de9185de919cea9cffffffffffff%
+  9cea9cffffffffffffffffffffffff85de919cea9c9cea9c79d48d72cd8d62bd8b6cc78c72cd8d6cc78c62bd8b3e9d85%
+  56b289409f863b9c853b9c8545a2862f9484299083399a8550ac88399a8550ac885eb98a5eb98a67c28b6cc78c85de91%
+  72cd8d72cd8d85de919cea9c9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c85de9185de916cc78c%
+  67c28b85de9185de9185de91ffffffffffff9cea9c85de91ffffff79d48d9cea9c9cea9c85de9185de916cc78c85de91%
+  85de9179d48d62bd8b5eb98a4da98753af884da98748a5863195844aa7873e9d85399a853b9c85409f865eb98a62bd8b%
+  5eb98a62bd8b5ab58967c28bffffff85de9185de91ffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c62bd8b85de9185de9185de919cea9c85de91ffffffffffffffffff85de919cea9c79d48d%
+  9cea9c85de916cc78c79d48d72cd8d5eb98a62bd8b5ab58962bd8b67c28b4aa78748a58648a586409f863e9d85379985%
+  3e9d8535988453af885eb98a5ab5895eb98a85de919cea9c79d48d85de9185de9185de91ffffff9cea9c9cea9cffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c85de9185de9185de919cea9c85de9172cd8d62bd8b6cc78c72cd8dffffffffffff9cea9c%
+  ffffffffffffffffff85de91ffffff72cd8d79d48dffffff9cea9c5eb98a6cc78c5eb98a6cc78c62bd8b4da987399a85%
+  4aa78743a1863e9d8543a18653af8848a5864da98767c28b6cc78c5eb98a9cea9c85de919cea9c9cea9c85de9172cd8d%
+  ffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffffffffff85de919cea9c79d48d79d48d9cea9c9cea9c79d48d6cc78c9cea9c72cd8d%
+  9cea9c9cea9c9cea9cffffffffffffffffff85de9185de9172cd8dffffffffffff85de919cea9c85de9167c28b72cd8d%
+  6cc78c56b2894da98753af883e9d8535988450ac8848a58648a58648a58650ac885eb98a72cd8d6cc78c5ab5895eb98a%
+  9cea9c79d48d9cea9c85de919cea9cffffffffffffffffffffffff79d48dffffff9cea9c9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c85de9179d48d72cd8d6cc78c%
+  72cd8d85de9179d48d9cea9c85de9185de91ffffffffffffffffff85de91ffffff85de919cea9cffffff9cea9c79d48d%
+  6cc78c79d48d72cd8d85de9167c28b62bd8b56b2895eb98a50ac883b9c8553af8845a2863e9d85399a8556b28953af88%
+  5eb98a6cc78c85de915eb98a45a2865eb98a9cea9c85de9185de919cea9c85de91ffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c85de91ffffffffffffffffff%
+  79d48dffffff62bd8b6cc78c79d48d85de9185de919cea9c9cea9c9cea9c9cea9cffffff9cea9c9cea9c85de919cea9c%
+  85de919cea9c79d48dffffff79d48d9cea9c9cea9c67c28b5ab58972cd8d62bd8b79d48d50ac8843a1864aa7874aa787%
+  3799854aa7874da9874da9874aa7876cc78c6cc78c4da987339684399a8579d48d85de919cea9cffffffffffff85de91%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff79d48dffffff9cea9c9cea9c79d48d79d48d72cd8dffffff85de919cea9cffffff79d48d9cea9c9cea9c67c28b%
+  62bd8b67c28b79d48d9cea9c85de9179d48d9cea9c9cea9c9cea9c9cea9c9cea9cffffff9cea9c79d48dffffff85de91%
+  67c28b72cd8d5eb98a56b28953af8850ac88409f8648a5865ab58950ac8872cd8d53af883e9d851e878231958479d48d%
+  ffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffff85de91ffffff79d48d9cea9c79d48d9cea9c85de919cea9c79d48d79d48d%
+  ffffff79d48dffffff56b28962bd8b45a28667c28b67c28b72cd8d85de919cea9c9cea9c6cc78c72cd8d85de9179d48d%
+  72cd8d79d48d85de9172cd8d6cc78c72cd8d62bd8b6cc78c79d48d5eb98a4da98753af88399a8553af885ab58967c28b%
+  53af88409f86268e8356b2899cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c72cd8d9cea9c9cea9c9cea9c%
+  85de91ffffff9cea9c9cea9cffffff9cea9c9cea9c9cea9c85de915eb98a67c28b85de9185de919cea9c85de919cea9c%
+  ffffff9cea9c72cd8d9cea9c79d48d85de9172cd8d79d48d6cc78c67c28b67c28b53af886cc78c5ab5895ab5895ab589%
+  50ac8850ac8850ac8867c28b85de9156b28950ac8867c28b85de919cea9cffffffffffffffffffffffffffffff9cea9c%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  72cd8dffffff9cea9cffffff85de919cea9cffffffffffff9cea9c9cea9cffffff85de916cc78c79d48d85de9185de91%
+  ffffff85de919cea9c9cea9cffffffffffff79d48dffffff72cd8d79d48d85de919cea9c85de9179d48d79d48d79d48d%
+  50ac8850ac8862bd8b67c28b67c28b3e9d855eb98a62bd8b5ab58972cd8d79d48d72cd8d79d48d9cea9cffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c9cea9cffffff85de91ffffffffffffffffff9cea9c%
+  9cea9c85de9185de9185de919cea9c9cea9cffffffffffff85de9172cd8d9cea9c9cea9c9cea9c79d48d67c28b56b289%
+  85de9179d48d85de9172cd8d79d48d79d48d6cc78c5eb98a67c28b5eb98a62bd8b72cd8d62bd8b72cd8d9cea9c79d48d%
+  79d48d85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffff85de919cea9c85de919cea9cffffffffffff85de91ffffff85de919cea9c72cd8d85de91%
+  79d48d79d48d62bd8b6cc78c85de9185de91ffffff67c28b85de9167c28b6cc78c56b2895ab58967c28b9cea9c6cc78c%
+  72cd8d79d48d67c28b9cea9c9cea9cffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff79d48dffffff9cea9cffffff9cea9cffffff79d48d9cea9c85de9185de919cea9c85de91ffffff%
+  85de919cea9c79d48d79d48d79d48d85de9179d48d72cd8d72cd8d79d48d5eb98a5eb98a67c28b62bd8b72cd8d72cd8d%
+  62bd8b67c28b6cc78c9cea9c9cea9c85de9172cd8d9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c85de919cea9c9cea9cffffffffffff9cea9c9cea9c%
+  6cc78c9cea9cffffff9cea9cffffff85de919cea9c9cea9c85de916cc78c9cea9c79d48d72cd8d72cd8d62bd8b85de91%
+  72cd8d9cea9c67c28b5ab58967c28b6cc78c6cc78c5ab5896cc78c9cea9c9cea9c9cea9c9cea9cffffffffffffffffff%
+  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffff%
+  85de919cea9cffffff79d48d72cd8d9cea9c6cc78c85de919cea9c85de9185de9172cd8d79d48d79d48d85de919cea9c%
+  72cd8d85de9185de9185de919cea9c9cea9c85de9179d48d72cd8d79d48d67c28b6cc78cffffff85de9185de919cea9c%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
+  ffffff9cea9c9cea9c79d48d85de916cc78c85de9179d48d72cd8d9cea9c79d48d72cd8d9cea9c79d48d85de919cea9c%
+  85de9172cd8d85de915ab58972cd8d72cd8d79d48d6cc78c79d48d9cea9c9cea9c67c28b72cd8d72cd8d67c28b62bd8b%
+  85de9172cd8dffffff9cea9c9cea9c9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff85de9185de919cea9c85de9172cd8d62bd8b5eb98a67c28b85de91ffffff72cd8d6cc78c%
+  85de919cea9cffffffffffffffffff6cc78c67c28b67c28b79d48d72cd8d9cea9c6cc78c85de916cc78cffffff85de91%
+  62bd8b9cea9c85de9172cd8d9cea9c9cea9c9cea9c79d48d9cea9c9cea9c9cea9c9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d79d48d62bd8b72cd8d5eb98a48a586%
+  85de919cea9c85de91ffffff79d48d9cea9c9cea9c79d48d72cd8d85de9185de9167c28b62bd8b67c28b72cd8d4aa787%
+  6cc78c6cc78c9cea9c6cc78c6cc78c9cea9c79d48d9cea9c85de919cea9cffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff85de91ffffff%
+  79d48dffffff5eb98a62bd8b67c28b72cd8d6cc78c85de916cc78c85de919cea9c79d48d72cd8d72cd8d79d48d6cc78c%
+  72cd8d4da9875eb98a4aa7874da9875eb98a53af885ab5896cc78c72cd8d67c28b85de91ffffff85de91ffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c9cea9c9cea9c72cd8d72cd8dffffff72cd8d6cc78c67c28b72cd8d79d48d79d48d79d48dffffffffffffffffff%
+  6cc78c79d48d6cc78c67c28b4aa78753af8850ac8845a2863b9c854aa78756b2893e9d8562bd8b6cc78cffffff72cd8d%
+  72cd8d9cea9c9cea9c9cea9cffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffff9cea9c9cea9c9cea9c9cea9c9cea9c67c28b85de9179d48d79d48dffffff9cea9c79d48d%
+  79d48d79d48d72cd8d5eb98a67c28b79d48d72cd8d79d48d3b9c8556b2892c928345a2862c92834da987399a85359884%
+  48a58645a28672cd8d6cc78c79d48d85de91ffffff9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d79d48d85de9185de91%
+  85de919cea9c85de9172cd8d9cea9c6cc78c9cea9c79d48d62bd8b72cd8d5ab5895ab58962bd8b4aa7874aa7872e9384%
+  3799852e938448a58637998545a28662bd8b5eb98a72cd8d9cea9cffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9cffffff9cea9cffffffffffff9cea9c79d48d%
+  ffffff9cea9c72cd8d9cea9c79d48d9cea9c6cc78c85de9179d48d85de9172cd8d6cc78c67c28b62bd8b85de9185de91%
+  4da98756b28943a1863b9c853e9d852c9283268e832c928348a58653af8856b28950ac8885de919cea9c9cea9c9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9cffffff9cea9cffffff9cea9cffffffffffff9cea9c79d48d72cd8d56b28948a586399a8562bd8b62bd8b67c28b%
+  5ab5895eb98a5eb98a5eb98a5eb98a5ab5895ab58943a1862f9484359884299083278f832f948435988456b28972cd8d%
+  72cd8d72cd8d72cd8d9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c79d48d67c28b4aa787%
+  319584409f864da98767c28b62bd8b56b28962bd8b50ac884da98767c28b45a28656b289399a853b9c85208a82268e83%
+  3396843b9c85399a8550ac8853af886cc78c62bd8b85de91ffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de9179d48d85de91ffffff79d48d9cea9c%
+  79d48d72cd8d67c28b5ab58962bd8b72cd8d56b28962bd8b4da9875ab58962bd8b5ab5894da9874da98745a28656b289%
+  3396843598842c9283248d833598843396842c92833396843e9d8553af8879d48d62bd8b85de919cea9cffffffffffff%
+  9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91%
+  79d48d6cc78c9cea9cffffff6cc78c72cd8d5eb98a5eb98a50ac8862bd8b5ab58962bd8b5eb98a67c28b67c28b43a186%
+  4aa7875eb98a3b9c8545a28643a18643a1863e9d852e9384379985409f863396842e9384268e8353af8856b2895ab589%
+  6cc78cffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c%
+  85de91ffffffffffffffffff79d48d85de919cea9c9cea9c9cea9c5ab58972cd8d79d48d85de915eb98a53af885eb98a%
+  62bd8b62bd8b62bd8b53af8862bd8b56b28972cd8d4aa78753af8843a1863e9d8548a5862990833b9c853195842a9183%
+  1e82822f948450ac8872cd8d79d48d85de91ffffff79d48dffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9cffffff85de919cea9c79d48d9cea9c67c28b6cc78c72cd8d6cc78c62bd8b67c28b85de91%
+  79d48d5ab58950ac8856b28972cd8d53af8872cd8d6cc78c67c28b53af885ab58962bd8b50ac884da9873e9d8545a286%
+  2a9183319584409f8645a2862e9384409f86409f8656b28979d48d79d48dffffff9cea9cffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffff79d48dffffff62bd8b6cc78c72cd8d72cd8d%
+  72cd8d62bd8b6cc78c6cc78c62bd8b5eb98a53af885eb98a79d48d4da9876cc78c53af88409f8653af885eb98a53af88%
+  45a28653af8843a186399a853e9d852f9484399a85409f86409f8645a2865ab58972cd8d79d48d67c28bffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff79d48d6cc78c9cea9c79d48d%
+  6cc78c62bd8b79d48d6cc78c5eb98a67c28b79d48d6cc78c67c28b62bd8b56b28956b28962bd8b53af8843a18656b289%
+  5ab5895eb98a48a5863b9c8545a28648a586399a8543a186379985409f86248d8343a186409f8650ac8853af8872cd8d%
+  85de919cea9c85de91ffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
+  9cea9c9cea9c9cea9c85de91ffffff9cea9c6cc78c79d48d72cd8d79d48d67c28b6cc78c67c28b6cc78c62bd8b56b289%
+  6cc78c6cc78c6cc78c4da98753af8850ac884aa78735988450ac88409f863e9d8550ac884da98745a2863b9c8553af88%
+  5eb98a9cea9c9cea9cffffff9cea9c85de91ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff85de91ffffff9cea9c9cea9c9cea9cffffff6cc78c67c28b5ab58979d48d72cd8d62bd8b5ab589%
+  5eb98a79d48d67c28b5eb98a5eb98a5ab58953af884da98756b2893e9d8543a1863396843e9d852e93843e9d855ab589%
+  48a58648a5864aa78767c28b79d48d62bd8b72cd8dffffffffffff85de919cea9cffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c79d48dffffff67c28b5eb98a4da987%
+  48a58648a5864da987409f8645a28667c28b6cc78c72cd8d5ab58967c28b53af8850ac884da98750ac88399a8543a186%
+  3e9d854aa78753af885eb98a62bd8b62bd8b72cd8d67c28b6cc78c85de919cea9c79d48dffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c%
+  ffffff79d48d85de9172cd8d5eb98a79d48d56b28950ac88409f863e9d8579d48d62bd8b9cea9c72cd8d6cc78c79d48d%
+  5ab58962bd8b5ab58956b2896cc78c79d48d6cc78c79d48d85de919cea9c9cea9c79d48d79d48dffffff9cea9c9cea9c%
+  9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffff9cea9c9cea9c79d48d5ab58979d48d62bd8b45a286339684278f8350ac88%
+  62bd8b5eb98a85de919cea9c6cc78c9cea9c85de9185de919cea9c9cea9c85de91ffffffffffffffffffffffff9cea9c%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
+  9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffff9cea9c9cea9c9cea9cffffffffffffffffffffffff%
+  ffffffffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff85de919cea9cffffff9cea9c9cea9c85de91%
+  9cea9cffffff9cea9c9cea9c85de9179d48d79d48d62bd8bffffff72cd8d9cea9cffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c72cd8d9cea9c%
+  ffffffffffff9cea9c85de9185de91ffffff9cea9c85de9179d48d6cc78c62bd8b5ab5895eb98a6cc78c72cd8d9cea9c%
+  ffffff85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  9cea9c72cd8d62bd8b5ab58967c28b72cd8d67c28b67c28b45a28656b289409f862f9484268e831f80821f7d821f7681%
+  1e82821f7f822a918345a28656b28972cd8dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffff85de9172cd8d5eb98a56b2893e9d8543a1862f94842a91832a91833598841f7f82%
+  1e87821f7c82206e81206f81206b812071811f7381228b8256b28979d48d9cea9c85de91ffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffff9cea9c85de9179d48d72cd8d79d48d5eb98a53af88409f86238c832e93841e8882%
+  248d831e82821f7a821f7b821f75811f7e82207181207181216881235f81216781206c81278f8348a5864da98772cd8d%
+  9cea9cffffff9cea9c9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9c85de915eb98a72cd8d62bd8b%
+  2f9484268e831f81821f76811f78811f7c821e87821f7a821f7e821f76811f78811f78811f78811f76811f7f821e8882%
+  5eb98a72cd8d85de919cea9c9cea9cffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
+  9cea9c9cea9c85de9179d48d45a28650ac8850ac8837998545a2864da98745a28648a58653af8850ac8867c28b62bd8b%
+  50ac8879d48d85de91ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
+  ffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
+  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff000080%
+  233581243981264181274d812557811e868256b28967c28b85de91ffffffffffffffffffffffffffffffffffffffffff%
   ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%

### 2016-04-20 paper/paper.tex
More page layout changes

@@
     \caption{On top, the cumulative number of MCCS instances solved in under a certain time using
-        different CP techniques. Below, instance-by-instance comparisons.}
+        different CP techniques, for 33\% labelled (left) and unlabelled undirected (right) graphs.
+    Below, instance-by-instance comparisons.}
         \label{figure:connected-cp}
@@
 \Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
-branching (Branch), by filtering (Filter), or by combining branching and
-filtering (Both). We show only results using the best variant for each class---that is, MAC for
-labelled graphs, and FC for unlabelled graphs (the other results are very similar).  On labelled
-graphs, we see many instances which are solved by branching but not filtering, and vice versa.
-However, combining both is rarely much worse than just doing one or the other, and is often much
-better, even if on average it is slightly slower.  On unlabelled graphs, we observe that the three
-variants have rather similar performance.
+branching (Branch), by filtering (Filter), or by combining branching and filtering (Both). We show
+only results using the best variant for each class---that is, MAC for labelled graphs, and FC for
+unlabelled graphs (the other results are very similar).  On labelled graphs, we see many instances
+which are solved very quickly by branching but not at all by filtering, and vice versa.  However,
+combining both is rarely much worse than just doing one or the other, and is often much better, even
+if on average it is slightly slower.
+
+On unlabelled graphs, we observe that the three variants have rather similar performance.
 

### 2016-04-20 paper/paper.tex
Use the colours everywhere

@@
 \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
-\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
-\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
-\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
+\definecolor{chromayellow}{rgb}{1.0, 1.0, 0.878431}
+\definecolor{chromagreen}{rgb}{0.564706, 0.933333, 0.564706}
+\definecolor{chromateal}{rgb}{0, 0.501961, 0.501961}
+\definecolor{chromanavy}{rgb}{0, 0, 0.501961}
 
@@
         \begin{scope}[rotate=90]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
 
@@
         \begin{scope}[xshift=7cm, rotate=90]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
 
@@
         \begin{scope}[xshift=18cm, rotate=90]
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
@@
         \begin{scope}[xshift=25cm, rotate=90]
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
@@
         \begin{scope}[xshift=12.8cm]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
@@
         \begin{scope}[xshift=25.6cm]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
@@
         \begin{scope}[yshift=-9cm]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
-            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
             \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
-            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};
@@
         \begin{scope}[xshift=12.8cm, yshift=-9cm]
-            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
-            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
-            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
@@
             \begin{tikzpicture}[scale=0.33]
-                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
-                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
-                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
-                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (3, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf5) at (3, 0) {\phantom{0}};
 
@@
             \begin{tikzpicture}[scale=0.33]
-                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 2) {\phantom{0}};
-                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 2) {\phantom{0}};
-                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
-                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (3, 0) {\phantom{0}};
-                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (6, 0) {\phantom{0}};
-                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc3) at (3, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md2) at (6, 0) {\phantom{0}};
+                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 0) {\phantom{0}};
 
@@
             \begin{tikzpicture}[scale=0.33]
-                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (9, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (12, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (15, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (18, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (21, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (24, 0) {\phantom{0}};
-                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (27, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf5) at (9, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb2) at (12, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb3) at (15, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc2) at (18, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc3) at (21, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md2) at (24, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md3) at (27, 0) {\phantom{0}};
 

### 2016-04-20 paper/paper.tex
Re-add some references

@@
 maximum clique problem. Both approaches are described for undirected, unlabelled graphs without
-loops; their extension to richer graphs is discussed in \cref{extension}.
+loops; their extension to richer graphs is discussed in \cref{extension}.  (Other approaches have
+been tried, mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
+\cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
+\cite{UpcomingIJCAIPaper}.)
 
@@
 
-In many applications, the common subgraph must be connected. As illustrated in
+In many applications, the common subgraph must be connected
+\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
+Adding the connectedness requirement makes certain special cases solvable in polynomial time,
+including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
+\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
 \cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness

### 2016-04-20 paper/paper.tex
See if we can fit the association graph figure in

@@
 v'$, and if they preserve both edges and non-edges, so $(u, v) \in \operatorname{E}(G) \Leftrightarrow
-(u', v') \in \operatorname{E}(H)$.
+(u', v') \in \operatorname{E}(H)$. We illustrate this in \cref{figure:association}.
+
+\begin{figure}[tb]
+    \centering
+    \begin{tikzpicture}[scale=0.33]%{{{
+        \begin{scope}
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 10) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 8) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 8) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 8) {\phantom{0}};
+
+            \node [right = 0 of Ma, font=\small] { \vphantom{0}a };
+            \node [below = 0 of Mb, font=\small] { \vphantom{0}b };
+            \node [below = 0 of Mc, font=\small] { \vphantom{0}c };
+            \node [below = 0 of Md, font=\small] { \vphantom{0}d };
+
+            \draw [very thick] (Mb) -- (Mc);
+            \draw [very thick] (Mc) -- (Md);
+            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!40] (Ma) to [out=150, in=80, looseness=8] (Ma);
+            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
+        \end{scope}
+
+        \begin{scope}
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
+
+            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };
+
+            \draw [very thick] (M1) -- (M2);
+            \draw [very thick] (M2) -- (M4);
+            \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \draw [color=uofgsandstone!40] (M1) -- (M3);
+
+            \draw [color=uofgsandstone!40] (M3) to [out=280, in=210, looseness=8] (M3);
+            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
+        \end{scope}
+
+        \begin{scope}[xshift=15cm]
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
+            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
+            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
+            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
+            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Ma1.north west) -- (Ma4.north east)
+            node [midway, above=0.7cm] { $a \mapsto$ };
+
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
+            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
+            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
+            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mb1.south west) -- (Mb4.north west)
+            node [midway, left=0.7cm] { $b \mapsto$ };
+
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
+            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
+            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
+            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
+            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mc4.south east) -- (Mc1.south west)
+            node [midway, below=0.7cm] { $c \mapsto$ };
+
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
+            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
+            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };
+
+            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
+            node [midway, right=0.7cm] { $d \mapsto$ };
+
+            \begin{scope}[on background layer]
+                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
+                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
+                \draw [draw=uofgsandstone!40] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
+                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
+                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
+                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
+                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
+        \end{scope}
+        \end{scope}
+
+    \end{tikzpicture}
+
+    \caption{A maximum common induced subgraph between the two graphs on the left has three
+        vertices---one solution is highlighted. On the right, the association graph encoding: the
+        highlighted clique of size three shows the same solution. In practice the isolated vertices
+        (representing assignments between incompatible vertices) would be omitted.}\label{figure:association}
+\end{figure}
 
@@
 
-?? Can we figure out why? Is it time-to-find or time-to-prove? Assume that this will take up a few
-sentences of space.
-
 \section{Conclusion}

### 2016-04-20 paper/paper.tex
Find or prove?
Slightly smaller picture

@@
         \begin{scope}
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 10) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 8) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 8) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};
 
@@
 
-        \begin{scope}[xshift=15cm]
+        \begin{scope}[xshift=15cm, yshift=-1cm]
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
@@
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
-            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
-            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
-            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
-            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Ma1.north west) -- (Ma4.north east)
-            node [midway, above=0.7cm] { $a \mapsto$ };
+            \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
+            \node (La2) [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
+            \node (La3) [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
+            \node (La4) [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
+
+            \node [left=0 of La1] { $a \mapsto \{$ };
+            \node [right=0 of La4] { $\}$ };
 
@@
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
-            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
-            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
-            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
-            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
-
-            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mc4.south east) -- (Mc1.south west)
-            node [midway, below=0.7cm] { $c \mapsto$ };
+            \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
+            \node (Lc2) [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
+            \node (Lc3) [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
+            \node (Lc4) [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
+
+            \node [left=0 of Lc1] { $c \mapsto \{$ };
+            \node [right=0 of Lc4] { $\}$ };
 
@@
             \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
-            node [midway, right=0.7cm] { $d \mapsto$ };
+            node [midway, right=0.7cm] { $\reflectbox{\ensuremath{\mapsto}} d$ };
 
@@
 
+?? Time to find or time to prove? Can we figure this out?
+
 \section{Conclusion}

### 2016-04-20 paper/paper.tex
No need to special-case loops

@@
 $\operatorname{E}(G) \subseteq \operatorname{V}(G) \times \operatorname{V}(G)$, where $(u, v) \in
-\operatorname{E}(G) \Rightarrow (v, u) \in \operatorname{E}(G) \wedge u \ne v$. The neighbourhood of
+\operatorname{E}(G) \Rightarrow (v, u) \in \operatorname{E}(G)$. The neighbourhood of
 a vertex $v$, written $\operatorname{N}(G, v)$, is the set of vertices to which it is adjacent.
@@
 and each pair of successive vertices is connected by an edge, i.e.\ $\forall i\in \{1 \ldots k \},
-(v_{i-1}, v_i) \in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every pair of vertices
-is connected by a path.
+(v_{i-1}, v_i) \in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every non-adjacent pair
+of vertices is connected by a path.
 
@@
 on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
-maximum clique problem. Both approaches are described for undirected, unlabelled graphs without
-loops; their extension to richer graphs is discussed in \cref{extension}.  (Other approaches have
-been tried, mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
+maximum clique problem. Both approaches are described for undirected, unlabelled graphs; their
+extension to richer graphs is discussed in \cref{extension}.  (Other approaches have been tried,
+mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
 \cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
@@
 
-\subsection{Extension to Labelled or Directed Graphs, and Loops}\label{extension}
+\subsection{Extension to Labelled or Directed Graphs}\label{extension}
 
@@
 is similarly straightforward.
-Finally, some datasets contain loops (self-adjacent vertices). In this case vertices with loops must
-be mapped to vertices with loops (with the same labels, if appropriate), and vertices without loops
-must be mapped to vertices without loops.
-
-Labels, directed edges and loops usually simplify the solution process, both for CP and clique-based
+
+Labels and directed edges usually simplify the solution process, both for CP and clique-based
 approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in the

### 2016-04-20 paper/paper.tex
Meaningful colours

@@
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};
 
@@
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
 
@@
 
-            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
@@
             \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
-            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
             \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };

### 2016-04-20 paper/paper.tex
Spacing

@@
             \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
-            node [midway, right=0.7cm] { $\reflectbox{\ensuremath{\mapsto}} d$ };
+            node [midway, right=0.7cm] { $\reflectbox{\ensuremath{\mapsto}}\, d$ };
 

### 2016-04-20 paper/paper.tex
Teal isn't my favourite colour

@@
         \begin{scope}[xshift=18cm, rotate=90]
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
@@
         \begin{scope}[xshift=25cm, rotate=90]
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};

### 2016-04-20 paper/paper.tex
Slightly more text, for page balance

@@
 \cite{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}. We illustrate two
-variants of this problem in \cref{figure:mcsexample}.
+variants of this problem in \cref{figure:mcsexample}---in both cases we are finding an induced
+subgraph and maximising the number of vertices selected, but in the second variant the common
+subgraph must be connected.
 

### 2016-04-20 paper/paper.tex
Initial initial

@@
 $\operatorname{min}(\left|\operatorname{V}(G_1)\right|, \left|\operatorname{V}(G_2)\right|)$
-colours, but with certain initial vertex orderings, a greedy sequential colouring will sometimes use
+colours, but with certain vertex orderings, a greedy sequential colouring will sometimes use
 many more colours).

### 2016-04-20 paper/paper.tex
Kerning

@@
     using the procedure of San Segundo et al.\ \cite{DBLP:journals/cor/SegundoRJ11} with a static
-    degree order from $G$ and $k_{min} = 0$. \;
+    degree order from $G$ and $k_{\mathit{min}} = 0$. \;
 }
@@
 algorithm introduced by San Segundo \textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}, with the
-$k_{min}$ parameter set to $0$, so we do not present it here. We use a simple static degree
+$k_{\mathit{min}}$ parameter set to $0$, so we do not present it here. We use a simple static degree
 ordering; other initial vertex orderings have been considered on general clique problems

### 2016-04-20 paper/paper.tex
Parens

@@
 and $H$ is a graph isomorphic to subgraphs of $G$ and $H$. A \emph{common connected subgraph} is a
-common subgraph which is connected.  A \emph{Maximum Common Subgraph} (MCS) (resp. \emph{Maximum
-Common Connected Subgraph} (MCCS) is a common subgraph (resp.\ common connected subgraph) which has
+common subgraph which is connected.  A \emph{Maximum Common Subgraph}, or MCS (resp. \emph{Maximum
+Common Connected Subgraph}, or MCCS) is a common subgraph (resp.\ common connected subgraph) which has
 a maximum number of vertices.

### 2016-04-20 paper/paper.tex
Compare to other works

@@
 \newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\newcommand{\christine}[1]{{\color{green} Christine:#1}}
 
@@
 In \cref{existing}, we review existing approaches for solving the MCS problem, with a specific focus
-on Constraint Programming (CP)-based approaches, and on approaches that reduce the problem to
-finding a maximum clique in an association graph.
-
-Conventional wisdom is that clique-based approaches are less effective in practice, but previous
-experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
-algorithms.  Therefore, in \cref{eval1}, we  re-evaluate the clique-based approach using a modern
-algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive with CP
-on unlabelled graphs.
+on Constraint Programming (CP)-based techniques, and on reductions of the problem to finding a
+maximum clique in an association graph.
+
+Previous experimental evaluations have used weak maximum clique algorithms, or even enumeration
+algorithms---for example, Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} compare a modified form
+of the Bron-Kerbosch maximal clique enumeration algorithm \cite{Bron:1973:AFC:362342.362367} with a
+CP optimisation approach. Our experience suggests that the optimisation form of the clique problem
+is often many orders of magnitude easier than enumeration, due to the possibility of employing a
+strong bound function to prune the search space.  Therefore, in \cref{eval1}, we  re-evaluate the
+clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled
+graphs, and that it is competitive with CP on unlabelled graphs.
 
@@
 
-\christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}
-
 It is not possible to determine connectedness from a raw association graph. However, we can take a
-maximum clique algorithm and mimic the CP branching strategy if we have access to the underlying graphs
-and can determine the ``meaning'' of the association graph vertices.
+maximum clique algorithm and mimic the CP branching strategy if we have access to the underlying
+graphs and can determine the ``meaning'' of the association graph vertices.
 
@@
 implementation details on how to use bitsets and other data structures to implement the colouring
-stage with very low constant factors).
+stage with very low constant factors). The approach we describe here differs considerably from that
+of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery \cite{DBLP:conf/mco/VismaraV08}:
+these earlier approaches worked by classifying labels in the association graph based upon whether a
+common vertex is shared, and then constructing cliques with particular edge properties---this is
+harder to integrate with a strong bound function.
 

### 2016-04-20 paper/paper.tex
Loops aren't special

@@
 
-We introduce definitions and algorithms on undirected and unlabelled graphs without loops; the
+We introduce definitions and algorithms on undirected and unlabelled graphs; the
 extension to general graphs is straightforward and is discussed in \cref{extension}. An undirected

### 2016-04-20 paper/paper.tex
Word
Unword

@@
 \Leftrightarrow (f(u),f(v)) \in \operatorname{E}(H)$.  A \emph{common subgraph} of two graphs $G$
-and $H$ is a graph isomorphic to subgraphs of $G$ and $H$. A \emph{common connected subgraph} is a
+and $H$ is a graph isomorphic to subgraphs of both $G$ and $H$. A \emph{common connected subgraph} is a
 common subgraph which is connected.  A \emph{Maximum Common Subgraph}, or MCS (resp. \emph{Maximum
@@
 branching and bounding rule used by modern clique algorithms to maintain connectedness during
-search.  We compare the clique-based approach with the best CP variant for the MCCS, and we show
+search.  We compare the clique-based approach with the best CP variant for MCCS, and we show
 that it outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.

### 2016-04-20 paper/paper.tex
Consistency
A bit darker, for printing

@@
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
-            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
@@
             \draw [very thick] (M3) -- (M5);
-            \draw [color=uofgsandstone!40] (M4) -- (M6);
-            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [color=uofgsandstone!60] (M4) -- (M6);
+            \draw [color=uofgsandstone!60] (M5) -- (M6);
             \draw [very thick] (M3) -- (M1);
-            \draw [color=uofgsandstone!40] (M6) -- (M7);
-            \draw [color=uofgsandstone!40] (M6) -- (M8);
-            \draw [color=uofgsandstone!40] (M6) -- (M9);
+            \draw [color=uofgsandstone!60] (M6) -- (M7);
+            \draw [color=uofgsandstone!60] (M6) -- (M8);
+            \draw [color=uofgsandstone!60] (M6) -- (M9);
             \draw [very thick] (M7) -- (M9);
@@
             \draw [very thick] (M3) -- (M5);
-            \draw [color=uofgsandstone!40] (M4) -- (M6);
-            \draw [color=uofgsandstone!40] (M5) -- (M6);
+            \draw [color=uofgsandstone!60] (M4) -- (M6);
+            \draw [color=uofgsandstone!60] (M5) -- (M6);
             \draw [very thick] (M3) -- (M1);
-            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [color=uofgsandstone!60] (M6) -- (M7);
             \draw [very thick] (M7) -- (M8);
@@
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
 
@@
             \draw [very thick] (M3) -- (M1);
-            \draw [color=uofgsandstone!40] (M6) -- (M7);
+            \draw [color=uofgsandstone!60] (M6) -- (M7);
             \draw [very thick] (M6) -- (M8);
-            \draw [color=uofgsandstone!40] (M6) -- (M9);
-            \draw [color=uofgsandstone!40] (M7) -- (M9);
-            \draw [color=uofgsandstone!40] (M8) -- (M9);
+            \draw [color=uofgsandstone!60] (M6) -- (M9);
+            \draw [color=uofgsandstone!60] (M7) -- (M9);
+            \draw [color=uofgsandstone!60] (M8) -- (M9);
         \end{scope}
@@
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
 
@@
             \draw [very thick] (M6) -- (M7);
-            \draw [draw=uofgsandstone!40] (M7) -- (M8);
-            \draw [draw=uofgsandstone!40] (M8) -- (M9);
+            \draw [draw=uofgsandstone!60] (M7) -- (M8);
+            \draw [draw=uofgsandstone!60] (M8) -- (M9);
         \end{scope}
@@
 different when they are not assigned to $\bot$. They find that the combination ``MAC+Bound'' (resp.
-``FC+Bound'') obtains the best results on labelled (resp. non labelled) graphs and outperforms the
+``FC+Bound'') obtains the best results on labelled (resp. unlabelled) graphs and outperforms the
 two previous approaches. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of
@@
         \begin{scope}
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
@@
             \draw [very thick] (Mc) -- (Md);
-            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [color=uofgsandstone!40] (Ma) to [out=150, in=80, looseness=8] (Ma);
+            \draw [color=uofgsandstone!60] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!60] (Ma) to [out=150, in=80, looseness=8] (Ma);
             \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
@@
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};
@@
             \draw [very thick] (M2) -- (M4);
-            \draw [color=uofgsandstone!40] (M3) -- (M4);
-            \draw [color=uofgsandstone!40] (M1) -- (M3);
-
-            \draw [color=uofgsandstone!40] (M3) to [out=280, in=210, looseness=8] (M3);
+            \draw [color=uofgsandstone!60] (M3) -- (M4);
+            \draw [color=uofgsandstone!60] (M1) -- (M3);
+
+            \draw [color=uofgsandstone!60] (M3) to [out=280, in=210, looseness=8] (M3);
             \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
@@
         \begin{scope}[xshift=15cm, yshift=-1cm]
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
             \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
@@
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
             \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
             \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
@@
             \begin{scope}[on background layer]
-                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
-                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
-                \draw [draw=uofgsandstone!40] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
-                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
+                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
+                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
+                \draw [draw=uofgsandstone!60] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!60] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
+                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
+                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
                 \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
@@
 
-            \draw [draw=uofgsandstone!40] (Ma) -- (Mb);
-            \draw [draw=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [draw=uofgsandstone!40] (Mb) -- (Mc);
-            \draw [draw=uofgsandstone!40] (Mb) -- (Md);
-            \draw [draw=uofgsandstone!40] (Mc) -- (Me);
+            \draw [draw=uofgsandstone!60] (Ma) -- (Mb);
+            \draw [draw=uofgsandstone!60] (Ma) -- (Mc);
+            \draw [draw=uofgsandstone!60] (Mb) -- (Mc);
+            \draw [draw=uofgsandstone!60] (Mb) -- (Md);
+            \draw [draw=uofgsandstone!60] (Mc) -- (Me);
 
@@
 
-            \draw [color=uofgsandstone!40] (M1) -- (M2);
-            \draw [color=uofgsandstone!40] (M1) -- (M3);
-            \draw [color=uofgsandstone!40] (M2) -- (M4);
-            \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \draw [color=uofgsandstone!60] (M1) -- (M2);
+            \draw [color=uofgsandstone!60] (M1) -- (M3);
+            \draw [color=uofgsandstone!60] (M2) -- (M4);
+            \draw [color=uofgsandstone!60] (M3) -- (M4);
 
@@
 
-            \draw [draw=uofgsandstone!40] (Ma) -- (Mb);
-            \draw [draw=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [draw=uofgsandstone!40] (Mb) -- (Mc);
+            \draw [draw=uofgsandstone!60] (Ma) -- (Mb);
+            \draw [draw=uofgsandstone!60] (Ma) -- (Mc);
+            \draw [draw=uofgsandstone!60] (Mb) -- (Mc);
             \draw [dotted] (Mb) -- (Md);
@@
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
@@
             \draw [very thick] (Ma) -- (Mb);
-            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [color=uofgsandstone!40] (Mb) -- (Mc);
-            \draw [color=uofgsandstone!40] (Mb) -- (Md);
-            \draw [color=uofgsandstone!40] (Mc) -- (Me);
+            \draw [color=uofgsandstone!60] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!60] (Mb) -- (Mc);
+            \draw [color=uofgsandstone!60] (Mb) -- (Md);
+            \draw [color=uofgsandstone!60] (Mc) -- (Me);
 
@@
             \draw [very thick] (M1) -- (M2);
-            \draw [color=uofgsandstone!40] (M1) -- (M3);
-            \draw [color=uofgsandstone!40] (M2) -- (M4);
-            \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \draw [color=uofgsandstone!60] (M1) -- (M3);
+            \draw [color=uofgsandstone!60] (M2) -- (M4);
+            \draw [color=uofgsandstone!60] (M3) -- (M4);
 
@@
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
@@
             \draw [very thick] (Ma) -- (Mb);
-            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
-            \draw [color=uofgsandstone!40] (Mb) -- (Mc);
+            \draw [color=uofgsandstone!60] (Ma) -- (Mc);
+            \draw [color=uofgsandstone!60] (Mb) -- (Mc);
             \draw [very thick] (Mb) -- (Md);
-            \draw [color=uofgsandstone!40] (Mc) -- (Me);
+            \draw [color=uofgsandstone!60] (Mc) -- (Me);
 
@@
             \draw [very thick] (M1) -- (M2);
-            \draw [color=uofgsandstone!40] (M1) -- (M3);
+            \draw [color=uofgsandstone!60] (M1) -- (M3);
             \draw [very thick] (M2) -- (M4);
-            \draw [color=uofgsandstone!40] (M3) -- (M4);
+            \draw [color=uofgsandstone!60] (M3) -- (M4);
 
@@
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};
 
@@
 
-                    \draw [color=uofgsandstone!40] (M1) -- (M2);
-                    \draw [color=uofgsandstone!40] (M1) -- (M3);
-                    \draw [color=uofgsandstone!40] (M2) -- (M4);
-                    \draw [color=uofgsandstone!40] (M3) -- (M4);
+                    \draw [color=uofgsandstone!60] (M1) -- (M2);
+                    \draw [color=uofgsandstone!60] (M1) -- (M3);
+                    \draw [color=uofgsandstone!60] (M2) -- (M4);
+                    \draw [color=uofgsandstone!60] (M3) -- (M4);
             \end{tikzpicture}

### 2016-04-20 paper/paper.tex
We need to talk about loops here

@@
 assignments, so two matching nodes $(u, u')$ and  $(v, v')$ are adjacent if $u \neq v$ and $u' \neq
-v'$, and if they preserve both edges and non-edges, so $(u, v) \in \operatorname{E}(G) \Leftrightarrow
-(u', v') \in \operatorname{E}(H)$. We illustrate this in \cref{figure:association}.
+v'$, and if they preserve both edges and non-edges, so $(u, v) \in \operatorname{E}(G)
+\Leftrightarrow (u', v') \in \operatorname{E}(H)$, and if either both or neither of $u$ and $u'$
+have a loop, and likewise for $v$ and $v'$. We illustrate this in \cref{figure:association}.
 
@@
         vertices---one solution is highlighted. On the right, the association graph encoding: the
-        highlighted clique of size three shows the same solution. In practice the isolated vertices
-        (representing assignments between incompatible vertices) would be omitted.}\label{figure:association}
+        highlighted clique of size three shows the same solution. In practice the isolated matching
+        nodes (representing assignments between incompatible vertices, due to the presence or
+    absence of loops) would be omitted.}\label{figure:association}
 \end{figure}

### 2016-04-20 paper/paper.tex
No the

@@
 Labels and directed edges usually simplify the solution process, both for CP and clique-based
-approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in the
+approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in
 association graphs; edge labels tighten edge constraints for CP, and make the association graph

### 2016-04-20 paper/paper.tex
Typo

@@
 \cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
-``FC+Bound'' and ``MAC+Bound'' (simply referred to has FC and MAC) CP implementations of Ndiaye and
+``FC+Bound'' and ``MAC+Bound'' (simply referred to as FC and MAC) CP implementations of Ndiaye and
 Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon

### 2016-04-20 paper/paper.tex
Clarify
No the

@@
 
-A closer inspection of the data suggests that the different randomness models have little effect on
-the runtimes for either approach. However, the relative size of the solution matters, particularly
-for the clique algorithm: if the solution is large (i.e.\ the two input graphs are very similar),
-the clique approach finds nearly every labelled instance trivial.
+A closer inspection of the data suggests that the different randomness models used to generate
+instances have little effect on the runtimes for either approach. However, the relative size of the
+solution matters, particularly for the clique algorithm: if the solution is large (i.e.\ the two
+input graphs are very similar), the clique approach finds nearly every labelled instance trivial.
 
@@
 \cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
-during the search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
+during search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
 may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when

### 2016-04-20 paper/paper.tex
Not ours

@@
 undirected). For directed graphs, there is more that one notion of connectivity, and it is not clear
-which should be selected---our approach extends easily to weakly connected directed graphs, but not
-to the strongly connected case.
+which should be selected---the approaches we consider extend easily to weakly connected directed
+graphs, but not to the strongly connected case.
 

### 2016-04-20 paper/paper.tex
Un

@@
 set of variables already assigned to values different from $\bot$. The next variable to be assigned
-is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
-$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
+is chosen within the set of unassigned variables which are the neighbour of at least one vertex of
+$\mathit{CComp}$.  When this set is empty, all remaining unassigned variables are assigned to
 $\bot$. We illustrate this in \cref{figure:restricted}.

### 2016-04-20 paper/paper.tex
That's not an i.e.

@@
 explored the use of constraint programming in the generation of connected graphs with specified
-degree sequences.  Two constraints were combined, i.e.\ the graphical constraint (a backtrackable
-implementation of the Havel-Hakimi algorithm) with a connectivity constraint implemented using sets
+degree sequences.  Two constraints were combined: the graphical constraint (a backtrackable
+implementation of the Havel-Hakimi algorithm), and a connectivity constraint implemented using sets
 of vertices, where vertex sets $A$ and $B$ are combined when there exists a pair of vertices $v \in

### 2016-04-20 paper/paper.tex
Use A instead of CComp, since we're using single letter names

@@
 Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
-branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
+branching rule which selects the next variable to be assigned. Let $A$ be the
 set of variables already assigned to values different from $\bot$. The next variable to be assigned
 is chosen within the set of unassigned variables which are the neighbour of at least one vertex of
-$\mathit{CComp}$.  When this set is empty, all remaining unassigned variables are assigned to
+$A$.  When this set is empty, all remaining unassigned variables are assigned to
 $\bot$. We illustrate this in \cref{figure:restricted}.
@@
 and may be combined: at each step of the search, we select the next variable to be assigned within
-the neighbors of $\mathit{CComp}$, and each time a vertex of $H$ is removed from a domain we filter
+the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter
 domains to ensure connectedness consistency.

### 2016-04-20 paper/paper.tex
Wording

@@
 implementation details on how to use bitsets and other data structures to implement the colouring
-stage with very low constant factors). The approach we describe here differs considerably from that
-of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery \cite{DBLP:conf/mco/VismaraV08}:
-these earlier approaches worked by classifying labels in the association graph based upon whether a
-common vertex is shared, and then constructing cliques with particular edge properties---this is
-harder to integrate with a strong bound function.
-
-We begin by building the association graph (\lineref{buildassoc}). The main part of the algorithm
+stage with very low constant factors). The way we extend this algorithm for connectedness differs
+considerably from that of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery
+\cite{DBLP:conf/mco/VismaraV08}: these earlier approaches worked by classifying labels in the
+association graph based upon whether a common vertex is shared, and then constructing cliques with
+particular edge properties---this is harder to integrate with a strong bound function.
+
+Our algorithm begins by building the association graph (\lineref{buildassoc}). The main part of the algorithm
 then works by building up candidate cliques in the $\mathit{solution}$ variable, by recursive calls
@@
 set of assignments which could be made next which maintain connectedness. (Using only one of the two
-input graphs is sufficient for correctness, and has the advantage that the $\FuncSty{connected}$
-function may be implemented as a simple lookup into a precomputed array which maps each vertex in
+input graphs is sufficient for correctness, and has the advantage that the connectedness set
+may be determined by a simple lookup into a precomputed array which maps each vertex in
 the first input graph to a bitset.) At the top of search, this set is empty, and is not used (our

### 2016-04-20 paper/paper.tex
Stop saying branchable

@@
 \vspace{1ex}
-\nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
+\nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{connected}$, Set $\mathit{remaining}$) \;
 \nl \Begin{
     \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \label{makecolours} \;
-    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{branchable}),$ \;
-    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{branchable}))$ \;
+    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{connected}),$ \;
+    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{connected}))$ \;
     \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$\label{outerloop}}{
@@
             |\mathit{incumbent}|$}{\KwSty{return}\label{bound}}
-            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne
+            \nl \lIf{$v \notin \mathit{connected} ~ \KwSty{and} ~ \mathit{solution} \ne
             \emptyset$}{\KwSty{return} \label{acceptbranchable}}
@@
             \mathit{solution}'$ \label{newincumbent}}
-            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \{ w \in G : \FuncSty{first}(w)
+            \nl $\mathit{connected}' \gets \mathit{connected} \cup \{ w \in G : \FuncSty{first}(w)
             \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \label{addtobranchable} \;
@@
             \nl \lIf{$\mathit{remaining}' \neq \emptyset$}{$\FuncSty{search}(G, \mathit{solution}',
-            \mathit{branchable}', \mathit{remaining}')$\label{recursesearch}}
+            \mathit{connected}', \mathit{remaining}')$\label{recursesearch}}
          }
@@
 
-The $\mathit{branchable}$ set contains the set of association graph vertices which correspond to
+The $\mathit{connected}$ set contains the set of association graph vertices which correspond to
 vertices adjacent to an already-accepted vertex in the first input graph---in constraint programming terms, it is the
@@
 may only accept vertices which are in this set, and if no such vertices remain then we return
-immediately (\lineref{acceptbranchable}). When recursing, we extend $\mathit{branchable}$ with the
+immediately (\lineref{acceptbranchable}). When recursing, we extend $\mathit{connected}$ with the
 new vertices permitted by our acceptance of the branching $v$ (\lineref{addtobranchable}). Note that
@@
                     \node [anchor=west] (Ns) at (0, 3.5) { $\mathit{solution}$ };
-                    \node [anchor=west] (Nb) at (0, 2) { $\mathit{branchable}$ };
+                    \node [anchor=west] (Nb) at (0, 2) { $\mathit{connected}$ };
                     \node [anchor=west] (Nr) at (0, 0.5) { $\mathit{remaining}$ };
@@
             \\[0.1cm]
-            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \setminus \mathit{branchable}$ &
-            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \cap \mathit{branchable}$
+            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \setminus
+            \mathit{connected}$ &
+            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \cap
+            \mathit{connected}$
             \\
@@
         have two subgraphs to colour. We need two colours for $\mathit{remaining} \setminus
-        \mathit{branchable}$, and we place these two colour classes first in the $\mathit{colourClasses}$
-        variable. We can also colour $\mathit{remaining} \cap \mathit{branchable}$ using two
+        \mathit{connected}$, and we place these two colour classes first in the $\mathit{colourClasses}$
+        variable. We can also colour $\mathit{remaining} \cap \mathit{connected}$ using two
         colours, since we cannot simultaneously map $c$ to $2$ and $d$ to $3$, or vice-versa. Thus
@@
 decreases by one, and if $f \mapsto 5$ were reached we would stop due to a lack of remaining
-branchable vertices. }\label{figure:assocrestricted}
+connected association nodes. }\label{figure:assocrestricted}
 \end{figure}

### 2016-04-21 paper/paper.tex
Let's assume we can't
Define the association graph to omit isolated vertices

@@
 \usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing,
-    patterns, matrix}
+    patterns, matrix, shapes}
 
@@
 an undirected graph $G \modularproduct H$ with vertex set $\operatorname{V}(G \modularproduct H) =
-\operatorname{V}(G) \times \operatorname{V}(H)$---to avoid confusing vertices of $G \modularproduct
+\{ (v, v') \in \operatorname{V}(G) \times \operatorname{V}(H) : (v, v) \in \operatorname{E}(G)
+\Leftrightarrow (v', v') \in \operatorname{E}(H)\}$---to avoid confusing vertices of $G \modularproduct
 H$ with vertices of the two original graphs, we call vertices of $G \modularproduct H$
@@
 v'$, and if they preserve both edges and non-edges, so $(u, v) \in \operatorname{E}(G)
-\Leftrightarrow (u', v') \in \operatorname{E}(H)$, and if either both or neither of $u$ and $u'$
-have a loop, and likewise for $v$ and $v'$. We illustrate this in \cref{figure:association}.
+\Leftrightarrow (u', v') \in \operatorname{E}(H)$. We illustrate this in \cref{figure:association}.
 
@@
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
             \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
-            \node (La2) [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
+            \node (La2) [above = 0 of Ma2, font=\small, color=uofgsandstone!60] { \vphantom{0}2 };
             \node (La3) [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
-            \node (La4) [above = 0 of Ma4, font=\small] { \vphantom{0}4 };
+            \node (La4) [above = 0 of Ma4, font=\small, color=uofgsandstone!60] { \vphantom{0}4 };
 
@@
             \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
             \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
-            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
+            \node [left = 0 of Mb2, font=\small, color=uofgsandstone!60] { \vphantom{0}2 };
             \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
-            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };
+            \node [left = 0 of Mb4, font=\small, color=uofgsandstone!60] { \vphantom{0}4 };
 
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
-            \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
+            \node (Lc1) [below = 0 of Mc1, font=\small, color=uofgsandstone!60] { \vphantom{0}1 };
             \node (Lc2) [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
-            \node (Lc3) [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
+            \node (Lc3) [below = 0 of Mc3, font=\small, color=uofgsandstone!60] { \vphantom{0}3 };
             \node (Lc4) [below = 0 of Mc4, font=\small] { \vphantom{0}4 };
@@
 
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
-            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
+            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
             \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
-            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
+            \node [right = 0 of Md1, font=\small, color=uofgsandstone!60] { \vphantom{0}1 };
             \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
-            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
+            \node [right = 0 of Md3, font=\small, color=uofgsandstone!60] { \vphantom{0}3 };
             \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };
@@
         vertices---one solution is highlighted. On the right, the association graph encoding: the
-        highlighted clique of size three shows the same solution. In practice the isolated matching
-        nodes (representing assignments between incompatible vertices, due to the presence or
-    absence of loops) would be omitted.}\label{figure:association}
+        highlighted clique of size three shows the same solution. The ``missing'' vertices
+        correspond to assignments which are impossible due to the presence or absence of
+        loops.}\label{figure:association}
 \end{figure}
@@
 
-?? Time to find or time to prove? Can we figure this out?
-
 \section{Conclusion}

### 2016-04-21 paper/paper.tex
Darker highlighting

@@
         \begin{scope}[rotate=90]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
 
@@
         \begin{scope}[xshift=7cm, rotate=90]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
+            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
 

### 2016-04-21 paper/paper.tex
Cite more
Define N(G, v) formally

@@
 Maximum common subgraph problems arise in biology and chemistry
-\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011}, in computer vision
-\cite{DBLP:journals/jair/CookH94}, in the analysis of source code
+\cite{DBLP:journals/jcamd/RaymondW02a,Ehrlich:2011,DAM2014}, in computer vision
+\cite{DBLP:journals/jair/CookH94,GBR2013}, in the analysis of source code
 \cite{DBLP:journals/tkde/DjokoCH97}, binary programs \cite{DBLP:conf/icics/GaoRS08}, and circuit
@@
 \operatorname{E}(G) \Rightarrow (v, u) \in \operatorname{E}(G)$. The neighbourhood of
-a vertex $v$, written $\operatorname{N}(G, v)$, is the set of vertices to which it is adjacent.
+a vertex $v$, written $\operatorname{N}(G, v)$, is the set of vertices to which it is adjacent, so
+$\operatorname{N}(G, v) = \{ u \in \operatorname{V}(G) : (u, v) \in \operatorname{E}(G) \}$.
 Given a graph $G$, two vertices $v_s, v_e \in \operatorname{V}(G)$ are connected by a path in $G$ if

### 2016-04-21 paper/paper.tex
Another cite

@@
 partial subgraphs---we do not consider this possibility in this paper, although everything we
-discuss may be extended to the partial case \cite{DBLP:conf/cp/NdiayeS11}.
+discuss may be extended to the partial case \cite{DBLP:conf/mco/VismaraV08,DBLP:conf/cp/NdiayeS11}.
 

### 2016-04-21 paper/paper.tex
Debracket
Support

@@
 maximum clique problem. Both approaches are described for undirected, unlabelled graphs; their
-extension to richer graphs is discussed in \cref{extension}.  (Other approaches have been tried,
+extension to richer graphs is discussed in \cref{extension}.  Other approaches have been tried,
 mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
 \cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
-\cite{UpcomingIJCAIPaper}.)
+\cite{UpcomingIJCAIPaper}.
 
@@
 approaches to do more filtering so long as $\bot$ remains in variable domains: every pair of
-variables $(x_i, x_j)$ having  $D(x_i) \neq \emptyset$ and $\bot \in D(x_j)$ is arc consistent,
+variables $(x_i, x_j)$ having  $\bot \in D(x_j)$ is arc consistent,
 since $\bot$ is a support for any value $u \in D(x_i)$. However, as soon as $\bot$ is removed from
 domains (i.e.\ when the number of variables assigned to $\bot$ has reached the best known bound on
-the size of the MCS), maintaining arc consistency may filter values, and then the tighter constraints
+the size of the MCS), maintaining arc consistency may filter values, and then tighter constraints
 increase the opportunities for filtering.

### 2016-04-21 paper/paper.tex
Change overly clever wording
Typo

@@
 For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
-undirected). For directed graphs, there is more that one notion of connectivity, and it is not clear
+undirected). For directed graphs, there is more than one notion of connectivity, and it is not clear
 which should be selected---the approaches we consider extend easily to weakly connected directed
@@
 In \cref{figure:connected-cumulative} we compare the clique-based approach to the connected problem
-with both CP Both approaches. The trend is broadly similar to the unconnected problem: for labelled
+with the two CP Both approaches. The trend is broadly similar to the unconnected problem: for labelled
 graphs, the clique-based approach is the clear winner, but for unlabelled graphs the clique approach

### 2016-04-21 paper/paper.tex
We must have order

@@
 clique in this subset has at most $k$ vertices. However, the colouring is also used as a branching
-heuristic: vertices are selected in reverse from their colour classes in turn, starting with the
+heuristic: vertices are selected in reverse order from their colour classes in turn, starting with the
 last colour class created. Because of this coupling of branching and the bound (which is important

### 2016-06-07 paper/paper.tex
Notation fix

@@
 written $G[H]$, is the graph with vertex set $H$, and with every edge in $G$ which has both
-endpoints in $G$, i.e.\ $\operatorname{E}(H) = \operatorname{E}(G) \cap (\operatorname{V}(H) \times
+endpoints in $G$, i.e.\ $\operatorname{E}(G[H]) = \operatorname{E}(G) \cap (\operatorname{V}(H) \times
 \operatorname{V}(H))$. We will consider only subgraphs which are induced by some set. It is also

### 2016-06-08 paper/paper.tex
Slightly darker yellow/green

@@
 \definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
-\definecolor{chromayellow}{rgb}{1.0, 1.0, 0.878431}
+\definecolor{chromayellowgreen}{rgb}{0.882353, 0.984314, 0.788235}
 \definecolor{chromagreen}{rgb}{0.564706, 0.933333, 0.564706}
@@
             \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
@@
         \begin{scope}
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
             \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
@@
         \begin{scope}[xshift=12.8cm]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
             \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
@@
         \begin{scope}[xshift=25.6cm]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
@@
 
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
@@
         \begin{scope}[yshift=-9cm]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
@@
         \begin{scope}[xshift=12.8cm, yshift=-9cm]
-            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
+            \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
             \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
@@
             \begin{tikzpicture}[scale=0.33]
-                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
-                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
+                    \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
                     \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
@@
             \begin{tikzpicture}[scale=0.33]
-                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
-                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
+                \node[draw, circle, fill=chromayellowgreen, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
                 \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};

### 2016-06-08 paper/paper.tex
Why we need to reevaluate

@@
 
-Previous experimental evaluations have used weak maximum clique algorithms, or even enumeration
+Previous experimental evaluations have used simple maximum clique algorithms, or even enumeration
 algorithms---for example, Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} compare a modified form
 of the Bron-Kerbosch maximal clique enumeration algorithm \cite{Bron:1973:AFC:362342.362367} with a
-CP optimisation approach. Our experience suggests that the optimisation form of the clique problem
-is often many orders of magnitude easier than enumeration, due to the possibility of employing a
-strong bound function to prune the search space.  Therefore, in \cref{eval1}, we  re-evaluate the
-clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled
-graphs, and that it is competitive with CP on unlabelled graphs.
+CP optimisation approach. Our experience suggests that a modern maximum clique algorithm could give
+many orders of magnitude improvement, due to a strong bound function which prunes the search space.
+Therefore, in \cref{eval1}, we re-evaluate the clique-based approach using a modern algorithm, and
+we show that it outperforms CP on labelled graphs, and that it is competitive with CP on unlabelled
+graphs, contradicting earlier conclusions.
 
@@
 maximisation problem was being considered), or very simple maximum clique algorithms
-\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}. Thus we re-evaluate the approach
-using a modern maximum clique algorithm. Association graphs are dense, even if the input is sparse,
-so we will using (the single-threaded, bit-parallel version of) the maximum clique solver by
-McCreesh and Prosser \cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
+\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}, and so their conclusions may now be
+overly pessimistic. Thus we re-evaluate the approach using a modern maximum clique algorithm.
+Association graphs are dense, even if the input is sparse, so we will using (the single-threaded,
+bit-parallel version of) the maximum clique solver by McCreesh and Prosser
+\cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
 \cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita

### 2016-06-08 paper/paper.tex
Heuristics

@@
 ``FC+Bound'' and ``MAC+Bound'' (simply referred to as FC and MAC) CP implementations of Ndiaye and
-Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
-E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
-used.
+Solnon \cite{DBLP:conf/cp/NdiayeS11}, using smallest domain first for variable ordering, and a value
+ordering which prefers vertices of most similar degree.  We perform our experiments on machines with
+Intel Xeon E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of
+one hour was used.
 

### 2016-06-08 paper/paper.tex
Why 33 for labels
Betterer wording

@@
 connectedness constraint to the model. Alternatively, we may use a special branching rule
-\cite{DBLP:conf/mco/VismaraV08} to grow connected subgraphs only. These two techniques may
-be combined, and we experimentally show that the best results are obtained when combining them.
+\cite{DBLP:conf/mco/VismaraV08} to grow connected subgraphs only. These two techniques may be
+combined, and we experimentally show that the best results are in fact obtained when combining them.
 When solving the MCCS problem with a clique-based approach, neither technique seems directly viable
@@
 branching and bounding rule used by modern clique algorithms to maintain connectedness during
-search.  We compare the clique-based approach with the best CP variant for MCCS, and we show
-that it outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.
+search.  We compare the clique-based approach with the best CP variant for MCCS, and we show that it
+outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.
 
@@
 
-McGregor \cite{McGreg82} proposed a branch and bound approach: each branch of the search tree
+McGregor \cite{McGreg82} proposed a branch and bound algorithm: each branch of the search tree
 corresponds to the matching of two vertices, and a bounding function evaluates the number of
@@
 
-This CP model is improved by Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11} by replacing binary
+This CP model was improved by Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11} by replacing binary
 difference constraints with a soft global allDifferent constraint which maximizes the number of
@@
 constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign
-distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker
+distinct values to enough $x_u$ variables to surpass the best cost found so far---it is a weaker
 version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that
-can be assigned distinct values).
+can be assigned distinct values.
 
@@
 number of vertices. In this paper, we report experiments with unlabelled graphs (labels are
-ignored), and with 33\% labellings. For unlabelled graphs, we select the 27,500 graph pairs where the
-number of vertices in each graph is no more than 35; for labelled graphs, which we find less
-computationally challenging, we select all 81,400 graph pairs, to include graphs with up to 100
-vertices.
+ignored), and with 33\% labellings (the problem becomes very easy with larger numbers of labels).
+For unlabelled graphs, we select the 27,500 graph pairs where the number of vertices in each graph
+is no more than 35; for labelled graphs, which we find less computationally challenging, we select
+all 81,400 graph pairs, to include graphs with up to 100 vertices.
 
@@
 connectivity via the \emph{reachable} constraint, ensuring that there is a path from a specified
-vertex to a specified set of vertices. One such constraint is then posted for each of the vertices
-in the graph and encodes the transitive closure of the graph. Brown et al.\ \cite{Brown:2005}
+vertex to a specified set of vertices. One such constraint could be posted for each of the vertices
+in the graph, encoding the transitive closure of the graph. Brown et al.\ \cite{Brown:2005}
 explored the use of constraint programming in the generation of connected graphs with specified
@@
 
-During the search, each time a variable is assigned to $\bot$, we remove the corresponding vertex
+During search, each time a variable is assigned to $\bot$, we remove the corresponding vertex
 from $S$ and perform a new traversal of $G[S]$ starting from the initial vertex $u$. For each vertex
@@
 algorithm introduced by San Segundo \textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}, with the
-$k_{\mathit{min}}$ parameter set to $0$, so we do not present it here. We use a simple static degree
+$k_{\mathit{min}}$ parameter set to $0$, so we do not describe it here. We use a simple static degree
 ordering; other initial vertex orderings have been considered on general clique problems

### 2016-06-08 paper/paper.tex
Why are labels helpful

@@
 
-The two plots on the top of \cref{figure:unconnected-cumulative} display the cumulative number of instances
-solved with respect to time.  When graphs are labelled, the clique-based approach clearly
-outperforms either CP model, and MAC has a slight advantage over FC. For unlabelled graphs, the
+The two plots on the top of \cref{figure:unconnected-cumulative} display the cumulative number of
+instances solved with respect to time.  When graphs are labelled, the clique-based approach clearly
+outperforms either CP model, and MAC has a slight advantage over FC. (Recall that edge labels
+    decrease the density of the association graph, which is typically very beneficial for clique
+algorithms, but do not help CP until $\bot$ is removed from domains.) For unlabelled graphs, the
 three approaches are broadly comparable, and ultimately FC beats MAC, which beats the clique

### 2016-06-08 paper/paper.tex
No applications of strongly connected

@@
 which should be selected---the approaches we consider extend easily to weakly connected directed
-graphs, but not to the strongly connected case.
+graphs, but not to the strongly connected case (for which we know of no applications).
 

### 2016-06-08 paper/paper.tex
Difference between branching and filtering

@@
 and may be combined: at each step of the search, we select the next variable to be assigned within
-the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter
-domains to ensure connectedness consistency.
+the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter domains to
+ensure connectedness consistency. In the example in \cref{figure:restricted}, after the first
+assignment, filtering alone would remove $5$ from every domain but would allow branching on any
+remaining variable, whilst branching alone would force the next variable to be either $b$ or $c$ but
+would not immediately eliminate $5$ from the domains of $d$ and $e$.
 

### 2016-06-08 paper/paper.tex
Save a bit of space

@@
 combining both is rarely much worse than just doing one or the other, and is often much better, even
-if on average it is slightly slower.
-
-On unlabelled graphs, we observe that the three variants have rather similar performance.
+if on average it is slightly slower.  On unlabelled graphs, the three variants have rather similar
+performance.
 
@@
     \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \label{makecolours} \;
-    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{connected}),$ \;
-    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{connected}))$ \;
+    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{connected}),\,\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{connected}))$ \;
     \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$\label{outerloop}}{
@@
 \nl \Begin{
-    \nl $\KwSty{return}$ a greedy sequential colouring of the vertices in $\mathit{uncoloured}$,
+    \nl $\KwSty{return}$ a greedy colouring of the vertices in $\mathit{uncoloured}$,
     using the procedure of San Segundo et al.\ \cite{DBLP:journals/cor/SegundoRJ11} with a static

### 2016-06-08 paper/paper.tex
We are novel

@@
 \cite{DBLP:conf/cp/McCreeshP14}), if we were to select only a subset of vertices for branching at
-each stage inside a clique algorithm, we would lose completeness. Thus we must adapt the bound to
-take into account restricted branching.
+each stage inside a clique algorithm, we would lose completeness. Thus we must adapt the bound in a
+non-trivial way to take into account restricted branching.
 
@@
 
-In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
+In \cref{algorithm:mccis} we present a novel clique-inspired algorithm which finds a maximum common
 connected induced subgraph isomorphism via an association graph. If the additional branching

### 2016-06-08 paper/paper.tex
Muck around with conclusion a bit

@@
 
-We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
-problems, particularly when edge labels are involved.  We believe there is further scope for
-tailoring clique algorithms for association graphs, including specialised inference, a bound
-function which is aware that it is working on an association graph, and better initial vertex
-orderings. Treating the first branch specially may also be beneficial, since the first branch has an
-unusually large effect on the search space with association graphs
-\cite{DBLP:conf/cocoon/SutersAZSSL05}.
+Contradicting earlier claims in the literature, we have seen that a modern clique algorithm can
+perform competitively for maximum common subgraph problems, particularly when edge labels are
+involved. However, the best approaches for these problems is still far behind the state-of-the-art
+for subgraph isomorphism, where we can often scale to unlabelled graphs with thousands of vertices.
+
+To start tackling this gap, we believe there is further scope for tailoring clique algorithms for
+association graphs, including specialised inference, a bound function which is aware that it is
+working on an association graph, and better initial vertex orderings. Treating the first branch
+specially may also be beneficial, since the first branch has an unusually large effect on the search
+space with association graphs \cite{DBLP:conf/cocoon/SutersAZSSL05}.
 

### 2016-06-13 paper/paper.tex
Better bibtex entry
Fix nonsense connected definition

@@
 and each pair of successive vertices is connected by an edge, i.e.\ $\forall i\in \{1 \ldots k \},
-(v_{i-1}, v_i) \in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every non-adjacent pair
+(v_{i-1}, v_i) \in \operatorname{E}(G)$. A graph $G$ is \emph{connected} if every distinct pair
 of vertices is connected by a path.
@@
 including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
-\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
+\cite{droschinsky_et_al:LIPIcs:2016:xxxx}, but the general case remains \NP-hard. As illustrated in
 \cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness

### 2016-06-13 paper/paper.tex
Unnecessary word

@@
 In \cref{algorithm:mccis} we present a novel clique-inspired algorithm which finds a maximum common
-connected induced subgraph isomorphism via an association graph. If the additional branching
+connected induced subgraph via an association graph. If the additional branching
 restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm

### 2016-06-13 paper/paper.tex
Matching nodes

@@
 
-The $\mathit{connected}$ set contains the set of association graph vertices which correspond to
+The $\mathit{connected}$ set contains the set of matching nodes which correspond to
 vertices adjacent to an already-accepted vertex in the first input graph---in constraint programming terms, it is the

### 2016-06-13 paper/paper.tex
Wrong word

@@
 
-For CP models, using a branching rule for correctness, rather than simply as an ordering heuristic,
+For CP models, using a branching rule for connectedness, rather than simply as an ordering heuristic,
 is unconventional and does not cleanly fit into the abstractions used by toolkits. However, we saw

### 2016-06-13 paper/paper.tex
Find -> Finding
Applications

@@
 
-\section{Find Maximum Common Connected Subgraphs}\label{mccs}
-
-In many applications, the common subgraph must be connected
+\section{Finding Maximum Common Connected Subgraphs}\label{mccs}
+
+In many applications, the common subgraph must satisfy some additional constraints. These
+constraints are usually handled in a straightforward way in CP, by branching rules and/or constraint
+propagation. In clique-based approaches, some constraints may be easily handled by modifying the
+definition of the association graph---for example, constraints on pairs of vertices that may be
+matched are handled by removing inconsistent pairs from $\operatorname{V}(G \modularproduct H)$.
+However, more global constraints cannot be handled by modifying the definition of the association
+graph.
+
+In this paper, we focus on the connectedness constraint, which occurs in many applications
 \cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.

### 2016-06-13 paper/paper.tex
Strategic word removal to stay under page limit

@@
 
-In many applications, the common subgraph must satisfy some additional constraints. These
-constraints are usually handled in a straightforward way in CP, by branching rules and/or constraint
-propagation. In clique-based approaches, some constraints may be easily handled by modifying the
+In many applications, the common subgraph must satisfy some additional constraints. This
+is usually handled in a straightforward way in CP, by branching rules and/or constraint
+propagation. In clique-based approaches, some constraints may be handled by modifying the
 definition of the association graph---for example, constraints on pairs of vertices that may be
@@
 counters on these edges. The counters were then used to detect the existence of cut-edges and
-protects these by forcing edges; the complexity of this constraint is cubic in the number of
-vertices.
+protects these by forcing edges.
 
@@
 
-Connectedness consistency is not ensured at the root node of the search---it is ensured only once a
-first variable has been assigned. Let $x_u$ be the first assigned variable, and $v$ the value
+Connectedness consistency is ensured only once a first variable has been assigned, rather than at
+the root of search. Let $x_u$ be the first assigned variable, and $v$ the value
 assigned to $x_u$. To ensure connectedness consistency, we perform a traversal of $G$ (resp.\ $H$),
@@
 }
-\vspace{1ex}
 \nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{connected}$, Set $\mathit{remaining}$) \;
@@
 }
-\vspace{0.5ex}
 \nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;

### 2016-06-16 paper/paper.tex
Compile graphs via PDFs

@@
 \documentclass{llncs}
-
-% \usepackage{showframe}
-% \usepackage{refcheck}
 
@@
 \usepackage{cleveref}                  % no need to type Figure etc
-\usepackage{gnuplot-lua-tikz}          % graphs
 \usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
@@
 
-\makeatletter\@ifpackageloaded{refcheck}{\newcommand{\citesforrefcheck}{\nocite{*}}}{\newcommand{\citesforrefcheck}{}}\makeatother
-
 \usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing,
-    patterns, matrix, shapes}
+    patterns, matrix, shapes, backgrounds}
 
@@
     \centering
-    \input{gen-graph-unconnected-cumulative}
+    \includegraphics{gen-graph-unconnected-cumulative.pdf}
     \vspace*{1em}
@@
     \centering
-    \input{gen-graph-unconnected-heatmap}
+    \includegraphics{gen-graph-unconnected-heatmap.pdf}
     \caption{The cumulative number of MCS instances solved in under a certain time: on the top, 33\%
@@
     \centering
-    \input{gen-graph-connected-cumulative-cp}
+    \includegraphics{gen-graph-connected-cumulative-cp.pdf}
 
@@
     \centering
-    \input{gen-graph-connected-cp}
+    \includegraphics{gen-graph-connected-cp.pdf}
     \caption{On top, the cumulative number of MCCS instances solved in under a certain time using
@@
     \centering
-    \input{gen-graph-connected-cumulative}
+    \includegraphics{gen-graph-connected-cumulative.pdf}
     \vspace*{1em}
@@
     \centering
-    \input{gen-graph-connected-heatmap}
+    \includegraphics{gen-graph-connected-heatmap.pdf}
     \caption{The cumulative number of connected instances solved in under a certain time: on the
@@
 
-\citesforrefcheck
-
 \bibliographystyle{splncs}

### 2016-08-29 talk/talk.tex
Start writing talk

% vim: set spell spelllang=en tw=100 et sw=4 sts=4 foldmethod=marker foldmarker={{{,}}} :

\documentclass{beamer}

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}                   % \operatorname
\usepackage{amsfonts}                  % \mathcal
\usepackage{amssymb}                   % \nexists
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[vlined]{algorithm2e} % algorithms
\usepackage{centernot}

\usetikzlibrary{shapes, arrows, shadows, calc, positioning, fit}
\usetikzlibrary{decorations.pathreplacing, decorations.pathmorphing, shapes.misc}
\usetikzlibrary{tikzmark}

\definecolor{uofguniversityblue}{rgb}{0, 0.219608, 0.396078}

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofgforest}{rgb}{0, 0.2, 0.129412}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgrust}{rgb}{0.603922, 0.227451, 0.023529}
\definecolor{uofgburgundy}{rgb}{0.490196, 0.133333, 0.223529}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgburgundy, text=white}}
\tikzset{vertexc2/.style={vertex, fill=uofgsandstone, text=white}}
\tikzset{vertexc3/.style={vertex, fill=uofgforest, text=white}}
\tikzset{vertexc4/.style={vertex, fill=uofgheather, text=white}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}

% {{{ theme things
\useoutertheme[footline=authortitle]{miniframes}
\useinnertheme{rectangles}

\setbeamerfont{block title}{size={}}
\setbeamerfont{title}{size=\large,series=\bfseries}
\setbeamerfont{section title}{size=\large,series=\mdseries}
\setbeamerfont{author}{size=\normalsize,series=\mdseries}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=white}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=uofgcobalt}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

\setbeamercolor*{titlelike}{parent=palette primary}

\beamertemplatenavigationsymbolsempty

\setbeamertemplate{title page}
{
    \begin{tikzpicture}[remember picture, overlay]
        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=white, anchor=north west, yshift=-0.5cm, opacity=0.8] (0, 0) rectangle (\paperwidth, -3.2cm);
            \end{tikzpicture}
        };

        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=white, anchor=north west, yshift=-0.5cm, xshift=0.7\paperwidth] (0, 0) rectangle (0.3\paperwidth, -3.2cm);
            \end{tikzpicture}
        };

        \node (logo) [anchor=north east, shift={(-0.15cm,-0.65cm)}] at (current page.north east) {
            \begin{minipage}{0.25\paperwidth}
                \begin{center}
                \includegraphics*[keepaspectratio=true,scale=0.4]{UoG_keyline.pdf} \\[0.15cm]
                    \colorbox{white}{\includegraphics*[keepaspectratio=true,scale=0.14]{Universite_Lyon_1.pdf}}\\[0.15cm]
                \includegraphics*[keepaspectratio=true,scale=0.12]{Logo_INSALyon-pantone-cartouche.pdf}
                \end{center}
            \end{minipage}
        };

        \node [anchor=west, xshift=0.1cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.70\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[black]{}\inserttitle}\\[0.2cm]
                {\usebeamerfont{author}\usebeamercolor[black]{}\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

\setbeamertemplate{section page}
{
    \begin{centering}
        \begin{beamercolorbox}[sep=12pt,center]{part title}
            \usebeamerfont{section title}\insertsection\par
        \end{beamercolorbox}
    \end{centering}
}

\newcommand{\frameofframes}{/}
\newcommand{\setframeofframes}[1]{\renewcommand{\frameofframes}{#1}}

\makeatletter
\setbeamertemplate{footline}
{%
    \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
    \end{beamercolorbox}
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
        \hfill%
        {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
    \end{beamercolorbox}%
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        {\usebeamerfont{title in head/foot}\insertshorttitle}%
        \hfill%
        {\usebeamerfont{frame number}\usebeamercolor[fg]{frame number}\insertframenumber~\frameofframes~\inserttotalframenumber}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
    \end{beamercolorbox}
}

\makeatletter
\newenvironment{nearlyplainframe}[2][]{
    \def\beamer@entrycode{\vspace*{-\headheight}\vspace*{3pt}}
    \setbeamertemplate{headline}
    {%
        \begin{beamercolorbox}[colsep=1.5pt]{upper separation line head}
        \end{beamercolorbox}
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[colsep=1.5pt]{lower separation line head}
        \end{beamercolorbox}
        \vspace*{\headheight}
    }

    \setbeamertemplate{footline}
    {%
        \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
        \end{beamercolorbox}
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
        \end{beamercolorbox}
    }

    \begin{frame}[#1]{#2}
    }{
    \end{frame}
}
\makeatother

% }}}

\author[Ciaran McCreesh, Samba Ndojh Ndiaye, Patrick Prosser and Christine Solnon]{Ciaran McCreesh,
Samba Ndojh Ndiaye, \\ Patrick Prosser and Christine Solnon}
\title{Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems}

\begin{document}

{
    \usebackgroundtemplate{
        \tikz[overlay, remember picture]
        \node[at=(current page.south), anchor=south, inner sep=0pt]{\includegraphics*[keepaspectratio=true, height=\paperheight]{background.jpg}};
    }
    \begin{frame}[plain,noframenumbering]
        \titlepage
    \end{frame}
}

\begin{frame}{Maximum Common Induced Subgraph}
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [color=uofgsandstone!60] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [very thick] (M7) -- (M9);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=6cm]
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M7) -- (M8);
            \draw [very thick] (M8) -- (M9);
        \end{scope}
    \end{tikzpicture}
\end{frame}

\begin{frame}{Why Care?}
    \begin{itemize}
        \item To determine the similarity between two graphs.
            \begin{itemize}
                \item Edit distance comes down to what's not in the maximum common subgraph.
            \end{itemize}

        \item As a relaxed form of subgraph isomorphism.
    \end{itemize}
\end{frame}

\begin{frame}{CP Models}
\end{frame}

\begin{frame}{Clique Models and Microstructure}
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
            \node[draw, circle, fill=uofgpumpkin, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};

            \node [right = 0 of Ma, font=\small] { \vphantom{0}a };
            \node [below = 0 of Mb, font=\small] { \vphantom{0}b };
            \node [below = 0 of Mc, font=\small] { \vphantom{0}c };
            \node [below = 0 of Md, font=\small] { \vphantom{0}d };

            \draw [very thick] (Mb) -- (Mc);
            \draw [very thick] (Mc) -- (Md);
            \draw [color=uofgsandstone!60] (Ma) -- (Mc);
            \draw [color=uofgsandstone!60] (Ma) to [out=150, in=80, looseness=8] (Ma);
            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
        \end{scope}

        \begin{scope}[yshift=-2cm]
            \node[draw, circle, fill=uofgpumpkin, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};

            \node [left = 0 of M1, font=\small] { \vphantom{0}1 };
            \node [right = 0 of M2, font=\small] { \vphantom{0}2 };
            \node [left = 0 of M3, font=\small] { \vphantom{0}3 };
            \node [right = 0 of M4, font=\small] { \vphantom{0}4 };

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [color=uofgsandstone!60] (M3) -- (M4);
            \draw [color=uofgsandstone!60] (M1) -- (M3);

            \draw [color=uofgsandstone!60] (M3) to [out=280, in=210, looseness=8] (M3);
            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
        \end{scope}

        \begin{scope}[xshift=15cm, yshift=-2cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node (La1) [above = 0.2cm of Ma1, font=\small] { \vphantom{0}1 };
            \node (La2) [above = 0.2cm of Ma2, font=\small, color=uofgsandstone!60] { \vphantom{0}2 };
            \node (La3) [above = 0.2cm of Ma3, font=\small] { \vphantom{0}3 };
            \node (La4) [above = 0.2cm of Ma4, font=\small, color=uofgsandstone!60] { \vphantom{0}4 };

            \node [left=0 of La1] { $a \mapsto \{$ };
            \node [right=0 of La4] { $\}$ };

            \node[draw, circle, fill=uofgpumpkin, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
            \node [left = 0.2cm of Mb1, font=\small] { \vphantom{0}1 };
            \node [left = 0.2cm of Mb2, font=\small, color=uofgsandstone!60] { \vphantom{0}2 };
            \node [left = 0.2cm of Mb3, font=\small] { \vphantom{0}3 };
            \node [left = 0.2cm of Mb4, font=\small, color=uofgsandstone!60] { \vphantom{0}4 };

            \draw [decorate, decoration={brace, raise=0.8cm}, thick] (Mb1.south west) -- (Mb4.north west) node [midway, left=1cm] { $b \mapsto$ };

            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node (Lc1) [below = 0.2cm of Mc1, font=\small, color=uofgsandstone!60] { \vphantom{0}1 };
            \node (Lc2) [below = 0.2cm of Mc2, font=\small] { \vphantom{0}2 };
            \node (Lc3) [below = 0.2cm of Mc3, font=\small, color=uofgsandstone!60] { \vphantom{0}3 };
            \node (Lc4) [below = 0.2cm of Mc4, font=\small] { \vphantom{0}4 };

            \node [left=0 of Lc1] { $c \mapsto \{$ };
            \node [right=0 of Lc4] { $\}$ };

            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=white, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
            \node [right = 0.2cm of Md1, font=\small, color=uofgsandstone!60] { \vphantom{0}1 };
            \node [right = 0.2cm of Md2, font=\small] { \vphantom{0}2 };
            \node [right = 0.2cm of Md3, font=\small, color=uofgsandstone!60] { \vphantom{0}3 };
            \node [right = 0.2cm of Md4, font=\small] { \vphantom{0}4 };

            \draw [decorate, decoration={brace, raise=0.8cm}, thick] (Md4.north east) -- (Md1.south east) node [midway, right=1cm] { $\reflectbox{\ensuremath{\mapsto}}\, d$ };

            \begin{scope}[on background layer]
                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [draw=uofgsandstone!60] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
        \end{scope}
        \end{scope}

    \end{tikzpicture}
\end{frame}

\begin{frame}{Benchmark Instances}
    \begin{itemize}
        \item Standard benchmark suite of 81,000 instances (random with varying densities; 2D, 3D
            and 4D regular and irregular meshes; regular bounded degree graphs, and irregular
            bounded degree graphs).
        \item Labels on vertices and edges:
            \begin{itemize}
                \item Up to 100 vertices.
                \item Number of labels is 33\% of the number of vertices.
            \end{itemize}
        \item Unlabelled:
            \begin{itemize}
                \item Up to 35 vertices.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Conventional Wisdom}
    \begin{itemize}
        \item We all know that microstructure is only of theoretical interest, and that solving CSPs
            by reduction is a silly idea.
        \item Several papers say the clique encoding is terrible.
            \begin{itemize}
                \item But this is based upon benchmarking against either maximal clique enumeration
                    algorithms, or very simple maximum clique algorithms.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{nearlyplainframe}[t]{So Which is Better?}
    \only<1>{
        \begin{center}
            \includegraphics*{gen-graph-unconnected-cumulative-unlabelled.pdf}
        \end{center}
    }

    \only<2>{
        \begin{center}
            \includegraphics*{gen-graph-unconnected-heatmap-unlabelled.pdf}
        \end{center}
    }

    \only<3>{
        \begin{center}
            \includegraphics*{gen-graph-unconnected-cumulative-labelled.pdf}
        \end{center}
    }

    \only<4>{
        \begin{center}
            \includegraphics*{gen-graph-unconnected-heatmap-labelled.pdf}
        \end{center}
    }
\end{nearlyplainframe}

\begin{frame}{Why?}
    \begin{itemize}
        \item Vertex labels:
            \begin{itemize}
                \item Remove values from domains in the CP encoding.
                \item Remove vertices in the clique encoding.
            \end{itemize}
        \item Edge labels:
            \begin{itemize}
                \item Don't do anything for MAC so long as $\bot$ remains in domains.

                \item Remove edges in the clique encoding. Maximum clique algorithms like sparse
                    graphs.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Are We Solving the Right Problem?}
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [color=uofgsandstone!60] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [very thick] (M7) -- (M9);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=6cm]
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=2pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M7) -- (M8);
            \draw [very thick] (M8) -- (M9);
        \end{scope}
    \end{tikzpicture}
\end{frame}

\begin{frame}{Maximum Common Connected Subgraph}
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [color=uofgsandstone!60] (M7) -- (M9);
            \draw [color=uofgsandstone!60] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=6cm]
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofglawn, inner sep=2pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [very thick] (M6) -- (M7);
            \draw [draw=uofgsandstone!60] (M7) -- (M8);
            \draw [draw=uofgsandstone!60] (M8) -- (M9);
        \end{scope}
    \end{tikzpicture}
\end{frame}

\begin{frame}{Connectedness as a Constraint}
\end{frame}

\begin{frame}{Connectedness via Restricted Branching}
\end{frame}

\begin{nearlyplainframe}[t]{Constraint, Branching, or Both?}
    \only<1>{
        \begin{center}
            \includegraphics*{gen-graph-connected-cumulative-cp.pdf}
        \end{center}
    }
    \only<2>{
        \begin{center}
            \includegraphics*{gen-graph-connected-heatmap-cp.pdf}
        \end{center}
    }
\end{nearlyplainframe}

\begin{frame}{Connectedness in Clique-Like Algorithms}
    \begin{itemize}
        \item Connectedness doesn't decompose cleanly into binary constraints, so we can't encode it
            as microstructure.
        \item On the other hand, we \emph{can} use restricted branching, if we give more information
            to the clique algorithm.
            \begin{itemize}
                \item Integrating this with the bound and ordering heuristic is horribly technical.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{nearlyplainframe}[t]{Which is Better Now?}
    \only<1>{
        \begin{center}
            \includegraphics*{gen-graph-connected-cumulative.pdf}
        \end{center}
    }

    \only<2>{
        \begin{center}
            \includegraphics*{gen-graph-connected-heatmap.pdf}
        \end{center}
    }
\end{nearlyplainframe}

\begin{frame}{Some Perspective}
    \begin{itemize}
        \item These instances are \emph{much} smaller than the ones we can solve for subgraph
            isomorphism (35 / 35 vertices versus 1,000 / 10,000 vertices).
    \end{itemize}
\end{frame}

\begin{frame}{Other Things}
    \begin{itemize}
        \item Parallelism?
            \begin{itemize}
                \item Decomposition EPS-style for MCS is reported to be not particularly wonderful,
                    and for clique it's a really bad idea.
                \item Dynamic decomposition for clique is well-studied and gives extremely good
                    speedups when done in a particular way (but has yet to be implemented beyond
                    shared memory).
            \end{itemize}
        \item I think we can improve the clique algorithm.
            \begin{itemize}
                \item The bound sometimes does silly things with association graphs.
                \item Can we do fancier or cheaper propagation?
                \item Better vertex ordering?
            \end{itemize}
        \item Other side constraints?
        \item Connectedness in directed graphs?
    \end{itemize}
\end{frame}

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        \href{mailto:c.mccreesh.1@research.gla.ac.uk}{\nolinkurl{c.mccreesh.1@research.gla.ac.uk}} \\
    \end{center}

    \begin{tikzpicture}[remember picture, overlay]
        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -3.2cm);
            \end{tikzpicture}
        };
    \end{tikzpicture}
\end{frame}

\end{document}

### 2016-08-30 talk/talk.tex
Use the white background logo
Reorder
CP Model

@@
                 \begin{center}
-                \includegraphics*[keepaspectratio=true,scale=0.4]{UoG_keyline.pdf} \\[0.15cm]
+                \includegraphics*[keepaspectratio=true,scale=0.45]{UoG_colour.pdf} \\[0.15cm]
                     \colorbox{white}{\includegraphics*[keepaspectratio=true,scale=0.14]{Universite_Lyon_1.pdf}}\\[0.15cm]
@@
 \begin{frame}{CP Models}
+    \begin{itemize}
+        \item One variable for each vertex in the smaller input graph.
+        \item Domains range over vertices in the other input graph, plus $\bot$.
+        \item Objective is to maximise variables not assigned $\bot$.
+        \item Adjacent pairs of non-$\bot$ vertices must be mapped to adjacent pairs of vertices.
+        \item Non-adjacent pairs of non-$\bot$ vertices must be mapped to non-adjacent pairs of vertices.
+        \item All different except $\bot$, with number of allowed $\bot$ occurrences controlled by
+            the objective variable.
+        \item Smallest domain first, prefer vertices of similar degree.
+    \end{itemize}
 \end{frame}
@@
             bounded degree graphs).
+        \item Unlabelled:
+            \begin{itemize}
+                \item Up to 35 vertices.
+            \end{itemize}
         \item Labels on vertices and edges:
@@
                 \item Number of labels is 33\% of the number of vertices.
-            \end{itemize}
-        \item Unlabelled:
-            \begin{itemize}
-                \item Up to 35 vertices.
             \end{itemize}

### 2016-08-30 talk/talk.tex
Describe the two CP approaches

@@
 \begin{frame}{Connectedness as a Constraint}
+    \begin{itemize}
+        \item Once we have assigned one variable to a non-$\bot$ value, traverse the variable graph,
+            ignoring any variables assigned to $\bot$. Assign any unvisited variables to $\bot$.
+        \item Repeat whenever any variable is assigned to $\bot$ during search.
+        \item Also, traverse the value graph, ignoring any values not present in any domain. Remove
+            any unvisited values from every domain.
+        \item Repeat whenever a value is removed from every domain during search.
+    \end{itemize}
 \end{frame}
@@
 \begin{frame}{Connectedness via Restricted Branching}
+    \begin{itemize}
+        \item When selecting a variable for branching (except for the first variable), only select
+            from variables which are adjacent to at least one variable already assigned to
+            non-$\bot$.
+        \item If no such variable exists, assign every remaining domain to $\bot$.
+    \end{itemize}
 \end{frame}

### 2016-09-02 talk/talk.tex
Split this in two

@@
 
-\begin{frame}{Connectedness as a Constraint}
+\begin{frame}{Connectedness as a Constraint (on Variables)}
     \begin{itemize}
@@
         \item Repeat whenever any variable is assigned to $\bot$ during search.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Connectedness as a Constraint (on Values)}
+    \begin{itemize}
         \item Also, traverse the value graph, ignoring any values not present in any domain. Remove
@@
             \begin{itemize}
-                \item Integrating this with the bound and ordering heuristic is horribly technical.
+                \item Integrating this with the bound and ordering heuristic used in modern clique
+                    algorithms is horribly technical and was far harder than we make it look in the
+                    paper (honest!).
             \end{itemize}

### 2016-09-07 talk/talk.tex
More animation

@@
     \begin{itemize}
+        \item We can do better than just verifying connectedness:
+            \begin{itemize}
                 \item Once we have assigned one variable to a non-$\bot$ value, traverse the variable graph,
@@
             \end{itemize}
+    \end{itemize}
+
+    \vspace{1em}
+
+    \begin{center}
+    \begin{tikzpicture}[scale=0.75]%{{{
+        \begin{scope}
+            \node <1>   [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node <2->  [draw, circle, fill=uofgcobalt, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node[draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mb) at (2, 0) {\phantom{0}};
+            \node <1-2> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mc) at (2, -2) {\phantom{0}};
+            \node <3->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mc) at (2, -2) {\phantom{0}};
+            \node <1-3> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Md) at (4, 0) {\phantom{0}};
+            \node <4->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Md) at (4, 0) {\phantom{0}};
+            \node <1-4> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Me) at (4, -2) {\phantom{0}};
+            \node <1-4> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mf) at (6, -2) {\phantom{0}};
+            \node <5->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Me) at (4, -2) {\phantom{0}};
+            \node <5->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mf) at (6, -2) {\phantom{0}};
+
+            \draw <1-2> [very thick] (Mc) -- (Me);
+            \draw <1-2> [very thick] (Ma) -- (Mc);
+            \draw <1-2> [very thick] (Mb) -- (Mc);
+
+            \draw <3->  [color=uofgsandstone!60] (Mc) -- (Me);
+            \draw <3->  [color=uofgsandstone!60] (Ma) -- (Mc);
+            \draw <3->  [color=uofgsandstone!60] (Mb) -- (Mc);
+
+            \draw <1-3> [very thick] (Mb) -- (Md);
+            \draw <1-3> [very thick] (Md) -- (Me);
+            \draw <4->  [color=uofgsandstone!60] (Mb) -- (Md);
+            \draw <4->  [color=uofgsandstone!60] (Md) -- (Me);
+
+            \draw <1-4> [very thick] (Me) -- (Mf);
+            \draw <5->  [color=uofgsandstone!60] (Me) -- (Mf);
+
+            \draw [very thick] (Ma) -- (Mb);
+        \end{scope}
+    \end{tikzpicture}
+    \end{center}
 \end{frame}
@@
 \begin{frame}{Connectedness as a Constraint (on Values)}
+    \begin{itemize}
+        \item We can do something similar on the dual viewpoint:
             \begin{itemize}
@@
         \end{itemize}
+    \end{itemize}
+
+    \vspace{1em}
+
+    \begin{center}
+    \begin{tikzpicture}[scale=0.75]%{{{
+        \begin{scope}
+            \node <1>   [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node <2->  [draw, circle, fill=uofgcobalt, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node <1->  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mb) at (1, -1) {\phantom{0}};
+            \node <1->  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mc) at (1, 1) {\phantom{0}};
+            \node <1-2>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <3->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <1-3>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Me) at (3, -1) {\phantom{0}};
+            \node <1-3>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mf) at (3, 1) {\phantom{0}};
+            \node <1-3>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mg) at (4, 0) {\phantom{0}};
+            \node <4->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Me) at (3, -1) {\phantom{0}};
+            \node <4->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mf) at (3, 1) {\phantom{0}};
+            \node <4->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mg) at (4, 0) {\phantom{0}};
+
+            \draw <1-2> [very thick] (Mb) -- (Md);
+            \draw <1-2> [very thick] (Mc) -- (Md);
+            \draw <1-2> [very thick] (Md) -- (Me);
+            \draw <1-2> [very thick] (Md) -- (Mf);
+            \draw <3->  [draw=uofgsandstone!60] (Mb) -- (Md);
+            \draw <3->  [draw=uofgsandstone!60] (Mc) -- (Md);
+            \draw <3->  [draw=uofgsandstone!60] (Md) -- (Me);
+            \draw <3->  [draw=uofgsandstone!60] (Md) -- (Mf);
+
+            \draw <1-3> [very thick] (Me) -- (Mg);
+            \draw <1-3> [very thick] (Mf) -- (Mg);
+            \draw <4->  [draw=uofgsandstone!60] (Me) -- (Mg);
+            \draw <4->  [draw=uofgsandstone!60] (Mf) -- (Mg);
+
+            \draw [very thick] (Ma) -- (Mb);
+            \draw [very thick] (Ma) -- (Mc);
+        \end{scope}
+    \end{tikzpicture}
+    \end{center}
 \end{frame}
@@
     \begin{itemize}
+        \item The following heretical approach is due to Vismara and Valery.
         \item When selecting a variable for branching (except for the first variable), only select
@@
     \end{itemize}
+
+    \vspace{1em}
+
+    \begin{center}
+    \begin{tikzpicture}[scale=1.25]%{{{
+        \begin{scope}
+            \node <1>   [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node <2->  [draw, circle, fill=uofgcobalt, inner sep=2.5pt, font=\normalsize] (Ma) at (0, 0) {\phantom{0}};
+            \node <1-3> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mb) at (1, 0) {\phantom{0}};
+            \node <4->  [draw, circle, fill=uofgpumpkin, inner sep=2.5pt, font=\normalsize] (Mb) at (1, 0) {\phantom{0}};
+            \node <1-6>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mc) at (1, -1) {\phantom{0}};
+            \node <7->  [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mc) at (1, -1) {\phantom{0}};
+            \node <1-2> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <1-2> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Me) at (2, -1) {\phantom{0}};
+            \node <3-4>  [draw, circle, dotted, fill=white, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <5>  [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <6->  [draw, circle, fill=uofglawn, inner sep=2.5pt, font=\normalsize] (Md) at (2, 0) {\phantom{0}};
+            \node <3-7>  [draw, circle, dotted, fill=white, inner sep=2.5pt, font=\normalsize] (Me) at (2, -1) {\phantom{0}};
+            \node <8->  [draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2.5pt, font=\normalsize] (Me) at (2, -1) {\phantom{0}};
+            \node <1-2> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mf) at (3, 0) {\phantom{0}};
+            \node <3-7>  [draw, circle, dotted, fill=white, inner sep=2.5pt, font=\normalsize] (Mf) at (3, 0) {\phantom{0}};
+            \node <8-> [draw, circle, fill=white, draw=uofgsandstone!60, inner sep=2.5pt, font=\normalsize] (Mf) at (3, 0) {\phantom{0}};
+            \node <1-2> [draw, circle, fill=white, inner sep=2.5pt, font=\normalsize] (Mg) at (3, -1) {\phantom{0}};
+            \node <3-7>  [draw, circle, dotted, fill=white, inner sep=2.5pt, font=\normalsize] (Mg) at (3, -1) {\phantom{0}};
+            \node <8->  [draw, circle, draw=uofgsandstone!60, fill=white, inner sep=2.5pt, font=\normalsize] (Mg) at (3, -1) {\phantom{0}};
+
+            \draw [very thick] (Ma) -- (Mb);
+            \draw [very thick] (Mb) -- (Md);
+            \draw <1-6> [very thick] (Mc) -- (Me);
+            \draw <1-6> [very thick] (Ma) -- (Mc);
+            \draw <1-6> [very thick] (Mb) -- (Mc);
+            \draw <7-> [draw=uofgsandstone!60] (Mc) -- (Me);
+            \draw <7-> [draw=uofgsandstone!60] (Ma) -- (Mc);
+            \draw <7-> [draw=uofgsandstone!60] (Mb) -- (Mc);
+            \draw <1-7> [very thick] (Mf) -- (Mg);
+            \draw <8-> [draw=uofgsandstone!60] (Mf) -- (Mg);
+        \end{scope}
+    \end{tikzpicture}
+    \end{center}
 \end{frame}
@@
 
-\begin{frame}{Connectedness in Clique-Like Algorithms}
+\begin{frame}{Connectedness in Clique-Like Algorithms?}
     \begin{itemize}
-        \item Connectedness doesn't decompose cleanly into binary constraints, so we can't encode it
-            as microstructure.
-        \item On the other hand, we \emph{can} use restricted branching, if we give more information
-            to the clique algorithm.
+        \item Connectedness doesn't decompose cleanly into binary constraints,
+            so we can't encode it as microstructure.
+        \item Modern maximum clique algorithms use a special bound function
+            which doesn't allow us to branch arbitrarily. Adapting the
+            restricted branching rule to work with this would be horribly
+            complicated and no-one in their right mind would even attempt it.
             \begin{itemize}
-                \item Integrating this with the bound and ordering heuristic used in modern clique
-                    algorithms is horribly technical and was far harder than we make it look in the
-                    paper (honest!).
+                \item <2-> But we did it anyway. See the paper for how.
             \end{itemize}

### 2016-09-09 code/clique.cc
Show progress times

@@ -9,6 +9,12 @@
 #include <iostream>
 #include <atomic>
 #include <mutex>
+#include <numeric>
+#include <chrono>
+
+using std::chrono::duration_cast;
+using std::chrono::milliseconds;
+using std::chrono::steady_clock;
 
 namespace
 {
@@ -60,6 +66,8 @@ namespace
         std::mutex mutex;
         std::vector<unsigned> c;
 
+        std::chrono::time_point<std::chrono::steady_clock> start_time;
+
         void update(const std::vector<unsigned> & new_c)
         {
             while (true) {
@@ -69,7 +77,8 @@ namespace
                     if (value.compare_exchange_strong(current_value, new_c_size)) {
                         std::unique_lock<std::mutex> lock(mutex);
                         c = new_c;
-                        std::cerr << "-- " << new_c.size() << std::endl;
+                        std::cerr << "-- " << (duration_cast<milliseconds>(steady_clock::now() - start_time)).count()
+                            << " " << new_c.size() << std::endl;
                         break;
                     }
                 }
@@ -101,6 +110,8 @@ namespace
             nodes(0),
             vertices_adjacent_to_by_g1(g1.size)
         {
+            incumbent.start_time = params.start_time;
+
             // populate our order with every vertex initially
             std::iota(order.begin(), order.end(), 0);
 
